### 2013-03-05 main.tex
Initial commit

\documentclass{article}

%\usepackage{hyperref}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage{amsmath}  % Maths
\usepackage{amsfonts} % Maths
\usepackage{amssymb}  % Maths
\usepackage{stmaryrd} % Maths (crochets doubles)

\usepackage{url}     % Mise en forme + liens pour URLs
\usepackage{array}   % Tableaux évolués

\usepackage{comment}

\usepackage{prettyref}
\newrefformat{def}{Def.~\ref{#1}}
\newrefformat{fig}{Fig.~\ref{#1}}
\newrefformat{pro}{Property~\ref{#1}}
\newrefformat{pps}{Proposition~\ref{#1}}
\newrefformat{lem}{Lemma~\ref{#1}}
\newrefformat{thm}{Theorem~\ref{#1}}
\newrefformat{sec}{Sect.~\ref{#1}}
\newrefformat{ssec}{Subsect.~\ref{#1}}
\newrefformat{suppl}{Appendix~\ref{#1}}
\newrefformat{eq}{Eq.~\eqref{#1}}
\def\pref{\prettyref}

\usepackage{ntheorem}
\theorembodyfont{\upshape}
\newtheorem{definition}{Definition}{}{}
\newtheorem*{example}{Example}{}{}
%\newtheorem{property}{Property}{}{}
%\newtheorem{proposition}{Proposition}{}{}

\usepackage{tikz}
\newdimen\pgfex
\newdimen\pgfem
\usetikzlibrary{arrows,shapes,shadows,scopes}
\usetikzlibrary{positioning}
\usetikzlibrary{matrix}
\usetikzlibrary{decorations.text}
\usetikzlibrary{decorations.pathmorphing}

\input{macros/macros}
\input{macros/macros-ph}
%\input{macros/macros-grn}

% Macros
\newcommand{\sN}{\mathbb{N}}
\def\DEF{\stackrel{\Delta}=}
\def\EQDEF{\stackrel{\Delta}\Leftrightarrow}
\newcommand{\segm}[2]{\llbracket #1; #2 \rrbracket}
\def\indexes#1{\mathbb{I}^{#1}}
\newcommand{\sfp}[3]{\mathbf{sfp}\{#1\}\left(#2\mapsto#3\right)}
%\def\lfp{\f{pppf}\;}

% Commandes À FAIRE
\usepackage{color} % Couleurs du texte
\newcommand{\towrite}[1]{\textcolor{blue}{#1}}
\newcommand{\todo}[1]{\textcolor{red}{[#1]}}

% Id est
\newcommand{\ie}{i.e. }

% Césures
\hyphenation{pa-ra-me-tri-za-tion}
\hyphenation{pa-ra-me-tri-za-tions}

\title{\todo{Le titre}}

\author{\todo{Les auteurs}}

\begin{document}

\maketitle

\begin{abstract}
\todo{L'abstract}
\end{abstract}

\section{Introduction}\label{sec:intro}
\towrite{Intro}

\section{The PH Framework}\label{sec:def-ph}
\todo{Définir les priorités fixes}
\input{parts/def-ph}

\section{Static analysis}\label{sec:sa}
\towrite{Reprendre définitions de l'analyse statique}
\todo{Ajouts pour les priorités fixes}
\input{parts/sa}

\section{Example}\label{sec:example}
\todo{Trouver un exemple représentatif (comportement différent avec / sans priorités)}
\towrite{Exemple}

\section{Discussion \& Conclusion}\label{sec:ccl}
\towrite{Pistes :
\begin{itemize}
  \item Modèles Zeno (système de précédences et prise en compte des états globaux)
\end{itemize}
}

\bibliographystyle{plain}
\bibliography{biblio}

%\input{parts/contributions}

\end{document}

### 2013-03-05 parts/def-ph.tex
Initial commit

\subsection{The Process Hitting framework}
\label{ssec:PH}

\towrite{Transition.}

\towrite{Reformuler (actuellement trop proche de CMSB)}
A PH (\pref{def:PH}) gathers a finite number of concurrent \emph{processes} grouped into a finite set of \emph{sorts}.
A process belongs to a unique sort and is noted $a_i$ where $a$ is the sort and $i$ the identifier of the process within the sort $a$.
At any time, one and only one process of each sort is present; a state of the PH thus corresponds to the set of such processes.

The concurrent interactions between processes are defined by a set of \emph{actions} divided into classes of priorities.
Actions describe the replacement of a process by another of the same sort conditioned by the presence of at most one other process and by the fact that no other action of higher priority is playable in the current state of the PH.
An action is denoted by $\PHhit{a_i}{b_j}{b_k}$ where $a_i,b_j,b_k$ are processes of sorts $a$ and $b$.
It is required that $b_j \neq b_k$ and that $a=b\Rightarrow a_i=b_j$.
An action $h=\PHfrappe{a_i}{b_j}{b_k}$ is read as ``$a_i$ \emph{hits} $b_j$ to make it bounce to $b_k$'', and $a_i,b_j,b_k$ are called respectively \emph{hitter}, \emph{target} and \emph{bounce} of the action, and can be referred to as $\PHhitter(h), \PHtarget(h), \PHbounce(h)$, respectively.

\begin{comment}
\begin{definition}[Process Hitting]\label{def:PH}
A \emph{Process Hitting} is a triple $(\PHs,\PHl,\PHa)$:
\begin{itemize}
\item $\PHs \DEF \{a,b,\dots\}$ is the finite set of \emph{sorts};
\item $\PHl \DEF \prod_{a\in\PHs} \PHl_a$ is the set of states with $\PHl_a = \{a_0,\dots,a_{l_a}\}$
the finite set of \emph{processes} of sort $a\in\Sigma$ and $l_a$ a positive integer with
	$a\neq b\Rightarrow \forall(a_i,b_j)\in\PHl_a\times\PHl_b,a_i\neq b_j$;
\item $\PHa \DEF \{ \PHfrappe{a_i}{b_j}{b_k}, \dots \mid
					(a,b)\in\PHs^2 \wedge (a_i,b_j,b_k)\in \PHl_a\times\PHl_b\times\PHl_b$ \\
	\hspace*{2cm} $\wedge b_j\neq b_k \wedge a=b\Rightarrow a_i=b_j\}$
			is the finite set of \emph{actions}.
\end{itemize}
$\PHproc$ denotes the set of all processes ($\PHproc \DEF \{ a_i\mid a\in\PHs \wedge a_i\in\PHl_a\}$).
\end{definition}
\end{comment}

\begin{definition}[Process Hitting with $k$ priorities] \towrite{Revoir terminologie}
  A \emph{Process Hitting with $k$ priorities}, where $k \in \sN^*$, is a triplet $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$, with $\PHa^{\langle k \rangle} = (\PHa^{(1)}; \dots; \PHa^{(k)})$ a $k$-uplet, where:
  \begin{itemize}
    \item $\PHs \DEF \{a,b,\dots\}$ is the finite set of \emph{sorts}.
    \item $\PHl \DEF \prod_{a \in \PHs} \PHl_a$ is the finite set of states, where $\PHl_a = \{a_0 ; \ldots ; a_{l_a}\}$ is the finite set of \emph{processes} of sort $a \in \PHs$ and $l_a \in \sN^*$. Each process belongs to a unique sort: $\forall (a_i; b_j) \in \PHl_a \times \PHl_b, a \neq b \Rightarrow a_i \neq b_j$.
    \item $\forall n \in \llbracket 1; k \rrbracket, \PHa^{(n)} \DEF \{\PHfrappe{a_i}{b_j}{b_k} \mid (a; b) \in \PHs^2 \wedge (a_i; b_j; b_k) \in \PHl_a \times \PHl_b \times \PHl_b \wedge b_j \neq b_k \wedge a = b \Rightarrow a_i = b_j \}$ is the finite set of \emph{actions of priority $n$}.
  \end{itemize}
  We call $\PHproc \DEF \bigcup_{a \in \PHs} \PHl_a$ the set of all processes, and $\PHh \DEF \bigcup_{n \in \segm{1}{k}} \PHh^{(n)}$ the set of all actions.
\end{definition}

\noindent
The sort of a process $a_i$ is referred to as $\PHsort(a_i)=a$ and the set of sorts present in an action $h\in\PHa$ as $\PHsort(h) = \{\PHsort(\PHhitter(h)),\PHsort(\PHtarget(h))\}$.
Given a state $s\in \PHl$, the process of sort $a\in\PHs$ present in $s$ is denoted by $\PHget{s}{a}$, that is the $a$-coordinate of the state $s$.
If $a_i\in \PHl_a$, we define the notation $a_i\in s \EQDEF \PHget{s}{a}=a_i$.

An action $h = \PHhit{a_i}{b_j}{b_k} \in \PHa^{(n)}$ of priority $n$ is \emph{playable} in $s \in \PHl$ iff $\PHget{s}{a} = a_i$, $\PHget{s}{b} = b_j$ and $\forall m < n, \forall g \in \PHa^{(m)}$, $g$ is not playable in $s$.
%Dans un tel cas, l'état résultant du jeu de l'action $h$ dans $\etat$ est dénoté $(\etat \PHjoue h)$, où $\PHget{(\etat \PHjoue h)}{b} = b_k$ et $\forall c \in \PHs, c \neq b \Rightarrow \PHget{(\etat \PHjoue h)}{c} = \PHget{\etat}{c}$.
%
%An action $h=\PHhit{a_i}{b_j}{b_k} \in\PHa$ is \emph{playable} in $s \in L$ if and only if $\PHget{s}{a} = a_i$ and $\PHget{s}{b} = b_j$.
In such a case, $(s \PHplay h)$ stands for the state resulting from the play of the action $h$ in $s$, that is $\PHget{(s \PHplay h)}{b} = b_k$ and $\forall c\in\PHs, c\neq b, \PHget{(s\PHplay h)}{c} = \PHget{s}{c}$.
For the sake of clarity, for all $h, h'\in\PHa$, $((s\PHplay h)\PHplay h')$ is abbreviated as $(s\PHplay h\PHplay h')$.

\begin{comment} %example*
\pref{fig:runningPH-1} represents a PH $(\PHs,\PHl,\PHa)$ with
$\PHs = \{a,b,c\}$,
$\PHl_a = \{a_0,a_1,a_2\}$,
$\PHl_b = \{b_0, b_1\}$,
$\PHl_c = \{c_0, c_1\}$, and
\begin{align*}
\PHa & = \{
	\PHfrappe{a_2}{b_1}{b_0},
&&  \PHfrappe{b_0}{a_2}{a_1},
&&	\PHfrappe{c_0}{a_2}{a_1},\\
&&& \PHfrappe{b_0}{a_1}{a_0},
&&	\PHfrappe{c_0}{a_1}{a_0},\\
&&& \PHfrappe{b_1}{a_0}{a_1},
&&	\PHfrappe{c_1}{a_0}{a_1},\\
&&& \PHfrappe{b_1}{a_1}{a_2},
&&	\PHfrappe{c_1}{a_1}{a_2} \}\enspace.
\end{align*}
The action $h=\PHfrappe{b_1}{a_1}{a_2}$ is playable in the state
$s = \PHstate{b_1,a_1,c_0}$; and $s\PHplay h=\PHstate{b_1,a_2,c_0}$.
%
\begin{figure}[t]
\centering
\scalebox{1.3}{
\begin{tikzpicture}
\TSort{(0,0)}{a}{3}{r}
\TSort{(-3,0.5)}{b}{2}{l}
\TSort{(3,0.5)}{c}{2}{r}
%
\THit{b_1}{very thick}{a_0}{.west}{a_1}
\THit{b_1}{very thick}{a_1}{.north west}{a_2}
\THit{b_0}{}{a_2}{.west}{a_1}
\THit{b_0}{}{a_1}{.west}{a_0}
%
\path[bounce, bend left=60]
\TBounce{a_1}{very thick}{a_2}{.south}
\TBounce{a_0}{very thick}{a_1}{.south}
;
\path[bounce, bend right=60]
\TBounce{a_2}{}{a_1}{.north}
\TBounce{a_1}{}{a_0}{.north}
;
%
\THit{c_1}{very thick}{a_0}{.east}{a_1}
\THit{c_1}{very thick}{a_1}{.north east}{a_2}
\THit{c_0}{}{a_2}{.east}{a_1}
\THit{c_0}{}{a_1}{.east}{a_0}
%
\path[bounce, bend right=60]
\TBounce{a_1}{very thick}{a_2}{.south east}
\TBounce{a_0}{very thick}{a_1}{.south east}
;
\path[bounce, bend left=60]
\TBounce{a_2}{}{a_1}{.north}
\TBounce{a_1}{}{a_0}{.north east}
;
%
\THit{a_2}{bend right}{b_1}{.north east}{b_0}
\path[bounce, bend left=80]
\TBounce{b_1}{out=100,in=140}{b_0}{.north}
;
\end{tikzpicture}
}
\caption{\label{fig:runningPH-1}
A Process Hitting (PH) example.
Sorts are represented by labeled boxes, and processes by circles (ticks are
the identifiers of the processes within the sort, for instance, $a_0$ is the
process ticked $0$ in the box $a$).
An action (for instance $\PHfrappe{b_1}{a_1}{a_2}$) is represented by a pair of
directed arcs, having the hit part ($b_1$ to $a_1$) in plain line and the bounce
part ($a_1$ to $a_2$) in dotted line.
Actions involving $b_1$ or $c_1$ are in thick lines.
%The current state is represented by the grayed processes:
%$\PHstate{a_0,b_1,c_0,d_0}$.
}
\end{figure}

This PH example actually models a BRN where the component $a$ has three qualitative
levels and components $b$ and $c$ are boolean.
In this BRN, $b$ and $c$ activate $a$, while $a$ inhibits $b$.
The inhibition of $b$ by $a$ is only effective when $a$ is at level $2$;
in the other cases, $b$ cannot evolve in any direction.
The activation of $a$ by $b$ ($c$) is encoded by the actions making the level of $a$ increase (resp.
decrease) when $b$ ($c$) is present (resp. absent).
It is worth noticing that the activation of $a$ by $b$ ($c$) is independent from $c$ ($b$).
This may express a lack of knowledge on the cooperation between these two regulators:
we thus model an over-approximation of the possible actions.
\end{example*}
\end{comment}

\paragraph{Modeling cooperation.}
\towrite{Sortes coopératives avec mise à jour prioritaire (pas de décalage temporel)}
As described in \cite{PMR10-TCSB}, the cooperation between processes to make another bounce can be
expressed in PH by building a \emph{cooperative sort}.
\pref{fig:PH-cooperativity} shows an example of cooperation between processes $b_1$ and $c_1$ to
make $a_1$ bounce to $a_2$:
a cooperative sort $bc$ is defined with 4 processes (one for each sub-state of the presence of
processes $b_1$ and $c_1$).
For the sake of clarity, the $bc$ processes are indexed using the sub-state they represent.
Hence, $bc_{01}$ represents the sub-state $\PHstate{b_0,c_1}$, and so on.
Each process of sort $b$ and $c$ hit $bc$ to make it bounce to the process reflecting the status of the sorts $b$
and $c$ (e.g., $\PHfrappe{b_1}{bc_{00}}{bc_{10}}$ and $\PHfrappe{b_1}{bc_{01}}{bc_{11}}$).
Then, it is the process $bc_{11}$ which hits $a_1$ to make it bounce to $a_2$ instead of the
independent hits from $b_1$ and $c_1$.

\begin{figure}[p]
\centering
\scalebox{1.3}{
\begin{tikzpicture}
\TSort{(0,0)}{b}{2}{t}
\TSort{(0,-3.8)}{c}{2}{b}
\TSort{(4.5,-3)}{a}{3}{r}

\TSetTick{bc}{0}{00}
\TSetTick{bc}{1}{01}
\TSetTick{bc}{2}{10}
\TSetTick{bc}{3}{11}
% \TSetSortLbcel{bc}{$\neg a\wedge b$}
\TSort{(-0.5,-2)}{bc}{4}{b}

\THit{b_1}{very thick,bend right}{bc_0}{.north}{bc_2}
\THit{b_1}{very thick,bend right}{bc_1}{.north}{bc_3}
\THit{b_0}{}{bc_2}{.north west}{bc_0}
\THit{b_0}{}{bc_3}{.north west}{bc_1}

\THit{c_0}{}{bc_1}{.south}{bc_0}
\THit{c_0}{}{bc_3}{.south}{bc_2}
\THit{c_1}{very thick}{bc_0}{.south}{bc_1}
\THit{c_1}{very thick}{bc_2}{.south}{bc_3}

\path[bounce, bend right=25]
\TBounce{bc_2}{}{bc_0}{.north east}
\TBounce{bc_3}{}{bc_1}{.north east}
;
\path[bounce, bend left=80, distance=30]
\TBounce{bc_0}{very thick}{bc_2}{.north}
\TBounce{bc_1}{very thick}{bc_3}{.north}
;
\path[bounce, bend right]
\TBounce{bc_0}{very thick}{bc_1}{.west}
\TBounce{bc_2}{very thick}{bc_3}{.west}
;
\path[bounce, bend left]
\TBounce{bc_3}{}{bc_2}{.east}
\TBounce{bc_1}{}{bc_0}{.east}
;

\THit{bc_3}{}{a_1}{.west}{a_2}
\path[bounce, bend left=40]
\TBounce{a_1}{}{a_2}{.south west}
;

\end{tikzpicture}
}

\caption{\label{fig:PH-cooperativity}
\towrite{Ajouter priorités}
A PH modeling a cooperativity between $b_1$ and $c_1$ to make
$a_1$ bounce to $a_2$.
Actions involving $b_1$ or $c_1$ are in thick lines.
}
\end{figure}

\begin{comment}
\begin{figure}[p]
\centering
\scalebox{1.3}{
\begin{tikzpicture}
\path[use as bounding box] (-4,-1.9) rectangle (4.5,3.9);
%
\TSort{(0,0)}{a}{3}{l}
\TSort{(3, 3)}{b}{2}{t}
\TSort{(3,-1)}{c}{2}{b}
%
\TSetTick{bc}{0}{00}
\TSetTick{bc}{1}{01}
\TSetTick{bc}{2}{10}
\TSetTick{bc}{3}{11}
% \TSetSortLbcel{bc}{$\neg a\wedge b$}
\TSort{(-3,-0.5)}{bc}{4}{l}
%
\THit{bc_3}{}{a_1}{.north west}{a_2}
\THit{bc_0}{}{a_1}{.south west}{a_0}
\path[bounce]
\TBounce{a_1}{bend left}{a_2}{.south west}
\TBounce{a_1}{bend right}{a_0}{.north west}
;
%
\THit{b_0}{}{a_2}{.east}{a_1}
\THit{b_1}{}{a_0}{.north east}{a_1}
\path[bounce]
\TBounce{a_2}{bend left}{a_1}{.north east}
\TBounce{a_0}{bend right=20}{a_1}{.south}
;
%
\THit{c_0}{bend right}{a_2}{.south east}{a_1}
\THit{c_1}{bend right}{a_0}{.east}{a_1}
\path[bounce]
\TBounce{a_2}{bend left=20}{a_1}{.north}
\TBounce{a_0}{bend right=30}{a_1}{.south east}
;
%
\path[dashed,hit]
	(2,-1.3) edge[bend left=10] (-2.3,-0.7)
	(2.2, 3.3) edge[bend right=10] (-2.3,3)
;
%
\THit{a_2}{bend left,out=40,in=80}{b_1}{.north west}{b_0}
\path[bounce, bend right]
\TBounce{b_1}{}{b_0}{.east}
;
%
\end{tikzpicture}
}
%
\caption{\label{fig:runningPH-2}
PH resulting from the refinement of the one in \pref{fig:runningPH-1} by the
specification of several cooperations.
The actions from $b$ and $c$ to the cooperative sort $bc$ are identical to those defined in
\pref{fig:PH-cooperativity} and are represented here by a single dashed arc.
}
\end{figure}
\end{comment}

We note that cooperative sorts are standard PH sorts and do not involve any
special treatment regarding the semantics of related actions.

When the number of cooperating processes is large, it is possible to chain several cooperative sorts
to prevent the combinatoric explosion of the number of processes created within cooperative sorts.
For instance, if $b_1$, $c_1$, and $d_1$ cooperate, one can create a cooperative sort $bc$ with 4
processes reflecting the presence of $b_1$ and $c_1$, and a cooperative sort $bcd$ with 4 processes
reflecting the presence of $bc_{11}$ and $d_1$.  Such constructions are helpful in PH
as the static analysis of dynamics developed in \cite{PMR12-MSCS} does not suffer from the number of
sorts, but on the number of processes within a single sort.

While the construction of cooperation in PH allows to encode any boolean functions
between cooperating processes \cite{PMR10-TCSB}, it is worth noticing they introduce a temporal
shift in their application.
This allows the existence of interleaving of actions leading to a cooperative sort representing a
past sub-state of the presence of the cooperative processes.
The resulting behavior is then an over-approximation
of the realization of an instantaneous cooperation.

\begin{example*}
The PH in \pref{fig:runningPH-2} results from the refinement of the PH in \pref{fig:runningPH-1}
where several cooperations have been specified.
In particular, the bounce to $a_2$ is the result of a cooperation between $b_1$ and $c_1$; and the
bounce to $a_0$ of a cooperation between $b_0$ and $c_0$.
Hence, this PH expresses a BRN where $a$ requires both $b$ and $c$ active to reach its
highest level, and $a$ does not become inactive unless both $b$ and $c$ are inactive.
\end{example*}

\todo{Modèles non-Zeno (OU : sans domaines-pièges)}

### 2013-03-05 parts/sa.tex
Initial commit

\towrite{Idée : prise en compte des actions perturbatrices, ou des réactions en chaîne pouvant rendre de telles actions jouables}

\newcommand{\abstr}[1]{#1^\wedge}%\text{\textasciicircum}}
\def\BS{\mathbf{BS}}
\def\prio{\mathbf{prio}}

Séquences de bonds abstraites :
$$\BS^\wedge(P) = \{ \zeta^\wedge \mid \zeta \in \BS(P), \nexists \zeta' \in \BS(P), \zeta'^\wedge \subsetneq \zeta^\wedge \}$$
where $\zeta^\wedge = (\zeta^\wedge_A, \zeta^\wedge_B, \zeta^\wedge_{max})$ with:
\begin{itemize}
  \item $\zeta^\wedge_A = \{ \PHhitter(\zeta_n) \mid n \in \indexes{\zeta} \wedge \PHsort(\PHhitter(\zeta_n)) \neq \PHsort(P) \}$ : ens. des requis d'autres sortes (frappeurs)
  \item $\zeta^\wedge_B = \{ \PHhitter(\zeta_n) \mid n \in \indexes{\zeta} \} \cup \{ \PHtarget(\zeta_n) \mid n \in \indexes{\zeta} \}$ : ens. des processus nécessaires (à ne pas perturber)
  \item $\zeta^\wedge_{max} = \max_{n \in \indexes{\zeta}}(\prio(\zeta_n))$ : plus faible priorité
\end{itemize}

Voisinage :
\begin{equation*}
\begin{split}
    V: \wp(\PHproc) \times \segm{1}{k} &\rightarrow \wp(\PHh) \\
    (ps; m) &\mapsto \sfp{\PHh^{(m)+}_{cibles}(ps)}{hs}{\PHh^{(m)+)}_{bonds}(\widehat{B}(hs)) \cup hs)}
  \end{split}
\end{equation*}
where:
\begin{equation*}
\begin{split}
    \widehat{B}: \wp(\PHh) &\rightarrow \wp(\PHproc) \\
    hs &\mapsto \{ \PHhitter(h) \mid h \in hs \} \cup \{ \PHtarget(h) \mid h \in hs \}
  \end{split}
\end{equation*}
\begin{equation*}
\begin{split}
    \PHh^{(m)+}_{\mathsf{ref}}: \wp(\PHproc) &\rightarrow \wp(\PHh) \quad,\quad m \in \segm{0}{k} \text{ and } \mathsf{ref} \in \{ \PHhitter, \PHtarget, \PHbounce \} \\
    ps &\mapsto \{ h \in \PHh \mid \mathsf{ref}(h) \in ps \wedge \prio(h) \leq m \}
  \end{split}
\end{equation*}

### 2013-03-08 parts/def-ph.tex
add defs

@@
 
-\todo{Modèles non-Zeno (OU : sans domaines-pièges)}
+\todo{Modèles non-Zeno / sans cycles (OU : sans domaines-pièges)}
+
+\todo{+ Restriction : toutes les actions frappant une sorte ont la même priorité :}
+$$\forall h_1, h_2 \in \PHh, \PHtarget(h_1) = \PHtarget(h_2) \Rightarrow \prio(h_1) = \prio(h_2) = \prio(\PHsort(\PHtarget(h_1)))$$

### 2013-03-08 parts/sa.tex
add defs

@@
 \def\BS{\mathbf{BS}}
-\def\prio{\mathbf{prio}}
+%\def\priomax{\mathsf{prio}_{max}}
+\def\procs{\mathsf{procs}}
+\def\allprocs{\mathsf{allProcs}}
+\def\pfp{\mathsf{pfp}}
 
+\def\ctx{\varsigma}
+\def\w{\omega}
+\def\aBS{\abstr{\BS}}
+
+\def\Req{\mathrm{Req}}
+\def\Sol{\mathrm{Sol}}
+\def\Cont{\mathrm{Cont}}
+\def\A{\mathcal{A}}
+\def\cwA{\A_\ctx^\w}
+\def\cwReq{\Req_\ctx^\w}
+\def\cwSol{\Sol_\ctx^\w}
+\def\cwCont{\Cont_\ctx^\w}
+
+\def\aB{\mathcal{B}}
+\def\sat#1{\lceil #1\rceil}
+\def\cwB{\sat{\aB_\ctx^\w}}
+\def\mycwB#1#2{\sat{\aB_{#1}^{#2}}}
+\def\Bsol{\sat{\Sol^\w_\ctx}}
+\def\Breq{\sat{\Req^\w_\ctx}}
+\def\Bcont{\sat{\Cont^\w_\ctx}}
+
+\def\myB{\aB^\w_\ctx}
+\def\mysol{\overline{\Sol^\w_\ctx}}
+\def\myreq{\overline{\Req^\w_\ctx}}
+\def\mycont{\overline{\Cont^\w_\ctx}}
+
+%\def\mlfp#1{\f{pppf}\{#1\}}
+
+\def\PHobjp#1#2#3{\PHobj{{#1}_{#2}}{{#1}_{#3}}}
+\def\Obj{\mathbf{Obj}}
+\def\powerset{\wp}
+\def\gCont{\f{maxCont}}
+\def\w{\omega}
+
+Approximation : pour qu'une séquence de bonds soit jouable, il faut pouvoir atteindre tous les processus nécessaires depuis tous les points fixes possibles locaux, uniquement à l'aide d'actions de priorité maximale pour la sorte considérée.
+
+%Plus haute priorité :
+%$$\forall a \in \PHs, \priomax(a) = \max_{h \in \PHh, \PHtarget(h) = a}(\prio(h))$$
+
+Processus possibles :
+\begin{align*}
+\procs((\cwSol,\cwReq,\cwCont)) = \{ p \in \PHproc \mid & \exists (P,ps) \in \cwSol, p \in ps
+\\ & \vee p = \PHtarget(P)
+\\ & \vee (P \neq \omega \Rightarrow p = \PHbounce(P)) \}
+%\\ & \vee \exists h \in \BS(P), (p = \PHhitter(h) \vee p = \PHbounce(h)) \}
+\end{align*}
+
+Processus rencontrés :
+\begin{align*}
+\allprocs((\cwSol,\cwReq,\cwCont)) = \{ p \in \PHproc \mid & \exists (P,ps) \in \cwSol, p \in ps
+\\ & \vee p = \PHtarget(P)
+%\\ & \vee (P \neq \omega \Rightarrow p = \PHbounce(P)) \}
+\\ & \vee \exists h \in \BS(P), (p = \PHhitter(h) \vee p = \PHbounce(h)) \}
+\end{align*}
+
+\subsection{Local fixed points}
+Actions chaînées :
+\begin{align*}
+\PHh(a, b) = \{ (h_i)_{i \in \segm{0}{s}} \in \PHh^{s+1} &\mid s \in \sN, \PHsort(\PHhitter(h_0)) = a \wedge \PHsort(\PHtarget(h_n)) = b \\
+  & \wedge \prio(h_{s-1}) \leq n \wedge \forall i \in \segm{0}{s-1}, \\
+  & (\prio(h_i) \leq n \wedge \PHsort(\PHhitter(h_i)) = \PHsort(\PHtarget(h_{i+1}))) \}
+\end{align*}
+
+Voisinage :
+$$
+V(a) = \{ b \in \PHs \mid \PHh^n(a, b) \neq \emptyset \}
+$$
+
+Points fixes possibles : pour toute sorte $a$ et tout contexte partiel $\ctx$ sur $V^n(a)$:
+\begin{align*}
+  \pfp_\ctx: \PHs &\rightarrow \wp(\PHproc) \\
+  a &\mapsto \{ s \in \times_{b \in V^n(a)} \PHl_b \mid \text{$s$ est accessible depuis $\ctx$ et aucune action n'y est jouable} \}
+\end{align*}
+
+Points fixes possibles sur un ensemble de sortes :
+\begin{align*}
+  \pfp: \mathbb{A} &\rightarrow \wp(\PHproc) \\
+  \myB &\mapsto \bigcup_{a \in A} \pfp_{\allprocs(\myB)}(a)
+\end{align*}
+
+\begin{comment}
 Séquences de bonds abstraites :
@@
 \end{itemize}
+\end{comment}
 
+\subsection{Abstract structure}
+Séquences de bonds abstraites :
+$$\BS^\wedge(P) = \{ \zeta^\wedge \mid \zeta \in \BS(P), \nexists \zeta' \in \BS(P), \zeta'^\wedge \subsetneq \zeta^\wedge \}$$
+where:
+$$\zeta^\wedge = \{ \PHhitter(\zeta_n) \mid n \in \indexes{\zeta} \wedge \PHsort(\PHhitter(\zeta_n)) \neq \PHsort(P) \}$$
+
+The abstract structure $\cwB=(\Breq,\Bsol,\Bcont)$ is defined as
+$
+ \cwB = \sfp{\myB}{\myB}{\aB^\w_{\ctx \Cap (\procs(\myB) \cup \pfp(\myB))}}
+$,
+with $\myB=(\myreq,\mysol,\mycont)$:
+\begin{align*}
+\myreq = &\{ (a_i,\PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid a_j \in \PHget{\ctx}{a}
+  \wedge (\exists (P,ps) \in \mysol, a_i \in ps \\
+& \qquad\qquad
+          \vee \exists n \in \indexes{\w}, \PHbounce(\w)=a_i\}
+\\
+\mysol \subseteq & \{ (P,ps) \in \Obj \times \powerset(\PHproc) \mid
+        \exists (a_i,P)\in \myreq \wedge ps \in \aBS(P)  \}
+\\
+\mycont = & \{ (P,\PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid 
+        \exists (P,ps)\in \mysol \\
+&\qquad\qquad
+        \wedge q \in \gCont_\ctx(\PHs(P),P)\}
+\end{align*}
+
+\begin{comment}
 Voisinage :
@@
 \end{equation*}
+\end{comment}

### 2013-03-11 parts/def-ph.tex
Plus de formalisme

--- 2013-03-05 parts/def-ph.tex
@@
 
+\subsection{Definition of the Process Hitting with $k$ priorities}
 \towrite{Reformuler (actuellement trop proche de CMSB)}
@@
 
+% Process Hitting sans priorités
 \begin{comment}
@@
 For the sake of clarity, for all $h, h'\in\PHa$, $((s\PHplay h)\PHplay h')$ is abbreviated as $(s\PHplay h\PHplay h')$.
+
+\begin{definition}[Process Hitting $n$-reduction] \towrite{Revoir terminologie}
+  If $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$ is a Process Hitting with $k$ priorities and $n \in \segm{1}{k}$, we denote $\restriction{\PH}{n}$ \towrite{$\PH_{|n}$ $\PH'$} the $n$-reduction of $\PH$ the following Process Hitting with $n$ priorities, where:
+  $$\restriction{\PH}{n} = (\PHs; \PHl; \PHa^{\langle n \rangle})$$
+  and:
+  $$\PHa^{\langle n \rangle} = (\PHa^{(1)}; \dots; \PHa^{(n)})$$
+\end{definition}
 
@@
 
-\paragraph{Modeling cooperation.}
+\subsection{Modeling cooperation.}
 \towrite{Sortes coopératives avec mise à jour prioritaire (pas de décalage temporel)}
@@
 between cooperating processes \cite{PMR10-TCSB}, it is worth noticing they introduce a temporal
-shift in their application.
+shift in their application. \towrite{Adapter avec priorités}
 This allows the existence of interleaving of actions leading to a cooperative sort representing a
@@
 
-\todo{Modèles non-Zeno (OU : sans domaines-pièges)}
+\subsection{Restrictions} \towrite{Reformuler}
+
+In this section, we describe several restrictions.
+Although the definition of a Process Hitting with $k$ priorities allows a wide range of models, the method given in the next section only applies to Process Hitting models that regard these restrictions.
+
+Let $\PH$ be a PH model on which we want to apply the static analysis. This PH has to regard the two restrictions below.
+
+\paragraph{Cycle-freeness of $\restriction{\PH}{k-1}$}
+\towrite{Définition formelle ? + justification}
+The model $\restriction{\PH}{k-1}$ contains no cycles. Cycles are still allowed in $\PH$ however.
+
+\paragraph{Local priorities}
+\towrite{Justification}
+All actions hitting the same sort belong to the same class of priority:
+$$\forall h_1, h_2 \in \PHh, \PHtarget(h_1) = \PHtarget(h_2) \Rightarrow \prio(h_1) = \prio(h_2)$$
+Furthermore, for all sort $a$, we denote $\prio(a)$ the priority of the actions hitting $a$, if any:
+$$\forall a \in \PHs, \exists h \in \PHh, \PHtarget(h) = a \Rightarrow \prio(a) = \prio(h)$$
+\towrite{Ou : $\nexists h \Rightarrow \prio(a) = 0$}

### 2013-03-11 parts/sa.tex
Plus de formalisme

@@
 \def\pfp{\mathsf{pfp}}
+\def\pfpprocs{\mathsf{pfpProcs}}
 
@@
 
+%%% N'est plus utile (?)
 %Plus haute priorité :
@@
 \begin{align*}
-\procs((\cwSol,\cwReq,\cwCont)) = \{ p \in \PHproc \mid & \exists (P,ps) \in \cwSol, p \in ps
+\procs((\cwSol,\cwReq,\cwCont)) = \{ p \in \PHproc &\mid \exists (P,ps) \in \cwSol, p \in ps
 \\ & \vee p = \PHtarget(P)
@@
 \begin{align*}
-\allprocs((\cwSol,\cwReq,\cwCont)) = \{ p \in \PHproc \mid & \exists (P,ps) \in \cwSol, p \in ps
+\allprocs((\cwSol,\cwReq,\cwCont)) = \{ p \in \PHproc &\mid \exists (P,ps) \in \cwSol, p \in ps
 \\ & \vee p = \PHtarget(P)
@@
 
-Points fixes possibles : pour toute sorte $a$ et tout contexte partiel $\ctx$ sur $V^n(a)$:
+\towrite{Formaliser}
+
+%%% Pas utile
+%Points fixes possibles : pour toute sorte $a$ et tout contexte partiel $\ctx$ sur $V^n(a)$:
+%\begin{align*}
+%  \pfp_\ctx: \PHs &\rightarrow \wp(\PHproc) \\
+%  a &\mapsto \{ s \in \underset{b \in V^n(a)}{\times} \PHl_b \mid \text{$s$ est accessible depuis $\ctx$ et aucune action n'y est jouable} \}
+%\end{align*}
+
+Points fixes possibles : pour toute sorte $a$ et tout contexte $\ctx$:
 \begin{align*}
   \pfp_\ctx: \PHs &\rightarrow \wp(\PHproc) \\
-  a &\mapsto \{ s \in \times_{b \in V^n(a)} \PHl_b \mid \text{$s$ est accessible depuis $\ctx$ et aucune action n'y est jouable} \}
+  a &\mapsto \{ s \in \underset{b \in V^n(a)}{\times} \PHl_b \mid \text{$s$ est (localement) accessible dans $\restriction{\PH}{\prio(a)}$ depuis $\ctx$}\\
+  &\qquad\qquad\qquad\qquad \text{et aucune action n'y est jouable} \}
 \end{align*}
 
-Points fixes possibles sur un ensemble de sortes :
+Processus rencontrés comme résultats d'un point fixe :
 \begin{align*}
-  \pfp: \mathbb{A} &\rightarrow \wp(\PHproc) \\
-  \myB &\mapsto \bigcup_{a \in A} \pfp_{\allprocs(\myB)}(a)
+\pfpprocs_\ctx(a) = \{ \PHget{s}{a} \mid s \in \pfp_\ctx(a) \}
 \end{align*}
+
+%%% N'est plus adapté
+%Points fixes possibles sur un ensemble de sortes :
+%\begin{align*}
+%  \pfp: \mathbb{A} &\rightarrow \wp(\PHproc) \\
+%  \myB &\mapsto \bigcup_{a \in A} \pfp_{\allprocs(\myB)}(a)
+%\end{align*}
 
@@
 \subsection{Abstract structure}
-Séquences de bonds abstraites :
-$$\BS^\wedge(P) = \{ \zeta^\wedge \mid \zeta \in \BS(P), \nexists \zeta' \in \BS(P), \zeta'^\wedge \subsetneq \zeta^\wedge \}$$
-where:
-$$\zeta^\wedge = \{ \PHhitter(\zeta_n) \mid n \in \indexes{\zeta} \wedge \PHsort(\PHhitter(\zeta_n)) \neq \PHsort(P) \}$$
+%Séquences de bonds abstraites :
+%$$\BS^\wedge(P) = \{ \zeta^\wedge \mid \zeta \in \BS(P), \nexists \zeta' \in \BS(P), \zeta'^\wedge \subsetneq \zeta^\wedge \}$$
+%where:
+%$$\zeta^\wedge = \{ \PHhitter(\zeta_n) \mid n \in \indexes{\zeta} \wedge \PHsort(\PHhitter(\zeta_n)) \neq \PHsort(P) \}$$
 
@@
 $
- \cwB = \sfp{\myB}{\myB}{\aB^\w_{\ctx \Cap (\procs(\myB) \cup \pfp(\myB))}}
+ \cwB = \sfp{\myB}{\myB}{\aB^\w_{\ctx \Cap \allprocs(\myB)}}
 $,
@@
 \begin{align*}
-\myreq = &\{ (a_i,\PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid a_j \in \PHget{\ctx}{a}
-  \wedge (\exists (P,ps) \in \mysol, a_i \in ps \\
-& \qquad\qquad
-          \vee \exists n \in \indexes{\w}, \PHbounce(\w)=a_i\}
+\myreq &= \{ (a_i,\PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid
+  (a_j \in \PHget{\ctx}{a} \vee a_j \in \pfpprocs_\ctx(a)) \\
+  & \qquad \wedge (\exists (P,ps) \in \mysol, a_i \in ps \vee \exists n \in \indexes{\w}, \PHbounce(\w_n)=a_i) \}
 \\
-\mysol \subseteq & \{ (P,ps) \in \Obj \times \powerset(\PHproc) \mid
+\mysol &\subseteq \{ (P,ps) \in \Obj \times \powerset(\PHproc) \mid
         \exists (a_i,P)\in \myreq \wedge ps \in \aBS(P) \}
 \\
-\mycont = & \{ (P,\PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid 
+\mycont & = \{ (P,\PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid 
         \exists (P,ps)\in \mysol \\

### 2013-03-12 parts/def-ph.tex
ENTCS style + package

@@
 
-\begin{example*}
+\begin{example}
 The PH in \pref{fig:runningPH-2} results from the refinement of the PH in \pref{fig:runningPH-1}
@@
 highest level, and $a$ does not become inactive unless both $b$ and $c$ are inactive.
-\end{example*}
+\end{example}
 

### 2013-03-14 parts/def-ph.tex
proof

@@
-\subsection{The Process Hitting framework}
-\label{ssec:PH}
+\section{The Process Hitting framework}
 
@@
 \subsection{Definition of the Process Hitting with $k$ priorities}
+\label{ssec:PH}
 \towrite{Reformuler (actuellement trop proche de CMSB)}
@@
 
-\begin{definition}[Process Hitting $n$-reduction] \towrite{Revoir terminologie}
+\begin{definition}[Process Hitting $n$-reduction] \towrite{Revoir terminologie : “reduction” ? “restriction” ?}
   If $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$ is a Process Hitting with $k$ priorities and $n \in \segm{1}{k}$, we denote $\restriction{\PH}{n}$ \towrite{$\PH_{|n}$ $\PH'$} the $n$-reduction of $\PH$ the following Process Hitting with $n$ priorities, where:
-  $$\restriction{\PH}{n} = (\PHs; \PHl; \PHa^{\langle n \rangle})$$
+  $$\restriction{\PH}{n} = (\PHs; \PHl; \restriction{\PHa}{n})$$
   and:
-  $$\PHa^{\langle n \rangle} = (\PHa^{(1)}; \dots; \PHa^{(n)})$$
+  $$\restriction{\PHa}{n} = (\PHa^{(1)}; \dots; \PHa^{(n)})$$
+
+  Furthermore, we define: $\restriction{\PH}{0} = (\PHs; \PHl; \restriction{\PHa}{0})$, where $\restriction{\PHa}{0} = ()$ is a $0$-uplet.
 \end{definition}
@@
 
+\begin{figure}
+  \centering
+  \begin{tikzpicture}
+    \TSort{(0,0)}{a}{2}{l}
+    \TSort{(2,0)}{b}{2}{r}
+    \TSort{(4,0)}{c}{2}{r}
+
+    \THit{a_1}{prio}{b_1}{.west}{b_0}
+    \THit{b_1}{}{c_0}{.north west}{c_1}
+
+    \path[bounce, bend right]
+    \TBounce{b_1}{}{b_0}{.north west}
+    ;
+    \path[bounce, bend left]
+    \TBounce{c_0}{}{c_1}{.south west}
+    ;
+  \end{tikzpicture}
+  \label{fig:ph-conca}
+  \caption{A simple PH example depicting “backward concurrency” between two actions belonging to different classes of priorities.}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \begin{tikzpicture}
+    \TSort{(0,0)}{a}{2}{l}
+    \TSort{(2,0)}{b}{2}{r}
+    \TSort{(4,0)}{c}{3}{r}
+
+    \THit{a_1}{}{b_0}{.west}{b_1}
+    \THit{b_0}{prio}{c_1}{.south west}{c_0}
+    \THit{b_1}{prio}{c_1}{.west}{c_2}
+
+    \path[bounce, bend left]
+    \TBounce{b_0}{}{b_1}{.south west}
+    \TBounce{c_1}{}{c_2}{.south west}
+    ;
+    \path[bounce, bend right]
+    \TBounce{c_1}{}{c_0}{.north west}
+    ;
+  \end{tikzpicture}
+  \label{fig:ph-concb}
+  \caption{A simple PH example depicting “forward concurrency” between two actions belonging to different classes of priorities.}
+\end{figure}
+
 \begin{comment}
@@
 
-\subsection{Restrictions} \towrite{Reformuler}
+\subsection{Hypothesis} \towrite{Reformuler}
 
@@
 
-Let $\PH$ be a PH model on which we want to apply the static analysis. This PH has to regard the two restrictions below.
+Let $\PH$ be a PH model on which we want to apply the static analysis.
+
+We define the set of chains of actions $\PHh(b, a)$ between two sorts $b$ and $a$ as below:
+\begin{align*}
+\PHh(b, a) = \{ (h_i)_{i \in \segm{0}{s}} \in (\restriction{\PHh}{\prio(b)})^{s+1} &\mid s \in \sN, \PHsort(\PHhitter(h_0)) = b \wedge \PHsort(\PHtarget(h_n)) = a \\
+  & \wedge \forall i \in \segm{1}{s}, \PHsort(\PHtarget(h_{i-1})) = \PHsort(\PHhitter(h_{i})) \}
+\end{align*}
+
+We define the neighbor \towrite{Revoir terminologie : “neighborhood” ? “vicinity” ?} sorts of any sort $a$ as :
+$$
+\Vs(a) = \{ b \in \PHs \mid \PHh(b, a) \neq \emptyset \}
+$$
+
+We define the neighbor actions of any sort $a$ as :
+$$
+\Vh(a) = \{ h \in \restriction{\PHh}{\prio(a)} \mid \PHsort(\PHhitter(h)) \in \Vs(a) \wedge \PHsort(\PHtarget(h)) \in \Vs(a) \cup \{ a \} \}
+$$
+
+This PH has to regard the two following restrictions.
 
@@
 \towrite{Ou : $\nexists h \Rightarrow \prio(a) = 0$}
+
+These restrictions bring new interesting properties to the PH models regarding them.
+
+\pref{th:vplay} tells that for any action $h = \PHhit{a_i}{b_j}{b_k}$, if no action can be played in the neighborhood of $a$ in a given state, then $h$ can be played after a series of hits that do not prevent it to be fired.
+Furthermore, if the requisites of \pref{th:vplay} are true, then no action of this series of hits belongs to $V(a)$, as stated in \pref{co:vplay}.
+\begin{theorem}
+\label{th:vplay}
+  $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, (\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j \wedge $\\
+  $\forall h' \in \Vh(a), \PHsort(\PHtarget(h')) \neq a \Rightarrow \text{$h'$ cannot be played in $s$}) \Rightarrow$\\
+  $(\exists \delta \in \Sce, \text{$h$ can be played in $s \PHplay \delta$})$
+\end{theorem}
+
+\begin{proof}
+  Because of the cycle-freeness of $\restriction{\PH}{k-1}$, $\restriction{\PH}{\prio(a)}$ is also cycle-free and there is a $\delta \in \Sce$ so that $\forall h' \in \PHh$, $h'$ cannot be played in $s \PHplay \delta$.
+Furthermore, $\forall h' \in \delta, \PHsort(\PHtarget(h')) \neq a$ by construction of $\Vs(a)$.
+\end{proof}
+
+\begin{corollary}
+  \label{co:vplay}
+  $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, (\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j \wedge $\\
+  $(\forall h' \in \Vh(a), \PHsort(\PHtarget(h')) \neq a \Rightarrow \text{$h'$ cannot be played in $s$}) \Rightarrow$\\
+  $\exists \delta \in \Sce, (\forall n \in \indexes{\delta}, \forall h' \in \delta_n, \PHsort(\PHtarget(h')) \notin \Vh(a)) \wedge (\text{$h$ can be played in $s \PHplay \delta$})$
+\end{corollary}
+
+\pref{th:totalss} states that from any state, a steady state is eventually reached. A local variant of this theorem, given in \pref{co:totalss}, can be derived,
+where, for all $\Omega \subset \PHs$, $$\restriction{\PHl}{\Omega} = \underset{a \in \Omega}{\times} \PHl_a$$ and
+for all $H \subset \PHh$, $$\restriction{\Sce}{H} = \{ \delta \in \Sce \mid \forall n \in \indexes{\delta}, \delta_n \in H \} \enspace .$$
+\begin{theorem}
+\label{th:totalss}
+  $\forall s \in \PHl, \exists \delta \in \Sce$, no action can be played in $s \PHplay \delta$.
+\end{theorem}
+
+\begin{corollary}
+\label{co:totalss}
+  $\forall a \in \PHs, \forall s \in \restriction{\PHl}{V(a)}, \exists \delta \in \restriction{\Sce}{V(a)}$, no action can be played in $s \PHplay \delta$.
+\end{corollary}
+
+\pref{th:autohits} states that any sequence $\zeta$ of self-actions can be played eventually.
+\begin{theorem}
+\label{th:autohits}
+  Let $a \in \PHs$, $s \in \PHl$ and $\zeta \in \BS(a)$, with $n = |\indexes{\zeta}|$ so that $\forall i \in \segm{1}{n}, \PHsort(\PHhitter(\zeta_i)) = a$.
+  %If no action can be played in $V(a)$ in state $s$, then
+  $\exists (\delta_i)_{i \in \segm{1}{n}} \in \Sce$ so that $\forall i \in \segm{1}{n}$, $\zeta_i$ can be played in $s \PHplay \delta_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_i$. 
+\end{theorem}
+
+\begin{proof}
+  With \pref{co:vplay} applied iteratively.
+\end{proof}
+
+\towrite{Théorème nécessaire pour la suite: une séquence d'actions dans $\BS(a)$ peut être jouée si précédée ou entrelacée par des $\zeta$ (?)}

### 2013-03-14 parts/sa.tex
remove procs
proof

--- 2013-03-05 parts/sa.tex
@@
 
-\newcommand{\abstr}[1]{#1^\wedge}%\text{\textasciicircum}}
-\def\BS{\mathbf{BS}}
-\def\prio{\mathbf{prio}}
+Approximation : pour qu'une séquence de bonds soit jouable, il faut pouvoir atteindre tous les processus nécessaires depuis tous les points fixes possibles locaux, uniquement à l'aide d'actions de priorité maximale pour la sorte considérée.
 
+%%% N'est plus utile (?)
+%Plus haute priorité :
+%$$\forall a \in \PHs, \priomax(a) = \max_{h \in \PHh, \PHtarget(h) = a}(\prio(h))$$
+
+%%% N'est plus utile (?)
+%Processus possibles :
+%\begin{align*}
+%\procs((\cwSol,\cwReq,\cwCont)) = \{ p \in \PHproc &\mid \exists (P,ps) \in \cwSol, p \in ps
+%\\ & \vee p = \PHtarget(P)
+%\\ & \vee (P \neq \omega \Rightarrow p = \PHbounce(P)) \}
+%%\\ & \vee \exists h \in \BS(P), (p = \PHhitter(h) \vee p = \PHbounce(h)) \}
+%\end{align*}
+
+Processus rencontrés :
+\begin{align*}
+\allprocs((\cwSol,\cwReq,\cwCont,\cwSat)) = \{ p \in \PHproc &\mid \exists (P,ps) \in \cwSol, p \in ps
+\\ & \vee p = \PHtarget(P)
+%\\ & \vee (P \neq \omega \Rightarrow p = \PHbounce(P)) \}
+\\ & \vee \exists h \in \BS(P), (p = \PHhitter(h) \vee p = \PHbounce(h)) \}
+\end{align*}
+
+\subsection{Local fixed points}
+
+%%% Pas utile
+%Points fixes possibles : pour toute sorte $a$ et tout contexte partiel $\ctx$ sur $V^n(a)$:
+%\begin{align*}
+%  \pfp_\ctx: \PHs &\rightarrow \wp(\PHproc) \\
+%  a &\mapsto \{ s \in \underset{b \in V^n(a)}{\times} \PHl_b \mid \text{$s$ est accessible depuis $\ctx$ et aucune action n'y est jouable} \}
+%\end{align*}
+
+\towrite{Formaliser}
+
+Points fixes possibles : pour toute sorte $a$ et tout contexte $\ctx$:
+\begin{align*}
+  \pfp_\ctx: \PHs &\rightarrow \wp(\PHproc) \\
+  a &\mapsto \{ s \in \restriction{\PHl}{\Vs(a)} \mid \text{$s$ est (localement) accessible dans $\restriction{\PH}{\prio(a)}$ depuis $\ctx$}\\
+  &\qquad\qquad\qquad\qquad \text{et aucune action n'y est jouable} \}
+\end{align*}
+
+Processus rencontrés comme résultats d'un point fixe :
+\begin{align*}
+\pfpprocs_\ctx(a) = \{ \PHget{s}{a} \mid s \in \pfp_\ctx(a) \}
+\end{align*}
+
+%%% N'est plus adapté
+%Points fixes possibles sur un ensemble de sortes :
+%\begin{align*}
+%  \pfp: \mathbb{A} &\rightarrow \wp(\PHproc) \\
+%  \myB &\mapsto \bigcup_{a \in A} \pfp_{\allprocs(\myB)}(a)
+%\end{align*}
+
+\begin{comment}
 Séquences de bonds abstraites :
@@
 \end{itemize}
+\end{comment}
 
+\subsection{Abstract structure}
+%Séquences de bonds abstraites :
+%$$\BS^\wedge(P) = \{ \zeta^\wedge \mid \zeta \in \BS(P), \nexists \zeta' \in \BS(P), \zeta'^\wedge \subsetneq \zeta^\wedge \}$$
+%where:
+%$$\zeta^\wedge = \{ \PHhitter(\zeta_n) \mid n \in \indexes{\zeta} \wedge \PHsort(\PHhitter(\zeta_n)) \neq \PHsort(P) \}$$
+
+\begin{definition}[$\gCont_\ctx : \Sigma \times \Obj \mapsto \powerset(\Proc)$]
+  \label{def:maxCont}
+  \begin{align*}
+    \gCont_\ctx(a,P) = 
+    \{ p \in \PHproc &\mid \exists ps \in \aBS(P), \exists b_i \in ps, b = a \wedge p = b_i \\
+      & \vee b \neq a \wedge p \in \gCont_\ctx(a, \PHobj{b_j}{b_i}) \wedge b_j \in \PHget{\ctx}{b} \}
+    \enspace.
+  \end{align*}
+\end{definition}
+
+\begin{definition}
+  \label{def:aS}
+  The abstract structure $\cwB=(\Breq,\Bsol,\Bcont,\Bsat)$ is defined as
+  $
+  \cwB = \sfp{\myB}{\myB}{\aB^\w_{\ctx \Cap \allprocs(\myB)}}
+  $,
+  with $\myB=(\myreq,\mysol,\mycont,\mysat)$:
+  \begin{align*}
+    \myreq &= \{ (a_i,\PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid
+      a_j \in \PHget{\ctx}{a} \\ % \vee a_j \in \pfpprocs_\ctx(a) \\
+      & \qquad \wedge (\exists (P,ps) \in \mysol, a_i \in ps \vee \exists n \in \indexes{\w}, \PHbounce(\w_n)=a_i) \}
+    \\
+    \mysol &\subseteq \{ (P,ps) \in \Obj \times \powerset(\PHproc) \mid
+            \exists (a_i, P) \in \myreq \wedge ps \in \aBS(P) \\
+      & \qquad\qquad \exists (Q, P) \in \myreq \cup \mysat \wedge ps \in \aBS(P) \}
+    \\
+    \mycont & = \{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid
+      \exists (P, ps) \in \mysol \\
+      & \qquad\qquad \wedge q \in \gCont_\ctx(\PHsort(P),P) \}
+    \\
+    \mysat & = \{ (\PHobjp{a}{j}{i}, \PHobjp{a}{k}{i}) \in \Obj \times \Obj \mid
+      \exists (a_i, \PHobjp{a}{j}{i}) \in \myreq, \\
+      & \qquad\qquad a_j \neq a_k \wedge a_j \in \pfpprocs_\ctx(a) \\
+      & \qquad\qquad \wedge (\exists (P, ps) \in \mysol, a_j \in ps \wedge \prio(\PHsort(P)) > \prio(a) \\
+      & \qquad\qquad\qquad \vee \exists (\PHobjp{a}{j}{i}, ps) \in \mysol, \exists p \in ps, \exists (p, P) \in \myreq,\\
+      & \qquad\qquad\qquad \text{$P$ is not trivial} \wedge \prio(\PHsort(P)) > \prio(a) \}
+  \end{align*}
+\end{definition}
+
+\def\muconcr{\ell}
+\def\uconcr{\muconcr_\ctx}
+
+\begin{theorem}[Approximation inf.]\label{th:approxinf}
+If the graph $\cwB$ contains no cycle and all objectives have at least one solution, then $\uconcr(\w) \neq \emptyset$.
+\end{theorem}
+
+\begin{proof}
+We note $max\ctx = \ctx \Cap \allprocs(\cwB)$ the context supported by $\cwB$.
+As there is no cycle in $\cwB$, we show by induction that $\forall s\in L, s\subseteq max\ctx$, 
+for all objective $P$ in $\cwB$ so that $\PHtarget(P) \in s$ and
+$\exists \delta \in \muconcr_s(P)$.% and $\ceil(\delta) \subseteq max\ctx$.
+
+\begin{itemize}
+  \item If $(P, \emptyset) \in \Bsol$, either $\PHtarget(P) = \PHbounce(P)$ and $\delta = \emptyseq$,
+    or $\forall \zeta \in \BS(P), \zeta \in \Sce \wedge \PHsort(\zeta) = \{ \PHsort(P) \}$ and $\delta$ is given by \pref{th:autohits}.
+
+  \item Suppose all children objectives of $P$ are concretizable.
+  \begin{itemize}
+    \item If $\exists Q \in \Bcont$, then by hypothesis,
+      $\muconcr_{s}(\obj{\PHtarget(P)}{\PHtarget(Q)} \concat Q) \neq \emptyset$, thus
+      $\muconcr_{s}(P) \neq \emptyset$.
+    \item Else, by \pref{def:maxCont}, the concretizations of the children of $P$ require no process of sort $\PHsort(P)$.
+      Furthermore, there exists $\zeta \in \BS(P)$ so that $(P, \aZ) \in \Bsol$.
+      We build recursively a scenario $\delta$. Let $m = |\indexes{\zeta}|$.
+      \begin{itemize}
+%        \item[*] Let $\zeta_1 = \PHhit{b_i}{a_j}{a_k}$. By hypothesis, $\exists \delta_1 \in \muconcr_s(\PHobj{\any}{b_i}), \PHget{s \PHplay \delta_1}{a} \in \pfp_s(a)$.
+%          If $\PHget{s \PHplay \delta_1}{a} \neq a_j$, then by construction of $\cwB$, $(\PHobj{a_j}{a_k}, \PHobj{\PHget{s \PHplay \delta_1}{a}}{a_k}) \in \Bsat$.
+%          By hypothesis, $\muconcr_s(\PHobj{\any}{a_k}) \neq \emptyset$.
+%          If $\PHget{s \PHplay \delta_1}{a} = a_j$, then from \pref{th:vplay}, $\exists \delta'_1 \in \Sce$, $\zeta_1$ can be played in $s \PHplay \delta_1 \PHplay \delta'_1$.
+        \item[*] For $n \in \indexes{\zeta}$, let $s_n = s \PHplay \delta_1 \PHplay \delta'_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_{n-1} \PHplay \delta'_{n-1} \PHplay \zeta_{n-1}$ (or $s_1 = s$),
+          and $\zeta_n = \PHhit{b_i}{a_j}{a_k}$. By hypothesis, $\exists \delta_n \in \muconcr_{s_n}(\PHobj{\any}{b_i})$, and we have: $\PHget{s_n \PHplay \delta_n}{a} \in \pfp_{s_n}(a)$.
+          If $\PHget{s_n \PHplay \delta_n}{a} \neq a_j$, then by construction of $\cwB$, $(\PHobj{a_j}{a_k}, \PHobj{\PHget{s_n \PHplay \delta_n}{a}}{a_k}) \in \Bsat$.
+          By hypothesis, $\muconcr_{s_n \PHplay \delta_n}(\PHobj{\any}{a_k}) \neq \emptyset$.
+          If $\PHget{s_n \PHplay \delta_n}{a} = a_j$, then from \pref{th:vplay}, $\exists \delta'_n \in \Sce$, $\zeta_n$ can be played in $s \PHplay \delta_n \PHplay \delta'_n$
+          \todo{Il reste à montrer que $\delta'_n$ ne perturbe pas $b$. Ça se montre par contradiction grâce à l'hyopthèse de cycle-freeness.}
+          .
+%        \item[*] For $n \in \segm{1}{m-1}$, $m = |\indexes{\zeta}|$, let $s_n = s \PHplay \delta_1 \PHplay \delta'_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_n \PHplay \delta'_n \PHplay \zeta_n$ and $\zeta_{n+1} = \PHhit{c_i}{a_j}{a_k}$.
+%          By hypothesis, $\exists \delta_1 \in \muconcr_{s_n}(\PHobj{\any}{c_i}), \PHget{s_n \PHplay \delta_{n+1}}{a} \in \pfp_s(a)$.
+      \end{itemize}
+      Thus, $\delta = \delta_m \in \muconcr_s(P)$. % and $\ceil(\delta) \subseteq max\ctx$.
+  \end{itemize}
+\end{itemize}
+
+Finally, as $\muconcr_{max\ctx}(\w) \neq \emptyset$, $\uconcr(\w) \neq \emptyset$ (property \towrite{xxx}).
+\end{proof}
+
+\begin{comment}
 Voisinage :
@@
 \end{equation*}
+\end{comment}
+
+\begin{figure}
+  \centering
+  \begin{tikzpicture}[aS,node distance=1.5cm]
+    \node[Aproc] (c1) {$c_1$};
+    \node[Aobj,right of=c1] (c01) {$\PHobj{c_0}{c_1}$};
+    \node[Asol,right of=c01] (c01s) {};
+    \node[Aproc,right of=c01s] (b1) {$b_1$};
+    \node[Aobj,right of=b1] (b11) {$\PHobj{b_1}{b_1}$};
+    \node[Asol,right of=b11] (b11s) {};
+    \node[Aobj,below right of=b1] (b01) {$\PHobj{b_0}{b_1}$};
+    \node[Anos,right of=b01] (b01nos) {$\bottom$};
+
+    \path
+    (c1) edge (c01)
+    (c01) edge (c01s)
+    (c01s) edge (b1)
+    (b1) edge (b11) edge (b01)
+    (b11) edge (b11s)
+    ;
+  \end{tikzpicture}
+  \label{fig:sa-conca}
+  \caption{The local causality graph of the PH in \pref{fig:ph-conca}.}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \begin{tikzpicture}[aS,node distance=1.5cm]
+    \node[Aproc] (c2) {$c_2$};
+    \node[Aobj,right of=c2] (c12) {$\PHobj{c_1}{c_2}$};
+    \node[Asol,right of=c12] (c12s) {};
+    \node[Aproc,right of=c12s] (b1) {$b_1$};
+    \node[Aobj,right of=b1] (b01) {$\PHobj{b_0}{b_1}$};
+    \node[Asol,right of=b01] (b01s) {};
+    \node[Aproc,right of=b01s] (a1) {$a_1$};
+    \node[Aobj,right of=a1] (a11) {$\PHobj{a_1}{a_1}$};
+    \node[Asol,right of=a11] (a11s) {};
+
+    \node[Aobj,above right of=c2] (c22) {$\PHobj{c_2}{c_2}$};
+    \node[Asol,right of=c22] (c22s) {};
+    \node[Aobj,below right of=c2] (c02) {$\PHobj{c_0}{c_2}$};
+    \node[Anos,right of=c02] (c02nos) {$\bottom$};
+
+    \path
+    (c2) edge (c12) edge (c22) edge (c02)
+    (c22) edge (c22s)
+    (c12) edge (c12s)
+    (c12s) edge (b1)
+    (b1) edge (b01)
+    (b01) edge (b01s)
+    (b01s) edge (a1)
+    (a1) edge (a11)
+    (a11) edge (a11s)
+    ;
+  \end{tikzpicture}
+  \label{fig:sa-concb}
+  \caption{The local causality graph of the PH in \pref{fig:ph-concb}.}
+\end{figure}

### 2013-03-19 parts/def-ph.tex
update defs

@@
 
-We define the set of chains of actions $\PHh(b, a)$ between two sorts $b$ and $a$ as below:
+We define the set of chains of actions $\PHh^n(b, a)$ between two sorts $b$ and $a$, with $n \in \segm{1}{k}$, as below:
 \begin{align*}
-\PHh(b, a) = \{ (h_i)_{i \in \segm{0}{s}} \in (\restriction{\PHh}{\prio(b)})^{s+1} &\mid s \in \sN, \PHsort(\PHhitter(h_0)) = b \wedge \PHsort(\PHtarget(h_n)) = a \\
+\PHh^n(b, a) = \{ (h_i)_{i \in \segm{0}{s}} \in (\restriction{\PHh}{n})^{s+1} &\mid s \in \sN, \PHsort(\PHhitter(h_0)) = b \wedge \PHsort(\PHtarget(h_s)) = a \\
   & \wedge \forall i \in \segm{1}{s}, \PHsort(\PHtarget(h_{i-1})) = \PHsort(\PHhitter(h_{i})) \}
@@
 
-We define the neighbor \towrite{Revoir terminologie : “neighborhood” ? “vicinity” ?} sorts of any sort $a$ as :
+We define the neighbor \towrite{Revoir terminologie : “neighborhood” ? “vicinity” ?} sorts of any sort $a$ and $n \in \segm{1}{k}$ as :
 $$
-\Vs(a) = \{ b \in \PHs \mid \PHh(b, a) \neq \emptyset \}
+\Vs^n(a) = \{ b \in \PHs \mid \PHh^m(b, a) \neq \emptyset \wedge m = \min(n, \prio(a)) \}
+$$
+
+And, as a shortcut:
+$$
+\Vs(a) = \Vs^{\prio(a)}(a)
 $$
@@
 
-\paragraph{Cycle-freeness of $\restriction{\PH}{k-1}$}
-\towrite{Définition formelle ? + justification}
-The model $\restriction{\PH}{k-1}$ contains no cycles. Cycles are still allowed in $\PH$ however.
+%\paragraph{Cycle-freeness of $\restriction{\PH}{k-1}$}
+%\towrite{Définition formelle ? + justification}
+%The model $\restriction{\PH}{k-1}$ contains no cycles. Cycles are still allowed in $\PH$ however.
+
+\paragraph{Bounded reachability property}
+The dynamics of model $\restriction{\PH}{k-1}$ contains no cycles. Cycles are still allowed in $\PH$ however.
+Formally : $\exists N \in \sN, \forall \delta \in \restriction{\Sce}{k-1}, |\indexes{\delta}| \leq N$.
 
@@
   $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, (\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j \wedge $\\
-  $\forall h' \in \Vh(a), \PHsort(\PHtarget(h')) \neq a \Rightarrow \text{$h'$ cannot be played in $s$}) \Rightarrow$\\
-  $(\exists \delta \in \Sce, \text{$h$ can be played in $s \PHplay \delta$})$
+  $\forall h' \in \Vh(a), \text{$h'$ cannot be played in $s$}) \Rightarrow (\exists \delta \in \Sce, \text{$h$ can be played in $s \PHplay \delta$})$
 \end{theorem}
@@
   $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, (\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j \wedge $\\
-  $(\forall h' \in \Vh(a), \PHsort(\PHtarget(h')) \neq a \Rightarrow \text{$h'$ cannot be played in $s$}) \Rightarrow$\\
-  $\exists \delta \in \Sce, (\forall n \in \indexes{\delta}, \forall h' \in \delta_n, \PHsort(\PHtarget(h')) \notin \Vh(a)) \wedge (\text{$h$ can be played in $s \PHplay \delta$})$
+  $(\forall h' \in \Vh(a), \text{$h'$ cannot be played in $s$}) \Rightarrow$\\
+  $\exists \delta \in \Sce, (\forall n \in \indexes{\delta}, \delta_n \notin \Vh(a)) \wedge (\text{$h$ can be played in $s \PHplay \delta$})$
 \end{corollary}
@@
 \label{th:totalss}
-  $\forall s \in \PHl, \exists \delta \in \Sce$, no action can be played in $s \PHplay \delta$.
+  $\forall n \in \segm{1}{k-1}, \forall s \in \PHl, \exists \delta \in \restriction{\Sce}{n}$, no action of model $\restriction{\PH}{n}$ can be played in $s \PHplay \delta$.
 \end{theorem}
@@
 \label{co:totalss}
-  $\forall a \in \PHs, \forall s \in \restriction{\PHl}{V(a)}, \exists \delta \in \restriction{\Sce}{V(a)}$, no action can be played in $s \PHplay \delta$.
+  $\forall a \in \PHs, \forall s \in \restriction{\PHl}{\Vs(a)}, \exists \delta \in \restriction{\Sce}{\Vh(a)}$, no action of $\Vh(a)$ can be played in $s \PHplay \delta$.
 \end{corollary}

### 2013-03-19 parts/sa.tex
update defs

@@
 \towrite{Idée : prise en compte des actions perturbatrices, ou des réactions en chaîne pouvant rendre de telles actions jouables}
-
-Approximation : pour qu'une séquence de bonds soit jouable, il faut pouvoir atteindre tous les processus nécessaires depuis tous les points fixes possibles locaux, uniquement à l'aide d'actions de priorité maximale pour la sorte considérée.
 
@@
       \exists (a_i, \PHobjp{a}{j}{i}) \in \myreq, \\
-      & \qquad\qquad a_j \neq a_k \wedge a_j \in \pfpprocs_\ctx(a) \\
+      & \qquad\qquad a_j \neq a_k \wedge a_k \in \pfpprocs_\ctx(a) \\
       & \qquad\qquad \wedge (\exists (P, ps) \in \mysol, a_j \in ps \wedge \prio(\PHsort(P)) > \prio(a) \\

### 2013-03-19 parts/sa.tex
change abstract structure - remove [Sat]

@@
 \begin{align*}
-\allprocs((\cwSol,\cwReq,\cwCont,\cwSat)) = \{ p \in \PHproc &\mid \exists (P,ps) \in \cwSol, p \in ps
+\allprocs((\cwSol,\cwReq,\cwCont)) = \{ p \in \PHproc &\mid \exists (P,ps) \in \cwSol, p \in ps
 \\ & \vee p = \PHtarget(P)
@@
   \pfp_\ctx: \PHs &\rightarrow \wp(\PHproc) \\
-  a &\mapsto \{ s \in \restriction{\PHl}{\Vs(a)} \mid \text{$s$ est (localement) accessible dans $\restriction{\PH}{\prio(a)}$ depuis $\ctx$}\\
-  &\qquad\qquad\qquad\qquad \text{et aucune action n'y est jouable} \}
+  a &\mapsto \{ s \PHplay \delta \in \restriction{\PHl}{\Vs(a)} \mid s \in \restriction{\ctx}{\Vs(a)} \wedge \delta \in \restriction{\Sce}{\Vs(a)} \\
+  &\qquad\qquad\qquad\qquad \wedge \forall h \in \Vh(a), \text{$h$ n'est pas jouable dans $s \PHplay \delta$} \}
 \end{align*}
@@
 \pfpprocs_\ctx(a) = \{ \PHget{s}{a} \mid s \in \pfp_\ctx(a) \}
+\end{align*}
+
+Le nouvel ensemble de processus à prendre en compte à chaque itération du point fixe :
+\begin{align*}
+\newprocs_\ctx(\myB) = %\allprocs(\myB) \cup \bigcup_{a \in \PHs} \pfpprocs_{\allprocs(\myB)}(a)
+  \{ a_k \in \PHproc &\mid a_k \in \allprocs(\myB) \vee \\
+  & (a_i, \PHobjp{a}{j}{i}) \in \cwReq \wedge a_k \in \pfpprocs_{\allprocs(\myB)}(a) \wedge \\
+  & \quad (\exists (P, ps) \in \cwSol, a_i \in ps \wedge \prio(\PHsort(P)) > \prio(a) \\
+  & \quad \vee \exists (\PHobjp{a}{j}{i}, ps) \in \cwSol, \exists p \in ps, \exists (p, P) \in \cwReq,\\
+  & \qquad \text{$P$ is not trivial} \wedge \prio(\PHsort(P)) > \prio(a) \}
 \end{align*}
@@
   \label{def:aS}
-  The abstract structure $\cwB=(\Breq,\Bsol,\Bcont,\Bsat)$ is defined as
+  The abstract structure $\cwB=(\Breq,\Bsol,\Bcont)$ is defined as
   $
-  \cwB = \sfp{\myB}{\myB}{\aB^\w_{\ctx \Cap \allprocs(\myB)}}
+  \cwB = \sfp{\myB}{\myB}{\aB^\w_{\ctx \Cap \newprocs_\ctx(\myB)}}
   $,
-  with $\myB=(\myreq,\mysol,\mycont,\mysat)$:
+  with $\myB=(\myreq,\mysol,\mycont)$:
   \begin{align*}
@@
             \exists (a_i, P) \in \myreq \wedge ps \in \aBS(P) \\
-      & \qquad\qquad \exists (Q, P) \in \myreq \cup \mysat \wedge ps \in \aBS(P) \}
+      & \qquad\qquad \vee \exists (Q, P) \in \mycont \wedge ps \in \aBS(P) \}
     \\
@@
       & \qquad\qquad \wedge q \in \gCont_\ctx(\PHsort(P),P) \}
-    \\
-    \mysat & = \{ (\PHobjp{a}{j}{i}, \PHobjp{a}{k}{i}) \in \Obj \times \Obj \mid
-      \exists (a_i, \PHobjp{a}{j}{i}) \in \myreq, \\
-      & \qquad\qquad a_j \neq a_k \wedge a_k \in \pfpprocs_\ctx(a) \\
-      & \qquad\qquad \wedge (\exists (P, ps) \in \mysol, a_j \in ps \wedge \prio(\PHsort(P)) > \prio(a) \\
-      & \qquad\qquad\qquad \vee \exists (\PHobjp{a}{j}{i}, ps) \in \mysol, \exists p \in ps, \exists (p, P) \in \myreq,\\
-      & \qquad\qquad\qquad \text{$P$ is not trivial} \wedge \prio(\PHsort(P)) > \prio(a) \}
   \end{align*}
@@
   \item Suppose all children objectives of $P$ are concretizable.
+\todo{Problème : ce n'est plus suffisant avec cette saturation (il faut que les frères de $P$ obtenus par saturation soient concrétisables aussi).}
   \begin{itemize}
@@
       We build recursively a scenario $\delta$. Let $m = |\indexes{\zeta}|$.
+      \todo{Idée avec les nouvelles defs : au rang 0, on se replace sur un processus de $\pfp$. Au rang n, il existe par saturation un objectif adéquat qui “reprend” la progression.}
       \begin{itemize}

### 2013-03-22 parts/def-ph.tex
fix neighborhood
new restriction: boolean networks

@@
 
-While the construction of cooperation in PH allows to encode any boolean functions
-between cooperating processes \cite{PMR10-TCSB}, it is worth noticing they introduce a temporal
-shift in their application. \towrite{Adapter avec priorités}
-This allows the existence of interleaving of actions leading to a cooperative sort representing a
-past sub-state of the presence of the cooperative processes.
-The resulting behavior is then an over-approximation
-of the realization of an instantaneous cooperation.
+The construction of cooperation in PH allows to encode any boolean functions between cooperating processes \cite{PMR10-TCSB}.
+Due to the presence of priorities, it is possible to build cooperations with no temporal shift by defining the actions on the cooperative sorts with the highest class of priority.
+This allows to gain the same expressivity in PH than in boolean networks.
+\towrite{Traduction BN depuis thèse.}
 
@@
 
-In this section, we describe several restrictions.
-Although the definition of a Process Hitting with $k$ priorities allows a wide range of models, the method given in the next section only applies to Process Hitting models that regard these restrictions.
+%In this section, we describe several restrictions.
+%Although the definition of a Process Hitting with $k$ priorities allows a wide range of models, the method given in the next section only applies to Process Hitting models that regard these restrictions.
 
-Let $\PH$ be a PH model on which we want to apply the static analysis.
-
+\begin{comment}
 We define the set of chains of actions $\PHh^n(b, a)$ between two sorts $b$ and $a$, with $n \in \segm{1}{k}$, as below:
@@
 $$
-\Vs^n(a) = \{ b \in \PHs \mid \PHh^m(b, a) \neq \emptyset \wedge m = \min(n, \prio(a)) \}
+\Vs^n(a) = \{ b \in \PHs \mid \PHh^m(b, a) \neq \emptyset \wedge m = \min(n, \prio(a)) \} \cup \{ a \}
 $$
@@
 $$
-\Vh(a) = \{ h \in \restriction{\PHh}{\prio(a)} \mid \PHsort(\PHhitter(h)) \in \Vs(a) \wedge \PHsort(\PHtarget(h)) \in \Vs(a) \cup \{ a \} \}
+\Vh(a) = \{ h \in \restriction{\PHh}{\prio(a)} \mid \{ \PHsort(\PHhitter(h)), \PHsort(\PHtarget(h)) \} \subset \Vs(a) \wedge \prio(h) \leq \prio(a) \}
 $$
-
-This PH has to regard the two following restrictions.
+\end{comment}
 
@@
 
-\paragraph{Bounded reachability property}
+Prédécesseurs prioritaires :
+$$\Vs(a) = \{ b \in \PHs \mid \PHh^1(b, a) \neq \emptyset \}$$
+$$\Vh(a) = \{ h \in \PHh^{(1)} \mid \PHsort(\PHhitter(h)) \in \Vs(a) \wedge \PHsort(\PHtarget(h)) \in \Vs(a) \cup \{ a \} \}$$
+
+Let $\PH$ be a PH model on which we want to apply the static analysis.
+In this paper, we focus on a specific class of models that are equivalent to boolean networks.
+
+\paragraph{Components \& cooperative sorts}
+The studied PH is only composed of sorts representing regular components with priority $2$ and of cooperative sorts with priority $1$.
+
+\begin{comment}
+\paragraph{Bounded termination}
 The dynamics of model $\restriction{\PH}{k-1}$ contains no cycles. Cycles are still allowed in $\PH$ however.
@@
 
+\paragraph{Local stable states}
+\towrite{Justification}
+We define $\pfp$ as the set of possible stable states of a sort from a given state:
+\begin{align*}
+  \pfp_\ctx = \{ s \PHplay \delta \in \PHl &\mid s \in \ctx \wedge \delta \in \restriction{\Sce}{k-1} \\
+  & \qquad \wedge \forall \PHhit{b_i}{c_j}{c_k} \in \restriction{\PHh}{k-1}, \PHget{(s \PHplay \delta)}{b} \neq b_i \vee \PHget{(s \PHplay \delta)}{c} \neq c_j \}
+  %\text{$h$ n'est pas jouable dans $s \PHplay \delta$} \}
+\end{align*}
+
+All processes are a stable state of a sub-state of the predecessors:
+$\forall a_i \in \PHproc, \prio(a) < k \Rightarrow \exists s \in \restriction{\PHl}{\Vs(a)}, a_i \in \pfp_s$.
+We note: $\stable_{a_i} = \{ s \in \restriction{\PHl}{\Vs(a)} \mid a_i \in \pfp_s \}$.
+\end{comment}
+
+\begin{comment}
 These restrictions bring new interesting properties to the PH models regarding them.
@@
   $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, (\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j \wedge $\\
-  $\forall h' \in \Vh(a), \text{$h'$ cannot be played in $s$}) \Rightarrow (\exists \delta \in \Sce, \text{$h$ can be played in $s \PHplay \delta$})$
+  $\forall h' \in \Vh^{\prio(b)-1}(a), \PHhitter(h') \notin s \wedge \PHtarget(h') \notin s) \Rightarrow$\\
+  $(\exists \delta \in \Sce, \text{$h$ can be played in $s \PHplay \delta$})$
 \end{theorem}
@@
   $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, (\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j \wedge $\\
-  $(\forall h' \in \Vh(a), \text{$h'$ cannot be played in $s$}) \Rightarrow$\\
+  $\forall h' \in \Vh^{\prio(b)-1}(a), \PHhitter(h') \notin s \wedge \PHtarget(h') \notin s) \Rightarrow$\\
   $\exists \delta \in \Sce, (\forall n \in \indexes{\delta}, \delta_n \notin \Vh(a)) \wedge (\text{$h$ can be played in $s \PHplay \delta$})$
@@
 \towrite{Théorème nécessaire pour la suite: une séquence d'actions dans $\BS(a)$ peut être jouée si précédée ou entrelacée par des $\zeta$ (?)}
+\end{comment}

### 2013-03-22 parts/sa.tex
new restriction: boolean networks

--- 2013-03-19 parts/sa.tex
@@
 \begin{align*}
-\allprocs((\cwSol,\cwReq,\cwCont,\cwSat)) = \{ p \in \PHproc &\mid \exists (P,ps) \in \cwSol, p \in ps
-\\ & \vee p = \PHtarget(P)
-%\\ & \vee (P \neq \omega \Rightarrow p = \PHbounce(P)) \}
-\\ & \vee \exists h \in \BS(P), (p = \PHhitter(h) \vee p = \PHbounce(h)) \}
+&\allprocs((\cwSol,\cwReq,\cwCont,\cwSat)) = \{ p \in \PHproc \mid \exists (P,ps) \in \cwSol, p \in ps \\
+  &\qquad\qquad \vee p = \PHtarget(P) \vee \exists h \in \BS(P), (p = \PHhitter(h) \vee p = \PHbounce(h)) \\
+  &\qquad\qquad \vee \exists(Q, \PHobj{p}{\PHbounce(Q)} \in \cwPrioCont \}
 \end{align*}
 
-\subsection{Local fixed points}
+\subsection{Local fixed points / possible bounces}
 
@@
 
-\towrite{Formaliser}
-
+\begin{comment}
 Points fixes possibles : pour toute sorte $a$ et tout contexte $\ctx$:
@@
   \pfp_\ctx: \PHs &\rightarrow \wp(\PHproc) \\
-  a &\mapsto \{ s \in \restriction{\PHl}{\Vs(a)} \mid \text{$s$ est (localement) accessible dans $\restriction{\PH}{\prio(a)}$ depuis $\ctx$}\\
-  &\qquad\qquad\qquad\qquad \text{et aucune action n'y est jouable} \}
+  a &\mapsto \{ s \PHplay \delta \in \restriction{\PHl}{\Vs(a)} \mid s \in \restriction{\ctx}{\Vs(a)} \wedge \delta \in \restriction{\Sce}{\Vs(a)} \\
+  &\qquad\qquad\qquad\qquad \wedge \forall \PHhit{b_i}{c_j}{c_k} \in \Vh(a), \PHget{(s \PHplay \delta)}{b} \neq b_i \vee \PHget{(s \PHplay \delta)}{c} \neq c_j \}
+  %\text{$h$ n'est pas jouable dans $s \PHplay \delta$} \}
 \end{align*}
-
+%
 Processus rencontrés comme résultats d'un point fixe :
@@
 \pfpprocs_\ctx(a) = \{ \PHget{s}{a} \mid s \in \pfp_\ctx(a) \}
+\end{align*}
+%
+Le nouvel ensemble de processus à prendre en compte à chaque itération du pppf :
+\begin{align*}
+\newprocs_\ctx(\myB) = %\allprocs(\myB) \cup \bigcup_{a \in \PHs} \pfpprocs_{\allprocs(\myB)}(a)
+  \{ a_k \in \PHproc &\mid a_k \in \allprocs(\myB) \vee \\
+  & (a_i, \PHobjp{a}{j}{i}) \in \cwReq \wedge a_k \in \pfpprocs_{\ctx \Cap \allprocs(\myB)}(a) \wedge \\
+  & \quad (\exists (P, ps) \in \cwSol, a_i \in ps \wedge \prio(\PHsort(P)) > \prio(a) \\
+  & \quad \vee \exists (\PHobjp{a}{j}{i}, ps) \in \cwSol, \exists p \in ps, \exists (p, P) \in \cwReq,\\
+  & \qquad \text{$P$ is not trivial} \wedge \prio(\PHsort(P)) > \prio(a) \}
+\end{align*}
+\end{comment}
+
+\begin{comment}
+=================
+%
+Nouvelle version des états stables possibles: pour tout contexte $\ctx$:
+\begin{align*}
+  \pfp_\ctx = \{ s \PHplay \delta \in \PHl &\mid s \in \ctx \wedge \delta \in \restriction{\Sce}{k-1} \\
+  & \qquad \wedge \forall \PHhit{b_i}{c_j}{c_k} \in \restriction{\PHh}{k-1}, \PHget{(s \PHplay \delta)}{b} \neq b_i \vee \PHget{(s \PHplay \delta)}{c} \neq c_j \}
+  %\text{$h$ n'est pas jouable dans $s \PHplay \delta$} \}
+\end{align*}
+%
+Processus rencontrés comme résultats d'un état stable :
+\begin{align*}
+\pfpprocs_\ctx = \{ a_i \in \PHproc \mid \exists s \in \pfp_\ctx, a_i \in s \}
+\end{align*}
+%
+Nouvel ensemble $\newprocs$ :
+\begin{align*}
+\newprocs_\ctx(\myB) = \allprocs(\myB) \cup \pfpprocs_\ctx
+\end{align*}
+\end{comment}
+
+\begin{comment}
+==========================
+
+Bonds possibles :
+\begin{align*}
+\bounceprocs_\ctx = \{ a_i \in \PHproc \mid \exists s \in \ctx, \exists \delta \in \restriction{\Sce}{k-1}, a_i \in (s \PHplay \delta) \}
+\end{align*}
+\end{comment}
+
+États focaux possibles: pour tout contexte $\ctx \in \restriction{\PHl}{\Vs(a)}$:
+\begin{align*}
+  \pfp_\ctx(a) = \{ a_i \in \PHl_a &\mid \exists s \in \ctx, \exists \delta \in \restriction{\Sce}{1}, \PHget{(\ctx \PHplay \delta)}{a} = a_i \\
+  & \quad \wedge \forall \PHhit{b_i}{c_j}{c_k} \in \Vh(a), \PHget{(s \PHplay \delta)}{b} \neq b_i \vee \PHget{(s \PHplay \delta)}{c} \neq c_j \}
 \end{align*}
@@
   $
-  \cwB = \sfp{\myB}{\myB}{\aB^\w_{\ctx \Cap \allprocs(\myB)}}
+  \cwB = \sfp{\myB}{\myB}{\aB^\w_{\ctx \Cap \allprocs_\ctx(\myB)}}
   $,
@@
     \mysat & = \{ (\PHobjp{a}{j}{i}, \PHobjp{a}{k}{i}) \in \Obj \times \Obj \mid
-      \exists (a_i, \PHobjp{a}{j}{i}) \in \myreq, \\
-      & \qquad\qquad a_j \neq a_k \wedge a_k \in \pfpprocs_\ctx(a) \\
-      & \qquad\qquad \wedge (\exists (P, ps) \in \mysol, a_j \in ps \wedge \prio(\PHsort(P)) > \prio(a) \\
-      & \qquad\qquad\qquad \vee \exists (\PHobjp{a}{j}{i}, ps) \in \mysol, \exists p \in ps, \exists (p, P) \in \myreq,\\
-      & \qquad\qquad\qquad \text{$P$ is not trivial} \wedge \prio(\PHsort(P)) > \prio(a) \}
+      a_j \neq a_k \wedge a_k \in \pfp_\ctx(a) \}
+%%% Version états stables locaux
+%    \mysat & = \{ (\PHobjp{a}{j}{i}, \PHobjp{a}{k}{i}) \in \Obj \times \Obj \mid
+%      \exists (a_i, \PHobjp{a}{j}{i}) \in \myreq, \\
+%      & \qquad\qquad a_j \neq a_k \wedge a_k \in \pfpprocs_\ctx(a) \\
+%      & \qquad\qquad \wedge (\exists (P, ps) \in \mysol, a_i \in ps \wedge \prio(\PHsort(P)) > \prio(a) \\
+%      & \qquad\qquad\qquad \vee \exists (\PHobjp{a}{j}{i}, ps) \in \mysol, \exists p \in ps, \exists (p, P) \in \myreq,\\
+%      & \qquad\qquad\qquad \text{$P$ is not trivial} \wedge \prio(\PHsort(P)) > \prio(a) \}
   \end{align*}
@@
 \begin{proof}
+\todo{À refaire}
+
+\begin{comment}
 We note $max\ctx = \ctx \Cap \allprocs(\cwB)$ the context supported by $\cwB$.
 As there is no cycle in $\cwB$, we show by induction that $\forall s\in L, s\subseteq max\ctx$, 
-for all objective $P$ in $\cwB$ so that $\PHtarget(P) \in s$ and
+for all objective $P$ in $\cwB$ so that $\PHtarget(P) \in s$,
 $\exists \delta \in \muconcr_s(P)$.% and $\ceil(\delta) \subseteq max\ctx$.
@@
       We build recursively a scenario $\delta$. Let $m = |\indexes{\zeta}|$.
+%      \todo{Idée avec les nouvelles defs : au rang 0, on se replace sur un processus de $\pfp$. Au rang n, il existe par saturation un objectif adéquat qui “reprend” la progression.}
       \begin{itemize}
@@
         \item[*] For $n \in \indexes{\zeta}$, let $s_n = s \PHplay \delta_1 \PHplay \delta'_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_{n-1} \PHplay \delta'_{n-1} \PHplay \zeta_{n-1}$ (or $s_1 = s$),
-          and $\zeta_n = \PHhit{b_i}{a_j}{a_k}$. By hypothesis, $\exists \delta_n \in \muconcr_{s_n}(\PHobj{\any}{b_i})$, and we have: $\PHget{s_n \PHplay \delta_n}{a} \in \pfp_{s_n}(a)$.
+          and $\zeta_n = \PHhit{b_i}{a_j}{a_k}$.
+By hypothesis, $\exists \delta_n \in \muconcr_{s_n}(\PHobj{\any}{b_i})$, and we have: $\PHget{s_n \PHplay \delta_n}{a} \in \bounceprocs_{s_n} \subset \bounceprocs_\ctx$ \todo{À montrer}.
           If $\PHget{s_n \PHplay \delta_n}{a} \neq a_j$, then by construction of $\cwB$, $(\PHobj{a_j}{a_k}, \PHobj{\PHget{s_n \PHplay \delta_n}{a}}{a_k}) \in \Bsat$.
           By hypothesis, $\muconcr_{s_n \PHplay \delta_n}(\PHobj{\any}{a_k}) \neq \emptyset$.
-          If $\PHget{s_n \PHplay \delta_n}{a} = a_j$, then from \pref{th:vplay}, $\exists \delta'_n \in \Sce$, $\zeta_n$ can be played in $s \PHplay \delta_n \PHplay \delta'_n$
-          \todo{Il reste à montrer que $\delta'_n$ ne perturbe pas $b$. Ça se montre par contradiction grâce à l'hyopthèse de cycle-freeness.}
+          If $\PHget{s_n \PHplay \delta_n}{a} = a_j$, then from \pref{th:vplay}, $\exists \delta'_n \in \restriction{\Sce}{k-1}$, $\zeta_n$ can be played in $s \PHplay \delta_n \PHplay \delta'_n$
+          \todo{$\delta'_n$ ne perturbe pas $b$ ?}
           .
@@
 Finally, as $\muconcr_{max\ctx}(\w) \neq \emptyset$, $\uconcr(\w) \neq \emptyset$ (property \towrite{xxx}).
+\end{comment}
 \end{proof}

### 2013-03-22 parts/def-ph.tex
defs + proof

@@
 
+Sorte coopérative :
+$a$ is a well-formed cooperative sort iff:
+\begin{itemize}
+  \item $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) = 1$
+  \item $\forall s \in \underset{b \in \Vs(a)}{\times} \PHl_b, |\pfp_s(a)| = 1$
+\end{itemize}
+
+Composant :
+$a$ is a well-formed component iff:
+\begin{itemize}
+  \item $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) = 2$
+\end{itemize}
+
+We call $\components$ the set of well-formed components and $\cs$ the set of well-formed cooperative sorts.
+We note that: $\forall a \in \components, \Vs(a) = \emptyset \wedge \Vh(a) = \emptyset$
+
 Let $\PH$ be a PH model on which we want to apply the static analysis.
@@
 \paragraph{Components \& cooperative sorts}
-The studied PH is only composed of sorts representing regular components with priority $2$ and of cooperative sorts with priority $1$.
+The studied PH is a PH with 2 priorities, and it is only composed of well-formed components and cooperative sorts:
+$\components \cup \cs = \PHs \wedge \components \cap \cs = \emptyset$
+
+\paragraph{Bounded termination}
+The dynamics of model $\restriction{\PH}{1}$ contains no cycles. Cycles are still allowed in $\PH$ however.
+Formally : $\exists N \in \sN, \forall \delta \in \restriction{\Sce}{1}, |\indexes{\delta}| \leq N$.
 
@@
 \end{comment}
+
+\subsection{Consequences of the restrictions}
+\pref{th:hcompcomp} states that for a given state $s$ and for any action $h = \PHhit{a_i}{b_j}{b_k}$ between well-formed components, $h$ can be played after a series of hits that do not prevent it to be fired.
+\pref{th:hcscomp} states the same if $a$ is a well-formed cooperative sort, under the condition that $a_i$ reflects the state of the neighborhood of $a$.
+\begin{theorem}
+\label{th:hcompcomp}
+  $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, a,b \in \components,$\\
+  $(\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j) \Rightarrow (\exists \delta \in \restriction{\Sce}{1}, \text{$h$ can be played in $s \PHplay \delta$})$
+\end{theorem}
+\begin{proof}
+  There exists a scenario $\delta$ so that: $(s \PHplay \delta) = \update(s)$.
+  As $a,b \in \components$, $a_i \in s \PHplay \delta$ and $b_j \in s \PHplay \delta$.
+  Finally, by definition of $\update(s)$, no action of priority $1$ can be played in $s \PHplay \delta$, thus $h$ can be played in $s \PHplay \delta$.
+\end{proof}
+\begin{theorem}
+\label{th:hcscomp}
+  $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, a \in \cs, b \in \components$\\
+  $(\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j \wedge \pfp_s(a) = a_i) \Rightarrow (\exists \delta \in \restriction{\Sce}{1}, \text{$h$ can be played in $s \PHplay \delta$})$
+\end{theorem}
+\begin{proof}
+  There exists a scenario $\delta$ so that: $(s \PHplay \delta) = \update(s)$.
+  As $a_i \in \pfp_s(a)$, $a_i \in s \PHplay \delta$.
+  Furthermore, $b \in \components$, thus $b_j \in s \PHplay \delta$.
+  Finally, by definition of $\update(s)$, no action of priority $1$ can be played in $s \PHplay \delta$, thus $h$ can be played in $s \PHplay \delta$.
+\end{proof}
+
+\pref{th:autohits} states that any sequence $\zeta$ of self-actions on a well-formed component can be played eventually.
+\begin{theorem}
+\label{th:autohits}
+  Let $a \in \PHs$, $s \in \PHl$ and $\zeta \in \BS$ so that $\forall i \in \indexes{\zeta}, \PHsort(\PHhitter(\zeta_i)) = \PHsort(\PHtarget(\zeta_i)) = a$.
+  $\exists (\delta_i)_{i \in \indexes{\zeta}} \in \restriction{\Sce}{1}$ so that $\forall i \in \indexes{\zeta}$, $\zeta_i$ can be played in $s \PHplay \delta_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_i$.
+\end{theorem}
+\begin{proof}
+  With \pref{th:hcompcomp} applied iteratively.
+\end{proof}

### 2013-03-22 parts/sa.tex
defs + proof

@@
 
+Mise à jour de l'état initial :
+\begin{align*}
+  \update(\ctx) = \ctx \Cap \bigcup_{a \in CS} \pfp_{\restriction{\ctx}{\Vs(a) \cup \{ a \}}}(a)
+\end{align*}
+
 %%% N'est plus adapté
@@
   The abstract structure $\cwB=(\Breq,\Bsol,\Bcont,\Bsat)$ is defined as
-  $
-  \cwB = \sfp{\myB}{\myB}{\aB^\w_{\ctx \Cap \allprocs_\ctx(\myB)}}
-  $,
+  $\cwB = \sfp{\aB^\w_{\update(\ctx)}}{\myB}{\aB^\w_{\ctx \Cap \allprocs_\ctx(\myB)}}$,\\
   with $\myB=(\myreq,\mysol,\mycont,\mysat)$:
@@
 \begin{proof}
-\todo{À refaire}
-
-\begin{comment}
-We note $max\ctx = \ctx \Cap \allprocs(\cwB)$ the context supported by $\cwB$.
+We note $max\ctx = \update(\ctx) \Cap \allprocs(\cwB)$ the context supported by $\cwB$.
 As there is no cycle in $\cwB$, we show by induction that $\forall s\in L, s\subseteq max\ctx$, 
@@
           and $\zeta_n = \PHhit{b_i}{a_j}{a_k}$.
-By hypothesis, $\exists \delta_n \in \muconcr_{s_n}(\PHobj{\any}{b_i})$, and we have: $\PHget{s_n \PHplay \delta_n}{a} \in \bounceprocs_{s_n} \subset \bounceprocs_\ctx$ \todo{À montrer}.
-          If $\PHget{s_n \PHplay \delta_n}{a} \neq a_j$, then by construction of $\cwB$, $(\PHobj{a_j}{a_k}, \PHobj{\PHget{s_n \PHplay \delta_n}{a}}{a_k}) \in \Bsat$.
-          By hypothesis, $\muconcr_{s_n \PHplay \delta_n}(\PHobj{\any}{a_k}) \neq \emptyset$.
-          If $\PHget{s_n \PHplay \delta_n}{a} = a_j$, then from \pref{th:vplay}, $\exists \delta'_n \in \restriction{\Sce}{k-1}$, $\zeta_n$ can be played in $s \PHplay \delta_n \PHplay \delta'_n$
-          \todo{$\delta'_n$ ne perturbe pas $b$ ?}
-          .
-%        \item[*] For $n \in \segm{1}{m-1}$, $m = |\indexes{\zeta}|$, let $s_n = s \PHplay \delta_1 \PHplay \delta'_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_n \PHplay \delta'_n \PHplay \zeta_n$ and $\zeta_{n+1} = \PHhit{c_i}{a_j}{a_k}$.
-%          By hypothesis, $\exists \delta_1 \in \muconcr_{s_n}(\PHobj{\any}{c_i}), \PHget{s_n \PHplay \delta_{n+1}}{a} \in \pfp_s(a)$.
+          By hypothesis, $\exists \delta_n \in \muconcr_{s_n}(\PHobj{\any}{b_i})$.
+          If $a \in \cs$, then $\prio(\zeta_n) = 1$ and $\zeta_n$ can be played in $s_n \PHplay \delta_n$ (\ie $\delta'_n = \varepsilon$).
+          If $a \notin \cs$ and $b \in \cs$, then there exists a scenario $\widehat{\delta_n}$ so that $b_i \in \pfp_{s_n \PHplay \delta_n \PHplay \widehat{\delta_n}}(b)$.
+          Then, by \pref{th:hcscomp}, there is a scenario $\delta' \in \restriction{\Sce}{1}$ so that $\zeta_n$ is playable in $s_n \PHplay \delta_n \PHplay \widehat{\delta_n} \PHplay \delta'_n$.
+          Finally, if $a,b \in \components$, then by \pref{th:hcompcomp}, there is a scenario $\delta' \in \restriction{\Sce}{1}$ so that $\zeta_n$ is playable in $s_n \PHplay \delta_n \PHplay \delta'_n$.
       \end{itemize}
@@
 Finally, as $\muconcr_{max\ctx}(\w) \neq \emptyset$, $\uconcr(\w) \neq \emptyset$ (property \towrite{xxx}).
-\end{comment}
 \end{proof}

### 2013-03-22 parts/sa.tex
more defs

@@
-\towrite{Idée : prise en compte des actions perturbatrices, ou des réactions en chaîne pouvant rendre de telles actions jouables}
+\begin{definition}[Scenario ($\Sce$)]
+\label{def:scenario}
+  For a given Process Hitting model $(\PHs,\PHl,\PHh)$,
+  a \emph{scenario} $\delta$ is a sequence of actions of $\PHh$ so that for all $n \in \indexes{\delta}$,
+  $a_i = \PHhitter(\delta_n)$ (resp. $\PHtarget(\delta_n)$) $\Rightarrow \last_a(\delta_{1..n-1}) \in \{ \varnothing, a_i \}$.
+  The set of all scenarios is noted $\Sce$.
+%  $\supp(\delta)$ and $\ceil(\delta)$ renvoient respectivement aux premiers et
+%  derniers processus de chaque sorte.
+%  \begin{align}
+%  &\supp(\delta) = \{p\in\Proc\mid \sort(p)\in\sort(\delta) \wedge
+%                        p = \first_{\sort(p)}(\delta) \}\enspace,
+%  \eqlabel{support}
+%  \\
+%  &\ceil(\delta) = \{p\in\Proc\mid \sort(p)\in\sort(\delta) \wedge
+%                        p = \last_{\sort(p)}(\delta) \}\enspace.
+%  \eqlabel{ceil}
+%  \end{align}
+\end{definition}
+
+\begin{definition}[Objective ($\Obj$)]
+\label{def:obj}
+  The reachability of a process $a_j$ prof a process $a_i$ is called an \emph{objective}, noted $\PHobj{a_i}{a_j}$.
+  The set of all objectives is called $\Obj = \{ \PHobj{a_i}{a_j} \mid a \in \PHs \wedge (a_i, a_j) \in \PHl_a^2 \}$.
+  For an objective $P \in \Obj$, where $P = \PHobj{a_i}{a_j}$, $\PHsort(P) = a$, $\PHtarget(P)=a_i$, $\PHbounce(P)=a_j$.
+  An objective $P$ is \emph{trivial} is $\PHtarget(P)=\PHbounce(P)$.
+\end{definition}
+
+\begin{definition}[Context $\ctx$ ($\Ctx$)]
+\label{def:context}
+  A \emph{context} $\ctx$ associates to each sort in $\PHs$ a non-empty subset of its processes:
+  $\forall a \in \PHs, \PHget{\ctx}{a} \subseteq \PHl_a \wedge \PHget{\ctx}{a} \neq \emptyset$.
+  $\Ctx$ is the set of all contexts.
+\end{definition}
+
+For a given context $\ctx$, we note $a_i \in \ctx$ if and only if $a_i \in \PHget{\ctx}{a}$, and
+$ps \in \powerset(\Proc), ps \subseteq \ctx \Leftrightarrow \forall a_i \in ps, a_i \in \ctx$.
+%The override of a context $\ctx$ by a set of processes $ps$ is noted $\ctx \Cap ps$ (\defref{ctxcap}).
+%Par exemple, $\state{a_1,a_2,b_1,c_1}\Cap\{ a_3, b_2, b_3 \} = \state{a_3,b_2,b_3,c_1}$.
+\begin{definition}[$\Cap: \Ctx \times \powerset(\PHproc) \mapsto \Ctx$]
+\label{def:ctxcap}
+  For a given context $\ctx\in\Ctx$ and a set of processes $ps \in \powerset(\PHproc)$,
+  the override of $\ctx$ by $ps$ is noted $\ctx \Cap ps$ and is defined by
+  \[ \forall a \in \PHs, \PHget{(\ctx \Cap ps)}{a} =
+  \begin{cases}
+    \{ p \in ps \mid \PHsort(p)=a \} & \text{if } \exists p \in ps, \PHsort(p)=a,\\
+    \PHget{\ctx}{a} & \text{else.}
+  \end{cases}
+  \]
+\end{definition}
+
+A scenario $\delta \in \Sce$ is \emph{playable} in a context $\ctx$ if and only if $\supp(\delta) \subseteq \ctx$. 
+The play of $\delta$ in $\ctx$ is denoted $\ctx \PHplay \delta$ where $\ctx \PHplay \delta = \ctx \Cap \ceil(\delta)$.
+
+\begin{definition}[Objective sequence ($\OS$)]
+\label{def:OS}
+  An \emph{objective sequence} is a sequence $\w = P_1 \concat \dots \concat P_{|\w|}$,
+  where $\forall n \in \indexes{\w}, \w_n \in \Obj$ and $a_i = \PHtarget(\w_n) \Rightarrow \last_a(\w_{1..n-1}) \in \{ \varnothing, a_i \}$.
+  The set of all objective sequences is denoted by $\OS$.
+  The definitions of $\last_a$ \todo{À définir}, $\first_a$ \todo{À définir}, $\supp$ \todo{À définir} and $\ceil$ \todo{À définir}
+  are simply derived by omitting the case of hitters.
+\end{definition}
+
+\begin{definition}[Bounce sequence ($\BS$)]
+\label{def:bs}
+  A \emph{bounce sequence} $\zeta$ is a sequence of actions so that $\forall n \in \indexes{\zeta}, n < |\zeta|, \PHbounce(\zeta_{n}) = \PHtarget(\zeta_{n+1})$.
+  $\BS$ denotes the set of all bounce sequences, and
+  $\BS(P)$ denotes the set of bounce sequences \emph{solving} an objective $P$:
+  \[
+    \BS(\PHobj{a_i}{a_j}) = \{ \zeta \in \BS \mid \PHtarget(\zeta_1)= a_i \wedge \PHbounce(\zeta_{|\zeta|}) = a_j \} \enspace.
+  \]
+  Obviously, $\BS(\obj{a_i}{a_i}) = \{\emptyseq\}$; and $\BS(\obj{a_i}{a_j}) = \emptyset$ if there is no way to reach $a_j$ from $a_i$.
+\end{definition}
+
+\begin{definition}[$\aBS:\Obj \mapsto \powerset(\Proc)$]
+\label{def:aBS}
+  \[
+    \aBS(P) = \{ \abstr{\zeta} \mid \zeta \in \BS(P), \nexists \zeta' \in \BS(P), \abstr{\zeta'} \subsetneq \abstr{\zeta} \} \enspace,
+  \]
+  where $\abstr{\zeta} = \{ \PHhitter(\zeta_n) \mid  n \in \indexes{\zeta} \wedge \PHsort(\PHhitter(\zeta_n)) \neq \PHsort(P) \}$.
+\end{definition}
+
+\subsection{Under-approximation}
+
+\begin{definition}[$\concr: \OS \mapsto \powerset(\Sce)$]
+\label{def:concr}
+  For a given $\w \in \OS$, $\concr(\w)$ is the set of scenarios concretising $\w$ in the context $\ctx$:
+  \begin{align*}
+    \concr(\w) = \{ \delta \in \Sce \mid & (\w^\vartriangle = \emptyseq \wedge \delta = \emptyseq) 
+      \vee (\w^\vartriangle \neq \emptyseq \wedge \supp(\delta) \subseteq \ctx
+    \\ &
+      \wedge \exists \phi:\indexes{\w} \mapsto \indexes{\delta}, (\forall n, m \in \indexes{\w}, n < m \Leftrightarrow \phi(n) \leq \phi(m)) 
+    \\ &
+      \wedge \forall n \in \indexes{\w}, \PHbounce(\w_n) \in \ctx \PHplay \delta_{1..\phi(n)})
+    \}
+    \enspace,
+  \end{align*}
+  where $\omega^\vartriangle$ refers to the sequence of objectives $\omega$ where the trivial objectives have been removed.
+\end{definition}
+%
+\begin{definition}[$\concr: \powerset(\OS) \mapsto \powerset(\Sce)$]
+\label{def:concr-set}
+  $\concr(\W) = \{ \delta \in \concr(\w) \mid \w \in \W \} \enspace.$
+\end{definition}
+
+\begin{definition}[$\uconcr: \OS \mapsto \powerset(\Sce)$]
+\label{def:uconcr}
+  \[
+  \uconcr(\w) = 
+  \begin{cases}
+    \concr(\w) & \text{if } \forall s \in \PHl, s \subseteq \ctx, \exists \delta \in \concr(\w), \supp(\delta) \subseteq s \\
+    \emptyset & \text{else.}
+  \end{cases}
+  \]
+\end{definition}
+% 
+\begin{theorem}
+\label{th:uconcr-ctx}
+  $\ctx' \subseteq \ctx \wedge \uconcr(\w) \neq \emptyset \Longrightarrow \muconcr_{\ctx'}(\w) \neq \emptyset \enspace.$
+\end{theorem}
+% 
+\begin{definition}[$\uconcr: \powerset(\OS) \mapsto \powerset(\Sce)$]
+\label{def:uconcr-set}
+  $\uconcr(\Omega) = \{ \delta \in \uconcr(\w) \mid \w \in \Omega\}$
+\end{definition}
 
@@
 
-\def\muconcr{\ell}
-\def\uconcr{\muconcr_\ctx}
-
 \begin{theorem}[Approximation inf.]\label{th:approxinf}

### 2013-03-24 parts/sa.tex
demo

@@
 \end{align*}
+Of couse, if $a \in \components$, then $\pfp_\ctx(a) = \PHget{\ctx}{a}$.
 
@@
   \begin{itemize}
-    \item If $\exists Q \in \Bcont$, then by hypothesis,
+    \item If $\exists (P, Q) \in \Bcont$, then by hypothesis,
+      $\muconcr_{s}(\obj{\PHtarget(P)}{\PHtarget(Q)} \concat Q) \neq \emptyset$, thus
+      $\muconcr_{s}(P) \neq \emptyset$.
+    \item If $\exists (P, Q) \in \Bpriocont$, then by hypothesis,
       $\muconcr_{s}(\obj{\PHtarget(P)}{\PHtarget(Q)} \concat Q) \neq \emptyset$, thus
@@
 %          If $\PHget{s \PHplay \delta_1}{a} = a_j$, then from \pref{th:vplay}, $\exists \delta'_1 \in \Sce$, $\zeta_1$ can be played in $s \PHplay \delta_1 \PHplay \delta'_1$.
-        \item[*] For $n \in \indexes{\zeta}$, let $s_n = s \PHplay \delta_1 \PHplay \delta'_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_{n-1} \PHplay \delta'_{n-1} \PHplay \zeta_{n-1}$ (or $s_1 = s$),
+        \item[*] For $n \in \indexes{\zeta}$, let $s_n = s \PHplay \delta_1 \PHplay \delta'_1 \PHplay \delta''_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_{n-1} \PHplay \delta'_{n-1} \PHplay \delta''_{n-1} \PHplay \zeta_{n-1}$ (or $s_1 = s$),
           and $\zeta_n = \PHhit{b_i}{a_j}{a_k}$.
           By hypothesis, $\exists \delta_n \in \muconcr_{s_n}(\PHobj{\any}{b_i})$.
-          If $a \in \cs$, then $\prio(\zeta_n) = 1$ and $\zeta_n$ can be played in $s_n \PHplay \delta_n$ (\ie $\delta'_n = \varepsilon$).
-          If $a \notin \cs$ and $b \in \cs$, then there exists a scenario $\widehat{\delta_n}$ so that $b_i \in \pfp_{s_n \PHplay \delta_n \PHplay \widehat{\delta_n}}(b)$.
-          Then, by \pref{th:hcscomp}, there is a scenario $\delta' \in \restriction{\Sce}{1}$ so that $\zeta_n$ is playable in $s_n \PHplay \delta_n \PHplay \widehat{\delta_n} \PHplay \delta'_n$.
-          Finally, if $a,b \in \components$, then by \pref{th:hcompcomp}, there is a scenario $\delta' \in \restriction{\Sce}{1}$ so that $\zeta_n$ is playable in $s_n \PHplay \delta_n \PHplay \delta'_n$.
+          If $a \in \cs$, then $\prio(\zeta_n) = 1$ and $\zeta_n$ can be played in $s_n \PHplay \delta_n$ (\ie $\delta'_n = \delta''_n = \varepsilon$).
+          If $a \notin \cs$ and $b \in \cs$, then there exists a scenario $\delta'_n$ so that $b_i \in \pfp_{s_n \PHplay \delta_n \PHplay \delta'_n}(b)$ (because of the $\Bpriocont$ relation).
+          Then, by \pref{th:hcscomp}, there is a scenario $\delta'' \in \restriction{\Sce}{1}$ so that $\zeta_n$ is playable in $s_n \PHplay \delta_n \PHplay \delta'_n \PHplay \delta''_n$.
+          Finally, if $a,b \in \components$, then by \pref{th:hcompcomp}, there is a scenario $\delta'' \in \restriction{\Sce}{1}$ so that $\zeta_n$ is playable in $s_n \PHplay \delta_n \PHplay \delta''_n$ (\ie $\delta'_n = \varepsilon$).
       \end{itemize}

### 2013-03-24 parts/def-ph.tex
examples + defs

@@
 If $a_i\in \PHl_a$, we define the notation $a_i\in s \EQDEF \PHget{s}{a}=a_i$.
+We define the semantics of actions in a Process Hitting model in \pref{def:play}.
 
-An action $h = \PHhit{a_i}{b_j}{b_k} \in \PHa^{(n)}$ of priority $n$ is \emph{playable} in $s \in \PHl$ iff $\PHget{s}{a} = a_i$, $\PHget{s}{b} = b_j$ and $\forall m < n, \forall g \in \PHa^{(m)}$, $g$ is not playable in $s$.
-%Dans un tel cas, l'état résultant du jeu de l'action $h$ dans $\etat$ est dénoté $(\etat \PHjoue h)$, où $\PHget{(\etat \PHjoue h)}{b} = b_k$ et $\forall c \in \PHs, c \neq b \Rightarrow \PHget{(\etat \PHjoue h)}{c} = \PHget{\etat}{c}$.
-%
-%An action $h=\PHhit{a_i}{b_j}{b_k} \in\PHa$ is \emph{playable} in $s \in L$ if and only if $\PHget{s}{a} = a_i$ and $\PHget{s}{b} = b_j$.
-In such a case, $(s \PHplay h)$ stands for the state resulting from the play of the action $h$ in $s$, that is $\PHget{(s \PHplay h)}{b} = b_k$ and $\forall c\in\PHs, c\neq b, \PHget{(s\PHplay h)}{c} = \PHget{s}{c}$.
+\begin{definition}
+\label{def:play}
+  An action $h = \PHhit{a_i}{b_j}{b_k} \in \PHa^{(n)}$ of priority $n$ is \emph{playable} in $s \in \PHl$ iff $\PHget{s}{a} = a_i$, $\PHget{s}{b} = b_j$ and $\forall m < n, \forall g \in \PHa^{(m)}, \PHhitter(g) \notin s \vee \PHtarget(g) \notin s$.
+  In such a case, $(s \PHplay h)$ stands for the state resulting from the play of the action $h$ in $s$, defined by: $\PHget{(s \PHplay h)}{b} = b_k$ and $\forall c\in\PHs, c\neq b, \PHget{(s\PHplay h)}{c} = \PHget{s}{c}$.
   For the sake of clarity, for all $h, h'\in\PHa$, $((s\PHplay h)\PHplay h')$ is abbreviated as $(s\PHplay h\PHplay h')$.
+\end{definition}
+
+\begin{definition}[Scenario ($\Sce$)]
+\label{def:scenario}
+  For a given Process Hitting model $(\PHs,\PHl,\PHh)$,
+  a \emph{scenario} $\delta$ is a sequence of actions of $\PHh$ so that for all $n \in \indexes{\delta}$,
+  $a_i = \PHhitter(\delta_n)$ (resp. $\PHtarget(\delta_n)$) $\Rightarrow \last_a(\delta_{1..n-1}) \in \{ \varnothing, a_i \}$.
+  The set of all scenarios is noted $\Sce$.
+\end{definition}
 
 \begin{definition}[Process Hitting $n$-reduction] \towrite{Revoir terminologie : “reduction” ? “restriction” ?}
-  If $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$ is a Process Hitting with $k$ priorities and $n \in \segm{1}{k}$, we denote $\restriction{\PH}{n}$ \towrite{$\PH_{|n}$ $\PH'$} the $n$-reduction of $\PH$ the following Process Hitting with $n$ priorities, where:
-  $$\restriction{\PH}{n} = (\PHs; \PHl; \restriction{\PHa}{n})$$
-  and:
+  If $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$ is a Process Hitting with $k$ priorities and $n \in \segm{1}{k}$, we denote $\restriction{\PH}{n}$ \towrite{$\PH_{|n}$ $\PH'$} the $n$-reduction of $\PH$ the following Process Hitting with $n$ priorities:
+  $\restriction{\PH}{n} = (\PHs; \PHl; \restriction{\PHa}{n})$,
+  with:
   $$\restriction{\PHa}{n} = (\PHa^{(1)}; \dots; \PHa^{(n)})$$
-
-  Furthermore, we define: $\restriction{\PH}{0} = (\PHs; \PHl; \restriction{\PHa}{0})$, where $\restriction{\PHa}{0} = ()$ is a $0$-uplet.
+  Furthermore, we denote: $\restriction{\Sce}{n}$ the set of scenarios of actions of $\restriction{\PHa}{n}$.
+%  
+%  Furthermore, we define: $\restriction{\PH}{0} = (\PHs; \PHl; \restriction{\PHa}{0})$, where $\restriction{\PHa}{0} = ()$ is a $0$-uplet.
 \end{definition}
@@
 
-\subsection{Modeling cooperation.}
+\subsection{Modeling cooperation}
 \towrite{Sortes coopératives avec mise à jour prioritaire (pas de décalage temporel)}
@@
 
+\begin{figure}
+  \centering
+  \begin{tikzpicture}
+    \TSort{(0,0)}{a}{2}{l}
+    \TSort{(0,4)}{b}{2}{l}
+    \TSort{(6,2)}{c}{2}{r}
+
+    \TSetTick{ab}{0}{00}
+    \TSetTick{ab}{1}{01}
+    \TSetTick{ab}{2}{10}
+    \TSetTick{ab}{3}{11}
+    \TSort{(3,1)}{ab}{4}{l}
+
+    \THit{a_0}{prio}{ab_3}{.west}{ab_1}
+    \THit{a_0}{prio}{ab_2}{.west}{ab_0}
+    \THit{a_1}{prio}{ab_1}{.west}{ab_3}
+    \THit{a_1}{prio}{ab_0}{.west}{ab_2}
+
+    \THit{b_0}{prio}{ab_3}{.west}{ab_2}
+    \THit{b_0}{prio}{ab_1}{.west}{ab_0}
+    \THit{b_1}{prio}{ab_2}{.west}{ab_3}
+    \THit{b_1}{prio}{ab_0}{.west}{ab_1}
+
+    \THit{a_1}{selfhit}{a_1}{.west}{a_0}
+    \THit{b_1}{selfhit}{b_1}{.west}{b_0}
+    \THit{a_0}{bend left}{b_0}{.south west}{b_1}
+    \THit{b_0}{bend right=60}{a_0}{.west}{a_1}
+
+    \THit{ab_3}{}{c_0}{.west}{c_1}
+
+    \path[bounce, bend right]
+      \TBounce{ab_3}{}{ab_1}{.north west}
+      \TBounce{ab_2}{}{ab_0}{.north west}
+      \TBounce{ab_3}{}{ab_2}{.north west}
+      \TBounce{ab_1}{}{ab_0}{.north west}
+    ;
+    \path[bounce, bend left]
+      \TBounce{ab_1}{}{ab_3}{.south west}
+      \TBounce{ab_0}{}{ab_2}{.south west}
+      \TBounce{ab_2}{}{ab_3}{.south west}
+      \TBounce{ab_0}{}{ab_1}{.south west}
+    ;
+    \path[bounce, bend right]
+      \TBounce{a_1}{}{a_0}{.north west}
+      \TBounce{b_1}{}{b_0}{.north west}
+    ;
+    \path[bounce, bend left]
+      \TBounce{a_0}{}{a_1}{.south west}
+      \TBounce{b_0}{}{b_1}{.south west}
+    ;
+    \path[bounce, bend left]
+      \TBounce{c_0}{}{c_1}{.south west}
+    ;
+  \end{tikzpicture}
+  \label{fig:ph-livelock}
+  \caption{An example of PH model with three well-formed components ($a$, $b$ and $c$) and a well-formed cooperative sort ($ab$).}
+\end{figure}
+
+\begin{comment}
 \begin{figure}[p]
@@
 \end{figure}
+\end{comment}
 
+\begin{comment}
 \begin{figure}
@@
 \end{figure}
+\end{comment}
 
@@
 
-Prédécesseurs prioritaires :
-$$\Vs(a) = \{ b \in \PHs \mid \PHh^1(b, a) \neq \emptyset \}$$
+Let $\PH$ be a PH model on which we want to apply the static analysis.
+In this paper, we focus on a specific class of models that are equivalent to boolean networks.
+
+\paragraph{2 priorities}
+In this paper, we only consider Process Hitting models with 2 priorities.
+
+Given this first hypothesis, we define the neighbor \towrite{revoir terminologie : neighbors ? vicinity ?} sorts and actions (\pref{def:neighbors}).
+\begin{definition}
+\label{def:chainsactions}
+  We define the set of chains of actions $\PHh(b, a)$ between two sorts $b$ and $a$ as below:
+  \begin{align*}
+  \PHh(b, a) = \{ (h_i)_{i \in \segm{0}{s}} \in (\PHh^{(1)})^{s+1} &\mid s \in \sN, \PHsort(\PHhitter(h_0)) = b \wedge \PHsort(\PHtarget(h_s)) = a \\
+    & \wedge \forall i \in \segm{1}{s}, \PHsort(\PHtarget(h_{i-1})) = \PHsort(\PHhitter(h_{i})) \}
+  \end{align*}
+\end{definition}
+\begin{definition}
+\label{def:neighbors}
+  The set of neighbor sorts $\Vs(a)$ of a given sort $a$ is the set of sorts that can interact with it through actions of priority $1$.
+  The set of neighbor actions $\Vh(a)$ of $a$ is the set of actions of priority $1$ influencing $a$.
+  $$\Vs(a) = \{ b \in \PHs \mid \PHh(b, a) \neq \emptyset \}$$
   $$\Vh(a) = \{ h \in \PHh^{(1)} \mid \PHsort(\PHhitter(h)) \in \Vs(a) \wedge \PHsort(\PHtarget(h)) \in \Vs(a) \cup \{ a \} \}$$
+\end{definition}
 
-Sorte coopérative :
-$a$ is a well-formed cooperative sort iff:
-\begin{itemize}
-  \item $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) = 1$
-  \item $\forall s \in \underset{b \in \Vs(a)}{\times} \PHl_b, |\pfp_s(a)| = 1$
-\end{itemize}
-
-Composant :
-$a$ is a well-formed component iff:
+In \pref{def:cs} and \pref{def:component} we define the notion of well-formed component and cooperative sort.
+A sort $a$ is a well-formed component iff
+it is hit only by actions of priority $2$.
+A cooperative sort $a$ is well-formed iff
+it is hit only by actions of priority $1$,
+if any sub-state of its neighborhood is represented by at least one local steady state in this sort,
+and if any of its processes represents at least one sub-state of its neighborhood.
+\begin{definition}
+\label{def:component}
+  A sort $a \in \PHs$ is said to be a well-formed component iff:
   \begin{itemize}
@@
   \end{itemize}
+\end{definition}
+\begin{definition}
+  \label{def:cs}
+  A sort $a \in \PHs$ is said to be a well-formed cooperative sort iff:
+  \begin{itemize}
+    \item $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) = 1$
+    \item $\forall s \in \underset{b \in \Vs(a)}{\times} \PHl_b, \pfp_s(a) \neq \emptyset$
+    \item $\forall a_i \in \PHl_a, \exists s \in \underset{b \in \Vs(a)}{\times} \PHl_b, a_i \in \pfp_s(a)$
+  \end{itemize}
+\end{definition}
 
@@
 We note that: $\forall a \in \components, \Vs(a) = \emptyset \wedge \Vh(a) = \emptyset$
-
-Let $\PH$ be a PH model on which we want to apply the static analysis.
-In this paper, we focus on a specific class of models that are equivalent to boolean networks.
 

### 2013-03-24 parts/sa.tex
examples + defs

@@
   The set of all scenarios is noted $\Sce$.
-%  $\supp(\delta)$ and $\ceil(\delta)$ renvoient respectivement aux premiers et
-%  derniers processus de chaque sorte.
-%  \begin{align}
-%  &\supp(\delta) = \{p\in\Proc\mid \sort(p)\in\sort(\delta) \wedge
-%                        p = \first_{\sort(p)}(\delta) \}\enspace,
-%  \eqlabel{support}
-%  \\
-%  &\ceil(\delta) = \{p\in\Proc\mid \sort(p)\in\sort(\delta) \wedge
-%                        p = \last_{\sort(p)}(\delta) \}\enspace.
-%  \eqlabel{ceil}
-%  \end{align}
 \end{definition}
@@
 
-Finally, as $\muconcr_{max\ctx}(\w) \neq \emptyset$, $\uconcr(\w) \neq \emptyset$ (property \towrite{xxx}).
+Finally, as $\muconcr_{max\ctx}(\w) \neq \emptyset$, $\uconcr(\w) \neq \emptyset$ (\pref{th:uconcr-ctx}).
 \end{proof}
@@
 
+\begin{figure}
+  \centering
+  \begin{tikzpicture}[aS,node distance=1.5cm]
+    \node[Aproc] (c1) {$c_1$};
+    \node[Aobj,below of=c1] (c01) {$\PHobj{c_0}{c_1}$};
+    \node[Asol,below of=c01] (c01s) {};
+
+    \node[Aproc,below of=c01s] (ab11) {$ab_{11}$};
+    \node[Aobj,below right of=ab11] (ab0111) {$\PHobj{ab_{01}}{ab_{11}}$};
+    \node[Asol,below of=ab0111] (ab0111s) {};
+    \node[Aobj,below of=ab11,node distance=2.5cm] (ab0011) {$\PHobj{ab_{00}}{ab_{11}}$};
+    \node[Asol,below of=ab0011] (ab0011s) {};
+    \node[Aobj,below left of=ab11] (ab1011) {$\PHobj{ab_{10}}{ab_{11}}$};
+    \node[Asol,below of=ab1011] (ab1011s) {};
+
+    \node[Aproc,below of=ab0111s] (a1) {$a_1$};
+    \node[Aobj,below of=a1] (a11) {$\PHobj{a_1}{a_1}$};
+    \node[Asol,below of=a11] (a11s) {};
+    \node[Aobj,below right of=a1] (a01) {$\PHobj{a_0}{a_1}$};
+    \node[Asol,below of=a01] (a01s) {};
+    \node[Aproc,below of=a01s] (b0) {$b_0$};
+    \node[Aobj,below of=b0] (b00) {$\PHobj{b_0}{b_0}$};
+    \node[Asol,below of=b00] (b00s) {};
+    \node[Aobj,below right of=b0] (b10) {$\PHobj{b_1}{b_0}$};
+    \node[Asol,below of=b10] (b10s) {};
+
+    \node[Aproc,below of=ab1011s] (b1) {$b_1$};
+    \node[Aobj,below of=b1] (b01) {$\PHobj{b_0}{b_1}$};
+    \node[Asol,below of=b01] (b01s) {};
+    \node[Aproc,below of=b01s] (a0) {$a_0$};
+    \node[Aobj,below of=a0] (a10) {$\PHobj{a_1}{a_0}$};
+    \node[Asol,below of=a10] (a10s) {};
+
+    \path
+    (c1) edge (c01)
+    (c01) edge (c01s)
+    (c01s) edge (ab11)
+    (ab11) edge (ab0011) edge (ab0111) edge (ab1011)
+    (ab0011) edge (ab0011s)
+    (ab1011) edge (ab1011s)
+    (ab0111) edge (ab0111s)
+
+    (ab0011s) edge (a1) edge (b1)
+    (ab1011s) edge (b1)
+    (ab0111s) edge (a1)
+
+    (a1) edge (a01) edge (a11)
+    (a01) edge (a01s)
+    (a01s) edge (b0)
+    (a11) edge (a11s)
+    (a0) edge (a10)
+    (a10) edge (a10s)
+
+    (b0) edge (b10) edge (b00)
+    (b10) edge (b10s)
+    (b00) edge (b00s)
+    (b1) edge (b01)
+    (b01) edge (b01s)
+    (b01s) edge (a0)
+    ;
+    \path
+    (ab0011) edge[double] (ab0111)
+    (ab0011) edge[double,bend right=10] (ab1011)
+    (ab1011) edge[double,bend right=10] (ab0011)
+    (ab0111) edge[double,bend right=10] (ab1011)
+    (ab1011) edge[double,bend right=10] (ab0111)
+    ;
+    \end{tikzpicture}
+  \label{fig:sa-livelock}
+  \caption{The local causality graph of the PH in \pref{fig:ph-livelock}.}
+\end{figure}
+
+\begin{comment}
 \begin{figure}
@@
 \end{figure}
+\end{comment}

### 2013-03-25 parts/intro.tex
intro

\section{Introduction}
\label{sec:intro}

Discrete modeling frameworks for biological networks is an active research field where formal methods have proved that they were very powerful.
Such a work started in the seventies.
It was later enriched in many directions and widely used to elucidate many biological questions.
Among these questions, a major one is to understand precisely how biological systems evolve and behave; why and how they change their usual behaviors...
This leads to questions about the accessibility (possible or inevitable) of certain states.
The ultimate goal is to discover how it could be possible to prevent from reaching some pathological states.

Of course, such formal models on which analyses are performed are abstract representations of the actual studied systems.
They are associated with parameters that have to be synthesized so as to be as much as possible fitting with the real systems having some observed behaviors.
As a matter of fact, the abstractions we get are more or less rough or accurate.
Usual formal frameworks for such modeling activities are state-transition systems or Petri nets or process algebras.
We developed a quite similar framework named the Process Hitting \cite{PMR10-TCSB}, with the aim of avoiding to build the whole state space so as to be able to tackle very large systems (which would have led to a huge number of states, hopelessly far to big to be analyzed).

Besides, one further objective of our work is now to be more accurate in the description of the dynamics of the studied systems.
The idea for this is to introduce timing features of a system into its model.
Indeed, we are interested in taking into account some knowledge about the relative length of some phenomena as it is a way to refute some kinds of models (parameters) non convenient with the observed dynamic behaviors.
In this paper, we are introducing these timing properties through priorities.
It is based on the simple founding idea that the highest priority actions have to be processed before the other ones.

Until now, such a priority scheduling of the actions was not studied very much in the different formal modeling frameworks of systems biology.
Nevertheless, such an attempt has been carried out for Petri nets by F. Bause \cite{Bause97} and the concept of priority relations among the transitions of a network has also more recently been introduced by A. K. Wagler \textit{et al.} in \cite{waw,WaglerW12} in order to allow the modelisation of deterministic systems for biological applications.

Our paper is organized as follows.
The Process Hitting framework is defined in section 2;
we introduce static analysis of the PH in section 3;
section 4 illustrates the approach on an example
before the discussion and conclusion in section 5.

### 2013-03-25 main.tex
add defs
Plus de formalisme
ENTCS style + package
proof
update defs
authors
new restriction: boolean networks
defs + proof
more defs
intro
title, keywords & abstract

@@
-\documentclass{article}
+\documentclass{entcs}
 
-%\usepackage{hyperref}
+\usepackage{entcsmacro}
 
@@
 \usepackage{url}     % Mise en forme + liens pour URLs
+\usepackage{hyperref}
 \usepackage{array}   % Tableaux évolués
@@
 \newrefformat{fig}{Fig.~\ref{#1}}
-\newrefformat{pro}{Property~\ref{#1}}
-\newrefformat{pps}{Proposition~\ref{#1}}
+%\newrefformat{prop}{Property~\ref{#1}}
+\newrefformat{prop}{Proposition~\ref{#1}}
 \newrefformat{lem}{Lemma~\ref{#1}}
-\newrefformat{thm}{Theorem~\ref{#1}}
+\newrefformat{th}{Theorem~\ref{#1}}
+\newrefformat{co}{Corollary~\ref{#1}}
 \newrefformat{sec}{Sect.~\ref{#1}}
@@
 
-\usepackage{ntheorem}
-\theorembodyfont{\upshape}
-\newtheorem{definition}{Definition}{}{}
-\newtheorem*{example}{Example}{}{}
+%\usepackage{ntheorem}
+%\theorembodyfont{\upshape}
+%\newtheorem{definition}{Definition}{}{}
+%\newtheorem*{example}{Example}{}{}
 %\newtheorem{property}{Property}{}{}
@@
 \input{macros/macros-ph}
-%\input{macros/macros-grn}
+\input{macros/macros-abstr}
 
@@
 \def\indexes#1{\mathbb{I}^{#1}}
-\newcommand{\sfp}[3]{\mathbf{sfp}\{#1\}\left(#2\mapsto#3\right)}
+\newcommand{\sfp}[3]{\mathbf{lfp}\{#1\}\left(#2\mapsto#3\right)}
 %\def\lfp{\f{pppf}\;}
+\def\f#1{\mathsf{#1}}
+\def\prio{\mathsf{prio}}
+\newcommand{\bottom}{\perp}
+\newcommand{\Vs}{V_\PHs}
+\newcommand{\Vh}{V_\PHh}
+\newcommand{\Va}{\Vh}
+\newcommand{\stable}{\mathsf{stable}}
+\newcommand{\update}{\mathsf{update}}
+\newcommand{\components}{\Gamma}
+\newcommand{\cs}{CS}
+
+\tikzstyle{prio}=[draw,double,-stealth]
+
+\def\restriction#1#2{\mathchoice
+              {\setbox1\hbox{${\displaystyle #1}_{\scriptstyle #2}$}
+              \restrictionaux{#1}{#2}}
+              {\setbox1\hbox{${\textstyle #1}_{\scriptstyle #2}$}
+              \restrictionaux{#1}{#2}}
+              {\setbox1\hbox{${\scriptstyle #1}_{\scriptscriptstyle #2}$}
+              \restrictionaux{#1}{#2}}
+              {\setbox1\hbox{${\scriptscriptstyle #1}_{\scriptscriptstyle #2}$}
+              \restrictionaux{#1}{#2}}}
+\def\restrictionaux#1#2{{#1\,\smash{\vrule height .8\ht1 depth .85\dp1}}_{\,#2}}
 
@@
 \usepackage{color} % Couleurs du texte
-\newcommand{\towrite}[1]{\textcolor{blue}{#1}}
-\newcommand{\todo}[1]{\textcolor{red}{[#1]}}
+\definecolor{darkgreen}{rgb}{0,0.5,0}
+\newcommand{\towrite}[1]{\textcolor{darkgreen}{[#1]}}
+\newcommand{\todo}[1]{\textcolor{red}{[[#1]]}}
 
@@
 
-\title{\todo{Le titre}}
-
-\author{\todo{Les auteurs}}
+\def\lastname{Folschette \emph{et al}}
 
 \begin{document}
+\begin{frontmatter}
+\title{Under-approximation of reachability through static analysis in multivalued asynchronous networks}
 
-\maketitle
+\author{Maxime Folschette\thanksref{myemail}}
+\address{\towrite{PRES LUNAM + IRCCyN}}
+\thanks[myemail]{\url{Maxime.Folschette@irccyn.ec-nantes.fr}}
+
+\author{Loïc Paulevé}
+\address{\towrite{ETZH}}
+
+\author{Morgan Magnin\thanksref{myemail}}
+\address{\towrite{PRES LUNAM + IRCCyN}}
+
+\author{Olivier Roux\thanksref{myemail}}
+\address{\towrite{PRES LUNAM + IRCCyN}}
 
 \begin{abstract}
-\todo{L'abstract}
+
+The Process Hitting is a recent framework based on the play of concurrent actions.
+Each action can modify the state of a component, and is conditioned by the state of at most one other component.
+Its original definition does not involve priorities between actions, allowing very efficient static analysis based on local causality to compute reachability properties.
+Although a new definition of the framework has been proposed including classes of priorities for actions,
+the static analysis methods were not adapted and thus did not apply to this extension of the framework.
+
+In this paper, we focus on a restriction of the Process Hitting with priorities by considering a class of models equivalent to multivalued networks.
+Then, we develop a new refinement for the under-approximation of the static analysis to give accurate results for this set of Process Hitting models.
+
 \end{abstract}
+\begin{keyword}
+qualitative modelling,
+model abstraction,
+static analysis,
+asynchronous network
+\end{keyword}
+\end{frontmatter}
 
-\section{Introduction}\label{sec:intro}
-\towrite{Intro}
+\input{parts/intro}
 
-\section{The PH Framework}\label{sec:def-ph}
-\todo{Définir les priorités fixes}
 \input{parts/def-ph}
 
-\section{Static analysis}\label{sec:sa}
-\towrite{Reprendre définitions de l'analyse statique}
-\todo{Ajouts pour les priorités fixes}
 \input{parts/sa}
@@
 
-\bibliographystyle{plain}
+\bibliographystyle{entcs}
 \bibliography{biblio}

### 2013-03-25 parts/def-ph.tex
move some defs

@@
 \towrite{Reformuler (actuellement trop proche de CMSB)}
-A PH (\pref{def:PH}) gathers a finite number of concurrent \emph{processes} grouped into a finite set of \emph{sorts}.
+A PH (\pref{def:ph}) gathers a finite number of concurrent \emph{processes} grouped into a finite set of \emph{sorts}.
 A process belongs to a unique sort and is noted $a_i$ where $a$ is the sort and $i$ the identifier of the process within the sort $a$.
@@
 \begin{definition}[Process Hitting with $k$ priorities] \towrite{Revoir terminologie}
+\label{def:ph}
   A \emph{Process Hitting with $k$ priorities}, where $k \in \sN^*$, is a triplet $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$, with $\PHa^{\langle k \rangle} = (\PHa^{(1)}; \dots; \PHa^{(k)})$ a $k$-uplet, where:
@@
 \end{definition}
-
 We call $\components$ the set of well-formed components and $\cs$ the set of well-formed cooperative sorts.
 We note that: $\forall a \in \components, \Vs(a) = \emptyset \wedge \Vh(a) = \emptyset$
+
+Finally, we denote $\pfp_s(a)$ the set of possible local steady-states of a sort $a$ from a state $s$.
+États focaux possibles: pour tout contexte $\ctx \in \restriction{\PHl}{\Vs(a)}$:
+\begin{align*}
+  \pfp_\ctx(a) = \{ a_i \in \PHl_a &\mid \exists s \in \ctx, \exists \delta \in \restriction{\Sce}{1}, \PHget{(\ctx \PHplay \delta)}{a} = a_i \\
+  & \quad \wedge \forall \PHhit{b_i}{c_j}{c_k} \in \Vh(a), \PHget{(s \PHplay \delta)}{b} \neq b_i \vee \PHget{(s \PHplay \delta)}{c} \neq c_j \}
+\end{align*}
+Of couse, if $a \in \components$, then $\pfp_\ctx(a) = \PHget{\ctx}{a}$.
 

### 2013-03-25 parts/sa.tex
move some defs

@@
-\begin{definition}[Scenario ($\Sce$)]
-\label{def:scenario}
-  For a given Process Hitting model $(\PHs,\PHl,\PHh)$,
-  a \emph{scenario} $\delta$ is a sequence of actions of $\PHh$ so that for all $n \in \indexes{\delta}$,
-  $a_i = \PHhitter(\delta_n)$ (resp. $\PHtarget(\delta_n)$) $\Rightarrow \last_a(\delta_{1..n-1}) \in \{ \varnothing, a_i \}$.
-  The set of all scenarios is noted $\Sce$.
-\end{definition}
+\section{Static analysis}\label{sec:sa}
 
@@
 \end{comment}
-
-États focaux possibles: pour tout contexte $\ctx \in \restriction{\PHl}{\Vs(a)}$:
-\begin{align*}
-  \pfp_\ctx(a) = \{ a_i \in \PHl_a &\mid \exists s \in \ctx, \exists \delta \in \restriction{\Sce}{1}, \PHget{(\ctx \PHplay \delta)}{a} = a_i \\
-  & \quad \wedge \forall \PHhit{b_i}{c_j}{c_k} \in \Vh(a), \PHget{(s \PHplay \delta)}{b} \neq b_i \vee \PHget{(s \PHplay \delta)}{c} \neq c_j \}
-\end{align*}
-Of couse, if $a \in \components$, then $\pfp_\ctx(a) = \PHget{\ctx}{a}$.
 

### 2013-03-25 main.tex
authors typo
update abstract

@@
 
-\author{Morgan Magnin\thanksref{myemail}}
+\author{Morgan Magnin}
 \address{\towrite{PRES LUNAM + IRCCyN}}
 
-\author{Olivier Roux\thanksref{myemail}}
+\author{Olivier Roux}
 \address{\towrite{PRES LUNAM + IRCCyN}}
@@
 
-In this paper, we focus on a restriction of the Process Hitting with priorities by considering a class of models equivalent to multivalued networks.
-Then, we develop a new refinement for the under-approximation of the static analysis to give accurate results for this set of Process Hitting models.
+In this paper, we focus on a restriction of the Process Hitting with two priorities and a specific behaviour of the components.
+We show that this class of Process Hitting models allows to represent any asynchronous networks, either boolean or multivalued.
+Then we develop a new refinement for the under-approximation of the static analysis to give accurate results for this set of Process Hitting models.
+Thus, our method allows to efficiently under-approximate local reachability properties in asynchronous multivalued networks.
 

### 2013-03-25 parts/sa.tex
redaction notes

@@
 \section{Static analysis}\label{sec:sa}
+
+\towrite{Mettre de la colle}
 
@@
 \label{def:OS}
+\towrite{Simplifier / réécrire en dehors d'une def}
   An \emph{objective sequence} is a sequence $\w = P_1 \concat \dots \concat P_{|\w|}$,
@@
 \label{def:concr}
+\towrite{Simplifier ? Supprimer la def formelle ?}
   For a given $\w \in \OS$, $\concr(\w)$ is the set of scenarios concretising $\w$ in the context $\ctx$:

### 2013-03-26 main.tex
change abstract

@@
 \begin{abstract}
+The Process Hitting is a recently introduced framework designed for the modelling of concurrent systems.
+Its originality lies in a compact representation of both components of the model and its corresponding actions:
+each action can modify the status of a component, and is conditioned by the status of at most one other component.
+This allowed to define very efficient static analysis based on local causality to compute reachability properties.
+However, in the case of cooperations between components (for example, when two components are supposed to interact with a third one only when they are in a given configuration), the approach leads to an over-approximated interleaving between actions, because of the pure asynchronous semantics of the model.
 
-The Process Hitting is a recent framework based on the play of concurrent actions.
-Each action can modify the state of a component, and is conditioned by the state of at most one other component.
-Its original definition does not involve priorities between actions, allowing very efficient static analysis based on local causality to compute reachability properties.
-Although a new definition of the framework has been proposed including classes of priorities for actions,
-the static analysis methods were not adapted and thus did not apply to this extension of the framework.
-
-In this paper, we focus on a restriction of the Process Hitting with two priorities and a specific behaviour of the components.
+To address this issue, we propose an extended definition of the framework, including priority classes for actions.
+In this paper, we focus on a restriction of the Process Hitting with two priorities and a specific behaviour of the components, that is sufficient to tackle the aforementioned problem of cooperations.
 We show that this class of Process Hitting models allows to represent any asynchronous networks, either boolean or multivalued.
-Then we develop a new refinement for the under-approximation of the static analysis to give accurate results for this set of Process Hitting models.
-Thus, our method allows to efficiently under-approximate local reachability properties in asynchronous multivalued networks.
-
+Then we develop a new refinement for the under-approximation of the static analysis to give accurate results for this class of Process Hitting models.
+Our method thus allows to efficiently under-approximate local reachability properties in asynchronous multivalued networks.
 \end{abstract}

### 2013-03-27 abstract.tex
title + abstract version

--- 2013-03-26 main.tex
@@
 % Commandes À FAIRE
-\usepackage{color} % Couleurs du texte
-\definecolor{darkgreen}{rgb}{0,0.5,0}
-\newcommand{\towrite}[1]{\textcolor{darkgreen}{[#1]}}
-\newcommand{\todo}[1]{\textcolor{red}{[[#1]]}}
+%\usepackage{color} % Couleurs du texte
+%\definecolor{darkgreen}{rgb}{0,0.5,0}
+%\newcommand{\towrite}[1]{\textcolor{darkgreen}{[#1]}}
+%\newcommand{\todo}[1]{\textcolor{red}{[[#1]]}}
 
@@
 \author{Maxime Folschette\thanksref{myemail}}
-\address{\towrite{PRES LUNAM + IRCCyN}}
+\address{LUNAM Universit\'e, \'Ecole Centrale de Nantes, IRCCyN UMR CNRS 6597\\
+(Institut de Recherche en Communications et Cybern\'etique de Nantes)\\
+1 rue de la No\"e - B.P. 92101 - 44321 Nantes Cedex 3, France.}
 \thanks[myemail]{\url{Maxime.Folschette@irccyn.ec-nantes.fr}}
@@
 \author{Loïc Paulevé}
-\address{\towrite{ETZH}}
+\address{ETH Zürich, Switzerland.}
 
 \author{Morgan Magnin}
-\address{\towrite{PRES LUNAM + IRCCyN}}
+\address{LUNAM Universit\'e, \'Ecole Centrale de Nantes, IRCCyN UMR CNRS 6597\\
+(Institut de Recherche en Communications et Cybern\'etique de Nantes)\\
+1 rue de la No\"e - B.P. 92101 - 44321 Nantes Cedex 3, France.}
 
 \author{Olivier Roux}
-\address{\towrite{PRES LUNAM + IRCCyN}}
+\address{LUNAM Universit\'e, \'Ecole Centrale de Nantes, IRCCyN UMR CNRS 6597\\
+(Institut de Recherche en Communications et Cybern\'etique de Nantes)\\
+1 rue de la No\"e - B.P. 92101 - 44321 Nantes Cedex 3, France.}
 
@@
 
-\input{parts/intro}
-
-\input{parts/def-ph}
-
-\input{parts/sa}
-
-\section{Example}\label{sec:example}
-\todo{Trouver un exemple représentatif (comportement différent avec / sans priorités)}
-\towrite{Exemple}
-
-\section{Discussion \& Conclusion}\label{sec:ccl}
-\towrite{Pistes :
-\begin{itemize}
-  \item Modèles Zeno (système de précédences et prise en compte des états globaux)
-\end{itemize}
-}
-
-\bibliographystyle{entcs}
-\bibliography{biblio}
-
-%\input{parts/contributions}
-
 \end{document}

### 2013-03-28 parts/sa.tex
fix PrioCont
new formalism: simultaneously required processes

@@
 Processus rencontrés :
+\todo{Revenir à la définition simple de procs ?}
 \begin{align*}
@@
 \subsection{Abstract structure}
-%Séquences de bonds abstraites :
-%$$\BS^\wedge(P) = \{ \zeta^\wedge \mid \zeta \in \BS(P), \nexists \zeta' \in \BS(P), \zeta'^\wedge \subsetneq \zeta^\wedge \}$$
-%where:
-%$$\zeta^\wedge = \{ \PHhitter(\zeta_n) \mid n \in \indexes{\zeta} \wedge \PHsort(\PHhitter(\zeta_n)) \neq \PHsort(P) \}$$
 
@@
 
+\begin{definition}[$\csState$]
+  \label{def:csState}
+  \towrite{À reformuler}
+  $$\csState(a_i) = \{ b_j \in \PHproc \mid b \in \Vs(a) \wedge \pfp_{\csState(a_i)}(a) = a_i \}$$
+\end{definition}
+
+\begin{definition}
+  \label{def:aS}
+  The abstract structure $\cwB=(\Breq,\Bsol,\Brsp,\Bcont)$ is defined as
+  $\cwB = \sfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs_\ctx(\myB)}}$,\\
+  with $\myB=(\myreq,\mysol,\myrsp,\mycont)$:
+  \begin{align*}
+    \myreq &= \{ (a_i,\PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid
+      a \in \components \wedge a_j \in \PHget{\ctx}{a} \\ % \vee a_j \in \pfpprocs_\ctx(a) \\
+      & \qquad \wedge ((\exists (P,ps) \in \mysol \vee \exists (b_j, ps) \in \myrsp), a_i \in ps \\
+      & \qquad\qquad \vee \exists n \in \indexes{\w}, \PHbounce(\w_n)=a_i) \}
+    \\
+    \mysol &\subseteq \{ (P,ps) \in \Obj \times \powerset(\PHproc) \mid
+            \exists (a_i, P) \in \myreq \wedge ps \in \aBS(P) \\
+      & \qquad\qquad \vee \exists (Q, P) \in \mycont \wedge ps \in \aBS(P) \}
+    \\
+    \myrsp &= \{ (a_i,ps) \in \PHproc \times \powerset(\PHproc) \mid a \in \cs \\
+      & \qquad \wedge (\exists (P,ps') \in \mysol \vee \exists (b_j,ps') \in \myrsp), \\
+      & \qquad\qquad a_i \in ps' \wedge \csState(a_i) = \towrite{\in?} ps \}
+    \\
+    \mycont & = \{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid
+      \exists (P, ps) \in \mysol \\
+      & \qquad\qquad \wedge q \in \gCont_\ctx(\PHsort(P),P) \}
+  \end{align*}
+\end{definition}
+
+\begin{definition}[Coherent solution]\label{def:coherent}
+  A cooperative sort requisite $(a_i, ps)$ in $\myrsp$ is said coherent iff
+  it has no successor $(b_k,\PHobjp{b}{j}{k})$ in $\myreq$ so that there exists $b_n \in ps$, $b_k \neq b_n$.
+\end{definition}
+
+\begin{theorem}[Approximation inf.]\label{th:approxinf}
+  If the graph $\cwB$ contains no cycle,
+  all objectives have at least one solution
+  and all cooperative sort requisites are coherent,
+  then $\uconcr(\w) \neq \emptyset$.
+\end{theorem}
+
+\begin{proof}
+We note $max\ctx = \ctx \Cap \allprocs(\cwB)$ the context supported by $\cwB$.
+
+\towrite{MQ par récurrence : tous les $a_i$ requis de sortes coopératives sont concrétisables}
+
+As there is no cycle in $\cwB$, we show by induction that $\forall s\in L, s\subseteq max\ctx$, 
+for all objective $P$ in $\cwB$ so that $\PHtarget(P) \in s$,
+$\exists \delta \in \muconcr_s(P)$.% and $\ceil(\delta) \subseteq max\ctx$.
+
+\begin{itemize}
+  \item If $(P, \emptyset) \in \Bsol$, either $\PHtarget(P) = \PHbounce(P)$ and $\delta = \emptyseq$,
+    or $\forall \zeta \in \BS(P), \zeta \in \Sce \wedge \PHsort(\zeta) = \{ \PHsort(P) \}$ and $\delta$ is given by \pref{th:autohits}.
+
+  \item Suppose all children objectives of $P$ are concretizable.
+  \begin{itemize}
+    \item If $\exists (P, Q) \in \Bcont$, then by hypothesis,
+      $\muconcr_{s}(\obj{\PHtarget(P)}{\PHtarget(Q)} \concat Q) \neq \emptyset$, thus
+      $\muconcr_{s}(P) \neq \emptyset$.
+    \item Else, by \pref{def:maxCont}, the concretizations of the children of $P$ require no process of sort $\PHsort(P)$.
+      Furthermore, there exists $\zeta \in \BS(P)$ so that $(P, \aZ) \in \Bsol$.
+      We build recursively a scenario $\delta$. Let $m = |\indexes{\zeta}|$.
+      \begin{itemize}
+        \item[*] \towrite{construire récurvivement ? Distinguer les cas $b_j$ dans $\components$ ou $\cs$ (stabilité requise et obtenue)}
+        For $n \in \indexes{\zeta}$, let $s_n = s \PHplay \delta_1 \PHplay \delta'_1 \PHplay \delta''_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_{n-1} \PHplay \delta'_{n-1} \PHplay \delta''_{n-1} \PHplay \zeta_{n-1}$ (or $s_1 = s$),
+          and $\zeta_n = \PHhit{b_i}{a_j}{a_k}$.
+          By hypothesis, $\exists \delta_n \in \muconcr_{s_n}(\PHobj{\any}{b_i})$.
+          If $a \in \cs$, then $\prio(\zeta_n) = 1$ and $\zeta_n$ can be played in $s_n \PHplay \delta_n$ (\ie $\delta'_n = \delta''_n = \varepsilon$).
+          If $a \notin \cs$ and $b \in \cs$, then there exists a scenario $\delta'_n$ so that $b_i \in \pfp_{s_n \PHplay \delta_n \PHplay \delta'_n}(b)$ (because of the $\Bpriocont$ relation).
+          Then, by \pref{th:hcscomp}, there is a scenario $\delta'' \in \restriction{\Sce}{1}$ so that $\zeta_n$ is playable in $s_n \PHplay \delta_n \PHplay \delta'_n \PHplay \delta''_n$.
+          Finally, if $a,b \in \components$, then by \pref{th:hcompcomp}, there is a scenario $\delta'' \in \restriction{\Sce}{1}$ so that $\zeta_n$ is playable in $s_n \PHplay \delta_n \PHplay \delta''_n$ (\ie $\delta'_n = \varepsilon$).
+      \end{itemize}
+      Thus, $\delta = \delta_m \in \muconcr_s(P)$. % and $\ceil(\delta) \subseteq max\ctx$.
+  \end{itemize}
+\end{itemize}
+
+Finally, as $\muconcr_{max\ctx}(\w) \neq \emptyset$, $\uconcr(\w) \neq \emptyset$ (\pref{th:uconcr-ctx}).
+\end{proof}
+
+%%% Ancien graphe avec PrioCont
+\begin{comment}
 \begin{definition}
@@
     \mysat & = \{ (\PHobjp{a}{j}{i}, \PHobjp{a}{k}{i}) \in \Obj \times \Obj \mid
-      a_j \neq a_k \wedge a_k \in \pfp_\ctx(a) \}
+      \exists (a_i, \PHobj{a_j}{a_i}) \in \myreq\\
+      & \qquad\qquad \wedge a_j \neq a_k \wedge a_k \in \pfp_\ctx(a) \}
 %%% Version états stables locaux
@@
 \end{proof}
+\end{comment}
 

### 2013-03-28 parts/ccl.tex
example & conclusion parts

\section{Discussion \& Conclusion}\label{sec:ccl}
\towrite{Pistes :
\begin{itemize}
  \item Plus de classes de priorités ?
  \item Modèles Zeno (système de précédences et prise en compte des états globaux)
\end{itemize}
}

### 2013-03-28 parts/example.tex
example & conclusion parts

\section{Example}\label{sec:example}

\towrite{Exemple \texttt{livelock\_and.ph} : différent avec / sans priorités}

\todo{Trouver un grs exemple représentatif (EGFR / TCRSIG)}

### 2013-03-28 parts/def-ph.tex
demo

@@
 
+In \pref{def:cs} we define the notion of well-formed component.
+A sort $a$ is a well-formed component iff
+it is hit only by actions of priority $2$.
+\begin{definition}
+\label{def:component}
+  A sort $a \in \PHs$ is said to be a well-formed component iff:
+  \begin{itemize}
+    \item $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) = 2$
+  \end{itemize}
+\end{definition}
+We call $\components$ the set of well-formed components.
+
 Given this first hypothesis, we define the neighbor \towrite{revoir terminologie : neighbors ? vicinity ?} sorts and actions (\pref{def:neighbors}).
@@
 \label{def:neighbors}
-  The set of neighbor sorts $\Vs(a)$ of a given sort $a$ is the set of sorts that can interact with it through actions of priority $1$.
-  The set of neighbor actions $\Vh(a)$ of $a$ is the set of actions of priority $1$ influencing $a$.
-  $$\Vs(a) = \{ b \in \PHs \mid \PHh(b, a) \neq \emptyset \}$$
+  The set of neighbour sorts $\Vs(a)$ of a given sort $a$ is the set of components that can interact with it through actions of priority $1$.
+  The set of neighbour actions $\Vh(a)$ of $a$ is the set of actions of priority $1$ influencing $a$.
+  $$\Vs(a) = \{ b \in \components \mid \PHh(b, a) \neq \emptyset \}$$
   $$\Vh(a) = \{ h \in \PHh^{(1)} \mid \PHsort(\PHhitter(h)) \in \Vs(a) \wedge \PHsort(\PHtarget(h)) \in \Vs(a) \cup \{ a \} \}$$
@@
 
-In \pref{def:cs} and \pref{def:component} we define the notion of well-formed component and cooperative sort.
-A sort $a$ is a well-formed component iff
-it is hit only by actions of priority $2$.
+We denote $\pfp_s(a)$ the set of possible local steady-states of a sort $a$ from a state $s$.
+\todo{À corriger : état global ? + prendre en compte l'état de la sorte}
+\begin{align*}
+  \pfp_s(a) = \{ a_i \in \PHl_a &\mid \exists \delta \in \restriction{\Sce}{1}, \PHget{(s \PHplay \delta)}{a} = a_i \\
+  & \quad \wedge \forall \PHhit{b_i}{c_j}{c_k} \in \Vh(a), \PHget{(s \PHplay \delta)}{b} \neq b_i \vee \PHget{(s \PHplay \delta)}{c} \neq c_j \}
+\end{align*}
+Of course, if $a \in \components$, then $\pfp_s(a) = \PHget{s}{a}$.
+
+In \pref{def:component} we define the notion of well-formed cooperative sort.
 A cooperative sort $a$ is well-formed iff
 it is hit only by actions of priority $1$,
-if any sub-state of its neighborhood is represented by at least one local steady state in this sort,
-and if any of its processes represents at least one sub-state of its neighborhood.
-\begin{definition}
-\label{def:component}
-  A sort $a \in \PHs$ is said to be a well-formed component iff:
-  \begin{itemize}
-    \item $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) = 2$
-  \end{itemize}
-\end{definition}
+if any sub-state of its neighbourhood is represented by at least one local steady state in this sort,
+and if any of its processes represents at least one sub-state of its neighbourhood.
 \begin{definition}
@@
     \item $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) = 1$
-    \item $\forall s \in \underset{b \in \Vs(a)}{\times} \PHl_b, \pfp_s(a) \neq \emptyset$
+    \item $\forall s \in \underset{b \in \Vs(a)}{\times} \PHl_b, |\pfp_s(a)| = 1$
     \item $\forall a_i \in \PHl_a, \exists s \in \underset{b \in \Vs(a)}{\times} \PHl_b, a_i \in \pfp_s(a)$
@@
 \end{definition}
-We call $\components$ the set of well-formed components and $\cs$ the set of well-formed cooperative sorts.
-We note that: $\forall a \in \components, \Vs(a) = \emptyset \wedge \Vh(a) = \emptyset$
-
-Finally, we denote $\pfp_s(a)$ the set of possible local steady-states of a sort $a$ from a state $s$.
-États focaux possibles: pour tout contexte $\ctx \in \restriction{\PHl}{\Vs(a)}$:
-\begin{align*}
-  \pfp_\ctx(a) = \{ a_i \in \PHl_a &\mid \exists s \in \ctx, \exists \delta \in \restriction{\Sce}{1}, \PHget{(\ctx \PHplay \delta)}{a} = a_i \\
-  & \quad \wedge \forall \PHhit{b_i}{c_j}{c_k} \in \Vh(a), \PHget{(s \PHplay \delta)}{b} \neq b_i \vee \PHget{(s \PHplay \delta)}{c} \neq c_j \}
-\end{align*}
-Of couse, if $a \in \components$, then $\pfp_\ctx(a) = \PHget{\ctx}{a}$.
+We call $\cs$ the set of well-formed cooperative sorts.
+%We note that: $\forall a \in \components, \Vs(a) = \emptyset \wedge \Vh(a) = \emptyset$
+As any local state of neighbour sorts of a cooperative sort leads to a local steady-state, we denote $\csState(a_i)$ the set of local states represented by the process $a_i$ of the cooperative sort $a$.
+\begin{definition}[$\csState$]
+\label{def:csState}
+  \towrite{À reformuler}
+  $$\csState(a_i) = \{ s \in \underset{b \in \Vs(a)}{\times} \PHl_b \mid \pfp_{s}(a) = a_i \}$$
+\end{definition}
 

### 2013-03-28 parts/sa.tex
demo

@@
 
-\begin{definition}[$\csState$]
-  \label{def:csState}
-  \towrite{À reformuler}
-  $$\csState(a_i) = \{ b_j \in \PHproc \mid b \in \Vs(a) \wedge \pfp_{\csState(a_i)}(a) = a_i \}$$
-\end{definition}
-
 \begin{definition}
@@
       & \qquad \wedge (\exists (P,ps') \in \mysol \vee \exists (b_j,ps') \in \myrsp), \\
-      & \qquad\qquad a_i \in ps' \wedge \csState(a_i) = \towrite{\in?} ps \}
+      & \qquad\qquad a_i \in ps' \wedge \csState(a_i) \in ps \}
     \\
@@
 
-\begin{definition}[Coherent solution]\label{def:coherent}
+\begin{definition}[Coherent solution]
+\label{def:coherent}
   A cooperative sort requisite $(a_i, ps)$ in $\myrsp$ is said coherent iff
@@
 
-\begin{theorem}[Approximation inf.]\label{th:approxinf}
+\begin{theorem}[Approximation inf.]
+\label{th:approxinf}
   If the graph $\cwB$ contains no cycle,
@@
 
-\towrite{MQ par récurrence : tous les $a_i$ requis de sortes coopératives sont concrétisables}
+Let $(a_i, ps) \in \Brsp$ be a cooperative sort requirement whom all children are concretizable.
+We label all processes of $ps$ by an integer: $ps = \{ p_n \}_{n \in \indexes{ps}}$.
+Let us prove that for all $n \in \indexes{ps}$, there exists a scenario $\delta_n$ so that:
+$\forall i \in \segm{1}{n}, \PHget{(s \PHplay \delta_n)}{\PHsort(p_i)} = p_i$.
+\begin{itemize}
+  \item It is straightforward for $\delta_0 = \varepsilon$.
+  \item Let us suppose such $\delta_n$ exists. \todo{Il faut être plus précis pour prendre en compte les coopérations en cascade}
+    By hypothesis, there exists $\delta' \in \muconcr_{s \PHplay \delta_n}(\PHobj{\any}{p_n})$.
+%    so that: $\PHget{(s \PHplay \delta_n \PHplay \delta')}{\PHsort(p_{n+1})} = p_{n+1}$.
+    By hypothesis, $(a_i, ps)$ is coherent (\pref{def:coherent}), which means that solving $p_{n+1}$ does not disturb the processes of $ps$.
+    Therefore, $\forall i \in \segm{1}{n+1}$, $\PHget{(s \PHplay \delta_n \PHplay \delta')}{\PHsort(p_{i})} = p_{i}$.
+    Finally, by theorem \todo{théorème mise à jour}, there exists a scenario $\delta'' \in \restriction{\Sce}{1}$
+    that can be played in $s \PHplay \delta_n \PHplay \delta'$
+    and so that, if we denote $\delta_{n+1} = \delta_n \PHplay \delta' \PHplay \delta''$,
+    we have: $\update(s \PHplay \delta_n \PHplay \delta') = s \PHplay \delta_{n+1}$ (\todo{théorème stabilité}), and the same property about processes.
+\end{itemize}
+Therefore, $\delta = \delta_{\indexes{ps}}$ exists, and given its properties, we have: $\PHget{(s \PHplay \delta)}{a} = a_i$
+and $\update(s \PHplay \delta) = s \PHplay \delta$.
 
@@
       Furthermore, there exists $\zeta \in \BS(P)$ so that $(P, \aZ) \in \Bsol$.
-      We build recursively a scenario $\delta$. Let $m = |\indexes{\zeta}|$.
+      We show by induction that for all $n \in \indexes{\zeta}$, there is a scenario $\delta_n$ so that $\PHget{(s \PHplay \delta_n)}{\PHsort(P)} = \PHbounce(\zeta_n)$.
+%      We build recursively a scenario $\delta$. Let $m = |\indexes{\zeta}|$.
       \begin{itemize}
         \item[*] \towrite{construire récurvivement ? Distinguer les cas $b_j$ dans $\components$ ou $\cs$ (stabilité requise et obtenue)}
-        For $n \in \indexes{\zeta}$, let $s_n = s \PHplay \delta_1 \PHplay \delta'_1 \PHplay \delta''_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_{n-1} \PHplay \delta'_{n-1} \PHplay \delta''_{n-1} \PHplay \zeta_{n-1}$ (or $s_1 = s$),
-          and $\zeta_n = \PHhit{b_i}{a_j}{a_k}$.
-          By hypothesis, $\exists \delta_n \in \muconcr_{s_n}(\PHobj{\any}{b_i})$.
-          If $a \in \cs$, then $\prio(\zeta_n) = 1$ and $\zeta_n$ can be played in $s_n \PHplay \delta_n$ (\ie $\delta'_n = \delta''_n = \varepsilon$).
-          If $a \notin \cs$ and $b \in \cs$, then there exists a scenario $\delta'_n$ so that $b_i \in \pfp_{s_n \PHplay \delta_n \PHplay \delta'_n}(b)$ (because of the $\Bpriocont$ relation).
-          Then, by \pref{th:hcscomp}, there is a scenario $\delta'' \in \restriction{\Sce}{1}$ so that $\zeta_n$ is playable in $s_n \PHplay \delta_n \PHplay \delta'_n \PHplay \delta''_n$.
-          Finally, if $a,b \in \components$, then by \pref{th:hcompcomp}, there is a scenario $\delta'' \in \restriction{\Sce}{1}$ so that $\zeta_n$ is playable in $s_n \PHplay \delta_n \PHplay \delta''_n$ (\ie $\delta'_n = \varepsilon$).
+        Suppose that $\delta_n$ exists and let $\zeta_n = \PHhit{b_i}{a_j}{a_k}$.
+        By hypothesis there exists $\delta' \in \muconcr_{s \PHplay \delta_n}(\PHobj{\any}{b_i})$ with $\PHsort(P) \notin \PHsort(\delta')$ by \pref{def:maxCont}.
+        By \todo{théorème mise à jour} there exists $\delta'' \in \restriction{\Sce}{1}$ so that $\update(s \PHplay \delta') = s \PHplay \delta' \PHplay \delta''$.
+        Furthermore, $\PHget{(s \PHplay \delta' \PHplay \delta'')}{b} = b_j$ \todo{car $b \in \components$ ou $b$ est stable}.
+        Therefore, $\delta_{n+1} = \delta_n \PHplay \delta' \PHplay \delta'' \PHplay \zeta_n$.
       \end{itemize}
-      Thus, $\delta = \delta_m \in \muconcr_s(P)$. % and $\ceil(\delta) \subseteq max\ctx$.
+      Thus, $\delta_{\indexes{\zeta}} \in \muconcr_s(P)$. % and $\ceil(\delta) \subseteq max\ctx$.
   \end{itemize}

### 2013-03-29 main.tex
example & conclusion parts
authors

@@
 
-\section{Example}\label{sec:example}
-\todo{Trouver un exemple représentatif (comportement différent avec / sans priorités)}
-\towrite{Exemple}
+\input{parts/example}
 
-\section{Discussion \& Conclusion}\label{sec:ccl}
-\towrite{Pistes :
-\begin{itemize}
-  \item Modèles Zeno (système de précédences et prise en compte des états globaux)
-\end{itemize}
-}
+\input{parts/ccl}
 

### 2013-03-29 parts/def-ph.tex
defs + demo

@@
 \subsection{Hypothesis} \towrite{Reformuler}
+\label{ssec:hypothesis}
 
@@
 
-Let $\PH$ be a PH model on which we want to apply the static analysis.
-In this paper, we focus on a specific class of models that are equivalent to boolean networks.
+In the scope of this paper, we focus on a specific class of Process Hitting models.
+We define here the restrictions that lead to this class of models \todo{and show that they are equivalent to discrete networks}.
+%Let $\PH$ be a PH model on which we want to apply the static analysis.
+%In this paper, we focus on a specific class of models that are equivalent to boolean networks.
 
@@
 
-In \pref{def:cs} we define the notion of well-formed component.
+This restriction allows to models two kinds of actions: controllable actions that model the non-determinacy of biological evolutions,
+and uncontrollable actions that are used to model non-biological behaviours in the model.
+
+In \pref{def:component} we define the notion of well-formed component.
 A sort $a$ is a well-formed component iff
@@
 
-Given this first hypothesis, we define the neighbor \towrite{revoir terminologie : neighbors ? vicinity ?} sorts and actions (\pref{def:neighbors}).
 \begin{definition}
@@
 \end{definition}
+
+\paragraph{Cycle-freeness between actions of priority $1$}
+There is no cycle in chains of actions: $\forall a \in \PHs, \PHh(a, a) = \emptyset$.
+
+Given this first hypothesis, we define the neighbor \towrite{revoir terminologie : neighbors ? vicinity ?} sorts and actions (\pref{def:neighbors}).
 \begin{definition}
@@
 
-In \pref{def:component} we define the notion of well-formed cooperative sort.
+In \pref{def:cs} we define the notion of well-formed cooperative sort.
 A cooperative sort $a$ is well-formed iff
 it is hit only by actions of priority $1$,
-if any sub-state of its neighbourhood is represented by at least one local steady state in this sort,
-and if any of its processes represents at least one sub-state of its neighbourhood.
+any sub-state of its neighbourhood is represented by exactly one local steady state in this sort,
+and all of its processes represents at least one sub-state of its neighbourhood.
 \begin{definition}
@@
     \item $\forall s \in \underset{b \in \Vs(a)}{\times} \PHl_b, |\pfp_s(a)| = 1$
-    \item $\forall a_i \in \PHl_a, \exists s \in \underset{b \in \Vs(a)}{\times} \PHl_b, a_i \in \pfp_s(a)$
+    \item $\forall a_i \in \PHl_a, \exists s \in \underset{b \in \Vs(a)}{\times} \PHl_b, \pfp_s(a) = \{ a_i \}$
   \end{itemize}
@@
 %We note that: $\forall a \in \components, \Vs(a) = \emptyset \wedge \Vh(a) = \emptyset$
-As any local state of neighbour sorts of a cooperative sort leads to a local steady-state, we denote $\csState(a_i)$ the set of local states represented by the process $a_i$ of the cooperative sort $a$.
+As any local state of neighbour sorts of a cooperative sort leads to a local steady-state, we denote $\csState(a_i)$ the set of sub-states represented by the process $a_i$ of the cooperative sort $a$.
 \begin{definition}[$\csState$]
@@
 \subsection{Consequences of the restrictions}
+Given these hypotheses, we can denote: $\pfp_s(a) = a_i$ the local steady-state of $a$ in state $s$.
+Furthermore, we denote by $\update(s)$ the state in which all cooperative sorts are updated.
+\begin{align*}
+  \update(s) = s \underset{a \in CS}{\Cap } \pfp_{s}(a)
+\end{align*}
+where for all process $a_i$, $s \Cap a_i$ is the state defined by:
+$\PHget{(s \Cap a_i)}{a} = a_i \wedge \forall b \neq a, \PHget{(s \Cap a_i)}{b} = \PHget{s}{b}$.
+
+\pref{th:update} states that from any state, there exists a scenario updating the cooperative sorts of this state.
+\begin{theorem}
+\label{th:update}
+  $\forall s \in \PHl, \exists \delta \in \restriction{\Sce}{1}, s \PHplay \delta = \update(s)$
+\end{theorem}
+\begin{proof}
+  Let $a$ be a cooperative sort so that $\PHget{s}{a} \neq \pfp_s(a)$.
+  Given the definition of $\pfp_s(a)$, there exists a scenario updating $a$ in $s$.
+  As there is no cycle in between the cooperative sorts and an updated cooperative sort cannot evolve, at most $|\cs|$ updates can be done.
+\end{proof}
 \pref{th:hcompcomp} states that for a given state $s$ and for any action $h = \PHhit{a_i}{b_j}{b_k}$ between well-formed components, $h$ can be played after a series of hits that do not prevent it to be fired.
@@
 \begin{proof}
-  There exists a scenario $\delta$ so that: $(s \PHplay \delta) = \update(s)$.
+  From \pref{th:update}, there exists a scenario $\delta$ so that: $(s \PHplay \delta) = \update(s)$.
   As $a,b \in \components$, $a_i \in s \PHplay \delta$ and $b_j \in s \PHplay \delta$.
@@
 \begin{proof}
-  There exists a scenario $\delta$ so that: $(s \PHplay \delta) = \update(s)$.
+  From \pref{th:update}, there exists a scenario $\delta$ so that: $(s \PHplay \delta) = \update(s)$.
   As $a_i \in \pfp_s(a)$, $a_i \in s \PHplay \delta$.

### 2013-03-29 parts/sa.tex
defs + demo

@@
 
-Processus rencontrés :
-\todo{Revenir à la définition simple de procs ?}
+The set of all processes involved in an abstract structure $\cwB$ is given in \pref{def:allprocs}.
+\begin{definition}
+\label{def:allprocs}
   \begin{align*}
-&\allprocs((\cwSol,\cwReq,\cwCont,\cwSat)) = \{ p \in \PHproc \mid \exists (P,ps) \in \cwSol, p \in ps \\
-  &\qquad\qquad \vee p = \PHtarget(P) \vee \exists h \in \BS(P), (p = \PHhitter(h) \vee p = \PHbounce(h)) \\
-  &\qquad\qquad \vee \exists(Q, \PHobj{p}{\PHbounce(Q)} \in \cwPrioCont \}
+  &\allprocs((\cwSol,\cwReq,\cwRSP,\cwCont)) = \{ p \in \PHproc \mid \exists (P,ps) \in \cwSol, \\
+    &\qquad\qquad p \in ps \vee p = \PHtarget(P) \vee p = \PHbounce(P) \} \\
+  %  &\qquad\qquad \vee p = \PHtarget(P) \vee \exists h \in \BS(P), (p = \PHhitter(h) \vee p = \PHbounce(h)) \\
+  %  &\qquad\qquad \vee \exists(Q, \PHobj{p}{\PHbounce(Q)} \in \cwPrioCont \}
   \end{align*}
+\end{definition}
 
@@
 \end{comment}
-
-Mise à jour de l'état initial :
-\begin{align*}
-  \update(\ctx) = \ctx \Cap \bigcup_{a \in CS} \pfp_{\restriction{\ctx}{\Vs(a) \cup \{ a \}}}(a)
-\end{align*}
 
@@
     Therefore, $\forall i \in \segm{1}{n+1}$, $\PHget{(s \PHplay \delta_n \PHplay \delta')}{\PHsort(p_{i})} = p_{i}$.
-    Finally, by theorem \todo{théorème mise à jour}, there exists a scenario $\delta'' \in \restriction{\Sce}{1}$
+    Finally, by \pref{th:update}, there exists a scenario $\delta'' \in \restriction{\Sce}{1}$
     that can be played in $s \PHplay \delta_n \PHplay \delta'$
     and so that, if we denote $\delta_{n+1} = \delta_n \PHplay \delta' \PHplay \delta''$,
-    we have: $\update(s \PHplay \delta_n \PHplay \delta') = s \PHplay \delta_{n+1}$ (\todo{théorème stabilité}), and the same property about processes.
+    we have: $\update(s \PHplay \delta_n \PHplay \delta') = s \PHplay \delta_{n+1}$ and the same property about processes (by \pref{th:hcscomp}).
 \end{itemize}
@@
         By hypothesis there exists $\delta' \in \muconcr_{s \PHplay \delta_n}(\PHobj{\any}{b_i})$ with $\PHsort(P) \notin \PHsort(\delta')$ by \pref{def:maxCont}.
-        By \todo{théorème mise à jour} there exists $\delta'' \in \restriction{\Sce}{1}$ so that $\update(s \PHplay \delta') = s \PHplay \delta' \PHplay \delta''$.
-        Furthermore, $\PHget{(s \PHplay \delta' \PHplay \delta'')}{b} = b_j$ \todo{car $b \in \components$ ou $b$ est stable}.
+        By \pref{th:update} there exists $\delta'' \in \restriction{\Sce}{1}$ so that $\update(s \PHplay \delta') = s \PHplay \delta' \PHplay \delta''$.
+        Furthermore, $\PHget{(s \PHplay \delta' \PHplay \delta'')}{b} = b_j$ (by \pref{th:hcompcomp} if $b \in \components$ or \pref{th:hcscomp} if $b \in \cs$).
         Therefore, $\delta_{n+1} = \delta_n \PHplay \delta' \PHplay \delta'' \PHplay \zeta_n$.
@@
 \end{itemize}
-
 Finally, as $\muconcr_{max\ctx}(\w) \neq \emptyset$, $\uconcr(\w) \neq \emptyset$ (\pref{th:uconcr-ctx}).

### 2013-03-29 parts/def-ph.tex
minor fixes
remove most comments

@@
 An action $h=\PHfrappe{a_i}{b_j}{b_k}$ is read as ``$a_i$ \emph{hits} $b_j$ to make it bounce to $b_k$'', and $a_i,b_j,b_k$ are called respectively \emph{hitter}, \emph{target} and \emph{bounce} of the action, and can be referred to as $\PHhitter(h), \PHtarget(h), \PHbounce(h)$, respectively.
-
-% Process Hitting sans priorités
-\begin{comment}
-\begin{definition}[Process Hitting]\label{def:PH}
-A \emph{Process Hitting} is a triple $(\PHs,\PHl,\PHa)$:
-\begin{itemize}
-\item $\PHs \DEF \{a,b,\dots\}$ is the finite set of \emph{sorts};
-\item $\PHl \DEF \prod_{a\in\PHs} \PHl_a$ is the set of states with $\PHl_a = \{a_0,\dots,a_{l_a}\}$
-the finite set of \emph{processes} of sort $a\in\Sigma$ and $l_a$ a positive integer with
-	$a\neq b\Rightarrow \forall(a_i,b_j)\in\PHl_a\times\PHl_b,a_i\neq b_j$;
-\item $\PHa \DEF \{ \PHfrappe{a_i}{b_j}{b_k}, \dots \mid
-					(a,b)\in\PHs^2 \wedge (a_i,b_j,b_k)\in \PHl_a\times\PHl_b\times\PHl_b$ \\
-	\hspace*{2cm} $\wedge b_j\neq b_k \wedge a=b\Rightarrow a_i=b_j\}$
-			is the finite set of \emph{actions}.
-\end{itemize}
-$\PHproc$ denotes the set of all processes ($\PHproc \DEF \{ a_i\mid a\in\PHs \wedge a_i\in\PHl_a\}$).
-\end{definition}
-\end{comment}
 
@@
   Furthermore, we denote: $\restriction{\Sce}{n}$ the set of scenarios of actions of $\restriction{\PHa}{n}$.
-%  
-%  Furthermore, we define: $\restriction{\PH}{0} = (\PHs; \PHl; \restriction{\PHa}{0})$, where $\restriction{\PHa}{0} = ()$ is a $0$-uplet.
 \end{definition}
-
-\begin{comment} %example*
-\pref{fig:runningPH-1} represents a PH $(\PHs,\PHl,\PHa)$ with
-$\PHs = \{a,b,c\}$,
-$\PHl_a = \{a_0,a_1,a_2\}$,
-$\PHl_b = \{b_0, b_1\}$,
-$\PHl_c = \{c_0, c_1\}$, and
-\begin{align*}
-\PHa & = \{
-	\PHfrappe{a_2}{b_1}{b_0},
-&&  \PHfrappe{b_0}{a_2}{a_1},
-&&	\PHfrappe{c_0}{a_2}{a_1},\\
-&&& \PHfrappe{b_0}{a_1}{a_0},
-&&	\PHfrappe{c_0}{a_1}{a_0},\\
-&&& \PHfrappe{b_1}{a_0}{a_1},
-&&	\PHfrappe{c_1}{a_0}{a_1},\\
-&&& \PHfrappe{b_1}{a_1}{a_2},
-&&	\PHfrappe{c_1}{a_1}{a_2} \}\enspace.
-\end{align*}
-The action $h=\PHfrappe{b_1}{a_1}{a_2}$ is playable in the state
-$s = \PHstate{b_1,a_1,c_0}$; and $s\PHplay h=\PHstate{b_1,a_2,c_0}$.
-%
-\begin{figure}[t]
-\centering
-\scalebox{1.3}{
-\begin{tikzpicture}
-\TSort{(0,0)}{a}{3}{r}
-\TSort{(-3,0.5)}{b}{2}{l}
-\TSort{(3,0.5)}{c}{2}{r}
-%
-\THit{b_1}{very thick}{a_0}{.west}{a_1}
-\THit{b_1}{very thick}{a_1}{.north west}{a_2}
-\THit{b_0}{}{a_2}{.west}{a_1}
-\THit{b_0}{}{a_1}{.west}{a_0}
-%
-\path[bounce, bend left=60]
-\TBounce{a_1}{very thick}{a_2}{.south}
-\TBounce{a_0}{very thick}{a_1}{.south}
-;
-\path[bounce, bend right=60]
-\TBounce{a_2}{}{a_1}{.north}
-\TBounce{a_1}{}{a_0}{.north}
-;
-%
-\THit{c_1}{very thick}{a_0}{.east}{a_1}
-\THit{c_1}{very thick}{a_1}{.north east}{a_2}
-\THit{c_0}{}{a_2}{.east}{a_1}
-\THit{c_0}{}{a_1}{.east}{a_0}
-%
-\path[bounce, bend right=60]
-\TBounce{a_1}{very thick}{a_2}{.south east}
-\TBounce{a_0}{very thick}{a_1}{.south east}
-;
-\path[bounce, bend left=60]
-\TBounce{a_2}{}{a_1}{.north}
-\TBounce{a_1}{}{a_0}{.north east}
-;
-%
-\THit{a_2}{bend right}{b_1}{.north east}{b_0}
-\path[bounce, bend left=80]
-\TBounce{b_1}{out=100,in=140}{b_0}{.north}
-;
-\end{tikzpicture}
-}
-\caption{\label{fig:runningPH-1}
-A Process Hitting (PH) example.
-Sorts are represented by labeled boxes, and processes by circles (ticks are
-the identifiers of the processes within the sort, for instance, $a_0$ is the
-process ticked $0$ in the box $a$).
-An action (for instance $\PHfrappe{b_1}{a_1}{a_2}$) is represented by a pair of
-directed arcs, having the hit part ($b_1$ to $a_1$) in plain line and the bounce
-part ($a_1$ to $a_2$) in dotted line.
-Actions involving $b_1$ or $c_1$ are in thick lines.
-%The current state is represented by the grayed processes:
-%$\PHstate{a_0,b_1,c_0,d_0}$.
-}
-\end{figure}
-
-This PH example actually models a BRN where the component $a$ has three qualitative
-levels and components $b$ and $c$ are boolean.
-In this BRN, $b$ and $c$ activate $a$, while $a$ inhibits $b$.
-The inhibition of $b$ by $a$ is only effective when $a$ is at level $2$;
-in the other cases, $b$ cannot evolve in any direction.
-The activation of $a$ by $b$ ($c$) is encoded by the actions making the level of $a$ increase (resp.
-decrease) when $b$ ($c$) is present (resp. absent).
-It is worth noticing that the activation of $a$ by $b$ ($c$) is independent from $c$ ($b$).
-This may express a lack of knowledge on the cooperation between these two regulators:
-we thus model an over-approximation of the possible actions.
-\end{example*}
-\end{comment}
 
@@
 
-\begin{comment}
-\begin{figure}[p]
-\centering
-\scalebox{1.3}{
-\begin{tikzpicture}
-\TSort{(0,0)}{b}{2}{t}
-\TSort{(0,-3.8)}{c}{2}{b}
-\TSort{(4.5,-3)}{a}{3}{r}
-
-\TSetTick{bc}{0}{00}
-\TSetTick{bc}{1}{01}
-\TSetTick{bc}{2}{10}
-\TSetTick{bc}{3}{11}
-% \TSetSortLbcel{bc}{$\neg a\wedge b$}
-\TSort{(-0.5,-2)}{bc}{4}{b}
-
-\THit{b_1}{very thick,bend right}{bc_0}{.north}{bc_2}
-\THit{b_1}{very thick,bend right}{bc_1}{.north}{bc_3}
-\THit{b_0}{}{bc_2}{.north west}{bc_0}
-\THit{b_0}{}{bc_3}{.north west}{bc_1}
-
-\THit{c_0}{}{bc_1}{.south}{bc_0}
-\THit{c_0}{}{bc_3}{.south}{bc_2}
-\THit{c_1}{very thick}{bc_0}{.south}{bc_1}
-\THit{c_1}{very thick}{bc_2}{.south}{bc_3}
-
-\path[bounce, bend right=25]
-\TBounce{bc_2}{}{bc_0}{.north east}
-\TBounce{bc_3}{}{bc_1}{.north east}
-;
-\path[bounce, bend left=80, distance=30]
-\TBounce{bc_0}{very thick}{bc_2}{.north}
-\TBounce{bc_1}{very thick}{bc_3}{.north}
-;
-\path[bounce, bend right]
-\TBounce{bc_0}{very thick}{bc_1}{.west}
-\TBounce{bc_2}{very thick}{bc_3}{.west}
-;
-\path[bounce, bend left]
-\TBounce{bc_3}{}{bc_2}{.east}
-\TBounce{bc_1}{}{bc_0}{.east}
-;
-
-\THit{bc_3}{}{a_1}{.west}{a_2}
-\path[bounce, bend left=40]
-\TBounce{a_1}{}{a_2}{.south west}
-;
-
-\end{tikzpicture}
-}
-
-\caption{\label{fig:PH-cooperativity}
-\towrite{Ajouter priorités}
-A PH modeling a cooperativity between $b_1$ and $c_1$ to make
-$a_1$ bounce to $a_2$.
-Actions involving $b_1$ or $c_1$ are in thick lines.
-}
-\end{figure}
-\end{comment}
-
-\begin{comment}
-\begin{figure}
-  \centering
-  \begin{tikzpicture}
-    \TSort{(0,0)}{a}{2}{l}
-    \TSort{(2,0)}{b}{2}{r}
-    \TSort{(4,0)}{c}{2}{r}
-
-    \THit{a_1}{prio}{b_1}{.west}{b_0}
-    \THit{b_1}{}{c_0}{.north west}{c_1}
-
-    \path[bounce, bend right]
-    \TBounce{b_1}{}{b_0}{.north west}
-    ;
-    \path[bounce, bend left]
-    \TBounce{c_0}{}{c_1}{.south west}
-    ;
-  \end{tikzpicture}
-  \label{fig:ph-conca}
-  \caption{A simple PH example depicting “backward concurrency” between two actions belonging to different classes of priorities.}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \begin{tikzpicture}
-    \TSort{(0,0)}{a}{2}{l}
-    \TSort{(2,0)}{b}{2}{r}
-    \TSort{(4,0)}{c}{3}{r}
-
-    \THit{a_1}{}{b_0}{.west}{b_1}
-    \THit{b_0}{prio}{c_1}{.south west}{c_0}
-    \THit{b_1}{prio}{c_1}{.west}{c_2}
-
-    \path[bounce, bend left]
-    \TBounce{b_0}{}{b_1}{.south west}
-    \TBounce{c_1}{}{c_2}{.south west}
-    ;
-    \path[bounce, bend right]
-    \TBounce{c_1}{}{c_0}{.north west}
-    ;
-  \end{tikzpicture}
-  \label{fig:ph-concb}
-  \caption{A simple PH example depicting “forward concurrency” between two actions belonging to different classes of priorities.}
-\end{figure}
-\end{comment}
-
-\begin{comment}
-\begin{figure}[p]
-\centering
-\scalebox{1.3}{
-\begin{tikzpicture}
-\path[use as bounding box] (-4,-1.9) rectangle (4.5,3.9);
-%
-\TSort{(0,0)}{a}{3}{l}
-\TSort{(3, 3)}{b}{2}{t}
-\TSort{(3,-1)}{c}{2}{b}
-%
-\TSetTick{bc}{0}{00}
-\TSetTick{bc}{1}{01}
-\TSetTick{bc}{2}{10}
-\TSetTick{bc}{3}{11}
-% \TSetSortLbcel{bc}{$\neg a\wedge b$}
-\TSort{(-3,-0.5)}{bc}{4}{l}
-%
-\THit{bc_3}{}{a_1}{.north west}{a_2}
-\THit{bc_0}{}{a_1}{.south west}{a_0}
-\path[bounce]
-\TBounce{a_1}{bend left}{a_2}{.south west}
-\TBounce{a_1}{bend right}{a_0}{.north west}
-;
-%
-\THit{b_0}{}{a_2}{.east}{a_1}
-\THit{b_1}{}{a_0}{.north east}{a_1}
-\path[bounce]
-\TBounce{a_2}{bend left}{a_1}{.north east}
-\TBounce{a_0}{bend right=20}{a_1}{.south}
-;
-%
-\THit{c_0}{bend right}{a_2}{.south east}{a_1}
-\THit{c_1}{bend right}{a_0}{.east}{a_1}
-\path[bounce]
-\TBounce{a_2}{bend left=20}{a_1}{.north}
-\TBounce{a_0}{bend right=30}{a_1}{.south east}
-;
-%
-\path[dashed,hit]
-	(2,-1.3) edge[bend left=10] (-2.3,-0.7)
-	(2.2, 3.3) edge[bend right=10] (-2.3,3)
-;
-%
-\THit{a_2}{bend left,out=40,in=80}{b_1}{.north west}{b_0}
-\path[bounce, bend right]
-\TBounce{b_1}{}{b_0}{.east}
-;
-%
-\end{tikzpicture}
-}
-%
-\caption{\label{fig:runningPH-2}
-PH resulting from the refinement of the one in \pref{fig:runningPH-1} by the
-specification of several cooperations.
-The actions from $b$ and $c$ to the cooperative sort $bc$ are identical to those defined in
-\pref{fig:PH-cooperativity} and are represented here by a single dashed arc.
-}
-\end{figure}
-\end{comment}
-
 We note that cooperative sorts are standard PH sorts and do not involve any
@@
 
-%In this section, we describe several restrictions.
-%Although the definition of a Process Hitting with $k$ priorities allows a wide range of models, the method given in the next section only applies to Process Hitting models that regard these restrictions.
-
-\begin{comment}
-We define the set of chains of actions $\PHh^n(b, a)$ between two sorts $b$ and $a$, with $n \in \segm{1}{k}$, as below:
-\begin{align*}
-\PHh^n(b, a) = \{ (h_i)_{i \in \segm{0}{s}} \in (\restriction{\PHh}{n})^{s+1} &\mid s \in \sN, \PHsort(\PHhitter(h_0)) = b \wedge \PHsort(\PHtarget(h_s)) = a \\
-  & \wedge \forall i \in \segm{1}{s}, \PHsort(\PHtarget(h_{i-1})) = \PHsort(\PHhitter(h_{i})) \}
-\end{align*}
-
-We define the neighbor \towrite{Revoir terminologie : “neighborhood” ? “vicinity” ?} sorts of any sort $a$ and $n \in \segm{1}{k}$ as :
-$$
-\Vs^n(a) = \{ b \in \PHs \mid \PHh^m(b, a) \neq \emptyset \wedge m = \min(n, \prio(a)) \} \cup \{ a \}
-$$
-
-And, as a shortcut:
-$$
-\Vs(a) = \Vs^{\prio(a)}(a)
-$$
-
-We define the neighbor actions of any sort $a$ as :
-$$
-\Vh(a) = \{ h \in \restriction{\PHh}{\prio(a)} \mid \{ \PHsort(\PHhitter(h)), \PHsort(\PHtarget(h)) \} \subset \Vs(a) \wedge \prio(h) \leq \prio(a) \}
-$$
-\end{comment}
-
-%\paragraph{Cycle-freeness of $\restriction{\PH}{k-1}$}
-%\towrite{Définition formelle ? + justification}
-%The model $\restriction{\PH}{k-1}$ contains no cycles. Cycles are still allowed in $\PH$ however.
-
 In the scope of this paper, we focus on a specific class of Process Hitting models.
 We define here the restrictions that lead to this class of models \todo{and show that they are equivalent to discrete networks}.
-%Let $\PH$ be a PH model on which we want to apply the static analysis.
-%In this paper, we focus on a specific class of models that are equivalent to boolean networks.
 
@@
 We denote $\pfp_s(a)$ the set of possible local steady-states of a sort $a$ from a state $s$.
-\todo{À corriger : état global ? + prendre en compte l'état de la sorte}
+\todo{À corriger : état global ?}
 \begin{align*}
@@
 Formally : $\exists N \in \sN, \forall \delta \in \restriction{\Sce}{1}, |\indexes{\delta}| \leq N$.
-
-\begin{comment}
-\paragraph{Bounded termination}
-The dynamics of model $\restriction{\PH}{k-1}$ contains no cycles. Cycles are still allowed in $\PH$ however.
-Formally : $\exists N \in \sN, \forall \delta \in \restriction{\Sce}{k-1}, |\indexes{\delta}| \leq N$.
-
-\paragraph{Local priorities}
-\towrite{Justification}
-All actions hitting the same sort belong to the same class of priority:
-$$\forall h_1, h_2 \in \PHh, \PHtarget(h_1) = \PHtarget(h_2) \Rightarrow \prio(h_1) = \prio(h_2)$$
-Furthermore, for all sort $a$, we denote $\prio(a)$ the priority of the actions hitting $a$, if any:
-$$\forall a \in \PHs, \exists h \in \PHh, \PHtarget(h) = a \Rightarrow \prio(a) = \prio(h)$$
-\towrite{Ou : $\nexists h \Rightarrow \prio(a) = 0$}
-
-\paragraph{Local stable states}
-\towrite{Justification}
-We define $\pfp$ as the set of possible stable states of a sort from a given state:
-\begin{align*}
-  \pfp_\ctx = \{ s \PHplay \delta \in \PHl &\mid s \in \ctx \wedge \delta \in \restriction{\Sce}{k-1} \\
-  & \qquad \wedge \forall \PHhit{b_i}{c_j}{c_k} \in \restriction{\PHh}{k-1}, \PHget{(s \PHplay \delta)}{b} \neq b_i \vee \PHget{(s \PHplay \delta)}{c} \neq c_j \}
-  %\text{$h$ n'est pas jouable dans $s \PHplay \delta$} \}
-\end{align*}
-
-All processes are a stable state of a sub-state of the predecessors:
-$\forall a_i \in \PHproc, \prio(a) < k \Rightarrow \exists s \in \restriction{\PHl}{\Vs(a)}, a_i \in \pfp_s$.
-We note: $\stable_{a_i} = \{ s \in \restriction{\PHl}{\Vs(a)} \mid a_i \in \pfp_s \}$.
-\end{comment}
-
-\begin{comment}
-These restrictions bring new interesting properties to the PH models regarding them.
-
-\pref{th:vplay} tells that for any action $h = \PHhit{a_i}{b_j}{b_k}$, if no action can be played in the neighborhood of $a$ in a given state, then $h$ can be played after a series of hits that do not prevent it to be fired.
-Furthermore, if the requisites of \pref{th:vplay} are true, then no action of this series of hits belongs to $V(a)$, as stated in \pref{co:vplay}.
-\begin{theorem}
-\label{th:vplay}
-  $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, (\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j \wedge $\\
-  $\forall h' \in \Vh^{\prio(b)-1}(a), \PHhitter(h') \notin s \wedge \PHtarget(h') \notin s) \Rightarrow$\\
-  $(\exists \delta \in \Sce, \text{$h$ can be played in $s \PHplay \delta$})$
-\end{theorem}
-
-\begin{proof}
-  Because of the cycle-freeness of $\restriction{\PH}{k-1}$, $\restriction{\PH}{\prio(a)}$ is also cycle-free and there is a $\delta \in \Sce$ so that $\forall h' \in \PHh$, $h'$ cannot be played in $s \PHplay \delta$.
-Furthermore, $\forall h' \in \delta, \PHsort(\PHtarget(h')) \neq a$ by construction of $\Vs(a)$.
-\end{proof}
-
-\begin{corollary}
-  \label{co:vplay}
-  $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, (\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j \wedge $\\
-  $\forall h' \in \Vh^{\prio(b)-1}(a), \PHhitter(h') \notin s \wedge \PHtarget(h') \notin s) \Rightarrow$\\
-  $\exists \delta \in \Sce, (\forall n \in \indexes{\delta}, \delta_n \notin \Vh(a)) \wedge (\text{$h$ can be played in $s \PHplay \delta$})$
-\end{corollary}
-
-\pref{th:totalss} states that from any state, a steady state is eventually reached. A local variant of this theorem, given in \pref{co:totalss}, can be derived,
-where, for all $\Omega \subset \PHs$, $$\restriction{\PHl}{\Omega} = \underset{a \in \Omega}{\times} \PHl_a$$ and
-for all $H \subset \PHh$, $$\restriction{\Sce}{H} = \{ \delta \in \Sce \mid \forall n \in \indexes{\delta}, \delta_n \in H \} \enspace .$$
-\begin{theorem}
-\label{th:totalss}
-  $\forall n \in \segm{1}{k-1}, \forall s \in \PHl, \exists \delta \in \restriction{\Sce}{n}$, no action of model $\restriction{\PH}{n}$ can be played in $s \PHplay \delta$.
-\end{theorem}
-
-\begin{corollary}
-\label{co:totalss}
-  $\forall a \in \PHs, \forall s \in \restriction{\PHl}{\Vs(a)}, \exists \delta \in \restriction{\Sce}{\Vh(a)}$, no action of $\Vh(a)$ can be played in $s \PHplay \delta$.
-\end{corollary}
-
-\pref{th:autohits} states that any sequence $\zeta$ of self-actions can be played eventually.
-\begin{theorem}
-\label{th:autohits}
-  Let $a \in \PHs$, $s \in \PHl$ and $\zeta \in \BS(a)$, with $n = |\indexes{\zeta}|$ so that $\forall i \in \segm{1}{n}, \PHsort(\PHhitter(\zeta_i)) = a$.
-  %If no action can be played in $V(a)$ in state $s$, then
-  $\exists (\delta_i)_{i \in \segm{1}{n}} \in \Sce$ so that $\forall i \in \segm{1}{n}$, $\zeta_i$ can be played in $s \PHplay \delta_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_i$. 
-\end{theorem}
-
-\begin{proof}
-  With \pref{co:vplay} applied iteratively.
-\end{proof}
-
-\towrite{Théorème nécessaire pour la suite: une séquence d'actions dans $\BS(a)$ peut être jouée si précédée ou entrelacée par des $\zeta$ (?)}
-\end{comment}
 

### 2013-03-29 parts/sa.tex
minor fixes
remove most comments

@@
 
-%%% N'est plus utile (?)
-%Plus haute priorité :
-%$$\forall a \in \PHs, \priomax(a) = \max_{h \in \PHh, \PHtarget(h) = a}(\prio(h))$$
-
-%%% N'est plus utile (?)
-%Processus possibles :
-%\begin{align*}
-%\procs((\cwSol,\cwReq,\cwCont)) = \{ p \in \PHproc &\mid \exists (P,ps) \in \cwSol, p \in ps
-%\\ & \vee p = \PHtarget(P)
-%\\ & \vee (P \neq \omega \Rightarrow p = \PHbounce(P)) \}
-%%\\ & \vee \exists h \in \BS(P), (p = \PHhitter(h) \vee p = \PHbounce(h)) \}
-%\end{align*}
-
 The set of all processes involved in an abstract structure $\cwB$ is given in \pref{def:allprocs}.
@@
 \end{definition}
-
-\subsection{Local fixed points / possible bounces}
-
-%%% Pas utile
-%Points fixes possibles : pour toute sorte $a$ et tout contexte partiel $\ctx$ sur $V^n(a)$:
-%\begin{align*}
-%  \pfp_\ctx: \PHs &\rightarrow \wp(\PHproc) \\
-%  a &\mapsto \{ s \in \underset{b \in V^n(a)}{\times} \PHl_b \mid \text{$s$ est accessible depuis $\ctx$ et aucune action n'y est jouable} \}
-%\end{align*}
-
-\begin{comment}
-Points fixes possibles : pour toute sorte $a$ et tout contexte $\ctx$:
-\begin{align*}
-  \pfp_\ctx: \PHs &\rightarrow \wp(\PHproc) \\
-  a &\mapsto \{ s \PHplay \delta \in \restriction{\PHl}{\Vs(a)} \mid s \in \restriction{\ctx}{\Vs(a)} \wedge \delta \in \restriction{\Sce}{\Vs(a)} \\
-  &\qquad\qquad\qquad\qquad \wedge \forall \PHhit{b_i}{c_j}{c_k} \in \Vh(a), \PHget{(s \PHplay \delta)}{b} \neq b_i \vee \PHget{(s \PHplay \delta)}{c} \neq c_j \}
-  %\text{$h$ n'est pas jouable dans $s \PHplay \delta$} \}
-\end{align*}
-%
-Processus rencontrés comme résultats d'un point fixe :
-\begin{align*}
-\pfpprocs_\ctx(a) = \{ \PHget{s}{a} \mid s \in \pfp_\ctx(a) \}
-\end{align*}
-%
-Le nouvel ensemble de processus à prendre en compte à chaque itération du pppf :
-\begin{align*}
-\newprocs_\ctx(\myB) = %\allprocs(\myB) \cup \bigcup_{a \in \PHs} \pfpprocs_{\allprocs(\myB)}(a)
-  \{ a_k \in \PHproc &\mid a_k \in \allprocs(\myB) \vee \\
-  & (a_i, \PHobjp{a}{j}{i}) \in \cwReq \wedge a_k \in \pfpprocs_{\ctx \Cap \allprocs(\myB)}(a) \wedge \\
-  & \quad (\exists (P, ps) \in \cwSol, a_i \in ps \wedge \prio(\PHsort(P)) > \prio(a) \\
-  & \quad \vee \exists (\PHobjp{a}{j}{i}, ps) \in \cwSol, \exists p \in ps, \exists (p, P) \in \cwReq,\\
-  & \qquad \text{$P$ is not trivial} \wedge \prio(\PHsort(P)) > \prio(a) \}
-\end{align*}
-\end{comment}
-
-\begin{comment}
-=================
-%
-Nouvelle version des états stables possibles: pour tout contexte $\ctx$:
-\begin{align*}
-  \pfp_\ctx = \{ s \PHplay \delta \in \PHl &\mid s \in \ctx \wedge \delta \in \restriction{\Sce}{k-1} \\
-  & \qquad \wedge \forall \PHhit{b_i}{c_j}{c_k} \in \restriction{\PHh}{k-1}, \PHget{(s \PHplay \delta)}{b} \neq b_i \vee \PHget{(s \PHplay \delta)}{c} \neq c_j \}
-  %\text{$h$ n'est pas jouable dans $s \PHplay \delta$} \}
-\end{align*}
-%
-Processus rencontrés comme résultats d'un état stable :
-\begin{align*}
-\pfpprocs_\ctx = \{ a_i \in \PHproc \mid \exists s \in \pfp_\ctx, a_i \in s \}
-\end{align*}
-%
-Nouvel ensemble $\newprocs$ :
-\begin{align*}
-\newprocs_\ctx(\myB) = \allprocs(\myB) \cup \pfpprocs_\ctx
-\end{align*}
-\end{comment}
-
-\begin{comment}
-==========================
-
-Bonds possibles :
-\begin{align*}
-\bounceprocs_\ctx = \{ a_i \in \PHproc \mid \exists s \in \ctx, \exists \delta \in \restriction{\Sce}{k-1}, a_i \in (s \PHplay \delta) \}
-\end{align*}
-\end{comment}
-
-%%% N'est plus adapté
-%Points fixes possibles sur un ensemble de sortes :
-%\begin{align*}
-%  \pfp: \mathbb{A} &\rightarrow \wp(\PHproc) \\
-%  \myB &\mapsto \bigcup_{a \in A} \pfp_{\allprocs(\myB)}(a)
-%\end{align*}
-
-\begin{comment}
-Séquences de bonds abstraites :
-$$\BS^\wedge(P) = \{ \zeta^\wedge \mid \zeta \in \BS(P), \nexists \zeta' \in \BS(P), \zeta'^\wedge \subsetneq \zeta^\wedge \}$$
-where $\zeta^\wedge = (\zeta^\wedge_A, \zeta^\wedge_B, \zeta^\wedge_{max})$ with:
-\begin{itemize}
-  \item $\zeta^\wedge_A = \{ \PHhitter(\zeta_n) \mid n \in \indexes{\zeta} \wedge \PHsort(\PHhitter(\zeta_n)) \neq \PHsort(P) \}$ : ens. des requis d'autres sortes (frappeurs)
-  \item $\zeta^\wedge_B = \{ \PHhitter(\zeta_n) \mid n \in \indexes{\zeta} \} \cup \{ \PHtarget(\zeta_n) \mid n \in \indexes{\zeta} \}$ : ens. des processus nécessaires (à ne pas perturber)
-  \item $\zeta^\wedge_{max} = \max_{n \in \indexes{\zeta}}(\prio(\zeta_n))$ : plus faible priorité
-\end{itemize}
-\end{comment}
 
@@
       \begin{itemize}
-        \item[*] \towrite{construire récurvivement ? Distinguer les cas $b_j$ dans $\components$ ou $\cs$ (stabilité requise et obtenue)}
-        Suppose that $\delta_n$ exists and let $\zeta_n = \PHhit{b_i}{a_j}{a_k}$.
+        \item[*] Suppose that $\delta_n$ exists and let $\zeta_n = \PHhit{b_i}{a_j}{a_k}$.
         By hypothesis there exists $\delta' \in \muconcr_{s \PHplay \delta_n}(\PHobj{\any}{b_i})$ with $\PHsort(P) \notin \PHsort(\delta')$ by \pref{def:maxCont}.
@@
 \end{proof}
-
-%%% Ancien graphe avec PrioCont
-\begin{comment}
-\begin{definition}
-  \label{def:aS}
-  The abstract structure $\cwB=(\Breq,\Bsol,\Bcont,\Bsat)$ is defined as
-  $\cwB = \sfp{\aB^\w_{\update(\ctx)}}{\myB}{\aB^\w_{\ctx \Cap \allprocs_\ctx(\myB)}}$,\\
-  with $\myB=(\myreq,\mysol,\mycont,\mysat)$:
-  \begin{align*}
-    \myreq &= \{ (a_i,\PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid
-      a_j \in \PHget{\ctx}{a} \\ % \vee a_j \in \pfpprocs_\ctx(a) \\
-      & \qquad \wedge (\exists (P,ps) \in \mysol, a_i \in ps \vee \exists n \in \indexes{\w}, \PHbounce(\w_n)=a_i) \}
-    \\
-    \mysol &\subseteq \{ (P,ps) \in \Obj \times \powerset(\PHproc) \mid
-            \exists (a_i, P) \in \myreq \wedge ps \in \aBS(P) \\
-      & \qquad\qquad \vee \exists (Q, P) \in \mycont \wedge ps \in \aBS(P) \}
-    \\
-    \mycont & = \{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid
-      \exists (P, ps) \in \mysol \\
-      & \qquad\qquad \wedge q \in \gCont_\ctx(\PHsort(P),P) \}
-    \\
-    \mysat & = \{ (\PHobjp{a}{j}{i}, \PHobjp{a}{k}{i}) \in \Obj \times \Obj \mid
-      \exists (a_i, \PHobj{a_j}{a_i}) \in \myreq\\
-      & \qquad\qquad \wedge a_j \neq a_k \wedge a_k \in \pfp_\ctx(a) \}
-%%% Version états stables locaux
-%    \mysat & = \{ (\PHobjp{a}{j}{i}, \PHobjp{a}{k}{i}) \in \Obj \times \Obj \mid
-%      \exists (a_i, \PHobjp{a}{j}{i}) \in \myreq, \\
-%      & \qquad\qquad a_j \neq a_k \wedge a_k \in \pfpprocs_\ctx(a) \\
-%      & \qquad\qquad \wedge (\exists (P, ps) \in \mysol, a_i \in ps \wedge \prio(\PHsort(P)) > \prio(a) \\
-%      & \qquad\qquad\qquad \vee \exists (\PHobjp{a}{j}{i}, ps) \in \mysol, \exists p \in ps, \exists (p, P) \in \myreq,\\
-%      & \qquad\qquad\qquad \text{$P$ is not trivial} \wedge \prio(\PHsort(P)) > \prio(a) \}
-  \end{align*}
-\end{definition}
-
-\begin{theorem}[Approximation inf.]\label{th:approxinf}
-If the graph $\cwB$ contains no cycle and all objectives have at least one solution, then $\uconcr(\w) \neq \emptyset$.
-\end{theorem}
-
-\begin{proof}
-We note $max\ctx = \update(\ctx) \Cap \allprocs(\cwB)$ the context supported by $\cwB$.
-As there is no cycle in $\cwB$, we show by induction that $\forall s\in L, s\subseteq max\ctx$, 
-for all objective $P$ in $\cwB$ so that $\PHtarget(P) \in s$,
-$\exists \delta \in \muconcr_s(P)$.% and $\ceil(\delta) \subseteq max\ctx$.
-
-\begin{itemize}
-  \item If $(P, \emptyset) \in \Bsol$, either $\PHtarget(P) = \PHbounce(P)$ and $\delta = \emptyseq$,
-    or $\forall \zeta \in \BS(P), \zeta \in \Sce \wedge \PHsort(\zeta) = \{ \PHsort(P) \}$ and $\delta$ is given by \pref{th:autohits}.
-
-  \item Suppose all children objectives of $P$ are concretizable.
-  \begin{itemize}
-    \item If $\exists (P, Q) \in \Bcont$, then by hypothesis,
-      $\muconcr_{s}(\obj{\PHtarget(P)}{\PHtarget(Q)} \concat Q) \neq \emptyset$, thus
-      $\muconcr_{s}(P) \neq \emptyset$.
-    \item If $\exists (P, Q) \in \Bpriocont$, then by hypothesis,
-      $\muconcr_{s}(\obj{\PHtarget(P)}{\PHtarget(Q)} \concat Q) \neq \emptyset$, thus
-      $\muconcr_{s}(P) \neq \emptyset$.
-    \item Else, by \pref{def:maxCont}, the concretizations of the children of $P$ require no process of sort $\PHsort(P)$.
-      Furthermore, there exists $\zeta \in \BS(P)$ so that $(P, \aZ) \in \Bsol$.
-      We build recursively a scenario $\delta$. Let $m = |\indexes{\zeta}|$.
-%      \todo{Idée avec les nouvelles defs : au rang 0, on se replace sur un processus de $\pfp$. Au rang n, il existe par saturation un objectif adéquat qui “reprend” la progression.}
-      \begin{itemize}
-%        \item[*] Let $\zeta_1 = \PHhit{b_i}{a_j}{a_k}$. By hypothesis, $\exists \delta_1 \in \muconcr_s(\PHobj{\any}{b_i}), \PHget{s \PHplay \delta_1}{a} \in \pfp_s(a)$.
-%          If $\PHget{s \PHplay \delta_1}{a} \neq a_j$, then by construction of $\cwB$, $(\PHobj{a_j}{a_k}, \PHobj{\PHget{s \PHplay \delta_1}{a}}{a_k}) \in \Bsat$.
-%          By hypothesis, $\muconcr_s(\PHobj{\any}{a_k}) \neq \emptyset$.
-%          If $\PHget{s \PHplay \delta_1}{a} = a_j$, then from \pref{th:vplay}, $\exists \delta'_1 \in \Sce$, $\zeta_1$ can be played in $s \PHplay \delta_1 \PHplay \delta'_1$.
-        \item[*] For $n \in \indexes{\zeta}$, let $s_n = s \PHplay \delta_1 \PHplay \delta'_1 \PHplay \delta''_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_{n-1} \PHplay \delta'_{n-1} \PHplay \delta''_{n-1} \PHplay \zeta_{n-1}$ (or $s_1 = s$),
-          and $\zeta_n = \PHhit{b_i}{a_j}{a_k}$.
-          By hypothesis, $\exists \delta_n \in \muconcr_{s_n}(\PHobj{\any}{b_i})$.
-          If $a \in \cs$, then $\prio(\zeta_n) = 1$ and $\zeta_n$ can be played in $s_n \PHplay \delta_n$ (\ie $\delta'_n = \delta''_n = \varepsilon$).
-          If $a \notin \cs$ and $b \in \cs$, then there exists a scenario $\delta'_n$ so that $b_i \in \pfp_{s_n \PHplay \delta_n \PHplay \delta'_n}(b)$ (because of the $\Bpriocont$ relation).
-          Then, by \pref{th:hcscomp}, there is a scenario $\delta'' \in \restriction{\Sce}{1}$ so that $\zeta_n$ is playable in $s_n \PHplay \delta_n \PHplay \delta'_n \PHplay \delta''_n$.
-          Finally, if $a,b \in \components$, then by \pref{th:hcompcomp}, there is a scenario $\delta'' \in \restriction{\Sce}{1}$ so that $\zeta_n$ is playable in $s_n \PHplay \delta_n \PHplay \delta''_n$ (\ie $\delta'_n = \varepsilon$).
-      \end{itemize}
-      Thus, $\delta = \delta_m \in \muconcr_s(P)$. % and $\ceil(\delta) \subseteq max\ctx$.
-  \end{itemize}
-\end{itemize}
-
-Finally, as $\muconcr_{max\ctx}(\w) \neq \emptyset$, $\uconcr(\w) \neq \emptyset$ (\pref{th:uconcr-ctx}).
-\end{proof}
-\end{comment}
-
-\begin{comment}
-Voisinage :
-\begin{equation*}
-\begin{split}
-    V: \wp(\PHproc) \times \segm{1}{k} &\rightarrow \wp(\PHh) \\
-    (ps; m) &\mapsto \sfp{\PHh^{(m)+}_{cibles}(ps)}{hs}{\PHh^{(m)+)}_{bonds}(\widehat{B}(hs)) \cup hs)}
-  \end{split}
-\end{equation*}
-where:
-\begin{equation*}
-\begin{split}
-    \widehat{B}: \wp(\PHh) &\rightarrow \wp(\PHproc) \\
-    hs &\mapsto \{ \PHhitter(h) \mid h \in hs \} \cup \{ \PHtarget(h) \mid h \in hs \}
-  \end{split}
-\end{equation*}
-\begin{equation*}
-\begin{split}
-    \PHh^{(m)+}_{\mathsf{ref}}: \wp(\PHproc) &\rightarrow \wp(\PHh) \quad,\quad m \in \segm{0}{k} \text{ and } \mathsf{ref} \in \{ \PHhitter, \PHtarget, \PHbounce \} \\
-    ps &\mapsto \{ h \in \PHh \mid \mathsf{ref}(h) \in ps \wedge \prio(h) \leq m \}
-  \end{split}
-\end{equation*}
-\end{comment}
 
@@
 \end{figure}
-
-\begin{comment}
-\begin{figure}
-  \centering
-  \begin{tikzpicture}[aS,node distance=1.5cm]
-    \node[Aproc] (c1) {$c_1$};
-    \node[Aobj,right of=c1] (c01) {$\PHobj{c_0}{c_1}$};
-    \node[Asol,right of=c01] (c01s) {};
-    \node[Aproc,right of=c01s] (b1) {$b_1$};
-    \node[Aobj,right of=b1] (b11) {$\PHobj{b_1}{b_1}$};
-    \node[Asol,right of=b11] (b11s) {};
-    \node[Aobj,below right of=b1] (b01) {$\PHobj{b_0}{b_1}$};
-    \node[Anos,right of=b01] (b01nos) {$\bottom$};
-
-    \path
-    (c1) edge (c01)
-    (c01) edge (c01s)
-    (c01s) edge (b1)
-    (b1) edge (b11) edge (b01)
-    (b11) edge (b11s)
-    ;
-  \end{tikzpicture}
-  \label{fig:sa-conca}
-  \caption{The local causality graph of the PH in \pref{fig:ph-conca}.}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \begin{tikzpicture}[aS,node distance=1.5cm]
-    \node[Aproc] (c2) {$c_2$};
-    \node[Aobj,right of=c2] (c12) {$\PHobj{c_1}{c_2}$};
-    \node[Asol,right of=c12] (c12s) {};
-    \node[Aproc,right of=c12s] (b1) {$b_1$};
-    \node[Aobj,right of=b1] (b01) {$\PHobj{b_0}{b_1}$};
-    \node[Asol,right of=b01] (b01s) {};
-    \node[Aproc,right of=b01s] (a1) {$a_1$};
-    \node[Aobj,right of=a1] (a11) {$\PHobj{a_1}{a_1}$};
-    \node[Asol,right of=a11] (a11s) {};
-
-    \node[Aobj,above right of=c2] (c22) {$\PHobj{c_2}{c_2}$};
-    \node[Asol,right of=c22] (c22s) {};
-    \node[Aobj,below right of=c2] (c02) {$\PHobj{c_0}{c_2}$};
-    \node[Anos,right of=c02] (c02nos) {$\bottom$};
-
-    \path
-    (c2) edge (c12) edge (c22) edge (c02)
-    (c22) edge (c22s)
-    (c12) edge (c12s)
-    (c12s) edge (b1)
-    (b1) edge (b01)
-    (b01) edge (b01s)
-    (b01s) edge (a1)
-    (a1) edge (a11)
-    (a11) edge (a11s)
-    ;
-  \end{tikzpicture}
-  \label{fig:sa-concb}
-  \caption{The local causality graph of the PH in \pref{fig:ph-concb}.}
-\end{figure}
-\end{comment}

### 2013-03-31 parts/def-ph.tex
start cleanup

@@
 \noindent
-The sort of a process $a_i$ is referred to as $\PHsort(a_i)=a$ and the set of sorts present in an action $h\in\PHa$ as $\PHsort(h) = \{\PHsort(\PHhitter(h)),\PHsort(\PHtarget(h))\}$.
-Given a state $s\in \PHl$, the process of sort $a\in\PHs$ present in $s$ is denoted by $\PHget{s}{a}$, that is the $a$-coordinate of the state $s$.
-If $a_i\in \PHl_a$, we define the notation $a_i\in s \EQDEF \PHget{s}{a}=a_i$.
-We define the semantics of actions in a Process Hitting model in \pref{def:play}.
-
+The sort of a process $a_i$ is referred to as $\PHsort(a_i) = a$.
+%and the set of sorts present in an action $h \in \PHa$ as $\PHsort(h) = \{\PHsort(\PHhitter(h)),\PHsort(\PHtarget(h))\}$.
+Given a state $s\in \PHl$, the process of sort $a \in \PHs$ present in $s$ is denoted by $\PHget{s}{a}$, that is the $a$-coordinate of the state $s$.
+If $a_i \in \PHl_a$, we define the notation $a_i \in s \EQDEF \PHget{s}{a} = a_i$.
+We define the override of a state by a process in \pref{def:statecap}, which allows to define the dynamics in a Process Hitting model (\pref{def:play}).
+\begin{definition}
+\label{def:statecap}
+  Given a state $s \in \PHl$ and a process $a_i \in \PHproc$, $(s \Cap a_i)$ is the state defined by:
+  $\PHget{(s \Cap a_i)}{a} = a_i \wedge \forall b \neq a, \PHget{(s \Cap a_i)}{b} = \PHget{s}{b}$.
+  We also extend this definition to a set of processes $ps$ given that all processes are from different sorts by the override of each process:
+  $\forall as \subset \PHs, \forall ps \in \underset{a \in as}{\times} \PHl_a, s \Cap ps = s \underset{a_i \in ps}{\Cap} a_i$.
+\end{definition}
 \begin{definition}
 \label{def:play}
-  An action $h = \PHhit{a_i}{b_j}{b_k} \in \PHa^{(n)}$ of priority $n$ is \emph{playable} in $s \in \PHl$ iff $\PHget{s}{a} = a_i$, $\PHget{s}{b} = b_j$ and $\forall m < n, \forall g \in \PHa^{(m)}, \PHhitter(g) \notin s \vee \PHtarget(g) \notin s$.
-  In such a case, $(s \PHplay h)$ stands for the state resulting from the play of the action $h$ in $s$, defined by: $\PHget{(s \PHplay h)}{b} = b_k$ and $\forall c\in\PHs, c\neq b, \PHget{(s\PHplay h)}{c} = \PHget{s}{c}$.
-  For the sake of clarity, for all $h, h'\in\PHa$, $((s\PHplay h)\PHplay h')$ is abbreviated as $(s\PHplay h\PHplay h')$.
+  An action $h = \PHhit{a_i}{b_j}{b_k} \in \PHa^{(n)}$ of priority $n$ is \emph{playable} in $s \in \PHl$
+  if and only if $\PHget{s}{a} = a_i$, $\PHget{s}{b} = b_j$ and $\forall m < n, \forall g \in \PHa^{(m)}, \PHhitter(g) \notin s \vee \PHtarget(g) \notin s$.
+  In such a case, $(s \PHplay h)$ stands for the state resulting from the play of the action $h$ in $s$, defined by: $(s \PHplay h) = s \Cap \PHbounce(h)$.
+%  For the sake of clarity, for all $h, h'\in\PHa$, $((s\PHplay h)\PHplay h')$ is abbreviated as $(s\PHplay h\PHplay h')$.
 \end{definition}
-
-\begin{definition}[Scenario ($\Sce$)]
-\label{def:scenario}
-  For a given Process Hitting model $(\PHs,\PHl,\PHh)$,
-  a \emph{scenario} $\delta$ is a sequence of actions of $\PHh$ so that for all $n \in \indexes{\delta}$,
-  $a_i = \PHhitter(\delta_n)$ (resp. $\PHtarget(\delta_n)$) $\Rightarrow \last_a(\delta_{1..n-1}) \in \{ \varnothing, a_i \}$.
-  The set of all scenarios is noted $\Sce$.
-\end{definition}
+%\begin{definition}[Scenario ($\Sce$)]
+%\label{def:scenario}
+  For a given state $s \in \PHl$,
+  a \emph{scenario} $\delta$ from $s$ is a sequence of actions of $\PHh$ that can be played successively in $s$.
+%  so that for all $n \in \indexes{\delta}$,
+%  $a_i = \PHhitter(\delta_n)$ (resp. $\PHtarget(\delta_n)$) $\Rightarrow \last_a(\delta_{1..n-1}) \in \{ \varnothing, a_i \}$.
+  The set of all scenarios from $s$ is noted $\Sce(s)$.
+%\end{definition}
 
@@
   $$\restriction{\PHa}{n} = (\PHa^{(1)}; \dots; \PHa^{(n)})$$
-  Furthermore, we denote: $\restriction{\Sce}{n}$ the set of scenarios of actions of $\restriction{\PHa}{n}$.
+  Furthermore, we denote: $\restriction{\Sce}{n}(s)$ the set of scenarios from $s$ made of actions of $\restriction{\PHa}{n}$.
 \end{definition}
@@
 
-\paragraph{2 priorities}
+\begin{criterion}[2 priorities]
+\label{cr:2prio}
+%\paragraph{2 priorities}
   In this paper, we only consider Process Hitting models with 2 priorities.
+\end{criterion}
 
-This restriction allows to models two kinds of actions: controllable actions that model the non-determinacy of biological evolutions,
+\pref{cr:2prio} allows to models two kinds of actions: controllable actions that model the non-determinacy of biological evolutions,
 and uncontrollable actions that are used to model non-biological behaviours in the model.
 
-In \pref{def:component} we define the notion of well-formed component.
-A sort $a$ is a well-formed component iff
-it is hit only by actions of priority $2$.
+In \pref{def:component} we define a well-formed component as a sort that is hit only by actions of priority $2$.
 \begin{definition}
 \label{def:component}
-  A sort $a \in \PHs$ is said to be a well-formed component iff:
-  \begin{itemize}
-    \item $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) = 2$
-  \end{itemize}
+  A sort $a \in \PHs$ is said to be a well-formed component if and only if:
+  $$\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) = 2 \enspace.$$
+  We call $\components$ the set of well-formed components.
 \end{definition}
-We call $\components$ the set of well-formed components.
 
@@
 \label{def:chainsactions}
-  We define the set of chains of actions $\PHh(b, a)$ between two sorts $b$ and $a$ as below:
+  The set of chains of actions $\PHh(b, a)$ between two sorts $b$ and $a$ is defined as below:
   \begin{align*}
@@
 
-\paragraph{Cycle-freeness between actions of priority $1$}
-There is no cycle in chains of actions: $\forall a \in \PHs, \PHh(a, a) = \emptyset$.
+\begin{criterion}[Cycle-freeness between actions of priority $1$]
+\label{cr:cyclefreeness}
+%\paragraph{Cycle-freeness between actions of priority $1$}
+  There is no cycle in chains of actions:
+  $$\forall a \in \PHs, \PHh(a, a) = \emptyset \enspace.$$
+\end{criterion}
 
-Given this first hypothesis, we define the neighbor \towrite{revoir terminologie : neighbors ? vicinity ?} sorts and actions (\pref{def:neighbors}).
-\begin{definition}
+Given \pref{cr:cyclefreeness}, we define the neighbour \towrite{revoir terminologie : neighbors ? vicinity ?} sorts and actions (\pref{def:neighbors}).
+\begin{definition}[Neighbour sorts ($\Vs$) and Neighbour actions ($\Vh$)]
 \label{def:neighbors}
@@
   $$\Vs(a) = \{ b \in \components \mid \PHh(b, a) \neq \emptyset \}$$
-  $$\Vh(a) = \{ h \in \PHh^{(1)} \mid \PHsort(\PHhitter(h)) \in \Vs(a) \wedge \PHsort(\PHtarget(h)) \in \Vs(a) \cup \{ a \} \}$$
+%  $$\Vh(a) = \{ h \in \PHh^{(1)} \mid \PHsort(\PHhitter(h)) \in \Vs(a) \wedge \PHsort(\PHtarget(h)) \in \Vs(a) \cup \{ a \} \}$$
+  $$\Vh(a) = \{ h \in \PHh^{(1)} \mid \exists b \in \Vs(a), \exists hs \in \PHh(b,a), h \in hs \}$$
 \end{definition}
 
-We denote $\pfp_s(a)$ the set of possible local steady-states of a sort $a$ from a state $s$.
-\todo{À corriger : état global ?}
+We denote $\pfp_s(a)$ the set of processes of sort $a$ that can be reached from state $s$ and that are local steady-states.
+%the set of possible local steady-states of a sort $a$ from a state $s$.
+%\todo{À corriger : état global ?}
+\begin{definition}[Local steady-state ($\pfp$)]
+\label{def:pfp}
+  For all $a \in \PHa$ and $s \in \PHl$,
   \begin{align*}
-  \pfp_s(a) = \{ a_i \in \PHl_a &\mid \exists \delta \in \restriction{\Sce}{1}, \PHget{(s \PHplay \delta)}{a} = a_i \\
+    \pfp_s(a) = \{ a_i \in \PHl_a &\mid \exists \delta \in \restriction{\Sce}{1}(s), \PHget{(s \PHplay \delta)}{a} = a_i \\
     & \quad \wedge \forall \PHhit{b_i}{c_j}{c_k} \in \Vh(a), \PHget{(s \PHplay \delta)}{b} \neq b_i \vee \PHget{(s \PHplay \delta)}{c} \neq c_j \}
   \end{align*}
-Of course, if $a \in \components$, then $\pfp_s(a) = \PHget{s}{a}$.
+  Of course, if $a \in \components$, then $\pfp_s(a) = \{ \PHget{s}{a} \}$.
+\end{definition}
 
-In \pref{def:cs} we define the notion of well-formed cooperative sort.
-A cooperative sort $a$ is well-formed iff
-it is hit only by actions of priority $1$,
+In \pref{def:cs} we define a well-formed cooperative sort as a sort that is only by actions of priority $1$ and so that
 any sub-state of its neighbourhood is represented by exactly one local steady state in this sort,
-and all of its processes represents at least one sub-state of its neighbourhood.
+and all of its processes represents at least one sub-state of its neighbourhood. \towrite{reformuler ou supprimer}
 \begin{definition}
@@
   A sort $a \in \PHs$ is said to be a well-formed cooperative sort iff:
-  \begin{itemize}
+  \begin{enumerate}
     \item $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) = 1$
-    \item $\forall s \in \underset{b \in \Vs(a)}{\times} \PHl_b, |\pfp_s(a)| = 1$
-    \item $\forall a_i \in \PHl_a, \exists s \in \underset{b \in \Vs(a)}{\times} \PHl_b, \pfp_s(a) = \{ a_i \}$
-  \end{itemize}
+%    \item $\forall s \in \underset{b \in \Vs(a)}{\times} \PHl_b, |\pfp_s(a)| = 1$
+%    \item $\forall a_i \in \PHl_a, \exists s \in \underset{b \in \Vs(a)}{\times} \PHl_b, \pfp_s(a) = \{ a_i \}$
+    \item \label{csai} $\forall s \in \PHl, |\pfp_s(a)| = 1$
+    \item \label{css} $\forall a_i \in \PHl_a, \exists s \in \PHl, \pfp_s(a) = \{ a_i \}$
+  \end{enumerate}
 \end{definition}
@@
 %We note that: $\forall a \in \components, \Vs(a) = \emptyset \wedge \Vh(a) = \emptyset$
-As any local state of neighbour sorts of a cooperative sort leads to a local steady-state, we denote $\csState(a_i)$ the set of sub-states represented by the process $a_i$ of the cooperative sort $a$.
-\begin{definition}[$\csState$]
+Because of (\ref{csai}), we denote in the following: $\pfp_s(a) = a_i$.
+Furthermore, because of (\ref{css}), we denote $\csState(a_i)$ the set of sub-states represented by the process $a_i$ of the cooperative sort $a$ (\pref{def:csState}).
+\begin{definition}[Represented sub-states ($\csState$)]
 \label{def:csState}
-  \towrite{À reformuler}
-  $$\csState(a_i) = \{ s \in \underset{b \in \Vs(a)}{\times} \PHl_b \mid \pfp_{s}(a) = a_i \}$$
+  $$\csState(a_i) = \{ ps \in \underset{b \in \Vs(a)}{\times} \PHl_b \mid \forall s \in \PHl, \pfp_{s \Cap ps}(a) = a_i \}$$
 \end{definition}
 
-\paragraph{Components \& cooperative sorts}
+\begin{criterion}[Components \& cooperative sorts]
+\label{cr:compcs}
+%\paragraph{Components \& cooperative sorts}
   The studied PH is a PH with 2 priorities, and it is only composed of well-formed components and cooperative sorts:
-$\components \cup \cs = \PHs \wedge \components \cap \cs = \emptyset$
+  $$\components \cup \cs = \PHs \wedge \components \cap \cs = \emptyset \enspace.$$
+\end{criterion}
 
-\paragraph{Bounded termination}
-The dynamics of model $\restriction{\PH}{1}$ contains no cycles. Cycles are still allowed in $\PH$ however.
-Formally : $\exists N \in \sN, \forall \delta \in \restriction{\Sce}{1}, |\indexes{\delta}| \leq N$.
+\begin{criterion}[Bounded termination]
+\label{cr:bounded}
+%\paragraph{Bounded termination}
+  The dynamics of model $\restriction{\PH}{1}$ contains no cycles:
+  %Cycles are still allowed in $\PH$ however.
+  %Formally :
+  $$\exists N \in \sN, \forall \delta \in \restriction{\Sce}{1}, |\indexes{\delta}| \leq N \enspace.$$
+\end{criterion}
 
 \subsection{Consequences of the restrictions}
-Given these hypotheses, we can denote: $\pfp_s(a) = a_i$ the local steady-state of $a$ in state $s$.
-Furthermore, we denote by $\update(s)$ the state in which all cooperative sorts are updated.
+%Given these hypotheses, we can denote: $\pfp_s(a) = a_i$ the local steady-state of $a$ in state $s$.
+We denote by $\update(s)$ the state in which all cooperative sorts are updated.
 \begin{align*}
-  \update(s) = s \underset{a \in CS}{\Cap } \pfp_{s}(a)
+  \update(s) = s \Cap \{ \pfp_{s}(a) \mid a \in CS \} \enspace.
 \end{align*}
-where for all process $a_i$, $s \Cap a_i$ is the state defined by:
-$\PHget{(s \Cap a_i)}{a} = a_i \wedge \forall b \neq a, \PHget{(s \Cap a_i)}{b} = \PHget{s}{b}$.
 
@@
 \label{th:update}
-  $\forall s \in \PHl, \exists \delta \in \restriction{\Sce}{1}, s \PHplay \delta = \update(s)$
+  $\forall s \in \PHl, \exists \delta \in \restriction{\Sce}{1}(s), s \PHplay \delta = \update(s)$
 \end{theorem}
@@
   $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, a,b \in \components,$\\
-  $(\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j) \Rightarrow (\exists \delta \in \restriction{\Sce}{1}, \text{$h$ can be played in $s \PHplay \delta$})$
+  $(\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j) \Rightarrow (\exists \delta \in \restriction{\Sce}{1}(s), \text{$h$ can be played in $s \PHplay \delta$})$
 \end{theorem}
@@
   $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, a \in \cs, b \in \components$\\
-  $(\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j \wedge \pfp_s(a) = a_i) \Rightarrow (\exists \delta \in \restriction{\Sce}{1}, \text{$h$ can be played in $s \PHplay \delta$})$
+  $(\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j \wedge \pfp_s(a) = a_i) \Rightarrow (\exists \delta \in \restriction{\Sce}{1}(s), \text{$h$ can be played in $s \PHplay \delta$})$
 \end{theorem}
@@
 
+\begin{comment}
 \pref{th:autohits} states that any sequence $\zeta$ of self-actions on a well-formed component can be played eventually.
@@
 \end{proof}
+\end{comment}

### 2013-03-31 parts/sa.tex
fix allProcs
start cleanup

@@
   The set of all objectives is called $\Obj = \{ \PHobj{a_i}{a_j} \mid a \in \PHs \wedge (a_i, a_j) \in \PHl_a^2 \}$.
-  For an objective $P \in \Obj$, where $P = \PHobj{a_i}{a_j}$, $\PHsort(P) = a$, $\PHtarget(P)=a_i$, $\PHbounce(P)=a_j$.
-  An objective $P$ is \emph{trivial} is $\PHtarget(P)=\PHbounce(P)$.
+  For an objective $P = \PHobj{a_i}{a_j} \in \Obj$, we define: $\PHsort(P) = a$, $\PHtarget(P)=a_i$, $\PHbounce(P)=a_j$,
+  and $P$ is \emph{trivial} if $a_i = a_j$.
 \end{definition}
+We define an \emph{objective sequence} as a sequence of objectives in which each target must be equal to the previous bounce of the same sort, if it exists.
+The set of all objective sequences is denoted by $\OS$.
 
@@
 
-For a given context $\ctx$, we note $a_i \in \ctx$ if and only if $a_i \in \PHget{\ctx}{a}$, and
-$ps \in \powerset(\Proc), ps \subseteq \ctx \Leftrightarrow \forall a_i \in ps, a_i \in \ctx$.
+For a given context $\ctx$, we note $a_i \in \ctx$ if and only if $a_i \in \PHget{\ctx}{a}$,
+and for all $ps \in \powerset(\Proc) \cup \PHl$, $ps \subseteq \ctx \EQDEF \forall a_i \in ps, a_i \in \ctx$.
 %The override of a context $\ctx$ by a set of processes $ps$ is noted $\ctx \Cap ps$ (\defref{ctxcap}).
 %Par exemple, $\state{a_1,a_2,b_1,c_1}\Cap\{ a_3, b_2, b_3 \} = \state{a_3,b_2,b_3,c_1}$.
+
 \begin{definition}[$\Cap: \Ctx \times \powerset(\PHproc) \mapsto \Ctx$]
@@
 
-A scenario $\delta \in \Sce$ is \emph{playable} in a context $\ctx$ if and only if $\supp(\delta) \subseteq \ctx$. 
-The play of $\delta$ in $\ctx$ is denoted $\ctx \PHplay \delta$ where $\ctx \PHplay \delta = \ctx \Cap \ceil(\delta)$.
+A sequence of actions $\delta$ is \emph{playable} in a context $\ctx$ if and only if 
+$\exists s \subseteq \ctx, \delta \in \Sce(s)$.
+We denote then: $\delta \in \Sce(\ctx)$,
+%$\supp(\delta) \subseteq \ctx$. 
+and the play of $\delta$ in $\ctx$ is $\ctx \PHplay \delta = \ctx \Cap \ceil(\delta)$,
+where $\ceil(\delta)$ is the set containing the last process (hitter or bounce) of each sort present in $\delta$.
 
+\begin{comment}
   \begin{definition}[Objective sequence ($\OS$)]
@@
   \end{definition}
+\end{comment}
 
@@
 
+We define $\concr(\w)$ as the set of scenarios concretising an objective sequence $\w$ in the context $\ctx$.
+In \pref{def:uconcr}, we define $\uconcr(\w)$ as equal to $\concr(\w)$ if it contains scenarios starting from all states $s \subseteq \ctx$.
+if such a scenario exists in all states $s \subseteq \ctx$.
+
+\begin{comment}
 \begin{definition}[$\concr: \OS \mapsto \powerset(\Sce)$]
@@
 \end{definition}
+\end{comment}
 
@@
   \begin{cases}
-    \concr(\w) & \text{if } \forall s \in \PHl, s \subseteq \ctx, \exists \delta \in \concr(\w), \supp(\delta) \subseteq s \\
+    \concr(\w) & \text{if } \forall s \in \PHl, s \subseteq \ctx, \exists \delta \in \concr(\w), \delta \in \Sce(s) \\
     \emptyset & \text{else.}
@@
 \label{th:uconcr-ctx}
-  $\ctx' \subseteq \ctx \wedge \uconcr(\w) \neq \emptyset \Longrightarrow \muconcr_{\ctx'}(\w) \neq \emptyset \enspace.$
+  $\ctx' \subseteq \ctx \wedge \uconcr(\w) \neq \emptyset \Longrightarrow \muconcr_{\ctx'}(\w) \neq \emptyset$.
 \end{theorem}
-% 
+
+\begin{comment}
 \begin{definition}[$\uconcr: \powerset(\OS) \mapsto \powerset(\Sce)$]
@@
   &\allprocs((\cwSol,\cwReq,\cwRSP,\cwCont)) = \{ p \in \PHproc \mid \exists (P,ps) \in \cwSol, \\
-    &\qquad\qquad p \in ps \vee p = \PHtarget(P) \vee p = \PHbounce(P) \} \\
+    &\qquad\qquad p \in ps \vee p = \PHtarget(P) \vee p = \PHbounce(P) \\
+    &\qquad\qquad \vee \exists (a_i,ps) \in \cwRSP, p \in ps \}
   %  &\qquad\qquad \vee p = \PHtarget(P) \vee \exists h \in \BS(P), (p = \PHhitter(h) \vee p = \PHbounce(h)) \\
@@
 \subsection{Abstract structure}
+
+\towrite{expliquer maxCont et le graphe de causalité}
 
@@
 \label{def:coherent}
-  A cooperative sort requisite $(a_i, ps)$ in $\myrsp$ is said coherent iff
-  it has no successor $(b_k,\PHobjp{b}{j}{k})$ in $\myreq$ so that there exists $b_n \in ps$, $b_k \neq b_n$.
+  A cooperative sort requisite $(a_i, ps)$ in $\Brsp$ is said coherent iff
+  it has no successor $(b_k,\PHobjp{b}{j}{k})$ in $\Breq$ so that there exists $b_n \in ps$, $b_k \neq b_n$.
 \end{definition}
 
-\begin{theorem}[Approximation inf.]
+\begin{theorem}[Under-Approximation]
 \label{th:approxinf}
@@
 \begin{itemize}
-  \item If $(P, \emptyset) \in \Bsol$, either $\PHtarget(P) = \PHbounce(P)$ and $\delta = \emptyseq$,
-    or $\forall \zeta \in \BS(P), \zeta \in \Sce \wedge \PHsort(\zeta) = \{ \PHsort(P) \}$ and $\delta$ is given by \pref{th:autohits}.
+  \item If $(P, \emptyset) \in \Bsol$, either $\PHtarget(P) = \PHbounce(P)$ and $\delta = \emptyseq$;
+    or $\forall \zeta \in \BS(P), \zeta \in \Sce(s) \wedge \PHsort(\zeta) = \{ \PHsort(P) \}$
+    and $\delta = \delta_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_{|\zeta|} \PHplay \zeta_{|\zeta|}$ is a sequence given by \pref{th:hcompcomp}.
 
@@
 
-\begin{figure}
+\begin{figure}[p]
   \centering

### 2013-03-31 parts/sa.tex
new graph definition

@@
 The set of all processes involved in an abstract structure $\cwB$ is given in \pref{def:allprocs}.
-\begin{definition}
+\begin{definition} \todo{À revoir avec la nouvelle sémantique}
 \label{def:allprocs}
@@
 
+\begin{comment}
+\begin{definition}
+  $\cwB = (\V, \E)$, $V \subset \PHproc \cup \Obj \cup \powerset(\PHproc)$ and $E \subset V \times V$
+  so that:\\
+  $\w \subset \V$\\
+  $\{ \PHbounce(P) \mid P \in \V \} \subset \V$\\
+  $\{ (P, ps) \in \Obj \times \powerset(\PHproc) \mid P \in \V \wedge ps \in \BS(P) \} \subset \E$\\ % Sol
+  $\{ ps \in \powerset(\PHproc) \mid (P, ps) \in \E \} \subset \V$\\
+  $\{ (ps, a_i) \in \powerset(\PHproc) \times \PHproc \mid a_i \in ps \} \subset \E$\\ % Sol
+  $\{ a_i \in \PHproc \mid (ps, a_i) \in \E \} \subset \V$\\
+  $\{ (a_i, \PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid a \in \components \wedge a_i \in \V \wedge a_j \in \ctx \} \subset \E$\\ % Req
+  $\{ \PHobjp{a}{j}{i} \in \Obj \mid (a_i, \PHobjp{a}{j}{i}) \in \E \} \subset \V$\\
+  $\{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid P \in \V \wedge q \in \gCont_\ctx(\PHsort(P), P) \} \subset \E$\\ % Cont
+  $\{ (a_i, ps) \in \Proc \times \powerset(\PHproc) \mid a \in \cs \wedge a_i \in \V \wedge ps \in \csState(a_i) \} \subset \E$\\ % ReqSolPrio
+\end{definition}
+
+\begin{definition}
+  $\cwB = (\V, \E)$, $V \subset \PHproc \cup \Obj \cup \powerset(\PHproc)$ and $E \subset V \times V$
+  so that:
+  \begin{align*}
+    \w &\subset \V\\
+    \{ \PHbounce(P) \mid P \in \V \} &\subset \V\\
+    \{ (P, ps) \in \Obj \times \powerset(\PHproc) \mid P \in \V \wedge ps \in \BS(P) \} &\subset \E\\ % Sol
+    \{ ps \in \powerset(\PHproc) \mid (P, ps) \in \E \} &\subset \V\\
+    \{ (ps, a_i) \in \powerset(\PHproc) \times \PHproc \mid a_i \in ps \} &\subset \E\\ % Sol
+    \{ a_i \in \PHproc \mid (ps, a_i) \in \E \} &\subset \V\\
+    \{ (a_i, \PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid a \in \components \wedge a_i \in \V \wedge a_j \in \ctx \} &\subset \E\\ % Req
+    \{ \PHobjp{a}{j}{i} \in \Obj \mid (a_i, \PHobjp{a}{j}{i}) \in \E \} &\subset \V\\
+    \{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid P \in \V \wedge q \in \gCont_\ctx(\PHsort(P), P) \} &\subset \E\\ % Cont
+    \{ (a_i, ps) \in \Proc \times \powerset(\PHproc) \mid a \in \cs \wedge a_i \in \V \wedge ps \in \csState(a_i) \} &\subset \E % ReqSolPrio
+  \end{align*}
+\end{definition}
+\end{comment}
+
+\newcommand{\V}{V}
+\newcommand{\E}{E}
+\newcommand{\cwV}{\V_\ctx^\w}
+\newcommand{\cwE}{\E_\ctx^\w}
+\newcommand{\VProc}{\V_\PHproc}
+\newcommand{\VObj}{\V_\Obj}
+\newcommand{\VSol}{\V_{Sol}}
+
+\def\Bv{\sat{\cwV}}
+\def\Be{\sat{\cwE}}
+
+\begin{definition}
+  The graph of local causality $\cwB = (\Bv, \Be)$ is defined as: $\cwB = \sfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs_\ctx(\myB)}}$,
+  where $\myB = (\cwV, \cwE)$ is the smallest graph where: $\cwV = \VProc \cup \VObj \cup \VSol$ with $\VProc \subset \PHproc$, $\VObj \subset \Obj$, $\VSol \subset \powerset(\PHproc)$ and $\cwE \subset \cwV \times \cwV$ so that:
+  \begin{align}
+    \w &\subset \cwV \label{eq:Vw} \\
+%      \{ \PHbounce(P) \mid P \in \VProc \} &\subset \V\\
+    P \in \VProc &\Rightarrow \PHbounce(P) \in \cwV \label{eq:Vproc} \\
+    (x, y) \in \E &\Rightarrow y \in \cwV \label{eq:VE} \\
+%    P \in \VObj &\Rightarrow \PHbounce(P) \in \V\\
+%      \{ (P, ps) \in \Obj \times \powerset(\PHproc) \mid P \in \V \wedge ps \in \BS(P) \} &\subset \E\\ % Sol
+    P \in \VObj \wedge ps \in \BS(P) &\Rightarrow (P, ps) \in \cwE \label{eq:ESol1} \\
+%    \{ ps \in \powerset(\PHproc) \mid (P, ps) \in \E \} &\subset \V\\
+%      \{ (ps, a_i) \in \powerset(\PHproc) \times \PHproc \mid a_i \in ps \} &\subset \E\\ % Sol
+    ps \in \VSol \wedge a_i \in ps &\Rightarrow (ps, a_i) \in \cwE \label{eq:ESol2} \\
+%    \{ a_i \in \PHproc \mid (ps, a_i) \in \E \} &\subset \V\\
+%      \{ (a_i, \PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid a \in \components \wedge a_i \in \V \wedge a_j \in \ctx \} &\subset \E\\ % Req
+    a \in \components \wedge a_i \in \VProc \wedge a_j \in \ctx &\Rightarrow (a_i, \PHobjp{a}{j}{i}) \in \cwE \label{eq:EReq} \\
+%    \{ \PHobjp{a}{j}{i} \in \Obj \mid (a_i, \PHobjp{a}{j}{i}) \in \E \} &\subset \V\\
+%      \{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid P \in \V \wedge q \in \gCont_\ctx(\PHsort(P), P) \} &\subset \E\\ % Cont
+    P \in \VObj \wedge q \in \gCont_\ctx(\PHsort(P), P) &\Rightarrow (P, \PHobj{q}{\PHbounce(P)}) \in \cwE \label{eq:ECont} \\
+%      \{ (a_i, ps) \in \Proc \times \powerset(\PHproc) \mid a \in \cs \wedge a_i \in \V \wedge ps \in \csState(a_i) \} &\subset \E\\ % ReqSolPrio
+    a \in \cs \wedge a_i \in \VProc \wedge ps \in \csState(a_i) &\Rightarrow (a_i, ps) \in \cwE \label{eq:EPrio}
+  \end{align}
+\end{definition}
+
+\pref{eq:Vw}, \eqref{eq:Vproc} and \eqref{eq:VE} ensure that all required nodes are in $\cwV$.
+\pref{eq:ESol1} links an objective $P$ to its solutions in $\BS(P)$,
+\pref{eq:ESol2} links a solution $ps$ to the processes $a_i \in ps$ it contains and
+\pref{eq:EReq} links a required process $a_i$ of a component to all objectives $\PHobjp{a}{j}{i}$ with $a_j \in \ctx$.
+If the resolution of an objective $P$ may require a process of $\PHsort(P)$, then \pref{eq:ECont} re-targets this objective ($\gCont$).
+Finally, \pref{eq:EPrio} links a required process $a_i$ of a cooperative sorts to its solutions in $\csState(a_i)$.
+
+\begin{comment}
 \begin{definition}
@@
 \end{definition}
+\end{comment}
+
+\begin{definition}[Coherent solution]
+\label{def:coherent}
+  An edge $(x, y) \in \cwE$ is said coherent if and only if
+  it does not belong to $(\PHproc \times \powerset(\PHproc))$
+  or if it does and $y$ has no process successor $a_j \in \Bv \cap \PHproc$ so that $\exists a_i \in y$, $a_i \neq a_k$.
+%  A set of processes $ps \in \Bv \cap \powerset(\PHproc)$ is said coherent if and only if
+%  it has no process successor $a_j \in \Bv \cap \PHproc$ so that there exists $a_i \in ps$, $a_i \neq a_k$.
+\end{definition}
 
@@
   all objectives have at least one solution
-  and all cooperative sort requisites are coherent,
+  and all edges are coherent,
+  %and $\forall (a_i, ps) \in \cwE \cap (\Proc \times \powerset(\PHproc))$, $ps$ is coherent,
+  %and all cooperative sort requisites are coherent,
   then $\uconcr(\w) \neq \emptyset$.

### 2013-03-31 parts/sa.tex
update demo

@@
 For a given context $\ctx$, we note $a_i \in \ctx$ if and only if $a_i \in \PHget{\ctx}{a}$,
-and for all $ps \in \powerset(\Proc) \cup \PHl$, $ps \subseteq \ctx \EQDEF \forall a_i \in ps, a_i \in \ctx$.
+and for all $ps \in \powerset(\PHproc) \cup \PHl$, $ps \subseteq \ctx \EQDEF \forall a_i \in ps, a_i \in \ctx$.
 %The override of a context $\ctx$ by a set of processes $ps$ is noted $\ctx \Cap ps$ (\defref{ctxcap}).
@@
 
-\begin{definition}[$\aBS:\Obj \mapsto \powerset(\Proc)$]
+In the following, we denote: $\Sol = \powerset(\PHproc)$.
+\begin{definition}[$\aBS:\Obj \mapsto \powerset(\Sol)$]
 \label{def:aBS}
   \[
-    \aBS(P) = \{ \abstr{\zeta} \mid \zeta \in \BS(P), \nexists \zeta' \in \BS(P), \abstr{\zeta'} \subsetneq \abstr{\zeta} \} \enspace,
+    \aBS(P) = \{ \abstr{\zeta} \in \Sol \mid \zeta \in \BS(P), \nexists \zeta' \in \BS(P), \abstr{\zeta'} \subsetneq \abstr{\zeta} \} \enspace,
   \]
@@
 
-\begin{definition}[$\gCont_\ctx : \Sigma \times \Obj \mapsto \powerset(\Proc)$]
+\begin{definition}[$\gCont_\ctx : \Sigma \times \Obj \mapsto \powerset(\PHproc)$]
   \label{def:maxCont}
@@
 \newcommand{\VObj}{\V_\Obj}
-\newcommand{\VSol}{\V_{Sol}}
+%\newcommand{\VSol}{\V_{Sol}}
+\newcommand{\VSol}{\V_{\Sol}}
 
@@
 \def\Be{\sat{\cwE}}
+\def\BvProc{\textcolor{red}{\sat{\cwV}^\PHproc}}
+\def\BvObj{\textcolor{red}{\sat{\cwV}^\Obj}}
+%\def\BvSol{\sat{\cwV}^{Sol}}
+\def\BvSol{\textcolor{red}{\sat{\cwV}^{\Sol}}}
+
+\newcommand{\Bee}[2]{\Be^{#1}_{#2}}
 
@@
   The graph of local causality $\cwB = (\Bv, \Be)$ is defined as: $\cwB = \sfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs_\ctx(\myB)}}$,
-  where $\myB = (\cwV, \cwE)$ is the smallest graph where: $\cwV = \VProc \cup \VObj \cup \VSol$ with $\VProc \subset \PHproc$, $\VObj \subset \Obj$, $\VSol \subset \powerset(\PHproc)$ and $\cwE \subset \cwV \times \cwV$ so that:
+  where $\myB = (\cwV, \cwE)$ is the smallest graph where: $\cwV = \VProc \cup \VObj \cup \VSol$ with $\VProc \subset \PHproc$, $\VObj \subset \Obj$, $\VSol \subset \Sol$ and $\cwE \subset \cwV \times \cwV$ so that:
   \begin{align}
@@
 \pref{eq:Vw}, \eqref{eq:Vproc} and \eqref{eq:VE} ensure that all required nodes are in $\cwV$.
+Elements in $\PHproc$ are required processes,
+elements in $\Obj$ are the objectives to reach these processes
+and elements in $\Sol$ are the sets of processes that are the solutions to these objectives.
 \pref{eq:ESol1} links an objective $P$ to its solutions in $\BS(P)$,
@@
 Finally, \pref{eq:EPrio} links a required process $a_i$ of a cooperative sorts to its solutions in $\csState(a_i)$.
+
+In the following, we denote:
+%$\BvProc = \Bv \cap \PHproc$, $\BvObj = \Bv \cap \Obj$ and $\BvSol = \Bv \cap \Sol$.
+$\Bee{X}{Y} = \Be \cap (X \times Y)$, with $X, Y$ amongst $\PHproc$, $\Obj$ and $\Sol$.
 
@@
   An edge $(x, y) \in \cwE$ is said coherent if and only if
-  it does not belong to $(\PHproc \times \powerset(\PHproc))$
-  or if it does and $y$ has no process successor $a_j \in \Bv \cap \PHproc$ so that $\exists a_i \in y$, $a_i \neq a_k$.
+  $(x, y) \in \Bee{\Proc}{\Sol} \Rightarrow y$ has no process successor $a_j \in \Bv \cap \Proc$ so that $\exists a_i \in y$, $a_i \neq a_k$.
 %  A set of processes $ps \in \Bv \cap \powerset(\PHproc)$ is said coherent if and only if
@@
 
-\begin{proof}
+\begin{proof} \towrite{Déplacer en annexe}
 We note $max\ctx = \ctx \Cap \allprocs(\cwB)$ the context supported by $\cwB$.
 
-Let $(a_i, ps) \in \Brsp$ be a cooperative sort requirement whom all children are concretizable.
+Let $(a_i, ps) \in \Bee{\Proc}{\Sol}$ be an edge linking the required process of a cooperative sort to a solution set and suppose all children of $ps$ are concretisable.
 We label all processes of $ps$ by an integer: $ps = \{ p_n \}_{n \in \indexes{ps}}$.
-Let us prove that for all $n \in \indexes{ps}$, there exists a scenario $\delta_n$ so that:
+Let us prove by induction that for all $n \in \indexes{ps}$, there exists a scenario $\delta_n$ so that:
 $\forall i \in \segm{1}{n}, \PHget{(s \PHplay \delta_n)}{\PHsort(p_i)} = p_i$.
@@
   \item It is straightforward for $\delta_0 = \varepsilon$.
-  \item Let us suppose such $\delta_n$ exists. \todo{Il faut être plus précis pour prendre en compte les coopérations en cascade}
-    By hypothesis, there exists $\delta' \in \muconcr_{s \PHplay \delta_n}(\PHobj{\any}{p_n})$.
-%    so that: $\PHget{(s \PHplay \delta_n \PHplay \delta')}{\PHsort(p_{n+1})} = p_{n+1}$.
-    By hypothesis, $(a_i, ps)$ is coherent (\pref{def:coherent}), which means that solving $p_{n+1}$ does not disturb the processes of $ps$.
-    Therefore, $\forall i \in \segm{1}{n+1}$, $\PHget{(s \PHplay \delta_n \PHplay \delta')}{\PHsort(p_{i})} = p_{i}$.
-    Finally, by \pref{th:update}, there exists a scenario $\delta'' \in \restriction{\Sce}{1}$
-    that can be played in $s \PHplay \delta_n \PHplay \delta'$
-    and so that, if we denote $\delta_{n+1} = \delta_n \PHplay \delta' \PHplay \delta''$,
+  \item Suppose such $\delta_n$ exists and let $q = \PHget{(s \PHplay \delta_n)}{\PHsort(p_{n+1})}$.
+    By hypothesis, $(a_i, ps)$ is coherent (\pref{def:coherent}) and all processes of $ps$ are processes of components;
+    this means that none of the processes needed to solve $p_{n+1}$ is another process of the same sort than another process of $ps$.
+    Therefore, there exists $\delta' \in \muconcr_{s \PHplay \delta_n}(\PHobj{q}{p_{n+1}})$,
+    so that $\forall i \in \segm{1}{n+1}$, $\PHget{(s \PHplay \delta_n \PHplay \delta')}{\PHsort(p_{i})} = p_{i}$.
+    Finally, by \pref{th:update}, there exists a scenario $\delta'' \in \restriction{\Sce}{1}(s \PHplay \delta_n \PHplay \delta')$
+    so that, if we denote $\delta_{n+1} = \delta_n \PHplay \delta' \PHplay \delta''$,
     we have: $\update(s \PHplay \delta_n \PHplay \delta') = s \PHplay \delta_{n+1}$ and the same property about processes (by \pref{th:hcscomp}).
 \end{itemize}
-Therefore, $\delta = \delta_{\indexes{ps}}$ exists, and given its properties, we have: $\PHget{(s \PHplay \delta)}{a} = a_i$
+Therefore, $\delta = \delta_{|ps|}$ exists, and given its properties, we have: $\PHget{(s \PHplay \delta)}{a} = a_i$
 and $\update(s \PHplay \delta) = s \PHplay \delta$.
@@
 As there is no cycle in $\cwB$, we show by induction that $\forall s\in L, s\subseteq max\ctx$, 
-for all objective $P$ in $\cwB$ so that $\PHtarget(P) \in s$,
+for all objective $P$ in $\Bv \cap \Obj$ so that $\PHtarget(P) \in s$,
 $\exists \delta \in \muconcr_s(P)$.% and $\ceil(\delta) \subseteq max\ctx$.
-
 \begin{itemize}
-  \item If $(P, \emptyset) \in \Bsol$, either $\PHtarget(P) = \PHbounce(P)$ and $\delta = \emptyseq$;
+  \item If $(P, \emptyset) \in \Bee{\Obj}{\Sol}$, either $\PHtarget(P) = \PHbounce(P)$ and $\delta = \emptyseq$;
     or $\forall \zeta \in \BS(P), \zeta \in \Sce(s) \wedge \PHsort(\zeta) = \{ \PHsort(P) \}$
-    and $\delta = \delta_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_{|\zeta|} \PHplay \zeta_{|\zeta|}$ is a sequence given by \pref{th:hcompcomp}.
+    and $\delta = \delta_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_{|\zeta|} \PHplay \zeta_{|\zeta|}$ is a valid sequence given by \pref{th:hcompcomp}.
 
   \item Suppose all children objectives of $P$ are concretizable.
-  \begin{itemize}
-    \item If $\exists (P, Q) \in \Bcont$, then by hypothesis,
+%  \begin{itemize}
+    %\item 
+    If $\exists (P, Q) \in \Bee{\Obj}{\Obj}$, then by hypothesis,
       $\muconcr_{s}(\obj{\PHtarget(P)}{\PHtarget(Q)} \concat Q) \neq \emptyset$, thus
       $\muconcr_{s}(P) \neq \emptyset$.
-    \item Else, by \pref{def:maxCont}, the concretizations of the children of $P$ require no process of sort $\PHsort(P)$.
-      Furthermore, there exists $\zeta \in \BS(P)$ so that $(P, \aZ) \in \Bsol$.
+    %\item 
+    Else, by \pref{def:maxCont}, the concretizations of the children of $P$ require no process of sort $\PHsort(P)$.
+      Furthermore, there exists $\zeta \in \BS(P)$ so that $(P, \aZ) \in \Bee{\Obj}{\Sol}$.
       We show by induction that for all $n \in \indexes{\zeta}$, there is a scenario $\delta_n$ so that $\PHget{(s \PHplay \delta_n)}{\PHsort(P)} = \PHbounce(\zeta_n)$.
-%      We build recursively a scenario $\delta$. Let $m = |\indexes{\zeta}|$.
       \begin{itemize}
         \item[*] Suppose that $\delta_n$ exists and let $\zeta_n = \PHhit{b_i}{a_j}{a_k}$.
-        By hypothesis there exists $\delta' \in \muconcr_{s \PHplay \delta_n}(\PHobj{\any}{b_i})$ with $\PHsort(P) \notin \PHsort(\delta')$ by \pref{def:maxCont}.
-        By \pref{th:update} there exists $\delta'' \in \restriction{\Sce}{1}$ so that $\update(s \PHplay \delta') = s \PHplay \delta' \PHplay \delta''$.
+        By hypothesis there exists $\delta' \in \muconcr_{s \PHplay \delta_n}(\PHobj{\any}{b_i})$ with $\PHsort(P) \notin \PHsort(\delta')$ (by \pref{def:maxCont}).
+        By \pref{th:update} there exists $\delta'' \in \restriction{\Sce}{1}(s \PHplay \delta')$ so that $\update(s \PHplay \delta') = s \PHplay \delta' \PHplay \delta''$.
         Furthermore, $\PHget{(s \PHplay \delta' \PHplay \delta'')}{b} = b_j$ (by \pref{th:hcompcomp} if $b \in \components$ or \pref{th:hcscomp} if $b \in \cs$).
@@
       \end{itemize}
-      Thus, $\delta_{\indexes{\zeta}} \in \muconcr_s(P)$. % and $\ceil(\delta) \subseteq max\ctx$.
-  \end{itemize}
+      Thus, $\delta_{|\zeta|} \in \muconcr_s(P)$. % and $\ceil(\delta) \subseteq max\ctx$.
+%  \end{itemize}
 \end{itemize}

### 2013-03-31 parts/appendix.tex
create appendix

\appendix

%\section{Demonstration of \pref{th:approxinf}}

\section{Demonstration of \towrite{équivalence PHP / réseaux discrets}}

\todo{Preuve}

### 2013-03-31 parts/appendix.tex
move demo to appendix

@@
 
+\begin{proof} \towrite{Déplacer en annexe}
+We note $max\ctx = \ctx \Cap \allprocs(\cwB)$ the context supported by $\cwB$.
+
+Let $(a_i, ps) \in \Bee{\Proc}{\Sol}$ be an edge linking the required process of a cooperative sort to a solution set and suppose all children of $ps$ are concretisable.
+We label all processes of $ps$ by an integer: $ps = \{ p_n \}_{n \in \indexes{ps}}$.
+Let us prove by induction that for all $n \in \indexes{ps}$, there exists a scenario $\delta_n$ so that:
+$\forall i \in \segm{1}{n}, \PHget{(s \PHplay \delta_n)}{\PHsort(p_i)} = p_i$.
+\begin{itemize}
+  \item It is straightforward for $\delta_0 = \varepsilon$.
+  \item Suppose such $\delta_n$ exists and let $q = \PHget{(s \PHplay \delta_n)}{\PHsort(p_{n+1})}$.
+    By hypothesis, $(a_i, ps)$ is coherent (\pref{def:coherent}) and all processes of $ps$ are processes of components;
+    this means that none of the processes needed to solve $p_{n+1}$ is another process of the same sort than another process of $ps$.
+    Therefore, there exists $\delta' \in \muconcr_{s \PHplay \delta_n}(\PHobj{q}{p_{n+1}})$,
+    so that $\forall i \in \segm{1}{n+1}$, $\PHget{(s \PHplay \delta_n \PHplay \delta')}{\PHsort(p_{i})} = p_{i}$.
+    Finally, by \pref{th:update}, there exists a scenario $\delta'' \in \restriction{\Sce}{1}(s \PHplay \delta_n \PHplay \delta')$
+    so that, if we denote $\delta_{n+1} = \delta_n \PHplay \delta' \PHplay \delta''$,
+    we have: $\update(s \PHplay \delta_n \PHplay \delta') = s \PHplay \delta_{n+1}$ and the same property about processes (by \pref{th:hcscomp}).
+\end{itemize}
+Therefore, $\delta = \delta_{|ps|}$ exists, and given its properties, we have: $\PHget{(s \PHplay \delta)}{a} = a_i$
+and $\update(s \PHplay \delta) = s \PHplay \delta$.
+
+As there is no cycle in $\cwB$, we show by induction that $\forall s\in L, s\subseteq max\ctx$, 
+for all objective $P$ in $\Bv \cap \Obj$ so that $\PHtarget(P) \in s$,
+$\exists \delta \in \muconcr_s(P)$.% and $\ceil(\delta) \subseteq max\ctx$.
+\begin{itemize}
+  \item If $(P, \emptyset) \in \Bee{\Obj}{\Sol}$, either $\PHtarget(P) = \PHbounce(P)$ and $\delta = \emptyseq$;
+    or $\forall \zeta \in \BS(P), \zeta \in \Sce(s) \wedge \PHsort(\zeta) = \{ \PHsort(P) \}$
+    and $\delta = \delta_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_{|\zeta|} \PHplay \zeta_{|\zeta|}$ is a valid sequence given by \pref{th:hcompcomp}.
+
+  \item Suppose all children objectives of $P$ are concretizable.
+%  \begin{itemize}
+    %\item 
+    If $\exists (P, Q) \in \Bee{\Obj}{\Obj}$, then by hypothesis,
+      $\muconcr_{s}(\obj{\PHtarget(P)}{\PHtarget(Q)} \concat Q) \neq \emptyset$, thus
+      $\muconcr_{s}(P) \neq \emptyset$.
+    %\item 
+    Else, by \pref{def:maxCont}, the concretizations of the children of $P$ require no process of sort $\PHsort(P)$.
+      Furthermore, there exists $\zeta \in \BS(P)$ so that $(P, \aZ) \in \Bee{\Obj}{\Sol}$.
+      We show by induction that for all $n \in \indexes{\zeta}$, there is a scenario $\delta_n$ so that $\PHget{(s \PHplay \delta_n)}{\PHsort(P)} = \PHbounce(\zeta_n)$.
+      \begin{itemize}
+        \item[*] Suppose that $\delta_n$ exists and let $\zeta_n = \PHhit{b_i}{a_j}{a_k}$.
+        By hypothesis there exists $\delta' \in \muconcr_{s \PHplay \delta_n}(\PHobj{\any}{b_i})$ with $\PHsort(P) \notin \PHsort(\delta')$ (by \pref{def:maxCont}).
+        By \pref{th:update} there exists $\delta'' \in \restriction{\Sce}{1}(s \PHplay \delta')$ so that $\update(s \PHplay \delta') = s \PHplay \delta' \PHplay \delta''$.
+        Furthermore, $\PHget{(s \PHplay \delta' \PHplay \delta'')}{b} = b_j$ (by \pref{th:hcompcomp} if $b \in \components$ or \pref{th:hcscomp} if $b \in \cs$).
+        Therefore, $\delta_{n+1} = \delta_n \PHplay \delta' \PHplay \delta'' \PHplay \zeta_n$.
+      \end{itemize}
+      Thus, $\delta_{|\zeta|} \in \muconcr_s(P)$. % and $\ceil(\delta) \subseteq max\ctx$.
+%  \end{itemize}
+\end{itemize}
+Finally, as $\muconcr_{max\ctx}(\w) \neq \emptyset$, $\uconcr(\w) \neq \emptyset$ (\pref{th:uconcr-ctx}).
+\end{proof}
+
 \section{Demonstration of \towrite{équivalence PHP / réseaux discrets}}

### 2013-03-31 parts/sa.tex
move demo to appendix

@@
 
-\begin{proof} \towrite{Déplacer en annexe}
-We note $max\ctx = \ctx \Cap \allprocs(\cwB)$ the context supported by $\cwB$.
-
-Let $(a_i, ps) \in \Bee{\Proc}{\Sol}$ be an edge linking the required process of a cooperative sort to a solution set and suppose all children of $ps$ are concretisable.
-We label all processes of $ps$ by an integer: $ps = \{ p_n \}_{n \in \indexes{ps}}$.
-Let us prove by induction that for all $n \in \indexes{ps}$, there exists a scenario $\delta_n$ so that:
-$\forall i \in \segm{1}{n}, \PHget{(s \PHplay \delta_n)}{\PHsort(p_i)} = p_i$.
-\begin{itemize}
-  \item It is straightforward for $\delta_0 = \varepsilon$.
-  \item Suppose such $\delta_n$ exists and let $q = \PHget{(s \PHplay \delta_n)}{\PHsort(p_{n+1})}$.
-    By hypothesis, $(a_i, ps)$ is coherent (\pref{def:coherent}) and all processes of $ps$ are processes of components;
-    this means that none of the processes needed to solve $p_{n+1}$ is another process of the same sort than another process of $ps$.
-    Therefore, there exists $\delta' \in \muconcr_{s \PHplay \delta_n}(\PHobj{q}{p_{n+1}})$,
-    so that $\forall i \in \segm{1}{n+1}$, $\PHget{(s \PHplay \delta_n \PHplay \delta')}{\PHsort(p_{i})} = p_{i}$.
-    Finally, by \pref{th:update}, there exists a scenario $\delta'' \in \restriction{\Sce}{1}(s \PHplay \delta_n \PHplay \delta')$
-    so that, if we denote $\delta_{n+1} = \delta_n \PHplay \delta' \PHplay \delta''$,
-    we have: $\update(s \PHplay \delta_n \PHplay \delta') = s \PHplay \delta_{n+1}$ and the same property about processes (by \pref{th:hcscomp}).
-\end{itemize}
-Therefore, $\delta = \delta_{|ps|}$ exists, and given its properties, we have: $\PHget{(s \PHplay \delta)}{a} = a_i$
-and $\update(s \PHplay \delta) = s \PHplay \delta$.
-
-As there is no cycle in $\cwB$, we show by induction that $\forall s\in L, s\subseteq max\ctx$, 
-for all objective $P$ in $\Bv \cap \Obj$ so that $\PHtarget(P) \in s$,
-$\exists \delta \in \muconcr_s(P)$.% and $\ceil(\delta) \subseteq max\ctx$.
-\begin{itemize}
-  \item If $(P, \emptyset) \in \Bee{\Obj}{\Sol}$, either $\PHtarget(P) = \PHbounce(P)$ and $\delta = \emptyseq$;
-    or $\forall \zeta \in \BS(P), \zeta \in \Sce(s) \wedge \PHsort(\zeta) = \{ \PHsort(P) \}$
-    and $\delta = \delta_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_{|\zeta|} \PHplay \zeta_{|\zeta|}$ is a valid sequence given by \pref{th:hcompcomp}.
-
-  \item Suppose all children objectives of $P$ are concretizable.
-%  \begin{itemize}
-    %\item 
-    If $\exists (P, Q) \in \Bee{\Obj}{\Obj}$, then by hypothesis,
-      $\muconcr_{s}(\obj{\PHtarget(P)}{\PHtarget(Q)} \concat Q) \neq \emptyset$, thus
-      $\muconcr_{s}(P) \neq \emptyset$.
-    %\item 
-    Else, by \pref{def:maxCont}, the concretizations of the children of $P$ require no process of sort $\PHsort(P)$.
-      Furthermore, there exists $\zeta \in \BS(P)$ so that $(P, \aZ) \in \Bee{\Obj}{\Sol}$.
-      We show by induction that for all $n \in \indexes{\zeta}$, there is a scenario $\delta_n$ so that $\PHget{(s \PHplay \delta_n)}{\PHsort(P)} = \PHbounce(\zeta_n)$.
-      \begin{itemize}
-        \item[*] Suppose that $\delta_n$ exists and let $\zeta_n = \PHhit{b_i}{a_j}{a_k}$.
-        By hypothesis there exists $\delta' \in \muconcr_{s \PHplay \delta_n}(\PHobj{\any}{b_i})$ with $\PHsort(P) \notin \PHsort(\delta')$ (by \pref{def:maxCont}).
-        By \pref{th:update} there exists $\delta'' \in \restriction{\Sce}{1}(s \PHplay \delta')$ so that $\update(s \PHplay \delta') = s \PHplay \delta' \PHplay \delta''$.
-        Furthermore, $\PHget{(s \PHplay \delta' \PHplay \delta'')}{b} = b_j$ (by \pref{th:hcompcomp} if $b \in \components$ or \pref{th:hcscomp} if $b \in \cs$).
-        Therefore, $\delta_{n+1} = \delta_n \PHplay \delta' \PHplay \delta'' \PHplay \zeta_n$.
-      \end{itemize}
-      Thus, $\delta_{|\zeta|} \in \muconcr_s(P)$. % and $\ceil(\delta) \subseteq max\ctx$.
-%  \end{itemize}
-\end{itemize}
-Finally, as $\muconcr_{max\ctx}(\w) \neq \emptyset$, $\uconcr(\w) \neq \emptyset$ (\pref{th:uconcr-ctx}).
-\end{proof}
-
 \begin{figure}[p]

### 2013-03-31 parts/sa.tex
update example

@@
   \centering
-  \begin{tikzpicture}[aS,node distance=1.5cm]
+  \begin{tikzpicture}[aS]
     \node[Aproc] (c1) {$c_1$};
@@
     \node[Aproc,below of=c01s] (ab11) {$ab_{11}$};
-    \node[Aobj,below right of=ab11] (ab0111) {$\PHobj{ab_{01}}{ab_{11}}$};
-    \node[Asol,below of=ab0111] (ab0111s) {};
-    \node[Aobj,below of=ab11,node distance=2.5cm] (ab0011) {$\PHobj{ab_{00}}{ab_{11}}$};
-    \node[Asol,below of=ab0011] (ab0011s) {};
-    \node[Aobj,below left of=ab11] (ab1011) {$\PHobj{ab_{10}}{ab_{11}}$};
-    \node[Asol,below of=ab1011] (ab1011s) {};
+    \node[AsolPrio,below of=ab11] (ab11s) {};
 
-    \node[Aproc,below of=ab0111s] (a1) {$a_1$};
+    \node[Aproc,below left of=ab11s] (a1) {$a_1$};
     \node[Aobj,below of=a1] (a11) {$\PHobj{a_1}{a_1}$};
     \node[Asol,below of=a11] (a11s) {};
-    \node[Aobj,below right of=a1] (a01) {$\PHobj{a_0}{a_1}$};
+    \node[Aobj,below left of=a1] (a01) {$\PHobj{a_0}{a_1}$};
     \node[Asol,below of=a01] (a01s) {};
@@
     \node[Asol,below of=b00] (b00s) {};
-    \node[Aobj,below right of=b0] (b10) {$\PHobj{b_1}{b_0}$};
+    \node[Aobj,below left of=b0] (b10) {$\PHobj{b_1}{b_0}$};
     \node[Asol,below of=b10] (b10s) {};
 
-    \node[Aproc,below of=ab1011s] (b1) {$b_1$};
-    \node[Aobj,below of=b1] (b01) {$\PHobj{b_0}{b_1}$};
+    \node[Aproc,below right of=ab11s] (b1) {$b_1$};
+    \node[Aobj,below of=b1] (b11) {$\PHobj{b_1}{b_1}$};
+    \node[Asol,below of=b11] (b11s) {};
+    \node[Aobj,below right of=b1] (b01) {$\PHobj{b_0}{b_1}$};
     \node[Asol,below of=b01] (b01s) {};
     \node[Aproc,below of=b01s] (a0) {$a_0$};
-    \node[Aobj,below of=a0] (a10) {$\PHobj{a_1}{a_0}$};
+    \node[Aobj,below of=a0] (a00) {$\PHobj{a_0}{a_0}$};
+    \node[Asol,below of=a00] (a00s) {};
+    \node[Aobj,below right of=a0] (a10) {$\PHobj{a_1}{a_0}$};
     \node[Asol,below of=a10] (a10s) {};
@@
     (c01s) edge (ab11)
-    (ab11) edge (ab0011) edge (ab0111) edge (ab1011)
-    (ab0011) edge (ab0011s)
-    (ab1011) edge (ab1011s)
-    (ab0111) edge (ab0111s)
-
-    (ab0011s) edge (a1) edge (b1)
-    (ab1011s) edge (b1)
-    (ab0111s) edge (a1)
+    (ab11) edge (ab11s)
+    (ab11s) edge (a1) edge (b1)
 
@@
     (a11) edge (a11s)
-    (a0) edge (a10)
+    (a0) edge (a10) edge (a00)
     (a10) edge (a10s)
+    (a00) edge (a00s)
 
@@
     (b00) edge (b00s)
-    (b1) edge (b01)
+    (b1) edge (b01) edge (b11)
     (b01) edge (b01s)
     (b01s) edge (a0)
-    ;
-    \path
-    (ab0011) edge[double] (ab0111)
-    (ab0011) edge[double,bend right=10] (ab1011)
-    (ab1011) edge[double,bend right=10] (ab0011)
-    (ab0111) edge[double,bend right=10] (ab1011)
-    (ab1011) edge[double,bend right=10] (ab0111)
+    (b11) edge (b11s)
     ;
@@
   \label{fig:sa-livelock}
-  \caption{The local causality graph of the PH in \pref{fig:ph-livelock}.}
+  \caption{
+    The graph of local causality of the PH model in \pref{fig:ph-livelock}.
+    \pref{th:approxinf} is inconclusive on this example as the only solution of process $ab_{11}$ is not coherent (\pref{def:coherent}).
+  }
 \end{figure}

### 2013-03-31 parts/ccl.tex
conclusion

@@
 }
+
+In this paper we introduced a new semantics to include priorities into the Process Hitting framework, which are especially useful to model cooperations.
+Then, we developed a method to efficiently perform a reachability analysis of a sequence of processes on a restricted class of Process Hitting models.
+This analysis is based on an under-approximation of the true reachability solutions; however, the most usual cases can be handled.
+Furthermore, our method can also be used to determine the reachability of a set of states of a model.
+The method has been implemented as an extension of the existing “ph-reach” tool into the existing Pint\footnote{\url{http://processhitting.wordpress.com/}} library.
+
+Finally, we showed that the class of Process Hitting models that can be handled by the aforementioned method are equivalent to discrete networks, which include boolean networks.
+This allows to efficiently compute reachability results on large biological models provided that they are equivalent to discrete networks and that a translation from the original framework into a Process Hitting model is possible.
+Such a translation for interaction graphs of Thomas modelling was proposed in~\cite{PMR10-TCSB} and is made possible by the Pint software.
+
+Further work can be derived from what have been presented in this paper.
+An over-approximation on Process Hitting models without priorities was proposed in~\cite{PMR12-MSCS}.
+Although it is still accurate on the Process Hitting framework with priorities (by “flattening” all actions),
+it turns out to be too wide even in some obvious cases that are consequently not conclusive.
+This over-approximation may be refined in order to better fit the introduction of priorities, and mode precisely the class of models studied in this paper.
+Furthermore, a more general under-approximation could be developed in order to handle a larger class of Process Hitting models, that is,
+models with more than two classes of priorities, that do not only contain components of cooperative sorts or whose behaviour may contain cycles or cyclic attractors.
+Finally, in order to take into account quantitative data on transition delays, the overall approximation method could be extended to handle evolution that are chronometric instead of only chronologic.

### 2013-03-31 parts/sa.tex
conclusion
example

@@
 
+\begin{example}
+  As an example showing the usefulness of our method, we can consider \pref{fig:ph-livelock}.
+  Let $\PH' = (\PHs, \PHl, \PHh'^{\langle 1 \rangle})$ be the “flattened” version of $\PH$, that is: $\PHh'^{\langle 1 \rangle} = \PHh^{(1)} \cup \PHh^{(2)}$.
+  As this PH model contains only $1$ priority, it is equivalent to a PH in the semantics without priorities.
+  The under-approximation on this class of models developed in~\cite{PMR12-MSCS} concludes that $c_1$ is reachable.
+  This is due to the “temporal shift” inherent to cooperative sorts in the semantics without priorities.
+
+  This is an unwanted behaviour that the semantics of PH with priorities proposed in this paper allows to avoid.
+  Indeed, the under-approximation given in \pref{th:approxinf} does not conclude as one of the edges of the resulting graph of local causality is not coherent (\pref{def:coherent}).
+  The graph of local causality for this example is given in \pref{fig:sa-livelock}.
+\end{example}
+
 \begin{figure}[p]
@@
     \end{tikzpicture}
+  \caption{
   \label{fig:sa-livelock}
-  \caption{
     The graph of local causality of the PH model in \pref{fig:ph-livelock}.
@@
 \end{figure}
+
+\todo{La méthode permet aussi de conclure sur l'accessilibité d'un état (global ou partiel)}

### 2013-03-31 parts/sa.tex
update procs

@@
 The set of all processes involved in an abstract structure $\cwB$ is given in \pref{def:allprocs}.
+\towrite{pré-définir la structure abstraite}
+\begin{definition}
+\label{def:allprocs}
+  \begin{align*}
+  \allprocs(\V, \E) = \{ p \in \PHproc &\mid p \in \V \vee \exists P \in \V \cap \Obj,\\
+  &\qquad p = \PHtarget(P) \vee p = \PHbounce(P) \}
+%    &\qquad\qquad p \in ps \vee p = \PHtarget(P) \vee p = \PHbounce(P) \\
+%    &\qquad\qquad \vee \exists (a_i,ps) \in \cwRSP, p \in ps \}
+  \end{align*}
+\end{definition}
+
+\begin{comment}
 \begin{definition} \todo{À revoir avec la nouvelle sémantique}
@@
 
-\newcommand{\V}{V}
-\newcommand{\E}{E}
-\newcommand{\cwV}{\V_\ctx^\w}
-\newcommand{\cwE}{\E_\ctx^\w}
-\newcommand{\VProc}{\V_\PHproc}
-\newcommand{\VObj}{\V_\Obj}
-%\newcommand{\VSol}{\V_{Sol}}
-\newcommand{\VSol}{\V_{\Sol}}
-
-\def\Bv{\sat{\cwV}}
-\def\Be{\sat{\cwE}}
-\def\BvProc{\textcolor{red}{\sat{\cwV}^\PHproc}}
-\def\BvObj{\textcolor{red}{\sat{\cwV}^\Obj}}
-%\def\BvSol{\sat{\cwV}^{Sol}}
-\def\BvSol{\textcolor{red}{\sat{\cwV}^{\Sol}}}
-
-\newcommand{\Bee}[2]{\Be^{#1}_{#2}}
-
 \begin{definition}
-  The graph of local causality $\cwB = (\Bv, \Be)$ is defined as: $\cwB = \sfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs_\ctx(\myB)}}$,
+  The graph of local causality $\cwB = (\Bv, \Be)$ is defined as: $\cwB = \sfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs(\myB)}}$,
   where $\myB = (\cwV, \cwE)$ is the smallest graph where: $\cwV = \VProc \cup \VObj \cup \VSol$ with $\VProc \subset \PHproc$, $\VObj \subset \Obj$, $\VSol \subset \Sol$ and $\cwE \subset \cwV \times \cwV$ so that:

### 2013-04-01 parts/def-ph.tex
example
read-through sections 2.1 & 2.2

@@
 
-\towrite{Transition.}
+We give in this section the definition and the semantics of the Process Hitting (PH) with priorities, which is an extension of the basic semantics given in~\cite{PMR10-TCSB}.
+Then we describe the modelling of cooperation between components and discuss how the new aforementioned semantics makes this modelling more accurate.
+\towrite{Démo équivalence avec réseaux discret : ici ou dans la section 3 ?}
+Finally, in order to perform a static analysis on this new semantics, we give several criteria to restrict the class of models that we can study,
+and give several theorems that follow.
 
@@
 \towrite{Reformuler (actuellement trop proche de CMSB)}
-A PH (\pref{def:ph}) gathers a finite number of concurrent \emph{processes} grouped into a finite set of \emph{sorts}.
+A PH with $k$ priorities (\pref{def:ph}), also simply called PH \towrite{abréviation ?} in the following, gathers a finite number of concurrent \emph{processes} divided into a finite set of \emph{sorts}.
 A process belongs to a unique sort and is noted $a_i$ where $a$ is the sort and $i$ the identifier of the process within the sort $a$.
-At any time, one and only one process of each sort is present; a state of the PH thus corresponds to the set of such processes.
+%At any time, one and only one process of each sort is present; a state of the PH thus corresponds to the set of such processes.
+Each process stands for a kind of “activity level” of its sort; a state of the PH thus corresponds to a set of processes containing exactly one process of each sort.
 
 The concurrent interactions between processes are defined by a set of \emph{actions} divided into classes of priorities.
-Actions describe the replacement of a process by another of the same sort conditioned by the presence of at most one other process and by the fact that no other action of higher priority is playable in the current state of the PH.
+Actions describe the replacement of a process by another of the same sort conditioned by the presence of at most one other process and by the fact that no other action of higher priority can be played in the considered state of the PH.
 An action is denoted by $\PHhit{a_i}{b_j}{b_k}$ where $a_i,b_j,b_k$ are processes of sorts $a$ and $b$.
@@
 \label{def:ph}
-  A \emph{Process Hitting with $k$ priorities}, where $k \in \sN^*$, is a triplet $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$, with $\PHa^{\langle k \rangle} = (\PHa^{(1)}; \dots; \PHa^{(k)})$ a $k$-uplet, where:
+  If $k \in \sN^*$, a \emph{Process Hitting with $k$ priorities} is a triplet $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$ with $\PHa^{\langle k \rangle} = (\PHa^{(1)}; \dots; \PHa^{(k)})$ a $k$-uplet, and:
   \begin{itemize}
     \item $\PHs \DEF \{a,b,\dots\}$ is the finite set of \emph{sorts}.
-    \item $\PHl \DEF \prod_{a \in \PHs} \PHl_a$ is the finite set of states, where $\PHl_a = \{a_0 ; \ldots ; a_{l_a}\}$ is the finite set of \emph{processes} of sort $a \in \PHs$ and $l_a \in \sN^*$.
+    \item $\PHl \DEF \prod_{a \in \PHs} \PHl_a$ is the finite set of \emph{states}, where $\PHl_a = \{a_0 ; \ldots ; a_{l_a}\}$ is the finite set of \emph{processes} of sort $a \in \PHs$ and $l_a \in \sN^*$.
 Each process belongs to a unique sort: $\forall (a_i; b_j) \in \PHl_a \times \PHl_b, a \neq b \Rightarrow a_i \neq b_j$.
-    \item $\forall n \in \llbracket 1; k \rrbracket, \PHa^{(n)} \DEF \{\PHfrappe{a_i}{b_j}{b_k} \mid (a; b) \in \PHs^2 \wedge (a_i; b_j; b_k) \in \PHl_a \times \PHl_b \times \PHl_b \wedge b_j \neq b_k \wedge a = b \Rightarrow a_i = b_j \}$ is the finite set of \emph{actions of priority $n$}.
+    \item $\forall n \in \llbracket 1; k \rrbracket, \PHa^{(n)} \DEF \{\PHfrappe{a_i}{b_j}{b_l} \mid (a; b) \in \PHs^2 \wedge (a_i; b_j; b_l) \in \PHl_a \times \PHl_b \times \PHl_b \wedge b_j \neq b_l \wedge a = b \Rightarrow a_i = b_j \}$ is the finite set of \emph{actions of priority $n$}.
   \end{itemize}
@@
 If $a_i \in \PHl_a$, we define the notation $a_i \in s \EQDEF \PHget{s}{a} = a_i$.
-We define the override of a state by a process in \pref{def:statecap}, which allows to define the dynamics in a Process Hitting model (\pref{def:play}).
-\begin{definition}
+The override of a state $s$ by a process $a_i$ is defined in \pref{def:statecap} as the same state in which the process of sort $a$ has been replace by $a_i$,
+which then allows to define the dynamics of a PH in \pref{def:play}.
+\begin{definition}[$\Cap : \PHl \times \PHproc \rightarrow \PHl$]
 \label{def:statecap}
@@
 \end{definition}
-\begin{definition}
+\begin{definition}[Dynamics of a Process Hitting with $k$ priorities]
 \label{def:play}
@@
   if and only if $\PHget{s}{a} = a_i$, $\PHget{s}{b} = b_j$ and $\forall m < n, \forall g \in \PHa^{(m)}, \PHhitter(g) \notin s \vee \PHtarget(g) \notin s$.
-  In such a case, $(s \PHplay h)$ stands for the state resulting from the play of the action $h$ in $s$, defined by: $(s \PHplay h) = s \Cap \PHbounce(h)$.
+  In such a case, $(s \PHplay h)$ stands for the state resulting from the play of the action $h$ in $s$ and is defined by: $(s \PHplay h) = s \Cap \PHbounce(h)$.
 %  For the sake of clarity, for all $h, h'\in\PHa$, $((s\PHplay h)\PHplay h')$ is abbreviated as $(s\PHplay h\PHplay h')$.
-\end{definition}
 %\begin{definition}[Scenario ($\Sce$)]
 %\label{def:scenario}
-  For a given state $s \in \PHl$,
+
+  If $s \in \PHl$,
   a \emph{scenario} $\delta$ from $s$ is a sequence of actions of $\PHh$ that can be played successively in $s$.
@@
 %\end{definition}
+\end{definition}
 
-\begin{definition}[Process Hitting $n$-reduction] \towrite{Revoir terminologie : “reduction” ? “restriction” ?}
-  If $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$ is a Process Hitting with $k$ priorities and $n \in \segm{1}{k}$, we denote $\restriction{\PH}{n}$ \towrite{$\PH_{|n}$ $\PH'$} the $n$-reduction of $\PH$ the following Process Hitting with $n$ priorities:
-  $\restriction{\PH}{n} = (\PHs; \PHl; \restriction{\PHa}{n})$,
-  with:
+In \pref{def:restriction}, we define the $n$-reduction of a given PH as the PH with $n$ priorities in which only actions of priority lower or equal to $n$ of the original PH are kept.
+\begin{definition}[Process Hitting $n$-reduction] %\towrite{Revoir terminologie : “reduction” ? “restriction” ?}
+\label{def:restriction}
+  If $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$ is a Process Hitting with $k$ priorities and $n \in \segm{1}{k}$, we denote $\restriction{\PH}{n}$ %\towrite{$\PH_{|n}$ $\PH'$}
+  the $n$-reduction of $\PH$.
+  %the following Process Hitting with $n$ priorities:
+  $\restriction{\PH}{n} = (\PHs; \PHl; \restriction{\PHa}{n})$ is a PH with $n$ priorities with:
   $$\restriction{\PHa}{n} = (\PHa^{(1)}; \dots; \PHa^{(n)})$$
@@
 
-\subsection{Modeling cooperation}
-\towrite{Sortes coopératives avec mise à jour prioritaire (pas de décalage temporel)}
-As described in \cite{PMR10-TCSB}, the cooperation between processes to make another bounce can be
-expressed in PH by building a \emph{cooperative sort}.
-\pref{fig:PH-cooperativity} shows an example of cooperation between processes $b_1$ and $c_1$ to
-make $a_1$ bounce to $a_2$:
-a cooperative sort $bc$ is defined with 4 processes (one for each sub-state of the presence of
-processes $b_1$ and $c_1$).
-For the sake of clarity, the $bc$ processes are indexed using the sub-state they represent.
-Hence, $bc_{01}$ represents the sub-state $\PHstate{b_0,c_1}$, and so on.
-Each process of sort $b$ and $c$ hit $bc$ to make it bounce to the process reflecting the status of the sorts $b$
-and $c$ (e.g., $\PHfrappe{b_1}{bc_{00}}{bc_{10}}$ and $\PHfrappe{b_1}{bc_{01}}{bc_{11}}$).
-Then, it is the process $bc_{11}$ which hits $a_1$ to make it bounce to $a_2$ instead of the
-independent hits from $b_1$ and $c_1$.
+\begin{example}
+  \pref{fig:ph-livelock} gives an example of PH with $2$ priorities, with $\PHs = \{ a, b, c, ab \}$ and:
+  \begin{align*}
+    \PHl_a &= \{ a_0, a_1 \} \enspace, & \PHl_b &= \{ b_0, b_1 \} \enspace, \\
+    \PHl_c &= \{ c_0, c_1 \} \enspace, & \PHl_{ab} &= \{ ab_{00}, ab_{01}, ab_{10}, ab_{11} \} \enspace.
+  \end{align*}
+  Actions of priority $1$ are represented with double arrows and actions of priority $2$ are represented with single arrows.
+  The hit part of each action in drawn in plain line and the bounce part is in dotted line.
+  The greyed processes stand for a possible state $s = \PHstate{a_1, b_0, c_0, ab_{10}}$.
 
@@
     \TSetTick{ab}{3}{11}
-    \TSort{(3,1)}{ab}{4}{l}
+    \TSort{(3,1)}{ab}{4}{r}
 
@@
     ;
+    \TState{a_1, b_0, ab_2, c_0}
   \end{tikzpicture}
+  \caption{
   \label{fig:ph-livelock}
-  \caption{An example of PH model with three well-formed components ($a$, $b$ and $c$) and a well-formed cooperative sort ($ab$).}
+    An example of PH model with three well-formed components ($a$, $b$ and $c$) and a well-formed cooperative sort ($ab$).
+  }
 \end{figure}
+
+\end{example}
+
+\subsection{Modeling cooperation}
+%\towrite{Sortes coopératives avec mise à jour prioritaire (pas de décalage temporel)}
+Cooperation between processes to make another process bounce can be expressed in PH by building a \emph{cooperative sort}, as described in \cite{PMR10-TCSB}.
+\pref{fig:ph-livelock} shows an example of cooperation between processes $a_1$ and $b_1$ to make $c_0$ bounce to $c_1$:
+a cooperative sort $ab$ is defined with 4 processes (one for each sub-state of the presence of processes $a_1$ and $b_1$).
+For the sake of clarity, the processes of $ab$ are indexed using the sub-state they represent.
+Hence, $ab_{01}$ represents the sub-state $\PHstate{a_0,b_1}$, and so on.
+Each process of sort $a$ and $b$ hit $ab$ to make it bounce to the process reflecting the status of the sorts $a$ and $b$
+(e.g., $\PHfrappe{a_1}{ab_{00}}{ab_{10}}$ and $\PHfrappe{a_1}{ab_{01}}{ab_{11}}$).
+Then, to represent the cooperation between $a_1$ and $b_1$, the process $ab_{11}$ hits $c_0$ to make it bounce to $c_1$ instead of independent hits from $b_1$ and $a_1$.
 
@@
 special treatment regarding the semantics of related actions.
+Furthermore, it is possible to chain cooperative sorts in order to express more complex cooperations
+or to decrease the number of processes created within each cooperative sort.
+%to prevent the combinatoric explosion of the number of processes created within cooperative sorts.
+%Such constructions are helpful as the static analysis of dynamics developed does not suffer from the number of sorts,
+%but on the number of processes within a single sort.
 
+\begin{comment}
 When the number of cooperating processes is large, it is possible to chain several cooperative sorts
@@
 sorts, but on the number of processes within a single sort.
+\end{comment}
 
 The construction of cooperation in PH allows to encode any boolean functions between cooperating processes \cite{PMR10-TCSB}.
-Due to the presence of priorities, it is possible to build cooperations with no temporal shift by defining the actions on the cooperative sorts with the highest class of priority.
-This allows to gain the same expressivity in PH than in boolean networks.
-\towrite{Traduction BN depuis thèse.}
+Due to the introduction of priorities into the PH framework,
+it is possible to build cooperations with no temporal shift by defining actions updating the cooperative sorts with the highest class of priority.
+This allows to gain the same expressivity in PH than in boolean networks, as explained in \towrite{section 2 ou 3}.
+The aim of this paper is to allow the static analysis of the dynamics to be handled on PH models comprising such higher priory actions updating cooperative sorts.
 
+\begin{comment}
 \begin{example}
@@
 \end{example}
+\end{comment}
 
+\todo{Nouvelle section pour les hypothèses + conséquences ?}
 \subsection{Hypothesis} \towrite{Reformuler}

### 2013-04-01 parts/def-ph.tex
typo
section 2.3

@@
 
-\subsection{Modeling cooperation}
+\subsection{Modelling cooperation}
+\label{ssec:cooperation}
 %\towrite{Sortes coopératives avec mise à jour prioritaire (pas de décalage temporel)}
@@
 \todo{Nouvelle section pour les hypothèses + conséquences ?}
-\subsection{Hypothesis} \towrite{Reformuler}
+\subsection{Restrictions} \towrite{Reformuler}
 \label{ssec:hypothesis}
 
-In the scope of this paper, we focus on a specific class of Process Hitting models.
+In the scope of this paper, we focus on a specific class of PH models.
 We define here the restrictions that lead to this class of models \todo{and show that they are equivalent to discrete networks}.
 
+\pref{cr:2prio} allows to models two kinds of actions: controllable actions that model the non-determinacy of biological evolutions,
+and uncontrollable actions that are used to model non-biological behaviours in the model, that is, the update of cooperative sorts.
+\pref{cr:bounded} states that the dynamics of the studied model $\PH$ contains no infinite sequence of uncontrollable actions.
+As these actions can be considered as non-biological and therefore instantaneous, we thus prevent the existence of any Zeno behaviour
+which would allow the play of an infinite sequence of high priority actions in zero time.
 \begin{criterion}[2 priorities]
@@
 %\paragraph{2 priorities}
-  In this paper, we only consider Process Hitting models with 2 priorities.
+  In this paper, we only consider Process Hitting with $2$ priorities.
+\end{criterion}
+%
+\begin{criterion}[Bounded termination]
+\label{cr:bounded}
+%\paragraph{Bounded termination}
+  The dynamics of $\restriction{\PH}{1}$ contains no cycles:
+  %Cycles are still allowed in $\PH$ however.
+  %Formally :
+  $$\exists N \in \sN, \forall \in \PHl, \forall \delta \in \restriction{\Sce}{1}(s), |\delta| \leq N \enspace.$$
 \end{criterion}
 
-\pref{cr:2prio} allows to models two kinds of actions: controllable actions that model the non-determinacy of biological evolutions,
-and uncontrollable actions that are used to model non-biological behaviours in the model.
-
 In \pref{def:component} we define a well-formed component as a sort that is hit only by actions of priority $2$.
+A well-formed component can stand for a real biological component (protein, light, nutriment…).
 \begin{definition}
 \label{def:component}
-  A sort $a \in \PHs$ is said to be a well-formed component if and only if:
+  A sort $a \in \PHs$ is a \emph{well-formed component} if and only if:
   $$\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) = 2 \enspace.$$
@@
 
+\pref{def:chainsactions} defines chains of uncontrollable actions,
+and \pref{cr:cyclefreeness} prevents the presence of cycles in these chains to avoid incoherent states between cooperative sorts.
 \begin{definition}
 \label{def:chainsactions}
-  The set of chains of actions $\PHh(b, a)$ between two sorts $b$ and $a$ is defined as below:
+  The set of chains of actions $\PHh(a, b)$ between two sorts $a, b \in \PHs$ is defined as below:
   \begin{align*}
-  \PHh(b, a) = \{ (h_i)_{i \in \segm{0}{s}} \in (\PHh^{(1)})^{s+1} &\mid s \in \sN, \PHsort(\PHhitter(h_0)) = b \wedge \PHsort(\PHtarget(h_s)) = a \\
+  \PHh(a, b) = \{ (h_i)_{i \in \segm{0}{s}} \in (\PHh^{(1)})^{s+1} &\mid s \in \sN, \PHsort(\PHhitter(h_0)) = a \wedge \PHsort(\PHtarget(h_s)) = b \\
     & \wedge \forall i \in \segm{1}{s}, \PHsort(\PHtarget(h_{i-1})) = \PHsort(\PHhitter(h_{i})) \}
@@
 \end{definition}
-
 \begin{criterion}[Cycle-freeness between actions of priority $1$]
@@
 
-Given \pref{cr:cyclefreeness}, we define the neighbour \towrite{revoir terminologie : neighbors ? vicinity ?} sorts and actions (\pref{def:neighbors}).
-\begin{definition}[Neighbour sorts ($\Vs$) and Neighbour actions ($\Vh$)]
-\label{def:neighbors}
+In \pref{def:neighbours} we define the notion of neighbour \towrite{revoir terminologie : neighbors ? vicinity ?} sorts and actions of a sort.
 The set of neighbour sorts $\Vs(a)$ of a given sort $a$ is the set of components that can interact with it through actions of priority $1$.
 The set of neighbour actions $\Vh(a)$ of $a$ is the set of actions of priority $1$ influencing $a$.
-  $$\Vs(a) = \{ b \in \components \mid \PHh(b, a) \neq \emptyset \}$$
-%  $$\Vh(a) = \{ h \in \PHh^{(1)} \mid \PHsort(\PHhitter(h)) \in \Vs(a) \wedge \PHsort(\PHtarget(h)) \in \Vs(a) \cup \{ a \} \}$$
-  $$\Vh(a) = \{ h \in \PHh^{(1)} \mid \exists b \in \Vs(a), \exists hs \in \PHh(b,a), h \in hs \}$$
+These definitions are permitted by the previous restrictions (\pref{cr:2prio} and~\ref{cr:cyclefreeness}).
+\begin{definition}[$\Vs : \PHs \rightarrow \powerset(\PHsort)$ ; $\Vh : \PHs \rightarrow \powerset(\PHh)$]
+\label{def:neighbours}
+  For all sort $a \in \PHs$,
+  \begin{align*}
+    \Vs(a) &= \{ b \in \components \mid \PHh(b, a) \neq \emptyset \}\\
+    \Vh(a) &= \{ h \in \PHh^{(1)} \mid \exists b \in \Vs(a), \exists hs \in \PHh(b,a), h \in hs \}
+  \end{align*}
 \end{definition}
 
-We denote $\pfp_s(a)$ the set of processes of sort $a$ that can be reached from state $s$ and that are local steady-states.
-%the set of possible local steady-states of a sort $a$ from a state $s$.
-%\todo{À corriger : état global ?}
-\begin{definition}[Local steady-state ($\pfp$)]
+Finally, we introduce the notion of local steady-state of a sort from a given state.
+This local steady-state is the set of processes towards which the sort tends to evolve to and stay in by playing only uncontrollable actions.
+We denote $\pfp_s(a)$ this set of processes for a sort $a$ in state $s$ (\pref{def:pfp}),
+and we derive from this the notion of well-formed cooperative sort (\pref{def:cs}).
+A well-formed cooperative sort allows to define a cooperation between sorts as presented in \pref{ssec:cooperation};
+therefore, it must be only hit by actions of high priority
+and in a way that it efficiently represents any configuration of its neighbour sorts.
+%any sub-state of its neighbourhood is represented by exactly one local steady state in this sort,
+%and all of its processes represents at least one sub-state of its neighbourhood. \towrite{reformuler ou supprimer}
+\begin{definition}[$\pfp : \PHl \times \PHs \rightarrow \powerset(\PHproc)$]
 \label{def:pfp}
-  For all $a \in \PHa$ and $s \in \PHl$,
+  For all $s \in \PHl$ and $a \in \PHs$,
   \begin{align*}
@@
 \end{definition}
-
-In \pref{def:cs} we define a well-formed cooperative sort as a sort that is only by actions of priority $1$ and so that
-any sub-state of its neighbourhood is represented by exactly one local steady state in this sort,
-and all of its processes represents at least one sub-state of its neighbourhood. \towrite{reformuler ou supprimer}
+%
 \begin{definition}
 \label{def:cs}
-  A sort $a \in \PHs$ is said to be a well-formed cooperative sort iff:
+  A sort $a \in \PHs$ is a \emph{well-formed cooperative} sort if and only if:
   \begin{enumerate}
@@
 %    \item $\forall a_i \in \PHl_a, \exists s \in \underset{b \in \Vs(a)}{\times} \PHl_b, \pfp_s(a) = \{ a_i \}$
-    \item \label{csai} $\forall s \in \PHl, |\pfp_s(a)| = 1$
+    \item \label{csai} $\forall s \in \PHl, \exists a_i \in \PHl_a, \pfp_s(a) = \{ a_i \}$
     \item \label{css} $\forall a_i \in \PHl_a, \exists s \in \PHl, \pfp_s(a) = \{ a_i \}$
@@
 We call $\cs$ the set of well-formed cooperative sorts.
-%We note that: $\forall a \in \components, \Vs(a) = \emptyset \wedge \Vh(a) = \emptyset$
 Because of (\ref{csai}), we denote in the following: $\pfp_s(a) = a_i$.
-Furthermore, because of (\ref{css}), we denote $\csState(a_i)$ the set of sub-states represented by the process $a_i$ of the cooperative sort $a$ (\pref{def:csState}).
-\begin{definition}[Represented sub-states ($\csState$)]
+Furthermore, because of (\ref{css}), we denote $\csState(a_i)$ the set of sub-states represented by the process $a_i$ of any cooperative sort $a$ (\pref{def:csState}).
+\begin{definition}[$\csState : \PHproc \rightarrow \powerset(\PHproc)$]
 \label{def:csState}
+  If $a \in \cs$ and $a_i \in \PHl_a$, we define:
   $$\csState(a_i) = \{ ps \in \underset{b \in \Vs(a)}{\times} \PHl_b \mid \forall s \in \PHl, \pfp_{s \Cap ps}(a) = a_i \}$$
@@
 
+In the following we will simply write “component” (resp.~“cooperative sort”) instead of “well-formed component” (resp.~“well-formed cooperative sort”).
+The last criterion states that the set of sorts of the considered PH must be divided between components and cooperative sorts.
+
 \begin{criterion}[Components \& cooperative sorts]
 \label{cr:compcs}
+\towrite{Problème : sortes non frappées dans $\components$ ou $\cs$ ?}
 %\paragraph{Components \& cooperative sorts}
-  The studied PH is a PH with 2 priorities, and it is only composed of well-formed components and cooperative sorts:
-  $$\components \cup \cs = \PHs \wedge \components \cap \cs = \emptyset \enspace.$$
+  %The studied PH is a PH with 2 priorities, and it is only composed of well-formed components and cooperative sorts:
+  $$\PHs = \components \cup \cs \wedge \components \cap \cs = \emptyset$$
 \end{criterion}
 
-\begin{criterion}[Bounded termination]
-\label{cr:bounded}
-%\paragraph{Bounded termination}
-  The dynamics of model $\restriction{\PH}{1}$ contains no cycles:
-  %Cycles are still allowed in $\PH$ however.
-  %Formally :
-  $$\exists N \in \sN, \forall \delta \in \restriction{\Sce}{1}, |\indexes{\delta}| \leq N \enspace.$$
-\end{criterion}
+\todo{The criteria given in this subsection allow to define a class of PH models that share the same behaviour than discrete models.
+The demonstration of this statement is found in Annex B.}
 

### 2013-04-01 parts/def-ph.tex
section 2.4

@@
 \subsection{Consequences of the restrictions}
-%Given these hypotheses, we can denote: $\pfp_s(a) = a_i$ the local steady-state of $a$ in state $s$.
-We denote by $\update(s)$ the state in which all cooperative sorts are updated.
+
+The previous restrictions lead to a particular class of PH models that can be efficiently studied.
+In this subsection, we give several general theorems that can be derived from these restrictions,
+and which will help building the static analysis of \pref{sec:sa}.
+
+We first denote by $\update(s)$ the state equivalent to $s$ but in which all cooperative sorts are updated (\pref{def:update}).
+This state is unique due to the properties of $\pfp$ given in the previous subsection.
+Then, \pref{th:update} states that from any state, there exists a scenario updating the cooperative sorts of this state.
+%
+\begin{definition}[$\update : \PHl \rightarrow \PHl$]
+\label{def:update}
+  For all $s \in \PHl$, we define:
   \begin{align*}
@@
   \end{align*}
-
-\pref{th:update} states that from any state, there exists a scenario updating the cooperative sorts of this state.
+\end{definition}
+%
 \begin{theorem}
@@
   Let $a$ be a cooperative sort so that $\PHget{s}{a} \neq \pfp_s(a)$.
-  Given the definition of $\pfp_s(a)$, there exists a scenario updating $a$ in $s$.
-  As there is no cycle in between the cooperative sorts and an updated cooperative sort cannot evolve, at most $|\cs|$ updates can be done.
+  Given the definition of $\pfp_s(a)$, there exists a scenario $\delta$ updating $a$ in $s$ so that
+  no scenario in $\restriction{\Sce}{1}(s \PHplay \delta)$ can change the active process of $a$.
+  As there is no cycle of actions between the cooperative sorts (\pref{cr:cyclefreeness}) and an updated cooperative sort cannot evolve, at most $|\cs|$ updates can be done.
 \end{proof}
-\pref{th:hcompcomp} states that for a given state $s$ and for any action $h = \PHhit{a_i}{b_j}{b_k}$ between well-formed components, $h$ can be played after a series of hits that do not prevent it to be fired.
-\pref{th:hcscomp} states the same if $a$ is a well-formed cooperative sort, under the condition that $a_i$ reflects the state of the neighborhood of $a$.
+\pref{th:hcompcomp} states that for a given state $s$ and for any action $h = \PHhit{a_i}{b_j}{b_k}$ between components,
+if $\PHget{s}{a} = a_i$ and $\PHget{s}{b} = b_j$, then
+$h$ can always be played after a series of hits (and these hits do not prevent it to be fired).
+\pref{th:hcscomp} states the same if $a$ is a cooperative sort, under the condition that $a$ is updated in $s$.
+%$a_i$ reflects the state of the neighborhood of $a$.
 \begin{theorem}
 \label{th:hcompcomp}
-  $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, a,b \in \components,$\\
+  $\forall s \in \PHl, \forall a,b \in \components, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh,$\\
   $(\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j) \Rightarrow (\exists \delta \in \restriction{\Sce}{1}(s), \text{$h$ can be played in $s \PHplay \delta$})$
@@
 \begin{proof}
-  From \pref{th:update}, there exists a scenario $\delta$ so that: $(s \PHplay \delta) = \update(s)$.
+  From \pref{th:update}, there exists such a scenario $\delta$ so that: $(s \PHplay \delta) = \update(s)$.
   As $a,b \in \components$, $a_i \in s \PHplay \delta$ and $b_j \in s \PHplay \delta$.
@@
 \begin{proof}
-  From \pref{th:update}, there exists a scenario $\delta$ so that: $(s \PHplay \delta) = \update(s)$.
-  As $a_i \in \pfp_s(a)$, $a_i \in s \PHplay \delta$.
-  Furthermore, $b \in \components$, thus $b_j \in s \PHplay \delta$.
-  Finally, by definition of $\update(s)$, no action of priority $1$ can be played in $s \PHplay \delta$, thus $h$ can be played in $s \PHplay \delta$.
+  Similar to the proof of \pref{th:hcompcomp}, and
+  %From \pref{th:update}, there exists such a scenario $\delta$ so that: $(s \PHplay \delta) = \update(s)$.
+  as $a_i \in \pfp_s(a)$, $a_i \in s \PHplay \delta$.
+  %Furthermore, $b \in \components$, thus $b_j \in s \PHplay \delta$.
+  %Finally, by definition of $\update(s)$, no action of priority $1$ can be played in $s \PHplay \delta$, thus $h$ can be played in $s \PHplay \delta$.
 \end{proof}

### 2013-04-01 parts/intro.tex
notations

@@
 before the discussion and conclusion in section 5.
+
+\paragraph*{Notations}
+In this paper, we denote: $\segm{0}{n} = \{0, 1, \dots, n\}$.
+If $A$ is a finite set,
+$|A|$ is the cardinality of $A$
+and $\powerset(A)$ is the power set of $A$.
+If $x = (x_i)_{i \in \segm{0}{n}}$ is a sequence of elements indexed by $i \in \segm{0}{n}$,
+we denote $|x| = n+1$ the size of this sequence
+and $\indexes{x} = \segm{0}{n}$ its set of indexes.
+We also denote by $\varsigma$ the empty sequence.
+Finally, if $A$ and $B$ are sets,
+$f : A \rightarrow B$ denotes an application $f$ that maps elements of $A$ to elements of $B$.

### 2013-04-01 parts/intro.tex
notations

@@
 \paragraph*{Notations}
-In this paper, we denote: $\segm{0}{n} = \{0, 1, \dots, n\}$.
+We denote: $\segm{a}{b} = \{ a, a+1, \dots, b-1, b \}$.
 If $A$ is a finite set,
@@
 and $\powerset(A)$ is the power set of $A$.
-If $x = (x_i)_{i \in \segm{0}{n}}$ is a sequence of elements indexed by $i \in \segm{0}{n}$,
-we denote $|x| = n+1$ the size of this sequence
-and $\indexes{x} = \segm{0}{n}$ its set of indexes.
+If $x = (x_i)_{i \in \segm{a}{b}}$ is a sequence of elements indexed by $i \in \segm{a}{b}$,
+we denote $|x| = (b-a)+1$ the size of this sequence
+and $\indexes{x} = \segm{1}{|x|}$ its set of indexes.
 We also denote by $\varsigma$ the empty sequence.

### 2013-04-01 parts/sa.tex
begin section 3

@@
 
-\towrite{Mettre de la colle}
+The aim of this section is to define the problem of reachability in a PH,
+and propose an under-approximation allowing to efficiently solve it.
+The static analysis presented here is inspired from~\cite{PMR12-MSCS}.
 
+\subsection{Preliminary definitions}
+\label{ssec:sa-def}
+
+The reachability of a process $a_i$ of a sort $a$ from another process $a_j$ is called an objective and is denoted $\PHobjp{a}{j}{i}$ (\pref{def:obj}).
 \begin{definition}[Objective ($\Obj$)]
@@
 \end{definition}
-We define an \emph{objective sequence} as a sequence of objectives in which each target must be equal to the previous bounce of the same sort, if it exists.
+\noindent
+We define an \emph{objective sequence} as a sequence of objectives in which each objective target must be equal to the previous objective bounce of the same sort, if it exists.
 The set of all objective sequences is denoted by $\OS$.
 
-\begin{definition}[Context $\ctx$ ($\Ctx$)]
+A context (\pref{def:context}) is an extension of the notion of state that can stand for a set of possible initial states.
+We also extend the notion of override of a context by a set of processes (\pref{def:ctxcap}).
+\begin{definition}[Context ($\Ctx$)]
 \label{def:context}
@@
 \end{definition}
-
 For a given context $\ctx$, we note $a_i \in \ctx$ if and only if $a_i \in \PHget{\ctx}{a}$,
-and for all $ps \in \powerset(\PHproc) \cup \PHl$, $ps \subseteq \ctx \EQDEF \forall a_i \in ps, a_i \in \ctx$.
-%The override of a context $\ctx$ by a set of processes $ps$ is noted $\ctx \Cap ps$ (\defref{ctxcap}).
-%Par exemple, $\state{a_1,a_2,b_1,c_1}\Cap\{ a_3, b_2, b_3 \} = \state{a_3,b_2,b_3,c_1}$.
-
-\begin{definition}[$\Cap: \Ctx \times \powerset(\PHproc) \mapsto \Ctx$]
+and for all $ps \in \powerset(\PHproc)$ or $ps \in \PHl$, $ps \subseteq \ctx \EQDEF \forall a_i \in ps, a_i \in \ctx$.
+%
+\begin{definition}[$\Cap: \Ctx \times \powerset(\PHproc) \rightarrow \Ctx$]
 \label{def:ctxcap}
   For a given context $\ctx\in\Ctx$ and a set of processes $ps \in \powerset(\PHproc)$,
-  the override of $\ctx$ by $ps$ is noted $\ctx \Cap ps$ and is defined by
+  the override of $\ctx$ by $ps$ is noted $\ctx \Cap ps$ and is defined by:
   \[ \forall a \in \PHs, \PHget{(\ctx \Cap ps)}{a} =
@@
 \end{definition}
-
+\noindent
 A sequence of actions $\delta$ is \emph{playable} in a context $\ctx$ if and only if 
@@
 
+Finally, bounce sequences on a sort (\pref{def:bs}) are sequences of actions in which the bounce of each action equals the hitter of the following action.
+Bounce sequences are used to find sequences of actions that locally solve a given objective.
+%solve an objective locally, by finding the sequences of actions that allow to reach a process.
+Bounce sequences can be abstracted into the sets of hitters of every action that are different from the considered sort (\pref{def:aBS}).
+This abstraction allows to propagate an objective into objectives on other sots.
+In the following, we denote: $\Sol = \powerset(\PHproc)$.
 \begin{definition}[Bounce sequence ($\BS$)]
@@
 \end{definition}
-
-In the following, we denote: $\Sol = \powerset(\PHproc)$.
+%
 \begin{definition}[$\aBS:\Obj \mapsto \powerset(\Sol)$]
@@
 We define $\concr(\w)$ as the set of scenarios concretising an objective sequence $\w$ in the context $\ctx$.
-In \pref{def:uconcr}, we define $\uconcr(\w)$ as equal to $\concr(\w)$ if it contains scenarios starting from all states $s \subseteq \ctx$.
-if such a scenario exists in all states $s \subseteq \ctx$.
+In \pref{def:uconcr}, we define $\uconcr(\w)$ as equal to $\concr(\w)$ if and only if $\concr(\w)$ contains scenarios starting from all states $s \subseteq \ctx$.
+%if such a scenario exists in all states $s \subseteq \ctx$.
 
@@
 
-The set of all processes involved in an abstract structure $\cwB$ is given in \pref{def:allprocs}.
-\towrite{pré-définir la structure abstraite}
+The aim of the this subsection is to build a graph of local causality that describes the propagation of objectives due to the bounce sequence abstraction of \pref{def:aBS}.
+This oriented graph has the form $(\V, \E)$, where $\V \subset \Proc \cup \Obj \cup \Sol$ and $\E \subset \V \times \V$.
+%In order to build an accurate under-approximation, this graph is defined as a fixed point, in which each iteration saturates 
+The set of all processes involved in such a graph $(\V, \E)$ is given in \pref{def:allprocs}.
+For any objective $P$ and context $\ctx$, \pref{def:maxCont} allows to obtain the set of processes of sort $\PHsort(P)$ that are required to solve $P$ in $\ctx$,
+by computing $\gCont_\ctx(\PHsort(P), P)$.
 \begin{definition}
@@
 \end{definition}
-
+%
 \begin{comment}
@@
 \end{comment}
-
-\subsection{Abstract structure}
-
-\towrite{expliquer maxCont et le graphe de causalité}
-
+%
+%\subsection{Abstract structure}
+%
+%
 \begin{definition}[$\gCont_\ctx : \Sigma \times \Obj \mapsto \powerset(\PHproc)$]
@@
 \end{comment}
+
+\towrite{expliquer le graphe de causalité}
 
@@
 
-\begin{definition}[Coherent solution]
+\towrite{Expliquer}
+
+\begin{definition}[Coherent edge]
 \label{def:coherent}
-  An edge $(x, y) \in \cwE$ is said coherent if and only if
+  An edge $(x, y) \in \cwE$ is said coherent if and only if:
   $(x, y) \in \Bee{\Proc}{\Sol} \Rightarrow y$ has no process successor $a_j \in \Bv \cap \Proc$ so that $\exists a_i \in y$, $a_i \neq a_k$.
@@
 \end{definition}
+
+\towrite{Expliquer}
 

### 2013-04-02 parts/suppl-ph-dn.tex
weak bisimulation of DNs

% vim:set spell spelllang=en:

\section{Weak Bisimulation of Asynchronous Discrete Networks}

\def\DNtrans{\rightarrow_{ADN}}
\def\DNdef{(\mathbb F, \langle f^1, \dots, f^n\rangle)}
\def\DNdep{\f{dep}}
\def\PHPtrans{\rightarrow_{PHP}}
\def\get#1#2{#1[{#2}]}
\def\encodeF#1{\mathbf{#1}}
\def\toPH{\encodeF{PH}}
\def\card#1{|#1|}
\def\decode#1{\llbracket#1\rrbracket}
\def\encode#1{\llparenthesis#1\rrparenthesis}
\def\Hits{\PHa}
\def\hit{\PHhit}
\def\play{\cdot}

\todo{synchronise notations and terminology with the main text}
\todo{define $\PHPtrans$? or defined in main text?}

We exhibit an encoding of Asynchronous Discrete Networks (ADN) with the Process
Hitting using two priority classes, and prove a weak bisimulation relation.

A Discrete Network gathers a finite number of components $i\in[1;n]$ having a discrete finite domain
$\mathbb F^i$ that we note $\mathbb{F}^i = [0;l_i]$.
For each component $i\in[1;n]$, a map $\mathbb F \mapsto F^i$ is defined, where
$\mathbb F = \mathbb F^1 \times \cdots \times \mathbb F^n$, giving the next value of the component
with respect to the global state of the network.
Typically $f^i$ depends on a subset of components that we denote $\DNdep(f^i)$.
In the case of Asynchronous Discrete Networks (ADN), a transition relation $\DNtrans\subset \mathbb
F\times \mathbb F$ is defined such that $x\DNtrans x'$ if and only if there exists a unique
$i\in[1;n]$ such that $\get{x'}{i}=f^i(x)$ and $\forall j\in[1;n], j\neq i, \get{x'}{j}
=\get{x}{j}$, i.e. one and only component has been updated.
This is formalised in \pref{def:DN}.

\begin{definition}[Asynchronous Discrete Network (ADN)]
\label{def:DN}
An ADN is defined by a couple $(\mathbb F, \langle f^1, \dots, f^n \rangle)$
where $\mathbb{F} = \mathbb{F}^1\times\dots\times\mathbb{F}^n$,
and $\forall i\in[1;n]$,
$f^i: \mathbb{F} \mapsto \mathbb{F}^i$ with
$\mathbb{F}^i = [0;l_i]$.
Given two states $x,x'\in\mathbb F$, the transition relation $\DNtrans$ is given by
\[
x\DNtrans x' \Longleftrightarrow
  \exists i\in[1;n], f^i(x)=\get{x'}{i}
  \wedge \forall j\in[1;n], j\neq i, \get{x}{j}=\get{x'}{j}
\enspace,
\]
where $\get{x}{i}$ is the $i$-th component of $x$.
%
We note $\DNdep(f^i)\subseteq \{1,\dots,n\}$ the set of components on which the value of $f^1$
depends: $\forall x,x'\in \mathbb F$ such that $\forall
j\in\DNdep(f^i), \get{x}{j}=\get{x'}{j}$, necessarily $f^i(x)=f^i(x')$.
\end{definition}

Let us denote by $\toPH\DNdef$ the encoding of the ADN $\DNdef$ in Process Hitting with $2$ priority
classes (\pref{def:DN2PH}).
For each component $i\in[1;n]$ of the ADN, two sorts are built: $a^i$ acting for the component
value, and $f^i$ acting for a cooperative sort between the components $\DNdep(f^i)$.
Sorts $a^i$ have one process $a^i_k$ per element in $k\in\mathbb F^i$.
Sorts $f^i$ have one process $f^i_\varsigma$ per state $\varsigma \in \prod_{j\in\DNdep(f^i)}
L_{a^j}$.
Two classes of actions are then defined:
$\Hits^1$ is the set of actions updating the cooperative sorts according to the actual state of the
components:
if $j\in\DNdep(f^i)$, $a^j_k$ hits each process $f^i_\varsigma$ where $\get{\varsigma}{a^j}\neq
a^j_k$ to make it bounce to the process $f^i_{\varsigma'}$ where $\get{\varsigma'}{a^j}=a^j_k$.
$\Hits^2$ is the set of actions encoding the transitions in the ADN:
$f^i_\varsigma$ hits the processes of sort $a^i$ to make them bounce to the process
$a^i_{k'}$ if and only if $k'=f^i(\decode \varsigma)$;
$\decode \varsigma$ being the ADN state correspond to the PH (partial) state $\varsigma$ (note that
$f^i(\decode \varsigma)$ is fully defined because $\decode \varsigma$ specifies the state for all
the components in $\DNdep(f^i)$).

\begin{definition}
\label{def:DN2PH}
$\toPH\DNdef=(\Sigma,L,\Hits^1,\Hits^2)$ is the Process Hitting with 2 priority classes encoding the
ADN $\DNdef$, with:
\begin{itemize}
\item $\Sigma = \{ a^1, \dots, a^n \} \cup \{ f^1, \dots, f^n \}$,
the sorts for components ($a^i$) and cooperative sorts ($f^i$).

\item $L=\prod_{i\in[1;n]} L_{a^i} \times \prod_{i\in[1;n]} L_{f^i}$, where
$L_{a^i}=\{a^i_0, \dots, a^i_{l_i}\}$, and
$L_{f^i}=\{f^i_\varsigma \mid \varsigma\in\prod_{j\in\DNdep(f^i)} L_{a^i} \}$
if $\DNdep(f^i)\neq\emptyset$, otherwise
$L_{f^i}=\{f^i_\emptyset\}$;

\item $\Hits^1= \{ \hit{a^j_k}{f^i_\varsigma}{f^i_{\varsigma'}}
 \mid i\in[1;n] \wedge
j\in\DNdep(f^i) \wedge a^j_k\in L_{a^j} \wedge f^i_\varsigma\in L_{f^i}
\wedge
\get{\varsigma}{a^j}\neq a^j_k 
\wedge \get{\varsigma'}{a^j}=a^j_k
\wedge (\get{\varsigma'}{a^{l}}=\get{\varsigma}{a^l},
\forall l\in[1;n],l\neq j)
\}$, 
the set of actions with priority $1$ for updating cooperative sorts.

\item $\Hits^2=\{ \hit{f^i_\varsigma}{a^i_k}{a^i_{k'}} \mid i\in[1;n] \wedge
      f^i_\varsigma\in L_{f^i} \wedge
      a^i_k\in L_{a^i}\wedge k\neq k' \wedge f^i(\decode \varsigma) = k'
    \}$,
the set of actions with priority $2$ for updating the components using their respective discrete
maps.
$\decode \varsigma$ is defined below.
\end{itemize}
Given a state $s\in L$ of the Process Hitting, 
$\decode s=x$ is the corresponding state in the ADN:
$\forall i\in[1;n], \get{s}{a^i}=a^i_k \Rightarrow \get{x}{i}=k$.

\noindent
Given a state $x\in \mathbb F$ of the ADN, 
$\encode x=s$ is the corresponding state in the Process Hitting:
$\forall i\in[1;n], \get{x}{i}=k \Rightarrow \get{s}{a^i}=a^i_k$
and
$\forall i\in[1;n], \get{s}{f^i}=f^i_\varsigma$ with $f^i_\varsigma\in L_{f^i}$
and $\forall j\in\DNdep(f^i), \get{\varsigma}{j}=\get{s}{a^j}$.
\end{definition}

\pref{thm:bisimDN} states the weak bisimulation relation between an ADN and its encoding in
Process Hitting with $2$ priority classes.
Intuitively, actions updating cooperative sorts being of higher priority, actions updating component
sorts follow strictly the possible transitions of the ADN.

\begin{theorem}[$\DNdef \approx \toPH\DNdef$]~
\label{thm:bisimDN}
\begin{enumerate}
\item $\forall x,x'\in\mathbb F$,
$x\DNtrans x' \Longrightarrow \encode x \PHPtrans^* \encode{x'}$,
where $\PHPtrans^*$ is a finite sequence of $\PHPtrans$ transitions.

\item $\forall s,s'\in L$,
$s\PHPtrans s' \Longrightarrow \decode s = \decode {s'} \vee \decode s \DNtrans
\decode{s'}\enspace.$
\end{enumerate}
\end{theorem}
\begin{proof}
(1) From \pref{def:DN} $x\DNtrans x'\Rightarrow \exists i\in[1;n],
f^i(x)=\get{x'}{i} \wedge \forall j\in[1;n],i\neq j, \get{x}{j}=\get{x'}{j}$.
Let us assume (without loss of generality) that $f^i(x)=k'$, $\get{x}{i}=k$ and
$\varsigma\in\prod_{j\in\DNdep(f^i)} L_{a^j}$ such that
$\forall j\in\DNdep(f^i), \get{\varsigma}{j}=a^j_{\get{x}{j}}$.
From \pref{def:DN2PH}, $h=\hit{f^i_\varsigma}{a^i_k}{a^i_{k'}}\in\Hits^2$.
From $\encode x$ definition,
$a^i_k\in \encode x$ and $f^i_\varsigma\in \encode x$;
moreover, as there is no action in $\Hits^1$ applicable in $\encode x$,
$h$ is applicable in $\encode x$:
$\encode x\PHPtrans \encode x\play h$.
In $\encode x\play h$, the only applicable actions of priority $1$ are those having
$a^i_{k'}$ as hitter and hitting cooperative sorts, giving a finite number of transitions towards
$\encode{x'}$.

(2) $s\PHPtrans s'$ only if there exists an action $h$ applicable in $s$ such that
$s\play h=s'$.
If $\prio(h)=1$, then, by $\Hits^1$ definition, 
$\decode s=\decode {s'}$.
If $\prio(h)=2$, then $\forall i\in[1;n]$,
if $\get{s}{f^i} = f^i_\varsigma$, then, $\forall j\in\DNdep(f^i),
\get{\varsigma}{a^j}=\get{s}{a^j}$.
Let us define $i\in[1;n]$ such that $\get{s}{a^i}\neq\get{s'}{a^i}$ ($i$ is unique for this
transition).
By \pref{def:DN2PH}, if $\get{s'}{a^i}=a^i_{k'}$, necessarily $f^i(\decode s)=k'$, hence
$\decode s\DNtrans \decode{s'}$.
\end{proof}

### 2013-04-02 parts/intro.tex
typo in notations
update lfp notation

@@
 and $\indexes{x} = \segm{1}{|x|}$ its set of indexes.
-We also denote by $\varsigma$ the empty sequence.
-Finally, if $A$ and $B$ are sets,
+We also denote by $\emptyseq$ the empty sequence.
+If $A$ and $B$ are sets,
 $f : A \rightarrow B$ denotes an application $f$ that maps elements of $A$ to elements of $B$.
+Finally, $\lfp{x_0}{x}{x'}$ is the least fixed point greater that $x_0$ of the function $x \mapsto x'$.

### 2013-04-02 parts/intro.tex
update intro + biblio

@@
 
-Discrete modeling frameworks for biological networks is an active research field where formal methods have proved that they were very powerful.
+Discrete modelling frameworks for biological networks is an active research field where formal methods have proved that they were very powerful.
 Such a work started in the seventies.
 It was later enriched in many directions and widely used to elucidate many biological questions.
-Among these questions, a major one is to understand precisely how biological systems evolve and behave; why and how they change their usual behaviors...
+Among these questions, a major one is to understand precisely how biological systems evolve and behave; why and how they change their usual behaviours…
 This leads to questions about the accessibility (possible or inevitable) of certain states.
@@
 Of course, such formal models on which analyses are performed are abstract representations of the actual studied systems.
-They are associated with parameters that have to be synthesized so as to be as much as possible fitting with the real systems having some observed behaviors.
+They are associated with parameters that have to be synthesised so as to be as much as possible fitting with the real systems having some observed behaviors.
 As a matter of fact, the abstractions we get are more or less rough or accurate.
-Usual formal frameworks for such modeling activities are state-transition systems or Petri nets or process algebras.
-We developed a quite similar framework named the Process Hitting \cite{PMR10-TCSB}, with the aim of avoiding to build the whole state space so as to be able to tackle very large systems (which would have led to a huge number of states, hopelessly far to big to be analyzed).
+Usual formal frameworks for such modelling activities are state-transition systems, Petri nets or process algebras.
+We developed a quite similar framework named the Process Hitting \cite{PMR10-TCSB}, with the aim of avoiding to build the whole state space in order to be able to tackle very large systems
+(which would have led to a huge number of states, hopelessly far too big to be analysed).
 
@@
 The idea for this is to introduce timing features of a system into its model.
-Indeed, we are interested in taking into account some knowledge about the relative length of some phenomena as it is a way to refute some kinds of models (parameters) non convenient with the observed dynamic behaviors.
-In this paper, we are introducing these timing properties through priorities.
-It is based on the simple founding idea that the highest priority actions have to be processed before the other ones.
+Indeed, we are interested in taking into account some knowledge about the relative length of some phenomena as it is a way to refute some kinds of models (parameters) non compatible with the observed dynamic behaviours.
+In this paper, we are dealing with these timing properties through priorities,
+that are based on the simple founding idea that the highest priority actions have to be processed before the other ones.
 
-Until now, such a priority scheduling of the actions was not studied very much in the different formal modeling frameworks of systems biology.
-Nevertheless, such an attempt has been carried out for Petri nets by F.
-Bause \cite{Bause97} and the concept of priority relations among the transitions of a network has also more recently been introduced by A.
+Until now, such a priority scheduling of the actions was not studied very much in the different formal modelling frameworks of systems biology.
+Nevertheless, such an attempt has been carried out for Petri nets by F. Bause \cite{Bause97}
+and the concept of priority relations among the transitions of a network has also more recently been introduced by A.
 K.
-Wagler \textit{et al.} in \cite{waw,WaglerW12} in order to allow the modelisation of deterministic systems for biological applications.
+Wagler \textit{et al.} in \cite{waw,WaglerW12} in order to allow modelling deterministic systems for biological applications.
+The concept of priority is much straightforward in the approach of process algebras as it was shown by R.
+Cleaveland and M.
+Hennessy in \cite{Cleaveland199058,Cleaveland99prioritiesin} and their abstractions and equivalences were studied in \cite{Cleaveland:2007:PAP:1282576.1282847}.
+It was later extended for applications in the field of system biology by M. John \textit{et al.} in \cite{jlnu2010}.
 
-Our paper is organized as follows.
+Since our formalism (Process Hitting) is inspired from the $\pi$-calculus, our work is related to such semantic ramifications of extending traditional process algebras with the concepts of priority that allow for some transitions to be given precedence over others.
+The concept is derived in two directions: dynamic versus static, the difference being naturally that the former one refer to a semantics where priority values may change during execution according to some evolution rules.
+In our work, actions exhibit a two-level static priority structure, with certain ones being designated as “prioritised” and others as “unprioritised”.
+
+Our paper is organised as follows.
 The Process Hitting framework is defined in section 2;

### 2013-04-02 parts/intro.tex
update notations

@@
 \paragraph*{Notations}
-We denote: $\segm{a}{b} = \{ a, a+1, \dots, b-1, b \}$.
+%We denote: $\segm{a}{b} = \{ a, a+1, \dots, b-1, b \}$.
+
 If $A$ is a finite set,
@@
 and $\powerset(A)$ is the power set of $A$.
-If $x = (x_i)_{i \in \segm{a}{b}}$ is a sequence of elements indexed by $i \in \segm{a}{b}$,
-we denote $|x| = (b-a)+1$ the size of this sequence
-and $\indexes{x} = \segm{1}{|x|}$ its set of indexes.
+If $x = (x_i)_{i \in \segm{1}{n}}$ is a sequence of elements indexed by $i \in \segm{1}{n}$,
+%we denote %$|x| = (b-a)+1$ the size of this sequence and
+$\indexes{x} = \segm{1}{n}$ is the set of indexes of this sequence.
 We also denote by $\emptyseq$ the empty sequence.
@@
 $f : A \rightarrow B$ denotes an application $f$ that maps elements of $A$ to elements of $B$.
-Finally, $\lfp{x_0}{x}{x'}$ is the least fixed point greater that $x_0$ of the function $x \mapsto x'$.
+$\lfp{x_0}{x}{x'}$ is the least fixed point greater that $x_0$ of the function $x \mapsto x'$.

### 2013-04-02 parts/def-ph.tex
update notations
section 3

@@
     \item $\PHs \DEF \{a,b,\dots\}$ is the finite set of \emph{sorts}.
-    \item $\PHl \DEF \prod_{a \in \PHs} \PHl_a$ is the finite set of \emph{states}, where $\PHl_a = \{a_0 ; \ldots ; a_{l_a}\}$ is the finite set of \emph{processes} of sort $a \in \PHs$ and $l_a \in \sN^*$.
+    %$\PHl \DEF \prod_{a \in \PHs} \PHl_a$
+    \item $\PHl \DEF \underset{a \in \PHs}{\times} \PHl_a$ is the finite set of \emph{states}, where $\PHl_a = \{a_0 ; \ldots ; a_{l_a}\}$ is the finite set of \emph{processes} of sort $a \in \PHs$ and $l_a \in \sN^*$.
 Each process belongs to a unique sort: $\forall (a_i; b_j) \in \PHl_a \times \PHl_b, a \neq b \Rightarrow a_i \neq b_j$.
@@
   \begin{align*}
-  \PHh(a, b) = \{ (h_i)_{i \in \segm{0}{s}} \in (\PHh^{(1)})^{s+1} &\mid s \in \sN, \PHsort(\PHhitter(h_0)) = a \wedge \PHsort(\PHtarget(h_s)) = b \\
-    & \wedge \forall i \in \segm{1}{s}, \PHsort(\PHtarget(h_{i-1})) = \PHsort(\PHhitter(h_{i})) \}
+  \PHh(a, b) = \{ (h_i)_{i \in \segm{1}{s+1}} \in (\PHh^{(1)})^{s+1} &\mid s \in \sN, \PHsort(\PHhitter(h_1)) = a \wedge \PHsort(\PHtarget(h_{s+1})) = b \\
+    & \wedge \forall i \in \segm{1}{s}, \PHsort(\PHtarget(h_{i})) = \PHsort(\PHhitter(h_{i+1})) \}
   \end{align*}

### 2013-04-02 parts/sa.tex
section 3

@@
 \label{def:obj}
-  The reachability of a process $a_j$ prof a process $a_i$ is called an \emph{objective}, noted $\PHobj{a_i}{a_j}$.
-  The set of all objectives is called $\Obj = \{ \PHobj{a_i}{a_j} \mid a \in \PHs \wedge (a_i, a_j) \in \PHl_a^2 \}$.
+  If $a \in \components$, the reachability of a process $a_j$ from a process $a_i$ is called an \emph{objective}, noted $\PHobj{a_i}{a_j}$.
+  The set of all objectives is called $\Obj \DEF \{ \PHobj{a_i}{a_j} \mid a \in \components \wedge (a_i, a_j) \in \PHl_a^2 \}$.
   For an objective $P = \PHobj{a_i}{a_j} \in \Obj$, we define: $\PHsort(P) = a$, $\PHtarget(P)=a_i$, $\PHbounce(P)=a_j$,
@@
 A context (\pref{def:context}) is an extension of the notion of state that can stand for a set of possible initial states.
-We also extend the notion of override of a context by a set of processes (\pref{def:ctxcap}).
+We also extend the override operator to a context and a set of processes (\pref{def:ctxcap}).
 \begin{definition}[Context ($\Ctx$)]
@@
 \end{definition}
-For a given context $\ctx$, we note $a_i \in \ctx$ if and only if $a_i \in \PHget{\ctx}{a}$,
-and for all $ps \in \powerset(\PHproc)$ or $ps \in \PHl$, $ps \subseteq \ctx \EQDEF \forall a_i \in ps, a_i \in \ctx$.
 %
@@
 \noindent
+For a given context $\ctx$, we note $a_i \in \ctx$ if and only if $a_i \in \PHget{\ctx}{a}$,
+and for all $ps \in \powerset(\PHproc)$ or $ps \in \PHl$, $ps \subseteq \ctx \EQDEF \forall a_i \in ps, a_i \in \ctx$.
 A sequence of actions $\delta$ is \emph{playable} in a context $\ctx$ if and only if 
@@
 
-Finally, bounce sequences on a sort (\pref{def:bs}) are sequences of actions in which the bounce of each action equals the hitter of the following action.
+Finally, bounce sequences on a sort $a$ (\pref{def:bs}) are sequences of actions hitting $a$ in which the bounce process of each action is the hitter process of the following action.
 Bounce sequences are used to find sequences of actions that locally solve a given objective.
 %solve an objective locally, by finding the sequences of actions that allow to reach a process.
-Bounce sequences can be abstracted into the sets of hitters of every action that are different from the considered sort (\pref{def:aBS}).
+A bounce sequence can be abstracted into its sets of hitters that are not in sort $a$.
+%of every action that are different from the considered sort (\pref{def:aBS}).
 This abstraction allows to propagate an objective into objectives on other sots.
@@
   \]
-  Obviously, $\BS(\obj{a_i}{a_i}) = \{\emptyseq\}$; and $\BS(\obj{a_i}{a_j}) = \emptyset$ if there is no way to reach $a_j$ from $a_i$.
+  Obviously, $\emptyseq \in \BS(\obj{a_i}{a_i})$; and $\BS(\obj{a_i}{a_j}) = \emptyset$ if there is no way to reach $a_j$ from $a_i$.
 \end{definition}
@@
 In \pref{def:uconcr}, we define $\uconcr(\w)$ as equal to $\concr(\w)$ if and only if $\concr(\w)$ contains scenarios starting from all states $s \subseteq \ctx$.
+\pref{th:uconcr-ctx} will be used to over-approximate the initial context $\ctx$.
 %if such a scenario exists in all states $s \subseteq \ctx$.
-
+%
 \begin{comment}
@@
 \end{comment}
-
+%
 \begin{definition}[$\uconcr: \OS \mapsto \powerset(\Sce)$]
@@
 \label{th:uconcr-ctx}
-  $\ctx' \subseteq \ctx \wedge \uconcr(\w) \neq \emptyset \Longrightarrow \muconcr_{\ctx'}(\w) \neq \emptyset$.
+  $\ctx \subseteq \ctx' \wedge \muconcr_{\ctx'}(\w) \neq \emptyset \Longrightarrow \muconcr_{\ctx}(\w) \neq \emptyset$.
 \end{theorem}
@@
 
-The aim of the this subsection is to build a graph of local causality that describes the propagation of objectives due to the bounce sequence abstraction of \pref{def:aBS}.
-This oriented graph has the form $(\V, \E)$, where $\V \subset \Proc \cup \Obj \cup \Sol$ and $\E \subset \V \times \V$.
-%In order to build an accurate under-approximation, this graph is defined as a fixed point, in which each iteration saturates 
-The set of all processes involved in such a graph $(\V, \E)$ is given in \pref{def:allprocs}.
 For any objective $P$ and context $\ctx$, \pref{def:maxCont} allows to obtain the set of processes of sort $\PHsort(P)$ that are required to solve $P$ in $\ctx$,
-by computing $\gCont_\ctx(\PHsort(P), P)$.
+given by $\gCont_\ctx(\PHsort(P), P)$.
+\begin{comment}
 \begin{definition}
@@
   \end{align*}
+  \begin{align*}
+  \allprocs(\V, \E) = (V \cap \Proc) \cup \{ \PHtarget(P), \PHbounce(P) \mid P \in \V \cap \Obj \}
+  \end{align*}
 \end{definition}
+\end{comment}
 %
@@
 
-\towrite{expliquer le graphe de causalité}
+The reachability of a process $a_i$ is approximated by the ability to solve all objectives $\PHobjp{a}{j}{i}$ so that $a_j$ is in the initial context.
+To this end, the abstractions of bounce sequences (\pref{def:aBS}) solving these objectives are computed, leading to new required processes, and thus new objectives in other sorts.
+Thus, the graph of local causality $\cwB = (\V, \E)$ defined in \pref{def:glc} is a graph where $\V \subset \Proc \cup \Obj \cup \Sol$ and $\E \subset \V \times \V$
+in which edges link any required processes $a_i \in \Proc$ to all corresponding objectives $P \in \Obj$,
+and any objective $P$ to abstractions of bounce sequences $ps \in \Sol$ (\pref{def:aBS}) solving this objective;
+such sets $ps$ then stand for new required processes.
+In the case where a process $a_i$ belongs to a cooperative sort, it is directly linked to the set of the processes $\csState(a_i)$ (\pref{def:csState}) that it represents.
+If the solving of an objective $P$ requires a process of $\PHsort(P)$, a continuity edge is added to re-target this objective (\pref{def:maxCont}).
+Finally, as the active process of every sort may evolve, the graph $\cwB$ is iteratively saturated by every process it contains,
+by overriding its initial context $\ctx$ with $\allprocs(\V, \E)$, defined by:
+%in which the initial context $\ctx$ is updated by iteratively adding every process that appears in the graph ($\allprocs$).
+%The aim of the this subsection is to build a graph of local causality that describes the propagation of objectives due to the bounce sequence abstraction of \pref{def:aBS}.
+%This oriented graph has the form $(\V, \E)$, where $\V \subset \Proc \cup \Obj \cup \Sol$ and $\E \subset \V \times \V$.
+%In order to build an accurate under-approximation, this graph is defined as a fixed point, in which each iteration saturates 
+%We denote $\allprocs(\V, \E)$ the set of all processes involved in such a graph $(\V, \E)$, defined by: %in \pref{def:allprocs}.
+$$\allprocs(\V, \E) = (V \cap \Proc) \cup \{ \PHtarget(P), \PHbounce(P) \mid P \in \V \cap \Obj \}$$
+
+%The final graph of local causality is computed by a fixed point 
+%is defined as a fixed point
 
 \begin{definition}
-  The graph of local causality $\cwB = (\Bv, \Be)$ is defined as: $\cwB = \sfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs(\myB)}}$,
+\label{def:glc}
+  The graph of local causality $\cwB = (\Bv, \Be)$ is defined as: $\cwB = \lfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs(\myB)}}$,
   where $\myB = (\cwV, \cwE)$ is the smallest graph where: $\cwV = \VProc \cup \VObj \cup \VSol$ with $\VProc \subset \PHproc$, $\VObj \subset \Obj$, $\VSol \subset \Sol$ and $\cwE \subset \cwV \times \cwV$ so that:
@@
 $\Bee{X}{Y} = \Be \cap (X \times Y)$, with $X, Y$ amongst $\PHproc$, $\Obj$ and $\Sol$.
-
+%
 \begin{comment}
@@
 \end{comment}
-
-\towrite{Expliquer}
-
+%
+%\towrite{Expliquer}
+%We define in \pref{def:coherent} the notion of coherent edge in the graph of local causality.
+In the graph of local causality, an edge linking a process of a cooperative sort to a solution set $ps$ is coherent if none of the successor processes of $ps$ conflict with the processes of $ps$ (\pref{def:coherent}).
+Then, \pref{th:approxinf} gives a sufficient condition for the concretization of a sequence of objectives in a given context,
+which is derived immediately from the graph of local causality.
+A proof of this theorem is given in Annex~\ref{suppl:demoapproxinf}.
 \begin{definition}[Coherent edge]
@@
   $(x, y) \in \Bee{\Proc}{\Sol} \Rightarrow y$ has no process successor $a_j \in \Bv \cap \Proc$ so that $\exists a_i \in y$, $a_i \neq a_k$.
-%  A set of processes $ps \in \Bv \cap \powerset(\PHproc)$ is said coherent if and only if
-%  it has no process successor $a_j \in \Bv \cap \PHproc$ so that there exists $a_i \in ps$, $a_i \neq a_k$.
 \end{definition}
-
-\towrite{Expliquer}
 
@@
   and all edges are coherent,
-  %and $\forall (a_i, ps) \in \cwE \cap (\Proc \times \powerset(\PHproc))$, $ps$ is coherent,
-  %and all cooperative sort requisites are coherent,
   then $\uconcr(\w) \neq \emptyset$.
@@
   As this PH model contains only $1$ priority, it is equivalent to a PH in the semantics without priorities.
-  The under-approximation on this class of models developed in~\cite{PMR12-MSCS} concludes that $c_1$ is reachable.
-  This is due to the “temporal shift” inherent to cooperative sorts in the semantics without priorities.
+  The under-approximation such models developed in~\cite{PMR12-MSCS} concludes that $c_1$ is reachable.
+  This is due to an over-approximation of the behaviours inherent to cooperative sorts in the semantics without priorities.
 
-  This is an unwanted behaviour that the semantics of PH with priorities proposed in this paper allows to avoid.
-  Indeed, the under-approximation given in \pref{th:approxinf} does not conclude as one of the edges of the resulting graph of local causality is not coherent (\pref{def:coherent}).
+  This unwanted behaviour is palliated by the semantics of PH with priorities proposed in this paper.
+  Indeed, the under-approximation given in \pref{th:approxinf} does not conclude regarding the reachability of $c_1$,
+  as one of the edges of the resulting graph of local causality is not coherent (\pref{def:coherent}).
   The graph of local causality for this example is given in \pref{fig:sa-livelock}.

### 2013-04-02 parts/sa.tex
add section 3.3: reachability of a state

@@
 
-\todo{La méthode permet aussi de conclure sur l'accessilibité d'un état (global ou partiel)}
+\subsection{Reachability of a state}
+
+%\newcommand{\total}{{total}}
+%\newcommand{\reach}{{reach}}
+\newcommand{\total}{\tau}
+\newcommand{\reach}{\sigma}
+
+We note that the semantics of PH with $2$ priorities defined in \pref{ssec:hypothesis} allows to model cooperative sorts representing a coherent configuration of a set of sorts.
+As the method presented in this section allows to efficiently conclude on the reachability of a process,
+we can derive a new method to conclude about the reachability of a state of components.
+Indeed, let $\PH = (\PHs, \PHl, (\PHh^{(1)}, \PHh^{(2)}))$ be a PH and suppose we want to study the reachability of a state $s \in \PHl$.
+Let $\PH' = (\PHs', \PHl', (\PHh'^{(1)}, \PHh'^{(2)}))$,
+with: $\PHs' = \PHs \cup \{ \total, \reach \}$, $\PHl' = \PHl \times \PHl_\total \times \PHl_\reach$,
+where $\total$ is a cooperative sort an all components $\components$ of $\PH$, thus $\PHl_\total = \underset{a \in \components}{\times} \PHl_a$,
+and $\reach$ is a component with $\PHl_\reach = \{ \reach_0, \reach_1 \}$.
+We also define $\PHh'^{(1)}$ as the set $\PHh^{(1)}$ completed with all actions updating the cooperative sort $\total$,
+and $\PHh'^{(2)} = \PHh^{(2)} \cup \{ \PHfrappe{\pfp_s(\total)}{\reach_0}{\reach_1} \}$;
+therefore, the additional action in $\PHh'^{(2)}$ allows to conclude on the reachability of process $\pfp_s(\total)$, that is, on the reachability of $s$ (considering only the components).

### 2013-04-02 parts/suppl-ph-dn.tex
synchronize notations of appendix B

@@
 \def\DNdep{\f{dep}}
-\def\PHPtrans{\rightarrow_{PHP}}
+\def\PHPtrans{\rightarrow_{PH}}
 \def\get#1#2{#1[{#2}]}
@@
 We exhibit an encoding of Asynchronous Discrete Networks (ADN) with the Process
-Hitting using two priority classes, and prove a weak bisimulation relation.
+Hitting using two classes of priorities, and prove a weak bisimulation relation.
 
-A Discrete Network gathers a finite number of components $i\in[1;n]$ having a discrete finite domain
-$\mathbb F^i$ that we note $\mathbb{F}^i = [0;l_i]$.
-For each component $i\in[1;n]$, a map $\mathbb F \mapsto F^i$ is defined, where
+A Discrete Network gathers a finite number of components $i\in\segm{1}{n}$ having a discrete finite domain
+$\mathbb F^i$ that we note $\mathbb{F}^i = \segm{1}{l_i}$.
+For each component $i\in\segm{1}{n}$, a map $\mathbb F \mapsto \mathbb F^i$ is defined, where
 $\mathbb F = \mathbb F^1 \times \cdots \times \mathbb F^n$, giving the next value of the component
@@
 F\times \mathbb F$ is defined such that $x\DNtrans x'$ if and only if there exists a unique
-$i\in[1;n]$ such that $\get{x'}{i}=f^i(x)$ and $\forall j\in[1;n], j\neq i, \get{x'}{j}
-=\get{x}{j}$, i.e. one and only component has been updated.
+$i\in\segm{1}{n}$ such that $\get{x'}{i}=f^i(x)$ and $\forall j\in\segm{1}{n}, j\neq i, \get{x'}{j}
+=\get{x}{j}$, i.e.~one and only one component has been updated.
 This is formalised in \pref{def:DN}.
@@
   where $\mathbb{F} = \mathbb{F}^1\times\dots\times\mathbb{F}^n$,
-and $\forall i\in[1;n]$,
+  and $\forall i\in\segm{1}{n}$,
   $f^i: \mathbb{F} \mapsto \mathbb{F}^i$ with
-$\mathbb{F}^i = [0;l_i]$.
+  $\mathbb{F}^i = \segm{1}{l_i}$.
   Given two states $x,x'\in\mathbb F$, the transition relation $\DNtrans$ is given by
@@
   x\DNtrans x' \Longleftrightarrow
-  \exists i\in[1;n], f^i(x)=\get{x'}{i}
-  \wedge \forall j\in[1;n], j\neq i, \get{x}{j}=\get{x'}{j}
+    \exists i\in\segm{1}{n}, f^i(x)=\get{x'}{i}
+    \wedge \forall j\in\segm{1}{n}, j\neq i, \get{x}{j}=\get{x'}{j}
   \enspace,
@@
   %
-We note $\DNdep(f^i)\subseteq \{1,\dots,n\}$ the set of components on which the value of $f^1$
+  We note $\DNdep(f^i)\subseteq \segm{1}{n}$ the set of components on which the value of $f^i$
   depends: $\forall x,x'\in \mathbb F$ such that $\forall
@@
 
-Let us denote by $\toPH\DNdef$ the encoding of the ADN $\DNdef$ in Process Hitting with $2$ priority
-classes (\pref{def:DN2PH}).
-For each component $i\in[1;n]$ of the ADN, two sorts are built: $a^i$ acting for the component
+Let us denote by $\toPH\DNdef$ the encoding of the ADN $\DNdef$ in Process Hitting with $2$ classes
+of priorities (\pref{def:DN2PH}).
+For each component $i\in\segm{1}{n}$ of the ADN, two sorts are built: $a^i$ acting for the component
 value, and $f^i$ acting for a cooperative sort between the components $\DNdep(f^i)$.
 Sorts $a^i$ have one process $a^i_k$ per element in $k\in\mathbb F^i$.
-Sorts $f^i$ have one process $f^i_\varsigma$ per state $\varsigma \in \prod_{j\in\DNdep(f^i)}
-L_{a^j}$.
+Sorts $f^i$ have one process $f^i_\varsigma$ per state $\varsigma \in \underset{j\in\DNdep(f^i)}{\times}
+\PHl_{a^j}$.
 Two classes of actions are then defined:
-$\Hits^1$ is the set of actions updating the cooperative sorts according to the actual state of the
+$\Hits^{(1)}$ is the set of actions updating the cooperative sorts according to the current state of the
 components:
 if $j\in\DNdep(f^i)$, $a^j_k$ hits each process $f^i_\varsigma$ where $\get{\varsigma}{a^j}\neq
-a^j_k$ to make it bounce to the process $f^i_{\varsigma'}$ where $\get{\varsigma'}{a^j}=a^j_k$.
-$\Hits^2$ is the set of actions encoding the transitions in the ADN:
+a^j_k$ to make it bounce to the process $f^i_{\varsigma \Cap a^j_k}$.
+%$f^i_{\varsigma'}$ where $\get{\varsigma'}{a^j}=a^j_k$.
+$\Hits^{(2)}$ is the set of actions encoding the transitions in the ADN:
 $f^i_\varsigma$ hits the processes of sort $a^i$ to make them bounce to the process
 $a^i_{k'}$ if and only if $k'=f^i(\decode \varsigma)$;
-$\decode \varsigma$ being the ADN state correspond to the PH (partial) state $\varsigma$ (note that
+$\decode \varsigma$ being the ADN state corresponding to the PH (partial) state $\varsigma$ (note that
 $f^i(\decode \varsigma)$ is fully defined because $\decode \varsigma$ specifies the state for all
@@
 \label{def:DN2PH}
-$\toPH\DNdef=(\Sigma,L,\Hits^1,\Hits^2)$ is the Process Hitting with 2 priority classes encoding the
+  $\toPH\DNdef=(\Sigma,\PHl,(\Hits^{(1)},\Hits^{(2)}))$ is the Process Hitting with 2 classes of priority encoding the
   ADN $\DNdef$, with:
@@
     \item $\Sigma = \{ a^1, \dots, a^n \} \cup \{ f^1, \dots, f^n \}$,
-the sorts for components ($a^i$) and cooperative sorts ($f^i$).
+      the sorts for components ($a^i$) and cooperative sorts ($f^i$);
 
-\item $L=\prod_{i\in[1;n]} L_{a^i} \times \prod_{i\in[1;n]} L_{f^i}$, where
-$L_{a^i}=\{a^i_0, \dots, a^i_{l_i}\}$, and
-$L_{f^i}=\{f^i_\varsigma \mid \varsigma\in\prod_{j\in\DNdep(f^i)} L_{a^i} \}$
+    \item $\PHl=\underset{i\in\segm{1}{n}}{\times} \PHl_{a^i} \times \underset{i\in\segm{1}{n}}{\times} \PHl_{f^i}$, where
+      $\PHl_{a^i}=\{a^i_0, \dots, a^i_{l_i}\}$, and
+      $\PHl_{f^i}=\{f^i_\varsigma \mid \varsigma\in\underset{j\in\DNdep(f^i)}{\times} \PHl_{a^i} \}$
       if $\DNdep(f^i)\neq\emptyset$, otherwise
-$L_{f^i}=\{f^i_\emptyset\}$;
+      $\PHl_{f^i}=\{f^i_\emptyset\}$;
 
-\item $\Hits^1= \{ \hit{a^j_k}{f^i_\varsigma}{f^i_{\varsigma'}}
- \mid i\in[1;n] \wedge
-j\in\DNdep(f^i) \wedge a^j_k\in L_{a^j} \wedge f^i_\varsigma\in L_{f^i}
+    \item $\Hits^{(1)}= \{ \hit{a^j_k}{f^i_\varsigma}{f^i_{\varsigma'}}
+      \mid i\in\segm{1}{n} \wedge
+      j\in\DNdep(f^i) \wedge a^j_k\in \PHl_{a^j} \wedge f^i_\varsigma\in \PHl_{f^i}
       \wedge
@@
       \wedge (\get{\varsigma'}{a^{l}}=\get{\varsigma}{a^l},
-\forall l\in[1;n],l\neq j)
+      \forall l\in\segm{1}{n},l\neq j)
       \}$, 
-the set of actions with priority $1$ for updating cooperative sorts.
+      the set of actions with priority $1$ that update cooperative sorts;
 
-\item $\Hits^2=\{ \hit{f^i_\varsigma}{a^i_k}{a^i_{k'}} \mid i\in[1;n] \wedge
-      f^i_\varsigma\in L_{f^i} \wedge
-      a^i_k\in L_{a^i}\wedge k\neq k' \wedge f^i(\decode \varsigma) = k'
+    \item $\Hits^{(2)}=\{ \hit{f^i_\varsigma}{a^i_k}{a^i_{k'}} \mid i\in\segm{1}{n} \wedge
+          f^i_\varsigma\in \PHl_{f^i} \wedge
+          a^i_k\in \PHl_{a^i}\wedge k\neq k' \wedge f^i(\decode \varsigma) = k'
         \}$,
@@
   \end{itemize}
-Given a state $s\in L$ of the Process Hitting, 
+  Given a state $s\in \PHl$ of the Process Hitting, 
   $\decode s=x$ is the corresponding state in the ADN:
-$\forall i\in[1;n], \get{s}{a^i}=a^i_k \Rightarrow \get{x}{i}=k$.
+  $\forall i\in\segm{1}{n}, \get{s}{a^i}=a^i_k \Rightarrow \get{x}{i}=k$.
 
@@
   $\encode x=s$ is the corresponding state in the Process Hitting:
-$\forall i\in[1;n], \get{x}{i}=k \Rightarrow \get{s}{a^i}=a^i_k$
+  $\forall i\in\segm{1}{n}, \get{x}{i}=k \Rightarrow \get{s}{a^i}=a^i_k$
   and
-$\forall i\in[1;n], \get{s}{f^i}=f^i_\varsigma$ with $f^i_\varsigma\in L_{f^i}$
+  $\forall i\in\segm{1}{n}, \get{s}{f^i}=f^i_\varsigma$ with $f^i_\varsigma\in \PHl_{f^i}$
   and $\forall j\in\DNdep(f^i), \get{\varsigma}{j}=\get{s}{a^j}$.
@@
 \pref{thm:bisimDN} states the weak bisimulation relation between an ADN and its encoding in
-Process Hitting with $2$ priority classes.
+Process Hitting with $2$ classes of priorities.
 Intuitively, actions updating cooperative sorts being of higher priority, actions updating component
@@
   \begin{enumerate}
-\item $\forall x,x'\in\mathbb F$,
+    \item \label{adn2ph} $\forall x,x'\in\mathbb F$,
       $x\DNtrans x' \Longrightarrow \encode x \PHPtrans^* \encode{x'}$,
@@
 
-\item $\forall s,s'\in L$,
+    \item \label{ph2adn} $\forall s,s'\in \PHl$,
       $s\PHPtrans s' \Longrightarrow \decode s = \decode {s'} \vee \decode s \DNtrans
@@
 \begin{proof}
-(1) From \pref{def:DN} $x\DNtrans x'\Rightarrow \exists i\in[1;n],
-f^i(x)=\get{x'}{i} \wedge \forall j\in[1;n],i\neq j, \get{x}{j}=\get{x'}{j}$.
+(\ref{adn2ph}) From \pref{def:DN}, $x\DNtrans x'\Rightarrow \exists i\in\segm{1}{n},
+f^i(x)=\get{x'}{i} \wedge \forall j\in\segm{1}{n},i\neq j, \get{x}{j}=\get{x'}{j}$.
 Let us assume (without loss of generality) that $f^i(x)=k'$, $\get{x}{i}=k$ and
-$\varsigma\in\prod_{j\in\DNdep(f^i)} L_{a^j}$ such that
+$\varsigma\in\underset{j\in\DNdep(f^i)}{\times} \PHl_{a^j}$ such that
 $\forall j\in\DNdep(f^i), \get{\varsigma}{j}=a^j_{\get{x}{j}}$.
-From \pref{def:DN2PH}, $h=\hit{f^i_\varsigma}{a^i_k}{a^i_{k'}}\in\Hits^2$.
-From $\encode x$ definition,
+From \pref{def:DN2PH}, $h=\hit{f^i_\varsigma}{a^i_k}{a^i_{k'}}\in\Hits^{(2)}$.
+From the definition of $\encode x$,
 $a^i_k\in \encode x$ and $f^i_\varsigma\in \encode x$;
-moreover, as there is no action in $\Hits^1$ applicable in $\encode x$,
+moreover, as there is no action in $\Hits^{(1)}$ applicable in $\encode x$,
 $h$ is applicable in $\encode x$:
@@
 
-(2) $s\PHPtrans s'$ only if there exists an action $h$ applicable in $s$ such that
+(\ref{ph2adn}) $s\PHPtrans s'$ only if there exists an action $h$ applicable in $s$ such that
 $s\play h=s'$.
-If $\prio(h)=1$, then, by $\Hits^1$ definition, 
+If $\prio(h)=1$, then, by definition of $\Hits^{(1)}$, 
 $\decode s=\decode {s'}$.
-If $\prio(h)=2$, then $\forall i\in[1;n]$,
+If $\prio(h)=2$, then $\forall i\in\segm{1}{n}$,
 if $\get{s}{f^i} = f^i_\varsigma$, then, $\forall j\in\DNdep(f^i),
 \get{\varsigma}{a^j}=\get{s}{a^j}$.
-Let us define $i\in[1;n]$ such that $\get{s}{a^i}\neq\get{s'}{a^i}$ ($i$ is unique for this
+Let $i\in\segm{1}{n}$ such that $\get{s}{a^i}\neq\get{s'}{a^i}$ ($i$ is unique for this
 transition).

### 2013-04-02 parts/sa.tex
complete with substate reachability

@@
 
-%\newcommand{\total}{{total}}
-%\newcommand{\reach}{{reach}}
 \newcommand{\total}{\tau}
@@
 We also define $\PHh'^{(1)}$ as the set $\PHh^{(1)}$ completed with all actions updating the cooperative sort $\total$,
-and $\PHh'^{(2)} = \PHh^{(2)} \cup \{ \PHfrappe{\pfp_s(\total)}{\reach_0}{\reach_1} \}$;
-therefore, the additional action in $\PHh'^{(2)}$ allows to conclude on the reachability of process $\pfp_s(\total)$, that is, on the reachability of $s$ (considering only the components).
+and $\PHh'^{(2)} = \PHh^{(2)} \cup \{ \PHhit{\pfp_s(\total)}{\reach_0}{\reach_1} \}$.
+
+Given an initial context $\ctx$, the reachability of $s$ in $\PH$ is equivalent to the concretization of $\PHobjp{\reach}{0}{1}$ in $\PH'$ from the initial context $\ctx \cup \{ \reach_0 \}$ (the initial state of $\total$ does not matter), which can be under-approximated using \pref{th:approxinf}.
+Indeed, the additional action $\PHhit{\pfp_s(\total)}{\reach_0}{\reach_1}$ in $\PHh'^{(2)}$ allows to conclude on the reachability of process $\pfp_s(\total)$, that is, on the reachability of the state $s$ (considering only the components).
+Moreover, it is possible to compute the reachability of a partial state by creating the sort $\total$ on a subset of $\components$,
+or the reachability of a set of states $S \subset \PHl$ by creating several actions $\PHhit{\total_s}{\reach_0}{\reach_1}$ for each state $s \in S$.

### 2013-04-02 parts/def-ph.tex
add notation for a transition in PH
proofreading of section 2

@@
 Then we describe the modelling of cooperation between components and discuss how the new aforementioned semantics makes this modelling more accurate.
-\towrite{Démo équivalence avec réseaux discret : ici ou dans la section 3 ?}
 Finally, in order to perform a static analysis on this new semantics, we give several criteria to restrict the class of models that we can study,
 and give several theorems that follow.
+This class of models is equivalent to Asynchronous Discrete Networks.
+%\towrite{Démo équivalence avec réseaux discret : ici ou dans la section 3 ?}
 
-\subsection{Definition of the Process Hitting with $k$ priorities}
+\subsection{Definition of the Process Hitting with $k$ classes of priorities}
 \label{ssec:PH}
-\towrite{Reformuler (actuellement trop proche de CMSB)}
-A PH with $k$ priorities (\pref{def:ph}), also simply called PH \towrite{abréviation ?} in the following, gathers a finite number of concurrent \emph{processes} divided into a finite set of \emph{sorts}.
+%\towrite{Reformuler (actuellement trop proche de CMSB)}
+A PH with $k$ classes of priorities (\pref{def:ph}), also simply called “PH” in the following when it is not ambiguous, gathers a finite number of concurrent \emph{processes} divided into a finite set of \emph{sorts}.
 A process belongs to a unique sort and is noted $a_i$ where $a$ is the sort and $i$ the identifier of the process within the sort $a$.
@@
 
-\begin{definition}[Process Hitting with $k$ priorities] \towrite{Revoir terminologie}
+\begin{definition}[Process Hitting with $k$ classes of priorities]% \towrite{Revoir terminologie}
 \label{def:ph}
-  If $k \in \sN^*$, a \emph{Process Hitting with $k$ priorities} is a triplet $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$ with $\PHa^{\langle k \rangle} = (\PHa^{(1)}; \dots; \PHa^{(k)})$ a $k$-uplet, and:
+  If $k \in \sN^*$, a \emph{Process Hitting with $k$ classes of priorities} is a triplet $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$,
+  where $\PHa^{\langle k \rangle} = (\PHa^{(1)}; \dots; \PHa^{(k)})$ is a $k$-uplet and:
   \begin{itemize}
-    \item $\PHs \DEF \{a,b,\dots\}$ is the finite set of \emph{sorts}.
+    \item $\PHs \DEF \{a,b,\dots\}$ is the finite set of \emph{sorts},
     %$\PHl \DEF \prod_{a \in \PHs} \PHl_a$
     \item $\PHl \DEF \underset{a \in \PHs}{\times} \PHl_a$ is the finite set of \emph{states}, where $\PHl_a = \{a_0 ; \ldots ; a_{l_a}\}$ is the finite set of \emph{processes} of sort $a \in \PHs$ and $l_a \in \sN^*$.
-Each process belongs to a unique sort: $\forall (a_i; b_j) \in \PHl_a \times \PHl_b, a \neq b \Rightarrow a_i \neq b_j$.
+Each process belongs to a unique sort: $\forall (a_i; b_j) \in \PHl_a \times \PHl_b, a \neq b \Rightarrow a_i \neq b_j$,
     \item $\forall n \in \llbracket 1; k \rrbracket, \PHa^{(n)} \DEF \{\PHfrappe{a_i}{b_j}{b_l} \mid (a; b) \in \PHs^2 \wedge (a_i; b_j; b_l) \in \PHl_a \times \PHl_b \times \PHl_b \wedge b_j \neq b_l \wedge a = b \Rightarrow a_i = b_j \}$ is the finite set of \emph{actions of priority $n$}.
@@
 \end{definition}
-
 \noindent
@@
 \end{definition}
-\begin{definition}[Dynamics of a Process Hitting with $k$ priorities]
+\begin{definition}[Dynamics of a PH ($\PHPtrans$)]
 \label{def:play}
@@
   In such a case, $(s \PHplay h)$ stands for the state resulting from the play of the action $h$ in $s$ and is defined by: $(s \PHplay h) = s \Cap \PHbounce(h)$.
+  Moreover, we denote: $s \PHPtrans (s \PHplay h)$.
+%  If $s, s' \in \PHl$ are two states and $\exists h \in \PHh$, $h$ is playable in $s$ and $s' = s \PHplay h$, then we denote: $s \PHPtrans s'$.
 %  For the sake of clarity, for all $h, h'\in\PHa$, $((s\PHplay h)\PHplay h')$ is abbreviated as $(s\PHplay h\PHplay h')$.
@@
 
-In \pref{def:restriction}, we define the $n$-reduction of a given PH as the PH with $n$ priorities in which only actions of priority lower or equal to $n$ of the original PH are kept.
-\begin{definition}[Process Hitting $n$-reduction] %\towrite{Revoir terminologie : “reduction” ? “restriction” ?}
+In \pref{def:restriction}, we define the $n$-reduction of a given PH as the PH with $n$ classes of priorities in which only actions of priority lower or equal to $n$ are kept.
+\begin{definition}[PH $n$-reduction] %\towrite{Revoir terminologie : “reduction” ? “restriction” ?}
 \label{def:restriction}
-  If $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$ is a Process Hitting with $k$ priorities and $n \in \segm{1}{k}$, we denote $\restriction{\PH}{n}$ %\towrite{$\PH_{|n}$ $\PH'$}
+  If $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$ is a Process Hitting with $k$ classes of priorities and $n \in \segm{1}{k}$, we denote $\restriction{\PH}{n}$ %\towrite{$\PH_{|n}$ $\PH'$}
   the $n$-reduction of $\PH$.
   %the following Process Hitting with $n$ priorities:
-  $\restriction{\PH}{n} = (\PHs; \PHl; \restriction{\PHa}{n})$ is a PH with $n$ priorities with:
-  $$\restriction{\PHa}{n} = (\PHa^{(1)}; \dots; \PHa^{(n)})$$
-  Furthermore, we denote: $\restriction{\Sce}{n}(s)$ the set of scenarios from $s$ made of actions of $\restriction{\PHa}{n}$.
+  $\restriction{\PH}{n} = (\PHs; \PHl; \PHa'^{\langle n \rangle})$ is a PH with $n$ classes of priorities with:
+  $$\PHa'^{\langle n \rangle} = (\PHa^{(1)}; \dots; \PHa^{(n)})$$
+  Furthermore, we denote: $\restriction{\Sce}{n}(s)$ the set of scenarios from $s$ in $\restriction{\PH}{n}$.
+  %made of actions of $\PHa'^{\langle n \rangle}$.
 \end{definition}
@@
 \begin{example}
-  \pref{fig:ph-livelock} gives an example of PH with $2$ priorities, with $\PHs = \{ a, b, c, ab \}$ and:
+  \pref{fig:ph-livelock} gives an example of PH with $2$ classes of priorities where:
   \begin{align*}
+    \PHs &= \{ a, b, c, ab \} \enspace, \\
     \PHl_a &= \{ a_0, a_1 \} \enspace, & \PHl_b &= \{ b_0, b_1 \} \enspace, \\
@@
   \end{align*}
-  Actions of priority $1$ are represented with double arrows and actions of priority $2$ are represented with single arrows.
-  The hit part of each action in drawn in plain line and the bounce part is in dotted line.
-  The greyed processes stand for a possible state $s = \PHstate{a_1, b_0, c_0, ab_{10}}$.
+  There also is especially: $\{ \PHhit{ab_{11}}{c_0}{c_1}, \PHhit{a_1}{a_1}{a_0}, \PHhit{a_0}{b_0}{b_1} \} \subset \PHh^{(2)}$.
 
@@
   \label{fig:ph-livelock}
-    An example of PH model with three well-formed components ($a$, $b$ and $c$) and a well-formed cooperative sort ($ab$).
+    An example of PH with $2$ classes of priorities.
+    Sorts are represented as labelled boxes and processes as circles with their identifier on the side.
+    Actions of $\PHh^{(1)}$ are represented by double arrows and actions of $\PHh^{(2)}$ are represented by single arrows;
+    the hit part of each action in drawn in plain line and the bounce part is in dotted line.
+    Greyed processes stand for a possible state $s = \PHstate{a_1, b_0, c_0, ab_{10}}$.
+    %This PH notably contains three well-formed components ($a$, $b$ and $c$) and a well-formed cooperative sort ($ab$).
   }
@@
 \label{ssec:cooperation}
+
 %\towrite{Sortes coopératives avec mise à jour prioritaire (pas de décalage temporel)}
@@
 For the sake of clarity, the processes of $ab$ are indexed using the sub-state they represent.
-Hence, $ab_{01}$ represents the sub-state $\PHstate{a_0,b_1}$, and so on.
+Hence, $ab_{10}$ represents the sub-state $\PHstate{a_1,b_0}$, and so on.
 Each process of sort $a$ and $b$ hit $ab$ to make it bounce to the process reflecting the status of the sorts $a$ and $b$
 (e.g., $\PHfrappe{a_1}{ab_{00}}{ab_{10}}$ and $\PHfrappe{a_1}{ab_{01}}{ab_{11}}$).
-Then, to represent the cooperation between $a_1$ and $b_1$, the process $ab_{11}$ hits $c_0$ to make it bounce to $c_1$ instead of independent hits from $b_1$ and $a_1$.
+Then, to represent the cooperation between $a_1$ and $b_1$, the process $ab_{11}$ hits $c_0$ to make it bounce to $c_1$ instead of independent hits from $a_1$ and $b_1$.
 
@@
 Furthermore, it is possible to chain cooperative sorts in order to express more complex cooperations
-or to decrease the number of processes created within each cooperative sort.
+or to decrease the number of processes created within each cooperative sort,
+as this number is exponential in the number of sorts that cooperate.
 %to prevent the combinatoric explosion of the number of processes created within cooperative sorts.
@@
 
-The construction of cooperation in PH allows to encode any boolean functions between cooperating processes \cite{PMR10-TCSB}.
+The construction of cooperation in PH allows to encode any Boolean functions between cooperating processes \cite{PMR10-TCSB}.
 Due to the introduction of priorities into the PH framework,
 it is possible to build cooperations with no temporal shift by defining actions updating the cooperative sorts with the highest class of priority.
-This allows to gain the same expressivity in PH than in boolean networks, as explained in \towrite{section 2 ou 3}.
+This allows to gain the same expressivity in PH than in Boolean networks, as stated in \pref{ssec:hypothesis}.
 The aim of this paper is to allow the static analysis of the dynamics to be handled on PH models comprising such higher priory actions updating cooperative sorts.
@@
 \todo{Nouvelle section pour les hypothèses + conséquences ?}
-\subsection{Restrictions} \towrite{Reformuler}
 \label{ssec:hypothesis}
+\subsection{Restrictions} %\towrite{Reformuler}
 
 In the scope of this paper, we focus on a specific class of PH models.
-We define here the restrictions that lead to this class of models \todo{and show that they are equivalent to discrete networks}.
+We define here the restrictions that lead to this class of models and show that they are equivalent to discrete networks.
 
-\pref{cr:2prio} allows to models two kinds of actions: controllable actions that model the non-determinacy of biological evolutions,
-and uncontrollable actions that are used to model non-biological behaviours in the model, that is, the update of cooperative sorts.
-\pref{cr:bounded} states that the dynamics of the studied model $\PH$ contains no infinite sequence of uncontrollable actions.
-As these actions can be considered as non-biological and therefore instantaneous, we thus prevent the existence of any Zeno behaviour
-which would allow the play of an infinite sequence of high priority actions in zero time.
+\pref{cr:2prio} allows to distinguish two kinds of actions:
+\emph{unprioritised actions} modelling the non-determinacy of biological evolutions
+and \emph{prioritised actions} used to model non-biological behaviours in the model, namely the update of cooperative sorts.
+\pref{cr:bounded} states that the dynamics of the studied model $\PH$ contains no infinite sequence of prioritised actions.
+As these actions can be considered as non-biological and therefore instantaneous, we thus prevent the existence of any Zeno-like behaviour
+which would allow the play of an infinite sequence of prioritised actions in “zero time”.
 \begin{criterion}[2 priorities]
@@
 %\paragraph{2 priorities}
-  In this paper, we only consider Process Hitting with $2$ priorities.
+  In this paper, we only consider Process Hitting with $2$ classes of priorities:
+  $\PH = (\PHs; \PHl; \PHa^{\langle 2 \rangle})$.
 \end{criterion}
@@
 
-In \pref{def:component} we define a well-formed component as a sort that is hit only by actions of priority $2$.
-A well-formed component can stand for a real biological component (protein, light, nutriment…).
-\begin{definition}
+In \pref{def:component} we define a well-formed component as a sort that is hit only by unprioritised actions, or that no action hits.
+%A well-formed component may stand for a real biological component (protein, light, nutriment…).
+\begin{definition}[Well-formed component ($\components$)]
 \label{def:component}
@@
 
-\pref{def:chainsactions} defines chains of uncontrollable actions,
-and \pref{cr:cyclefreeness} prevents the presence of cycles in these chains to avoid incoherent states between cooperative sorts.
+\pref{def:chainsactions} defines chains of prioritised actions,
+and \pref{cr:cyclefreeness} prevents the presence of cycles in these chains.
+%as prioritised actions are used to update non-biological components.
+%this restriction will prevent incoherent states between cooperative sorts ().
 \begin{definition}
@@
 \end{definition}
-\begin{criterion}[Cycle-freeness between actions of priority $1$]
+\begin{criterion}[Cycle-freeness between prioritised actions]
 \label{cr:cyclefreeness}
@@
 
-In \pref{def:neighbours} we define the notion of neighbour \towrite{revoir terminologie : neighbors ? vicinity ?} sorts and actions of a sort.
-The set of neighbour sorts $\Vs(a)$ of a given sort $a$ is the set of components that can interact with it through actions of priority $1$.
-The set of neighbour actions $\Vh(a)$ of $a$ is the set of actions of priority $1$ influencing $a$.
+In \pref{def:neighbours} we define the notion of neighbouring sorts and actions of a given sort.
+The set of neighbouring sorts $\Vs(a)$ of a sort $a$ is the set of components that can interact with it through prioritised actions.
+The set of neighbouring actions $\Vh(a)$ of $a$ is the set of prioritised actions influencing $a$.
 These definitions are permitted by the previous restrictions (\pref{cr:2prio} and~\ref{cr:cyclefreeness}).
-\begin{definition}[$\Vs : \PHs \rightarrow \powerset(\PHsort)$ ; $\Vh : \PHs \rightarrow \powerset(\PHh)$]
+\begin{definition}[$\Vs : \PHs \rightarrow \powerset(\PHsort)$; $\Vh : \PHs \rightarrow \powerset(\PHh)$]
 \label{def:neighbours}
@@
 Finally, we introduce the notion of local steady-state of a sort from a given state.
-This local steady-state is the set of processes towards which the sort tends to evolve to and stay in by playing only uncontrollable actions.
+This local steady-state is the set of processes towards which the sort tends to evolve to, and stay in, when playing only prioritised actions.
 We denote $\pfp_s(a)$ this set of processes for a sort $a$ in state $s$ (\pref{def:pfp}),
 and we derive from this the notion of well-formed cooperative sort (\pref{def:cs}).
-A well-formed cooperative sort allows to define a cooperation between sorts as presented in \pref{ssec:cooperation};
-therefore, it must be only hit by actions of high priority
-and in a way that it efficiently represents any configuration of its neighbour sorts.
+A well-formed cooperative sort models a cooperation between sorts as presented in \pref{ssec:cooperation};
+therefore, it must be only hit by prioritised actions,
+in a way that its local steady-states efficiently represents all configurations of its neighbouring sorts.
 %any sub-state of its neighbourhood is represented by exactly one local steady state in this sort,
@@
 %
-\begin{definition}
+\begin{definition}[Well-formed cooperative sorts ($\cs$)]
 \label{def:cs}
@@
   \begin{enumerate}
-    \item $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) = 1$
+    \item $\exists b \in \PHs, \PHh(b, a) \neq \emptyset$
 %    \item $\forall s \in \underset{b \in \Vs(a)}{\times} \PHl_b, |\pfp_s(a)| = 1$
@@
   \end{enumerate}
+  We call $\cs$ the set of well-formed cooperative sorts.
 \end{definition}
-We call $\cs$ the set of well-formed cooperative sorts.
-Because of (\ref{csai}), we denote in the following: $\pfp_s(a) = a_i$.
-Furthermore, because of (\ref{css}), we denote $\csState(a_i)$ the set of sub-states represented by the process $a_i$ of any cooperative sort $a$ (\pref{def:csState}).
+
+Because of \pref{def:cs}(\ref{csai}), we denote in the following: $\pfp_s(a) = a_i$.
+Furthermore, because of \pref{def:cs}(\ref{css}), we denote $\csState(a_i)$ the set of sub-states represented by the process $a_i$ of any cooperative sort $a$ (\pref{def:csState}).
 \begin{definition}[$\csState : \PHproc \rightarrow \powerset(\PHproc)$]
@@
 
-In the following we will simply write “component” (resp.~“cooperative sort”) instead of “well-formed component” (resp.~“well-formed cooperative sort”).
-The last criterion states that the set of sorts of the considered PH must be divided between components and cooperative sorts.
-
-\begin{criterion}[Components \& cooperative sorts]
+In the following we simply write “component” (resp.~“cooperative sort”) instead of “well-formed component” (resp.~“well-formed cooperative sort”).
+Finally, \pref{cr:compcs} states that the set of sorts of the considered PH must be divided between components and cooperative sorts.
+\begin{criterion}[Components \& cooperative sorts partition]
 \label{cr:compcs}
-\towrite{Problème : sortes non frappées dans $\components$ ou $\cs$ ?}
 %\paragraph{Components \& cooperative sorts}
@@
 
-\todo{The criteria given in this subsection allow to define a class of PH models that share the same behaviour than discrete models.
-The demonstration of this statement is found in Annex B.}
+The criteria given in this subsection allow to define a class of PH models that is (weakly) bisimilar to Asynchronous Boolean Networks
+or, more generally, to the multivalued version of this framework, called Asynchronous Discrete Models (ADM).
+A translation of ADM into PH is given in \pref{suppl:demotrad}, alongside with a demonstration of the weak bisimulation.
 
@@
 
-The previous restrictions lead to a particular class of PH models that can be efficiently studied.
-In this subsection, we give several general theorems that can be derived from these restrictions,
+%The particular class of PH models defined in \pref{ssec:hypothesis} allows to be efficiently studied.
+%The previous restrictions lead to a particular class of PH models that can be efficiently studied.
+In this subsection, we give several general theorems that can be derived from the restrictions of \pref{ssec:hypothesis},
 and which will help building the static analysis of \pref{sec:sa}.
@@
   Given the definition of $\pfp_s(a)$, there exists a scenario $\delta$ updating $a$ in $s$ so that
-  no scenario in $\restriction{\Sce}{1}(s \PHplay \delta)$ can change the active process of $a$.
-  As there is no cycle of actions between the cooperative sorts (\pref{cr:cyclefreeness}) and an updated cooperative sort cannot evolve, at most $|\cs|$ updates can be done.
+  $\forall \delta' \in \restriction{\Sce}{1}(s \PHplay \delta)$, $\PHget{(s \PHplay \delta \PHplay \delta')}{a} = \pfp_s(a)$.
+%  no scenario in $\restriction{\Sce}{1}(s \PHplay \delta)$ can change the active process of $a$.
+  As there is no cycle of actions between the cooperative sorts (\pref{cr:cyclefreeness}) and given that an updated cooperative sort cannot evolve, at most $|\cs|$ updates have to be performed.
 \end{proof}
-\pref{th:hcompcomp} states that for a given state $s$ and for any action $h = \PHhit{a_i}{b_j}{b_k}$ between components,
+
+\pref{th:hcompcomp} states that for a given state $s$, and for any action $h = \PHhit{a_i}{b_j}{b_k}$ where $a$ and $b$ are components,
 if $\PHget{s}{a} = a_i$ and $\PHget{s}{b} = b_j$, then
@@
   $\forall s \in \PHl, \forall a,b \in \components, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh,$\\
-  $(\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j) \Rightarrow (\exists \delta \in \restriction{\Sce}{1}(s), \text{$h$ can be played in $s \PHplay \delta$})$
+  $(\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j) \Rightarrow (\exists \delta \in \restriction{\Sce}{1}(s),
+  (s \PHplay \delta) \PHPtrans (s \PHplay \delta \PHplay h))$
+  %\text{$h$ can be played in $s \PHplay \delta$})$
 \end{theorem}
 \begin{proof}
-  From \pref{th:update}, there exists such a scenario $\delta$ so that: $(s \PHplay \delta) = \update(s)$.
-  As $a,b \in \components$, $a_i \in s \PHplay \delta$ and $b_j \in s \PHplay \delta$.
-  Finally, by definition of $\update(s)$, no action of priority $1$ can be played in $s \PHplay \delta$, thus $h$ can be played in $s \PHplay \delta$.
+  From \pref{th:update}, there exists a scenario $\delta$ with: $(s \PHplay \delta) = \update(s)$.
+  As $a,b \in \components$, $a_i \in (s \PHplay \delta)$ and $b_j \in (s \PHplay \delta)$.
+  Finally, by definition of $\update(s)$, no prioritised action can be played in $(s \PHplay \delta)$, thus $h$ can be played in $(s \PHplay \delta)$.
 \end{proof}
@@
   $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, a \in \cs, b \in \components$\\
-  $(\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j \wedge \pfp_s(a) = a_i) \Rightarrow (\exists \delta \in \restriction{\Sce}{1}(s), \text{$h$ can be played in $s \PHplay \delta$})$
+  $(\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j \wedge \pfp_s(a) = a_i) \Rightarrow (\exists \delta \in \restriction{\Sce}{1}(s),
+  (s \PHplay \delta) \PHPtrans (s \PHplay \delta \PHplay h))$
+%  \text{$h$ can be played in $s \PHplay \delta$})$
 \end{theorem}
 \begin{proof}
-  Similar to the proof of \pref{th:hcompcomp}, and
+  Similar to the proof of \pref{th:hcompcomp};
   %From \pref{th:update}, there exists such a scenario $\delta$ so that: $(s \PHplay \delta) = \update(s)$.
-  as $a_i \in \pfp_s(a)$, $a_i \in s \PHplay \delta$.
+  as $a_i \in \pfp_s(a)$, $a_i \in (s \PHplay \delta)$.
   %Furthermore, $b \in \components$, thus $b_j \in s \PHplay \delta$.

### 2013-04-02 parts/suppl-ph-dn.tex
add notation for a transition in PH
proofreading of section 2

@@
 \section{Weak Bisimulation of Asynchronous Discrete Networks}
-
-\def\DNtrans{\rightarrow_{ADN}}
-\def\DNdef{(\mathbb F, \langle f^1, \dots, f^n\rangle)}
-\def\DNdep{\f{dep}}
-\def\PHPtrans{\rightarrow_{PH}}
-\def\get#1#2{#1[{#2}]}
-\def\encodeF#1{\mathbf{#1}}
-\def\toPH{\encodeF{PH}}
-\def\card#1{|#1|}
-\def\decode#1{\llbracket#1\rrbracket}
-\def\encode#1{\llparenthesis#1\rrparenthesis}
-\def\Hits{\PHa}
-\def\hit{\PHhit}
-\def\play{\cdot}
-
-\todo{synchronise notations and terminology with the main text}
-\todo{define $\PHPtrans$? or defined in main text?}
+\label{suppl:demotrad}
 
@@
 \pref{thm:bisimDN} states the weak bisimulation relation between an ADN and its encoding in
-Process Hitting with $2$ classes of priorities.
-Intuitively, actions updating cooperative sorts being of higher priority, actions updating component
+PH with $2$ classes of priorities.
+Intuitively, actions updating cooperative sorts being prioritised, actions updating component
 sorts follow strictly the possible transitions of the ADN.

### 2013-04-02 parts/sa.tex
proofreading of section 3

--- 2013-04-02 parts/sa.tex
@@
 
-The reachability of a process $a_i$ of a sort $a$ from another process $a_j$ is called an objective and is denoted $\PHobjp{a}{j}{i}$ (\pref{def:obj}).
+The reachability of a process $a_j$ of a given sort $a$ from another process $a_i$ is called an objective and is denoted $\PHobjp{a}{j}{i}$ (\pref{def:obj}).
 \begin{definition}[Objective ($\Obj$)]
@@
   and $P$ is \emph{trivial} if $a_i = a_j$.
-\end{definition}
-\noindent
+
   We define an \emph{objective sequence} as a sequence of objectives in which each objective target must be equal to the previous objective bounce of the same sort, if it exists.
   The set of all objective sequences is denoted by $\OS$.
+\end{definition}
 
-A context (\pref{def:context}) is an extension of the notion of state that can stand for a set of possible initial states.
-We also extend the override operator to a context and a set of processes (\pref{def:ctxcap}).
+A context (\pref{def:context}) extends the notion of state to a set of possible initial states.
+%the extension of the override operator follows (\pref{def:ctxcap}).
+We also extend the override operator to contexts (\pref{def:ctxcap}).
 \begin{definition}[Context ($\Ctx$)]
@@
 \label{def:ctxcap}
-  For a given context $\ctx\in\Ctx$ and a set of processes $ps \in \powerset(\PHproc)$,
+  For any $\ctx\in\Ctx$ and set of processes $ps \in \powerset(\PHproc)$,
   the override of $\ctx$ by $ps$ is noted $\ctx \Cap ps$ and is defined by:
@@
 
-Finally, bounce sequences on a sort $a$ (\pref{def:bs}) are sequences of actions hitting $a$ in which the bounce process of each action is the hitter process of the following action.
-Bounce sequences are used to find sequences of actions that locally solve a given objective.
+Finally, a bounce sequence on a sort $a$ (\pref{def:bs}) is a sequence of actions hitting $a$
+in which the bounce process of each action is the hitter process of the following action.
+Bounce sequences are used to find local solutions to a given objective.
+%Bounce sequences are used to find sequences of actions that locally solve a given objective.
 %solve an objective locally, by finding the sequences of actions that allow to reach a process.
-A bounce sequence can be abstracted into its sets of hitters that are not in sort $a$.
+A bounce sequence can be abstracted into sets of all its hitters that are not in sort $a$.
 %of every action that are different from the considered sort (\pref{def:aBS}).
@@
   \]
-  Obviously, $\emptyseq \in \BS(\obj{a_i}{a_i})$; and $\BS(\obj{a_i}{a_j}) = \emptyset$ if there is no way to reach $a_j$ from $a_i$.
+%  Obviously, $\emptyseq \in \BS(\obj{a_i}{a_i})$; and $\BS(\obj{a_i}{a_j}) = \emptyset$ if there is no way to reach $a_j$ from $a_i$.
+  $\BS(\obj{a_i}{a_j}) = \emptyset$ if there is no way to reach $a_j$ from $a_i$ and $\emptyseq \in \BS(\obj{a_i}{a_i})$.
 \end{definition}
 %
-\begin{definition}[$\aBS:\Obj \mapsto \powerset(\Sol)$]
+\begin{definition}[$\aBS:\Obj \rightarrow \powerset(\Sol)$]
 \label{def:aBS}
@@
 In \pref{def:uconcr}, we define $\uconcr(\w)$ as equal to $\concr(\w)$ if and only if $\concr(\w)$ contains scenarios starting from all states $s \subseteq \ctx$.
-\pref{th:uconcr-ctx} will be used to over-approximate the initial context $\ctx$.
+\pref{th:uconcr-ctx} is used to over-approximate the initial context $\ctx$.
 %if such a scenario exists in all states $s \subseteq \ctx$.
@@
 %
-\begin{definition}[$\uconcr: \OS \mapsto \powerset(\Sce)$]
+\begin{definition}[$\uconcr: \OS \rightarrow \powerset(\Sce)$]
 \label{def:uconcr}
@@
 
-For any objective $P$ and context $\ctx$, \pref{def:maxCont} allows to obtain the set of processes of sort $\PHsort(P)$ that are required to solve $P$ in $\ctx$,
-given by $\gCont_\ctx(\PHsort(P), P)$.
+For any objective $P$ and context $\ctx$, \pref{def:maxCont} allows to obtain the set of processes of sort $\PHsort(P)$ are required to solve $P$ in $\ctx$, given by $\gCont_\ctx(\PHsort(P), P)$.
 \begin{comment}
@@
 %
-\begin{definition}[$\gCont_\ctx : \Sigma \times \Obj \mapsto \powerset(\PHproc)$]
+\begin{definition}[$\gCont_\ctx : \Sigma \times \Obj \rightarrow \powerset(\PHproc)$]
   \label{def:maxCont}
@@
 The reachability of a process $a_i$ is approximated by the ability to solve all objectives $\PHobjp{a}{j}{i}$ so that $a_j$ is in the initial context.
-To this end, the abstractions of bounce sequences (\pref{def:aBS}) solving these objectives are computed, leading to new required processes, and thus new objectives in other sorts.
+To this end, the abstractions of bounce sequences (\pref{def:aBS}) solving these objectives are computed, leading to new required processes, and thus new objectives on other sorts.
 Thus, the graph of local causality $\cwB = (\V, \E)$ defined in \pref{def:glc} is a graph where $\V \subset \Proc \cup \Obj \cup \Sol$ and $\E \subset \V \times \V$
-in which edges link any required processes $a_i \in \Proc$ to all corresponding objectives $P \in \Obj$,
+in which edges link any required process $a_i$ in $\Proc$ to all corresponding objectives $P$ in $\Obj$,
 and any objective $P$ to abstractions of bounce sequences $ps \in \Sol$ (\pref{def:aBS}) solving this objective;
@@
 If the solving of an objective $P$ requires a process of $\PHsort(P)$, a continuity edge is added to re-target this objective (\pref{def:maxCont}).
-Finally, as the active process of every sort may evolve, the graph $\cwB$ is iteratively saturated by every process it contains,
-by overriding its initial context $\ctx$ with $\allprocs(\V, \E)$, defined by:
+Finally, as the active process of every sort may evolve, $\cwB$ is obtained iteratively by saturation with every process it contains,
+\ie by overriding its initial context $\ctx$ by $\allprocs(\V, \E)$, defined by:
 %in which the initial context $\ctx$ is updated by iteratively adding every process that appears in the graph ($\allprocs$).
@@
   The graph of local causality $\cwB = (\Bv, \Be)$ is defined as: $\cwB = \lfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs(\myB)}}$,
-  where $\myB = (\cwV, \cwE)$ is the smallest graph where: $\cwV = \VProc \cup \VObj \cup \VSol$ with $\VProc \subset \PHproc$, $\VObj \subset \Obj$, $\VSol \subset \Sol$ and $\cwE \subset \cwV \times \cwV$ so that:
+  where $\myB = (\cwV, \cwE)$ is the smallest graph where:
+  %$\cwV = \VProc \cup \VObj \cup \VSol$ with $\VProc \subset \PHproc$, $\VObj \subset \Obj$, $\VSol \subset \Sol$ and $\cwE \subset \cwV \times \cwV$
+  $\cwV \subset \Proc \cup \Obj \cup \Sol$ and $\cwE \subset \cwV \times \cwV$
+  so that:
   \begin{align}
@@
     a \in \components \wedge a_i \in \VProc \wedge a_j \in \ctx &\Rightarrow (a_i, \PHobjp{a}{j}{i}) \in \cwE \label{eq:EReq} \\
+%      \{ (a_i, ps) \in \Proc \times \powerset(\PHproc) \mid a \in \cs \wedge a_i \in \V \wedge ps \in \csState(a_i) \} &\subset \E\\ % ReqSolPrio
+    a \in \cs \wedge a_i \in \VProc \wedge ps \in \csState(a_i) &\Rightarrow (a_i, ps) \in \cwE \label{eq:EPrio} \\
 %    \{ \PHobjp{a}{j}{i} \in \Obj \mid (a_i, \PHobjp{a}{j}{i}) \in \E \} &\subset \V\\
 %      \{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid P \in \V \wedge q \in \gCont_\ctx(\PHsort(P), P) \} &\subset \E\\ % Cont
-    P \in \VObj \wedge q \in \gCont_\ctx(\PHsort(P), P) &\Rightarrow (P, \PHobj{q}{\PHbounce(P)}) \in \cwE \label{eq:ECont} \\
-%      \{ (a_i, ps) \in \Proc \times \powerset(\PHproc) \mid a \in \cs \wedge a_i \in \V \wedge ps \in \csState(a_i) \} &\subset \E\\ % ReqSolPrio
-    a \in \cs \wedge a_i \in \VProc \wedge ps \in \csState(a_i) &\Rightarrow (a_i, ps) \in \cwE \label{eq:EPrio}
+    P \in \VObj \wedge q \in \gCont_\ctx(\PHsort(P), P) &\Rightarrow (P, \PHobj{q}{\PHbounce(P)}) \in \cwE \label{eq:ECont}
   \end{align}
@@
 elements in $\Obj$ are the objectives to reach these processes
-and elements in $\Sol$ are the sets of processes that are the solutions to these objectives.
-\pref{eq:ESol1} links an objective $P$ to its solutions in $\BS(P)$,
-\pref{eq:ESol2} links a solution $ps$ to the processes $a_i \in ps$ it contains and
-\pref{eq:EReq} links a required process $a_i$ of a component to all objectives $\PHobjp{a}{j}{i}$ with $a_j \in \ctx$.
-If the resolution of an objective $P$ may require a process of $\PHsort(P)$, then \pref{eq:ECont} re-targets this objective ($\gCont$).
-Finally, \pref{eq:EPrio} links a required process $a_i$ of a cooperative sorts to its solutions in $\csState(a_i)$.
+and elements in $\Sol$ are the sets of processes that allow to solve these objectives.
+\pref{eq:ESol1} links an objective $P$ to its solutions in $\BS(P)$
+and \pref{eq:ESol2} links a solution $ps$ to the processes $a_i \in ps$ it contains.
+Then, \pref{eq:EReq} links a required component process $a_i$ to all objectives $\PHobjp{a}{j}{i}$ with $a_j \in \ctx$
+while \pref{eq:EPrio} links a required cooperative sort process $a_i$ to its solutions in $\csState(a_i)$.
+Finally, if the resolution of an objective $P$ requires a process of $\PHsort(P)$, then \pref{eq:ECont} re-targets this objective ($\gCont$).
 
-In the following, we denote:
+%In the following, we denote:
 %$\BvProc = \Bv \cap \PHproc$, $\BvObj = \Bv \cap \Obj$ and $\BvSol = \Bv \cap \Sol$.
-$\Bee{X}{Y} = \Be \cap (X \times Y)$, with $X, Y$ amongst $\PHproc$, $\Obj$ and $\Sol$.
+%$\Bee{X}{Y} = \Be \cap (X \times Y)$, with $X, Y$ amongst $\PHproc$, $\Obj$ and $\Sol$.
 %
@@
 %We define in \pref{def:coherent} the notion of coherent edge in the graph of local causality.
-In the graph of local causality, an edge linking a process of a cooperative sort to a solution set $ps$ is coherent if none of the successor processes of $ps$ conflict with the processes of $ps$ (\pref{def:coherent}).
+In the graph of local causality, an edge linking a process of a cooperative sort to a solution set $ps$ is said coherent (\pref{def:coherent}) if none of the processes in $ps$ conflict with the children processes of $ps$.
 Then, \pref{th:approxinf} gives a sufficient condition for the concretization of a sequence of objectives in a given context,
@@
   An edge $(x, y) \in \cwE$ is said coherent if and only if:
-  $(x, y) \in \Bee{\Proc}{\Sol} \Rightarrow y$ has no process successor $a_j \in \Bv \cap \Proc$ so that $\exists a_i \in y$, $a_i \neq a_k$.
+%  $(x, y) \in \Bee{\Proc}{\Sol} \Rightarrow y$ has no process successor $a_j \in \Bv \cap \Proc$ so that $\exists a_i \in y$, $a_i \neq a_k$.
+  $(x, y) \in \Be \cap (\Proc \times \Sol) \Rightarrow y$ has no children process $a_j \in \Bv \cap \Proc$ so that $\exists a_i \in y$, $a_i \neq a_k$.
 \end{definition}
@@
 \begin{example}
-  As an example showing the usefulness of our method, we can consider \pref{fig:ph-livelock}.
-  Let $\PH' = (\PHs, \PHl, \PHh'^{\langle 1 \rangle})$ be the “flattened” version of $\PH$, that is: $\PHh'^{\langle 1 \rangle} = \PHh^{(1)} \cup \PHh^{(2)}$.
-  As this PH model contains only $1$ priority, it is equivalent to a PH in the semantics without priorities.
-  The under-approximation such models developed in~\cite{PMR12-MSCS} concludes that $c_1$ is reachable.
-  This is due to an over-approximation of the behaviours inherent to cooperative sorts in the semantics without priorities.
+  %As an example showing the usefulness of our method, we can consider \pref{fig:ph-livelock}.
+  Let $\PH' = (\PHs, \PHl, \PHh'^{\langle 1 \rangle})$ be the “flattened” version of the PH in \pref{fig:ph-livelock}, that is: $\PHh'^{\langle 1 \rangle} = \PHh^{(1)} \cup \PHh^{(2)}$,
+  %As this PH model contains only one class of priority, 
+  which is equivalent to a PH in the semantics without priorities.
+  The under-approximation on such models developed in~\cite{PMR12-MSCS} concludes that $c_1$ is reachable from $\ctx = \PHstate{a_1, b_0, c_0, ab_{10}}$;
+  this is due to an over-approximation of the behaviours inherent to cooperative sorts in the semantics without priorities.
 
@@
   Indeed, the under-approximation given in \pref{th:approxinf} does not conclude regarding the reachability of $c_1$,
-  as one of the edges of the resulting graph of local causality is not coherent (\pref{def:coherent}).
-  The graph of local causality for this example is given in \pref{fig:sa-livelock}.
+  as one of the edges of the resulting graph of local causality is not coherent (\pref{def:coherent}),
+  as shown in in \pref{fig:sa-livelock}.
+
+  We note that if the actions $\PHhit{a_0}{b_0}{b_1}$ and $\PHhit{b_0}{a_0}{a_1}$ are replaced by the self-hits
+  $\PHhit{a_0}{a_0}{a_1}$ and $\PHhit{b_0}{b_0}{b_1}$,
+  then \pref{th:approxinf} concludes that $c_1$ is reachable from $\ctx$.
 \end{example}
@@
 
-\todo{La méthode permet aussi de conclure sur l'accessilibité d'un état (global ou partiel)}
+\subsection{Reachability of a state}
+
+\newcommand{\total}{\tau}
+\newcommand{\reach}{\sigma}
+
+The semantics of PH with $2$ classes of priorities studied in this paper allows to model cooperative sorts accurately representing a coherent configuration of a set of sorts.
+%As the method presented in this section allows to efficiently conclude on the reachability of a process,
+Therefore, we can derive a new method to conclude about the reachability of a state (considering only components).
+Indeed, let $\PH = (\PHs, \PHl, (\PHh^{(1)}, \PHh^{(2)}))$ be a PH and suppose that we want to study the reachability of a state $s \in \PHl$.
+Let $\PH' = (\PHs', \PHl', (\PHh'^{(1)}, \PHh'^{(2)}))$
+with: $\PHs' = \PHs \cup \{ \total, \reach \}$ and $\PHl' = \PHl \times \PHl_\total \times \PHl_\reach$,
+where $\total$ is a cooperative sort on all components $\components$ of $\PH$ (thus $\PHl_\total = \underset{a \in \components}{\times} \PHl_a$)
+and $\reach$ is a component with $\PHl_\reach = \{ \reach_0, \reach_1 \}$;
+furthermore, $\PHh'^{(1)}$ is the set $\PHh^{(1)}$ completed with all actions updating the cooperative sort $\total$,
+and $\PHh'^{(2)} = \PHh^{(2)} \cup \{ \PHhit{\pfp_s(\total)}{\reach_0}{\reach_1} \}$.
+
+Given an initial context $\ctx$, the reachability of $s$ in $\PH$ is equivalent to the concretization of $\PHobjp{\reach}{0}{1}$ in $\PH'$ from the initial context $\ctx \cup \{ \reach_0 \}$ (the initial state of $\total$ does not matter), which can be efficiently under-approximated using \pref{th:approxinf}.
+Indeed, the additional action $\PHhit{\pfp_s(\total)}{\reach_0}{\reach_1}$ in $\PHh'^{(2)}$ allows to conclude on the reachability of process $\pfp_s(\total)$, that is, on the reachability of the state $s$ (considering only the components).
+
+%It is also possible to compute the reachability of a partial state
+%by modelling in $\total$ the cooperation of a subset of $\components$,
+It is also possible to compute the reachability of a set of states $S \subset \PHl$ by creating several actions $\PHhit{\total_s}{\reach_0}{\reach_1}$ in $\PHh^{(2)}$ for each state $s \in S$.

### 2013-04-02 parts/ccl.tex
proofreading of conclusion

--- 2013-03-28 parts/ccl.tex
@@
 \section{Discussion \& Conclusion}\label{sec:ccl}
-\towrite{Pistes :
-\begin{itemize}
-  \item Plus de classes de priorités ?
-  \item Modèles Zeno (système de précédences et prise en compte des états globaux)
-\end{itemize}
-}
+
+We introduced a new semantics to include priorities into the Process Hitting framework, which prove especially useful to model cooperations.
+Then, we developed a method to efficiently perform a reachability analysis of a sequence of objectives in a restricted class of Process Hitting models,
+but it is also useful to establish the reachability of a partial state.
+This analysis is based on an under-approximation of the true reachability solutions.
+%; however, the most usual cases can be handled.
+The method has been implemented as an extension of the existing “ph-reach” tool into the existing Pint\footnote{\url{http://processhitting.wordpress.com/}} library.
+\towrite{Déplacer dans la section exemples ?}
+
+We showed that the class of Process Hitting models that can be handled by the aforementioned method are equivalent to Asynchronous Discrete Networks, and therefore to Asynchronous Boolean Networks.
+This allows to efficiently compute reachability results on large biological models provided that they are equivalent to Asynchronous Discrete Networks and that a translation from the original framework into a Process Hitting model is possible.
+Such a translation for interaction graphs of Thomas modelling was proposed in~\cite{PMR10-TCSB} \towrite{[À garder ?] and is made possible by the Pint software}.
+
+Further work can be derived from what have been presented in this paper.
+The over-approximation on Process Hitting models without priorities proposed in~\cite{PMR12-MSCS}
+is still accurate in the framework with priorities (by “flattening” all actions),
+but may be refined given the restrictions proposed in this paper.
+%but turns out to be too wide even in some obvious cases that are consequently not conclusive.
+%This approximation may be refined in order to better fit the introduction of priorities, and mak the overall approximation approach 
+%and mode precisely the class of models studied in this paper.
+Furthermore, a more general under-approximation could be developed in order to handle a larger class of Process Hitting models, that is,
+models with more than two classes of priorities, that do not only contain components of cooperative sorts, or whose behaviour may contain cycles or cyclic attractors.
+Finally, in order to take into account quantitative data in transition delays, the overall approximation method could be extended to handle evolution that are chronometric instead of only chronologic.

### 2013-04-02 parts/def-ph.tex
proofreading of section 3
proofreading of conclusion

@@
 
-\begin{figure}
+\begin{figure}[p]
   \centering
+  \scalebox{1.5}{
   \begin{tikzpicture}
@@
   \end{tikzpicture}
+  }
   \caption{
@@
 %and all of its processes represents at least one sub-state of its neighbourhood. \towrite{reformuler ou supprimer}
-\begin{definition}[$\pfp : \PHl \times \PHs \rightarrow \powerset(\PHproc)$]
+\begin{definition}[$\pfp : \PHs \rightarrow \powerset(\PHproc)$]
 \label{def:pfp}
-  For all $s \in \PHl$ and $a \in \PHs$,
+  For all $a \in \PHs$,
   \begin{align*}
@@
 
+\begin{example}
+  The PH in \pref{fig:ph-livelock} contains three components $a$, $b$ and $c$ and a cooperative sort $ab$ that models cooperation between sorts $a$ and $b$.
+\end{example}
+
 The criteria given in this subsection allow to define a class of PH models that is (weakly) bisimilar to Asynchronous Boolean Networks
-or, more generally, to the multivalued version of this framework, called Asynchronous Discrete Models (ADM).
-A translation of ADM into PH is given in \pref{suppl:demotrad}, alongside with a demonstration of the weak bisimulation.
+or, more generally, to the multivalued version of this framework, called Asynchronous Discrete Models (ADN).
+A translation of ADN into PH is given in \pref{suppl:demotrad}, alongside with a demonstration of the weak bisimulation.
 

### 2013-04-02 parts/def-ph.tex
note on inconclusiveness and TODO on complexity

@@
 special treatment regarding the semantics of related actions.
-Furthermore, it is possible to chain cooperative sorts in order to express more complex cooperations
-or to decrease the number of processes created within each cooperative sort,
-as this number is exponential in the number of sorts that cooperate.
+Furthermore, it is possible to chain cooperative sorts in order to express more complex cooperations or
+to decrease the number of processes created within each cooperative sort,
+as the static analysis method developed in \pref{sec:sa} does not suffer from the number of sorts but from the number of processes in one sort.
+%as this number is exponential in the number of sorts that cooperate.
 %to prevent the combinatoric explosion of the number of processes created within cooperative sorts.

### 2013-04-02 parts/sa.tex
note on inconclusiveness and TODO on complexity

@@
 
+\todo{Complexité de la construction du GLC}
+
 %In the following, we denote:
@@
 
+\todo{Complexité de la vérification du GLC}
+
 \begin{example}
@@
   as shown in in \pref{fig:sa-livelock}.
+  (However, from the inconclusiveness of \pref{th:approxinf}, one cannot conclude about the unreachability of $c_1$.
+  Such analysis should be driven for instance with over-approximation methods developed in~\cite{PMR10-TCSB}.)
 

### 2013-04-02 parts/def-ph.tex
compress

@@
 which would allow the play of an infinite sequence of prioritised actions in “zero time”.
-\begin{criterion}[2 priorities]
+\begin{criterion}[2 classes of priorities]
 \label{cr:2prio}
@@
   %Formally :
-  $$\exists N \in \sN, \forall \in \PHl, \forall \delta \in \restriction{\Sce}{1}(s), |\delta| \leq N \enspace.$$
+  $\exists N \in \sN, \forall \in \PHl, \forall \delta \in \restriction{\Sce}{1}(s), |\delta| \leq N$.
 \end{criterion}
@@
   A sort $a \in \PHs$ is a \emph{well-formed component} if and only if:
-  $$\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) = 2 \enspace.$$
+  $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) = 2$.\\
   We call $\components$ the set of well-formed components.
@@
   There is no cycle in chains of actions:
-  $$\forall a \in \PHs, \PHh(a, a) = \emptyset \enspace.$$
+  $\forall a \in \PHs, \PHh(a, a) = \emptyset$.
 \end{criterion}

### 2013-04-02 parts/def-ph.tex
comments cealnup

@@
 This class of models is equivalent to Asynchronous Discrete Networks.
-%\towrite{Démo équivalence avec réseaux discret : ici ou dans la section 3 ?}
 
@@
 \label{ssec:PH}
-%\towrite{Reformuler (actuellement trop proche de CMSB)}
 A PH with $k$ classes of priorities (\pref{def:ph}), also simply called “PH” in the following when it is not ambiguous, gathers a finite number of concurrent \emph{processes} divided into a finite set of \emph{sorts}.
 A process belongs to a unique sort and is noted $a_i$ where $a$ is the sort and $i$ the identifier of the process within the sort $a$.
-%At any time, one and only one process of each sort is present; a state of the PH thus corresponds to the set of such processes.
 Each process stands for a kind of “activity level” of its sort; a state of the PH thus corresponds to a set of processes containing exactly one process of each sort.
@@
 
-\begin{definition}[Process Hitting with $k$ classes of priorities]% \towrite{Revoir terminologie}
+\begin{definition}[Process Hitting with $k$ classes of priorities]
 \label{def:ph}
@@
     \item $\PHs \DEF \{a,b,\dots\}$ is the finite set of \emph{sorts},
-    %$\PHl \DEF \prod_{a \in \PHs} \PHl_a$
     \item $\PHl \DEF \underset{a \in \PHs}{\times} \PHl_a$ is the finite set of \emph{states}, where $\PHl_a = \{a_0 ; \ldots ; a_{l_a}\}$ is the finite set of \emph{processes} of sort $a \in \PHs$ and $l_a \in \sN^*$.
@@
 The sort of a process $a_i$ is referred to as $\PHsort(a_i) = a$.
-%and the set of sorts present in an action $h \in \PHa$ as $\PHsort(h) = \{\PHsort(\PHhitter(h)),\PHsort(\PHtarget(h))\}$.
 Given a state $s\in \PHl$, the process of sort $a \in \PHs$ present in $s$ is denoted by $\PHget{s}{a}$, that is the $a$-coordinate of the state $s$.
@@
   Moreover, we denote: $s \PHPtrans (s \PHplay h)$.
-%  If $s, s' \in \PHl$ are two states and $\exists h \in \PHh$, $h$ is playable in $s$ and $s' = s \PHplay h$, then we denote: $s \PHPtrans s'$.
-%  For the sake of clarity, for all $h, h'\in\PHa$, $((s\PHplay h)\PHplay h')$ is abbreviated as $(s\PHplay h\PHplay h')$.
-%\begin{definition}[Scenario ($\Sce$)]
-%\label{def:scenario}
 
@@
   a \emph{scenario} $\delta$ from $s$ is a sequence of actions of $\PHh$ that can be played successively in $s$.
-%  so that for all $n \in \indexes{\delta}$,
-%  $a_i = \PHhitter(\delta_n)$ (resp. $\PHtarget(\delta_n)$) $\Rightarrow \last_a(\delta_{1..n-1}) \in \{ \varnothing, a_i \}$.
   The set of all scenarios from $s$ is noted $\Sce(s)$.
-%\end{definition}
 \end{definition}
@@
 In \pref{def:restriction}, we define the $n$-reduction of a given PH as the PH with $n$ classes of priorities in which only actions of priority lower or equal to $n$ are kept.
-\begin{definition}[PH $n$-reduction] %\towrite{Revoir terminologie : “reduction” ? “restriction” ?}
+\begin{definition}[PH $n$-reduction]
 \label{def:restriction}
-  If $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$ is a Process Hitting with $k$ classes of priorities and $n \in \segm{1}{k}$, we denote $\restriction{\PH}{n}$ %\towrite{$\PH_{|n}$ $\PH'$}
+  If $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$ is a Process Hitting with $k$ classes of priorities and $n \in \segm{1}{k}$, we denote $\restriction{\PH}{n}$
   the $n$-reduction of $\PH$.
-  %the following Process Hitting with $n$ priorities:
   $\restriction{\PH}{n} = (\PHs; \PHl; \PHa'^{\langle n \rangle})$ is a PH with $n$ classes of priorities with:
@@
   Furthermore, we denote: $\restriction{\Sce}{n}(s)$ the set of scenarios from $s$ in $\restriction{\PH}{n}$.
-  %made of actions of $\PHa'^{\langle n \rangle}$.
 \end{definition}
@@
     Greyed processes stand for a possible state $s = \PHstate{a_1, b_0, c_0, ab_{10}}$.
-    %This PH notably contains three well-formed components ($a$, $b$ and $c$) and a well-formed cooperative sort ($ab$).
   }
@@
 
-%\towrite{Sortes coopératives avec mise à jour prioritaire (pas de décalage temporel)}
 Cooperation between processes to make another process bounce can be expressed in PH by building a \emph{cooperative sort}, as described in \cite{PMR10-TCSB}.
@@
 as the static analysis method developed in \pref{sec:sa} does not suffer from the number of sorts but from the number of processes in one sort.
-%as this number is exponential in the number of sorts that cooperate.
-%to prevent the combinatoric explosion of the number of processes created within cooperative sorts.
-%Such constructions are helpful as the static analysis of dynamics developed does not suffer from the number of sorts,
-%but on the number of processes within a single sort.
-
-\begin{comment}
-When the number of cooperating processes is large, it is possible to chain several cooperative sorts
-to prevent the combinatoric explosion of the number of processes created within cooperative sorts.
-For instance, if $b_1$, $c_1$, and $d_1$ cooperate, one can create a cooperative sort $bc$ with 4
-processes reflecting the presence of $b_1$ and $c_1$, and a cooperative sort $bcd$ with 4 processes
-reflecting the presence of $bc_{11}$ and $d_1$.  Such constructions are helpful in PH
-as the static analysis of dynamics developed in \cite{PMR12-MSCS} does not suffer from the number of
-sorts, but on the number of processes within a single sort.
-\end{comment}
 
@@
 
-\begin{comment}
-\begin{example}
-The PH in \pref{fig:runningPH-2} results from the refinement of the PH in \pref{fig:runningPH-1}
-where several cooperations have been specified.
-In particular, the bounce to $a_2$ is the result of a cooperation between $b_1$ and $c_1$; and the
-bounce to $a_0$ of a cooperation between $b_0$ and $c_0$.
-Hence, this PH expresses a BRN where $a$ requires both $b$ and $c$ active to reach its
-highest level, and $a$ does not become inactive unless both $b$ and $c$ are inactive.
-\end{example}
-\end{comment}
-
 \todo{Nouvelle section pour les hypothèses + conséquences ?}
 \label{ssec:hypothesis}
-\subsection{Restrictions} %\towrite{Reformuler}
+\subsection{Restrictions}
 
@@
 \label{cr:2prio}
-%\paragraph{2 priorities}
   In this paper, we only consider Process Hitting with $2$ classes of priorities:
@@
 \label{cr:bounded}
-%\paragraph{Bounded termination}
   The dynamics of $\restriction{\PH}{1}$ contains no cycles:
-  %Cycles are still allowed in $\PH$ however.
-  %Formally :
   $\exists N \in \sN, \forall \in \PHl, \forall \delta \in \restriction{\Sce}{1}(s), |\delta| \leq N$.
@@
 In \pref{def:component} we define a well-formed component as a sort that is hit only by unprioritised actions, or that no action hits.
-%A well-formed component may stand for a real biological component (protein, light, nutriment…).
 \begin{definition}[Well-formed component ($\components$)]
@@
 and \pref{cr:cyclefreeness} prevents the presence of cycles in these chains.
-%as prioritised actions are used to update non-biological components.
-%this restriction will prevent incoherent states between cooperative sorts ().
 \begin{definition}
@@
 \label{cr:cyclefreeness}
-%\paragraph{Cycle-freeness between actions of priority $1$}
   There is no cycle in chains of actions:
@@
 in a way that its local steady-states efficiently represents all configurations of its neighbouring sorts.
-%any sub-state of its neighbourhood is represented by exactly one local steady state in this sort,
-%and all of its processes represents at least one sub-state of its neighbourhood. \towrite{reformuler ou supprimer}
 \begin{definition}[$\pfp : \PHs \rightarrow \powerset(\PHproc)$]
@@
     \item $\exists b \in \PHs, \PHh(b, a) \neq \emptyset$
-%    \item $\forall s \in \underset{b \in \Vs(a)}{\times} \PHl_b, |\pfp_s(a)| = 1$
-%    \item $\forall a_i \in \PHl_a, \exists s \in \underset{b \in \Vs(a)}{\times} \PHl_b, \pfp_s(a) = \{ a_i \}$
     \item \label{csai} $\forall s \in \PHl, \exists a_i \in \PHl_a, \pfp_s(a) = \{ a_i \}$
@@
 \label{cr:compcs}
-%\paragraph{Components \& cooperative sorts}
-  %The studied PH is a PH with 2 priorities, and it is only composed of well-formed components and cooperative sorts:
   $$\PHs = \components \cup \cs \wedge \components \cap \cs = \emptyset$$
@@
 
-%The particular class of PH models defined in \pref{ssec:hypothesis} allows to be efficiently studied.
-%The previous restrictions lead to a particular class of PH models that can be efficiently studied.
 In this subsection, we give several general theorems that can be derived from the restrictions of \pref{ssec:hypothesis},
@@
   $\forall \delta' \in \restriction{\Sce}{1}(s \PHplay \delta)$, $\PHget{(s \PHplay \delta \PHplay \delta')}{a} = \pfp_s(a)$.
-%  no scenario in $\restriction{\Sce}{1}(s \PHplay \delta)$ can change the active process of $a$.
   As there is no cycle of actions between the cooperative sorts (\pref{cr:cyclefreeness}) and given that an updated cooperative sort cannot evolve, at most $|\cs|$ updates have to be performed.
@@
 \pref{th:hcscomp} states the same if $a$ is a cooperative sort, under the condition that $a$ is updated in $s$.
-%$a_i$ reflects the state of the neighborhood of $a$.
 \begin{theorem}
@@
   (s \PHplay \delta) \PHPtrans (s \PHplay \delta \PHplay h))$
-  %\text{$h$ can be played in $s \PHplay \delta$})$
 \end{theorem}
@@
   (s \PHplay \delta) \PHPtrans (s \PHplay \delta \PHplay h))$
-%  \text{$h$ can be played in $s \PHplay \delta$})$
 \end{theorem}
@@
   Similar to the proof of \pref{th:hcompcomp};
-  %From \pref{th:update}, there exists such a scenario $\delta$ so that: $(s \PHplay \delta) = \update(s)$.
   as $a_i \in \pfp_s(a)$, $a_i \in (s \PHplay \delta)$.
-  %Furthermore, $b \in \components$, thus $b_j \in s \PHplay \delta$.
-  %Finally, by definition of $\update(s)$, no action of priority $1$ can be played in $s \PHplay \delta$, thus $h$ can be played in $s \PHplay \delta$.
 \end{proof}
-
-\begin{comment}
-\pref{th:autohits} states that any sequence $\zeta$ of self-actions on a well-formed component can be played eventually.
-\begin{theorem}
-\label{th:autohits}
-  Let $a \in \PHs$, $s \in \PHl$ and $\zeta \in \BS$ so that $\forall i \in \indexes{\zeta}, \PHsort(\PHhitter(\zeta_i)) = \PHsort(\PHtarget(\zeta_i)) = a$.
-  $\exists (\delta_i)_{i \in \indexes{\zeta}} \in \restriction{\Sce}{1}$ so that $\forall i \in \indexes{\zeta}$, $\zeta_i$ can be played in $s \PHplay \delta_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_i$.
-\end{theorem}
-\begin{proof}
-  With \pref{th:hcompcomp} applied iteratively.
-\end{proof}
-\end{comment}

### 2013-04-02 parts/sa.tex
comments cealnup

@@
 A context (\pref{def:context}) extends the notion of state to a set of possible initial states.
-%the extension of the override operator follows (\pref{def:ctxcap}).
 We also extend the override operator to contexts (\pref{def:ctxcap}).
@@
 We denote then: $\delta \in \Sce(\ctx)$,
-%$\supp(\delta) \subseteq \ctx$. 
 and the play of $\delta$ in $\ctx$ is $\ctx \PHplay \delta = \ctx \Cap \ceil(\delta)$,
 where $\ceil(\delta)$ is the set containing the last process (hitter or bounce) of each sort present in $\delta$.
-
-\begin{comment}
-  \begin{definition}[Objective sequence ($\OS$)]
-  \label{def:OS}
-  \towrite{Simplifier / réécrire en dehors d'une def}
-    An \emph{objective sequence} is a sequence $\w = P_1 \concat \dots \concat P_{|\w|}$,
-    where $\forall n \in \indexes{\w}, \w_n \in \Obj$ and $a_i = \PHtarget(\w_n) \Rightarrow \last_a(\w_{1..n-1}) \in \{ \varnothing, a_i \}$.
-    The set of all objective sequences is denoted by $\OS$.
-    The definitions of $\last_a$ \todo{À définir}, $\first_a$ \todo{À définir}, $\supp$ \todo{À définir} and $\ceil$ \todo{À définir}
-    are simply derived by omitting the case of hitters.
-  \end{definition}
-\end{comment}
 
@@
 Bounce sequences are used to find local solutions to a given objective.
-%Bounce sequences are used to find sequences of actions that locally solve a given objective.
-%solve an objective locally, by finding the sequences of actions that allow to reach a process.
 A bounce sequence can be abstracted into sets of all its hitters that are not in sort $a$.
-%of every action that are different from the considered sort (\pref{def:aBS}).
 This abstraction allows to propagate an objective into objectives on other sots.
@@
   \]
-%  Obviously, $\emptyseq \in \BS(\obj{a_i}{a_i})$; and $\BS(\obj{a_i}{a_j}) = \emptyset$ if there is no way to reach $a_j$ from $a_i$.
   $\BS(\obj{a_i}{a_j}) = \emptyset$ if there is no way to reach $a_j$ from $a_i$ and $\emptyseq \in \BS(\obj{a_i}{a_i})$.
@@
 \pref{th:uconcr-ctx} is used to over-approximate the initial context $\ctx$.
-%if such a scenario exists in all states $s \subseteq \ctx$.
-%
-\begin{comment}
-\begin{definition}[$\concr: \OS \mapsto \powerset(\Sce)$]
-\label{def:concr}
-\towrite{Simplifier ? Supprimer la def formelle ?}
-  For a given $\w \in \OS$, $\concr(\w)$ is the set of scenarios concretising $\w$ in the context $\ctx$:
-  \begin{align*}
-    \concr(\w) = \{ \delta \in \Sce \mid & (\w^\vartriangle = \emptyseq \wedge \delta = \emptyseq) 
-      \vee (\w^\vartriangle \neq \emptyseq \wedge \supp(\delta) \subseteq \ctx
-    \\ &
-      \wedge \exists \phi:\indexes{\w} \mapsto \indexes{\delta}, (\forall n, m \in \indexes{\w}, n < m \Leftrightarrow \phi(n) \leq \phi(m)) 
-    \\ &
-      \wedge \forall n \in \indexes{\w}, \PHbounce(\w_n) \in \ctx \PHplay \delta_{1..\phi(n)})
-    \}
-    \enspace,
-  \end{align*}
-  where $\omega^\vartriangle$ refers to the sequence of objectives $\omega$ where the trivial objectives have been removed.
-\end{definition}
-%
-\begin{definition}[$\concr: \powerset(\OS) \mapsto \powerset(\Sce)$]
-\label{def:concr-set}
-  $\concr(\W) = \{ \delta \in \concr(\w) \mid \w \in \W \} \enspace.$
-\end{definition}
-\end{comment}
-%
 \begin{definition}[$\uconcr: \OS \rightarrow \powerset(\Sce)$]
@@
 
-\begin{comment}
-\begin{definition}[$\uconcr: \powerset(\OS) \mapsto \powerset(\Sce)$]
-\label{def:uconcr-set}
-  $\uconcr(\Omega) = \{ \delta \in \uconcr(\w) \mid \w \in \Omega\}$
-\end{definition}
-\end{comment}
-
 For any objective $P$ and context $\ctx$, \pref{def:maxCont} allows to obtain the set of processes of sort $\PHsort(P)$ are required to solve $P$ in $\ctx$, given by $\gCont_\ctx(\PHsort(P), P)$.
-\begin{comment}
-\begin{definition}
-\label{def:allprocs}
-  \begin{align*}
-  \allprocs(\V, \E) = \{ p \in \PHproc &\mid p \in \V \vee \exists P \in \V \cap \Obj,\\
-  &\qquad p = \PHtarget(P) \vee p = \PHbounce(P) \}
-%    &\qquad\qquad p \in ps \vee p = \PHtarget(P) \vee p = \PHbounce(P) \\
-%    &\qquad\qquad \vee \exists (a_i,ps) \in \cwRSP, p \in ps \}
-  \end{align*}
-  \begin{align*}
-  \allprocs(\V, \E) = (V \cap \Proc) \cup \{ \PHtarget(P), \PHbounce(P) \mid P \in \V \cap \Obj \}
-  \end{align*}
-\end{definition}
-\end{comment}
-%
-\begin{comment}
-\begin{definition} \todo{À revoir avec la nouvelle sémantique}
-\label{def:allprocs}
-  \begin{align*}
-  &\allprocs((\cwSol,\cwReq,\cwRSP,\cwCont)) = \{ p \in \PHproc \mid \exists (P,ps) \in \cwSol, \\
-    &\qquad\qquad p \in ps \vee p = \PHtarget(P) \vee p = \PHbounce(P) \\
-    &\qquad\qquad \vee \exists (a_i,ps) \in \cwRSP, p \in ps \}
-  %  &\qquad\qquad \vee p = \PHtarget(P) \vee \exists h \in \BS(P), (p = \PHhitter(h) \vee p = \PHbounce(h)) \\
-  %  &\qquad\qquad \vee \exists(Q, \PHobj{p}{\PHbounce(Q)} \in \cwPrioCont \}
-  \end{align*}
-\end{definition}
-\end{comment}
-%
-%\subsection{Abstract structure}
-%
-%
 \begin{definition}[$\gCont_\ctx : \Sigma \times \Obj \rightarrow \powerset(\PHproc)$]
@@
 \end{definition}
-
-\begin{comment}
-\begin{definition}
-  $\cwB = (\V, \E)$, $V \subset \PHproc \cup \Obj \cup \powerset(\PHproc)$ and $E \subset V \times V$
-  so that:\\
-  $\w \subset \V$\\
-  $\{ \PHbounce(P) \mid P \in \V \} \subset \V$\\
-  $\{ (P, ps) \in \Obj \times \powerset(\PHproc) \mid P \in \V \wedge ps \in \BS(P) \} \subset \E$\\ % Sol
-  $\{ ps \in \powerset(\PHproc) \mid (P, ps) \in \E \} \subset \V$\\
-  $\{ (ps, a_i) \in \powerset(\PHproc) \times \PHproc \mid a_i \in ps \} \subset \E$\\ % Sol
-  $\{ a_i \in \PHproc \mid (ps, a_i) \in \E \} \subset \V$\\
-  $\{ (a_i, \PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid a \in \components \wedge a_i \in \V \wedge a_j \in \ctx \} \subset \E$\\ % Req
-  $\{ \PHobjp{a}{j}{i} \in \Obj \mid (a_i, \PHobjp{a}{j}{i}) \in \E \} \subset \V$\\
-  $\{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid P \in \V \wedge q \in \gCont_\ctx(\PHsort(P), P) \} \subset \E$\\ % Cont
-  $\{ (a_i, ps) \in \Proc \times \powerset(\PHproc) \mid a \in \cs \wedge a_i \in \V \wedge ps \in \csState(a_i) \} \subset \E$\\ % ReqSolPrio
-\end{definition}
-
-\begin{definition}
-  $\cwB = (\V, \E)$, $V \subset \PHproc \cup \Obj \cup \powerset(\PHproc)$ and $E \subset V \times V$
-  so that:
-  \begin{align*}
-    \w &\subset \V\\
-    \{ \PHbounce(P) \mid P \in \V \} &\subset \V\\
-    \{ (P, ps) \in \Obj \times \powerset(\PHproc) \mid P \in \V \wedge ps \in \BS(P) \} &\subset \E\\ % Sol
-    \{ ps \in \powerset(\PHproc) \mid (P, ps) \in \E \} &\subset \V\\
-    \{ (ps, a_i) \in \powerset(\PHproc) \times \PHproc \mid a_i \in ps \} &\subset \E\\ % Sol
-    \{ a_i \in \PHproc \mid (ps, a_i) \in \E \} &\subset \V\\
-    \{ (a_i, \PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid a \in \components \wedge a_i \in \V \wedge a_j \in \ctx \} &\subset \E\\ % Req
-    \{ \PHobjp{a}{j}{i} \in \Obj \mid (a_i, \PHobjp{a}{j}{i}) \in \E \} &\subset \V\\
-    \{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid P \in \V \wedge q \in \gCont_\ctx(\PHsort(P), P) \} &\subset \E\\ % Cont
-    \{ (a_i, ps) \in \Proc \times \powerset(\PHproc) \mid a \in \cs \wedge a_i \in \V \wedge ps \in \csState(a_i) \} &\subset \E % ReqSolPrio
-  \end{align*}
-\end{definition}
-\end{comment}
 
@@
 \ie by overriding its initial context $\ctx$ by $\allprocs(\V, \E)$, defined by:
-%in which the initial context $\ctx$ is updated by iteratively adding every process that appears in the graph ($\allprocs$).
-%The aim of the this subsection is to build a graph of local causality that describes the propagation of objectives due to the bounce sequence abstraction of \pref{def:aBS}.
-%This oriented graph has the form $(\V, \E)$, where $\V \subset \Proc \cup \Obj \cup \Sol$ and $\E \subset \V \times \V$.
-%In order to build an accurate under-approximation, this graph is defined as a fixed point, in which each iteration saturates 
-%We denote $\allprocs(\V, \E)$ the set of all processes involved in such a graph $(\V, \E)$, defined by: %in \pref{def:allprocs}.
 $$\allprocs(\V, \E) = (V \cap \Proc) \cup \{ \PHtarget(P), \PHbounce(P) \mid P \in \V \cap \Obj \}$$
-
-%The final graph of local causality is computed by a fixed point 
-%is defined as a fixed point
 
@@
   where $\myB = (\cwV, \cwE)$ is the smallest graph where:
-  %$\cwV = \VProc \cup \VObj \cup \VSol$ with $\VProc \subset \PHproc$, $\VObj \subset \Obj$, $\VSol \subset \Sol$ and $\cwE \subset \cwV \times \cwV$
   $\cwV \subset \Proc \cup \Obj \cup \Sol$ and $\cwE \subset \cwV \times \cwV$
@@
     \w &\subset \cwV \label{eq:Vw} \\
-%      \{ \PHbounce(P) \mid P \in \VProc \} &\subset \V\\
     P \in \VProc &\Rightarrow \PHbounce(P) \in \cwV \label{eq:Vproc} \\
     (x, y) \in \E &\Rightarrow y \in \cwV \label{eq:VE} \\
-%    P \in \VObj &\Rightarrow \PHbounce(P) \in \V\\
-%      \{ (P, ps) \in \Obj \times \powerset(\PHproc) \mid P \in \V \wedge ps \in \BS(P) \} &\subset \E\\ % Sol
     P \in \VObj \wedge ps \in \BS(P) &\Rightarrow (P, ps) \in \cwE \label{eq:ESol1} \\
-%    \{ ps \in \powerset(\PHproc) \mid (P, ps) \in \E \} &\subset \V\\
-%      \{ (ps, a_i) \in \powerset(\PHproc) \times \PHproc \mid a_i \in ps \} &\subset \E\\ % Sol
     ps \in \VSol \wedge a_i \in ps &\Rightarrow (ps, a_i) \in \cwE \label{eq:ESol2} \\
-%    \{ a_i \in \PHproc \mid (ps, a_i) \in \E \} &\subset \V\\
-%      \{ (a_i, \PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid a \in \components \wedge a_i \in \V \wedge a_j \in \ctx \} &\subset \E\\ % Req
     a \in \components \wedge a_i \in \VProc \wedge a_j \in \ctx &\Rightarrow (a_i, \PHobjp{a}{j}{i}) \in \cwE \label{eq:EReq} \\
-%      \{ (a_i, ps) \in \Proc \times \powerset(\PHproc) \mid a \in \cs \wedge a_i \in \V \wedge ps \in \csState(a_i) \} &\subset \E\\ % ReqSolPrio
     a \in \cs \wedge a_i \in \VProc \wedge ps \in \csState(a_i) &\Rightarrow (a_i, ps) \in \cwE \label{eq:EPrio} \\
-%    \{ \PHobjp{a}{j}{i} \in \Obj \mid (a_i, \PHobjp{a}{j}{i}) \in \E \} &\subset \V\\
-%      \{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid P \in \V \wedge q \in \gCont_\ctx(\PHsort(P), P) \} &\subset \E\\ % Cont
     P \in \VObj \wedge q \in \gCont_\ctx(\PHsort(P), P) &\Rightarrow (P, \PHobj{q}{\PHbounce(P)}) \in \cwE \label{eq:ECont}
@@
 
-%In the following, we denote:
-%$\BvProc = \Bv \cap \PHproc$, $\BvObj = \Bv \cap \Obj$ and $\BvSol = \Bv \cap \Sol$.
-%$\Bee{X}{Y} = \Be \cap (X \times Y)$, with $X, Y$ amongst $\PHproc$, $\Obj$ and $\Sol$.
-%
-\begin{comment}
-\begin{definition}
-  \label{def:aS}
-  The abstract structure $\cwB=(\Breq,\Bsol,\Brsp,\Bcont)$ is defined as
-  $\cwB = \sfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs_\ctx(\myB)}}$,\\
-  with $\myB=(\myreq,\mysol,\myrsp,\mycont)$:
-  \begin{align*}
-    \myreq &= \{ (a_i,\PHobjp{a}{j}{i}) \in \PHproc \times \Obj \mid
-      a \in \components \wedge a_j \in \PHget{\ctx}{a} \\ % \vee a_j \in \pfpprocs_\ctx(a) \\
-      & \qquad \wedge ((\exists (P,ps) \in \mysol \vee \exists (b_j, ps) \in \myrsp), a_i \in ps \\
-      & \qquad\qquad \vee \exists n \in \indexes{\w}, \PHbounce(\w_n)=a_i) \}
-    \\
-    \mysol &\subseteq \{ (P,ps) \in \Obj \times \powerset(\PHproc) \mid
-            \exists (a_i, P) \in \myreq \wedge ps \in \aBS(P) \\
-      & \qquad\qquad \vee \exists (Q, P) \in \mycont \wedge ps \in \aBS(P) \}
-    \\
-    \myrsp &= \{ (a_i,ps) \in \PHproc \times \powerset(\PHproc) \mid a \in \cs \\
-      & \qquad \wedge (\exists (P,ps') \in \mysol \vee \exists (b_j,ps') \in \myrsp), \\
-      & \qquad\qquad a_i \in ps' \wedge \csState(a_i) \in ps \}
-    \\
-    \mycont & = \{ (P, \PHobj{q}{\PHbounce(P)}) \in \Obj \times \Obj \mid
-      \exists (P, ps) \in \mysol \\
-      & \qquad\qquad \wedge q \in \gCont_\ctx(\PHsort(P),P) \}
-  \end{align*}
-\end{definition}
-
-\begin{definition}[Coherent solution]
-\label{def:coherent}
-  A cooperative sort requisite $(a_i, ps)$ in $\Brsp$ is said coherent iff
-  it has no successor $(b_k,\PHobjp{b}{j}{k})$ in $\Breq$ so that there exists $b_n \in ps$, $b_k \neq b_n$.
-\end{definition}
-\end{comment}
-%
-%\towrite{Expliquer}
-%We define in \pref{def:coherent} the notion of coherent edge in the graph of local causality.
 In the graph of local causality, an edge linking a process of a cooperative sort to a solution set $ps$ is said coherent (\pref{def:coherent}) if none of the processes in $ps$ conflict with the children processes of $ps$.
@@
   An edge $(x, y) \in \cwE$ is said coherent if and only if:
-%  $(x, y) \in \Bee{\Proc}{\Sol} \Rightarrow y$ has no process successor $a_j \in \Bv \cap \Proc$ so that $\exists a_i \in y$, $a_i \neq a_k$.
   $(x, y) \in \Be \cap (\Proc \times \Sol) \Rightarrow y$ has no children process $a_j \in \Bv \cap \Proc$ so that $\exists a_i \in y$, $a_i \neq a_k$.
@@
 \begin{example}
-  %As an example showing the usefulness of our method, we can consider \pref{fig:ph-livelock}.
   Let $\PH' = (\PHs, \PHl, \PHh'^{\langle 1 \rangle})$ be the “flattened” version of the PH in \pref{fig:ph-livelock}, that is: $\PHh'^{\langle 1 \rangle} = \PHh^{(1)} \cup \PHh^{(2)}$,
-  %As this PH model contains only one class of priority, 
   which is equivalent to a PH in the semantics without priorities.
@@
 The semantics of PH with $2$ classes of priorities studied in this paper allows to model cooperative sorts accurately representing a coherent configuration of a set of sorts.
-%As the method presented in this section allows to efficiently conclude on the reachability of a process,
 Therefore, we can derive a new method to conclude about the reachability of a state (considering only components).
@@
 
-%It is also possible to compute the reachability of a partial state
-%by modelling in $\total$ the cooperation of a subset of $\components$,
 It is also possible to compute the reachability of a set of states $S \subset \PHl$ by creating several actions $\PHhit{\total_s}{\reach_0}{\reach_1}$ in $\PHh^{(2)}$ for each state $s \in S$.

### 2013-04-02 parts/sa.tex
compression of GLC explanations

@@
 
-The reachability of a process $a_i$ is approximated by the ability to solve all objectives $\PHobjp{a}{j}{i}$ so that $a_j$ is in the initial context.
+The graph of local causality $\cwB = (\V, \E)$ defined in \pref{def:glc} is a graph where $\V \subset \Proc \cup \Obj \cup \Sol$ and $\E \subset \V \times \V$.
+A node in $\PHproc$ is a required process,
+a node in $\Obj$ is an objective to reach a given process
+and a node in $\Sol$ is a sets of processes required for the solving.
+An objective $P \in \Obj$ is solvable if the abstractions of bounce sequences $\aBS(P) \in \Sol$ (\pref{def:aBS}) can be reached (\pref{eq:ESol1}), leading to several required processes (\pref{eq:ESol2}).
+If $a$ is a component, the reachability of a process $a_i$ is approximated by the ability to solve all objectives $\PHobjp{a}{j}{i} \in \Obj$ for all $a_j$ in the initial context (\pref{eq:EReq});
+if $a$ is a cooperative sort, the reachability of $a_i$ is directly solved by the set of the processes $\csState(a_i)$ (\pref{def:csState}) it represents (\pref{eq:EPrio}).
+Finally, if the resolution of an objective $P$ requires a process of $\PHsort(P)$, \ie $\gCont(\PHsort(P), P) \neq \emptyset$ (\pref{def:maxCont}), then this objective is re-targeted (\pref{eq:ECont}).
+\pref{eq:Vw}, \eqref{eq:Vproc} and \eqref{eq:VE} ensure that all required nodes are in $\cwV$.
+
+\begin{comment}
+The reachability of a process $a_i$ is approximated by the ability to solve all objectives $\PHobjp{a}{j}{i}$ for all $a_j$ in the initial context.
 To this end, the abstractions of bounce sequences (\pref{def:aBS}) solving these objectives are computed, leading to new required processes, and thus new objectives on other sorts.
@@
 $$\allprocs(\V, \E) = (V \cap \Proc) \cup \{ \PHtarget(P), \PHbounce(P) \mid P \in \V \cap \Obj \}$$
+\end{comment}
 
@@
 
+\begin{comment}
 \pref{eq:Vw}, \eqref{eq:Vproc} and \eqref{eq:VE} ensure that all required nodes are in $\cwV$.
@@
 Finally, if the resolution of an objective $P$ requires a process of $\PHsort(P)$, then \pref{eq:ECont} re-targets this objective ($\gCont$).
+\end{comment}
 
@@
   which is equivalent to a PH in the semantics without priorities.
-  The under-approximation on such models developed in~\cite{PMR12-MSCS} concludes that $c_1$ is reachable from $\ctx = \PHstate{a_1, b_0, c_0, ab_{10}}$;
-  this is due to an over-approximation of the behaviours inherent to cooperative sorts in the semantics without priorities.
+  Due to spurious behaviours inherent to the cooperative sorts in this semantics, 
+  the original under-approximation developed in~\cite{PMR12-MSCS} concludes that $c_1$ is reachable in $\PH'$ from $\ctx = \PHstate{a_1, b_0, c_0, ab_{10}}$.
+  %this is due to an over-approximation of the behaviours inherent to cooperative sorts in the semantics without priorities.
 
-  This unwanted behaviour is palliated by the semantics of PH with priorities proposed in this paper.
+  Such unwanted behaviours are palliated by the semantics of PH with priorities proposed in this paper.
   Indeed, the under-approximation given in \pref{th:approxinf} does not conclude regarding the reachability of $c_1$,
@@
   (However, from the inconclusiveness of \pref{th:approxinf}, one cannot conclude about the unreachability of $c_1$.
-  Such analysis should be driven for instance with over-approximation methods developed in~\cite{PMR10-TCSB}.)
+  Such analysis should be driven for instance with over-approximation methods developed in~\cite{PMR12-MSCS}.)
 
-  We note that if the actions $\PHhit{a_0}{b_0}{b_1}$ and $\PHhit{b_0}{a_0}{a_1}$ are replaced by the self-hits
+  However, if $\PHhit{a_0}{b_0}{b_1}$ and $\PHhit{b_0}{a_0}{a_1}$ are replaced by
   $\PHhit{a_0}{a_0}{a_1}$ and $\PHhit{b_0}{b_0}{b_1}$,

### 2013-04-02 parts/sa.tex
fix GLC explanations

@@
 if $a$ is a cooperative sort, the reachability of $a_i$ is directly solved by the set of the processes $\csState(a_i)$ (\pref{def:csState}) it represents (\pref{eq:EPrio}).
-Finally, if the resolution of an objective $P$ requires a process of $\PHsort(P)$, \ie $\gCont(\PHsort(P), P) \neq \emptyset$ (\pref{def:maxCont}), then this objective is re-targeted (\pref{eq:ECont}).
+The resolution of an objective $P$ may a process of $\PHsort(P)$, \ie $\gCont(\PHsort(P), P) \neq \emptyset$ (\pref{def:maxCont}); in this cas, the objective is re-targeted (\pref{eq:ECont}).
 \pref{eq:Vw}, \eqref{eq:Vproc} and \eqref{eq:VE} ensure that all required nodes are in $\cwV$.
+Finally, as the active process of every sort may evolve, $\cwB$ is obtained iteratively by saturation with every process it contains,
+\ie by overriding its initial context $\ctx$ by $\allprocs(\V, \E)$, defined by:
+$$\allprocs(\V, \E) = (V \cap \Proc) \cup \{ \PHtarget(P), \PHbounce(P) \mid P \in \V \cap \Obj \}$$
 

### 2013-04-02 main.tex
start cleanup
create appendix
update lfp notation
change title
proofreading of section 2
proofreading of section 3
abstract

@@
 \newrefformat{suppl}{Appendix~\ref{#1}}
+\newrefformat{cr}{Criterion~\ref{#1}}
 \newrefformat{eq}{Eq.~\eqref{#1}}
@@
 \def\indexes#1{\mathbb{I}^{#1}}
-\newcommand{\sfp}[3]{\mathbf{lfp}\{#1\}\left(#2\mapsto#3\right)}
-%\def\lfp{\f{pppf}\;}
 \def\f#1{\mathsf{#1}}
@@
 \newcommand{\components}{\Gamma}
-\newcommand{\cs}{CS}
-
-\tikzstyle{prio}=[draw,double,-stealth]
+%\newcommand{\cs}{CS}
+\newcommand{\cs}{\Delta}
 
@@
 
+%\renewcommand{\restriction}[2]{#1_{#2}}
+
 % Commandes À FAIRE
@@
 % Id est
-\newcommand{\ie}{i.e. }
+\newcommand{\ie}{i.e.~}
 
@@
 \begin{frontmatter}
-\title{Under-approximation of reachability through static analysis in multivalued asynchronous networks}
+\title{Under-approximation of reachability in multivalued asynchronous networks}
 
@@
 To address this issue, we propose an extended definition of the framework, including priority classes for actions.
-In this paper, we focus on a restriction of the Process Hitting with two priorities and a specific behaviour of the components, that is sufficient to tackle the aforementioned problem of cooperations.
-We show that this class of Process Hitting models allows to represent any asynchronous networks, either boolean or multivalued.
+In this paper, we focus on a restriction of the Process Hitting with two classes of priorities and a specific behaviour of the components, that is sufficient to tackle the aforementioned problem of cooperations.
+We show that this class of Process Hitting models allows to represent any Asynchronous Discrete Networks, either Boolean or multivalued.
 Then we develop a new refinement for the under-approximation of the static analysis to give accurate results for this class of Process Hitting models.
-Our method thus allows to efficiently under-approximate local reachability properties in asynchronous multivalued networks.
+Our method thus allows to efficiently under-approximate reachability properties in Asynchronous Discrete Networks;
+it is in particular conclusive on reachability properties in a 94 components Boolean network, which is unprecedented.
 \end{abstract}
@@
 
-%\input{parts/contributions}
+\input{parts/appendix}
 

### 2013-04-02 parts/example.tex
large-scale application

@@
-\section{Example}\label{sec:example}
+% vim:set spell spelllang=en:
+
+\section{Examples}\label{sec:example}
 
@@
 
-\todo{Trouver un grs exemple représentatif (EGFR / TCRSIG)}
+\subsection{Large-scale application}
+
+In order to support the scalability and applicability of our under-approximation of reachability, we
+apply our new approach for the analysis of large-scale model of the T-cell receptor (TCR)
+signalling pathway \cite{tcrsig94}.
+This model gathers 94 interacting components and is specified as a Boolean network.
+The under-approximation presented in this paper has been implemented in the existing Pint
+software\footnote{Pint is freely available at \url{http://process.hitting.free.fr}.}.
+
+The Boolean model has been automatically encoded into a Process Hitting with 2 classes of priority%
+\footnote{Model and scripts are available at
+\url{http://www.irccyn.ec-nantes.fr/~folschet/underapprox-tcrsig94.tbz2}.}.
+Then, we verified the reachability for the independent activation of 4 outputs of the signalling
+cascade (SRE, AP1, NFkB, NFAT) from all possible input combinations (CD45, CD28, TCRlib) using our
+new reachability under-approximation (answering either \emph{yes} or \emph{inconclusive}) and a 
+previously defined reachability over-approximation \cite{PMR12-MSCS} (answering either \emph{no} or
+\emph{inconclusive}).
+All result in conclusive decisions, and the under-approximation has been satisfied in 12 cases (over
+32) proving the satisfiability of the concerned reachability property in the encoded Boolean network
+(and non-satisfiability in the other cases).
+
+Computations times are in the order of a few hundredths of a second on a 2.4GHz processor with 2GB
+of RAM.
+To give a comparison, we did the same experiments with a standard symbolic model-checker, libDDD
+\cite{libddd}, known for its good performances, the input model being the Boolean network expressed
+as a Petri net.
+However, due to the large scale of the model, the program runs out of memory for all the experiments.
+
+While ensuring a low complexity for the analysis of reachability in Boolean and discrete networks, our
+under-approximation method reveals to be conclusive in numerous cases when applied to real
+large-scale biological models, which were not tractable with exact model-checking.

### 2013-04-02 parts/ccl.tex
large-scale application
fixes (Morgan)

@@
 is still accurate in the framework with priorities (by “flattening” all actions),
-but may be refined given the restrictions proposed in this paper.
+but may be refined given the restrictions proposed in this paper,
+and a specific search of key processes or cut sets may be derived.
 %but turns out to be too wide even in some obvious cases that are consequently not conclusive.

### 2013-04-02 parts/def-ph.tex
fixes (Morgan)

@@
 Then we describe the modelling of cooperation between components and discuss how the new aforementioned semantics makes this modelling more accurate.
-Finally, in order to perform a static analysis on this new semantics, we give several criteria to restrict the class of models that we can study,
+Finally, in order to perform a static analysis adapted to this new semantics, we give several criteria to restrict the class of models that we can study,
 and give several theorems that follow.
@@
 
-In \pref{def:restriction}, we define the $n$-reduction of a given PH as the PH with $n$ classes of priorities in which only actions of priority lower or equal to $n$ are kept.
+In \pref{def:restriction}, we define the $n$-reduction of a given PH as the PH with $n$ classes of priorities in which only actions of priority lower or equal to $n$ are considered.
 \begin{definition}[PH $n$-reduction]

### 2013-04-02 parts/def-ph.tex
typo

@@
     Sorts are represented as labelled boxes and processes as circles with their identifier on the side.
-    Actions of $\PHh^{(1)}$ are represented by double arrows and actions of $\PHh^{(2)}$ are represented by single arrows;
+    Actions of $\PHh^{(1)}$ are represented by thick arrows and actions of $\PHh^{(2)}$ are represented by single arrows;
     the hit part of each action in drawn in plain line and the bounce part is in dotted line.

### 2013-04-02 underapprox-tcrsig94/run.sh
+ underapprox-tcrsig94

@@ -1,0 +1,18 @@
+#!/usr/bin/env bash
+ph="../model.ph"
+outputs="sre ap1 nfkb nfat"
+mode=${1}
+
+for i in 0 1; do
+	for j in 0 1; do
+		for k in 0 1; do
+			init="cd45 $i, cd28 $j, tcrlig $k"
+			echo "--- $init"
+			for z in $outputs; do
+				echo "# $z 1"
+				./unitrun.sh $mode "$i$j$k" --no-debug --initial-state "$init" -i $ph $z 1
+			done
+		done
+	done
+done
+

### 2013-04-02 underapprox-tcrsig94/unitrun.sh

@@ -1,0 +1,54 @@
+#!/usr/bin/env bash
+mode=$1; shift
+name=$1; shift
+
+its=its-ctl
+
+bd=$name.work
+
+sdd_xml="$bd/model.xml"
+sdd_ctl="$bd/model.ctl"
+bc_file="$bd/model.bc"
+
+export TIME="%e\t%U"
+
+do_time() {
+	n="$bd/$1"; shift
+	time "$@" 2>&1
+	#/usr/bin/time -- "$@" 2>&1
+}
+
+if [[ "$mode" == "ph" ]]; then
+	do_time ph-reach ph-reach "$@"
+elif [[ "$mode" == "priority" ]]; then
+	do_time ph-reach ph-reach --coop-priority "$@"
+elif [[ "$mode" == "phtest" ]]; then
+	do_time ph-reach ph-reach --method test "$@"
+elif [[ "$mode" == "sdd-bn" ]]; then
+	mkdir -p $bd
+	./CNA2PN ../doc/Tcell/reactions "$@" > $bd/output
+	tail -n1 $bd/output > $bd/model.ctl
+	head -n-1 $bd/output > $bd/model.xml
+	do_time its timeout 30m $its --quiet --forward -i $bd/model.xml -ctl $bd/model.ctl
+	rm -rf $bd
+elif [[ "$mode" == "sdd" ]]; then
+	echo -n "exporting to sdd..."
+	mkdir -p $bd
+	pint ph2sdd.ml --output-xml "$sdd_xml" --output-ctl "$sdd_ctl" "$@" || exit 1
+	echo " done"
+	do_time its-forward $its --forward -i "$sdd_xml" -ctl "$sdd_ctl"
+	#do_time its-back $its --backward -i model.ph.xml -ctl model.ph.ctl
+	rm -rf "$bd"
+elif [[ "$mode" == "biocham" ]]; then
+	echo -n "exporting to biocham..."
+	mkdir -p $bd
+	pint ph2bc.ml -o "$bc_file" "$@" || exit 1
+	echo " done"
+	export GLOBALZ=500000
+	do_time biocham biocham "$PWD/$bc_file"
+else
+	echo "unknown mode (ph/phtest/sdd/biocham)"
+	exit 1
+fi
+
+

### 2013-04-02 parts/intro.tex
synchronize notations of appendix B

@@
 This leads to questions about the accessibility (possible or inevitable) of certain states.
-The ultimate goal is to discover how it could be possible to prevent from reaching some pathological states.
+The ultimate goal is to discover how it could be possible to prevent biological systems from reaching some pathological states.
 
 Of course, such formal models on which analyses are performed are abstract representations of the actual studied systems.
-They are associated with parameters that have to be synthesised so as to be as much as possible fitting with the real systems having some observed behaviors.
+They are associated with parameters that have to be synthesised %so as to be as much as possible fitting with the real systems having some observed behaviors.
+to give the most faithful representation of the real systems with their observed behaviours.
 As a matter of fact, the abstractions we get are more or less rough or accurate.
-Usual formal frameworks for such modelling activities are state-transition systems, Petri nets or process algebras.
-We developed a quite similar framework named the Process Hitting \cite{PMR10-TCSB}, with the aim of avoiding to build the whole state space in order to be able to tackle very large systems
-(which would have led to a huge number of states, hopelessly far too big to be analysed).
+Usual formal frameworks for such modelling activities are state-transition systems or process algebras. % Petri nets
+We developed a quite similar framework named the Process Hitting \cite{PMR10-TCSB}: %, with the aim of avoiding to build the whole state space in order to be able to tackle very large systems
+our motivation behind this framework was to design a model and analysis techniques that avoid to build the whole state space.
+This allows us to tackle very large systems
+(which would have led to a huge number of states, hopelessly too huge to be analysed).
 
-Besides, one further objective of our work is now to be more accurate in the description of the dynamics of the studied systems.
-The idea for this is to introduce timing features of a system into its model.
-Indeed, we are interested in taking into account some knowledge about the relative length of some phenomena as it is a way to refute some kinds of models (parameters) non compatible with the observed dynamic behaviours.
+Besides, one further objective of our work is now %to be more accurate in the description of the studied systems.
+to improve the accuracy of the description of the dynamics of the studied systems.
+The idea for this is to introduce timing features into its model.
+Indeed, we are interested in taking into account some knowledge about the relative length of some phenomena as it is a way to refute some kinds of models (parameters) that are inconsistent with the observed dynamic behaviours.
 In this paper, we are dealing with these timing properties through priorities,
@@
 
-Until now, such a priority scheduling of the actions was not studied very much in the different formal modelling frameworks of systems biology.
+Until now, such a priority scheduling of the actions was not studied very much in the different formal modelling frameworks dedicated to systems biology.
 Nevertheless, such an attempt has been carried out for Petri nets by F. Bause \cite{Bause97}
@@
 
-Since our formalism (Process Hitting) is inspired from the $\pi$-calculus, our work is related to such semantic ramifications of extending traditional process algebras with the concepts of priority that allow for some transitions to be given precedence over others.
+Since our formalism (Process Hitting) can be considered as a subset of CCS, %is inspired from the $\pi$-calculus,
+our work is related to such semantic ramifications of extending traditional process algebras with the concepts of priority that allow for some transitions to be given precedence over others.
 The concept is derived in two directions: dynamic versus static, the difference being naturally that the former one refer to a semantics where priority values may change during execution according to some evolution rules.
@@
 The Process Hitting framework is defined in section 2;
-we introduce static analysis of the PH in section 3;
+we introduce static analysis of the Process Hitting in section 3;
 section 4 illustrates the approach on an example
@@
 $\lfp{x_0}{x}{x'}$ is the least fixed point greater that $x_0$ of the function $x \mapsto x'$.
+The Cartesian product is denoted $\times$.

### 2013-04-02 parts/sa.tex

@@
 
-\todo{Complexité de la construction du GLC}
-
 In the graph of local causality, an edge linking a process of a cooperative sort to a solution set $ps$ is said coherent (\pref{def:coherent}) if none of the processes in $ps$ conflict with the children processes of $ps$.
@@
 
-\todo{Complexité de la vérification du GLC}
+Computing the graph of local causality is polynomial in the number of sorts in $\PH$ and exponential in the number of processes in one sort.
+Checking the properties allowing to apply \pref{th:approxinf} is polynomial in the size of the graph.
+%Therefore, if the number of processes in each sort is small, the overall method can be processed in polynomial time.
+Furthermore, it is possible to compute only a subset of $\V \cap \Sol$;
+in this case, the overall method turns out to be exponential in the number of solutions to each objective.
+Our method can thus be considered as efficient compared to regular model-checking which is usually PSPACE-complete~\cite{Harel02}.
 

### 2013-04-02 parts/appendix.tex
title in appendix
weak bisimulation of DNs
section 3
proofreading of section 3
several fixes; first final version

@@
 
-%\section{Demonstration of \pref{th:approxinf}}
+\section{Proof of Under-approximation (\pref{th:approxinf})}
+\label{suppl:demoapproxinf}
 
-\begin{proof} \towrite{Déplacer en annexe}
+In the following, we denote:
+%$\BvProc = \Bv \cap \PHproc$, $\BvObj = \Bv \cap \Obj$ and $\BvSol = \Bv \cap \Sol$.
+$\Bee{X}{Y} = \Be \cap (X \times Y)$, with $X, Y$ amongst $\PHproc$, $\Obj$ and $\Sol$.
+
+\begin{proof}
 We note $max\ctx = \ctx \Cap \allprocs(\cwB)$ the context supported by $\cwB$.
@@
 
-\section{Demonstration of \towrite{équivalence PHP / réseaux discrets}}
-
-\todo{Preuve}
+\input{parts/suppl-ph-dn.tex}

### 2013-04-02 parts/ccl.tex
several fixes; first final version

@@
 %; however, the most usual cases can be handled.
-The method has been implemented as an extension of the existing “ph-reach” tool into the existing Pint\footnote{\url{http://processhitting.wordpress.com/}} library.
-\towrite{Déplacer dans la section exemples ?}
 
@@
 This allows to efficiently compute reachability results on large biological models provided that they are equivalent to Asynchronous Discrete Networks and that a translation from the original framework into a Process Hitting model is possible.
-Such a translation for interaction graphs of Thomas modelling was proposed in~\cite{PMR10-TCSB} \towrite{[À garder ?] and is made possible by the Pint software}.
+Such a translation for interaction graphs of Thomas modelling was proposed in~\cite{PMR10-TCSB}. % \towrite{[À garder ?] and is made possible by the Pint software}.
 

### 2013-04-02 parts/intro.tex
contributions

@@
 Among these questions, a major one is to understand precisely how biological systems evolve and behave; why and how they change their usual behaviours…
-This leads to questions about the accessibility (possible or inevitable) of certain states.
+This leads to questions about the accessibility (possible or inevitable) of some states.
 The ultimate goal is to discover how it could be possible to prevent biological systems from reaching some pathological states.
@@
 
-Since our formalism (Process Hitting) can be considered as a subset of CCS, %is inspired from the $\pi$-calculus,
+\paragraph{Contributions}
+Since our formalism (the Process Hitting) can be considered as a subset of CCS, %is inspired from the $\pi$-calculus,
 our work is related to such semantic ramifications of extending traditional process algebras with the concepts of priority that allow for some transitions to be given precedence over others.
@@
 In our work, actions exhibit a two-level static priority structure, with certain ones being designated as “prioritised” and others as “unprioritised”.
+
+In this paper, we introduce a new extension to the semantics of Process Hitting by partitioning actions into classes of priorities.
+One of the objectives is to reach an accurate representation of cooperating components in the model, that was not fulfilled with the initial semantics.
+We then develop an efficient under-approximation of the reachability of the state of independent components on a subclass of this new framework, thus allowing to compute efficient static analysis.
+This local reachability under-approximation can be also easily extended to study the reachability of a global state.
+Finally, as the subclass of models studied proves to be bisimilar to Asynchronous Discrete Networks, we state to have developed an efficient method to compute the reachability of a state and thus study the behaviour of such models.
+
+The method developed in this paper has been implemented into the existing Pint library and tested on a large-scale biological model containing 94 components.
+This piece of software turned out to be conclusive in all cases and results were computed in hundredths of seconds,
+thus overtaking the efficiency of usual model-checkers.
 

### 2013-04-02 parts/intro.tex
fixes in intro

@@
 our motivation behind this framework was to design a model and analysis techniques that avoid to build the whole state space.
-This allows us to tackle very large systems
+This allows to tackle very large systems
 (which would have led to a huge number of states, hopelessly too huge to be analysed).
@@
 Besides, one further objective of our work is now %to be more accurate in the description of the studied systems.
-to improve the accuracy of the description of the dynamics of the studied systems.
+to improve the accuracy of the description of the studied systems dynamics.
 The idea for this is to introduce timing features into its model.
-Indeed, we are interested in taking into account some knowledge about the relative length of some phenomena as it is a way to refute some kinds of models (parameters) that are inconsistent with the observed dynamic behaviours.
+Indeed, we are interested in taking into account some knowledge about the relative length of some phenomena as it is a way to refute some models (parameters) that are inconsistent with the observed dynamic behaviours.
 In this paper, we are dealing with these timing properties through priorities,
@@
 
-Until now, such a priority scheduling of the actions was not studied very much in the different formal modelling frameworks dedicated to systems biology.
-Nevertheless, such an attempt has been carried out for Petri nets by F. Bause \cite{Bause97}
-and the concept of priority relations among the transitions of a network has also more recently been introduced by A.
-K.
-Wagler \textit{et al.} in \cite{waw,WaglerW12} in order to allow modelling deterministic systems for biological applications.
-The concept of priority is much straightforward in the approach of process algebras as it was shown by R.
-Cleaveland and M.
-Hennessy in \cite{Cleaveland199058,Cleaveland99prioritiesin} and their abstractions and equivalences were studied in \cite{Cleaveland:2007:PAP:1282576.1282847}.
-It was later extended for applications in the field of system biology by M. John \textit{et al.} in \cite{jlnu2010}.
+Until now, such a priority scheduling of the actions was not studied extensively in the different formal modelling frameworks dedicated to systems biology.
+Nevertheless, such an attempt has been carried out for Petri nets by F.~Bause \cite{Bause97},
+and the concept of priority relations among the transitions of a network has also more recently been introduced by A.~K.~Wagler \textit{et~al.} \cite{waw,WaglerW12} in order to allow modelling deterministic systems for biological applications.
+The concept of priority is much straightforward in the approach of process algebras as it was shown by R.~Cleaveland and M.~Hennessy in \cite{Cleaveland199058,Cleaveland99prioritiesin} and their abstractions and equivalences were studied in \cite{Cleaveland:2007:PAP:1282576.1282847}.
+It was later extended for applications in the field of system biology by M.~John \textit{et~al.} \cite{jlnu2010}.
 
@@
 The concept is derived in two directions: dynamic versus static, the difference being naturally that the former one refer to a semantics where priority values may change during execution according to some evolution rules.
-In our work, actions exhibit a two-level static priority structure, with certain ones being designated as “prioritised” and others as “unprioritised”.
+In our work, actions exhibit a two-level static priority structure, some of them ones being designated as “prioritised” and others as “unprioritised”.
 
@@
 One of the objectives is to reach an accurate representation of cooperating components in the model, that was not fulfilled with the initial semantics.
-We then develop an efficient under-approximation of the reachability of the state of independent components on a subclass of this new framework, thus allowing to compute efficient static analysis.
+We then develop an efficient under-approximation of the reachability of the state of components on a subclass of this new framework, thus allowing to compute efficient static analysis.
 This local reachability under-approximation can be also easily extended to study the reachability of a global state.
@@
 The method developed in this paper has been implemented into the existing Pint library and tested on a large-scale biological model containing 94 components.
-This piece of software turned out to be conclusive in all cases and results were computed in hundredths of seconds,
+The under-approximation turned out to be conclusive in all cases and results were computed in hundredths of seconds,
 thus overtaking the efficiency of usual model-checkers.
@@
 If $A$ and $B$ are sets,
-$f : A \rightarrow B$ denotes an application $f$ that maps elements of $A$ to elements of $B$.
-$\lfp{x_0}{x}{x'}$ is the least fixed point greater that $x_0$ of the function $x \mapsto x'$.
+$f : A \rightarrow B$ denotes an application $f$ that maps the elements of $A$ to elements of $B$.
+$\lfp{x_0}{x}{x'}$ is the least fixed point of the function $x \mapsto x'$ which is greater that $x_0$ .
 The Cartesian product is denoted $\times$.

### 2013-04-02 parts/sa.tex
several fixes; first final version
minor fixes; third final version

@@
-\section{Static analysis}\label{sec:sa}
+\section{Static Analysis}\label{sec:sa}
 
@@
 
-We define $\concr(\w)$ as the set of scenarios concretising an objective sequence $\w$ in the context $\ctx$.
+We denote $\concr(\w)$ the set of scenarios concretising an objective sequence $\w$ in the context $\ctx$.
 In \pref{def:uconcr}, we define $\uconcr(\w)$ as equal to $\concr(\w)$ if and only if $\concr(\w)$ contains scenarios starting from all states $s \subseteq \ctx$.
@@
 a node in $\Obj$ is an objective to reach a given process
-and a node in $\Sol$ is a sets of processes required for the solving.
-An objective $P \in \Obj$ is solvable if the abstractions of bounce sequences $\aBS(P) \in \Sol$ (\pref{def:aBS}) can be reached (\pref{eq:ESol1}), leading to several required processes (\pref{eq:ESol2}).
-If $a$ is a component, the reachability of a process $a_i$ is approximated by the ability to solve all objectives $\PHobjp{a}{j}{i} \in \Obj$ for all $a_j$ in the initial context (\pref{eq:EReq});
-if $a$ is a cooperative sort, the reachability of $a_i$ is directly solved by the set of the processes $\csState(a_i)$ (\pref{def:csState}) it represents (\pref{eq:EPrio}).
-The resolution of an objective $P$ may a process of $\PHsort(P)$, \ie $\gCont(\PHsort(P), P) \neq \emptyset$ (\pref{def:maxCont}); in this cas, the objective is re-targeted (\pref{eq:ECont}).
-\pref{eq:Vw}, \eqref{eq:Vproc} and \eqref{eq:VE} ensure that all required nodes are in $\cwV$.
-Finally, as the active process of every sort may evolve, $\cwB$ is obtained iteratively by saturation with every process it contains,
+and a node in $\Sol$ is a set of processes required for the solving.
+An objective $P \in \Obj$ is solvable if the abstractions of bounce sequences $\aBS(P) \in \Sol$ (\pref{def:aBS}) can be reached (\pref{eq:ESol1}), thus leading to several required processes (\pref{eq:ESol2}).
+If $a \in \components$, the reachability of one of its process $a_i$ is approximated by the ability to solve all objectives $\PHobjp{a}{j}{i} \in \Obj$ for all $a_j$ in the initial context (\pref{eq:EReq});
+if $a \in \cs$, the reachability of $a_i$ is simply solved by the set of processes $\csState(a_i)$ (\pref{def:csState}) that it represents (\pref{eq:EPrio}).
+The solving of an objective $P$ may require a process of $\PHsort(P)$, \ie $\gCont(\PHsort(P), P) \neq \emptyset$ (\pref{def:maxCont}); in this case, $P$ is re-targeted (\pref{eq:ECont}).
+\pref{eq:Vw}, \eqref{eq:Vproc} and~\eqref{eq:VE} ensure that all required nodes are in $\cwV$.
+Finally, as the active process of every sort may evolve, $\cwB$ is obtained by iteratively saturating with every process it contains,
 \ie by overriding its initial context $\ctx$ by $\allprocs(\V, \E)$, defined by:
@@
   The graph of local causality $\cwB = (\Bv, \Be)$ is defined as: $\cwB = \lfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs(\myB)}}$,
-  where $\myB = (\cwV, \cwE)$ is the smallest graph where:
+  where $\myB = (\cwV, \cwE)$ is the smallest graph with
   $\cwV \subset \Proc \cup \Obj \cup \Sol$ and $\cwE \subset \cwV \times \cwV$
@@
 
-In the graph of local causality, an edge linking a process of a cooperative sort to a solution set $ps$ is said coherent (\pref{def:coherent}) if none of the processes in $ps$ conflict with the children processes of $ps$.
+In the graph of local causality, an edge $(p, ps) \in \Proc \times \Sol$ %linking a process of a cooperative sort to a solution set $ps$
+is said coherent (\pref{def:coherent}) if none of the processes in $ps$ conflict with the children processes of $ps$.
 Then, \pref{th:approxinf} gives a sufficient condition for the concretization of a sequence of objectives in a given context,

### 2013-05-21 parts/ccl.tex
some corrections after the reviews

@@
 models with more than two classes of priorities, that do not only contain components of cooperative sorts, or whose behaviour may contain cycles or cyclic attractors.
-Finally, in order to take into account quantitative data in transition delays, the overall approximation method could be extended to handle evolution that are chronometric instead of only chronologic.
+Finally, in order to take into account quantitative data in transition delays, the overall approximation method could be extended to handle evolutions that are chronometric instead of only chronologic.

### 2013-05-21 parts/def-ph.tex
several fixes; first final version
minor fixes; third final version
some corrections after the reviews

@@
-\section{The Process Hitting framework}
+\section{The Process Hitting Framework}
 
@@
   If $k \in \sN^*$, a \emph{Process Hitting with $k$ classes of priorities} is a triplet $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$,
-  where $\PHa^{\langle k \rangle} = (\PHa^{(1)}; \dots; \PHa^{(k)})$ is a $k$-uplet and:
+  where $\PHa^{\langle k \rangle} = (\PHa^{(1)}; \dots; \PHa^{(k)})$ is a $k$-tuple and:
   \begin{itemize}
-    \item $\PHs \DEF \{a,b,\dots\}$ is the finite set of \emph{sorts},
-    \item $\PHl \DEF \underset{a \in \PHs}{\times} \PHl_a$ is the finite set of \emph{states}, where $\PHl_a = \{a_0 ; \ldots ; a_{l_a}\}$ is the finite set of \emph{processes} of sort $a \in \PHs$ and $l_a \in \sN^*$.
+    \item $\PHs \DEF \{a, b, \dots\}$ is the finite set of \emph{sorts},
+    \item $\PHl \DEF \underset{a \in \PHs}{\times} \PHl_a$ is the finite set of \emph{states}, where $\PHl_a = \{a_0, \ldots, a_{l_a}\}$ is the finite set of \emph{processes} of sort $a \in \PHs$ and $l_a \in \sN^*$.
 Each process belongs to a unique sort: $\forall (a_i; b_j) \in \PHl_a \times \PHl_b, a \neq b \Rightarrow a_i \neq b_j$,
@@
   We also extend this definition to a set of processes $ps$ given that all processes are from different sorts by the override of each process:
-  $\forall as \subset \PHs, \forall ps \in \underset{a \in as}{\times} \PHl_a, s \Cap ps = s \underset{a_i \in ps}{\Cap} a_i$.
+  $\forall as \subseteq \PHs, \forall ps \in \underset{a \in as}{\times} \PHl_a, s \Cap ps = s \underset{a_i \in ps}{\Cap} a_i$.
 \end{definition}
@@
   \end{align*}
-  There also is especially: $\{ \PHhit{ab_{11}}{c_0}{c_1}, \PHhit{a_1}{a_1}{a_0}, \PHhit{a_0}{b_0}{b_1} \} \subset \PHh^{(2)}$.
+  There also is especially: $\{ \PHhit{ab_{11}}{c_0}{c_1}, \PHhit{a_1}{a_1}{a_0}, \PHhit{a_0}{b_0}{b_1} \} \subseteq \PHh^{(2)}$.
 
@@
 special treatment regarding the semantics of related actions.
-Furthermore, it is possible to chain cooperative sorts in order to express more complex cooperations or
-to decrease the number of processes created within each cooperative sort,
-as the static analysis method developed in \pref{sec:sa} does not suffer from the number of sorts but from the number of processes in one sort.
+Furthermore, it is possible to “factorise” cooperative sorts in order to decrease the number of processes created within each cooperative sort.
+For example, if three processes $x_1$, $y_1$ and $z_1$ cooperate,
+it is preferable to create a cooperative sort $xy$ with 4 processes to state the presence of $x_1$ and $y_1$
+and a second cooperative sort $xyz$ with 4 processes to state the presence of $xy_{11}$ and $z_1$,
+rather than a unique cooperative sort with 8 processes stating the presence of $x_1$, $y_1$ and $z_1$.
+This “factorisation” allows to prevent the combinatorial explosion of the number of processes in cooperative sorts,
+especially for cooperations between more than three processes.
+It may have computational consequences as the static analysis method developed in~\pref{sec:sa} does not suffer from the number of sorts but from the number of processes in each sort.
 
-The construction of cooperation in PH allows to encode any Boolean functions between cooperating processes \cite{PMR10-TCSB}.
+The construction of cooperation in PH allows to encode any Boolean function between cooperating processes \cite{PMR10-TCSB}.
 Due to the introduction of priorities into the PH framework,
@@
 This allows to gain the same expressivity in PH than in Boolean networks, as stated in \pref{ssec:hypothesis}.
-The aim of this paper is to allow the static analysis of the dynamics to be handled on PH models comprising such higher priory actions updating cooperative sorts.
+The aim of this paper is to allow the static analysis of the dynamics to be handled on PH models comprising such higher priority actions updating cooperative sorts.
 
-\todo{Nouvelle section pour les hypothèses + conséquences ?}
+%\todo{Nouvelle section pour les hypothèses + conséquences ?}
 \label{ssec:hypothesis}
@@
   The dynamics of $\restriction{\PH}{1}$ contains no cycles:
-  $\exists N \in \sN, \forall \in \PHl, \forall \delta \in \restriction{\Sce}{1}(s), |\delta| \leq N$.
+  $\exists N \in \sN, \forall s \in \PHl, \forall \delta \in \restriction{\Sce}{1}(s), |\delta| \leq N$.
 \end{criterion}
@@
   \end{align*}
+  where $(\PHh^{(1)})^{s+1}$ is the Cartesian product of $s+1$ times the set $\PHh^{(1)}$.
 \end{definition}
-\begin{criterion}[Cycle-freeness between prioritised actions]
+\begin{criterion}[Cycle-freeness in prioritised actions]
 \label{cr:cyclefreeness}
@@
 therefore, it must be only hit by prioritised actions,
-in a way that its local steady-states efficiently represents all configurations of its neighbouring sorts.
+in a way that its local steady-states efficiently represent all configurations of its neighbouring sorts.
 \begin{definition}[$\pfp : \PHs \rightarrow \powerset(\PHproc)$]
@@
 The criteria given in this subsection allow to define a class of PH models that is (weakly) bisimilar to Asynchronous Boolean Networks
-or, more generally, to the multivalued version of this framework, called Asynchronous Discrete Models (ADN).
+or, more generally, to the multivalued version of this framework, called Asynchronous Discrete Networks (ADN).
 A translation of ADN into PH is given in \pref{suppl:demotrad}, alongside with a demonstration of the weak bisimulation.
@@
   \begin{align*}
-    \update(s) = s \Cap \{ \pfp_{s}(a) \mid a \in CS \} \enspace.
+    \update(s) = s \Cap \{ \pfp_{s}(a) \mid a \in \cs \} \enspace.
   \end{align*}

### 2013-05-21 parts/intro.tex
some corrections after the reviews

@@
 This local reachability under-approximation can be also easily extended to study the reachability of a global state.
-Finally, as the subclass of models studied proves to be bisimilar to Asynchronous Discrete Networks, we state to have developed an efficient method to compute the reachability of a state and thus study the behaviour of such models.
+Finally, as the subclass of models studied proves to be bisimilar to Asynchronous Discrete Networks~\cite{Thomas73} \todo{Autre formalisme ?}, we state to have developed an efficient method to compute the reachability of a state and thus study the behaviour of such models.
 
@@
 and $\powerset(A)$ is the power set of $A$.
+$\sN$ is the set of natural numbers,
+$\sN^* = \sN \setminus \{ 0 \}$ is the set of positive natural numbers
+and $\segm{x}{y} = \{ x, x+1, \dots, y-1, y \}$ is the set of natural numbers from $x$ to $y$ included.
 If $x = (x_i)_{i \in \segm{1}{n}}$ is a sequence of elements indexed by $i \in \segm{1}{n}$,
@@
 $f : A \rightarrow B$ denotes an application $f$ that maps the elements of $A$ to elements of $B$.
-$\lfp{x_0}{x}{x'}$ is the least fixed point of the function $x \mapsto x'$ which is greater that $x_0$ .
+$\lfp{x_0}{x}{x'}$ is the least fixed point of the function $x \mapsto x'$ which is greater than $x_0$ .
 The Cartesian product is denoted $\times$.

### 2013-05-21 parts/sa.tex
some corrections after the reviews

@@
 
-The reachability of a process $a_j$ of a given sort $a$ from another process $a_i$ is called an objective and is denoted $\PHobjp{a}{j}{i}$ (\pref{def:obj}).
+The reachability of a process $a_j$ of a given sort $a$ from another process $a_i$ is called an objective and is denoted $\PHobjp{a}{i}{j}$ (\pref{def:obj}).
 \begin{definition}[Objective ($\Obj$)]
@@
   For an objective $P = \PHobj{a_i}{a_j} \in \Obj$, we define: $\PHsort(P) = a$, $\PHtarget(P)=a_i$, $\PHbounce(P)=a_j$,
-  and $P$ is \emph{trivial} if $a_i = a_j$.
+  and $P$ is said \emph{trivial} if $a_i = a_j$.
 
@@
 and the play of $\delta$ in $\ctx$ is $\ctx \PHplay \delta = \ctx \Cap \ceil(\delta)$,
-where $\ceil(\delta)$ is the set containing the last process (hitter or bounce) of each sort present in $\delta$.
+where $\ceil(\delta)$ is the set containing the last process in the sequence $\delta$ (hitter or bounce) of every sort mentioned in $\delta$.
 
@@
 Bounce sequences are used to find local solutions to a given objective.
-A bounce sequence can be abstracted into sets of all its hitters that are not in sort $a$.
-This abstraction allows to propagate an objective into objectives on other sots.
+A bounce sequence on $a$ can be abstracted into sets of all its hitters that are not in sort $a$ (\pref{def:aBS}).
+This abstraction allows to propagate an objective on the sort $a$ into objectives on other sots.
 In the following, we denote: $\Sol = \powerset(\PHproc)$.
@@
 \label{def:aBS}
+  The \emph{abstractions of bounce sequences} of an objective $P$, denoted by the set $\aBS(P)$, are the sets of hitters of bounce sequences solving $P$:
   \[
@@
 
-For any objective $P$ and context $\ctx$, \pref{def:maxCont} allows to obtain the set of processes of sort $\PHsort(P)$ are required to solve $P$ in $\ctx$, given by $\gCont_\ctx(\PHsort(P), P)$.
+For any objective $P$ and context $\ctx$, \pref{def:maxCont} allows to obtain the set of processes of sort $\PHsort(P)$ that are required to solve $P$ in $\ctx$, given by $\gCont_\ctx(\PHsort(P), P)$.
 \begin{definition}[$\gCont_\ctx : \Sigma \times \Obj \rightarrow \powerset(\PHproc)$]
@@
 
-The graph of local causality $\cwB = (\V, \E)$ defined in \pref{def:glc} is a graph where $\V \subset \Proc \cup \Obj \cup \Sol$ and $\E \subset \V \times \V$.
+The graph of local causality $\cwB = (\V, \E)$ defined in \pref{def:glc} is a graph where $\V \subseteq \Proc \cup \Obj \cup \Sol$ and $\E \subseteq \V \times \V$.
 A node in $\PHproc$ is a required process,
@@
   where $\myB = (\cwV, \cwE)$ is the smallest graph with
-  $\cwV \subset \Proc \cup \Obj \cup \Sol$ and $\cwE \subset \cwV \times \cwV$
+  $\cwV \subseteq \Proc \cup \Obj \cup \Sol$ and $\cwE \subseteq \cwV \times \cwV$
   so that:
   \begin{align}
-    \w &\subset \cwV \label{eq:Vw} \\
+    \w &\subseteq \cwV \label{eq:Vw} \\
     P \in \VProc &\Rightarrow \PHbounce(P) \in \cwV \label{eq:Vproc} \\
@@
     a \in \cs \wedge a_i \in \VProc \wedge ps \in \csState(a_i) &\Rightarrow (a_i, ps) \in \cwE \label{eq:EPrio} \\
-    P \in \VObj \wedge q \in \gCont_\ctx(\PHsort(P), P) &\Rightarrow (P, \PHobj{q}{\PHbounce(P)}) \in \cwE \label{eq:ECont}
+    P \in \VObj \wedge q \in \gCont_\ctx(\PHsort(P), P) &\Rightarrow (P, \PHobj{q}{\PHbounce(P)}) \in \cwE \label{eq:ECont} \!
   \end{align}
@@
   An edge $(x, y) \in \cwE$ is said coherent if and only if:
-  $(x, y) \in \Be \cap (\Proc \times \Sol) \Rightarrow y$ has no children process $a_j \in \Bv \cap \Proc$ so that $\exists a_i \in y$, $a_i \neq a_k$.
+  $(x, y) \in \Be \cap (\Proc \times \Sol) \Rightarrow y$ has no children process $a_j \in \Bv \cap \Proc$ so that $\exists a_i \in y$, $a_i \neq a_j$.
 \end{definition}
@@
 
-    \node[Aproc,below of=c01s] (ab11) {$ab_{11}$};
+    \node[AprocPrio,below of=c01s] (ab11) {$ab_{11}$};
     \node[AsolPrio,below of=ab11] (ab11s) {};
@@
     (c01s) edge (ab11)
-    (ab11) edge (ab11s)
+    (ab11) edge[aSPrio] (ab11s)
     (ab11s) edge (a1) edge (b1)
@@
     The graph of local causality of the PH model in \pref{fig:ph-livelock}.
-    \pref{th:approxinf} is inconclusive on this example as the only solution of process $ab_{11}$ is not coherent (\pref{def:coherent}).
+    Rectangular nodes containing a single process are elements in $\Proc$,
+    nodes containing a couple of processes are elements in $\Obj$
+    and circle nodes are elements in $\Sol$.
+    %The double arrow and the two surrounding nodes represent the only edge in $\Proc \times \Sol$.
+    \pref{th:approxinf} is inconclusive on this example as edge $(ab_{11}, \{ a_1, b_1 \}) \in \Proc \times \Sol$ (here represented with a double line) is not coherent (\pref{def:coherent}).
+    Indeed, $a_0 \in \Proc$ is a child of $\{ a_1, b_1 \}$, but $a_0 \neq a_1$ (and the same also stands for $b_0$).
   }
@@
 
-It is also possible to compute the reachability of a set of states $S \subset \PHl$ by creating several actions $\PHhit{\total_s}{\reach_0}{\reach_1}$ in $\PHh^{(2)}$ for each state $s \in S$.
+It is also possible to compute the reachability of a set of states $S \subseteq \PHl$ by creating several actions $\PHhit{\total_s}{\reach_0}{\reach_1}$ in $\PHh^{(2)}$ for each state $s \in S$.

### 2013-05-21 parts/suppl-ph-dn.tex
several fixes; first final version
some corrections after the reviews

@@
 
-\section{Weak Bisimulation of Asynchronous Discrete Networks}
+\section{Weak Bisimulation of Asynchronous Discrete Networks (\pref{ssec:hypothesis})}
 \label{suppl:demotrad}
@@
 Typically $f^i$ depends on a subset of components that we denote $\DNdep(f^i)$.
-In the case of Asynchronous Discrete Networks (ADN), a transition relation $\DNtrans\subset \mathbb
+In the case of Asynchronous Discrete Networks (ADN), a transition relation $\DNtrans\subseteq \mathbb
 F\times \mathbb F$ is defined such that $x\DNtrans x'$ if and only if there exists a unique

### 2013-05-22 parts/def-ph.tex
new TODOs and minor changes

@@
 \end{definition}
+
+\todo{Mieux replacer le PH dans un contexte biologique (catalytic networks, metabolic networks)}
 
@@
   In this paper, we only consider Process Hitting with $2$ classes of priorities:
-  $\PH = (\PHs; \PHl; \PHa^{\langle 2 \rangle})$.
+  \begin{align*}
+    \PH = (\PHs; \PHl; \PHa^{\langle 2 \rangle}) \enspace.
+  \end{align*}
 \end{criterion}
@@
   The dynamics of $\restriction{\PH}{1}$ contains no cycles:
-  $\exists N \in \sN, \forall s \in \PHl, \forall \delta \in \restriction{\Sce}{1}(s), |\delta| \leq N$.
+  \begin{align*}
+    \exists N \in \sN, \forall s \in \PHl, \forall \delta \in \restriction{\Sce}{1}(s), |\delta| \leq N \enspace.
+  \end{align*}
 \end{criterion}
@@
   A sort $a \in \PHs$ is a \emph{well-formed component} if and only if:
-  $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) = 2$.\\
+  \begin{align*}
+    \forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) = 2 \enspace.
+  \end{align*}
   We call $\components$ the set of well-formed components.
@@
   \begin{align*}
-  \PHh(a, b) = \{ (h_i)_{i \in \segm{1}{s+1}} \in (\PHh^{(1)})^{s+1} &\mid s \in \sN, \PHsort(\PHhitter(h_1)) = a \wedge \PHsort(\PHtarget(h_{s+1})) = b \\
+  \PHh(a, b) = \{ (h_i)_{i \in \segm{1}{s+1}} &\in (\PHh^{(1)})^{s+1} \mid s \in \sN \\
+    & \wedge \PHsort(\PHhitter(h_1)) = a \wedge \PHsort(\PHtarget(h_{s+1})) = b \\
     & \wedge \forall i \in \segm{1}{s}, \PHsort(\PHtarget(h_{i})) = \PHsort(\PHhitter(h_{i+1})) \}
@@
   There is no cycle in chains of actions:
-  $\forall a \in \PHs, \PHh(a, a) = \emptyset$.
+  \begin{align*}
+    \forall a \in \PHs, \PHh(a, a) = \emptyset \enspace.
+  \end{align*}
 \end{criterion}

### 2013-05-22 parts/intro.tex
new TODOs and minor changes

@@
 (which would have led to a huge number of states, hopelessly too huge to be analysed).
+\todo{Mieux replacer le PH dans un contexte biologique (catalytic networks, metabolic networks)}
 
@@
 This local reachability under-approximation can be also easily extended to study the reachability of a global state.
-Finally, as the subclass of models studied proves to be bisimilar to Asynchronous Discrete Networks~\cite{Thomas73} \todo{Autre formalisme ?}, we state to have developed an efficient method to compute the reachability of a state and thus study the behaviour of such models.
+Finally, as the subclass of models studied proves to be bisimilar to Asynchronous Discrete Networks~\cite{Thomas73,Thomas95} \todo{Autre formalisme ?
+Cf.
+de Jong}, we state to have developed an efficient method to compute the reachability of a state and thus study the behaviour of such models.
 

### 2013-05-22 parts/sa.tex
new TODOs and minor changes

@@
 
-For any objective $P$ and context $\ctx$, \pref{def:maxCont} allows to obtain the set of processes of sort $\PHsort(P)$ that are required to solve $P$ in $\ctx$, given by $\gCont_\ctx(\PHsort(P), P)$.
+For any objective $P$ and context $\ctx$, \pref{def:maxCont} gives the set of processes of sort $\PHsort(P)$ that are required to solve $P$ in $\ctx$, given by $\gCont_\ctx(\PHsort(P), P)$.
 \begin{definition}[$\gCont_\ctx : \Sigma \times \Obj \rightarrow \powerset(\PHproc)$]

### 2013-05-27 parts/intro.tex
other chages after review (references, context)

--- 2013-05-21 parts/intro.tex
@@
 Usual formal frameworks for such modelling activities are state-transition systems or process algebras. % Petri nets
-We developed a quite similar framework named the Process Hitting \cite{PMR10-TCSB}: %, with the aim of avoiding to build the whole state space in order to be able to tackle very large systems
-our motivation behind this framework was to design a model and analysis techniques that avoid to build the whole state space.
-This allows to tackle very large systems
-(which would have led to a huge number of states, hopelessly too huge to be analysed).
+We developed a quite similar framework named the Process Hitting \cite{PMR10-TCSB},
+consisting in a restriction where the evolution of a component is determined by the state of at most one other component that does not evolve.
+In a sense, these kind of actions are of the form $X + Y \rightarrow X + Z$ where $X$ behaves like a catalyst molecule that “hits” another molecule $Y$ and changes it into $Z$, without being itself changed.
+Assuming catalysts are always available, this can represent any biochemical system made of monomolecular reactions, and can also represent catalytic networks such as metabolic networks.
+%, with the aim of avoiding to build the whole state space in order to be able to tackle very large systems
+Our motivation behind this framework was to design a model and analysis techniques that avoid to build the whole state space.
+This allows to tackle very large systems (which would have led to a huge number of states, hopelessly too huge to be analysed).
 
@@
 to improve the accuracy of the description of the studied systems dynamics.
-The idea for this is to introduce timing features into its model.
+The idea for this is to introduce timing features into models.
 Indeed, we are interested in taking into account some knowledge about the relative length of some phenomena as it is a way to refute some models (parameters) that are inconsistent with the observed dynamic behaviours.
 In this paper, we are dealing with these timing properties through priorities,
-that are based on the simple founding idea that the highest priority actions have to be processed before the other ones.
+that are based on the simple founding idea that prioritised actions have to be processed before the other ones.
+Indeed, due to the Process Hitting framework restrictions, bimolecular reactions are not immediately available, but one can simulate them with an encoding called “cooperation”.
+That encoding however introduces extra reactions, and this is where the priorities become useful, if not necessary.
+The extra reactions can be given “infinite speed” (high priority) so that they do not affect the behaviour of “normal” (low priority) reactions, including the bimolecular ones.
 
@@
 The concept is derived in two directions: dynamic versus static, the difference being naturally that the former one refer to a semantics where priority values may change during execution according to some evolution rules.
-In our work, actions exhibit a two-level static priority structure, some of them ones being designated as “prioritised” and others as “unprioritised”.
+In our work, actions exhibit a two-level static priority structure, some of them being designated as “prioritised” and others as “unprioritised”.
 
@@
 This local reachability under-approximation can be also easily extended to study the reachability of a global state.
-Finally, as the subclass of models studied proves to be bisimilar to Asynchronous Discrete Networks~\cite{Thomas73} \todo{Autre formalisme ?}, we state to have developed an efficient method to compute the reachability of a state and thus study the behaviour of such models.
+Finally, as the subclass of models studied proves to be bisimilar to Asynchronous Discrete Networks~\cite{kauffman69,Thomas73,deJong02}, we state to have developed an efficient method to compute the reachability of a state and thus study the behaviour of such models.
 
@@
 $f : A \rightarrow B$ denotes an application $f$ that maps the elements of $A$ to elements of $B$.
-$\lfp{x_0}{x}{x'}$ is the least fixed point of the function $x \mapsto x'$ which is greater than $x_0$ .
+$\lfp{x_0}{x}{x'}$ is the least fixed point of the function $x \mapsto x'$ which is greater than $x_0$.
 The Cartesian product is denoted $\times$.

### 2013-05-27 parts/suppl-ph-dn.tex
new TODOs and minor changes
other chages after review (references, context)

@@
 $\mathbb F^i$ that we note $\mathbb{F}^i = \segm{1}{l_i}$.
-For each component $i\in\segm{1}{n}$, a map $\mathbb F \mapsto \mathbb F^i$ is defined, where
+For each component $i\in\segm{1}{n}$, a map $\mathbb F \rightarrow \mathbb F^i$ is defined, where
 $\mathbb F = \mathbb F^1 \times \cdots \times \mathbb F^n$, giving the next value of the component
@@
   and $\forall i\in\segm{1}{n}$,
-  $f^i: \mathbb{F} \mapsto \mathbb{F}^i$ with
+  $f^i: \mathbb{F} \rightarrow \mathbb{F}^i$ with
   $\mathbb{F}^i = \segm{1}{l_i}$.
@@
 
-Let us denote by $\toPH\DNdef$ the encoding of the ADN $\DNdef$ in Process Hitting with $2$ classes
-of priorities (\pref{def:DN2PH}).
+Let us denote the encoding of the ADN $\DNdef$ in Process Hitting with $2$ classes
+of priorities by $\toPH\DNdef$ (\pref{def:DN2PH}).
 For each component $i\in\segm{1}{n}$ of the ADN, two sorts are built: $a^i$ acting for the component

### 2013-05-27 parts/def-ph.tex
other chages after review (references, context)
formatting

@@
 
-\todo{Mieux replacer le PH dans un contexte biologique (catalytic networks, metabolic networks)}
+%\todo{Mieux replacer le PH dans un contexte biologique (catalytic networks, metabolic networks)}
 
@@
   In this paper, we only consider Process Hitting with $2$ classes of priorities:
-  \begin{align*}
-    \PH = (\PHs; \PHl; \PHa^{\langle 2 \rangle}) \enspace.
-  \end{align*}
+  $\PH = (\PHs; \PHl; \PHa^{\langle 2 \rangle})$.
 \end{criterion}
@@
   The dynamics of $\restriction{\PH}{1}$ contains no cycles:
-  \begin{align*}
-    \exists N \in \sN, \forall s \in \PHl, \forall \delta \in \restriction{\Sce}{1}(s), |\delta| \leq N \enspace.
-  \end{align*}
+  $\exists N \in \sN, \forall s \in \PHl, \forall \delta \in \restriction{\Sce}{1}(s), |\delta| \leq N$.
 \end{criterion}
@@
 \end{definition}
+%
 \begin{criterion}[Cycle-freeness in prioritised actions]
 \label{cr:cyclefreeness}
-  There is no cycle in chains of actions:
-  \begin{align*}
-    \forall a \in \PHs, \PHh(a, a) = \emptyset \enspace.
-  \end{align*}
+  There is no cycles in chains of actions:
+  $\forall a \in \PHs, \PHh(a, a) = \emptyset$.
 \end{criterion}

### 2013-05-27 parts/intro.tex
refactor intro (adapted to models with few expression levels)

@@
 %, with the aim of avoiding to build the whole state space in order to be able to tackle very large systems
-Our motivation behind this framework was to design a model and analysis techniques that avoid to build the whole state space.
-This allows to tackle very large systems (which would have led to a huge number of states, hopelessly too huge to be analysed).
+Our motivation behind this framework was to design a model and analysis techniques adapted to biological modelling.
+These analyses avoid to build the whole state space, which allows to tackle very large systems (that would have led to a huge number of states, hopelessly too huge to be analysed).
+They are based on the fact that most biological models have few levels of expression per component:
+in Boolean networks~\cite{kauffman69,Thomas73} there are only two levels per component and in its multivalued equivalent, Asynchronous Discrete Networks~\cite{deJong02}, components rarely have more that four levels.
 
@@
 to improve the accuracy of the description of the studied systems dynamics.
-The idea for this is to introduce timing features into models.
-Indeed, we are interested in taking into account some knowledge about the relative length of some phenomena as it is a way to refute some models (parameters) that are inconsistent with the observed dynamic behaviours.
+The idea for this is to introduce timing features into models:
+we are interested in taking into account some knowledge about the relative length of some phenomena as it is a way to refute some models (or parameters) that are inconsistent with the observed dynamic behaviours.
 In this paper, we are dealing with these timing properties through priorities,
@@
 This local reachability under-approximation can be also easily extended to study the reachability of a global state.
-Finally, as the subclass of models studied proves to be bisimilar to Asynchronous Discrete Networks~\cite{kauffman69,Thomas73,deJong02}, we state to have developed an efficient method to compute the reachability of a state and thus study the behaviour of such models.
+Finally, as the subclass of models studied proves to be bisimilar to Asynchronous Discrete Networks, we state to have developed an efficient method to compute the reachability of a state and thus study the behaviour of such models.
 

### 2013-05-28 parts/intro.tex
changes by Morgan's review

@@
 Among these questions, a major one is to understand precisely how biological systems evolve and behave; why and how they change their usual behaviours…
-This leads to questions about the accessibility (possible or inevitable) of some states.
+This leads to questions about the reachability (possible or inevitable) of some states.
 The ultimate goal is to discover how it could be possible to prevent biological systems from reaching some pathological states.
@@
 The concept of priority is much straightforward in the approach of process algebras as it was shown by R.~Cleaveland and M.~Hennessy in \cite{Cleaveland199058,Cleaveland99prioritiesin} and their abstractions and equivalences were studied in \cite{Cleaveland:2007:PAP:1282576.1282847}.
-It was later extended for applications in the field of system biology by M.~John \textit{et~al.} \cite{jlnu2010}.
+It was later extended for applications in the field of systems biology by M.~John \textit{et~al.} \cite{jlnu2010}.
 
 \paragraph{Contributions}
-Since our formalism (the Process Hitting) can be considered as a subset of CCS, %is inspired from the $\pi$-calculus,
+Since our formalism (the Process Hitting) can be considered as a subset of Calculus of Communicating Systems, %is inspired from the $\pi$-calculus,
 our work is related to such semantic ramifications of extending traditional process algebras with the concepts of priority that allow for some transitions to be given precedence over others.
-The concept is derived in two directions: dynamic versus static, the difference being naturally that the former one refer to a semantics where priority values may change during execution according to some evolution rules.
+The concept is derived in two directions: dynamic versus static, the difference being naturally that the former one refers to a semantics where priority values may change during execution according to some evolution rules.
 In our work, actions exhibit a two-level static priority structure, some of them being designated as “prioritised” and others as “unprioritised”.

### 2013-05-31 underapprox-tcrsig94/run.sh
fix errors in underapprox-tcrsig94 example

@@ -1,5 +1,5 @@
 #!/usr/bin/env bash
-ph="../model.ph"
+ph="model.ph"
 outputs="sre ap1 nfkb nfat"
 mode=${1}
 

### 2013-08-15 main.tex
several fixes; first final version
titles
some corrections after the reviews
other chages after review (references, context)
boldface abstract

@@
 
-\def\lastname{Folschette \emph{et al}}
+\def\lastname{Folschette \emph{et al.}}
 
@@
 \begin{frontmatter}
-\title{Under-approximation of reachability in multivalued asynchronous networks}
+\title{Under-approximation of Reachability in Multivalued Asynchronous Networks}
 
@@
 
-\begin{abstract}
+\begin{abstract}\bfseries
 The Process Hitting is a recently introduced framework designed for the modelling of concurrent systems.

### 2013-08-15 main.tex
boldface 'Abstract' + Loïc's adress

@@
 \author{Loïc Paulevé}
-\address{ETH Zürich, Switzerland.}
+%\address{ETH Zürich, Switzerland.}
+\address{BISON group, Automatic Control Laboratory, ETH Zürich\\
+Physikstrasse 3, 8092 Zurich, Switzerland.}
 
@@
 
-\begin{abstract}\bfseries
+\def\abstractname{\textbf{Abstract}}
+\begin{abstract}
 The Process Hitting is a recently introduced framework designed for the modelling of concurrent systems.

### 2014-02-28 parts/models.tex
add new section and TODOs for the TCS extended version

\section{\todo{Title?} Equivalence with other frameworks}

\subsection{Asynchronous Discrete Networks}
\todo{Detail the equivalence with ADNs (cf. the annex)}

\subsection{PH with multiple classes of priorities}
\todo{Reduce and reuse the flattening method}

### 2014-03-03 main.tex
add new section and TODOs for the TCS extended version
change documentclass to elsarticle + .cls and .bst files

@@
-\documentclass{entcs}
-
-\usepackage{entcsmacro}
+\documentclass{elsarticle}
 
@@
 
+% Theorems and definitions
+\newdefinition{definition}{Definition}
+\newdefinition{criterion}{Criterion}
+\newtheorem{theorem}{Theorem}
+\newproof{example}{Example}
+\newproof{rawproof}{Proof}
+
+\newenvironment{proof}{\begin{rawproof}}{\hfill$\Box$\end{rawproof}}
+
+% Pretty references
 \usepackage{prettyref}
@@
 \newrefformat{fig}{Fig.~\ref{#1}}
-%\newrefformat{prop}{Property~\ref{#1}}
-\newrefformat{prop}{Proposition~\ref{#1}}
 \newrefformat{lem}{Lemma~\ref{#1}}
@@
 \def\pref{\prettyref}
-
-%\usepackage{ntheorem}
-%\theorembodyfont{\upshape}
-%\newtheorem{definition}{Definition}{}{}
-%\newtheorem*{example}{Example}{}{}
-%\newtheorem{property}{Property}{}{}
-%\newtheorem{proposition}{Proposition}{}{}
 
@@
 
+% Restriction notation
 \def\restriction#1#2{\mathchoice
@@
 % Commandes À FAIRE
-%\usepackage{color} % Couleurs du texte
+\usepackage{color} % Couleurs du texte
 %\definecolor{darkgreen}{rgb}{0,0.5,0}
 %\newcommand{\towrite}[1]{\textcolor{darkgreen}{[#1]}}
-%\newcommand{\todo}[1]{\textcolor{red}{[[#1]]}}
+\newcommand{\todo}[1]{\textcolor{red}{\textbf{[#1]}}}
 
-% Id est
-\newcommand{\ie}{i.e.~}
+% Special notations
+\newcommand{\ie}{i.e.,\ }
+\newcommand{\Ie}{I.e.,\ }
+\newcommand{\eg}{e.g.,\ }
+\newcommand{\Eg}{E.g.,\ }
+\newcommand{\resp}{resp.\ }
+\newcommand{\Resp}{Resp.\ }
 
@@
 
-\author{Maxime Folschette\thanksref{myemail}}
-\address{LUNAM Universit\'e, \'Ecole Centrale de Nantes, IRCCyN UMR CNRS 6597\\
-(Institut de Recherche en Communications et Cybern\'etique de Nantes)\\
-1 rue de la No\"e - B.P. 92101 - 44321 Nantes Cedex 3, France.}
-\thanks[myemail]{\url{Maxime.Folschette@irccyn.ec-nantes.fr}}
+\author[irccyn]{Maxime Folschette}
+\ead{Maxime.Folschette@irccyn.ec-nantes.fr}
+\author[eth]{Loïc Paulevé}
+\author[irccyn]{Morgan Magnin}
+\author[irccyn]{Olivier Roux}
 
-\author{Loïc Paulevé}
-%\address{ETH Zürich, Switzerland.}
-\address{BISON group, Automatic Control Laboratory, ETH Zürich\\
-Physikstrasse 3, 8092 Zurich, Switzerland.}
-
-\author{Morgan Magnin}
-\address{LUNAM Universit\'e, \'Ecole Centrale de Nantes, IRCCyN UMR CNRS 6597\\
+\address[irccyn]{LUNAM Universit\'e, \'Ecole Centrale de Nantes, IRCCyN UMR CNRS 6597\\
 (Institut de Recherche en Communications et Cybern\'etique de Nantes)\\
@@
 
-\author{Olivier Roux}
-\address{LUNAM Universit\'e, \'Ecole Centrale de Nantes, IRCCyN UMR CNRS 6597\\
-(Institut de Recherche en Communications et Cybern\'etique de Nantes)\\
-1 rue de la No\"e - B.P. 92101 - 44321 Nantes Cedex 3, France.}
+\address[eth]{BISON group, Automatic Control Laboratory, ETH Zürich\\
+Physikstrasse 3, 8092 Zurich, Switzerland.}
 
-\def\abstractname{\textbf{Abstract}}
 \begin{abstract}
@@
 \begin{keyword}
-qualitative modelling,
-model abstraction,
-static analysis,
+qualitative modelling \sep
+model abstraction \sep
+static analysis \sep
 asynchronous network
@@
 
+\input{parts/models}
+
 \input{parts/example}
@@
 
-\bibliographystyle{entcs}
+\bibliographystyle{elsarticle-num}
 \bibliography{biblio}

### 2014-03-03 parts/def-ph.tex
add new section and TODOs for the TCS extended version
change documentclass to elsarticle + .cls and .bst files

@@
 
-\begin{figure}[p]
+\begin{figure}[ht]
   \centering
@@
 Each process of sort $a$ and $b$ hit $ab$ to make it bounce to the process reflecting the status of the sorts $a$ and $b$
-(e.g., $\PHfrappe{a_1}{ab_{00}}{ab_{10}}$ and $\PHfrappe{a_1}{ab_{01}}{ab_{11}}$).
+(\eg $\PHfrappe{a_1}{ab_{00}}{ab_{10}}$ and $\PHfrappe{a_1}{ab_{01}}{ab_{11}}$).
 Then, to represent the cooperation between $a_1$ and $b_1$, the process $ab_{11}$ hits $c_0$ to make it bounce to $c_1$ instead of independent hits from $a_1$ and $b_1$.
@@
 which would allow the play of an infinite sequence of prioritised actions in “zero time”.
+\todo{Change “Criterion” to something else?}
 \begin{criterion}[2 classes of priorities]
@@
   A sort $a \in \PHs$ is a \emph{well-formed cooperative} sort if and only if:
-  \begin{enumerate}
+  \begin{enumerate}[(i)]
     \item $\exists b \in \PHs, \PHh(b, a) \neq \emptyset$
@@
 
-In the following we simply write “component” (resp.~“cooperative sort”) instead of “well-formed component” (resp.~“well-formed cooperative sort”).
+In the following we simply write “component” (\resp “cooperative sort”) instead of “well-formed component” (\resp “well-formed cooperative sort”).
 Finally, \pref{cr:compcs} states that the set of sorts of the considered PH must be divided between components and cooperative sorts.

### 2014-03-03 parts/suppl-ph-dn.tex
change documentclass to elsarticle + .cls and .bst files

@@
 $i\in\segm{1}{n}$ such that $\get{x'}{i}=f^i(x)$ and $\forall j\in\segm{1}{n}, j\neq i, \get{x'}{j}
-=\get{x}{j}$, i.e.~one and only one component has been updated.
+=\get{x}{j}$, \ie one and only one component has been updated.
 This is formalised in \pref{def:DN}.

### 2014-03-13 parts/models.tex
start flattening

@@
 \todo{Reduce and reuse the flattening method}
+
+\newcommand{\ov}{\overline}
+\newcommand{\F}{F}
+\newcommand{\Fopsymbol}{\F}
+\newcommand{\Fop}[1]{\Fopsymbol(#1)}
+\newcommand{\Fsem}[2]{\left[#1\right](#2)}
+%\newcommand{\Fall}{\F}
+
+Consider a PH with $k \in \sN^*$ classes of priories:
+$\ov{\PH} = (\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}})$.
+We want to translate it to a PH with $2$ classes of priorities
+$\PH = (\PHs; \PHl; \PHa^{\angles{2}})$
+that respects all Criteria given in \pref{ssec:hypothesis}.
+
+A playability property (PP) as defined in \pref{def:pp} is a formula where the atoms are processes of $\ov{\PH}$.
+
+\begin{definition}[Playability property language ($\F$)]
+  \label{def:pp}
+  A \emph{playability property} (PP) is an element of the language $\F$ inductively defined by:
+  \begin{itemize}
+    \item $\top$ and $\bot$ belong to $\F$;
+    \item if $a \in \ov{\PHs}$ and $a_i \in \ov{\PHl}_a$, then $a_i \in \F$ and we call it an \emph{atom};
+    \item if $P \in \F$ and $Q \in \F$, then $\neg P \in \F$, $P \wedge Q \in \F$ and $P \vee Q \in \F$.
+  \end{itemize}
+  We note $\Fsem{P}{s}$ the \emph{evaluation} of a PP $P \in \F$ in a state $s \in \ov{\PHl}$.
+  The semantics of this evaluation is the following for any state $s \in \ov{\PHl}$:
+  \begin{itemize}
+    \item if $P = a_i \in \ov{\PHs}_a$ is an atom, with $a \in \ov{\PHs}$, then $\Fsem{a_i}{s}$ is true iff $a_i \in s$;
+    \item if $P$ is not an atom, then $\Fsem{P}{s}$ is true iff all its subformulas are inductively true in $s$
+      with the classical semantics for the logic operators $\top$, $\bot$, $\neg$, $\wedge$ and $\vee$.
+  \end{itemize}
+\end{definition}
+
+Because we only use classical logic operators, the formulas of Boolean logic on distribution and negation (de Morgan's laws) can be used.
+We also have the following property for the negation of an atom:
+\[\forall a \in \ov{\PHs}, \forall a_i \in \ov{\PHl}_a, \Fsem{\neg a_i}{s}
+  \Leftrightarrow \Fsem{\bigvee_{\substack{a_j \in \PHl_a\\a_j \neq a_i}} a_j}{s}\]
+Indeed, if a process is not active in a state, this means that another process of the same sort is active.
+
+In \pref{def:fop}, we finally define the the operator $\Fopsymbol$ which characterizes the playability of an action
+given the semantics of PH (\pref{def:play}).
+\begin{definition}[Playability property of an action ($\Fopsymbol : \PHh \rightarrow \F$)]\label{def:fop}
+  $$\forall h \in \ov{\PHh}, \Fop{h} \equiv \hitter{h} \wedge
+    \left( \bigwedge_{\substack{g \in \PHh^{(n)}\\n < \prio(h)}}
+    \neg \left( \target{g} \wedge \hitter{g}\right) \right)$$
+\end{definition}
+
+By definition of the semantics of a PH given in \pref{def:play},
+an action $h \in \ov{\PHh}$ is playable in a state $s \in \ov{\PHl}$ iff $\Fsem{\Fop{h}}{s}$.
+
+\todo{--- Le reste de la traduction ici ---}
+
+\newcommand{\n}[1][h]{n^{#1}}
+\newcommand{\m}[1][h]{m^{#1}}
+
+Because we only use classical logic operators, we can compute the PP on any action in $\ov{\PH}$.
+For any action $h \in \ov{\PHh}$, this DNF takes the form:
+\[\Fop{h} \equiv \bot \qquad \text{or} \qquad
+  \Fop{h} \equiv \bigvee_{i \in \segm{1}{\n}} \left( \bigwedge_{j \in \segm{1}{\m_i}} p_{i,j} \right)\]
+where $\n \in \sN^*$ and $\forall i \in \segm{1}{\n}, \m_i \in \sN^*$.
+The case $\Fop{h} \equiv \bot$ means that the action can never be played
+because it is always preempted other actions with higher priorities.
+The case $\Fop{h} \not\equiv \bot$, on the other hand,
+can be seen as a disjunction of $\n$ smaller playability properties consisting only of conjunctions of atoms.
+These $\n$ conjunctions can be translated to as many prioritized cooperative sorts,
+thus creating a new PH model which is entailed in the restrictions depicted in \pref{ssec:hypothesis}.
+%Indeed, for any $i \in \segm{1}{\n}$, the PP $\bigwedge_{j \in \segm{1}{\m_i}} p_{i,j}$
+In this second case, we denote, for any $i \in \segm{1}{\n}$:
+$\PHdep{i}{h} = \{ \PHsort(p_{i,j}) \mid j \in \segm{1}{\m_i} \}$
+
+\todo{--- Le reste de la traduction ici ---}
+
+\begin{definition}[Equivalent Process Hitting]\label{def:equiv}
+  Two PH models $\ov{\PH} = (\ov{\PHs}; \ov{\PHl}; \ov{\PHh}^\angles{k})$ and $\PH = (\PHs; \PHl; \PHh^\angles{n})$,
+  where $k, n \in \sN^*$,
+  are \emph{equivalent} iff:
+  $$\forall s \in \ov{\PHl}, ( \exists h = \PHhit{A}{b_i}{b_j} \in \PHh, \Fsem{\F(h)}{s}
+    \Longleftrightarrow \exists g = \PHhit{\ov{A}}{b_i}{b_j} \in \ov{\PHh}, \Fsem{\F(g)}{s} )$$
+\end{definition}
+
+We note that several PH models can be equivalent to a same PH model.
+For example, adding actions that are never playable (due to priorities) allows to create an equivalent model.
+
+\begin{theorem}[Bisimilarity of equivalent PH]
+  Two equivalent PH models are bisimilar.
+\end{theorem}
+
+\begin{proof}
+  Let $\PH = (\PHs; \PHl; \PHh^\angles{k})$ and $\ov{\PH} = (\PHs; \PHl; \ov{\PHh}^\angles{n})$
+  two equivalent PH models, with $k, n \in \sN^*$.
+  We want to show:
+  $$\forall s, s' \in \PHl, s \neq s', s \trans{\PH} s' \Longleftrightarrow s \trans{\ov{\PH}} s' $$
+  Let $s, s' \in \PHl$ with $s \neq s'$.
+  ($\Rightarrow$) Suppose $s \trans{\PH} s'$.
+  It means that there exists $h = \PHhit{A}{b_i}{b_j} \in \PHh$ so that $s' = s \PHplay h = s \Cap b_j$
+  in $\PH$ (\pref{def:play}), \ie $\Fsem{\F(h)}{s}$ and $b_i \in s$.
+  As $\ov{\PH}$ is equivalent to $\PH$,
+  there exists $g = \PHhit{\ov{A}}{b_i}{b_j} \in \ov{\PHh}$ so that $\Fsem{\F(g)}{s}$ (\pref{def:equiv}).
+  Therefore, $g$ is playable in $s$ and $s \PHplay g = s \Cap b_j = s'$;
+  which means: $s \trans{\ov{\PH}} s'$
+  ($\Leftarrow$) Same reasoning.
+\end{proof}
+
+\begin{definition}[Flattening]
+  Given a PH model $\PH = (\PHs; \PHl; \PHh^\angles{k})$, where $k \in \sN^*$,
+  we call \emph{flattening} of $\PH$ any PH model $\ov{\PH} = (\PHs; \PHl; \ov{\PHh}^\angles{1})$
+  with 1 class of priority and cooperative actions that is equivalent to $\PH$.
+\todo{Is this definition really useful?}
+\end{definition}
+
+\begin{theorem}[Existence of a flattening]\label{th:exists-flattening}
+  For all $k \in \sN^*$, there exists a flattening of any PH model with $k$ priorities and cooperative actions.
+\todo{Is this theorem really useful?}
+\end{theorem}
+
+The demonstration of this theorem is given in the following subsection.
+
+\begin{comment}
+
+%\newcommand{\poz}{\F}
+%\newcommand{\pon}{P_{DNF}}
+%\newcommand{\unneg}{\mathsf{UnNeg}}
+%\newcommand{\negate}{\mathsf{Negate}}
+%\newcommand{\prednf}{\mathsf{Distribute}}
+%\newcommand{\dnf}{\mathsf{DNF}}
+%\newcommand{\DNF}{\dnf}
+%\newcommand{\dnff}{\delta\F}
+
+%\newcommand{\fun}{\mathcal{F}}
+
+\begin{definition}[Equivalent Process Hitting]\label{def:equiv}
+  Two PH models $\PH = (\PHs; \PHl; \PHh^\angles{k})$ and $\ov{\PH} = (\PHs; \PHl; \ov{\PHh}^\angles{n})$,
+  where $k, n \in \sN^*$,
+  are \emph{equivalent} iff:
+  $$\forall s \in \PHl, ( \exists h = \PHhit{A}{b_i}{b_j} \in \PHh, \Fsem{\F(h)}{s}
+    \Longleftrightarrow \exists g = \PHhit{\ov{A}}{b_i}{b_j} \in \ov{\PHh}, \Fsem{\F(g)}{s} )$$
+\end{definition}
+
+We note that several PH models can be equivalent to a same PH model.
+For example, adding actions that are never playable (due to priorities) allows to create an equivalent model.
+
+\begin{theorem}[Bisimilarity of equivalent PH]
+  Two equivalent PH models are bisimilar.
+\end{theorem}
+
+\begin{demo}
+  Let $\PH = (\PHs; \PHl; \PHh^\angles{k})$ and $\ov{\PH} = (\PHs; \PHl; \ov{\PHh}^\angles{n})$
+  two equivalent PH models, with $k, n \in \sN^*$.
+  We want to show:
+  $$\forall s, s' \in \PHl, s \neq s', s \trans{\PH} s' \Longleftrightarrow s \trans{\ov{\PH}} s' $$
+  Let $s, s' \in \PHl$ with $s \neq s'$.
+  ($\Rightarrow$) Suppose $s \trans{\PH} s'$.
+  It means that there exists $h = \PHhit{A}{b_i}{b_j} \in \PHh$ so that $s' = s \PHplay h = s \Cap b_j$
+  in $\PH$ (\pref{def:play}), \ie $\Fsem{\F(h)}{s}$ and $b_i \in s$.
+  As $\ov{\PH}$ is equivalent to $\PH$,
+  there exists $g = \PHhit{\ov{A}}{b_i}{b_j} \in \ov{\PHh}$ so that $\Fsem{\F(g)}{s}$ (\pref{def:equiv}).
+  Therefore, $g$ is playable in $s$ and $s \PHplay g = s \Cap b_j = s'$;
+  which means: $s \trans{\ov{\PH}} s'$
+  ($\Leftarrow$) Same reasoning.
+\end{demo}
+
+\begin{definition}[Flattening]
+  Given a PH model $\PH = (\PHs; \PHl; \PHh^\angles{k})$, where $k \in \sN^*$,
+  we call \emph{flattening} of $\PH$ any PH model $\ov{\PH} = (\PHs; \PHl; \ov{\PHh}^\angles{1})$
+  with 1 class of priority and cooperative actions that is equivalent to $\PH$.
+\todo{Is this definition really useful?}
+\end{definition}
+
+\begin{theorem}[Existence of a flattening]\label{th:exists-flattening}
+  For all $k \in \sN^*$, there exists a flattening of any PH model with $k$ priorities and cooperative actions.
+\todo{Is this theorem really useful?}
+\end{theorem}
+
+The demonstration of this theorem is given in the following subsection.
+
+\end{comment}

### 2014-03-14 parts/models.tex
continue flattening

@@
 \newcommand{\n}[1][h]{n^{#1}}
-\newcommand{\m}[1][h]{m^{#1}}
+\newcommand{\m}[1][h,i]{m^{#1}}
 
@@
 For any action $h \in \ov{\PHh}$, this DNF takes the form:
-\[\Fop{h} \equiv \bot \qquad \text{or} \qquad
-  \Fop{h} \equiv \bigvee_{i \in \segm{1}{\n}} \left( \bigwedge_{j \in \segm{1}{\m_i}} p_{i,j} \right)\]
-where $\n \in \sN^*$ and $\forall i \in \segm{1}{\n}, \m_i \in \sN^*$.
-The case $\Fop{h} \equiv \bot$ means that the action can never be played
-because it is always preempted other actions with higher priorities.
-The case $\Fop{h} \not\equiv \bot$, on the other hand,
+\[\Fop{h} \equiv \bigvee_{i \in \segm{1}{\n}} \left( \bigwedge_{j \in \segm{1}{\m}} p_{i,j} \right)\]
+where $\n \in \sN$ and $\forall i \in \segm{1}{\n}, \m \in \sN^*$.
+If $\n = 0$, then $\Fop{h} \equiv \bot$; this means that $h$ can never be played
+due to preemptions by other actions with higher priorities.
+If $\Fop{h} \not\equiv \bot$, on the other hand, then in this case $\Fop{h}$
 can be seen as a disjunction of $\n$ smaller playability properties consisting only of conjunctions of atoms.
@@
 thus creating a new PH model which is entailed in the restrictions depicted in \pref{ssec:hypothesis}.
-%Indeed, for any $i \in \segm{1}{\n}$, the PP $\bigwedge_{j \in \segm{1}{\m_i}} p_{i,j}$
+%Indeed, for any $i \in \segm{1}{\n}$, the PP $\bigwedge_{j \in \segm{1}{\m}} p_{i,j}$
 In this second case, we denote, for any $i \in \segm{1}{\n}$:
-$\PHdep{i}{h} = \{ \PHsort(p_{i,j}) \mid j \in \segm{1}{\m_i} \}$
+$\PHdep{i}{h} = \{ \PHsort(p_{i,j}) \mid j \in \segm{1}{\m} \}$.
+
+\begin{definition}
+  \label{def:flattening}
+  If $k \in \sN^*$, we note $\PHflat(\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}}) = (\PHs; \PHl; \PHa^{\angles{2}})$
+  the flattening of the PH with $k$ classes of priorities $\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}}$, with:
+  \begin{itemize}
+    \item $\PHs = \ov{\PHs} \cup \{ f^{h,i} \mid h \in \ov{\PHh} \wedge \n \geq 1 \wedge i \in \segm{1}{\n} \}$;
+    \item $\PHl = \underset{a \in \PHs}{\times} \PHl_{a}$, where
+      $\PHl_{a} = \ov{\PHl}_{a}$ if $a \in \ov{\PHs}$; and 
+      $\PHl_{f^{h,i}} = \{ f^{h,i}_\varsigma \mid \varsigma \in \underset{b \in \PHdep{i}{h}}{\times} \PHl_{b} \}$ otherwise.
+    \item $\PHh^{(1)} = \{ \PHhit{a_k}{f^{h,i}_\varsigma}{f^{h,i}_{\varsigma'}} \mid
+      h \in \ov{\PHh} \wedge %\n \geq 1 \wedge i \in \segm{1}{\n} \wedge
+      a \in \PHdep{i}{h} \wedge a_k \in \PHl_a \wedge
+      f^{h,i}_\varsigma , f^{h,i}_{\varsigma'} \in \PHl_{f^{h,i}} \wedge
+      \PHget{\varsigma}{a} \neq a_k \wedge \varsigma' = \varsigma \Cap \{ a_k \} \}$;
+%      \todo{From here: ...} \PHget{\varsigma'}{a} = a_k \wedge
+%      (\forall b \in \PHdep{i}{h} \setminus \{ a \}, \PHget{\varsigma'}{b} = \PHget{\varsigma}{b}) \}$;
+%      \todo{... can be replaced by: $\varsigma' = \varsigma \Cap \{ a_k \}$}
+    \item $\PHh^{(2)}=\{ \PHhit{f^{h,i}_\varsigma}{\target{h}}{\bounce{h}} \mid
+      h \in \ov{\PHh} \wedge f^{h,i}_\varsigma \in \PHl_{f^{h,i}} \wedge \Fsem{h}{\varsigma} \}$.
+
+    \item $\Hits^{(1)}= \{ \hit{a^j_k}{f^i_\varsigma}{f^i_{\varsigma'}}
+      \mid i\in\segm{1}{n} \wedge
+      j\in\DNdep(f^i) \wedge a^j_k\in \PHl_{a^j} \wedge f^i_\varsigma\in \PHl_{f^i}
+      \wedge
+      \get{\varsigma}{a^j}\neq a^j_k 
+      \wedge \get{\varsigma'}{a^j}=a^j_k
+      \wedge (\get{\varsigma'}{a^{l}}=\get{\varsigma}{a^l},
+      \forall l\in\segm{1}{n},l\neq j)
+      \}$, 
+      the set of actions with priority $1$ that update cooperative sorts;
+
+          \item $\Hits^{(2)}=\{ \hit{f^i_\varsigma}{a^i_k}{a^i_{k'}} \mid i\in\segm{1}{n} \wedge
+          f^i_\varsigma\in \PHl_{f^i} \wedge
+          a^i_k\in \PHl_{a^i}\wedge k\neq k' \wedge f^i(\decode \varsigma) = k'
+        \}$,
+
+  \end{itemize}
+
+\end{definition}
 

### 2014-03-17 parts/models.tex
continue flattening ; only the big proof left

@@
 \end{definition}
-
-By definition of the semantics of a PH given in \pref{def:play},
-an action $h \in \ov{\PHh}$ is playable in a state $s \in \ov{\PHl}$ iff $\Fsem{\Fop{h}}{s}$.
-
-\todo{--- Le reste de la traduction ici ---}
+%
+\begin{theorem}
+\label{th:ppplay}
+  $h \in \ov{\PHh}$ is playable in $s \in \ov{\PHl}$ if and only if $\Fsem{\Fop{h}}{s}$.
+\end{theorem}
+%
+\begin{proof}
+  By definition of the semantics of a PH given in \pref{def:play}.
+\end{proof}
 
@@
 
-Because we only use classical logic operators, we can compute the PP on any action in $\ov{\PH}$.
+Because we only use classical logic operators, we can compute the Disjunctive Normal Form (DNF) of any PP.
 For any action $h \in \ov{\PHh}$, this DNF takes the form:
@@
 
+\newcommand{\flats}[1]{\lfloor #1 \rfloor}
+\newcommand{\unflats}[1]{\lceil #1 \rceil}
+
+\newcommand{\os}{\ov{s}}
+\newcommand{\oPH}{\ov{\PH}}
+
 \begin{definition}
@@
   \begin{itemize}
-    \item $\PHs = \ov{\PHs} \cup \{ f^{h,i} \mid h \in \ov{\PHh} \wedge \n \geq 1 \wedge i \in \segm{1}{\n} \}$;
-    \item $\PHl = \underset{a \in \PHs}{\times} \PHl_{a}$, where
-      $\PHl_{a} = \ov{\PHl}_{a}$ if $a \in \ov{\PHs}$; and 
-      $\PHl_{f^{h,i}} = \{ f^{h,i}_\varsigma \mid \varsigma \in \underset{b \in \PHdep{i}{h}}{\times} \PHl_{b} \}$ otherwise.
+    \item $\PHs = \ov{\PHs} \cup \PHs_f$
+      where $\PHs_f = \{ f^{h,i} \mid h \in \ov{\PHh} \wedge \n \geq 1 \wedge i \in \segm{1}{\n} \}$;
+    \item $\PHl = \left( \underset{a \in \ov{\PHs}}{\times} \PHl_{a} \right) \times
+      \left(\underset{f^{h,i} \in \PHs_f}{\times} \PHl_{f^{h,i}} \right)$,
+      where $\forall a \in \ov{\PHs}, \PHl_{a} = \ov{\PHl}_{a}$, and
+      $\forall f^{h,i} \in \PHs_f,
+      \PHl_{f^{h,i}} = \{ f^{h,i}_\varsigma \mid \varsigma \in \underset{b \in \PHdep{i}{h}}{\times} \PHl_{b} \}$;
     \item $\PHh^{(1)} = \{ \PHhit{a_k}{f^{h,i}_\varsigma}{f^{h,i}_{\varsigma'}} \mid
-      h \in \ov{\PHh} \wedge %\n \geq 1 \wedge i \in \segm{1}{\n} \wedge
+      %h \in \ov{\PHh} \wedge %\n \geq 1 \wedge i \in \segm{1}{\n} \wedge
+      f^{h,i} \in \PHs_f \wedge
       a \in \PHdep{i}{h} \wedge a_k \in \PHl_a \wedge
@@
     \item $\PHh^{(2)}=\{ \PHhit{f^{h,i}_\varsigma}{\target{h}}{\bounce{h}} \mid
-      h \in \ov{\PHh} \wedge f^{h,i}_\varsigma \in \PHl_{f^{h,i}} \wedge \Fsem{h}{\varsigma} \}$.
+      f^{h,i} \in \PHs_f \wedge
+      %h \in \ov{\PHh} \wedge 
+      f^{h,i}_\varsigma \in \PHl_{f^{h,i}} \wedge \Fsem{h}{\varsigma} \}$.
+  \end{itemize}
+  Given a state $s \in \PHl$, $\unflats{s} = \os$ is the corresponding state in $\ov{\PHl}$:
+  $\forall a \in \ov{\PHs}, \PHget{\os}{a} = \PHget{s}{a}$.
 
-    \item $\Hits^{(1)}= \{ \hit{a^j_k}{f^i_\varsigma}{f^i_{\varsigma'}}
-      \mid i\in\segm{1}{n} \wedge
-      j\in\DNdep(f^i) \wedge a^j_k\in \PHl_{a^j} \wedge f^i_\varsigma\in \PHl_{f^i}
-      \wedge
-      \get{\varsigma}{a^j}\neq a^j_k 
-      \wedge \get{\varsigma'}{a^j}=a^j_k
-      \wedge (\get{\varsigma'}{a^{l}}=\get{\varsigma}{a^l},
-      \forall l\in\segm{1}{n},l\neq j)
-      \}$, 
-      the set of actions with priority $1$ that update cooperative sorts;
+  \noindent
+  Given a state $\os \in \ov{\PHl}$, $\flats{\os} = s$ is the corresponding state in $\PHl$:
+  $\forall a \in \ov{\PHs}, \PHget{s}{a} = \PHget{\os}{a}$
+  and $\forall f^{h,i} \in \PHs_f, \PHget{s}{f^{h,i}} = f^{h,i}_\varsigma$ with $f^{h,i}_\varsigma \in \PHl_{f^{h,i}}$
+  and $\forall b \in \PHdep{i}{h}, \PHget{\varsigma}{b} = \PHget{\os}{b}$.
+\end{definition}
 
-          \item $\Hits^{(2)}=\{ \hit{f^i_\varsigma}{a^i_k}{a^i_{k'}} \mid i\in\segm{1}{n} \wedge
-          f^i_\varsigma\in \PHl_{f^i} \wedge
-          a^i_k\in \PHl_{a^i}\wedge k\neq k' \wedge f^i(\decode \varsigma) = k'
-        \}$,
+\begin{theorem}[$(\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}}) \approx \PHflat(\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}})$]
+\label{thm:bisimPHP}
+  Let $\ov{\PH} = (\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}})$ a PH with $k$ classes of priorities,
+  and $\PH = \PHflat(\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}}) = (\PHs; \PHl; \PHa^{\angles{2}})$ its flattening.
+  \begin{enumerate}
+    \item \label{php2ph} $\forall \os, \os' \in \ov{\PHl}$,
+      $\os \PHPtrans[\oPH] \os' \Longrightarrow \flats{\os} \PHPtrans[\oPH]^* \flats{\os'}$,
+      where $\PHPtrans[\oPH]^*$ is a finite sequence of $\PHPtrans[\oPH]$ transitions.
 
-  \end{itemize}
+    \item \label{ph2php} $\forall s, s' \in \PHl$,
+      $s \PHPtrans s' \Longrightarrow \unflats{s} = \unflats{s'} \vee
+      \unflats{s} \PHPtrans \unflats{s'}\enspace.$
+  \end{enumerate}
+\end{theorem}
+%
+\begin{proof}
+  (\ref{php2ph}) Let $\flats{\os} = s$.
+    From \pref{def:play}, if $\os \PHPtrans[\PH] \os'$,
+    then there exists $h \in \ov{\PHh}$ so that $\os' = \os \PHplay h$.
+    Furthermore, given \pref{th:ppplay}, $\Fsem{\F(h)}{\os}$.
+    Finally, given \pref{def:flattening}, $\PHget{s}{f^{h,i}}$
 
-\end{definition}
+  \todo{-- À continuer --}
+\end{proof}
 
@@
 The demonstration of this theorem is given in the following subsection.
-
-\begin{comment}
-
-%\newcommand{\poz}{\F}
-%\newcommand{\pon}{P_{DNF}}
-%\newcommand{\unneg}{\mathsf{UnNeg}}
-%\newcommand{\negate}{\mathsf{Negate}}
-%\newcommand{\prednf}{\mathsf{Distribute}}
-%\newcommand{\dnf}{\mathsf{DNF}}
-%\newcommand{\DNF}{\dnf}
-%\newcommand{\dnff}{\delta\F}
-
-%\newcommand{\fun}{\mathcal{F}}
-
-\begin{definition}[Equivalent Process Hitting]\label{def:equiv}
-  Two PH models $\PH = (\PHs; \PHl; \PHh^\angles{k})$ and $\ov{\PH} = (\PHs; \PHl; \ov{\PHh}^\angles{n})$,
-  where $k, n \in \sN^*$,
-  are \emph{equivalent} iff:
-  $$\forall s \in \PHl, ( \exists h = \PHhit{A}{b_i}{b_j} \in \PHh, \Fsem{\F(h)}{s}
-    \Longleftrightarrow \exists g = \PHhit{\ov{A}}{b_i}{b_j} \in \ov{\PHh}, \Fsem{\F(g)}{s} )$$
-\end{definition}
-
-We note that several PH models can be equivalent to a same PH model.
-For example, adding actions that are never playable (due to priorities) allows to create an equivalent model.
-
-\begin{theorem}[Bisimilarity of equivalent PH]
-  Two equivalent PH models are bisimilar.
-\end{theorem}
-
-\begin{demo}
-  Let $\PH = (\PHs; \PHl; \PHh^\angles{k})$ and $\ov{\PH} = (\PHs; \PHl; \ov{\PHh}^\angles{n})$
-  two equivalent PH models, with $k, n \in \sN^*$.
-  We want to show:
-  $$\forall s, s' \in \PHl, s \neq s', s \trans{\PH} s' \Longleftrightarrow s \trans{\ov{\PH}} s' $$
-  Let $s, s' \in \PHl$ with $s \neq s'$.
-  ($\Rightarrow$) Suppose $s \trans{\PH} s'$.
-  It means that there exists $h = \PHhit{A}{b_i}{b_j} \in \PHh$ so that $s' = s \PHplay h = s \Cap b_j$
-  in $\PH$ (\pref{def:play}), \ie $\Fsem{\F(h)}{s}$ and $b_i \in s$.
-  As $\ov{\PH}$ is equivalent to $\PH$,
-  there exists $g = \PHhit{\ov{A}}{b_i}{b_j} \in \ov{\PHh}$ so that $\Fsem{\F(g)}{s}$ (\pref{def:equiv}).
-  Therefore, $g$ is playable in $s$ and $s \PHplay g = s \Cap b_j = s'$;
-  which means: $s \trans{\ov{\PH}} s'$
-  ($\Leftarrow$) Same reasoning.
-\end{demo}
-
-\begin{definition}[Flattening]
-  Given a PH model $\PH = (\PHs; \PHl; \PHh^\angles{k})$, where $k \in \sN^*$,
-  we call \emph{flattening} of $\PH$ any PH model $\ov{\PH} = (\PHs; \PHl; \ov{\PHh}^\angles{1})$
-  with 1 class of priority and cooperative actions that is equivalent to $\PH$.
-\todo{Is this definition really useful?}
-\end{definition}
-
-\begin{theorem}[Existence of a flattening]\label{th:exists-flattening}
-  For all $k \in \sN^*$, there exists a flattening of any PH model with $k$ priorities and cooperative actions.
-\todo{Is this theorem really useful?}
-\end{theorem}
-
-The demonstration of this theorem is given in the following subsection.
-
-\end{comment}

### 2014-03-18 parts/models.tex
finish proof for flattening; minor review/additions left

@@
 \subsection{PH with multiple classes of priorities}
-\todo{Reduce and reuse the flattening method}
+\todo{Glue up all this section}
 
 \newcommand{\ov}{\overline}
+\newcommand{\os}{\ov{s}}
+\newcommand{\oPH}{\ov{\PH}}
+
 \newcommand{\F}{F}
@@
 %\newcommand{\Fall}{\F}
+\newcommand{\mysigma}{\sigma}
 
@@
 
-A playability property (PP) as defined in \pref{def:pp} is a formula where the atoms are processes of $\ov{\PH}$.
+\newcommand{\PHsubl}[1][\ov{\PHl}]{#1^\diamond}
+
+\todo{Rather define a sub-state on a subset of sorts}
+\begin{definition}[Sub-states ($\PHsubl$)]
+  A sub-state of $\oPH$ is an element of:
+    \[\PHsubl \DEF \{ \mysigma \in \bigtimes{a \in S} \ov{\PHl}_a \mid S \subset \ov{\PHs} \} \enspace.\]
+  Furthermore, if $\mysigma \in \PHsubl$ and $s \in \ov{\PHl}$, we note:
+    \[\mysigma \subseteq s \EQDEF \forall a_i \in \Proc, a_i \in \mysigma \Rightarrow a_i \in s \enspace.\]
+\end{definition}
+
+We note that a state is \textit{a fortiori} a sub-state: $\ov{\PHl} \subset \PHsubl$.
+
+A playability property (PP) as defined in \pref{def:pp} is a Boolean formula where the atoms are processes of $\ov{\PH}$.
 
@@
   \end{itemize}
-  We note $\Fsem{P}{s}$ the \emph{evaluation} of a PP $P \in \F$ in a state $s \in \ov{\PHl}$.
-  The semantics of this evaluation is the following for any state $s \in \ov{\PHl}$:
+  If $P \in \F$ is a PP and $\mysigma \in \PHsubl$ is a sub-state,
+  we note $\Fsem{P}{\mysigma}$ the \emph{evaluation} of $P$ in $\mysigma$:
+%  We note $\Fsem{P}{s}$ the \emph{evaluation} of a PP $P \in \F$ in a state $s \in \ov{\PHl}$.
+%  The semantics of this evaluation is the following for any state $s \in \ov{\PHl}$:
   \begin{itemize}
-    \item if $P = a_i \in \ov{\PHs}_a$ is an atom, with $a \in \ov{\PHs}$, then $\Fsem{a_i}{s}$ is true iff $a_i \in s$;
-    \item if $P$ is not an atom, then $\Fsem{P}{s}$ is true iff all its subformulas are inductively true in $s$
+    \item if $P = a_i \in \ov{\PHs}_a$ is an atom, with $a \in \ov{\PHs}$, then $\Fsem{a_i}{\mysigma}$ is true iff $a_i \in \mysigma$;
+    \item if $P$ is not an atom, then $\Fsem{P}{\mysigma}$ is true iff all its subformulas are inductively true in $\mysigma$
       with the classical semantics for the logic operators $\top$, $\bot$, $\neg$, $\wedge$ and $\vee$.
@@
 We also have the following property for the negation of an atom:
-\[\forall a \in \ov{\PHs}, \forall a_i \in \ov{\PHl}_a, \Fsem{\neg a_i}{s}
-  \Leftrightarrow \Fsem{\bigvee_{\substack{a_j \in \PHl_a\\a_j \neq a_i}} a_j}{s}\]
+\[\forall a \in \ov{\PHs}, \forall a_i \in \ov{\PHl}_a, \forall \mysigma \in \PHsubl,
+  \Fsem{\neg a_i}{s} \Leftrightarrow \Fsem{\bigvee_{\substack{a_j \in \PHl_a\\a_j \neq a_i}} a_j}{s}\]
 Indeed, if a process is not active in a state, this means that another process of the same sort is active.
@@
 
+\todo{Glue up}
+\begin{theorem}
+\label{th:ppplaysubset}
+  $h \in \ov{\PHh}$ is playable in $s \in \ov{\PHl}$ if and only if
+  $\exists \mysigma \subseteq s, \Fsem{\F(h)}{\mysigma}$.
+%  \[\exists i \in \segm{1}{\n}, \exists \mysigma \in \bigtimes{b \in \PHdep{i}{h}} \PHl_b,
+%    \mysigma \subseteq s \wedge \Fsem{\F(h)}{\mysigma} \enspace.\]
+\end{theorem}
+%
+\begin{proof}
+  ($\Rightarrow$) If $\Fsem{\F(h)}{s}$ then $\F(h) \not\equiv \bot$ and, by property of a DNF,
+    at least one of the $\n$ conjunctions of $\F(h)$ is true in $s$.
+    Suppose the $i$\textsuperscript{th} conjunction is true in $s$, with $i \in \segm{1}{\n}$;
+    then we have: $\forall j \in \segm{1}{\m}, p_{i,j} \in s$.
+    Let $\mysigma \in \bigtimes{b \in \PHdep{i}{h}} \PHl_b$ with $\forall b \in \PHdep{i}{h}, \PHget{\mysigma}{b} = \PHget{s}{b}$.
+    We immediately have: $\mysigma \subseteq s$,
+    and, by construction of $\PHdep{i}{h}$, $\Fsem{\F(h)}{\mysigma}$.
+
+  ($\Leftarrow$) Trivial.
+\end{proof}
+
 \newcommand{\flats}[1]{\lfloor #1 \rfloor}
 \newcommand{\unflats}[1]{\lceil #1 \rceil}
-
-\newcommand{\os}{\ov{s}}
-\newcommand{\oPH}{\ov{\PH}}
 
@@
       $\forall f^{h,i} \in \PHs_f,
-      \PHl_{f^{h,i}} = \{ f^{h,i}_\varsigma \mid \varsigma \in \underset{b \in \PHdep{i}{h}}{\times} \PHl_{b} \}$;
-    \item $\PHh^{(1)} = \{ \PHhit{a_k}{f^{h,i}_\varsigma}{f^{h,i}_{\varsigma'}} \mid
-      %h \in \ov{\PHh} \wedge %\n \geq 1 \wedge i \in \segm{1}{\n} \wedge
+      \PHl_{f^{h,i}} = \{ f^{h,i}_\mysigma \mid \mysigma \in \underset{b \in \PHdep{i}{h}}{\times} \PHl_{b} \}$;
+    \item $\PHh^{(1)} = \{ \PHhit{a_k}{f^{h,i}_\mysigma}{f^{h,i}_{\mysigma'}} \mid
+      h \in \ov{\PHh} \wedge
+      %\n \geq 1 \wedge i \in \segm{1}{\n} \wedge
       f^{h,i} \in \PHs_f \wedge
       a \in \PHdep{i}{h} \wedge a_k \in \PHl_a \wedge
-      f^{h,i}_\varsigma , f^{h,i}_{\varsigma'} \in \PHl_{f^{h,i}} \wedge
-      \PHget{\varsigma}{a} \neq a_k \wedge \varsigma' = \varsigma \Cap \{ a_k \} \}$;
-%      \todo{From here: ...} \PHget{\varsigma'}{a} = a_k \wedge
-%      (\forall b \in \PHdep{i}{h} \setminus \{ a \}, \PHget{\varsigma'}{b} = \PHget{\varsigma}{b}) \}$;
-%      \todo{... can be replaced by: $\varsigma' = \varsigma \Cap \{ a_k \}$}
-    \item $\PHh^{(2)}=\{ \PHhit{f^{h,i}_\varsigma}{\target{h}}{\bounce{h}} \mid
+      f^{h,i}_\mysigma , f^{h,i}_{\mysigma'} \in \PHl_{f^{h,i}} \wedge
+      \PHget{\mysigma}{a} \neq a_k \wedge \mysigma' = \mysigma \Cap \{ a_k \} \}$;
+%      \todo{From here: ...} \PHget{\mysigma'}{a} = a_k \wedge
+%      (\forall b \in \PHdep{i}{h} \setminus \{ a \}, \PHget{\mysigma'}{b} = \PHget{\mysigma}{b}) \}$;
+%      \todo{... can be replaced by: $\mysigma' = \mysigma \Cap \{ a_k \}$}
+    \item $\PHh^{(2)}=\{ \PHhit{f^{h,i}_\mysigma}{\target{h}}{\bounce{h}} \mid
+      h \in \ov{\PHh} \wedge 
       f^{h,i} \in \PHs_f \wedge
-      %h \in \ov{\PHh} \wedge 
-      f^{h,i}_\varsigma \in \PHl_{f^{h,i}} \wedge \Fsem{h}{\varsigma} \}$.
+      f^{h,i}_\mysigma \in \PHl_{f^{h,i}} \wedge \Fsem{\F(h)}{\mysigma} \}$.
   \end{itemize}
@@
   $\forall a \in \ov{\PHs}, \PHget{s}{a} = \PHget{\os}{a}$
-  and $\forall f^{h,i} \in \PHs_f, \PHget{s}{f^{h,i}} = f^{h,i}_\varsigma$ with $f^{h,i}_\varsigma \in \PHl_{f^{h,i}}$
-  and $\forall b \in \PHdep{i}{h}, \PHget{\varsigma}{b} = \PHget{\os}{b}$.
+  and $\forall f^{h,i} \in \PHs_f, \PHget{s}{f^{h,i}} = f^{h,i}_\mysigma$ with $f^{h,i}_\mysigma \in \PHl_{f^{h,i}}$
+  and $\forall b \in \PHdep{i}{h}, \PHget{\mysigma}{b} = \PHget{\os}{b}$.
 \end{definition}
@@
       where $\PHPtrans[\oPH]^*$ is a finite sequence of $\PHPtrans[\oPH]$ transitions.
-
     \item \label{ph2php} $\forall s, s' \in \PHl$,
       $s \PHPtrans s' \Longrightarrow \unflats{s} = \unflats{s'} \vee
-      \unflats{s} \PHPtrans \unflats{s'}\enspace.$
+      \unflats{s} \PHPtrans \unflats{s'} \enspace.$
   \end{enumerate}
@@
   (\ref{php2ph}) Let $\flats{\os} = s$.
-    From \pref{def:play}, if $\os \PHPtrans[\PH] \os'$,
-    then there exists $h \in \ov{\PHh}$ so that $\os' = \os \PHplay h$.
-    Furthermore, given \pref{th:ppplay}, $\Fsem{\F(h)}{\os}$.
-    Finally, given \pref{def:flattening}, $\PHget{s}{f^{h,i}}$
+    Given the dynamics of a PH (\pref{def:play}), if $\os \PHPtrans[\PH] \os'$,
+    then there exists $h \in \ov{\PHh}$ playable in $\os$;
+    therefore, $\os' = \os \PHplay h$ and $\target{h} \in \os$.
+    Furthermore, given \pref{th:ppplay}, $\Fsem{\F(h)}{\os}$,
+    and given \pref{th:ppplaysubset}, there exists $\mysigma \subseteq s$ so that $\Fsem{\F(h)}{\mysigma}$.
+    Therefore, by construction of $\PH$ (\pref{def:flattening}) there exists
+    $g = \PHhit{f^{h,i}_\mysigma}{\target{h}}{\bounce{h}} \in \PHh^{(2)}$.
+    By construction of $s$ (\pref{def:flattening}), $\PHget{s}{f^{h,i}} = f^{h,i}_\mysigma$ and $\target{h} = \target{g} \in s$.
+    Therefore, $g$ is playable in $s$.
+    In $s \PHplay g$, the only playable actions are those in $\PHh^{(1)}$ having $\bounce{h} = \bounce{g}$ as hitter
+    and updating cooperative sorts, allowing to reach $\flats{\os'}$ in a finite number of actions.
+    Thus, $\flats{\os} \PHPtrans[\oPH]^* \flats{\os'}$.
 
-  \todo{-- À continuer --}
+  (\ref{ph2php}) Let $\os = \unflats{s}$.
+    Given the dynamics of a PH (\pref{def:play}), if $s \PHPtrans s'$,
+    then there exists $g \in \PHh$ playable in $s$; therefore, $s' = s \PHplay g$ and $\target{g} \in s$.
+    If $\prio(g) = 1$ then only the active process of a cooperative sort has evolved, and $\unflats{s} = \unflats{s'}$.
+    Otherwise, $\prio(g) = 2$; we note in this case: $g = \PHhit{f^{h,i}_\mysigma}{b_j}{b_k}$.
+    By construction of the flattening (\pref{def:flattening}), there exists $h \in \ov{\PHh}$ so that
+    $\target{h} = b_j$, $\bounce{h} = b_k$ and $\Fsem{\F(h)}{\mysigma}$.
+    If $g$ is playable, this means that no other action in $\PHh^{(1)}$ is playable, and especially the cooperative sort
+    $f^{h,i}$ is already updated; therefore, $\mysigma \subseteq s$.
+    By \pref{th:ppplaysubset}, it comes that $h$ is playable in $\os$.
+    Thus, $\unflats{s} \PHPtrans \unflats{s'}$.
 \end{proof}
-
-\todo{--- Le reste de la traduction ici ---}
-
-\begin{definition}[Equivalent Process Hitting]\label{def:equiv}
-  Two PH models $\ov{\PH} = (\ov{\PHs}; \ov{\PHl}; \ov{\PHh}^\angles{k})$ and $\PH = (\PHs; \PHl; \PHh^\angles{n})$,
-  where $k, n \in \sN^*$,
-  are \emph{equivalent} iff:
-  $$\forall s \in \ov{\PHl}, ( \exists h = \PHhit{A}{b_i}{b_j} \in \PHh, \Fsem{\F(h)}{s}
-    \Longleftrightarrow \exists g = \PHhit{\ov{A}}{b_i}{b_j} \in \ov{\PHh}, \Fsem{\F(g)}{s} )$$
-\end{definition}
-
-We note that several PH models can be equivalent to a same PH model.
-For example, adding actions that are never playable (due to priorities) allows to create an equivalent model.
-
-\begin{theorem}[Bisimilarity of equivalent PH]
-  Two equivalent PH models are bisimilar.
-\end{theorem}
-
-\begin{proof}
-  Let $\PH = (\PHs; \PHl; \PHh^\angles{k})$ and $\ov{\PH} = (\PHs; \PHl; \ov{\PHh}^\angles{n})$
-  two equivalent PH models, with $k, n \in \sN^*$.
-  We want to show:
-  $$\forall s, s' \in \PHl, s \neq s', s \trans{\PH} s' \Longleftrightarrow s \trans{\ov{\PH}} s' $$
-  Let $s, s' \in \PHl$ with $s \neq s'$.
-  ($\Rightarrow$) Suppose $s \trans{\PH} s'$.
-  It means that there exists $h = \PHhit{A}{b_i}{b_j} \in \PHh$ so that $s' = s \PHplay h = s \Cap b_j$
-  in $\PH$ (\pref{def:play}), \ie $\Fsem{\F(h)}{s}$ and $b_i \in s$.
-  As $\ov{\PH}$ is equivalent to $\PH$,
-  there exists $g = \PHhit{\ov{A}}{b_i}{b_j} \in \ov{\PHh}$ so that $\Fsem{\F(g)}{s}$ (\pref{def:equiv}).
-  Therefore, $g$ is playable in $s$ and $s \PHplay g = s \Cap b_j = s'$;
-  which means: $s \trans{\ov{\PH}} s'$
-  ($\Leftarrow$) Same reasoning.
-\end{proof}
-
-\begin{definition}[Flattening]
-  Given a PH model $\PH = (\PHs; \PHl; \PHh^\angles{k})$, where $k \in \sN^*$,
-  we call \emph{flattening} of $\PH$ any PH model $\ov{\PH} = (\PHs; \PHl; \ov{\PHh}^\angles{1})$
-  with 1 class of priority and cooperative actions that is equivalent to $\PH$.
-\todo{Is this definition really useful?}
-\end{definition}
-
-\begin{theorem}[Existence of a flattening]\label{th:exists-flattening}
-  For all $k \in \sN^*$, there exists a flattening of any PH model with $k$ priorities and cooperative actions.
-\todo{Is this theorem really useful?}
-\end{theorem}
-
-The demonstration of this theorem is given in the following subsection.

### 2014-03-19 parts/def-ph.tex
start flattening
several fixes + refactoring of files

@@
 %\todo{Nouvelle section pour les hypothèses + conséquences ?}
+\subsection{Restrictions}
 \label{ssec:hypothesis}
-\subsection{Restrictions}
 
@@
 \end{theorem}
-\begin{proof}
+%
+\newproof{proofupdate}{Proof of \pref{th:update}}
+\begin{proofupdate}
   Let $a$ be a cooperative sort so that $\PHget{s}{a} \neq \pfp_s(a)$.
@@
   As there is no cycle of actions between the cooperative sorts (\pref{cr:cyclefreeness}) and given that an updated cooperative sort cannot evolve, at most $|\cs|$ updates have to be performed.
-\end{proof}
+\end{proofupdate}
 
@@
 \end{theorem}
-\begin{proof}
+%
+\newproof{proofhcompcomp}{Proof of \pref{th:hcompcomp}}
+\begin{proofhcompcomp}
   From \pref{th:update}, there exists a scenario $\delta$ with: $(s \PHplay \delta) = \update(s)$.
@@
   Finally, by definition of $\update(s)$, no prioritised action can be played in $(s \PHplay \delta)$, thus $h$ can be played in $(s \PHplay \delta)$.
-\end{proof}
+\end{proofhcompcomp}
+%
 \begin{theorem}
 \label{th:hcscomp}
-  $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, a \in \cs, b \in \components$\\
+  $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, a \in \cs, b \in \components,$\\
   $(\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j \wedge \pfp_s(a) = a_i) \Rightarrow (\exists \delta \in \restriction{\Sce}{1}(s),
@@
 \end{theorem}
-\begin{proof}
+%
+\newproof{proofhcscomp}{Proof of \pref{th:hcscomp}}
+\begin{proofhcscomp}
   Similar to the proof of \pref{th:hcompcomp};
   as $a_i \in \pfp_s(a)$, $a_i \in (s \PHplay \delta)$.
-\end{proof}
+\end{proofhcscomp}

### 2014-03-19 parts/models-ph-dn.tex
several fixes + refactoring of files

--- 2014-03-14 parts/models.tex
@@
-\section{\todo{Title?} Equivalence with other frameworks}
-
 \subsection{Asynchronous Discrete Networks}
 \todo{Detail the equivalence with ADNs (cf. the annex)}
-
-\subsection{PH with multiple classes of priorities}
-\todo{Reduce and reuse the flattening method}
-
-\newcommand{\ov}{\overline}
-\newcommand{\F}{F}
-\newcommand{\Fopsymbol}{\F}
-\newcommand{\Fop}[1]{\Fopsymbol(#1)}
-\newcommand{\Fsem}[2]{\left[#1\right](#2)}
-%\newcommand{\Fall}{\F}
-
-Consider a PH with $k \in \sN^*$ classes of priories:
-$\ov{\PH} = (\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}})$.
-We want to translate it to a PH with $2$ classes of priorities
-$\PH = (\PHs; \PHl; \PHa^{\angles{2}})$
-that respects all Criteria given in \pref{ssec:hypothesis}.
-
-A playability property (PP) as defined in \pref{def:pp} is a formula where the atoms are processes of $\ov{\PH}$.
-
-\begin{definition}[Playability property language ($\F$)]
-  \label{def:pp}
-  A \emph{playability property} (PP) is an element of the language $\F$ inductively defined by:
-  \begin{itemize}
-    \item $\top$ and $\bot$ belong to $\F$;
-    \item if $a \in \ov{\PHs}$ and $a_i \in \ov{\PHl}_a$, then $a_i \in \F$ and we call it an \emph{atom};
-    \item if $P \in \F$ and $Q \in \F$, then $\neg P \in \F$, $P \wedge Q \in \F$ and $P \vee Q \in \F$.
-  \end{itemize}
-  We note $\Fsem{P}{s}$ the \emph{evaluation} of a PP $P \in \F$ in a state $s \in \ov{\PHl}$.
-  The semantics of this evaluation is the following for any state $s \in \ov{\PHl}$:
-  \begin{itemize}
-    \item if $P = a_i \in \ov{\PHs}_a$ is an atom, with $a \in \ov{\PHs}$, then $\Fsem{a_i}{s}$ is true iff $a_i \in s$;
-    \item if $P$ is not an atom, then $\Fsem{P}{s}$ is true iff all its subformulas are inductively true in $s$
-      with the classical semantics for the logic operators $\top$, $\bot$, $\neg$, $\wedge$ and $\vee$.
-  \end{itemize}
-\end{definition}
-
-Because we only use classical logic operators, the formulas of Boolean logic on distribution and negation (de Morgan's laws) can be used.
-We also have the following property for the negation of an atom:
-\[\forall a \in \ov{\PHs}, \forall a_i \in \ov{\PHl}_a, \Fsem{\neg a_i}{s}
-  \Leftrightarrow \Fsem{\bigvee_{\substack{a_j \in \PHl_a\\a_j \neq a_i}} a_j}{s}\]
-Indeed, if a process is not active in a state, this means that another process of the same sort is active.
-
-In \pref{def:fop}, we finally define the the operator $\Fopsymbol$ which characterizes the playability of an action
-given the semantics of PH (\pref{def:play}).
-\begin{definition}[Playability property of an action ($\Fopsymbol : \PHh \rightarrow \F$)]\label{def:fop}
-  $$\forall h \in \ov{\PHh}, \Fop{h} \equiv \hitter{h} \wedge
-    \left( \bigwedge_{\substack{g \in \PHh^{(n)}\\n < \prio(h)}}
-    \neg \left( \target{g} \wedge \hitter{g}\right) \right)$$
-\end{definition}
-
-By definition of the semantics of a PH given in \pref{def:play},
-an action $h \in \ov{\PHh}$ is playable in a state $s \in \ov{\PHl}$ iff $\Fsem{\Fop{h}}{s}$.
-
-\todo{--- Le reste de la traduction ici ---}
-
-\newcommand{\n}[1][h]{n^{#1}}
-\newcommand{\m}[1][h,i]{m^{#1}}
-
-Because we only use classical logic operators, we can compute the PP on any action in $\ov{\PH}$.
-For any action $h \in \ov{\PHh}$, this DNF takes the form:
-\[\Fop{h} \equiv \bigvee_{i \in \segm{1}{\n}} \left( \bigwedge_{j \in \segm{1}{\m}} p_{i,j} \right)\]
-where $\n \in \sN$ and $\forall i \in \segm{1}{\n}, \m \in \sN^*$.
-If $\n = 0$, then $\Fop{h} \equiv \bot$; this means that $h$ can never be played
-due to preemptions by other actions with higher priorities.
-If $\Fop{h} \not\equiv \bot$, on the other hand, then in this case $\Fop{h}$
-can be seen as a disjunction of $\n$ smaller playability properties consisting only of conjunctions of atoms.
-These $\n$ conjunctions can be translated to as many prioritized cooperative sorts,
-thus creating a new PH model which is entailed in the restrictions depicted in \pref{ssec:hypothesis}.
-%Indeed, for any $i \in \segm{1}{\n}$, the PP $\bigwedge_{j \in \segm{1}{\m}} p_{i,j}$
-In this second case, we denote, for any $i \in \segm{1}{\n}$:
-$\PHdep{i}{h} = \{ \PHsort(p_{i,j}) \mid j \in \segm{1}{\m} \}$.
-
-\begin{definition}
-  \label{def:flattening}
-  If $k \in \sN^*$, we note $\PHflat(\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}}) = (\PHs; \PHl; \PHa^{\angles{2}})$
-  the flattening of the PH with $k$ classes of priorities $\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}}$, with:
-  \begin{itemize}
-    \item $\PHs = \ov{\PHs} \cup \{ f^{h,i} \mid h \in \ov{\PHh} \wedge \n \geq 1 \wedge i \in \segm{1}{\n} \}$;
-    \item $\PHl = \underset{a \in \PHs}{\times} \PHl_{a}$, where
-      $\PHl_{a} = \ov{\PHl}_{a}$ if $a \in \ov{\PHs}$; and 
-      $\PHl_{f^{h,i}} = \{ f^{h,i}_\varsigma \mid \varsigma \in \underset{b \in \PHdep{i}{h}}{\times} \PHl_{b} \}$ otherwise.
-    \item $\PHh^{(1)} = \{ \PHhit{a_k}{f^{h,i}_\varsigma}{f^{h,i}_{\varsigma'}} \mid
-      h \in \ov{\PHh} \wedge %\n \geq 1 \wedge i \in \segm{1}{\n} \wedge
-      a \in \PHdep{i}{h} \wedge a_k \in \PHl_a \wedge
-      f^{h,i}_\varsigma , f^{h,i}_{\varsigma'} \in \PHl_{f^{h,i}} \wedge
-      \PHget{\varsigma}{a} \neq a_k \wedge \varsigma' = \varsigma \Cap \{ a_k \} \}$;
-%      \todo{From here: ...} \PHget{\varsigma'}{a} = a_k \wedge
-%      (\forall b \in \PHdep{i}{h} \setminus \{ a \}, \PHget{\varsigma'}{b} = \PHget{\varsigma}{b}) \}$;
-%      \todo{... can be replaced by: $\varsigma' = \varsigma \Cap \{ a_k \}$}
-    \item $\PHh^{(2)}=\{ \PHhit{f^{h,i}_\varsigma}{\target{h}}{\bounce{h}} \mid
-      h \in \ov{\PHh} \wedge f^{h,i}_\varsigma \in \PHl_{f^{h,i}} \wedge \Fsem{h}{\varsigma} \}$.
-
-    \item $\Hits^{(1)}= \{ \hit{a^j_k}{f^i_\varsigma}{f^i_{\varsigma'}}
-      \mid i\in\segm{1}{n} \wedge
-      j\in\DNdep(f^i) \wedge a^j_k\in \PHl_{a^j} \wedge f^i_\varsigma\in \PHl_{f^i}
-      \wedge
-      \get{\varsigma}{a^j}\neq a^j_k 
-      \wedge \get{\varsigma'}{a^j}=a^j_k
-      \wedge (\get{\varsigma'}{a^{l}}=\get{\varsigma}{a^l},
-      \forall l\in\segm{1}{n},l\neq j)
-      \}$, 
-      the set of actions with priority $1$ that update cooperative sorts;
-
-          \item $\Hits^{(2)}=\{ \hit{f^i_\varsigma}{a^i_k}{a^i_{k'}} \mid i\in\segm{1}{n} \wedge
-          f^i_\varsigma\in \PHl_{f^i} \wedge
-          a^i_k\in \PHl_{a^i}\wedge k\neq k' \wedge f^i(\decode \varsigma) = k'
-        \}$,
-
-  \end{itemize}
-
-\end{definition}
-
-\todo{--- Le reste de la traduction ici ---}
-
-\begin{definition}[Equivalent Process Hitting]\label{def:equiv}
-  Two PH models $\ov{\PH} = (\ov{\PHs}; \ov{\PHl}; \ov{\PHh}^\angles{k})$ and $\PH = (\PHs; \PHl; \PHh^\angles{n})$,
-  where $k, n \in \sN^*$,
-  are \emph{equivalent} iff:
-  $$\forall s \in \ov{\PHl}, ( \exists h = \PHhit{A}{b_i}{b_j} \in \PHh, \Fsem{\F(h)}{s}
-    \Longleftrightarrow \exists g = \PHhit{\ov{A}}{b_i}{b_j} \in \ov{\PHh}, \Fsem{\F(g)}{s} )$$
-\end{definition}
-
-We note that several PH models can be equivalent to a same PH model.
-For example, adding actions that are never playable (due to priorities) allows to create an equivalent model.
-
-\begin{theorem}[Bisimilarity of equivalent PH]
-  Two equivalent PH models are bisimilar.
-\end{theorem}
-
-\begin{proof}
-  Let $\PH = (\PHs; \PHl; \PHh^\angles{k})$ and $\ov{\PH} = (\PHs; \PHl; \ov{\PHh}^\angles{n})$
-  two equivalent PH models, with $k, n \in \sN^*$.
-  We want to show:
-  $$\forall s, s' \in \PHl, s \neq s', s \trans{\PH} s' \Longleftrightarrow s \trans{\ov{\PH}} s' $$
-  Let $s, s' \in \PHl$ with $s \neq s'$.
-  ($\Rightarrow$) Suppose $s \trans{\PH} s'$.
-  It means that there exists $h = \PHhit{A}{b_i}{b_j} \in \PHh$ so that $s' = s \PHplay h = s \Cap b_j$
-  in $\PH$ (\pref{def:play}), \ie $\Fsem{\F(h)}{s}$ and $b_i \in s$.
-  As $\ov{\PH}$ is equivalent to $\PH$,
-  there exists $g = \PHhit{\ov{A}}{b_i}{b_j} \in \ov{\PHh}$ so that $\Fsem{\F(g)}{s}$ (\pref{def:equiv}).
-  Therefore, $g$ is playable in $s$ and $s \PHplay g = s \Cap b_j = s'$;
-  which means: $s \trans{\ov{\PH}} s'$
-  ($\Leftarrow$) Same reasoning.
-\end{proof}
-
-\begin{definition}[Flattening]
-  Given a PH model $\PH = (\PHs; \PHl; \PHh^\angles{k})$, where $k \in \sN^*$,
-  we call \emph{flattening} of $\PH$ any PH model $\ov{\PH} = (\PHs; \PHl; \ov{\PHh}^\angles{1})$
-  with 1 class of priority and cooperative actions that is equivalent to $\PH$.
-\todo{Is this definition really useful?}
-\end{definition}
-
-\begin{theorem}[Existence of a flattening]\label{th:exists-flattening}
-  For all $k \in \sN^*$, there exists a flattening of any PH model with $k$ priorities and cooperative actions.
-\todo{Is this theorem really useful?}
-\end{theorem}
-
-The demonstration of this theorem is given in the following subsection.
-
-\begin{comment}
-
-%\newcommand{\poz}{\F}
-%\newcommand{\pon}{P_{DNF}}
-%\newcommand{\unneg}{\mathsf{UnNeg}}
-%\newcommand{\negate}{\mathsf{Negate}}
-%\newcommand{\prednf}{\mathsf{Distribute}}
-%\newcommand{\dnf}{\mathsf{DNF}}
-%\newcommand{\DNF}{\dnf}
-%\newcommand{\dnff}{\delta\F}
-
-%\newcommand{\fun}{\mathcal{F}}
-
-\begin{definition}[Equivalent Process Hitting]\label{def:equiv}
-  Two PH models $\PH = (\PHs; \PHl; \PHh^\angles{k})$ and $\ov{\PH} = (\PHs; \PHl; \ov{\PHh}^\angles{n})$,
-  where $k, n \in \sN^*$,
-  are \emph{equivalent} iff:
-  $$\forall s \in \PHl, ( \exists h = \PHhit{A}{b_i}{b_j} \in \PHh, \Fsem{\F(h)}{s}
-    \Longleftrightarrow \exists g = \PHhit{\ov{A}}{b_i}{b_j} \in \ov{\PHh}, \Fsem{\F(g)}{s} )$$
-\end{definition}
-
-We note that several PH models can be equivalent to a same PH model.
-For example, adding actions that are never playable (due to priorities) allows to create an equivalent model.
-
-\begin{theorem}[Bisimilarity of equivalent PH]
-  Two equivalent PH models are bisimilar.
-\end{theorem}
-
-\begin{demo}
-  Let $\PH = (\PHs; \PHl; \PHh^\angles{k})$ and $\ov{\PH} = (\PHs; \PHl; \ov{\PHh}^\angles{n})$
-  two equivalent PH models, with $k, n \in \sN^*$.
-  We want to show:
-  $$\forall s, s' \in \PHl, s \neq s', s \trans{\PH} s' \Longleftrightarrow s \trans{\ov{\PH}} s' $$
-  Let $s, s' \in \PHl$ with $s \neq s'$.
-  ($\Rightarrow$) Suppose $s \trans{\PH} s'$.
-  It means that there exists $h = \PHhit{A}{b_i}{b_j} \in \PHh$ so that $s' = s \PHplay h = s \Cap b_j$
-  in $\PH$ (\pref{def:play}), \ie $\Fsem{\F(h)}{s}$ and $b_i \in s$.
-  As $\ov{\PH}$ is equivalent to $\PH$,
-  there exists $g = \PHhit{\ov{A}}{b_i}{b_j} \in \ov{\PHh}$ so that $\Fsem{\F(g)}{s}$ (\pref{def:equiv}).
-  Therefore, $g$ is playable in $s$ and $s \PHplay g = s \Cap b_j = s'$;
-  which means: $s \trans{\ov{\PH}} s'$
-  ($\Leftarrow$) Same reasoning.
-\end{demo}
-
-\begin{definition}[Flattening]
-  Given a PH model $\PH = (\PHs; \PHl; \PHh^\angles{k})$, where $k \in \sN^*$,
-  we call \emph{flattening} of $\PH$ any PH model $\ov{\PH} = (\PHs; \PHl; \ov{\PHh}^\angles{1})$
-  with 1 class of priority and cooperative actions that is equivalent to $\PH$.
-\todo{Is this definition really useful?}
-\end{definition}
-
-\begin{theorem}[Existence of a flattening]\label{th:exists-flattening}
-  For all $k \in \sN^*$, there exists a flattening of any PH model with $k$ priorities and cooperative actions.
-\todo{Is this theorem really useful?}
-\end{theorem}
-
-The demonstration of this theorem is given in the following subsection.
-
-\end{comment}

### 2014-03-19 parts/models-ph-php.tex
several fixes + refactoring of files

--- 2014-03-18 parts/models.tex
@@
-\section{\todo{Title?} Equivalence with other frameworks}
-
-\subsection{Asynchronous Discrete Networks}
-\todo{Detail the equivalence with ADNs (cf. the annex)}
-
 \subsection{PH with multiple classes of priorities}
+\label{ssec:flattening}
 \todo{Glue up all this section}
-
-\newcommand{\ov}{\overline}
-\newcommand{\os}{\ov{s}}
-\newcommand{\oPH}{\ov{\PH}}
-
-\newcommand{\F}{F}
-\newcommand{\Fopsymbol}{\F}
-\newcommand{\Fop}[1]{\Fopsymbol(#1)}
-\newcommand{\Fsem}[2]{\left[#1\right](#2)}
-%\newcommand{\Fall}{\F}
-\newcommand{\mysigma}{\sigma}
 
@@
 
-\newcommand{\PHsubl}[1][\ov{\PHl}]{#1^\diamond}
+\begin{definition}[Sub-states ($\PHsubl$)]
+  If $S \subset \ov{\PHs}$ is a set of sorts, a sub-set on $S$ is an element of:
+  $\PHsubl_S \DEF \{ \mysigma \in \bigtimes{a \in S} \ov{\PHl}_a \}$.
+  The set of all sub-sets is:
+  $\PHsubl \DEF \bigcup_{S \subset \ov{\PHs}} \PHsubl_S$.
 
-\todo{Rather define a sub-state on a subset of sorts}
-\begin{definition}[Sub-states ($\PHsubl$)]
-  A sub-state of $\oPH$ is an element of:
-    \[\PHsubl \DEF \{ \mysigma \in \bigtimes{a \in S} \ov{\PHl}_a \mid S \subset \ov{\PHs} \} \enspace.\]
+  \noindent
   Furthermore, if $\mysigma \in \PHsubl$ and $s \in \ov{\PHl}$, we note:
@@
 
-A playability property (PP) as defined in \pref{def:pp} is a Boolean formula where the atoms are processes of $\ov{\PH}$.
+A \emph{playability property} as defined in \pref{def:pp} is a Boolean formula where the atoms are processes of $\ov{\PH}$.
 
@@
   \label{def:pp}
-  A \emph{playability property} (PP) is an element of the language $\F$ inductively defined by:
+  A \emph{playability property} is an element of the language $\F$ inductively defined by:
   \begin{itemize}
@@
   \end{itemize}
-  If $P \in \F$ is a PP and $\mysigma \in \PHsubl$ is a sub-state,
+  If $P \in \F$ is a playability property and $\mysigma \in \PHsubl$ is a sub-state of $\oPH$,
   we note $\Fsem{P}{\mysigma}$ the \emph{evaluation} of $P$ in $\mysigma$:
-%  We note $\Fsem{P}{s}$ the \emph{evaluation} of a PP $P \in \F$ in a state $s \in \ov{\PHl}$.
-%  The semantics of this evaluation is the following for any state $s \in \ov{\PHl}$:
   \begin{itemize}
@@
 \[\forall a \in \ov{\PHs}, \forall a_i \in \ov{\PHl}_a, \forall \mysigma \in \PHsubl,
-  \Fsem{\neg a_i}{s} \Leftrightarrow \Fsem{\bigvee_{\substack{a_j \in \PHl_a\\a_j \neq a_i}} a_j}{s}\]
+  \Fsem{\neg a_i}{\mysigma} \Leftrightarrow \Fsem{\bigvee_{\substack{a_j \in \PHl_a\\a_j \neq a_i}} a_j}{\mysigma}\]
 Indeed, if a process is not active in a state, this means that another process of the same sort is active.
@@
 %
-\begin{proof}
+\newproof{proofppplay}{Proof of \pref{th:ppplay}}
+\begin{proofppplay}
   By definition of the semantics of a PH given in \pref{def:play}.
-\end{proof}
+\end{proofppplay}
 
-\newcommand{\n}[1][h]{n^{#1}}
-\newcommand{\m}[1][h,i]{m^{#1}}
-
-Because we only use classical logic operators, we can compute the Disjunctive Normal Form (DNF) of any PP.
+Because we only use classical logic operators, we can compute the Disjunctive Normal Form (DNF) of any playability property.
 For any action $h \in \ov{\PHh}$, this DNF takes the form:
@@
 thus creating a new PH model which is entailed in the restrictions depicted in \pref{ssec:hypothesis}.
-%Indeed, for any $i \in \segm{1}{\n}$, the PP $\bigwedge_{j \in \segm{1}{\m}} p_{i,j}$
 In this second case, we denote, for any $i \in \segm{1}{\n}$:
@@
   $h \in \ov{\PHh}$ is playable in $s \in \ov{\PHl}$ if and only if
-  $\exists \mysigma \subseteq s, \Fsem{\F(h)}{\mysigma}$.
+  $\exists \mysigma \subseteq s, \Fsem{\Fop{h}}{\mysigma}$.
 %  \[\exists i \in \segm{1}{\n}, \exists \mysigma \in \bigtimes{b \in \PHdep{i}{h}} \PHl_b,
@@
 %
-\begin{proof}
-  ($\Rightarrow$) If $\Fsem{\F(h)}{s}$ then $\F(h) \not\equiv \bot$ and, by property of a DNF,
-    at least one of the $\n$ conjunctions of $\F(h)$ is true in $s$.
+\newproof{proofppplaysubset}{Proof of \pref{th:ppplaysubset}}
+\begin{proofppplaysubset}
+  ($\Rightarrow$) If $\Fsem{\Fop{h}}{s}$ then $\Fop{h} \not\equiv \bot$ and, by property of a DNF,
+    at least one of the $\n$ conjunctions of $\Fop{h}$ is true in $s$.
     Suppose the $i$\textsuperscript{th} conjunction is true in $s$, with $i \in \segm{1}{\n}$;
     then we have: $\forall j \in \segm{1}{\m}, p_{i,j} \in s$.
-    Let $\mysigma \in \bigtimes{b \in \PHdep{i}{h}} \PHl_b$ with $\forall b \in \PHdep{i}{h}, \PHget{\mysigma}{b} = \PHget{s}{b}$.
+%    Let $\mysigma \in \bigtimes{b \in \PHdep{i}{h}} \PHl_b$
+    Let $\mysigma \in \PHsubl_{\PHdep{i}{h}}$
+    with $\forall b \in \PHdep{i}{h}, \PHget{\mysigma}{b} = \PHget{s}{b}$.
     We immediately have: $\mysigma \subseteq s$,
-    and, by construction of $\PHdep{i}{h}$, $\Fsem{\F(h)}{\mysigma}$.
+    and, by construction of $\PHdep{i}{h}$, $\Fsem{\Fop{h}}{\mysigma}$.
 
   ($\Leftarrow$) Trivial.
-\end{proof}
-
-\newcommand{\flats}[1]{\lfloor #1 \rfloor}
-\newcommand{\unflats}[1]{\lceil #1 \rceil}
+\end{proofppplaysubset}
 
@@
       where $\PHs_f = \{ f^{h,i} \mid h \in \ov{\PHh} \wedge \n \geq 1 \wedge i \in \segm{1}{\n} \}$;
-    \item $\PHl = \left( \underset{a \in \ov{\PHs}}{\times} \PHl_{a} \right) \times
-      \left(\underset{f^{h,i} \in \PHs_f}{\times} \PHl_{f^{h,i}} \right)$,
+    \item $\PHl = \left( \bigtimes{a \in \ov{\PHs}} \PHl_{a} \right) \times
+      \left(\bigtimes{f^{h,i} \in \PHs_f} \PHl_{f^{h,i}} \right)$,
       where $\forall a \in \ov{\PHs}, \PHl_{a} = \ov{\PHl}_{a}$, and
       $\forall f^{h,i} \in \PHs_f,
-      \PHl_{f^{h,i}} = \{ f^{h,i}_\mysigma \mid \mysigma \in \underset{b \in \PHdep{i}{h}}{\times} \PHl_{b} \}$;
+      \PHl_{f^{h,i}} = \{ f^{h,i}_\mysigma \mid \mysigma \in \PHsubl_{\PHdep{i}{h}} \}$;
     \item $\PHh^{(1)} = \{ \PHhit{a_k}{f^{h,i}_\mysigma}{f^{h,i}_{\mysigma'}} \mid
@@
       f^{h,i} \in \PHs_f \wedge
-      f^{h,i}_\mysigma \in \PHl_{f^{h,i}} \wedge \Fsem{\F(h)}{\mysigma} \}$.
+      f^{h,i}_\mysigma \in \PHl_{f^{h,i}} \wedge \Fsem{\Fop{h}}{\mysigma} \}$.
   \end{itemize}
@@
 \begin{theorem}[$(\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}}) \approx \PHflat(\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}})$]
-\label{thm:bisimPHP}
+\label{th:bisimPHP}
   Let $\ov{\PH} = (\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}})$ a PH with $k$ classes of priorities,
@@
 %
-\begin{proof}
+\newproof{proofbisimPHP}{Proof of \pref{th:bisimPHP}}
+\begin{proofbisimPHP}
   (\ref{php2ph}) Let $\flats{\os} = s$.
@@
     therefore, $\os' = \os \PHplay h$ and $\target{h} \in \os$.
-    Furthermore, given \pref{th:ppplay}, $\Fsem{\F(h)}{\os}$,
-    and given \pref{th:ppplaysubset}, there exists $\mysigma \subseteq s$ so that $\Fsem{\F(h)}{\mysigma}$.
+    Furthermore, given \pref{th:ppplay}, $\Fsem{\Fop{h}}{\os}$,
+    and given \pref{th:ppplaysubset}, there exists $\mysigma \subseteq s$ so that $\Fsem{\Fop{h}}{\mysigma}$.
     Therefore, by construction of $\PH$ (\pref{def:flattening}) there exists
@@
     By construction of the flattening (\pref{def:flattening}), there exists $h \in \ov{\PHh}$ so that
-    $\target{h} = b_j$, $\bounce{h} = b_k$ and $\Fsem{\F(h)}{\mysigma}$.
+    $\target{h} = b_j$, $\bounce{h} = b_k$ and $\Fsem{\Fop{h}}{\mysigma}$.
     If $g$ is playable, this means that no other action in $\PHh^{(1)}$ is playable, and especially the cooperative sort
-    $f^{h,i}$ is already updated; therefore, $\mysigma \subseteq s$.
+    $f^{h,i}$ is already updated; therefore, $\mysigma \subseteq \os$.
     By \pref{th:ppplaysubset}, it comes that $h$ is playable in $\os$.
     Thus, $\unflats{s} \PHPtrans \unflats{s'}$.
-\end{proof}
+\end{proofbisimPHP}

### 2014-03-19 parts/models.tex
several fixes + refactoring of files

--- 2014-03-14 parts/models.tex
@@
 
-\subsection{Asynchronous Discrete Networks}
-\todo{Detail the equivalence with ADNs (cf. the annex)}
+% Equivalence with ADNs
+\input{parts/models-ph-php.tex}
 
-\subsection{PH with multiple classes of priorities}
-\todo{Reduce and reuse the flattening method}
-
-\newcommand{\ov}{\overline}
-\newcommand{\F}{F}
-\newcommand{\Fopsymbol}{\F}
-\newcommand{\Fop}[1]{\Fopsymbol(#1)}
-\newcommand{\Fsem}[2]{\left[#1\right](#2)}
-%\newcommand{\Fall}{\F}
-
-Consider a PH with $k \in \sN^*$ classes of priories:
-$\ov{\PH} = (\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}})$.
-We want to translate it to a PH with $2$ classes of priorities
-$\PH = (\PHs; \PHl; \PHa^{\angles{2}})$
-that respects all Criteria given in \pref{ssec:hypothesis}.
-
-A playability property (PP) as defined in \pref{def:pp} is a formula where the atoms are processes of $\ov{\PH}$.
-
-\begin{definition}[Playability property language ($\F$)]
-  \label{def:pp}
-  A \emph{playability property} (PP) is an element of the language $\F$ inductively defined by:
-  \begin{itemize}
-    \item $\top$ and $\bot$ belong to $\F$;
-    \item if $a \in \ov{\PHs}$ and $a_i \in \ov{\PHl}_a$, then $a_i \in \F$ and we call it an \emph{atom};
-    \item if $P \in \F$ and $Q \in \F$, then $\neg P \in \F$, $P \wedge Q \in \F$ and $P \vee Q \in \F$.
-  \end{itemize}
-  We note $\Fsem{P}{s}$ the \emph{evaluation} of a PP $P \in \F$ in a state $s \in \ov{\PHl}$.
-  The semantics of this evaluation is the following for any state $s \in \ov{\PHl}$:
-  \begin{itemize}
-    \item if $P = a_i \in \ov{\PHs}_a$ is an atom, with $a \in \ov{\PHs}$, then $\Fsem{a_i}{s}$ is true iff $a_i \in s$;
-    \item if $P$ is not an atom, then $\Fsem{P}{s}$ is true iff all its subformulas are inductively true in $s$
-      with the classical semantics for the logic operators $\top$, $\bot$, $\neg$, $\wedge$ and $\vee$.
-  \end{itemize}
-\end{definition}
-
-Because we only use classical logic operators, the formulas of Boolean logic on distribution and negation (de Morgan's laws) can be used.
-We also have the following property for the negation of an atom:
-\[\forall a \in \ov{\PHs}, \forall a_i \in \ov{\PHl}_a, \Fsem{\neg a_i}{s}
-  \Leftrightarrow \Fsem{\bigvee_{\substack{a_j \in \PHl_a\\a_j \neq a_i}} a_j}{s}\]
-Indeed, if a process is not active in a state, this means that another process of the same sort is active.
-
-In \pref{def:fop}, we finally define the the operator $\Fopsymbol$ which characterizes the playability of an action
-given the semantics of PH (\pref{def:play}).
-\begin{definition}[Playability property of an action ($\Fopsymbol : \PHh \rightarrow \F$)]\label{def:fop}
-  $$\forall h \in \ov{\PHh}, \Fop{h} \equiv \hitter{h} \wedge
-    \left( \bigwedge_{\substack{g \in \PHh^{(n)}\\n < \prio(h)}}
-    \neg \left( \target{g} \wedge \hitter{g}\right) \right)$$
-\end{definition}
-
-By definition of the semantics of a PH given in \pref{def:play},
-an action $h \in \ov{\PHh}$ is playable in a state $s \in \ov{\PHl}$ iff $\Fsem{\Fop{h}}{s}$.
-
-\todo{--- Le reste de la traduction ici ---}
-
-\newcommand{\n}[1][h]{n^{#1}}
-\newcommand{\m}[1][h,i]{m^{#1}}
-
-Because we only use classical logic operators, we can compute the PP on any action in $\ov{\PH}$.
-For any action $h \in \ov{\PHh}$, this DNF takes the form:
-\[\Fop{h} \equiv \bigvee_{i \in \segm{1}{\n}} \left( \bigwedge_{j \in \segm{1}{\m}} p_{i,j} \right)\]
-where $\n \in \sN$ and $\forall i \in \segm{1}{\n}, \m \in \sN^*$.
-If $\n = 0$, then $\Fop{h} \equiv \bot$; this means that $h$ can never be played
-due to preemptions by other actions with higher priorities.
-If $\Fop{h} \not\equiv \bot$, on the other hand, then in this case $\Fop{h}$
-can be seen as a disjunction of $\n$ smaller playability properties consisting only of conjunctions of atoms.
-These $\n$ conjunctions can be translated to as many prioritized cooperative sorts,
-thus creating a new PH model which is entailed in the restrictions depicted in \pref{ssec:hypothesis}.
-%Indeed, for any $i \in \segm{1}{\n}$, the PP $\bigwedge_{j \in \segm{1}{\m}} p_{i,j}$
-In this second case, we denote, for any $i \in \segm{1}{\n}$:
-$\PHdep{i}{h} = \{ \PHsort(p_{i,j}) \mid j \in \segm{1}{\m} \}$.
-
-\begin{definition}
-  \label{def:flattening}
-  If $k \in \sN^*$, we note $\PHflat(\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}}) = (\PHs; \PHl; \PHa^{\angles{2}})$
-  the flattening of the PH with $k$ classes of priorities $\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}}$, with:
-  \begin{itemize}
-    \item $\PHs = \ov{\PHs} \cup \{ f^{h,i} \mid h \in \ov{\PHh} \wedge \n \geq 1 \wedge i \in \segm{1}{\n} \}$;
-    \item $\PHl = \underset{a \in \PHs}{\times} \PHl_{a}$, where
-      $\PHl_{a} = \ov{\PHl}_{a}$ if $a \in \ov{\PHs}$; and 
-      $\PHl_{f^{h,i}} = \{ f^{h,i}_\varsigma \mid \varsigma \in \underset{b \in \PHdep{i}{h}}{\times} \PHl_{b} \}$ otherwise.
-    \item $\PHh^{(1)} = \{ \PHhit{a_k}{f^{h,i}_\varsigma}{f^{h,i}_{\varsigma'}} \mid
-      h \in \ov{\PHh} \wedge %\n \geq 1 \wedge i \in \segm{1}{\n} \wedge
-      a \in \PHdep{i}{h} \wedge a_k \in \PHl_a \wedge
-      f^{h,i}_\varsigma , f^{h,i}_{\varsigma'} \in \PHl_{f^{h,i}} \wedge
-      \PHget{\varsigma}{a} \neq a_k \wedge \varsigma' = \varsigma \Cap \{ a_k \} \}$;
-%      \todo{From here: ...} \PHget{\varsigma'}{a} = a_k \wedge
-%      (\forall b \in \PHdep{i}{h} \setminus \{ a \}, \PHget{\varsigma'}{b} = \PHget{\varsigma}{b}) \}$;
-%      \todo{... can be replaced by: $\varsigma' = \varsigma \Cap \{ a_k \}$}
-    \item $\PHh^{(2)}=\{ \PHhit{f^{h,i}_\varsigma}{\target{h}}{\bounce{h}} \mid
-      h \in \ov{\PHh} \wedge f^{h,i}_\varsigma \in \PHl_{f^{h,i}} \wedge \Fsem{h}{\varsigma} \}$.
-
-    \item $\Hits^{(1)}= \{ \hit{a^j_k}{f^i_\varsigma}{f^i_{\varsigma'}}
-      \mid i\in\segm{1}{n} \wedge
-      j\in\DNdep(f^i) \wedge a^j_k\in \PHl_{a^j} \wedge f^i_\varsigma\in \PHl_{f^i}
-      \wedge
-      \get{\varsigma}{a^j}\neq a^j_k 
-      \wedge \get{\varsigma'}{a^j}=a^j_k
-      \wedge (\get{\varsigma'}{a^{l}}=\get{\varsigma}{a^l},
-      \forall l\in\segm{1}{n},l\neq j)
-      \}$, 
-      the set of actions with priority $1$ that update cooperative sorts;
-
-          \item $\Hits^{(2)}=\{ \hit{f^i_\varsigma}{a^i_k}{a^i_{k'}} \mid i\in\segm{1}{n} \wedge
-          f^i_\varsigma\in \PHl_{f^i} \wedge
-          a^i_k\in \PHl_{a^i}\wedge k\neq k' \wedge f^i(\decode \varsigma) = k'
-        \}$,
-
-  \end{itemize}
-
-\end{definition}
-
-\todo{--- Le reste de la traduction ici ---}
-
-\begin{definition}[Equivalent Process Hitting]\label{def:equiv}
-  Two PH models $\ov{\PH} = (\ov{\PHs}; \ov{\PHl}; \ov{\PHh}^\angles{k})$ and $\PH = (\PHs; \PHl; \PHh^\angles{n})$,
-  where $k, n \in \sN^*$,
-  are \emph{equivalent} iff:
-  $$\forall s \in \ov{\PHl}, ( \exists h = \PHhit{A}{b_i}{b_j} \in \PHh, \Fsem{\F(h)}{s}
-    \Longleftrightarrow \exists g = \PHhit{\ov{A}}{b_i}{b_j} \in \ov{\PHh}, \Fsem{\F(g)}{s} )$$
-\end{definition}
-
-We note that several PH models can be equivalent to a same PH model.
-For example, adding actions that are never playable (due to priorities) allows to create an equivalent model.
-
-\begin{theorem}[Bisimilarity of equivalent PH]
-  Two equivalent PH models are bisimilar.
-\end{theorem}
-
-\begin{proof}
-  Let $\PH = (\PHs; \PHl; \PHh^\angles{k})$ and $\ov{\PH} = (\PHs; \PHl; \ov{\PHh}^\angles{n})$
-  two equivalent PH models, with $k, n \in \sN^*$.
-  We want to show:
-  $$\forall s, s' \in \PHl, s \neq s', s \trans{\PH} s' \Longleftrightarrow s \trans{\ov{\PH}} s' $$
-  Let $s, s' \in \PHl$ with $s \neq s'$.
-  ($\Rightarrow$) Suppose $s \trans{\PH} s'$.
-  It means that there exists $h = \PHhit{A}{b_i}{b_j} \in \PHh$ so that $s' = s \PHplay h = s \Cap b_j$
-  in $\PH$ (\pref{def:play}), \ie $\Fsem{\F(h)}{s}$ and $b_i \in s$.
-  As $\ov{\PH}$ is equivalent to $\PH$,
-  there exists $g = \PHhit{\ov{A}}{b_i}{b_j} \in \ov{\PHh}$ so that $\Fsem{\F(g)}{s}$ (\pref{def:equiv}).
-  Therefore, $g$ is playable in $s$ and $s \PHplay g = s \Cap b_j = s'$;
-  which means: $s \trans{\ov{\PH}} s'$
-  ($\Leftarrow$) Same reasoning.
-\end{proof}
-
-\begin{definition}[Flattening]
-  Given a PH model $\PH = (\PHs; \PHl; \PHh^\angles{k})$, where $k \in \sN^*$,
-  we call \emph{flattening} of $\PH$ any PH model $\ov{\PH} = (\PHs; \PHl; \ov{\PHh}^\angles{1})$
-  with 1 class of priority and cooperative actions that is equivalent to $\PH$.
-\todo{Is this definition really useful?}
-\end{definition}
-
-\begin{theorem}[Existence of a flattening]\label{th:exists-flattening}
-  For all $k \in \sN^*$, there exists a flattening of any PH model with $k$ priorities and cooperative actions.
-\todo{Is this theorem really useful?}
-\end{theorem}
-
-The demonstration of this theorem is given in the following subsection.
-
-\begin{comment}
-
-%\newcommand{\poz}{\F}
-%\newcommand{\pon}{P_{DNF}}
-%\newcommand{\unneg}{\mathsf{UnNeg}}
-%\newcommand{\negate}{\mathsf{Negate}}
-%\newcommand{\prednf}{\mathsf{Distribute}}
-%\newcommand{\dnf}{\mathsf{DNF}}
-%\newcommand{\DNF}{\dnf}
-%\newcommand{\dnff}{\delta\F}
-
-%\newcommand{\fun}{\mathcal{F}}
-
-\begin{definition}[Equivalent Process Hitting]\label{def:equiv}
-  Two PH models $\PH = (\PHs; \PHl; \PHh^\angles{k})$ and $\ov{\PH} = (\PHs; \PHl; \ov{\PHh}^\angles{n})$,
-  where $k, n \in \sN^*$,
-  are \emph{equivalent} iff:
-  $$\forall s \in \PHl, ( \exists h = \PHhit{A}{b_i}{b_j} \in \PHh, \Fsem{\F(h)}{s}
-    \Longleftrightarrow \exists g = \PHhit{\ov{A}}{b_i}{b_j} \in \ov{\PHh}, \Fsem{\F(g)}{s} )$$
-\end{definition}
-
-We note that several PH models can be equivalent to a same PH model.
-For example, adding actions that are never playable (due to priorities) allows to create an equivalent model.
-
-\begin{theorem}[Bisimilarity of equivalent PH]
-  Two equivalent PH models are bisimilar.
-\end{theorem}
-
-\begin{demo}
-  Let $\PH = (\PHs; \PHl; \PHh^\angles{k})$ and $\ov{\PH} = (\PHs; \PHl; \ov{\PHh}^\angles{n})$
-  two equivalent PH models, with $k, n \in \sN^*$.
-  We want to show:
-  $$\forall s, s' \in \PHl, s \neq s', s \trans{\PH} s' \Longleftrightarrow s \trans{\ov{\PH}} s' $$
-  Let $s, s' \in \PHl$ with $s \neq s'$.
-  ($\Rightarrow$) Suppose $s \trans{\PH} s'$.
-  It means that there exists $h = \PHhit{A}{b_i}{b_j} \in \PHh$ so that $s' = s \PHplay h = s \Cap b_j$
-  in $\PH$ (\pref{def:play}), \ie $\Fsem{\F(h)}{s}$ and $b_i \in s$.
-  As $\ov{\PH}$ is equivalent to $\PH$,
-  there exists $g = \PHhit{\ov{A}}{b_i}{b_j} \in \ov{\PHh}$ so that $\Fsem{\F(g)}{s}$ (\pref{def:equiv}).
-  Therefore, $g$ is playable in $s$ and $s \PHplay g = s \Cap b_j = s'$;
-  which means: $s \trans{\ov{\PH}} s'$
-  ($\Leftarrow$) Same reasoning.
-\end{demo}
-
-\begin{definition}[Flattening]
-  Given a PH model $\PH = (\PHs; \PHl; \PHh^\angles{k})$, where $k \in \sN^*$,
-  we call \emph{flattening} of $\PH$ any PH model $\ov{\PH} = (\PHs; \PHl; \ov{\PHh}^\angles{1})$
-  with 1 class of priority and cooperative actions that is equivalent to $\PH$.
-\todo{Is this definition really useful?}
-\end{definition}
-
-\begin{theorem}[Existence of a flattening]\label{th:exists-flattening}
-  For all $k \in \sN^*$, there exists a flattening of any PH model with $k$ priorities and cooperative actions.
-\todo{Is this theorem really useful?}
-\end{theorem}
-
-The demonstration of this theorem is given in the following subsection.
-
-\end{comment}
+% Flattening of a PH with k priorities
+\input{parts/models-ph-dn.tex}

### 2014-03-19 parts/suppl-ph-dn.tex
several fixes + refactoring of files

@@
 
-\pref{thm:bisimDN} states the weak bisimulation relation between an ADN and its encoding in
+\pref{th:bisimDN} states the weak bisimulation relation between an ADN and its encoding in
 PH with $2$ classes of priorities.
@@
 \begin{theorem}[$\DNdef \approx \toPH\DNdef$]~
-\label{thm:bisimDN}
+\label{th:bisimDN}
   \begin{enumerate}
@@
 \end{theorem}
-\begin{proof}
+%
+\newproof{proofbisimDN}{Proof of \pref{th:bisimDN}}
+\begin{proofbisimDN}
 (\ref{adn2ph}) From \pref{def:DN}, $x\DNtrans x'\Rightarrow \exists i\in\segm{1}{n},
@@
 $\decode s\DNtrans \decode{s'}$.
-\end{proof}
+\end{proofbisimDN}

### 2014-03-19 parts/suppl-ph-php.tex
several fixes + refactoring of files

\section{Proofs about flattening (\pref{ssec:flattening})}
\label{suppl:demoflattening}

### 2014-03-19 parts/suppl-sa.tex
several fixes + refactoring of files

\section{Proof of Under-approximation (\pref{th:approxinf})}
\label{suppl:demoapproxinf}

In the following, we denote:
%$\BvProc = \Bv \cap \PHproc$, $\BvObj = \Bv \cap \Obj$ and $\BvSol = \Bv \cap \Sol$.
$\Bee{X}{Y} = \Be \cap (X \times Y)$, with $X, Y$ amongst $\PHproc$, $\Obj$ and $\Sol$.

\newproof{proofapproxinf}{Proof of \pref{th:approxinf}}
\begin{proofapproxinf}
We note $max\ctx = \ctx \Cap \allprocs(\cwB)$ the context supported by $\cwB$.

Let $(a_i, ps) \in \Bee{\Proc}{\Sol}$ be an edge linking the required process of a cooperative sort to a solution set and suppose all children of $ps$ are concretisable.
We label all processes of $ps$ by an integer: $ps = \{ p_n \}_{n \in \indexes{ps}}$.
Let us prove by induction that for all $n \in \indexes{ps}$, there exists a scenario $\delta_n$ so that:
$\forall i \in \segm{1}{n}, \PHget{(s \PHplay \delta_n)}{\PHsort(p_i)} = p_i$.
\begin{itemize}
  \item It is straightforward for $\delta_0 = \varepsilon$.
  \item Suppose such $\delta_n$ exists and let $q = \PHget{(s \PHplay \delta_n)}{\PHsort(p_{n+1})}$.
    By hypothesis, $(a_i, ps)$ is coherent (\pref{def:coherent}) and all processes of $ps$ are processes of components;
    this means that none of the processes needed to solve $p_{n+1}$ is another process of the same sort than another process of $ps$.
    Therefore, there exists $\delta' \in \muconcr_{s \PHplay \delta_n}(\PHobj{q}{p_{n+1}})$,
    so that $\forall i \in \segm{1}{n+1}$, $\PHget{(s \PHplay \delta_n \PHplay \delta')}{\PHsort(p_{i})} = p_{i}$.
    Finally, by \pref{th:update}, there exists a scenario $\delta'' \in \restriction{\Sce}{1}(s \PHplay \delta_n \PHplay \delta')$
    so that, if we denote $\delta_{n+1} = \delta_n \PHplay \delta' \PHplay \delta''$,
    we have: $\update(s \PHplay \delta_n \PHplay \delta') = s \PHplay \delta_{n+1}$ and the same property about processes (by \pref{th:hcscomp}).
\end{itemize}
Therefore, $\delta = \delta_{|ps|}$ exists, and given its properties, we have: $\PHget{(s \PHplay \delta)}{a} = a_i$
and $\update(s \PHplay \delta) = s \PHplay \delta$.

As there is no cycle in $\cwB$, we show by induction that $\forall s\in L, s\subseteq max\ctx$, 
for all objective $P$ in $\Bv \cap \Obj$ so that $\PHtarget(P) \in s$,
$\exists \delta \in \muconcr_s(P)$.% and $\ceil(\delta) \subseteq max\ctx$.
\begin{itemize}
  \item If $(P, \emptyset) \in \Bee{\Obj}{\Sol}$, either $\PHtarget(P) = \PHbounce(P)$ and $\delta = \emptyseq$;
    or $\forall \zeta \in \BS(P), \zeta \in \Sce(s) \wedge \PHsort(\zeta) = \{ \PHsort(P) \}$
    and $\delta = \delta_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_{|\zeta|} \PHplay \zeta_{|\zeta|}$ is a valid sequence given by \pref{th:hcompcomp}.

  \item Suppose all children objectives of $P$ are concretizable.
%  \begin{itemize}
    %\item 
    If $\exists (P, Q) \in \Bee{\Obj}{\Obj}$, then by hypothesis,
      $\muconcr_{s}(\obj{\PHtarget(P)}{\PHtarget(Q)} \concat Q) \neq \emptyset$, thus
      $\muconcr_{s}(P) \neq \emptyset$.
    %\item 
    Else, by \pref{def:maxCont}, the concretizations of the children of $P$ require no process of sort $\PHsort(P)$.
      Furthermore, there exists $\zeta \in \BS(P)$ so that $(P, \aZ) \in \Bee{\Obj}{\Sol}$.
      We show by induction that for all $n \in \indexes{\zeta}$, there is a scenario $\delta_n$ so that $\PHget{(s \PHplay \delta_n)}{\PHsort(P)} = \PHbounce(\zeta_n)$.
      \begin{itemize}
        \item[$\circ$] Suppose that $\delta_n$ exists and let $\zeta_n = \PHhit{b_i}{a_j}{a_k}$.
        By hypothesis there exists $\delta' \in \muconcr_{s \PHplay \delta_n}(\PHobj{\any}{b_i})$ with $\PHsort(P) \notin \PHsort(\delta')$ (by \pref{def:maxCont}).
        By \pref{th:update} there exists $\delta'' \in \restriction{\Sce}{1}(s \PHplay \delta')$ so that $\update(s \PHplay \delta') = s \PHplay \delta' \PHplay \delta''$.
        Furthermore, $\PHget{(s \PHplay \delta' \PHplay \delta'')}{b} = b_j$ (by \pref{th:hcompcomp} if $b \in \components$ or \pref{th:hcscomp} if $b \in \cs$).
        Therefore, $\delta_{n+1} = \delta_n \PHplay \delta' \PHplay \delta'' \PHplay \zeta_n$.
      \end{itemize}
      Thus, $\delta_{|\zeta|} \in \muconcr_s(P)$. % and $\ceil(\delta) \subseteq max\ctx$.
%  \end{itemize}
\end{itemize}
Finally, as $\muconcr_{max\ctx}(\w) \neq \emptyset$, $\uconcr(\w) \neq \emptyset$ (\pref{th:uconcr-ctx}).
\end{proofapproxinf}

### 2014-03-19 main.tex
nouvelle affiliation
titre

@@
 \begin{frontmatter}
-\title{Under-approximation of Reachability in Multivalued Asynchronous Networks}
+\title{Sufficient Conditions for Reachability in Automata Networks with Priorities}
 
@@
 \ead{Maxime.Folschette@irccyn.ec-nantes.fr}
-\author[eth]{Loïc Paulevé}
+\author[lri,amib]{Loïc Paulevé}
 \author[irccyn]{Morgan Magnin}
@@
 
-\address[eth]{BISON group, Automatic Control Laboratory, ETH Zürich\\
-Physikstrasse 3, 8092 Zurich, Switzerland.}
+\address[lri]{CNRS, Laboratoire de Recherche en Informatique (LRI)\\
+		Université Paris-Sud - CNRS UMR 8623, France}
+\address[amib]{AMIB group, Inria Saclay, France}{}
 

### 2014-03-19 main.tex
change title + todo in abstract

--- 2014-03-03 main.tex
@@
 \begin{frontmatter}
-\title{Under-approximation of Reachability in Multivalued Asynchronous Networks}
+\title{\todo{Title} Sufficient conditions for reachability in automat networks with priorities}
+%\title{Under-approximation of Reachability in Multivalued Asynchronous Networks}
 
@@
 \begin{abstract}
+\todo{Add flattening}
 The Process Hitting is a recently introduced framework designed for the modelling of concurrent systems.

### 2014-03-19 parts/models-ph-dn.tex
restructuration

@@
-\subsection{Asynchronous Discrete Networks}
-\todo{Detail the equivalence with ADNs (cf. the annex)}
+\subsection{Weak Bisimulation of Asynchronous Discrete Networks}
+\label{sec:dn}
+
+We exhibit an encoding of Asynchronous Discrete Networks (ADN) with the Process
+Hitting using two classes of priorities, and prove a weak bisimulation relation.
+
+A Discrete Network gathers a finite number of components $i\in\segm{1}{n}$ having a discrete finite domain
+$\mathbb F^i$ that we note $\mathbb{F}^i = \segm{1}{l_i}$.
+For each component $i\in\segm{1}{n}$, a map $\mathbb F \rightarrow \mathbb F^i$ is defined, where
+$\mathbb F = \mathbb F^1 \times \cdots \times \mathbb F^n$, giving the next value of the component
+with respect to the global state of the network.
+Typically $f^i$ depends on a subset of components that we denote $\DNdep(f^i)$.
+In the case of Asynchronous Discrete Networks (ADN), a transition relation $\DNtrans\subseteq \mathbb
+F\times \mathbb F$ is defined such that $x\DNtrans x'$ if and only if there exists a unique
+$i\in\segm{1}{n}$ such that $\get{x'}{i}=f^i(x)$ and $\forall j\in\segm{1}{n}, j\neq i, \get{x'}{j}
+=\get{x}{j}$, \ie one and only one component has been updated.
+This is formalised in \pref{def:DN}.
+
+\begin{definition}[Asynchronous Discrete Network (ADN)]
+\label{def:DN}
+  An ADN is defined by a couple $(\mathbb F, \langle f^1, \dots, f^n \rangle)$
+  where $\mathbb{F} = \mathbb{F}^1\times\dots\times\mathbb{F}^n$,
+  and $\forall i\in\segm{1}{n}$,
+  $f^i: \mathbb{F} \rightarrow \mathbb{F}^i$ with
+  $\mathbb{F}^i = \segm{1}{l_i}$.
+  Given two states $x,x'\in\mathbb F$, the transition relation $\DNtrans$ is given by
+  \[
+  x\DNtrans x' \Longleftrightarrow
+    \exists i\in\segm{1}{n}, f^i(x)=\get{x'}{i}
+    \wedge \forall j\in\segm{1}{n}, j\neq i, \get{x}{j}=\get{x'}{j}
+  \enspace,
+  \]
+  where $\get{x}{i}$ is the $i$-th component of $x$.
+  %
+  We note $\DNdep(f^i)\subseteq \segm{1}{n}$ the set of components on which the value of $f^i$
+  depends: $\forall x,x'\in \mathbb F$ such that $\forall
+  j\in\DNdep(f^i), \get{x}{j}=\get{x'}{j}$, necessarily $f^i(x)=f^i(x')$.
+\end{definition}
+
+Let us denote the encoding of the ADN $\DNdef$ in Process Hitting with $2$ classes
+of priorities by $\toPH\DNdef$ (\pref{def:DN2PH}).
+For each component $i\in\segm{1}{n}$ of the ADN, two sorts are built: $a^i$ acting for the component
+value, and $f^i$ acting for a cooperative sort between the components $\DNdep(f^i)$.
+Sorts $a^i$ have one process $a^i_k$ per element in $k\in\mathbb F^i$.
+Sorts $f^i$ have one process $f^i_\varsigma$ per state $\varsigma \in \underset{j\in\DNdep(f^i)}{\times}
+\PHl_{a^j}$.
+Two classes of actions are then defined:
+$\Hits^{(1)}$ is the set of actions updating the cooperative sorts according to the current state of the
+components:
+if $j\in\DNdep(f^i)$, $a^j_k$ hits each process $f^i_\varsigma$ where $\get{\varsigma}{a^j}\neq
+a^j_k$ to make it bounce to the process $f^i_{\varsigma \Cap a^j_k}$.
+%$f^i_{\varsigma'}$ where $\get{\varsigma'}{a^j}=a^j_k$.
+$\Hits^{(2)}$ is the set of actions encoding the transitions in the ADN:
+$f^i_\varsigma$ hits the processes of sort $a^i$ to make them bounce to the process
+$a^i_{k'}$ if and only if $k'=f^i(\decode \varsigma)$;
+$\decode \varsigma$ being the ADN state corresponding to the PH (partial) state $\varsigma$ (note that
+$f^i(\decode \varsigma)$ is fully defined because $\decode \varsigma$ specifies the state for all
+the components in $\DNdep(f^i)$).
+
+\begin{definition}
+\label{def:DN2PH}
+  $\toPH\DNdef=(\Sigma,\PHl,(\Hits^{(1)},\Hits^{(2)}))$ is the Process Hitting with 2 classes of priority encoding the
+  ADN $\DNdef$, with:
+  \begin{itemize}
+    \item $\Sigma = \{ a^1, \dots, a^n \} \cup \{ f^1, \dots, f^n \}$,
+      the sorts for components ($a^i$) and cooperative sorts ($f^i$);
+
+    \item $\PHl=\underset{i\in\segm{1}{n}}{\times} \PHl_{a^i} \times \underset{i\in\segm{1}{n}}{\times} \PHl_{f^i}$, where
+      $\PHl_{a^i}=\{a^i_0, \dots, a^i_{l_i}\}$, and
+      $\PHl_{f^i}=\{f^i_\varsigma \mid \varsigma\in\underset{j\in\DNdep(f^i)}{\times} \PHl_{a^i} \}$
+      if $\DNdep(f^i)\neq\emptyset$, otherwise
+      $\PHl_{f^i}=\{f^i_\emptyset\}$;
+
+    \item $\Hits^{(1)}= \{ \hit{a^j_k}{f^i_\varsigma}{f^i_{\varsigma'}}
+      \mid i\in\segm{1}{n} \wedge
+      j\in\DNdep(f^i) \wedge a^j_k\in \PHl_{a^j} \wedge f^i_\varsigma\in \PHl_{f^i}
+      \wedge
+      \get{\varsigma}{a^j}\neq a^j_k 
+      \wedge \get{\varsigma'}{a^j}=a^j_k
+      \wedge (\get{\varsigma'}{a^{l}}=\get{\varsigma}{a^l},
+      \forall l\in\segm{1}{n},l\neq j)
+      \}$, 
+      the set of actions with priority $1$ that update cooperative sorts;
+
+    \item $\Hits^{(2)}=\{ \hit{f^i_\varsigma}{a^i_k}{a^i_{k'}} \mid i\in\segm{1}{n} \wedge
+          f^i_\varsigma\in \PHl_{f^i} \wedge
+          a^i_k\in \PHl_{a^i}\wedge k\neq k' \wedge f^i(\decode \varsigma) = k'
+        \}$,
+      the set of actions with priority $2$ for updating the components using their respective discrete
+      maps.
+      $\decode \varsigma$ is defined below.
+  \end{itemize}
+  Given a state $s\in \PHl$ of the Process Hitting, 
+  $\decode s=x$ is the corresponding state in the ADN:
+  $\forall i\in\segm{1}{n}, \get{s}{a^i}=a^i_k \Rightarrow \get{x}{i}=k$.
+
+  \noindent
+  Given a state $x\in \mathbb F$ of the ADN, 
+  $\encode x=s$ is the corresponding state in the Process Hitting:
+  $\forall i\in\segm{1}{n}, \get{x}{i}=k \Rightarrow \get{s}{a^i}=a^i_k$
+  and
+  $\forall i\in\segm{1}{n}, \get{s}{f^i}=f^i_\varsigma$ with $f^i_\varsigma\in \PHl_{f^i}$
+  and $\forall j\in\DNdep(f^i), \get{\varsigma}{j}=\get{s}{a^j}$.
+\end{definition}
+
+\pref{th:bisimDN} states the weak bisimulation relation between an ADN and its encoding in
+PH with $2$ classes of priorities.
+Intuitively, actions updating cooperative sorts being prioritised, actions updating component
+sorts follow strictly the possible transitions of the ADN.
+
+\begin{theorem}[$\DNdef \approx \toPH\DNdef$]~
+\label{th:bisimDN}
+  \begin{enumerate}
+    \item \label{adn2ph} $\forall x,x'\in\mathbb F$,
+      $x\DNtrans x' \Longrightarrow \encode x \PHPtrans^* \encode{x'}$,
+      where $\PHPtrans^*$ is a finite sequence of $\PHPtrans$ transitions.
+
+    \item \label{ph2adn} $\forall s,s'\in \PHl$,
+      $s\PHPtrans s' \Longrightarrow \decode s = \decode {s'} \vee \decode s \DNtrans
+      \decode{s'}\enspace.$
+  \end{enumerate}
+\end{theorem}
+%
+\newproof{proofbisimADN}{Proof of \pref{th:bisimDN}}
+\begin{proofbisimADN}
+(\ref{adn2ph}) From \pref{def:DN}, $x\DNtrans x'\Rightarrow \exists i\in\segm{1}{n},
+f^i(x)=\get{x'}{i} \wedge \forall j\in\segm{1}{n},i\neq j, \get{x}{j}=\get{x'}{j}$.
+Let us assume (without loss of generality) that $f^i(x)=k'$, $\get{x}{i}=k$ and
+$\varsigma\in\underset{j\in\DNdep(f^i)}{\times} \PHl_{a^j}$ such that
+$\forall j\in\DNdep(f^i), \get{\varsigma}{j}=a^j_{\get{x}{j}}$.
+From \pref{def:DN2PH}, $h=\hit{f^i_\varsigma}{a^i_k}{a^i_{k'}}\in\Hits^{(2)}$.
+From the definition of $\encode x$,
+$a^i_k\in \encode x$ and $f^i_\varsigma\in \encode x$;
+moreover, as there is no action in $\Hits^{(1)}$ applicable in $\encode x$,
+$h$ is applicable in $\encode x$:
+$\encode x\PHPtrans \encode x\play h$.
+In $\encode x\play h$, the only applicable actions of priority $1$ are those having
+$a^i_{k'}$ as hitter and hitting cooperative sorts, giving a finite number of transitions towards
+$\encode{x'}$.
+
+(\ref{ph2adn}) $s\PHPtrans s'$ only if there exists an action $h$ applicable in $s$ such that
+$s\play h=s'$.
+If $\prio(h)=1$, then, by definition of $\Hits^{(1)}$, 
+$\decode s=\decode {s'}$.
+If $\prio(h)=2$, then $\forall i\in\segm{1}{n}$,
+if $\get{s}{f^i} = f^i_\varsigma$, then, $\forall j\in\DNdep(f^i),
+\get{\varsigma}{a^j}=\get{s}{a^j}$.
+Let $i\in\segm{1}{n}$ such that $\get{s}{a^i}\neq\get{s'}{a^i}$ ($i$ is unique for this
+transition).
+By \pref{def:DN2PH}, if $\get{s'}{a^i}=a^i_{k'}$, necessarily $f^i(\decode s)=k'$, hence
+$\decode s\DNtrans \decode{s'}$.
+\end{proofbisimADN}

### 2014-03-20 parts/example.tex
several fixes; first final version
titles
link
other chages after review (references, context)
change documentclass to elsarticle + .cls and .bst files
restructuration
simplifications in flattening + begin example

@@
 
-\section{Examples}\label{sec:example}
+\section{Biological Examples}\label{sec:example}
 
-\towrite{Exemple \texttt{livelock\_and.ph} : différent avec / sans priorités}
+\subsection{\ldots (metazoan)}
 
-\subsection{Large-scale application}
+\todo{Describe the model}
+
+\begin{example}
+  The model of \pref{fig:metazoan-php} gives an example of PH with $3$ classes of priorities.
+  Although the actions of the highest class of priority are only used to update a cooperative sort,
+  the actions of the intermediate priority do not follow the constraints of \pref{ssec:hypothesis},
+  thus having a biological meaning by representing different reaction speeds.
+
+  \begin{figure}[htp]
+    \centering
+    \scalebox{1}{
+    \begin{tikzpicture}
+      \TSort{(0,4)}{c}{2}{l}
+      \TSort{(1,1)}{f}{2}{l}
+      \TSort{(6,4)}{a}{2}{r}
+
+      \TSetTick{fc}{0}{00}
+      \TSetTick{fc}{1}{01}
+      \TSetTick{fc}{2}{10}
+      \TSetTick{fc}{3}{11}
+      \TSort{(4,1)}{fc}{4}{r}
+
+      \THit{fc_2}{prio}{a_0}{.west}{a_1}
+      \path[bounce, bend left]
+        \TBounce{a_0}{prio}{a_1}{.south west};
+
+      \THit{c_1}{prio}{a_1}{.west}{a_0}
+      \path[bounce, bend right]
+        \TBounce{a_1}{prio}{a_0}{.north west};
+
+      \THit{f_1}{bend left=30, in=90}{c_0}{.west}{c_1}
+      \path[bounce, bend left]
+        \TBounce{c_0}{}{c_1}{.south west};
+
+      \THit{c_1}{selfhit}{c_1}{.west}{c_0}
+      \path[bounce, bend right]
+        \TBounce{c_1}{}{c_0}{.north west};
+
+      \path (1.8, 1.5) edge[superprio,coopupdate] (3.2, 2);
+      \path (0.8, 4.5) edge[superprio,coopupdate] (3.2, 3);
+    \end{tikzpicture}
+    }
+    \caption{
+    \label{fig:metazoan-php}
+      An example of PH $\oPH$ with $3$ classes of priorities.
+      Actions of $\ov{\PHh}^{(3)}$ (lowest priority) are in thin lines,
+      actions of $\ov{\PHh}^{(2)}$ (intermediate priority) are in thick lines,
+      and actions of $\ov{\PHh}^{(1)}$ (highest priority), whose only purpose is to update the cooperative sort $fc$,
+      are not represented but modeled by the double dashed arrows.
+    }
+  \end{figure}
+\end{example}
+
+\begin{example}
+  \pref{fig:metazoan-ph} gives the flattened model of the PH of \pref{fig:metazoan-php}.
+  It contains $2$ classes of priority, and prioritized actions are only used to update cooperative sorts.
+  The simplifications mentioned at the end of \pref{ssec:flattening} have been applied:
+  \begin{itemize}
+    \item The auto-action $h_1 = \PHhit{c_1}{c_1}{c_0}$ in $\oPH$ has been flattened to a regular action $\PHhit{a_0}{c_1}{c_0}$
+      because its playability property could be simplified to $\Fop{h_1} \equiv c_1 \wedge a_0 \equiv a_0$.
+    \item The existing cooperative sort $fc$ was kept as in $\oPH$ to avoid an exploding complexity due to
+      the numerous updating actions in $\ov{\PHh}^{(1)}$.
+  \end{itemize}
+
+  \begin{figure}[htp]
+    \centering
+    \scalebox{1}{
+    \begin{tikzpicture}
+      \TSort{(-5,4)}{c}{2}{l}
+      \TSort{(0,1)}{f}{2}{l}
+      \TSort{(5,4)}{a}{2}{r}
+
+      \TSetTick{fc}{0}{00}
+      \TSetTick{fc}{1}{01}
+      \TSetTick{fc}{2}{10}
+      \TSetTick{fc}{3}{11}
+      \TSort{(3,0)}{fc}{4}{r}
+
+      \TSetTick{fa}{0}{00}
+      \TSetTick{fa}{1}{01}
+      \TSetTick{fa}{2}{10}
+      \TSetTick{fa}{3}{11}
+      \TSort{(-3,0)}{fa}{4}{l}
+
+      \THit{fc_2}{}{a_0}{.west}{a_1}
+      \path[bounce, bend left]
+        \TBounce{a_0}{}{a_1}{.south west};
+
+      \THit{fa_3}{}{c_0}{.east}{c_1}
+      \path[bounce, bend right]
+        \TBounce{c_0}{}{c_1}{.south east};
+
+      \THit{c_1.north east}{}{a_1}{.west}{a_0}
+      \path[bounce, bend right]
+        \TBounce{a_1}{}{a_0}{.north west};
+
+      \THit{a_0.south west}{}{c_1}{.east}{c_0}
+      \path[bounce, bend left]
+        \TBounce{c_1}{}{c_0}{.north east};
+
+      \path (0.8, 1.5) edge[prio,coopupdate] (2.2, 1.5);
+      \path (-4.3, 4.5) edge[prio,coopupdate] (2.2, 2.5);
+
+      \path (-0.8, 1.5) edge[prio,coopupdate] (-2.2, 1.5);
+      \path (4.3, 4.5) edge[prio,coopupdate] (-2.2, 2.5);
+    \end{tikzpicture}
+    }
+    \caption{
+    \label{fig:metazoan-ph}
+      An example of PH $\PH$ with $2$ classes of priorities.
+      Actions of $\PHh^{(2)}$ (unprioritized) are in thin lines,
+      and actions of $\PHh^{(1)}$ (prioritized) which are used to update cooperative sorts,
+      are abstracted by thick dashed arrows.
+    }
+  \end{figure}
+\end{example}
+
+\subsection{Large-scale Application}
 
@@
 \footnote{Model and scripts are available at
-\url{http://www.irccyn.ec-nantes.fr/~folschet/underapprox-tcrsig94.tbz2}.}.
+\url{http://www.irccyn.ec-nantes.fr/~folschet/underapprox-tcrsig94.zip}.}.
 Then, we verified the reachability for the independent activation of 4 outputs of the signalling

### 2014-03-20 parts/models-ph-php.tex
simplifications in flattening + begin example

@@
 \label{th:ppplay}
-  $h \in \ov{\PHh}$ is playable in $s \in \ov{\PHl}$ if and only if $\Fsem{\Fop{h}}{s}$.
+  $h \in \ov{\PHh}$ is playable in $s \in \ov{\PHl}$ if and only if $\Fsem{\Fop{h}}{s} \wedge \target{h} \in s$.
 \end{theorem}
@@
   $h \in \ov{\PHh}$ is playable in $s \in \ov{\PHl}$ if and only if
-  $\exists \mysigma \subseteq s, \Fsem{\Fop{h}}{\mysigma}$.
+  $\exists \mysigma \subseteq s, \Fsem{\Fop{h}}{\mysigma} \wedge \target{h} \in s$.
 %  \[\exists i \in \segm{1}{\n}, \exists \mysigma \in \bigtimes{b \in \PHdep{i}{h}} \PHl_b,
@@
     then there exists $h \in \ov{\PHh}$ playable in $\os$;
-    therefore, $\os' = \os \PHplay h$ and $\target{h} \in \os$.
-    Furthermore, given \pref{th:ppplay}, $\Fsem{\Fop{h}}{\os}$,
+    therefore, $\os' = \os \PHplay h$.
+    Furthermore, given \pref{th:ppplay}, $\Fsem{\Fop{h}}{\os}$ and $\target{h} \in \os$,
     and given \pref{th:ppplaysubset}, there exists $\mysigma \subseteq s$ so that $\Fsem{\Fop{h}}{\mysigma}$.
@@
     $f^{h,i}$ is already updated; therefore, $\mysigma \subseteq \os$.
-    By \pref{th:ppplaysubset}, it comes that $h$ is playable in $\os$.
-    Thus, $\unflats{s} \PHPtrans \unflats{s'}$.
+    Furthermore, $b_j \in \os$.
+    Thus, by \pref{th:ppplaysubset}, it comes that $h$ is playable in $\os$,
+    and $\unflats{s} \PHPtrans \unflats{s'}$.
 \end{proofbisimPHP}
+
+We showed in this subsection that it is possible to model a PH model with $k$ classes of priorities as a PH model
+with $2$ classes of priorities that respects all Criteria of \pref{ssec:hypothesis} and with the same dynamics.
+We note however that the translation given in this section may not be minimal in terms of number of actions
+or cooperative sorts.
+We give here several ways to simplify the resulting model, but we do not give the proofs.
+
+\paragraph{Additional properties}
+It is possible to obtain a flattened PH with the same dynamics
+by simplifying the playability property of an action $h = \PHhit{a_i}{b_j}{b_k}$ with the following properties:
+\begin{itemize}
+  \item it is always possible to simplify the target because its presence is checked besides: $b_j \equiv \top$;
+  \item any process $b_l \neq b_j$ of the same sort than $b_k$ always prevents the playability, thus: $b_l \equiv \bot$;
+  \item if $c_p, c_q$ are different processes ($c_p \neq c_q$) of the same sort $c$, then $c_p \wedge c_q \equiv \bot$.
+\end{itemize}
+
+\paragraph{Removal of the resulting cooperative sorts}
+There are two cases where it is possible to remove a cooperative sort $f^{h,i}$ in the flattened PH:
+\begin{itemize}
+  \item if $\Fop{h} \equiv \top$, then the action $h$ can be modeled in the flattened model by an auto-action
+    (as it is always playable if the target is present);
+  \item if the $i$\textsuperscript{th} conjunction of $\Fop{h}$ consists of only one element $p$,
+    then $h$ can be modeled as a regular action $\PHhit{p}{\target{h}}{\bounce{h}}$ in the flattened PH
+    (as, apart from the target, only one process is required).
+\end{itemize}
+
+\paragraph{Keeping initial cooperations}
+The initial model $\oPH$ may contain cooperative sorts similar than those described in \pref{ssec:hypothesis},
+only hit by a specific class of priorities, which is the highest.
+It is then possible to simplify the translation by keeping these cooperative sorts and ignoring all updating
+actions in the playability properties of the other actions.
+In this way, the meaning of these cooperative actions is kept, and they end up modeled as regular cooperative sorts
+in the flattened model.

### 2014-03-21 parts/example.tex
fix pint url

@@
 The under-approximation presented in this paper has been implemented in the existing Pint
-software\footnote{Pint is freely available at \url{http://process.hitting.free.fr}.}.
+software\footnote{Pint is freely available at \url{http://loicpauleve.name/pint}.}.
 

### 2014-03-25 parts/def-ph.tex
restructuration
simplifications in flattening + begin example
take into account prioritized cooperative sorts in flattening + adapt citeria

@@
 \label{def:ph}
-  If $k \in \sN^*$, a \emph{Process Hitting with $k$ classes of priorities} is a triplet $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$,
+  If $k \in \sNN$, a \emph{Process Hitting with $k$ classes of priorities} is a triplet $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$,
   where $\PHa^{\langle k \rangle} = (\PHa^{(1)}; \dots; \PHa^{(k)})$ is a $k$-tuple and:
@@
 
+\pref{def:substate} defines the notion of sub-state on a set of sorts,
+that is used to consider the interesting part of a complete state.
+\begin{definition}[Sub-states ($\PHsublize{\PHl}$)]
+\label{def:substate}
+  If $S \subset \PHs$ is a set of sorts, a sub-set on $S$ is an element of:
+  $\PHsubl[\PHl]_S \DEF \{ \mysigma \in \bigtimes{a \in S} \PHl_a \}$.
+  The set of all sub-sets is:
+  $\PHsubl[\PHl] \DEF \bigcup_{S \subset \PHs} \PHsubl[\PHl]_S$.
+
+  \noindent
+  Furthermore, if $\mysigma \in \PHsubl[\PHl]$ and $s \in \PHl$, we note:
+    \[\mysigma \subseteq s \EQDEF \forall a_i \in \Proc, a_i \in \mysigma \Rightarrow a_i \in s \enspace.\]
+\end{definition}
+We note that a state is \textit{a fortiori} a sub-state: $\PHl \subset \PHsubl[\PHl]$.
+
 In \pref{def:restriction}, we define the $n$-reduction of a given PH as the PH with $n$ classes of priorities in which only actions of priority lower or equal to $n$ are considered.
@@
   \centering
-  \scalebox{1.5}{
+  \scalebox{1.4}{
   \begin{tikzpicture}
@@
 
-%\todo{Nouvelle section pour les hypothèses + conséquences ?}
+\todo{Nouvelle section pour les hypothèses + conséquences ?}
 \subsection{Restrictions}
@@
 
-In the scope of this paper, we focus on a specific class of PH models.
-We define here the restrictions that lead to this class of models and show that they are equivalent to discrete networks.
+In the scope of this paper, we focus on a specific class of PH models
+in which actions of $\PHh^{(1)}$ are called \emph{prioritized actions} and allow to model non-biological actions.
+%and show that they are equivalent to discrete networks.
+We consider in this section a PH model with $k$ classes of priorities: $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$, with $k \in \sNN$
+and we define here the restrictions that lead to this class of models.
 
-\pref{cr:2prio} allows to distinguish two kinds of actions:
-\emph{unprioritised actions} modelling the non-determinacy of biological evolutions
-and \emph{prioritised actions} used to model non-biological behaviours in the model, namely the update of cooperative sorts.
+%\pref{cr:2prio} allows to distinguish two kinds of actions:
+%\emph{unprioritised actions} modelling the non-determinacy of biological evolutions
+%and \emph{prioritised actions} used to model non-biological behaviours in the model, namely the update of cooperative sorts.
 \pref{cr:bounded} states that the dynamics of the studied model $\PH$ contains no infinite sequence of prioritised actions.
@@
 \todo{Change “Criterion” to something else?}
-\begin{criterion}[2 classes of priorities]
-\label{cr:2prio}
-  In this paper, we only consider Process Hitting with $2$ classes of priorities:
-  $\PH = (\PHs; \PHl; \PHa^{\langle 2 \rangle})$.
-\end{criterion}
+%\begin{criterion}[2 classes of priorities]
+%\label{cr:2prio}
+%  In this paper, we only consider Process Hitting with $2$ classes of priorities:
+%  $\PH = (\PHs; \PHl; \PHa^{\langle 2 \rangle})$.
+%\end{criterion}
 %
@@
   \begin{align*}
-    \forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) = 2 \enspace.
+    \forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) \geq 2 \enspace.
   \end{align*}
@@
 The set of neighbouring actions $\Vh(a)$ of $a$ is the set of prioritised actions influencing $a$.
-These definitions are permitted by the previous restrictions (\pref{cr:2prio} and~\ref{cr:cyclefreeness}).
+These definitions are permitted by \pref{cr:cyclefreeness}.
 \begin{definition}[$\Vs : \PHs \rightarrow \powerset(\PHsort)$; $\Vh : \PHs \rightarrow \powerset(\PHh)$]
@@
 in a way that its local steady-states efficiently represent all configurations of its neighbouring sorts.
-\begin{definition}[$\pfp : \PHs \rightarrow \powerset(\PHproc)$]
+\begin{definition}[$\pfp : \PHl \times \PHs \rightarrow \powerset(\PHproc)$]
 \label{def:pfp}
-  For all $a \in \PHs$,
+  For all $s \in \PHl$ and $a \in \PHs$,
   \begin{align*}
@@
   If $a \in \cs$ and $a_i \in \PHl_a$, we define:
-  $$\csState(a_i) = \{ ps \in \underset{b \in \Vs(a)}{\times} \PHl_b \mid \forall s \in \PHl, \pfp_{s \Cap ps}(a) = a_i \}$$
+  $$\csState(a_i) = \{ ps \in \PHsubl[\PHl]_{\Vs(a)} \mid \forall s \in \PHl, \pfp_{s \Cap ps}(a) = a_i \}$$
+%  $$\csState(a_i) = \{ ps \in \underset{b \in \Vs(a)}{\times} \PHl_b \mid \forall s \in \PHl, \pfp_{s \Cap ps}(a) = a_i \}$$
 \end{definition}
@@
 or, more generally, to the multivalued version of this framework, called Asynchronous Discrete Networks (ADN).
-A translation of ADN into PH is given in \pref{suppl:demotrad}, alongside with a demonstration of the weak bisimulation.
+A translation of ADN into PH and its correction are given in \pref{sec:dn}.
 
@@
 
-In this subsection, we give several general theorems that can be derived from the restrictions of \pref{ssec:hypothesis},
-and which will help building the static analysis of \pref{sec:sa}.
+In this subsection, we give several general theorems that can be derived from the restrictions of \pref{ssec:hypothesis}, %(\pref{cr:bounded}, \ref{cr:cyclefreeness} \& \ref{cr:compcs})
+in the special case of a PH model with $2$ classes of priorities $\PH = (\PHs; \PHl; \PHa^{\langle 2 \rangle})$.
+These results will help building the static analysis of \pref{sec:sa}.
 
@@
   \end{align*}
+\todo{Extend to $s \in \PHsubl[\PHl]$ to use it in $\PHflat$?}
 \end{definition}
@@
 if $\PHget{s}{a} = a_i$ and $\PHget{s}{b} = b_j$, then
-$h$ can always be played after a series of hits (and these hits do not prevent it to be fired).
+$h$ can always be played after a series of prioritised hits (and these hits do not prevent it to be fired).
 \pref{th:hcscomp} states the same if $a$ is a cooperative sort, under the condition that $a$ is updated in $s$.

### 2014-03-25 parts/example.tex
take into account prioritized cooperative sorts in flattening + adapt citeria

@@
   It contains $2$ classes of priority, and prioritized actions are only used to update cooperative sorts.
-  The simplifications mentioned at the end of \pref{ssec:flattening} have been applied:
-  \begin{itemize}
-    \item The auto-action $h_1 = \PHhit{c_1}{c_1}{c_0}$ in $\oPH$ has been flattened to a regular action $\PHhit{a_0}{c_1}{c_0}$
+  Note that according to the simplifications mentioned at the end of \pref{ssec:flattening},
+  the auto-action $h_1 = \PHhit{c_1}{c_1}{c_0}$ in $\oPH$ has been flattened to a regular action $\PHhit{a_0}{c_1}{c_0}$
   because its playability property could be simplified to $\Fop{h_1} \equiv c_1 \wedge a_0 \equiv a_0$.
-    \item The existing cooperative sort $fc$ was kept as in $\oPH$ to avoid an exploding complexity due to
-      the numerous updating actions in $\ov{\PHh}^{(1)}$.
-  \end{itemize}
 

### 2014-03-25 parts/models-ph-dn.tex
take into account prioritized cooperative sorts in flattening + adapt citeria

@@
 We exhibit an encoding of Asynchronous Discrete Networks (ADN) with the Process
-Hitting using two classes of priorities, and prove a weak bisimulation relation.
+Hitting using two classes of priorities
+that respects all Criteria of \pref{ssec:hypothesis},
+and prove a weak bisimulation relation.
+
+\todo{Prove that $\toPH\DNdef$ respects all Criteria!}
 

### 2014-03-25 parts/models-ph-php.tex
take into account prioritized cooperative sorts in flattening + adapt citeria

@@
 
+The aim of this section is to propose a translation of any Process Hitting model
+into a PH model with $2$ classes of priorities
+which is weakkly bisimilar
+and that respects all Criteria of \pref{ssec:hypothesis}.
+
+\todo{Prove that $\PHflat(\oPH)$ respects all Criteria!}
+
 Consider a PH with $k \in \sN^*$ classes of priories:
 $\ov{\PH} = (\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}})$.
+that respects all Criteria given in \pref{ssec:hypothesis}.
 We want to translate it to a PH with $2$ classes of priorities
@@
 
-\begin{definition}[Sub-states ($\PHsubl$)]
-  If $S \subset \ov{\PHs}$ is a set of sorts, a sub-set on $S$ is an element of:
-  $\PHsubl_S \DEF \{ \mysigma \in \bigtimes{a \in S} \ov{\PHl}_a \}$.
-  The set of all sub-sets is:
-  $\PHsubl \DEF \bigcup_{S \subset \ov{\PHs}} \PHsubl_S$.
-
-  \noindent
-  Furthermore, if $\mysigma \in \PHsubl$ and $s \in \ov{\PHl}$, we note:
-    \[\mysigma \subseteq s \EQDEF \forall a_i \in \Proc, a_i \in \mysigma \Rightarrow a_i \in s \enspace.\]
-\end{definition}
-
-We note that a state is \textit{a fortiori} a sub-state: $\ov{\PHl} \subset \PHsubl$.
+Note that it is possible to apply this method to any PH model $\ov{\PH}$ that may not respect the aforementioned Criteria.
+It is then sufficient to instead consider the PH model with $k+1$ classes of priorities
+$\ov{\PH}' = (\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k+1}})$
+where $\PHh^{(1)} = \emptyset$.
 
@@
 \begin{definition}[Playability property of an action ($\Fopsymbol : \PHh \rightarrow \F$)]\label{def:fop}
-  $$\forall h \in \ov{\PHh}, \Fop{h} \equiv \hitter{h} \wedge
+  \[\forall h \in \ov{\PHh}, \Fop{h} \equiv \virtualhitters{h} \wedge
     \left( \bigwedge_{\substack{g \in \PHh^{(n)}\\n < \prio(h)}}
-    \neg \left( \target{g} \wedge \hitter{g}\right) \right)$$
+    \neg \left( \target{g} \wedge \hitter{g}\right) \right)\]
+  where $\forall h \in \ov{\PHh} \setminus \ov{\PHh}^{(1)}$ so that $\hitter{h} = a_i$,
+  \[\virtualhitters(h) =
+    \begin{cases}
+      a_i & \text{if } a \in \components \\
+      \bigvee_{ps \in \csState(a_i)} \left( \bigwedge_{p \in ps} p \right) & \text{if } a \in \cs
+    \end{cases}\]
 \end{definition}
@@
     \item $\PHh^{(2)}=\{ \PHhit{f^{h,i}_\mysigma}{\target{h}}{\bounce{h}} \mid
-      h \in \ov{\PHh} \wedge 
+      h \in \ov{\PHh} \setminus \ov{\PHh}^{(1)} \wedge
       f^{h,i} \in \PHs_f \wedge
@@
 
-\paragraph{Additional properties}
+\paragraph{Playability properties simplifications}
 It is possible to obtain a flattened PH with the same dynamics
@@
 
-\paragraph{Removal of the resulting cooperative sorts}
+\paragraph{Removal of the unnecessary cooperative sorts}
 There are two cases where it is possible to remove a cooperative sort $f^{h,i}$ in the flattened PH:
@@
 \end{itemize}
-
-\paragraph{Keeping initial cooperations}
-The initial model $\oPH$ may contain cooperative sorts similar than those described in \pref{ssec:hypothesis},
-only hit by a specific class of priorities, which is the highest.
-It is then possible to simplify the translation by keeping these cooperative sorts and ignoring all updating
-actions in the playability properties of the other actions.
-In this way, the meaning of these cooperative actions is kept, and they end up modeled as regular cooperative sorts
-in the flattened model.

### 2014-03-25 parts/sa.tex
add new section and TODOs for the TCS extended version
fix appendix references
restructuration
take into account prioritized cooperative sorts in flattening + adapt citeria

@@
 The static analysis presented here is inspired from~\cite{PMR12-MSCS}.
+
+We consider in this section a PH model $\PH = (\PHs; \PHl; \PHa^{\langle 2 \rangle})$ with $2$ classes of priorities
+that respects all Criteria (\ref{cr:bounded}, \ref{cr:cyclefreeness} \& \ref{cr:compcs}) of \pref{ssec:hypothesis}.
 
@@
   If $a \in \components$, the reachability of a process $a_j$ from a process $a_i$ is called an \emph{objective}, noted $\PHobj{a_i}{a_j}$.
-  The set of all objectives is called $\Obj \DEF \{ \PHobj{a_i}{a_j} \mid a \in \components \wedge (a_i, a_j) \in \PHl_a^2 \}$.
+  The set of all objectives is called $\Obj \DEF \{ \PHobj{a_i}{a_j} \mid a \in \components \wedge (a_i, a_j) \in \PHl_a \times \PHl_a \}$.
   For an objective $P = \PHobj{a_i}{a_j} \in \Obj$, we define: $\PHsort(P) = a$, $\PHtarget(P)=a_i$, $\PHbounce(P)=a_j$,
@@
 which is derived immediately from the graph of local causality.
-A proof of this theorem is given in Annex~\ref{suppl:demoapproxinf}.
+A proof of this theorem is given in \pref{suppl:demoapproxinf}.
 \begin{definition}[Coherent edge]
@@
 It is also possible to compute the reachability of a set of states $S \subseteq \PHl$ by creating several actions $\PHhit{\total_s}{\reach_0}{\reach_1}$ in $\PHh^{(2)}$ for each state $s \in S$.
+
+\subsection{Sequential reachability}
+
+\todo{Loic? Maxime?}

### 2014-03-26 parts/sa.tex
debut sequencial reachability

@@
+% vi:spell spelllang=en:
 \section{Static Analysis}\label{sec:sa}
@@
 
-The semantics of PH with $2$ classes of priorities studied in this paper allows to model cooperative sorts accurately representing a coherent configuration of a set of sorts.
-Therefore, we can derive a new method to conclude about the reachability of a state (considering only components).
+The reachability property studied so far concern a single process, \ie{} the
+local state of a single component.
+However, we remark that the reachability of a partial or global state can be
+addressed with the very same analysis by introducing a dedicated cooperative
+sort in the scope of the PH semantics with $2$ classes of priorities.
+
 Indeed, let $\PH = (\PHs, \PHl, (\PHh^{(1)}, \PHh^{(2)}))$ be a PH and suppose that we want to study the reachability of a state $s \in \PHl$.
@@
 
-\todo{Loic? Maxime?}
+The sufficient condition for the reachability of a process from a given context
+can be extended for the successive reachability of several processes ($a_i$,
+then $b_j$, etc.) in the following manner.
+
+\todo{}
+
+\begin{definition}
+\label{def:lastprocs}
+\end{definition}
+
+\begin{theorem}[Sequential under-approximation]
+\label{thm:ordered-ua}
+Given a context $\ctx$ and an objective sequence $\w =
+P\concat\w'\in\OS$,
+$\uconcr(P)\neq\emptyset \wedge
+	\muconcr_{\ctx'}(\w')\neq\emptyset
+	\Longrightarrow \uconcr(\w)\neq\emptyset$,
+where $\ctx' = \procs(\mycwB{\ctx}{P})\Cap\lastprocs(P)$
+\end{theorem}

### 2014-03-26 parts/def-ph.tex
minor updates

@@
   If $S \subset \PHs$ is a set of sorts, a sub-set on $S$ is an element of:
-  $\PHsubl[\PHl]_S \DEF \{ \mysigma \in \bigtimes{a \in S} \PHl_a \}$.
+  $\PHsubl[\PHl]_S \DEF \bigtimes{a \in S} \PHl_a$.
   The set of all sub-sets is:
-  $\PHsubl[\PHl] \DEF \bigcup_{S \subset \PHs} \PHsubl[\PHl]_S$.
+  $\PHsubl[\PHl] \DEF \bigcup_{S \in\powerset(\PHs)} \PHsubl[\PHl]_S$.
 
@@
 In \pref{def:component} we define a well-formed component as a sort that is hit only by unprioritised actions, or that no action hits.
-\begin{definition}[Well-formed component ($\components$)]
+\begin{definition}[Well-formed component]
 \label{def:component}
   A sort $a \in \PHs$ is a \emph{well-formed component} if and only if:
-  \begin{align*}
-    \forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) \geq 2 \enspace.
-  \end{align*}
-  We call $\components$ the set of well-formed components.
+    $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) \geq 2$ \enspace.
+  We denote $\components\subset\Sigma$ the set of well-formed components.
 \end{definition}

### 2014-03-27 parts/sa.tex
sequential under-approximation

@@
 
-The reachability property studied so far concern a single process, \ie{} the
-local state of a single component.
+The reachability property studied so far concern a single process at a time.
 However, we remark that the reachability of a partial or global state can be
@@
 
-\subsection{Sequential reachability}
+\subsection{Sequential under-approximation}
 
-The sufficient condition for the reachability of a process from a given context
-can be extended for the successive reachability of several processes ($a_i$,
-then $b_j$, etc.) in the following manner.
+In this section, we briefly explain an alternative sufficient condition that
+progressively takes into account the successive objectives, instead of
+considering all of them at a time, as it is done in the previous sections.
+Because objectives are taken into account individually, such an approach
+considers only a subset of scenarios.
+However, because each iteration focuses on a smaller part of the network, this
+sequential under-approximation may be more conclusive.
 
-\todo{}
+Let us define a sequence of objective $\w=\obj{a_i}{a_j}\concat\w'$ with
+$a_i\neq a_j$ and a state $s\in L$ with $\get{s}{a}=a_i$.
+One can remark that any scenario reaching $a_j$ necessarily includes one of the
+bounce sequence in $\BS(\obj{a_i}{a_j})$, and in particular,
+any minimal scenario reaching $a_j$ ends in a state where $a_j$ is present but
+also the hitter of the last of one bounce sequence in $\BS(\obj{a_i}{a_j})$.
+If such hitter $b_k$ is in a cooperative sort $b\in\cs$, it also means that one of the sub-state
+in $\csState(b_k)$.
+\pref{def:lastprocs} defines $\lastprocs(\obj{a_i}{a_j})$ as the set of set of
+processes that may be present just after reaching $a_j$.
 
-\begin{definition}
+From \pref{th:approxinf}, we can deduce that
+for any scenario $\delta$ in $\uconcr(P)$,
+there exists a set of processes $ps\in\lastprocs(P)$
+such that $ps \subset (s\play\delta)$.
+Hence, if $\muconcr_{\ctx'\Cap ps}(\w')\neq\emptyset$,
+with $\ctx'=\ctx\Cap\procs(\mycwB{\ctx}{P})$,
+there exists a scenario $\delta'$ concretizing $\w'$ from the
+state $(s\play\delta)$.
+Therefore, the scenario $\delta\concat\delta'$ concretizes
+$\w$.
+
+\begin{definition}[$\lastprocs$]
 \label{def:lastprocs}
+Given an objective $\obj{a_i}{a_j}$, $\lastprocs:
+\Obj\to\powerset(\powerset(\Proc))$ is
+defined such that, $\forall lps\in\lastprocs(\obj{a_i}{a_j})$, 
+$lps\in\powerset(\Proc)$,
+\begin{enumerate}
+\item $\{\hitter{\zeta_{\card\zeta}}\} \subset lps$;
+\item $\forall b_j\in lps, b\in\cs, \exists ps\in\csState(b_j): ps\subset lps$;
+\item $\forall b_j\in lps, b\in\cs, 
+		\forall ps\in\csState(b_j),
+			\exists lps'\in\lastprocs(\obj{a_i}{a_j}),
+				ps\subset lps'$;
+\item $\nexists lps'\in\lastprocs(\obj{a_i}{a_j}): lps'\subset lps \wedge
+									lps'\neq lps$.
+\end{enumerate}
 \end{definition}
@@
 $\uconcr(P)\neq\emptyset \wedge
-	\muconcr_{\ctx'}(\w')\neq\emptyset
+	\forall ps \in\lastprocs(P),
+	\muconcr_{\ctx'\Cap ps}(\w')\neq\emptyset
 	\Longrightarrow \uconcr(\w)\neq\emptyset$,
-where $\ctx' = \procs(\mycwB{\ctx}{P})\Cap\lastprocs(P)$
+where $\ctx' = \ctx\Cap\procs(\mycwB{\ctx}{P})$.
 \end{theorem}
+\begin{proof}
+If $\uconcr(P)\neq\emptyset$,
+for all $s\in L, s\subset\ctx$,
+there exists a scenario $\delta\in\uconcr(P)\cap\Sce(s)$;
+from \pref{def:lastprocs} and proof of \pref{th:approxinf},
+$\exists ps\in\lastprocs(P)$ such that
+$(s\play\delta)\subset\ctx'\Cap ps$.
+Hence, if $\muconcr_{\ctx'\Cap ps}(\w')\neq\emptyset$,
+there exists a scenario $\delta'\in\muconcr_{\ctx'\Cap ps}(\w')$ such that
+$\delta'\in\Sce(s\play\delta)$.
+Hence, $\delta\concat\delta'$ is a scenario playable in $s$.
+Therefore, for all $s\in L, s\subset\ctx$, there exists a scenario
+concretizing $\w$.
+Hence, $\uconcr(\w)\neq\emptyset$.
+\end{proof}

### 2014-03-27 parts/def-ph.tex
simplification section 2

@@
 
-%\todo{Mieux replacer le PH dans un contexte biologique (catalytic networks, metabolic networks)}
-
 \begin{example}
@@
 
-\begin{figure}[ht]
+\begin{figure}[tb]
   \centering
-  \scalebox{1.4}{
+  \scalebox{1.2}{
   \begin{tikzpicture}
@@
   \label{fig:ph-livelock}
+  	\todo{(Loic) mettre la sorte coopérative horizontale pour mieux voir les
+	frappes}
     An example of PH with $2$ classes of priorities.
@@
 
-\todo{Nouvelle section pour les hypothèses + conséquences ?}
 \subsection{Restrictions}
@@
 which would allow the play of an infinite sequence of prioritised actions in “zero time”.
-\todo{Change “Criterion” to something else?}
-%\begin{criterion}[2 classes of priorities]
+As a consequence, the set $\restriction{\Sce}{1}$ is finite.
+%\begin{condition}[2 classes of priorities]
 %\label{cr:2prio}
@@
 %  $\PH = (\PHs; \PHl; \PHa^{\langle 2 \rangle})$.
-%\end{criterion}
+%\end{condition}
 %
-\begin{criterion}[Bounded termination]
+\begin{condition}[Bounded termination]
 \label{cr:bounded}
@@
   $\exists N \in \sN, \forall s \in \PHl, \forall \delta \in \restriction{\Sce}{1}(s), |\delta| \leq N$.
-\end{criterion}
+\end{condition}
 
-In \pref{def:component} we define a well-formed component as a sort that is hit only by unprioritised actions, or that no action hits.
-\begin{definition}[Well-formed component]
-\label{def:component}
-  A sort $a \in \PHs$ is a \emph{well-formed component} if and only if:
-    $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) \geq 2$ \enspace.
-  We denote $\components\subset\Sigma$ the set of well-formed components.
-\end{definition}
+Given a sort $a\in\Sigma$ and a state $s\in L$, 
+we denote $\pfp_s(a)$ (\pref{def:pfp}) the processes of sort $a$ that can be present after
+playing all actions of priority $1$,
+which is always defined because of \pref{cr:bounded}.
 
-\pref{def:chainsactions} defines chains of prioritised actions,
-and \pref{cr:cyclefreeness} prevents the presence of cycles in these chains.
-\begin{definition}
-\label{def:chainsactions}
-  The set of chains of actions $\PHh(a, b)$ between two sorts $a, b \in \PHs$ is defined as below:
-  \begin{align*}
-  \PHh(a, b) = \{ (h_i)_{i \in \segm{1}{s+1}} &\in (\PHh^{(1)})^{s+1} \mid s \in \sN \\
-    & \wedge \PHsort(\PHhitter(h_1)) = a \wedge \PHsort(\PHtarget(h_{s+1})) = b \\
-    & \wedge \forall i \in \segm{1}{s}, \PHsort(\PHtarget(h_{i})) = \PHsort(\PHhitter(h_{i+1})) \}
-  \end{align*}
-  where $(\PHh^{(1)})^{s+1}$ is the Cartesian product of $s+1$ times the set $\PHh^{(1)}$.
-\end{definition}
-%
-\begin{criterion}[Cycle-freeness in prioritised actions]
-\label{cr:cyclefreeness}
-  There is no cycles in chains of actions:
-  $\forall a \in \PHs, \PHh(a, a) = \emptyset$.
-\end{criterion}
-
-In \pref{def:neighbours} we define the notion of neighbouring sorts and actions of a given sort.
-The set of neighbouring sorts $\Vs(a)$ of a sort $a$ is the set of components that can interact with it through prioritised actions.
-The set of neighbouring actions $\Vh(a)$ of $a$ is the set of prioritised actions influencing $a$.
-These definitions are permitted by \pref{cr:cyclefreeness}.
-\begin{definition}[$\Vs : \PHs \rightarrow \powerset(\PHsort)$; $\Vh : \PHs \rightarrow \powerset(\PHh)$]
-\label{def:neighbours}
-  For all sort $a \in \PHs$,
-  \begin{align*}
-    \Vs(a) &= \{ b \in \components \mid \PHh(b, a) \neq \emptyset \}\\
-    \Vh(a) &= \{ h \in \PHh^{(1)} \mid \exists b \in \Vs(a), \exists hs \in \PHh(b,a), h \in hs \}
-  \end{align*}
-\end{definition}
-
-Finally, we introduce the notion of local steady-state of a sort from a given state.
-This local steady-state is the set of processes towards which the sort tends to evolve to, and stay in, when playing only prioritised actions.
-We denote $\pfp_s(a)$ this set of processes for a sort $a$ in state $s$ (\pref{def:pfp}),
-and we derive from this the notion of well-formed cooperative sort (\pref{def:cs}).
-A well-formed cooperative sort models a cooperation between sorts as presented in \pref{ssec:cooperation};
-therefore, it must be only hit by prioritised actions,
-in a way that its local steady-states efficiently represent all configurations of its neighbouring sorts.
 \begin{definition}[$\pfp : \PHl \times \PHs \rightarrow \powerset(\PHproc)$]
@@
   \begin{align*}
-    \pfp_s(a) = \{ a_i \in \PHl_a &\mid \exists \delta \in \restriction{\Sce}{1}(s), \PHget{(s \PHplay \delta)}{a} = a_i \\
-    & \quad \wedge \forall \PHhit{b_i}{c_j}{c_k} \in \Vh(a), \PHget{(s \PHplay \delta)}{b} \neq b_i \vee \PHget{(s \PHplay \delta)}{c} \neq c_j \}
+    \pfp_s(a) = \{ \get{(s\play\delta)}{a} \in \PHl_a &\mid \delta \in \restriction{\Sce}{1}(s)
+					\wedge\nexists h\in\PHh^{(1)}, (\delta; h) \in\restriction{\Sce}{1}(s) \}
   \end{align*}
-  Of course, if $a \in \components$, then $\pfp_s(a) = \{ \PHget{s}{a} \}$.
 \end{definition}
-%
+
+Our second condition (\pref{cr:compcs}) imposes that any sort in the Process
+Hitting is either a well-formed component (\pref{def:component}) or a well-formed cooperative sort
+(\pref{def:cs}).
+The former is a sort that is hit only by actions with priority greater than $2$.
+The latter is a sort that is hit only by actions with priority $1$ and which
+always converge to the same process with respect to the state of the components
+that have an influence on it (\pref{def:conn}).
+We note $\components\subset\Sigma$ the set of well-formed components,
+and $\cs\subset\Sigma$ the set of well-formed cooperative sorts.
+
+\begin{definition}[Well-formed component ($\components$)]
+\label{def:component}
+A sort $a \in \PHs$ is a \emph{well-formed component} if and only if:
+    $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) \geq 2$ \enspace.
+\end{definition}
+
+\begin{definition}[Components influence $(\compin: \PHs\to\powerset(\components))$]
+\label{def:conn}
+Given a sort $a$, $\compin(a)\DEF \conn(a)\cap\components$ where
+$\conn(a)$ is the smallest set of sorts satisfying the following properties:
+\begin{align*}
+a\in\conn(a) &
+\\
+\forall h\in  \PHh^{(1)},
+	\Sigma(\target{h})\in\conn(a) & \Longrightarrow \Sigma(\hitter{h})\in\conn(a)
+\end{align*}
+\end{definition}
+
 \begin{definition}[Well-formed cooperative sorts ($\cs$)]
@@
 \begin{enumerate}[(i)]
-    \item $\exists b \in \PHs, \PHh(b, a) \neq \emptyset$
-    \item \label{csai} $\forall s \in \PHl, \exists a_i \in \PHl_a, \pfp_s(a) = \{ a_i \}$
-    \item \label{css} $\forall a_i \in \PHl_a, \exists s \in \PHl, \pfp_s(a) = \{ a_i \}$
+\item $\forall h\in\PHh, \Sigma(\PHtarget(h))=a \Longrightarrow \prio(h) = 1$;
+\item\label{csai} $\forall s\in\PHl, \card{\pfp_s(a)} = 1$;
+\item\label{css} $\forall a_i \in \PHl_a, \exists s \in \PHl, a_i\in\pfp_s(a)$;
+\item $\forall \sigma\in\PHsubl[\PHl]_{\compin(a)},
+			\forall s,s'\in\PHl,
+				\sigma\subseteq s\wedge \sigma\subseteq s'\Rightarrow 
+							\pfp_s(a) = \pfp_{s'}(a)$\enspace.
 \end{enumerate}
-  We call $\cs$ the set of well-formed cooperative sorts.
 \end{definition}
+
+\begin{condition}[Components \& cooperative sorts partition]
+\label{cr:compcs}
+  $$\PHs = \components \cup \cs \wedge \components \cap \cs = \emptyset$$
+\end{condition}
 
@@
 \label{def:csState}
-  If $a \in \cs$ and $a_i \in \PHl_a$, we define:
-  $$\csState(a_i) = \{ ps \in \PHsubl[\PHl]_{\Vs(a)} \mid \forall s \in \PHl, \pfp_{s \Cap ps}(a) = a_i \}$$
-%  $$\csState(a_i) = \{ ps \in \underset{b \in \Vs(a)}{\times} \PHl_b \mid \forall s \in \PHl, \pfp_{s \Cap ps}(a) = a_i \}$$
+  If $a \in \cs$ and $a_i \in \PHl_a$, 
+  $$\csState(a_i) \DEF \{ \toset{ps} \mid ps\in\PHsubl[\PHl]_{\compin(a)} \wedge
+  							\exists s\in\PHl, (ps\subset s\wedge \pfp_s(a)=a_i)
+							\}$$
 \end{definition}
@@
 In the following we simply write “component” (\resp “cooperative sort”) instead of “well-formed component” (\resp “well-formed cooperative sort”).
-Finally, \pref{cr:compcs} states that the set of sorts of the considered PH must be divided between components and cooperative sorts.
-\begin{criterion}[Components \& cooperative sorts partition]
-\label{cr:compcs}
-  $$\PHs = \components \cup \cs \wedge \components \cap \cs = \emptyset$$
-\end{criterion}
 
@@
 \end{example}
-
-The criteria given in this subsection allow to define a class of PH models that is (weakly) bisimilar to Asynchronous Boolean Networks
-or, more generally, to the multivalued version of this framework, called Asynchronous Discrete Networks (ADN).
-A translation of ADN into PH and its correction are given in \pref{sec:dn}.
 
@@
   \end{align*}
-\todo{Extend to $s \in \PHsubl[\PHl]$ to use it in $\PHflat$?}
 \end{definition}
@@
 %
-\newproof{proofupdate}{Proof of \pref{th:update}}
-\begin{proofupdate}
+\begin{proof}
   Let $a$ be a cooperative sort so that $\PHget{s}{a} \neq \pfp_s(a)$.
@@
   $\forall \delta' \in \restriction{\Sce}{1}(s \PHplay \delta)$, $\PHget{(s \PHplay \delta \PHplay \delta')}{a} = \pfp_s(a)$.
-  As there is no cycle of actions between the cooperative sorts (\pref{cr:cyclefreeness}) and given that an updated cooperative sort cannot evolve, at most $|\cs|$ updates have to be performed.
-\end{proofupdate}
+\end{proof}
 
@@
 %
-\newproof{proofhcompcomp}{Proof of \pref{th:hcompcomp}}
-\begin{proofhcompcomp}
+\begin{proof}
   From \pref{th:update}, there exists a scenario $\delta$ with: $(s \PHplay \delta) = \update(s)$.
@@
   Finally, by definition of $\update(s)$, no prioritised action can be played in $(s \PHplay \delta)$, thus $h$ can be played in $(s \PHplay \delta)$.
-\end{proofhcompcomp}
+\end{proof}
 %
@@
 \end{theorem}
-%
-\newproof{proofhcscomp}{Proof of \pref{th:hcscomp}}
-\begin{proofhcscomp}
+\begin{proof}
   Similar to the proof of \pref{th:hcompcomp};
   as $a_i \in \pfp_s(a)$, $a_i \in (s \PHplay \delta)$.
-\end{proofhcscomp}
+\end{proof}

### 2014-03-27 parts/sa.tex
simplification section 2

@@
 We consider in this section a PH model $\PH = (\PHs; \PHl; \PHa^{\langle 2 \rangle})$ with $2$ classes of priorities
-that respects all Criteria (\ref{cr:bounded}, \ref{cr:cyclefreeness} \& \ref{cr:compcs}) of \pref{ssec:hypothesis}.
+that respects all conditions (\ref{cr:bounded} \& \ref{cr:compcs}) of \pref{ssec:hypothesis}.
 
@@
   then \pref{th:approxinf} concludes that $c_1$ is reachable from $\ctx$.
-\end{example}
 
-\begin{figure}[ht]
+\begin{figure}[tp]
   \centering
@@
 \end{figure}
+\end{example}
 

### 2014-03-27 parts/def-ph.tex
essai pour rendre la figure plus lisible
lemmes

@@
 Finally, in order to perform a static analysis adapted to this new semantics, we give several criteria to restrict the class of models that we can study,
-and give several theorems that follow.
+and give several lemmas that follow.
 This class of models is equivalent to Asynchronous Discrete Networks.
@@
     \TSort{(0,4)}{b}{2}{l}
-    \TSort{(6,2)}{c}{2}{r}
+    \TSort{(7,2.5)}{c}{2}{r}
 
@@
     \TSetTick{ab}{3}{11}
-    \TSort{(3,1)}{ab}{4}{r}
+    \TSort{(2,2.5)}{ab}{4}{t}
 
-    \THit{a_0}{prio}{ab_3}{.west}{ab_1}
-    \THit{a_0}{prio}{ab_2}{.west}{ab_0}
-    \THit{a_1}{prio}{ab_1}{.west}{ab_3}
-    \THit{a_1}{prio}{ab_0}{.west}{ab_2}
+    \THit{a_0}{prio}{ab_3}{.south}{ab_1}
+    \THit{a_0}{prio}{ab_2}{.south}{ab_0}
+    \THit{a_1}{prio}{ab_1}{.south}{ab_3}
+    \THit{a_1}{prio}{ab_0}{.south}{ab_2}
 
-    \THit{b_0}{prio}{ab_3}{.west}{ab_2}
-    \THit{b_0}{prio}{ab_1}{.west}{ab_0}
-    \THit{b_1}{prio}{ab_2}{.west}{ab_3}
-    \THit{b_1}{prio}{ab_0}{.west}{ab_1}
+    \THit{b_0}{prio}{ab_3}{.north}{ab_2}
+    \THit{b_0}{prio}{ab_1}{.north}{ab_0}
+    \THit{b_1}{prio}{ab_2}{.north}{ab_3}
+    \THit{b_1}{prio}{ab_0}{.north}{ab_1}
 
@@
     \THit{b_1}{selfhit}{b_1}{.west}{b_0}
-    \THit{a_0}{bend left}{b_0}{.south west}{b_1}
-    \THit{b_0}{bend right=60}{a_0}{.west}{a_1}
+    \THit{a_0.north}{bend left}{b_0}{.west}{b_1}
+    \THit{b_0.south}{bend right=60}{a_0}{.west}{a_1}
 
@@
 
-    \path[bounce, bend right]
-      \TBounce{ab_3}{}{ab_1}{.north west}
-      \TBounce{ab_2}{}{ab_0}{.north west}
-      \TBounce{ab_3}{}{ab_2}{.north west}
-      \TBounce{ab_1}{}{ab_0}{.north west}
+	\path[bounce, bend right=55]
+      \TBounce{ab_0}{}{ab_2}{.west}
+      \TBounce{ab_1}{}{ab_3}{.west}
 	;
-    \path[bounce, bend left]
-      \TBounce{ab_1}{}{ab_3}{.south west}
-      \TBounce{ab_0}{}{ab_2}{.south west}
-      \TBounce{ab_2}{}{ab_3}{.south west}
-      \TBounce{ab_0}{}{ab_1}{.south west}
+	\path[bounce, bend left=20]
+      \TBounce{ab_3}{}{ab_1}{.south east}
+      \TBounce{ab_2}{}{ab_0}{.south east}
+	;
+    \path[bounce, bend right=20]
+      \TBounce{ab_3}{}{ab_2}{.north east}
+      \TBounce{ab_1}{}{ab_0}{.north east}
+    ;
+    \path[bounce, bend left=30]
+      \TBounce{ab_2}{}{ab_3}{.west}
+      \TBounce{ab_0}{}{ab_1}{.west}
     ;
@@
   \label{fig:ph-livelock}
-  	\todo{(Loic) mettre la sorte coopérative horizontale pour mieux voir les
-	frappes}
     An example of PH with $2$ classes of priorities.
@@
 
-In this subsection, we give several general theorems that can be derived from the restrictions of \pref{ssec:hypothesis}, %(\pref{cr:bounded}, \ref{cr:cyclefreeness} \& \ref{cr:compcs})
+In this subsection, we give several general lemmas that can be derived from the restrictions of \pref{ssec:hypothesis}, %(\pref{cr:bounded}, \ref{cr:cyclefreeness} \& \ref{cr:compcs})
 in the special case of a PH model with $2$ classes of priorities $\PH = (\PHs; \PHl; \PHa^{\langle 2 \rangle})$.
@@
 This state is unique due to the properties of $\pfp$ given in the previous subsection.
-Then, \pref{th:update} states that from any state, there exists a scenario updating the cooperative sorts of this state.
+Then, \pref{lem:update} states that from any state, there exists a scenario updating the cooperative sorts of this state.
 %
@@
 %
-\begin{theorem}
-\label{th:update}
+\begin{lemma}
+\label{lem:update}
   $\forall s \in \PHl, \exists \delta \in \restriction{\Sce}{1}(s), s \PHplay \delta = \update(s)$
-\end{theorem}
+\end{lemma}
 %
@@
 
-\pref{th:hcompcomp} states that for a given state $s$, and for any action $h = \PHhit{a_i}{b_j}{b_k}$ where $a$ and $b$ are components,
+\pref{lem:hcompcomp} states that for a given state $s$, and for any action $h = \PHhit{a_i}{b_j}{b_k}$ where $a$ and $b$ are components,
 if $\PHget{s}{a} = a_i$ and $\PHget{s}{b} = b_j$, then
 $h$ can always be played after a series of prioritised hits (and these hits do not prevent it to be fired).
-\pref{th:hcscomp} states the same if $a$ is a cooperative sort, under the condition that $a$ is updated in $s$.
-\begin{theorem}
-\label{th:hcompcomp}
+\pref{lem:hcscomp} states the same if $a$ is a cooperative sort, under the condition that $a$ is updated in $s$.
+\begin{lemma}
+\label{lem:hcompcomp}
   $\forall s \in \PHl, \forall a,b \in \components, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh,$\\
@@
   (s \PHplay \delta) \PHPtrans (s \PHplay \delta \PHplay h))$
-\end{theorem}
+\end{lemma}
 %
 \begin{proof}
-  From \pref{th:update}, there exists a scenario $\delta$ with: $(s \PHplay \delta) = \update(s)$.
+  From \pref{lem:update}, there exists a scenario $\delta$ with: $(s \PHplay \delta) = \update(s)$.
   As $a,b \in \components$, $a_i \in (s \PHplay \delta)$ and $b_j \in (s \PHplay \delta)$.
@@
 %
-\begin{theorem}
-\label{th:hcscomp}
+\begin{lemma}
+\label{lem:hcscomp}
   $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, a \in \cs, b \in \components,$\\
@@
   (s \PHplay \delta) \PHPtrans (s \PHplay \delta \PHplay h))$
-\end{theorem}
+\end{lemma}
 \begin{proof}
-  Similar to the proof of \pref{th:hcompcomp};
+  Similar to the proof of \pref{lem:hcompcomp};
   as $a_i \in \pfp_s(a)$, $a_i \in (s \PHplay \delta)$.

### 2014-03-27 parts/sa.tex
lemmes

@@
 In \pref{def:uconcr}, we define $\uconcr(\w)$ as equal to $\concr(\w)$ if and only if $\concr(\w)$ contains scenarios starting from all states $s \subseteq \ctx$.
-\pref{th:uconcr-ctx} is used to over-approximate the initial context $\ctx$.
+\pref{lem:uconcr-ctx} is used to over-approximate the initial context $\ctx$.
 \begin{definition}[$\uconcr: \OS \rightarrow \powerset(\Sce)$]
@@
 % 
-\begin{theorem}
-\label{th:uconcr-ctx}
+\begin{lemma}
+\label{lem:uconcr-ctx}
   $\ctx \subseteq \ctx' \wedge \muconcr_{\ctx'}(\w) \neq \emptyset \Longrightarrow \muconcr_{\ctx}(\w) \neq \emptyset$.
-\end{theorem}
+\end{lemma}
 
@@
 \label{th:approxinf}
-  If the graph $\cwB$ contains no cycle,
+Given a Process Hitting $(\PHs; \PHl; \PHa^{\langle 2 \rangle})$
+that satisfies \pref{cr:bounded} and \pref{cr:compcs},
+a context $\ctx$ and a sequence of objectives $\w$,
+  if the graph $\cwB$ contains no cycle,
   all objectives have at least one solution

### 2014-03-27 parts/suppl-sa.tex
lemmes

@@
     so that $\forall i \in \segm{1}{n+1}$, $\PHget{(s \PHplay \delta_n \PHplay \delta')}{\PHsort(p_{i})} = p_{i}$.
-    Finally, by \pref{th:update}, there exists a scenario $\delta'' \in \restriction{\Sce}{1}(s \PHplay \delta_n \PHplay \delta')$
+    Finally, by \pref{lem:update}, there exists a scenario $\delta'' \in \restriction{\Sce}{1}(s \PHplay \delta_n \PHplay \delta')$
     so that, if we denote $\delta_{n+1} = \delta_n \PHplay \delta' \PHplay \delta''$,
-    we have: $\update(s \PHplay \delta_n \PHplay \delta') = s \PHplay \delta_{n+1}$ and the same property about processes (by \pref{th:hcscomp}).
+    we have: $\update(s \PHplay \delta_n \PHplay \delta') = s \PHplay
+	\delta_{n+1}$ and the same property about processes (by \pref{lem:hcscomp}).
 \end{itemize}
@@
     or $\forall \zeta \in \BS(P), \zeta \in \Sce(s) \wedge \PHsort(\zeta) = \{ \PHsort(P) \}$
-    and $\delta = \delta_1 \PHplay \zeta_1 \PHplay \dots \PHplay \delta_{|\zeta|} \PHplay \zeta_{|\zeta|}$ is a valid sequence given by \pref{th:hcompcomp}.
+    and $\delta = \delta_1 \PHplay \zeta_1 \PHplay \dots \PHplay
+	\delta_{|\zeta|} \PHplay \zeta_{|\zeta|}$ is a valid sequence given by
+	\pref{lem:hcompcomp}.
 
@@
         By hypothesis there exists $\delta' \in \muconcr_{s \PHplay \delta_n}(\PHobj{\any}{b_i})$ with $\PHsort(P) \notin \PHsort(\delta')$ (by \pref{def:maxCont}).
-        By \pref{th:update} there exists $\delta'' \in \restriction{\Sce}{1}(s \PHplay \delta')$ so that $\update(s \PHplay \delta') = s \PHplay \delta' \PHplay \delta''$.
-        Furthermore, $\PHget{(s \PHplay \delta' \PHplay \delta'')}{b} = b_j$ (by \pref{th:hcompcomp} if $b \in \components$ or \pref{th:hcscomp} if $b \in \cs$).
+        By \pref{lem:update} there exists $\delta'' \in \restriction{\Sce}{1}(s \PHplay \delta')$ so that $\update(s \PHplay \delta') = s \PHplay \delta' \PHplay \delta''$.
+        Furthermore, $\PHget{(s \PHplay \delta' \PHplay \delta'')}{b} = b_j$ (by
+		\pref{lem:hcompcomp} if $b \in \components$ or \pref{lem:hcscomp} if $b \in \cs$).
         Therefore, $\delta_{n+1} = \delta_n \PHplay \delta' \PHplay \delta'' \PHplay \zeta_n$.
@@
 \end{itemize}
-Finally, as $\muconcr_{max\ctx}(\w) \neq \emptyset$, $\uconcr(\w) \neq \emptyset$ (\pref{th:uconcr-ctx}).
+Finally, as $\muconcr_{max\ctx}(\w) \neq \emptyset$, $\uconcr(\w) \neq
+\emptyset$ (\pref{lem:uconcr-ctx}).
 \end{proofapproxinf}

### 2014-03-27 parts/sa.tex
concr definition

@@
   The set of all objectives is called $\Obj \DEF \{ \PHobj{a_i}{a_j} \mid a \in \components \wedge (a_i, a_j) \in \PHl_a \times \PHl_a \}$.
-  For an objective $P = \PHobj{a_i}{a_j} \in \Obj$, we define: $\PHsort(P) = a$, $\PHtarget(P)=a_i$, $\PHbounce(P)=a_j$,
+  For an objective $P = \PHobj{a_i}{a_j} \in \Obj$, we define: $\PHsort(P) \DEF
+  a$, $\PHtarget(P)\DEF a_i$, $\PHbounce(P)\DEF a_j$,
   and $P$ is said \emph{trivial} if $a_i = a_j$.
@@
   the override of $\ctx$ by $ps$ is noted $\ctx \Cap ps$ and is defined by:
-  \[ \forall a \in \PHs, \PHget{(\ctx \Cap ps)}{a} =
+  \[ \forall a \in \PHs, \PHget{(\ctx \Cap ps)}{a} \DEF
   \begin{cases}
@@
   \[
-    \BS(\PHobj{a_i}{a_j}) = \{ \zeta \in \BS \mid \PHtarget(\zeta_1)= a_i \wedge \PHbounce(\zeta_{|\zeta|}) = a_j \} \enspace.
+    \BS(\PHobj{a_i}{a_j}) \DEF \{ \zeta \in \BS \mid \PHtarget(\zeta_1)= a_i \wedge \PHbounce(\zeta_{|\zeta|}) = a_j \} \enspace.
   \]
@@
   \[
-    \aBS(P) = \{ \abstr{\zeta} \in \Sol \mid \zeta \in \BS(P), \nexists \zeta' \in \BS(P), \abstr{\zeta'} \subsetneq \abstr{\zeta} \} \enspace,
+    \aBS(P) \DEF \{ \abstr{\zeta} \in \Sol \mid \zeta \in \BS(P), \nexists \zeta' \in \BS(P), \abstr{\zeta'} \subsetneq \abstr{\zeta} \} \enspace,
   \]
-  where $\abstr{\zeta} = \{ \PHhitter(\zeta_n) \mid  n \in \indexes{\zeta} \wedge \PHsort(\PHhitter(\zeta_n)) \neq \PHsort(P) \}$.
+  where $\abstr{\zeta} \DEF \{ \PHhitter(\zeta_n) \mid  n \in \indexes{\zeta} \wedge \PHsort(\PHhitter(\zeta_n)) \neq \PHsort(P) \}$.
 \end{definition}
@@
 
-We denote $\concr(\w)$ the set of scenarios concretising an objective sequence $\w$ in the context $\ctx$.
+We denote $\concr(\w)$ (\pref{def:concr}) the set of scenarios concretising an objective sequence $\w$ in the context $\ctx$.
 In \pref{def:uconcr}, we define $\uconcr(\w)$ as equal to $\concr(\w)$ if and only if $\concr(\w)$ contains scenarios starting from all states $s \subseteq \ctx$.
 \pref{lem:uconcr-ctx} is used to over-approximate the initial context $\ctx$.
+
+\begin{definition}[$\concr: \OS \to \powerset(\Sce)$]\label{def:concr}
+Given $\w\in\OS$, $\concr(\w)$ is the set of minimal scenarios concretizing $\w$ in the
+context $\ctx$. It is defined as the largest set satisfying the following conditions:
+\begin{enumerate}[(i)]
+\item $\forall\delta\in\concr(\w), \exists s\subseteq\ctx: \delta\in\Sce(s)$
+\item $\forall\delta\in\concr(\w),
+  \exists \phi:\indexes{\w}\to\indexes{\delta},
+    (\forall n,m\in\indexes{\w}, n<m \Leftrightarrow \phi(n)\leq\phi(m)):$
+\\\hspace*{2cm}$\forall n\in\indexes{\w}, \PHbounce(\w_n) \in \ctx\play\delta_{1..\phi(n)}$
+\item $\forall\delta,\delta'\in\concr(\w)
+				\card{\delta}\leq\card{\delta'} \Rightarrow
+					\delta\neq\delta'_{1..\card{\delta}}$.
+\end{enumerate}
+\end{definition}
 \begin{definition}[$\uconcr: \OS \rightarrow \powerset(\Sce)$]
@@
   \[
-  \uconcr(\w) = 
+  \uconcr(\w) \DEF
   \begin{cases}
@@
   \begin{align*}
-    \gCont_\ctx(a,P) = 
+    \gCont_\ctx(a,P) \DEF
     \{ p \in \PHproc &\mid \exists ps \in \aBS(P), \exists b_i \in ps, b = a \wedge p = b_i \\
@@
 \label{def:glc}
-  The graph of local causality $\cwB = (\Bv, \Be)$ is defined as: $\cwB = \lfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs(\myB)}}$,
-  where $\myB = (\cwV, \cwE)$ is the smallest graph with
+  The graph of local causality $\cwB \DEF (\Bv, \Be)$ is defined as: $\cwB \DEF \lfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs(\myB)}}$,
+  where $\myB \DEF (\cwV, \cwE)$ is the smallest graph with
   $\cwV \subseteq \Proc \cup \Obj \cup \Sol$ and $\cwE \subseteq \cwV \times \cwV$

### 2014-03-27 main.tex
take into account prioritized cooperative sorts in flattening + adapt citeria
simplification section 2
lemmes
service minimum pour l'introduction

--- 2014-03-19 main.tex
@@
 \newdefinition{definition}{Definition}
-\newdefinition{criterion}{Criterion}
+\newdefinition{condition}{Condition}
 \newtheorem{theorem}{Theorem}
+\newtheorem{lemma}{Lemma}
 \newproof{example}{Example}
@@
 \newrefformat{suppl}{Appendix~\ref{#1}}
-\newrefformat{cr}{Criterion~\ref{#1}}
+\newrefformat{cr}{Condition~\ref{#1}}
+\newrefformat{crs}{Conditions~\ref{#1}}
 \newrefformat{eq}{Eq.~\eqref{#1}}
@@
 \newcommand{\sN}{\mathbb{N}}
+\newcommand{\sNN}{\mathbb{N}^{**}}
 \def\DEF{\stackrel{\Delta}=}
@@
 \newcommand{\bottom}{\perp}
-\newcommand{\Vs}{V_\PHs}
-\newcommand{\Vh}{V_\PHh}
-\newcommand{\Va}{\Vh}
 \newcommand{\stable}{\mathsf{stable}}
@@
 \begin{keyword}
-qualitative modelling \sep
-model abstraction \sep
-static analysis \sep
-asynchronous network
+discrete networks \sep
+abstract interpretation \sep
+reachability \sep
+qualitative models \sep
+systems biology
 \end{keyword}

### 2014-03-27 parts/intro.tex
add new section and TODOs for the TCS extended version
take into account prioritized cooperative sorts in flattening + adapt citeria
simplification section 2
service minimum pour l'introduction

@@
+% vi:spell spelllang=en:
 \section{Introduction}
@@
 
-In this paper, we introduce a new extension to the semantics of Process Hitting by partitioning actions into classes of priorities.
+This paper is an extension of \cite{FPMR13-CS2Bio} were we
+we introduced a new extension to the semantics of Process Hitting by partitioning actions into classes of priorities
+(\pref{sec:ph}).
 One of the objectives is to reach an accurate representation of cooperating components in the model, that was not fulfilled with the initial semantics.
-We then develop an efficient under-approximation of the reachability of the state of components on a subclass of this new framework, thus allowing to compute efficient static analysis.
+In \pref{sec:sa},
+we develop an efficient under-approximation of the reachability of the state of components on a subclass of this new framework, thus allowing to compute efficient static analysis.
 This local reachability under-approximation can be also easily extended to study the reachability of a global state.
-Finally, as the subclass of models studied proves to be bisimilar to Asynchronous Discrete Networks, we state to have developed an efficient method to compute the reachability of a state and thus study the behaviour of such models.
+Furthermore, we provide a new extended under-approximation method to decide a successive reachability property.
 
-The method developed in this paper has been implemented into the existing Pint library and tested on a large-scale biological model containing 94 components.
+Whereas the analysis presented in \pref{sec:sa} consider a particular class of
+Process Hitting with two classes of priority,
+we provide in \pref{sec:encodings} formal encodings of Asynchronous Discrete Networks and general
+Process Hitting models with priorities.
+Those encodings result in Process Hitting fulfilling the conditions for our
+static analysis and show the broad applicability of our method.
+
+In \pref{sec:example}, after giving an example of the encoding of a biological
+network with multiple priority classes,
+we apply our method on a large-scale biological model containing 94 components.
 The under-approximation turned out to be conclusive in all cases and results were computed in hundredths of seconds,
 thus overtaking the efficiency of usual model-checkers.
-
-Our paper is organised as follows.
-The Process Hitting framework is defined in section 2;
-we introduce static analysis of the Process Hitting in section 3;
-section 4 illustrates the approach on an example
-before the discussion and conclusion in section 5.
 
@@
 The Cartesian product is denoted $\times$.
+If $z$ is a tuple of $n$ components, $\toset{z}$ denotes the corresponding set
+	$\{z_1, \cdots, z_n\}$.

### 2014-03-27 main.tex
service minium pour abstract et conclusion

@@
 \begin{abstract}
-\todo{Add flattening}
 The Process Hitting is a recently introduced framework designed for the modelling of concurrent systems.
@@
 In this paper, we focus on a restriction of the Process Hitting with two classes of priorities and a specific behaviour of the components, that is sufficient to tackle the aforementioned problem of cooperations.
-We show that this class of Process Hitting models allows to represent any Asynchronous Discrete Networks, either Boolean or multivalued.
+We show that this class of Process Hitting models allows to represent any
+Asynchronous Discrete Networks, either Boolean or multivalued; and also any
+Process Hitting model with arbirtrary number of priorty classes.
 Then we develop a new refinement for the under-approximation of the static analysis to give accurate results for this class of Process Hitting models.

### 2014-03-27 parts/intro.tex
glued up flattening

--- 2013-05-28 parts/intro.tex
@@
+% vi:spell spelllang=en:
 \section{Introduction}
 \label{sec:intro}
+
+\todo{Add stuff about/adapt to multiple priorities}
 
@@
 before the discussion and conclusion in section 5.
+\todo{Section 4}
 
@@
 $\sN$ is the set of natural numbers,
-$\sN^* = \sN \setminus \{ 0 \}$ is the set of positive natural numbers
+$\sN^* = \sN \setminus \{ 0 \}$ is the set of positive natural numbers,
+$\sNN = \sN \setminus \{ 0, 1 \}$ is the set of natural numbers strictly greater than 1,
 and $\segm{x}{y} = \{ x, x+1, \dots, y-1, y \}$ is the set of natural numbers from $x$ to $y$ included.

### 2014-03-27 parts/models-ph-php.tex
glued up flattening

@@
 \label{ssec:flattening}
-\todo{Glue up all this section}
 
-The aim of this section is to propose a translation of any Process Hitting model
-into a PH model with $2$ classes of priorities
-which is weakkly bisimilar
-and that respects all Criteria of \pref{ssec:hypothesis}.
+\todo{Prove that $\PHflat(\oPH)$ respects all Conditions!}
 
-\todo{Prove that $\PHflat(\oPH)$ respects all Criteria!}
+Consider a PH with $k \in \sNN$ classes of priories
+$\ov{\PH} = (\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}})$
+that respects all Conditions given in \pref{ssec:hypothesis}.
+If $\oPH$ does not respect these Conditions,
+it is then sufficient to instead consider the PH model with $k+1$ classes of priorities
+$\ov{\PH}' = (\ov{\PHs}; \ov{\PHl}; \ov{\PHa}'^{\angles{k+1}})$
+where $\ov{\PHh}'^{(1)} = \emptyset$.
+The aim of this section is to propose a translation of $\oPH$
+into a PH model with $2$ classes of priorities $\PH = (\PHs; \PHl; \PHa^{\angles{2}})$
+called \emph{flattening},
+which is weakly bisimilar
+and that also respects all Conditions of \pref{ssec:hypothesis}.
 
-Consider a PH with $k \in \sN^*$ classes of priories:
-$\ov{\PH} = (\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}})$.
-that respects all Criteria given in \pref{ssec:hypothesis}.
-We want to translate it to a PH with $2$ classes of priorities
-$\PH = (\PHs; \PHl; \PHa^{\angles{2}})$
-that respects all Criteria given in \pref{ssec:hypothesis}.
-
-Note that it is possible to apply this method to any PH model $\ov{\PH}$ that may not respect the aforementioned Criteria.
-It is then sufficient to instead consider the PH model with $k+1$ classes of priorities
-$\ov{\PH}' = (\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k+1}})$
-where $\PHh^{(1)} = \emptyset$.
-
-A \emph{playability property} as defined in \pref{def:pp} is a Boolean formula where the atoms are processes of $\ov{\PH}$.
+This translation is based on the notion of \emph{playability property} defined in \pref{def:pp}
+which is a Boolean formula where the atoms are processes of $\ov{\PH}$.
 
@@
 
-Because we only use classical logic operators, the formulas of Boolean logic on distribution and negation (de Morgan's laws) can be used.
+Because we only use classical logic operators, the formulas of Boolean logic on 
+distributivity, associativity and commutativity can be used, together with De Morgan's laws on negation.
 We also have the following property for the negation of an atom:
@@
 
-In \pref{def:fop}, we finally define the the operator $\Fopsymbol$ which characterizes the playability of an action
+In \pref{def:fop}, we define the the operator $\Fopsymbol$ which characterises the playability of an action
 given the semantics of PH (\pref{def:play}).
+This operator considers the \emph{virtual hitters} of an action,
+which are the sub-states given by $\csState$ to activate the hitter of the given action if it is a process of cooperative sort.
+Furthermore, the target of the action if not taken into account as it is not needed for the rest of the flattening.
+%\pref{th:ppplay} gives the condition for an action to be playable given its playability property.
+%
 \begin{definition}[Playability property of an action ($\Fopsymbol : \PHh \rightarrow \F$)]\label{def:fop}
-  \[\forall h \in \ov{\PHh}, \Fop{h} \equiv \virtualhitters{h} \wedge
+  \[\forall h \in \ov{\PHh}, \Fop{h} \equiv \virtualhitters(h) \wedge
     \left( \bigwedge_{\substack{g \in \PHh^{(n)}\\n < \prio(h)}}
     \neg \left( \target{g} \wedge \hitter{g}\right) \right)\]
-  where $\forall h \in \ov{\PHh} \setminus \ov{\PHh}^{(1)}$ so that $\hitter{h} = a_i$,
+  where if we note $\hitter{h} = a_i$, then:
   \[\virtualhitters(h) =
     \begin{cases}
-      a_i & \text{if } a \in \components \\
+      a_i & \text{if } a \in \components \text{ or } h \in \ov{\PHh}^{(1)} \\
       \bigvee_{ps \in \csState(a_i)} \left( \bigwedge_{p \in ps} p \right) & \text{if } a \in \cs
@@
 %
-\begin{theorem}
-\label{th:ppplay}
-  $h \in \ov{\PHh}$ is playable in $s \in \ov{\PHl}$ if and only if $\Fsem{\Fop{h}}{s} \wedge \target{h} \in s$.
-\end{theorem}
-%
-\newproof{proofppplay}{Proof of \pref{th:ppplay}}
-\begin{proofppplay}
-  By definition of the semantics of a PH given in \pref{def:play}.
-\end{proofppplay}
+By construction of this operator and given the dynamics of a PH model,
+an action $h$ is playable in a state $s \in \ov{\PHl}$ if and only if: $\Fsem{\Fop{h}}{s} \wedge \target{h} \in s$.
+%%
+%\begin{theorem}
+%\label{th:ppplay}
+%  $h \in \ov{\PHh}$ is playable in $s \in \ov{\PHl}$ if and only if $\Fsem{\Fop{h}}{s} \wedge \target{h} \in s$.
+%\end{theorem}
+%%
+%\newproof{proofppplay}{Proof of \pref{th:ppplay}}
+%\begin{proofppplay}
+%  By definition of the semantics of a PH given in \pref{def:play}.
+%\end{proofppplay}
 
@@
 can be seen as a disjunction of $\n$ smaller playability properties consisting only of conjunctions of atoms.
-These $\n$ conjunctions can be translated to as many prioritized cooperative sorts,
+These $\n$ conjunctions can be translated to as many prioritised cooperative sorts,
 thus creating a new PH model which is entailed in the restrictions depicted in \pref{ssec:hypothesis}.
@@
 
-\todo{Glue up}
+With \pref{th:ppplaysubset}, we can then characterise the playability of an action in a state only with a sub-state.
+This sub-state corresponds to one of the conjunctions of its playability property's DNF.
+Finally, \pref{def:flattening} gives the construction of the flattening of $\oPH$:
+for each action $h \in \ov{\PHh}$, several cooperative sorts $f^{h,i}$ are built to reflect each of the conjunction in $\Fop{h}$,
+\ie for $i \in \segm{1}{\n}$.
+This construction allows to obtain the same dynamics as $\oPH$, which is proven by \pref{th:bisimPHP}.
+%
 \begin{theorem}
 \label{th:ppplaysubset}
-  $h \in \ov{\PHh}$ is playable in $s \in \ov{\PHl}$ if and only if
-  $\exists \mysigma \subseteq s, \Fsem{\Fop{h}}{\mysigma} \wedge \target{h} \in s$.
+  Let $h \in \ov{\PHh}$ and $s \in \ov{\PHl}$;
+  $h$ is playable in $s$ if and only if:
+  \[\target{h} \in s \wedge \exists \mysigma \subseteq s, \Fsem{\Fop{h}}{\mysigma} \enspace.\]
 %  \[\exists i \in \segm{1}{\n}, \exists \mysigma \in \bigtimes{b \in \PHdep{i}{h}} \PHl_b,
@@
 \begin{proofppplaysubset}
-  ($\Rightarrow$) If $\Fsem{\Fop{h}}{s}$ then $\Fop{h} \not\equiv \bot$ and, by property of a DNF,
+  ($\Rightarrow$)
+    If $h$ is playable in $s$, then $\target{h} \in s$ and $\Fsem{\Fop{h}}{s}$;
+    thus, $\Fop{h} \not\equiv \bot$ and, by property of a DNF,
     at least one of the $\n$ conjunctions of $\Fop{h}$ is true in $s$.
@@
 
-  ($\Leftarrow$) Trivial.
+  ($\Leftarrow$)
+    Trivial.
 \end{proofppplaysubset}
@@
   \label{def:flattening}
-  If $k \in \sN^*$, we note $\PHflat(\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}}) = (\PHs; \PHl; \PHa^{\angles{2}})$
-  the flattening of the PH with $k$ classes of priorities $\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}}$, with:
+  If $k \in \sNN$ and $\oPH = (\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}})$
+  is a PH with $k$ classes of priorities that respects all Conditions of \pref{ssec:hypothesis},
+  we note $\PHflat(\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}}) = (\PHs; \PHl; \PHa^{\angles{2}})$
+  the \emph{flattening} of $\oPH$, where:
   \begin{itemize}
@@
     therefore, $\os' = \os \PHplay h$.
-    Furthermore, given \pref{th:ppplay}, $\Fsem{\Fop{h}}{\os}$ and $\target{h} \in \os$,
+    Thus, $\Fsem{\Fop{h}}{\os}$ and $\target{h} \in \os$,
     and given \pref{th:ppplaysubset}, there exists $\mysigma \subseteq s$ so that $\Fsem{\Fop{h}}{\mysigma}$.
@@
 
-We showed in this subsection that it is possible to model a PH model with $k$ classes of priorities as a PH model
-with $2$ classes of priorities that respects all Criteria of \pref{ssec:hypothesis} and with the same dynamics.
+We showed in this subsection that it is possible to model a PH with $k$ classes of priorities as a PH
+with $2$ classes of priorities with the same dynamics that respects all Conditions of \pref{ssec:hypothesis}.
 We note however that the translation given in this section may not be minimal in terms of number of actions
@@
 \paragraph{Playability properties simplifications}
-It is possible to obtain a flattened PH with the same dynamics
-by simplifying the playability property of an action $h = \PHhit{a_i}{b_j}{b_k}$ with the following properties:
+The playability property $\Fop{h}$ of an action $h = \PHhit{a_i}{b_j}{b_k}$ can be simplified with the following properties,
+which may remove the necessity to create some useless actions (that are never playable) or cooperations (that are always true):
 \begin{itemize}
   \item it is always possible to simplify the target because its presence is checked besides: $b_j \equiv \top$;
-  \item any process $b_l \neq b_j$ of the same sort than $b_k$ always prevents the playability, thus: $b_l \equiv \bot$;
+  \item any process $b_l \neq b_j$ of the same sort than the target always prevents the playability, thus: $b_l \equiv \bot$;
   \item if $c_p, c_q$ are different processes ($c_p \neq c_q$) of the same sort $c$, then $c_p \wedge c_q \equiv \bot$.
@@
 \paragraph{Removal of the unnecessary cooperative sorts}
-There are two cases where it is possible to remove a cooperative sort $f^{h,i}$ in the flattened PH:
+There are two cases where it is possible to remove a cooperative sort $f^{h,i}$ in the flattening:
 \begin{itemize}
-  \item if $\Fop{h} \equiv \top$, then the action $h$ can be modeled in the flattened model by an auto-action
+  \item if $\Fop{h} \equiv \top$, then the action $h$ can be translated as an auto-action
     (as it is always playable if the target is present);
   \item if the $i$\textsuperscript{th} conjunction of $\Fop{h}$ consists of only one element $p$,
-    then $h$ can be modeled as a regular action $\PHhit{p}{\target{h}}{\bounce{h}}$ in the flattened PH
+    then $h$ can be translated as a regular action $\PHhit{p}{\target{h}}{\bounce{h}}$ instead of a cooperative sort
     (as, apart from the target, only one process is required).

### 2014-03-27 parts/ccl.tex

@@
+% vi:spell spelllang=en:
 \section{Discussion \& Conclusion}\label{sec:ccl}
@@
 
+We also demonstrated that general Process Hitting models with arbitrary priority
+classes can also be encoded in the particular class of two-prioritized Process Hitting.
+Therefore, our static analysis is applicable to a broad range of automata
+networks with priorities.
+
 Further work can be derived from what have been presented in this paper.
@@
 %and mode precisely the class of models studied in this paper.
-Furthermore, a more general under-approximation could be developed in order to handle a larger class of Process Hitting models, that is,
-models with more than two classes of priorities, that do not only contain components of cooperative sorts, or whose behaviour may contain cycles or cyclic attractors.
+Furthermore, we are investigating alternative under-approximations that can be
+applied directly on a larger class of Process Hitting models, \ie{} without an
+intermediate encoding; our objective being to increase the conclusiveness of the static
+analysis approach.
 Finally, in order to take into account quantitative data in transition delays, the overall approximation method could be extended to handle evolutions that are chronometric instead of only chronologic.

### 2014-03-27 parts/example.tex
describe metazoan example

@@
 
-\subsection{\ldots (metazoan)}
+\subsection{Flattening of a model: Metazoan segmentation}
 
-\todo{Describe the model}
+In this section, we illustrate the flattening method presented in \pref{ssec:flattening}
+on a model of metazoan segmentation established in silico in \cite{MSB:MSB4100192}
+in a differential equations framework.
+It is composed of a wavefront gene $f$ that activates the gap-gene $a$ whose products are responsible or stripes.
+Gene $f$ also activates a gene $c$ whose products repress the gene $a$.
+The auto-inhibition of $c$ generalises a chain of repressors on $a$.
+The auto-inhibition of $f$, which terminates the stripes formation in the original model,
+have been removed in order to focus on the stationary dynamics of the model.
 
-\begin{example}
-  The model of \pref{fig:metazoan-php} gives an example of PH with $3$ classes of priorities.
-  Although the actions of the highest class of priority are only used to update a cooperative sort,
-  the actions of the intermediate priority do not follow the constraints of \pref{ssec:hypothesis},
-  thus having a biological meaning by representing different reaction speeds.
+The actions of the original model make $3$ classes of priorities, as represented in \pref{fig:metazoan-php}.
+Thus, although the actions of the highest class of priority are only used to update a cooperative sort,
+the actions of the two other classes of priorities do have a biological meaning.
+%by representing different reaction rates.
+Indeed, they have been derived given the different reaction rates,
+given the fact that the switches of genes $a$ and $c$ have to alternate in order not to miss a stripe.
 
@@
 \end{figure}
-\end{example}
 
-\begin{example}
-  \pref{fig:metazoan-ph} gives the flattened model of the PH of \pref{fig:metazoan-php}.
-  It contains $2$ classes of priority, and prioritized actions are only used to update cooperative sorts.
+\pref{fig:metazoan-ph} gives the flattening of this model.
+It contains $2$ classes of priority, and prioritised actions are only used to update cooperative sorts.
 Note that according to the simplifications mentioned at the end of \pref{ssec:flattening},
@@
 because its playability property could be simplified to $\Fop{h_1} \equiv c_1 \wedge a_0 \equiv a_0$.
+
+\todo{Results on reachability?}
 
@@
 \end{figure}
-\end{example}
 
-\subsection{Large-scale Application}
+\subsection{Large-scale Application: T-cell receptor}
 

### 2014-03-28 parts/ccl.tex
global proofread

@@
 The over-approximation on Process Hitting models without priorities proposed in~\cite{PMR12-MSCS}
-is still accurate in the framework with priorities (by “flattening” all actions),
+is still accurate in the framework with priorities (by “merging” all actions),
 but may be refined given the restrictions proposed in this paper,
@@
 Furthermore, we are investigating alternative under-approximations that can be
-applied directly on a larger class of Process Hitting models, \ie{} without an
+applied directly on a larger class of Process Hitting models, \ie without an
 intermediate encoding; our objective being to increase the conclusiveness of the static

### 2014-03-28 parts/def-ph.tex
global proofread

@@
 \section{The Process Hitting Framework}
+\label{sec:ph}
 
@@
 \label{ssec:PH}
-A PH with $k$ classes of priorities (\pref{def:ph}), also simply called “PH” in the following when it is not ambiguous, gathers a finite number of concurrent \emph{processes} divided into a finite set of \emph{sorts}.
+A PH with $k \in \sN^*$ classes of priorities (\pref{def:ph}), also simply called “PH” in the following when it is not ambiguous, gathers a finite number of concurrent \emph{processes} divided into a finite set of \emph{sorts}.
 A process belongs to a unique sort and is noted $a_i$ where $a$ is the sort and $i$ the identifier of the process within the sort $a$.
@@
 \label{def:ph}
-  If $k \in \sNN$, a \emph{Process Hitting with $k$ classes of priorities} is a triplet $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$,
+  If $k \in \sN^*$, a \emph{Process Hitting with $k$ classes of priorities} is a triplet $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$,
   where $\PHa^{\langle k \rangle} = (\PHa^{(1)}; \dots; \PHa^{(k)})$ is a $k$-tuple and:
@@
   We call $\PHproc \DEF \bigcup_{a \in \PHs} \PHl_a$ the set of all processes, and $\PHh \DEF \bigcup_{n \in \segm{1}{k}} \PHh^{(n)}$ the set of all actions.
+  Furthermore, for all $n \in \sN^*$ and $h \in \PHh^{(n)}$, $\prio(h) \DEF n$.
 \end{definition}
+%
 \noindent
@@
 If $a_i \in \PHl_a$, we define the notation $a_i \in s \EQDEF \PHget{s}{a} = a_i$.
-The override of a state $s$ by a process $a_i$ is defined in \pref{def:statecap} as the same state in which the process of sort $a$ has been replace by $a_i$,
+\pref{def:substate} defines the notion of sub-state on a set of sorts, that is used to focus on the interesting part of a complete state.
+Note that a state is \textit{a fortiori} a sub-state.
+The override of a state $s$ by a process $a_i$ (or by a set of processes)
+is defined in \pref{def:statecap} as the same state in which the process of sort $a$ has been replaced by $a_i$,
 which then allows to define the dynamics of a PH in \pref{def:play}.
-\begin{definition}[$\Cap : \PHl \times \PHproc \rightarrow \PHl$]
-\label{def:statecap}
-  Given a state $s \in \PHl$ and a process $a_i \in \PHproc$, $(s \Cap a_i)$ is the state defined by:
-  $\PHget{(s \Cap a_i)}{a} = a_i \wedge \forall b \neq a, \PHget{(s \Cap a_i)}{b} = \PHget{s}{b}$.
-  We also extend this definition to a set of processes $ps$ given that all processes are from different sorts by the override of each process:
-  $\forall as \subseteq \PHs, \forall ps \in \underset{a \in as}{\times} \PHl_a, s \Cap ps = s \underset{a_i \in ps}{\Cap} a_i$.
-\end{definition}
-\begin{definition}[Dynamics of a PH ($\PHPtrans$)]
-\label{def:play}
-  An action $h = \PHhit{a_i}{b_j}{b_k} \in \PHa^{(n)}$ of priority $n$ is \emph{playable} in $s \in \PHl$
-  if and only if $\PHget{s}{a} = a_i$, $\PHget{s}{b} = b_j$ and $\forall m < n, \forall g \in \PHa^{(m)}, \PHhitter(g) \notin s \vee \PHtarget(g) \notin s$.
-  In such a case, $(s \PHplay h)$ stands for the state resulting from the play of the action $h$ in $s$ and is defined by: $(s \PHplay h) = s \Cap \PHbounce(h)$.
-  Moreover, we denote: $s \PHPtrans (s \PHplay h)$.
-
-  If $s \in \PHl$,
-  a \emph{scenario} $\delta$ from $s$ is a sequence of actions of $\PHh$ that can be played successively in $s$.
-  The set of all scenarios from $s$ is noted $\Sce(s)$.
-\end{definition}
-
-\pref{def:substate} defines the notion of sub-state on a set of sorts,
-that is used to consider the interesting part of a complete state.
+%
 \begin{definition}[Sub-states ($\PHsublize{\PHl}$)]
@@
 \end{definition}
-We note that a state is \textit{a fortiori} a sub-state: $\PHl \subset \PHsubl[\PHl]$.
+%
+\begin{definition}[$\Cap : \PHl \times \PHproc \rightarrow \PHl$]
+\label{def:statecap}
+  Given a state $s \in \PHl$ and a process $a_i \in \PHproc$, $(s \Cap a_i)$ is the state defined by:
+  $\PHget{(s \Cap a_i)}{a} = a_i \wedge \forall b \neq a, \PHget{(s \Cap a_i)}{b} = \PHget{s}{b}$.
+  We also extend this definition to a set of processes given that all processes are from different sorts by the override of each process:
+  $\forall ps \in \PHsubl[\PHl], s \Cap \toset{ps} = s \underset{a_i \in \toset{ps}}{\Cap} a_i$.
+  %$\forall as \subseteq \PHs, \forall ps \in \underset{a \in as}{\times} \PHl_a, s \Cap ps = s \underset{a_i \in ps}{\Cap} a_i$.
+\end{definition}
+%
+\begin{definition}[Dynamics of a PH ($\PHPtrans$)]
+\label{def:play}
+  An action $h = \PHhit{a_i}{b_j}{b_k} \in \PHa^{(n)}$ of priority $n$ is \emph{playable} in $s \in \PHl$
+  if and only if $\PHget{s}{a} = a_i$, $\PHget{s}{b} = b_j$ and $\forall m < n, \forall g \in \PHa^{(m)}, \PHhitter(g) \notin s \vee \PHtarget(g) \notin s$.
+  In such a case, $(s \PHplay h)$ stands for the state resulting from the play of the action $h$ in $s$ and is defined by: $(s \PHplay h) = s \Cap b_k$.
+  Moreover, we denote: $s \PHPtrans (s \PHplay h)$.
+
+  If $s \in \PHl$,
+  a \emph{scenario} $\delta$ from $s$ is a sequence of actions of $\PHh$ that can be played successively in $s$.
+  The set of all scenarios from $s$ is noted $\Sce(s)$.
+\end{definition}
 
@@
     Sorts are represented as labelled boxes and processes as circles with their identifier on the side.
-    Actions of $\PHh^{(1)}$ are represented by thick arrows and actions of $\PHh^{(2)}$ are represented by single arrows;
+    Actions of $\PHh^{(1)}$ are represented by thick arrows and actions of $\PHh^{(2)}$ are represented by thin arrows;
     the hit part of each action in drawn in plain line and the bounce part is in dotted line.
@@
 it is possible to build cooperations with no temporal shift by defining actions updating the cooperative sorts with the highest class of priority.
-This allows to gain the same expressivity in PH than in Boolean networks, as stated in \pref{ssec:hypothesis}.
-The aim of this paper is to allow the static analysis of the dynamics to be handled on PH models comprising such higher priority actions updating cooperative sorts.
+This allows to gain the same expressivity in PH than in Boolean networks, as stated in \pref{sec:dn}.
+The aim of this paper is to allow the static analysis of the dynamics to be handled on PH models comprising such prioritised actions updating cooperative sorts.
 
@@
 in which actions of $\PHh^{(1)}$ are called \emph{prioritized actions} and allow to model non-biological actions.
-%and show that they are equivalent to discrete networks.
 We consider in this section a PH model with $k$ classes of priorities: $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$, with $k \in \sNN$
@@
 
-%\pref{cr:2prio} allows to distinguish two kinds of actions:
-%\emph{unprioritised actions} modelling the non-determinacy of biological evolutions
-%and \emph{prioritised actions} used to model non-biological behaviours in the model, namely the update of cooperative sorts.
 \pref{cr:bounded} states that the dynamics of the studied model $\PH$ contains no infinite sequence of prioritised actions.
@@
 As a consequence, the set $\restriction{\Sce}{1}$ is finite.
-%\begin{condition}[2 classes of priorities]
-%\label{cr:2prio}
-%  In this paper, we only consider Process Hitting with $2$ classes of priorities:
-%  $\PH = (\PHs; \PHl; \PHa^{\langle 2 \rangle})$.
-%\end{condition}
-%
+
 \begin{condition}[Bounded termination]
@@
 The latter is a sort that is hit only by actions with priority $1$ and which
-always converge to the same process with respect to the state of the components
+always converges to the same process with respect to the state of the components
 that have an influence on it (\pref{def:conn}).
@@
 Given a sort $a$, $\compin(a)\DEF \conn(a)\cap\components$ where
-$\conn(a)$ is the smallest set of sorts satisfying the following properties:
+$\conn(a) \subset \PHs$ is the smallest set of sorts satisfying the following properties:
 \begin{align*}
@@
 
+We note that a sort $a$ that is hit by no action (\ie $\forall h \in \PHh, \PHsort(\target{h}) \neq a$)
+does comply with both definitions of well-formed components and well-formed cooperative sorts.
+In this case, such a sort can be arbitrarily affected to either of sets.
+Such case may occur for “input” sorts (which state is initially fixed and do not evolve)
+or some special cases of cooperative sorts produces by the translations of \pref{sec:encodings}.
+
 Because of \pref{def:cs}(\ref{csai}), we denote in the following: $\pfp_s(a) = a_i$.
@@
 \begin{example}
-  The PH in \pref{fig:ph-livelock} contains three components $a$, $b$ and $c$ and a cooperative sort $ab$ that models cooperation between sorts $a$ and $b$.
+  The PH in \pref{fig:ph-livelock} contains three components ($a$, $b$ and $c$) and a cooperative sort ($ab$, which models cooperation between sorts $a$ and $b$).
 \end{example}

### 2014-03-28 parts/example.tex
global proofread

@@
 In this section, we illustrate the flattening method presented in \pref{ssec:flattening}
-on a model of metazoan segmentation established in silico in \cite{MSB:MSB4100192}
-in a differential equations framework.
-It is composed of a wavefront gene $f$ that activates the gap-gene $a$ whose products are responsible or stripes.
-Gene $f$ also activates a gene $c$ whose products repress the gene $a$.
+on a model of metazoan segmentation inspired from a first translation to Process Hitting given in \cite{PMR10-TCSB}.
+This model was originally established in silico in \cite{MSB:MSB4100192} in a differential equations framework.
+It is composed of a wavefront gene $f$ that activates the gap-gene $a$ whose products are responsible for stripes formation.
+Gene $f$ also activates a gene $c$ whose products represses the gene $a$.
 The auto-inhibition of $c$ generalises a chain of repressors on $a$.
 The auto-inhibition of $f$, which terminates the stripes formation in the original model,
-have been removed in order to focus on the stationary dynamics of the model.
+has been removed in order to focus on the stationary dynamics of the model.
 
@@
   \label{fig:metazoan-php}
-    An example of PH $\oPH$ with $3$ classes of priorities.
+    An example of PH $\oPH$ with $3$ classes of priorities,
+    modelling the process of metazoan segmentation.
     Actions of $\ov{\PHh}^{(3)}$ (lowest priority) are in thin lines,
@@
     and actions of $\ov{\PHh}^{(1)}$ (highest priority), whose only purpose is to update the cooperative sort $fc$,
-    are not represented but modeled by the double dashed arrows.
+    are not represented but modelled by the double dashed arrows.
   }
@@
 because its playability property could be simplified to $\Fop{h_1} \equiv c_1 \wedge a_0 \equiv a_0$.
-
-\todo{Results on reachability?}
 
@@
   \label{fig:metazoan-ph}
-    An example of PH $\PH$ with $2$ classes of priorities.
-    Actions of $\PHh^{(2)}$ (unprioritized) are in thin lines,
-    and actions of $\PHh^{(1)}$ (prioritized) which are used to update cooperative sorts,
+    An example of PH $\PH$ with $2$ classes of priorities,
+    which is the flattening of the PH in \pref{fig:metazoan-php}.
+    Actions of $\PHh^{(2)}$ (unprioritised) are in thin lines,
+    and actions of $\PHh^{(1)}$ (prioritised) which are used to update cooperative sorts,
     are abstracted by thick dashed arrows.

### 2014-03-28 parts/intro.tex
global proofread

@@
 consisting in a restriction where the evolution of a component is determined by the state of at most one other component that does not evolve.
-In a sense, these kind of actions are of the form $X + Y \rightarrow X + Z$ where $X$ behaves like a catalyst molecule that “hits” another molecule $Y$ and changes it into $Z$, without being itself changed.
+In a sense, these kind of actions are of the form $X + Y \rightarrow X + Y'$ where $X$ behaves like a catalyst molecule that “hits” another molecule $Y$ and changes it into $Y'$, without being itself changed.
 Assuming catalysts are always available, this can represent any biochemical system made of monomolecular reactions, and can also represent catalytic networks such as metabolic networks.
@@
 They are based on the fact that most biological models have few levels of expression per component:
-in Boolean networks~\cite{kauffman69,Thomas73} there are only two levels per component and in its multivalued equivalent, Asynchronous Discrete Networks~\cite{deJong02}, components rarely have more that four levels.
+in Boolean networks~\cite{kauffman69,Thomas73} there are only two levels per component and in their multivalued equivalent, Asynchronous Discrete Networks~\cite{deJong02}, components rarely have more that four levels.
 
@@
 In this paper, we are dealing with these timing properties through priorities,
-that are based on the simple founding idea that prioritised actions have to be processed before the other ones.
-Indeed, due to the Process Hitting framework restrictions, bimolecular reactions are not immediately available, but one can simulate them with an encoding called “cooperation”.
+that are based on the simple founding idea that actions with higher priority have to be processed before the ones with lower priority.
+Furthermore, due to the Process Hitting framework restrictions, multimolecular reactions are not immediately available, but one can simulate them with an encoding called “cooperation”.
 That encoding however introduces extra reactions, and this is where the priorities become useful, if not necessary.
-The extra reactions can be given “infinite speed” (high priority) so that they do not affect the behaviour of “normal” (low priority) reactions, including the bimolecular ones.
+The extra reactions can be given “infinite speed” (highest priority) so that they do not affect the behaviour of “normal” (lower priority) reactions, including the multimolecular ones.
 
@@
 Since our formalism (the Process Hitting) can be considered as a subset of Calculus of Communicating Systems, %is inspired from the $\pi$-calculus,
-our work is related to such semantic ramifications of extending traditional process algebras with the concepts of priority that allow for some transitions to be given precedence over others.
+our work is related to such semantic ramifications of extending traditional process algebras with the concept of priority that allows for some transitions to be given precedence over others.
 The concept is derived in two directions: dynamic versus static, the difference being naturally that the former one refers to a semantics where priority values may change during execution according to some evolution rules.
-In our work, actions exhibit a two-level static priority structure, some of them being designated as “prioritised” and others as “unprioritised”.
+In our work, actions exhibit a static priority structure.
+The actions modelling biological processes are divided in several classes of priorities which stand for the different reaction rates or relative preemptions.
+Furthermore, the highest class of priority is used to model particular nonbiological actions, designated as “prioritised”,
+that are used to encode Boolean functions inside the model.
 
@@
 
-Whereas the analysis presented in \pref{sec:sa} consider a particular class of
+Whereas the analysis presented in \pref{sec:sa} considers a particular class of
 Process Hitting with two classes of priority,
@@
 Process Hitting models with priorities.
-Those encodings result in Process Hitting fulfilling the conditions for our
+Those encodings result in a Process Hitting fulfilling the conditions for our
 static analysis and show the broad applicability of our method.

### 2014-03-28 parts/models-ph-dn.tex
debut sequencial reachability
global proofread

--- 2014-03-19 parts/models-ph-dn.tex
@@
 We exhibit an encoding of Asynchronous Discrete Networks (ADN) with the Process
-Hitting using two classes of priorities, and prove a weak bisimulation relation.
+Hitting using two classes of priorities
+that respects all Conditions of \pref{ssec:hypothesis},
+and prove a weak bisimulation relation.
 
@@
 
+By construction, the cooperative sorts are well-formed, hence $\toPH\DNdef$
+satisfies the Conditions of \pref{ssec:hypothesis}.
 \pref{th:bisimDN} states the weak bisimulation relation between an ADN and its encoding in

### 2014-03-28 parts/models-ph-php.tex
global proofread

@@
 \label{ssec:flattening}
-
-\todo{Prove that $\PHflat(\oPH)$ respects all Conditions!}
 
@@
 We showed in this subsection that it is possible to model a PH with $k$ classes of priorities as a PH
-with $2$ classes of priorities with the same dynamics that respects all Conditions of \pref{ssec:hypothesis}.
+with $2$ classes of priorities and the same dynamics.
+Furthermore, by construction, the cooperative sorts are well-formed, and $\PHflat(\oPH)$
+thus satisfies the Conditions of \pref{ssec:hypothesis}.
 We note however that the translation given in this section may not be minimal in terms of number of actions

### 2014-03-28 parts/sa.tex
global proofread

@@
 We consider in this section a PH model $\PH = (\PHs; \PHl; \PHa^{\langle 2 \rangle})$ with $2$ classes of priorities
-that respects all conditions (\ref{cr:bounded} \& \ref{cr:compcs}) of \pref{ssec:hypothesis}.
+that respects all Conditions (\ref{cr:bounded} \& \ref{cr:compcs}) of \pref{ssec:hypothesis}.
 
@@
 \begin{enumerate}[(i)]
-\item $\forall\delta\in\concr(\w), \exists s\subseteq\ctx: \delta\in\Sce(s)$
+\item $\forall\delta\in\concr(\w), \exists s\subseteq\ctx, \delta\in\Sce(s)$
 \item $\forall\delta\in\concr(\w),
   \exists \phi:\indexes{\w}\to\indexes{\delta},
-    (\forall n,m\in\indexes{\w}, n<m \Leftrightarrow \phi(n)\leq\phi(m)):$
+    (\forall n,m\in\indexes{\w}, n<m \Leftrightarrow \phi(n)\leq\phi(m)),$
 \\\hspace*{2cm}$\forall n\in\indexes{\w}, \PHbounce(\w_n) \in \ctx\play\delta_{1..\phi(n)}$
@@
 \begin{example}
-  Let $\PH' = (\PHs, \PHl, \PHh'^{\langle 1 \rangle})$ be the “flattened” version of the PH in \pref{fig:ph-livelock}, that is: $\PHh'^{\langle 1 \rangle} = \PHh^{(1)} \cup \PHh^{(2)}$,
-  which is equivalent to a PH in the semantics without priorities.
+  Let $\PH' = (\PHs, \PHl, \PHh'^{\langle 1 \rangle})$ be the “merged” version of the PH in \pref{fig:ph-livelock}, that is: $\PHh'^{\langle 1 \rangle} = \PHh^{(1)} \cup \PHh^{(2)}$,
+  which is how it would have been represented in the semantics without priorities.
   Due to spurious behaviours inherent to the cooperative sorts in this semantics, 
   the original under-approximation developed in~\cite{PMR12-MSCS} concludes that $c_1$ is reachable in $\PH'$ from $\ctx = \PHstate{a_1, b_0, c_0, ab_{10}}$.
-  %this is due to an over-approximation of the behaviours inherent to cooperative sorts in the semantics without priorities.
 
@@
 
-  However, if $\PHhit{a_0}{b_0}{b_1}$ and $\PHhit{b_0}{a_0}{a_1}$ are replaced by
+  However, if $\PHhit{a_0}{b_0}{b_1}$ and $\PHhit{b_0}{a_0}{a_1}$ are replaced by the auto-actions
   $\PHhit{a_0}{a_0}{a_1}$ and $\PHhit{b_0}{b_0}{b_1}$,
@@
   \label{fig:sa-livelock}
-    The graph of local causality of the PH model in \pref{fig:ph-livelock}.
+    The graph of local causality of the PH model in \pref{fig:ph-livelock}
+    for the objective $\w = \PHobj{c_0}{c_1}$ and the initial context $\ctx = \PHstate{a_1, b_0, c_0, ab_{10}}$.
     Rectangular nodes containing a single process are elements in $\Proc$,
-    nodes containing a couple of processes are elements in $\Obj$
+    borderless nodes containing a couple of processes are elements in $\Obj$
     and circle nodes are elements in $\Sol$.
@@
 
-The reachability property studied so far concern a single process at a time.
+The reachability property studied so far concerns a single process at a time.
 However, we remark that the reachability of a partial or global state can be
@@
 
-It is also possible to compute the reachability of a set of states $S \subseteq \PHl$ by creating several actions $\PHhit{\total_s}{\reach_0}{\reach_1}$ in $\PHh^{(2)}$ for each state $s \in S$.
+It is also possible to compute the reachability of a set of states $S \subseteq \PHl$ by creating several actions $\PHhit{\total_s}{\reach_0}{\reach_1}$ in $\PHh^{(2)}$ for each state $s \in S$,
+or on a sub-state $s \in \PHsubl[\PHl]_S$ of a set of components $S \subset \PHs$ by adapting the sort $\total$ with: $\PHl_\total = \PHsubl[\PHl]_S$
 
@@
 
-Let us define a sequence of objective $\w=\obj{a_i}{a_j}\concat\w'$ with
-$a_i\neq a_j$ and a state $s\in L$ with $\get{s}{a}=a_i$.
+Let us define a sequence of objectives $\w=\obj{a_i}{a_j}\concat\w'$ with
+$a_i\neq a_j$ and a state $s\in \PHl$ with $\get{s}{a}=a_i$.
 One can remark that any scenario reaching $a_j$ necessarily includes one of the
-bounce sequence in $\BS(\obj{a_i}{a_j})$, and in particular,
+bounce sequences in $\BS(\obj{a_i}{a_j})$, and, in particular,
 any minimal scenario reaching $a_j$ ends in a state where $a_j$ is present but
-also the hitter of the last of one bounce sequence in $\BS(\obj{a_i}{a_j})$.
-If such hitter $b_k$ is in a cooperative sort $b\in\cs$, it also means that one of the sub-state
-in $\csState(b_k)$.
+also the hitter of the last bounce of one bounce sequence in $\BS(\obj{a_i}{a_j})$.
+If such hitter $b_k$ is in a cooperative sort $b\in\cs$, it also means that one of the sub-states
+in $\csState(b_k)$ is included in the ending state.
 \pref{def:lastprocs} defines $\lastprocs(\obj{a_i}{a_j})$ as the set of set of
@@
 \item $\{\hitter{\zeta_{\card\zeta}}\} \subset lps$;
-\item $\forall b_j\in lps, b\in\cs, \exists ps\in\csState(b_j): ps\subset lps$;
+\item $\forall b_j\in lps, b\in\cs, \exists ps\in\csState(b_j), ps\subset lps$;
 \item $\forall b_j\in lps, b\in\cs, 
@@
 				ps\subset lps'$;
-\item $\nexists lps'\in\lastprocs(\obj{a_i}{a_j}): lps'\subset lps \wedge
+\item $\nexists lps'\in\lastprocs(\obj{a_i}{a_j}), lps'\subset lps \wedge
 									lps'\neq lps$.
@@
 If $\uconcr(P)\neq\emptyset$,
-for all $s\in L, s\subset\ctx$,
+for all $s\in \PHl, s\subset\ctx$,
 there exists a scenario $\delta\in\uconcr(P)\cap\Sce(s)$;
@@
 Hence, $\delta\concat\delta'$ is a scenario playable in $s$.
-Therefore, for all $s\in L, s\subset\ctx$, there exists a scenario
+Therefore, for all $s\in \PHl, s\subset\ctx$, there exists a scenario
 concretizing $\w$.

### 2014-03-31 main.tex
glued up flattening
minor changes

@@
 \newrefformat{cr}{Condition~\ref{#1}}
-\newrefformat{crs}{Conditions~\ref{#1}}
 \newrefformat{eq}{Eq.~\eqref{#1}}
@@
 \newcommand{\sN}{\mathbb{N}}
-\newcommand{\sNN}{\mathbb{N}^{**}}
+\newcommand{\sNN}{\mathbb{N}^\bullet}
 \def\DEF{\stackrel{\Delta}=}
@@
 Then we develop a new refinement for the under-approximation of the static analysis to give accurate results for this class of Process Hitting models.
-Our method thus allows to efficiently under-approximate reachability properties in Asynchronous Discrete Networks;
-it is in particular conclusive on reachability properties in a 94 components Boolean network, which is unprecedented.
+Our method thus allows to efficiently under-approximate reachability properties
+in Asynchronous Discrete Networks,
+as it is illustrated on the model-checking of a signaling network of 94
+components, which is unprecedented.
 \end{abstract}

### 2014-03-31 parts/intro.tex
minor changes

@@
 This paper is an extension of \cite{FPMR13-CS2Bio} were we
-we introduced a new extension to the semantics of Process Hitting by partitioning actions into classes of priorities
+introduced a new extension to the semantics of Process Hitting by partitioning actions into classes of priorities
 (\pref{sec:ph}).
@@
 Those encodings result in a Process Hitting fulfilling the conditions for our
-static analysis and show the broad applicability of our method.
+static analysis and support the broad applicability of our method.
 

### 2014-03-31 parts/sa.tex
minor changes

@@
 \label{thm:ordered-ua}
-Given a context $\ctx$ and an objective sequence $\w =
+Given a Process Hitting $(\PHs; \PHl; \PHa^{\langle 2 \rangle})$
+that satisfies \pref{cr:bounded} and \pref{cr:compcs},
+a context $\ctx$ and an objective sequence $\w =
 P\concat\w'\in\OS$,

### 2014-04-03 parts/models-ph-dn.tex
move proofs in appendix

@@
 sorts follow strictly the possible transitions of the ADN.
+A detailed proof is given in \pref{suppl:proofbisimADN}.
 
@@
 \end{theorem}
-%
-\newproof{proofbisimADN}{Proof of \pref{th:bisimDN}}
-\begin{proofbisimADN}
-(\ref{adn2ph}) From \pref{def:DN}, $x\DNtrans x'\Rightarrow \exists i\in\segm{1}{n},
-f^i(x)=\get{x'}{i} \wedge \forall j\in\segm{1}{n},i\neq j, \get{x}{j}=\get{x'}{j}$.
-Let us assume (without loss of generality) that $f^i(x)=k'$, $\get{x}{i}=k$ and
-$\varsigma\in\underset{j\in\DNdep(f^i)}{\times} \PHl_{a^j}$ such that
-$\forall j\in\DNdep(f^i), \get{\varsigma}{j}=a^j_{\get{x}{j}}$.
-From \pref{def:DN2PH}, $h=\hit{f^i_\varsigma}{a^i_k}{a^i_{k'}}\in\Hits^{(2)}$.
-From the definition of $\encode x$,
-$a^i_k\in \encode x$ and $f^i_\varsigma\in \encode x$;
-moreover, as there is no action in $\Hits^{(1)}$ applicable in $\encode x$,
-$h$ is applicable in $\encode x$:
-$\encode x\PHPtrans \encode x\play h$.
-In $\encode x\play h$, the only applicable actions of priority $1$ are those having
-$a^i_{k'}$ as hitter and hitting cooperative sorts, giving a finite number of transitions towards
-$\encode{x'}$.
-
-(\ref{ph2adn}) $s\PHPtrans s'$ only if there exists an action $h$ applicable in $s$ such that
-$s\play h=s'$.
-If $\prio(h)=1$, then, by definition of $\Hits^{(1)}$, 
-$\decode s=\decode {s'}$.
-If $\prio(h)=2$, then $\forall i\in\segm{1}{n}$,
-if $\get{s}{f^i} = f^i_\varsigma$, then, $\forall j\in\DNdep(f^i),
-\get{\varsigma}{a^j}=\get{s}{a^j}$.
-Let $i\in\segm{1}{n}$ such that $\get{s}{a^i}\neq\get{s'}{a^i}$ ($i$ is unique for this
-transition).
-By \pref{def:DN2PH}, if $\get{s'}{a^i}=a^i_{k'}$, necessarily $f^i(\decode s)=k'$, hence
-$\decode s\DNtrans \decode{s'}$.
-\end{proofbisimADN}

### 2014-04-03 parts/models-ph-php.tex
move proofs in appendix

@@
-\subsection{PH with multiple classes of priorities}
+\subsection{Process Hitting with multiple classes of priorities}
 \label{ssec:flattening}
@@
 
-With \pref{th:ppplaysubset}, we can then characterise the playability of an action in a state only with a sub-state.
+With \pref{lem:ppplaysubset}, we can then characterise the playability of an action in a state only with a sub-state.
 This sub-state corresponds to one of the conjunctions of its playability property's DNF.
@@
 \ie for $i \in \segm{1}{\n}$.
-This construction allows to obtain the same dynamics as $\oPH$, which is proven by \pref{th:bisimPHP}.
+This construction allows to obtain the same dynamics as $\oPH$, as stated by \pref{th:bisimPHP}.
+A detailed proof of this theorem is available in \pref{suppl:demoflattening}.
 %
-\begin{theorem}
-\label{th:ppplaysubset}
+\begin{lemma}
+\label{lem:ppplaysubset}
   Let $h \in \ov{\PHh}$ and $s \in \ov{\PHl}$;
@@
 %    \mysigma \subseteq s \wedge \Fsem{\F(h)}{\mysigma} \enspace.\]
-\end{theorem}
+\end{lemma}
 %
-\newproof{proofppplaysubset}{Proof of \pref{th:ppplaysubset}}
-\begin{proofppplaysubset}
+%\newproof{proofppplaysubset}{Proof of \pref{lem:ppplaysubset}}
+%\begin{proofppplaysubset}
+\begin{proof}
   ($\Rightarrow$)
-    If $h$ is playable in $s$, then $\target{h} \in s$ and $\Fsem{\Fop{h}}{s}$;
-    thus, $\Fop{h} \not\equiv \bot$ and, by property of a DNF,
+    If $h$ is playable in $s$, then $\target{h} \in s$ and $\Fsem{\Fop{h}}{s}$.
+    Thus, $\Fop{h} \not\equiv \bot$ and, by property of a DNF,
     at least one of the $\n$ conjunctions of $\Fop{h}$ is true in $s$.
@@
   ($\Leftarrow$)
-    Trivial.
-\end{proofppplaysubset}
+    $\Fsem{\Fop{h}}{\mysigma}$ therefore $\Fsem{\Fop{h}}{s}$; as $\target{h} \in s$, $h$ is playable in $s$.
+\end{proof}
+%\end{proofppplaysubset}
 
@@
 \end{theorem}
-%
-\newproof{proofbisimPHP}{Proof of \pref{th:bisimPHP}}
-\begin{proofbisimPHP}
-  (\ref{php2ph}) Let $\flats{\os} = s$.
-    Given the dynamics of a PH (\pref{def:play}), if $\os \PHPtrans[\PH] \os'$,
-    then there exists $h \in \ov{\PHh}$ playable in $\os$;
-    therefore, $\os' = \os \PHplay h$.
-    Thus, $\Fsem{\Fop{h}}{\os}$ and $\target{h} \in \os$,
-    and given \pref{th:ppplaysubset}, there exists $\mysigma \subseteq s$ so that $\Fsem{\Fop{h}}{\mysigma}$.
-    Therefore, by construction of $\PH$ (\pref{def:flattening}) there exists
-    $g = \PHhit{f^{h,i}_\mysigma}{\target{h}}{\bounce{h}} \in \PHh^{(2)}$.
-    By construction of $s$ (\pref{def:flattening}), $\PHget{s}{f^{h,i}} = f^{h,i}_\mysigma$ and $\target{h} = \target{g} \in s$.
-    Therefore, $g$ is playable in $s$.
-    In $s \PHplay g$, the only playable actions are those in $\PHh^{(1)}$ having $\bounce{h} = \bounce{g}$ as hitter
-    and updating cooperative sorts, allowing to reach $\flats{\os'}$ in a finite number of actions.
-    Thus, $\flats{\os} \PHPtrans[\oPH]^* \flats{\os'}$.
-
-  (\ref{ph2php}) Let $\os = \unflats{s}$.
-    Given the dynamics of a PH (\pref{def:play}), if $s \PHPtrans s'$,
-    then there exists $g \in \PHh$ playable in $s$; therefore, $s' = s \PHplay g$ and $\target{g} \in s$.
-    If $\prio(g) = 1$ then only the active process of a cooperative sort has evolved, and $\unflats{s} = \unflats{s'}$.
-    Otherwise, $\prio(g) = 2$; we note in this case: $g = \PHhit{f^{h,i}_\mysigma}{b_j}{b_k}$.
-    By construction of the flattening (\pref{def:flattening}), there exists $h \in \ov{\PHh}$ so that
-    $\target{h} = b_j$, $\bounce{h} = b_k$ and $\Fsem{\Fop{h}}{\mysigma}$.
-    If $g$ is playable, this means that no other action in $\PHh^{(1)}$ is playable, and especially the cooperative sort
-    $f^{h,i}$ is already updated; therefore, $\mysigma \subseteq \os$.
-    Furthermore, $b_j \in \os$.
-    Thus, by \pref{th:ppplaysubset}, it comes that $h$ is playable in $\os$,
-    and $\unflats{s} \PHPtrans \unflats{s'}$.
-\end{proofbisimPHP}
 

### 2014-04-03 parts/sa.tex
move proofs in appendix
remove a lot of comments

@@
 \subsection{Under-approximation}
+\label{ssec:ua}
 
@@
 
-\begin{comment}
-The reachability of a process $a_i$ is approximated by the ability to solve all objectives $\PHobjp{a}{j}{i}$ for all $a_j$ in the initial context.
-To this end, the abstractions of bounce sequences (\pref{def:aBS}) solving these objectives are computed, leading to new required processes, and thus new objectives on other sorts.
-Thus, the graph of local causality $\cwB = (\V, \E)$ defined in \pref{def:glc} is a graph where $\V \subset \Proc \cup \Obj \cup \Sol$ and $\E \subset \V \times \V$
-in which edges link any required process $a_i$ in $\Proc$ to all corresponding objectives $P$ in $\Obj$,
-and any objective $P$ to abstractions of bounce sequences $ps \in \Sol$ (\pref{def:aBS}) solving this objective;
-such sets $ps$ then stand for new required processes.
-In the case where a process $a_i$ belongs to a cooperative sort, it is directly linked to the set of the processes $\csState(a_i)$ (\pref{def:csState}) that it represents.
-If the solving of an objective $P$ requires a process of $\PHsort(P)$, a continuity edge is added to re-target this objective (\pref{def:maxCont}).
-Finally, as the active process of every sort may evolve, $\cwB$ is obtained iteratively by saturation with every process it contains,
-\ie by overriding its initial context $\ctx$ by $\allprocs(\V, \E)$, defined by:
-$$\allprocs(\V, \E) = (V \cap \Proc) \cup \{ \PHtarget(P), \PHbounce(P) \mid P \in \V \cap \Obj \}$$
-\end{comment}
-
 \begin{definition}
@@
 
-\begin{comment}
-\pref{eq:Vw}, \eqref{eq:Vproc} and \eqref{eq:VE} ensure that all required nodes are in $\cwV$.
-Elements in $\PHproc$ are required processes,
-elements in $\Obj$ are the objectives to reach these processes
-and elements in $\Sol$ are the sets of processes that allow to solve these objectives.
-\pref{eq:ESol1} links an objective $P$ to its solutions in $\BS(P)$
-and \pref{eq:ESol2} links a solution $ps$ to the processes $a_i \in ps$ it contains.
-Then, \pref{eq:EReq} links a required component process $a_i$ to all objectives $\PHobjp{a}{j}{i}$ with $a_j \in \ctx$
-while \pref{eq:EPrio} links a required cooperative sort process $a_i$ to its solutions in $\csState(a_i)$.
-Finally, if the resolution of an objective $P$ requires a process of $\PHsort(P)$, then \pref{eq:ECont} re-targets this objective ($\gCont$).
-\end{comment}
-
-In the graph of local causality, an edge $(p, ps) \in \Proc \times \Sol$ %linking a process of a cooperative sort to a solution set $ps$
+In the graph of local causality, an edge $(p, ps) \in \Proc \times \Sol$
 is said coherent (\pref{def:coherent}) if none of the processes in $ps$ conflict with the children processes of $ps$.
@@
 Checking the properties allowing to apply \pref{th:approxinf} is polynomial in the size of the graph.
-%Therefore, if the number of processes in each sort is small, the overall method can be processed in polynomial time.
 Furthermore, it is possible to compute only a subset of $\V \cap \Sol$;
@@
     and circle nodes are elements in $\Sol$.
-    %The double arrow and the two surrounding nodes represent the only edge in $\Proc \times \Sol$.
     \pref{th:approxinf} is inconclusive on this example as edge $(ab_{11}, \{ a_1, b_1 \}) \in \Proc \times \Sol$ (here represented with a double line) is not coherent (\pref{def:coherent}).

### 2014-04-03 parts/suppl-sa.tex
move proofs in appendix
remove a lot of comments

@@
-\section{Proof of Under-approximation (\pref{th:approxinf})}
+\section{Proof of Under-approximation (\pref{ssec:ua})}
 \label{suppl:demoapproxinf}
@@
 In the following, we denote:
-%$\BvProc = \Bv \cap \PHproc$, $\BvObj = \Bv \cap \Obj$ and $\BvSol = \Bv \cap \Sol$.
 $\Bee{X}{Y} = \Be \cap (X \times Y)$, with $X, Y$ amongst $\PHproc$, $\Obj$ and $\Sol$.
@@
 for all objective $P$ in $\Bv \cap \Obj$ so that $\PHtarget(P) \in s$,
-$\exists \delta \in \muconcr_s(P)$.% and $\ceil(\delta) \subseteq max\ctx$.
+$\exists \delta \in \muconcr_s(P)$.
 \begin{itemize}
@@
   \item Suppose all children objectives of $P$ are concretizable.
-%  \begin{itemize}
-    %\item 
     If $\exists (P, Q) \in \Bee{\Obj}{\Obj}$, then by hypothesis,
@@
       $\muconcr_{s}(P) \neq \emptyset$.
-    %\item 
     Else, by \pref{def:maxCont}, the concretizations of the children of $P$ require no process of sort $\PHsort(P)$.
@@
       Thus, $\delta_{|\zeta|} \in \muconcr_s(P)$. % and $\ceil(\delta) \subseteq max\ctx$.
-%  \end{itemize}
 \end{itemize}

### 2014-04-07 main.tex

@@
 %\newcommand{\towrite}[1]{\textcolor{darkgreen}{[#1]}}
-\newcommand{\todo}[1]{\textcolor{red}{\textbf{[#1]}}}
+%\newcommand{\todo}[1]{\textcolor{red}{\textbf{[#1]}}}
 
@@
 Asynchronous Discrete Networks, either Boolean or multivalued; and also any
-Process Hitting model with arbirtrary number of priorty classes.
+Process Hitting model with arbitrary number of priority classes.
 Then we develop a new refinement for the under-approximation of the static analysis to give accurate results for this class of Process Hitting models.
@@
 in Asynchronous Discrete Networks,
-as it is illustrated on the model-checking of a signaling network of 94
+as it is illustrated on the model-checking of a signalling network of 94
 components, which is unprecedented.

### 2014-04-07 parts/def-ph.tex

@@
   $\forall ps \in \PHsubl[\PHl], s \Cap \toset{ps} = s \underset{a_i \in \toset{ps}}{\Cap} a_i$.
-  %$\forall as \subseteq \PHs, \forall ps \in \underset{a \in as}{\times} \PHl_a, s \Cap ps = s \underset{a_i \in ps}{\Cap} a_i$.
 \end{definition}
@@
 
-In this subsection, we give several general lemmas that can be derived from the restrictions of \pref{ssec:hypothesis}, %(\pref{cr:bounded}, \ref{cr:cyclefreeness} \& \ref{cr:compcs})
+In this subsection, we give several general lemmas that can be derived from the restrictions of \pref{ssec:hypothesis},
 in the special case of a PH model with $2$ classes of priorities $\PH = (\PHs; \PHl; \PHa^{\langle 2 \rangle})$.

### 2014-04-07 parts/suppl-ph-dn.tex

--- 2014-03-03 parts/suppl-ph-dn.tex
@@
-% vim:set spell spelllang=en:
+\section{Proof of the Weak Bisimulation of Asynchronous Discrete Networks (\pref{sec:dn})}
+\label{suppl:proofbisimADN}
 
-\section{Weak Bisimulation of Asynchronous Discrete Networks (\pref{ssec:hypothesis})}
-\label{suppl:demotrad}
-
-We exhibit an encoding of Asynchronous Discrete Networks (ADN) with the Process
-Hitting using two classes of priorities, and prove a weak bisimulation relation.
-
-A Discrete Network gathers a finite number of components $i\in\segm{1}{n}$ having a discrete finite domain
-$\mathbb F^i$ that we note $\mathbb{F}^i = \segm{1}{l_i}$.
-For each component $i\in\segm{1}{n}$, a map $\mathbb F \rightarrow \mathbb F^i$ is defined, where
-$\mathbb F = \mathbb F^1 \times \cdots \times \mathbb F^n$, giving the next value of the component
-with respect to the global state of the network.
-Typically $f^i$ depends on a subset of components that we denote $\DNdep(f^i)$.
-In the case of Asynchronous Discrete Networks (ADN), a transition relation $\DNtrans\subseteq \mathbb
-F\times \mathbb F$ is defined such that $x\DNtrans x'$ if and only if there exists a unique
-$i\in\segm{1}{n}$ such that $\get{x'}{i}=f^i(x)$ and $\forall j\in\segm{1}{n}, j\neq i, \get{x'}{j}
-=\get{x}{j}$, \ie one and only one component has been updated.
-This is formalised in \pref{def:DN}.
-
-\begin{definition}[Asynchronous Discrete Network (ADN)]
-\label{def:DN}
-  An ADN is defined by a couple $(\mathbb F, \langle f^1, \dots, f^n \rangle)$
-  where $\mathbb{F} = \mathbb{F}^1\times\dots\times\mathbb{F}^n$,
-  and $\forall i\in\segm{1}{n}$,
-  $f^i: \mathbb{F} \rightarrow \mathbb{F}^i$ with
-  $\mathbb{F}^i = \segm{1}{l_i}$.
-  Given two states $x,x'\in\mathbb F$, the transition relation $\DNtrans$ is given by
-  \[
-  x\DNtrans x' \Longleftrightarrow
-    \exists i\in\segm{1}{n}, f^i(x)=\get{x'}{i}
-    \wedge \forall j\in\segm{1}{n}, j\neq i, \get{x}{j}=\get{x'}{j}
-  \enspace,
-  \]
-  where $\get{x}{i}$ is the $i$-th component of $x$.
-  %
-  We note $\DNdep(f^i)\subseteq \segm{1}{n}$ the set of components on which the value of $f^i$
-  depends: $\forall x,x'\in \mathbb F$ such that $\forall
-  j\in\DNdep(f^i), \get{x}{j}=\get{x'}{j}$, necessarily $f^i(x)=f^i(x')$.
-\end{definition}
-
-Let us denote the encoding of the ADN $\DNdef$ in Process Hitting with $2$ classes
-of priorities by $\toPH\DNdef$ (\pref{def:DN2PH}).
-For each component $i\in\segm{1}{n}$ of the ADN, two sorts are built: $a^i$ acting for the component
-value, and $f^i$ acting for a cooperative sort between the components $\DNdep(f^i)$.
-Sorts $a^i$ have one process $a^i_k$ per element in $k\in\mathbb F^i$.
-Sorts $f^i$ have one process $f^i_\varsigma$ per state $\varsigma \in \underset{j\in\DNdep(f^i)}{\times}
-\PHl_{a^j}$.
-Two classes of actions are then defined:
-$\Hits^{(1)}$ is the set of actions updating the cooperative sorts according to the current state of the
-components:
-if $j\in\DNdep(f^i)$, $a^j_k$ hits each process $f^i_\varsigma$ where $\get{\varsigma}{a^j}\neq
-a^j_k$ to make it bounce to the process $f^i_{\varsigma \Cap a^j_k}$.
-%$f^i_{\varsigma'}$ where $\get{\varsigma'}{a^j}=a^j_k$.
-$\Hits^{(2)}$ is the set of actions encoding the transitions in the ADN:
-$f^i_\varsigma$ hits the processes of sort $a^i$ to make them bounce to the process
-$a^i_{k'}$ if and only if $k'=f^i(\decode \varsigma)$;
-$\decode \varsigma$ being the ADN state corresponding to the PH (partial) state $\varsigma$ (note that
-$f^i(\decode \varsigma)$ is fully defined because $\decode \varsigma$ specifies the state for all
-the components in $\DNdep(f^i)$).
-
-\begin{definition}
-\label{def:DN2PH}
-  $\toPH\DNdef=(\Sigma,\PHl,(\Hits^{(1)},\Hits^{(2)}))$ is the Process Hitting with 2 classes of priority encoding the
-  ADN $\DNdef$, with:
-  \begin{itemize}
-    \item $\Sigma = \{ a^1, \dots, a^n \} \cup \{ f^1, \dots, f^n \}$,
-      the sorts for components ($a^i$) and cooperative sorts ($f^i$);
-
-    \item $\PHl=\underset{i\in\segm{1}{n}}{\times} \PHl_{a^i} \times \underset{i\in\segm{1}{n}}{\times} \PHl_{f^i}$, where
-      $\PHl_{a^i}=\{a^i_0, \dots, a^i_{l_i}\}$, and
-      $\PHl_{f^i}=\{f^i_\varsigma \mid \varsigma\in\underset{j\in\DNdep(f^i)}{\times} \PHl_{a^i} \}$
-      if $\DNdep(f^i)\neq\emptyset$, otherwise
-      $\PHl_{f^i}=\{f^i_\emptyset\}$;
-
-    \item $\Hits^{(1)}= \{ \hit{a^j_k}{f^i_\varsigma}{f^i_{\varsigma'}}
-      \mid i\in\segm{1}{n} \wedge
-      j\in\DNdep(f^i) \wedge a^j_k\in \PHl_{a^j} \wedge f^i_\varsigma\in \PHl_{f^i}
-      \wedge
-      \get{\varsigma}{a^j}\neq a^j_k 
-      \wedge \get{\varsigma'}{a^j}=a^j_k
-      \wedge (\get{\varsigma'}{a^{l}}=\get{\varsigma}{a^l},
-      \forall l\in\segm{1}{n},l\neq j)
-      \}$, 
-      the set of actions with priority $1$ that update cooperative sorts;
-
-    \item $\Hits^{(2)}=\{ \hit{f^i_\varsigma}{a^i_k}{a^i_{k'}} \mid i\in\segm{1}{n} \wedge
-          f^i_\varsigma\in \PHl_{f^i} \wedge
-          a^i_k\in \PHl_{a^i}\wedge k\neq k' \wedge f^i(\decode \varsigma) = k'
-        \}$,
-      the set of actions with priority $2$ for updating the components using their respective discrete
-      maps.
-      $\decode \varsigma$ is defined below.
-  \end{itemize}
-  Given a state $s\in \PHl$ of the Process Hitting, 
-  $\decode s=x$ is the corresponding state in the ADN:
-  $\forall i\in\segm{1}{n}, \get{s}{a^i}=a^i_k \Rightarrow \get{x}{i}=k$.
-
-  \noindent
-  Given a state $x\in \mathbb F$ of the ADN, 
-  $\encode x=s$ is the corresponding state in the Process Hitting:
-  $\forall i\in\segm{1}{n}, \get{x}{i}=k \Rightarrow \get{s}{a^i}=a^i_k$
-  and
-  $\forall i\in\segm{1}{n}, \get{s}{f^i}=f^i_\varsigma$ with $f^i_\varsigma\in \PHl_{f^i}$
-  and $\forall j\in\DNdep(f^i), \get{\varsigma}{j}=\get{s}{a^j}$.
-\end{definition}
-
-\pref{thm:bisimDN} states the weak bisimulation relation between an ADN and its encoding in
-PH with $2$ classes of priorities.
-Intuitively, actions updating cooperative sorts being prioritised, actions updating component
-sorts follow strictly the possible transitions of the ADN.
-
-\begin{theorem}[$\DNdef \approx \toPH\DNdef$]~
-\label{thm:bisimDN}
-  \begin{enumerate}
-    \item \label{adn2ph} $\forall x,x'\in\mathbb F$,
-      $x\DNtrans x' \Longrightarrow \encode x \PHPtrans^* \encode{x'}$,
-      where $\PHPtrans^*$ is a finite sequence of $\PHPtrans$ transitions.
-
-    \item \label{ph2adn} $\forall s,s'\in \PHl$,
-      $s\PHPtrans s' \Longrightarrow \decode s = \decode {s'} \vee \decode s \DNtrans
-      \decode{s'}\enspace.$
-  \end{enumerate}
-\end{theorem}
-\begin{proof}
+\newproof{proofbisimADN}{Proof of \pref{th:bisimDN}}
+\begin{proofbisimADN}
 (\ref{adn2ph}) From \pref{def:DN}, $x\DNtrans x'\Rightarrow \exists i\in\segm{1}{n},
@@
 $\decode s\DNtrans \decode{s'}$.
-\end{proof}
+\end{proofbisimADN}

### 2014-04-07 parts/suppl-ph-php.tex

@@
-\section{Proofs about flattening (\pref{ssec:flattening})}
+\section{Proof of the Weak Bisimulation of the Flattening (\pref{ssec:flattening})}
 \label{suppl:demoflattening}
+
+\newproof{proofbisimPHP}{Proof of \pref{th:bisimPHP}}
+\begin{proofbisimPHP}
+  (\ref{php2ph}) Let $\flats{\os} = s$.
+    Given the dynamics of a PH (\pref{def:play}), if $\os \PHPtrans[\PH] \os'$,
+    then there exists $h \in \ov{\PHh}$ playable in $\os$;
+    therefore, $\os' = \os \PHplay h$.
+    Thus, $\Fsem{\Fop{h}}{\os}$ and $\target{h} \in \os$,
+    and given \pref{lem:ppplaysubset}, there exists $\mysigma \subseteq s$ so that $\Fsem{\Fop{h}}{\mysigma}$.
+    Therefore, by construction of $\PH$ (\pref{def:flattening}) there exists
+    $g = \PHhit{f^{h,i}_\mysigma}{\target{h}}{\bounce{h}} \in \PHh^{(2)}$.
+    By construction of $s$ (\pref{def:flattening}), $\PHget{s}{f^{h,i}} = f^{h,i}_\mysigma$ and $\target{h} = \target{g} \in s$.
+    Therefore, $g$ is playable in $s$.
+    In $s \PHplay g$, the only playable actions are those in $\PHh^{(1)}$ having $\bounce{h} = \bounce{g}$ as hitter
+    and updating cooperative sorts, allowing to reach $\flats{\os'}$ in a finite number of actions.
+    Thus, $\flats{\os} \PHPtrans[\oPH]^* \flats{\os'}$.
+
+  (\ref{ph2php}) Let $\os = \unflats{s}$.
+    Given the dynamics of a PH (\pref{def:play}), if $s \PHPtrans s'$,
+    then there exists $g \in \PHh$ playable in $s$; therefore, $s' = s \PHplay g$ and $\target{g} \in s$.
+    If $\prio(g) = 1$ then only the active process of a cooperative sort has evolved, and $\unflats{s} = \unflats{s'}$.
+    Otherwise, $\prio(g) = 2$; we note in this case: $g = \PHhit{f^{h,i}_\mysigma}{b_j}{b_k}$.
+    By construction of the flattening (\pref{def:flattening}), there exists $h \in \ov{\PHh}$ so that
+    $\target{h} = b_j$, $\bounce{h} = b_k$ and $\Fsem{\Fop{h}}{\mysigma}$.
+    If $g$ is playable, this means that no other action in $\PHh^{(1)}$ is playable, and especially the cooperative sort
+    $f^{h,i}$ is already updated; therefore, $\mysigma \subseteq \os$.
+    Furthermore, $b_j \in \os$.
+    Thus, by \pref{lem:ppplaysubset}, it comes that $h$ is playable in $\os$,
+    and $\unflats{s} \PHPtrans \unflats{s'}$.
+\end{proofbisimPHP}

### 2014-04-07 parts/sa.tex
fix lastprocs
label for ordered ua
fixes in GLC + TODO: remove procs

@@
 \ie by overriding its initial context $\ctx$ by $\allprocs(\V, \E)$, defined by:
-$$\allprocs(\V, \E) = (V \cap \Proc) \cup \{ \PHtarget(P), \PHbounce(P) \mid P \in \V \cap \Obj \}$$
+%$$\allprocs(\V, \E) = (V \cap \Proc) \cup \{ \PHtarget(P), \PHbounce(P) \mid P \in \V \cap \Obj \}$$
+$\allprocs(\V, \E) = (V \cap \Proc)$.
+\todo{Remove $\allprocs$}
 
@@
     \w &\subseteq \cwV \label{eq:Vw} \\
-    P \in \VProc &\Rightarrow \PHbounce(P) \in \cwV \label{eq:Vproc} \\
-    (x, y) \in \E &\Rightarrow y \in \cwV \label{eq:VE} \\
-    P \in \VObj \wedge ps \in \BS(P) &\Rightarrow (P, ps) \in \cwE \label{eq:ESol1} \\
-    ps \in \VSol \wedge a_i \in ps &\Rightarrow (ps, a_i) \in \cwE \label{eq:ESol2} \\
-    a \in \components \wedge a_i \in \VProc \wedge a_j \in \ctx &\Rightarrow (a_i, \PHobjp{a}{j}{i}) \in \cwE \label{eq:EReq} \\
-    a \in \cs \wedge a_i \in \VProc \wedge ps \in \csState(a_i) &\Rightarrow (a_i, ps) \in \cwE \label{eq:EPrio} \\
-    P \in \VObj \wedge q \in \gCont_\ctx(\PHsort(P), P) &\Rightarrow (P, \PHobj{q}{\PHbounce(P)}) \in \cwE \label{eq:ECont} \!
+    P \in \cwVObj &\Rightarrow \PHbounce(P) \in \cwV \label{eq:Vproc} \\
+    (x, y) \in \cwE &\Rightarrow y \in \cwV \label{eq:VE} \\
+    P \in \cwVObj \wedge ps \in \BS(P) &\Rightarrow (P, ps) \in \cwE \label{eq:ESol1} \\
+    ps \in \cwVSol \wedge a_i \in ps &\Rightarrow (ps, a_i) \in \cwE \label{eq:ESol2} \\
+    a \in \components \wedge a_i \in \cwVProc \wedge a_j \in \ctx &\Rightarrow (a_i, \PHobjp{a}{j}{i}) \in \cwE \label{eq:EReq} \\
+    a \in \cs \wedge a_i \in \cwVProc \wedge ps \in \csState(a_i) &\Rightarrow (a_i, ps) \in \cwE \label{eq:EPrio} \\
+    P \in \cwVObj \wedge q \in \gCont_\ctx(\PHsort(P), P) &\Rightarrow (P, \PHobj{q}{\PHbounce(P)}) \in \cwE \label{eq:ECont} \!
   \end{align}
@@
 \subsection{Sequential under-approximation}
+\label{ssec:ordered-ua}
 
@@
 \begin{enumerate}
-\item $\{\hitter{\zeta_{\card\zeta}}\} \subset lps$;
+\item $a_j\in lps$;
+\item $\exists\zeta\in\BS(\obj{a_i}{a_j})$ s.t.
+ $\PHsort(\hitter{\zeta_{\card\zeta}}) \neq 
+		\PHsort(\bounce{\zeta_{\card\zeta}})
+		 \Rightarrow
+		  \hitter{\zeta_{\card\zeta}}\in lps$;
 \item $\forall b_j\in lps, b\in\cs, \exists ps\in\csState(b_j), ps\subset lps$;

### 2014-04-07 parts/example.tex
change footnote + personal address
reachability on the metazoan example

@@
 
+The static analysis results of \pref{ssec:ua} and \pref{ssec:ordered-ua} can be used to check if the model is functional, \ie
+if genes $a$ and $c$ are successively activated and deactivated,
+thus leading to the formation of regular stripes.
+Starting from context $\ctx = \PHstate{f_1, a_0, c_0}$,
+we want to check the reachability of
+$\w = \PHobj{a_0}{a_1} \PHconcat \PHobj{c_0}{c_1} \PHconcat \PHobj{a_1}{a_0} \PHconcat \PHobj{c_1}{c_0}$.
+Rather than checking this whole objective sequence,
+we decompose it into the following ones:
+\begin{align*}
+  \ctx^1 &= \PHstate{f_1, a_0, c_0} \text{ and } P_1 = \PHobj{a_0}{a_1} &
+  \ctx^3 &= \PHstate{f_1, a_1, c_1} \text{ and } P_2 = \PHobj{a_1}{a_0} \\
+  \ctx^2 &= \PHstate{f_1, a_1, c_0} \text{ and } P_3 = \PHobj{c_0}{c_1} &
+  \ctx^4 &= \PHstate{f_1, a_0, c_1} \text{ and } P_4 = \PHobj{c_1}{c_0}
+\end{align*}
+Given \pref{th:approxinf}, we have: $\forall i \in \segm{1}{4}, \muconcr_{\ctx^i}(P_i) \neq \emptyset$.
+Finally, after checking that it can be applied for $i = 3$ down to $i = 1$,
+\pref{thm:ordered-ua} gives: $\uconcr(\w) \neq \emptyset$.
+Thus the model is functional.
+
 \begin{figure}[htp]
@@
 The Boolean model has been automatically encoded into a Process Hitting with 2 classes of priority%
-\footnote{Model and scripts are available at
-\url{http://www.irccyn.ec-nantes.fr/~folschet/underapprox-tcrsig94.zip}.}.
+\footnote{Files are available at
+\url{http://maxime.folschette.name/underapprox-tcrsig94.zip}.}.
 Then, we verified the reachability for the independent activation of 4 outputs of the signalling

### 2014-04-11 parts/ccl.tex
fixes after Morgan's review

@@
 We also demonstrated that general Process Hitting models with arbitrary priority
-classes can also be encoded in the particular class of two-prioritized Process Hitting.
+classes can also be encoded in the particular class of two-prioritised Process Hitting.
 Therefore, our static analysis is applicable to a broad range of automata

### 2014-04-11 parts/def-ph.tex
fixes after Morgan's review

@@
   \end{align*}
-  There also is especially: $\{ \PHhit{ab_{11}}{c_0}{c_1}, \PHhit{a_1}{a_1}{a_0}, \PHhit{a_0}{b_0}{b_1} \} \subseteq \PHh^{(2)}$.
+  Note that: $\{ \PHhit{ab_{11}}{c_0}{c_1}, \PHhit{a_1}{a_1}{a_0}, \PHhit{a_0}{b_0}{b_1} \} \subseteq \PHh^{(2)}$.
 
@@
 This allows to gain the same expressivity in PH than in Boolean networks, as stated in \pref{sec:dn}.
-The aim of this paper is to allow the static analysis of the dynamics to be handled on PH models comprising such prioritised actions updating cooperative sorts.
+The aim of this paper is to allow the static analysis of the dynamics to be handled on PH models involving such prioritised actions updating cooperative sorts.
 
@@
 In the scope of this paper, we focus on a specific class of PH models
-in which actions of $\PHh^{(1)}$ are called \emph{prioritized actions} and allow to model non-biological actions.
+in which actions of $\PHh^{(1)}$ are called \emph{prioritised actions} and allow to model non-biological actions.
 We consider in this section a PH model with $k$ classes of priorities: $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$, with $k \in \sNN$
@@
 does comply with both definitions of well-formed components and well-formed cooperative sorts.
-In this case, such a sort can be arbitrarily affected to either of sets.
-Such case may occur for “input” sorts (which state is initially fixed and do not evolve)
-or some special cases of cooperative sorts produces by the translations of \pref{sec:encodings}.
+In this case, such a sort can be arbitrarily affected to either set.
+Such a case may occur for “input” sorts (whose state is initially fixed and does not evolve)
+or some special cases of cooperative sorts produced by the translations of \pref{sec:encodings}.
 

### 2014-04-11 parts/intro.tex
fixes after Morgan's review

@@
 consisting in a restriction where the evolution of a component is determined by the state of at most one other component that does not evolve.
-In a sense, these kind of actions are of the form $X + Y \rightarrow X + Y'$ where $X$ behaves like a catalyst molecule that “hits” another molecule $Y$ and changes it into $Y'$, without being itself changed.
+In a sense, these kind of actions are of the form $X + Y \rightarrow X + Y'$ where $X$ behaves like a catalyst molecule that “hits” another molecule $Y$ and changes it into $Y'$, without being changed itself.
 Assuming catalysts are always available, this can represent any biochemical system made of monomolecular reactions, and can also represent catalytic networks such as metabolic networks.
@@
 
-This paper is an extension of \cite{FPMR13-CS2Bio} were we
+This paper is an extension of \cite{FPMR13-CS2Bio} where we
 introduced a new extension to the semantics of Process Hitting by partitioning actions into classes of priorities
 (\pref{sec:ph}).
-One of the objectives is to reach an accurate representation of cooperating components in the model, that was not fulfilled with the initial semantics.
+One of the objectives is to reach an accurate representation of cooperating components in the model, that was not fulfilled with the initial semantics, using only two classes of priorities.
 In \pref{sec:sa},
@@
 thus overtaking the efficiency of usual model-checkers.
+
+The main additions in this paper compared to \cite{FPMR13-CS2Bio} are
+two theorems, the first
+stating that any Process Hitting model with any number of classes of priorities can be represented
+with only two classes of priorities,
+and the other giving a method to cope with successive reachability,
+both extending the application range of the static analysis we developed.
 

### 2014-04-11 parts/models-ph-php.tex
fixes after Morgan's review

@@
   \begin{itemize}
-    \item if $P = a_i \in \ov{\PHs}_a$ is an atom, with $a \in \ov{\PHs}$, then $\Fsem{a_i}{\mysigma}$ is true iff $a_i \in \mysigma$;
+    \item if $P = a_i \in \ov{\PHl}_a$ is an atom, with $a \in \ov{\PHs}$, then $\Fsem{a_i}{\mysigma}$ is true iff $a_i \in \mysigma$;
     \item if $P$ is not an atom, then $\Fsem{P}{\mysigma}$ is true iff all its subformulas are inductively true in $\mysigma$
@@
 \[\forall a \in \ov{\PHs}, \forall a_i \in \ov{\PHl}_a, \forall \mysigma \in \PHsubl,
-  \Fsem{\neg a_i}{\mysigma} \Leftrightarrow \Fsem{\bigvee_{\substack{a_j \in \PHl_a\\a_j \neq a_i}} a_j}{\mysigma}\]
+  \Fsem{\neg a_i}{\mysigma} \Leftrightarrow \Fsem{\bigvee_{\substack{a_j \in \ov{\PHl}_a\\a_j \neq a_i}} a_j}{\mysigma}\]
 Indeed, if a process is not active in a state, this means that another process of the same sort is active.
@@
 which are the sub-states given by $\csState$ to activate the hitter of the given action if it is a process of cooperative sort.
-Furthermore, the target of the action if not taken into account as it is not needed for the rest of the flattening.
-%\pref{th:ppplay} gives the condition for an action to be playable given its playability property.
+Furthermore, the target of the action is not taken into account as it is not needed for the rest of the flattening.
 %
@@
   \[\forall h \in \ov{\PHh}, \Fop{h} \equiv \virtualhitters(h) \wedge
-    \left( \bigwedge_{\substack{g \in \PHh^{(n)}\\n < \prio(h)}}
+    \left( \bigwedge_{\substack{g \in \ov{\PHh}^{(n)}\\n < \prio(h)}}
     \neg \left( \target{g} \wedge \hitter{g}\right) \right)\]
@@
 an action $h$ is playable in a state $s \in \ov{\PHl}$ if and only if: $\Fsem{\Fop{h}}{s} \wedge \target{h} \in s$.
-%%
-%\begin{theorem}
-%\label{th:ppplay}
-%  $h \in \ov{\PHh}$ is playable in $s \in \ov{\PHl}$ if and only if $\Fsem{\Fop{h}}{s} \wedge \target{h} \in s$.
-%\end{theorem}
-%%
-%\newproof{proofppplay}{Proof of \pref{th:ppplay}}
-%\begin{proofppplay}
-%  By definition of the semantics of a PH given in \pref{def:play}.
-%\end{proofppplay}
 
@@
   \[\target{h} \in s \wedge \exists \mysigma \subseteq s, \Fsem{\Fop{h}}{\mysigma} \enspace.\]
-%  \[\exists i \in \segm{1}{\n}, \exists \mysigma \in \bigtimes{b \in \PHdep{i}{h}} \PHl_b,
-%    \mysigma \subseteq s \wedge \Fsem{\F(h)}{\mysigma} \enspace.\]
 \end{lemma}
 %
-%\newproof{proofppplaysubset}{Proof of \pref{lem:ppplaysubset}}
-%\begin{proofppplaysubset}
 \begin{proof}
@@
     then we have: $\forall j \in \segm{1}{\m}, p_{i,j} \in s$.
-%    Let $\mysigma \in \bigtimes{b \in \PHdep{i}{h}} \PHl_b$
     Let $\mysigma \in \PHsubl_{\PHdep{i}{h}}$
@@
 \end{proof}
-%\end{proofppplaysubset}
 
@@
       h \in \ov{\PHh} \wedge
-      %\n \geq 1 \wedge i \in \segm{1}{\n} \wedge
       f^{h,i} \in \PHs_f \wedge
@@
       \PHget{\mysigma}{a} \neq a_k \wedge \mysigma' = \mysigma \Cap \{ a_k \} \}$;
-%      \todo{From here: ...} \PHget{\mysigma'}{a} = a_k \wedge
-%      (\forall b \in \PHdep{i}{h} \setminus \{ a \}, \PHget{\mysigma'}{b} = \PHget{\mysigma}{b}) \}$;
-%      \todo{... can be replaced by: $\mysigma' = \mysigma \Cap \{ a_k \}$}
     \item $\PHh^{(2)}=\{ \PHhit{f^{h,i}_\mysigma}{\target{h}}{\bounce{h}} \mid

### 2014-04-11 parts/sa.tex
restore procs
fix (again) def of lastprocs
minor fix in lastprocs
remove last minor fix in lastprocs
fixes after Morgan's review

@@
 \begin{definition}[$\concr: \OS \to \powerset(\Sce)$]\label{def:concr}
-Given $\w\in\OS$, $\concr(\w)$ is the set of minimal scenarios concretizing $\w$ in the
+Given $\w\in\OS$, $\concr(\w)$ is the set of minimal scenarios concretising $\w$ in the
 context $\ctx$. It is defined as the largest set satisfying the following conditions:
@@
 \ie by overriding its initial context $\ctx$ by $\allprocs(\V, \E)$, defined by:
-%$$\allprocs(\V, \E) = (V \cap \Proc) \cup \{ \PHtarget(P), \PHbounce(P) \mid P \in \V \cap \Obj \}$$
-$\allprocs(\V, \E) = (V \cap \Proc)$.
-\todo{Remove $\allprocs$}
+\[\allprocs(\V, \E) = (V \cap \Proc) \cup \{ \PHtarget(P), \PHbounce(P) \mid P \in \V \cap \Obj \} \enspace.\]
 
@@
 In the graph of local causality, an edge $(p, ps) \in \Proc \times \Sol$
-is said coherent (\pref{def:coherent}) if none of the processes in $ps$ conflict with the children processes of $ps$.
-Then, \pref{th:approxinf} gives a sufficient condition for the concretization of a sequence of objectives in a given context,
+is said to be coherent (\pref{def:coherent}) if none of the processes in $ps$ conflict with the children processes of $ps$.
+Then, \pref{th:approxinf} gives a sufficient condition for the concretisation of a sequence of objectives in a given context,
 which is derived immediately from the graph of local causality.
@@
 \label{def:coherent}
-  An edge $(x, y) \in \cwE$ is said coherent if and only if:
+  An edge $(x, y) \in \cwE$ is said to be coherent if and only if:
   $(x, y) \in \Be \cap (\Proc \times \Sol) \Rightarrow y$ has no children process $a_j \in \Bv \cap \Proc$ so that $\exists a_i \in y$, $a_i \neq a_j$.
@@
 
-Given an initial context $\ctx$, the reachability of $s$ in $\PH$ is equivalent to the concretization of $\PHobjp{\reach}{0}{1}$ in $\PH'$ from the initial context $\ctx \cup \{ \reach_0 \}$ (the initial state of $\total$ does not matter), which can be efficiently under-approximated using \pref{th:approxinf}.
+Given an initial context $\ctx$, the reachability of $s$ in $\PH$ is equivalent to the concretisation of $\PHobjp{\reach}{0}{1}$ in $\PH'$ from the initial context $\ctx \cup \{ \reach_0 \}$ (the initial state of $\total$ does not matter), which can be efficiently under-approximated using \pref{th:approxinf}.
 Indeed, the additional action $\PHhit{\pfp_s(\total)}{\reach_0}{\reach_1}$ in $\PHh'^{(2)}$ allows to conclude on the reachability of process $\pfp_s(\total)$, that is, on the reachability of the state $s$ (considering only the components).
@@
 with $\ctx'=\ctx\Cap\procs(\mycwB{\ctx}{P})$,
-there exists a scenario $\delta'$ concretizing $\w'$ from the
+there exists a scenario $\delta'$ concretising $\w'$ from the
 state $(s\play\delta)$.
-Therefore, the scenario $\delta\concat\delta'$ concretizes
+Therefore, the scenario $\delta\concat\delta'$ concretises
 $\w$.
@@
 \Obj\to\powerset(\powerset(\Proc))$ is
-defined such that, $\forall lps\in\lastprocs(\obj{a_i}{a_j})$, 
+defined as the largest set such that, $\forall lps\in\lastprocs(\obj{a_i}{a_j})$, 
 $lps\in\powerset(\Proc)$,
@@
 \item $a_j\in lps$;
-\item $\exists\zeta\in\BS(\obj{a_i}{a_j})$ s.t.
- $\PHsort(\hitter{\zeta_{\card\zeta}}) \neq 
+\item $\exists\zeta\in\BS(\obj{a_i}{a_j}),
+    \PHsort(\hitter{\zeta_{\card\zeta}}) \neq 
 		\PHsort(\bounce{\zeta_{\card\zeta}})
@@
 \item $\forall b_j\in lps, b\in\cs, \exists ps\in\csState(b_j), ps\subset lps$;
-\item $\forall b_j\in lps, b\in\cs, 
-		\forall ps\in\csState(b_j),
-			\exists lps'\in\lastprocs(\obj{a_i}{a_j}),
-				ps\subset lps'$;
 \item $\nexists lps'\in\lastprocs(\obj{a_i}{a_j}), lps'\subset lps \wedge
@@
 Therefore, for all $s\in \PHl, s\subset\ctx$, there exists a scenario
-concretizing $\w$.
+concretising $\w$.
 Hence, $\uconcr(\w)\neq\emptyset$.

### 2014-04-11 parts/suppl-sa.tex
fixes after Morgan's review

@@
 
-  \item Suppose all children objectives of $P$ are concretizable.
+  \item Suppose all children objectives of $P$ are concretisable.
     If $\exists (P, Q) \in \Bee{\Obj}{\Obj}$, then by hypothesis,
@@
       $\muconcr_{s}(P) \neq \emptyset$.
-    Else, by \pref{def:maxCont}, the concretizations of the children of $P$ require no process of sort $\PHsort(P)$.
+    Else, by \pref{def:maxCont}, the concretisations of the children of $P$ require no process of sort $\PHsort(P)$.
       Furthermore, there exists $\zeta \in \BS(P)$ so that $(P, \aZ) \in \Bee{\Obj}{\Sol}$.

### 2014-04-14 main.tex
fixes in GLC + TODO: remove procs
add 'References' title
minor rewriting of abstract and intro (additions compared to [12])

@@
 %\newcommand{\towrite}[1]{\textcolor{darkgreen}{[#1]}}
-%\newcommand{\todo}[1]{\textcolor{red}{\textbf{[#1]}}}
+\newcommand{\todo}[1]{\textcolor{red}{\textbf{[#1]}}}
 
@@
 In this paper, we focus on a restriction of the Process Hitting with two classes of priorities and a specific behaviour of the components, that is sufficient to tackle the aforementioned problem of cooperations.
-We show that this class of Process Hitting models allows to represent any
-Asynchronous Discrete Networks, either Boolean or multivalued; and also any
-Process Hitting model with arbitrary number of priority classes.
-Then we develop a new refinement for the under-approximation of the static analysis to give accurate results for this class of Process Hitting models.
+We develop a new refinement for the under-approximation of the static analysis to give accurate results for this class of Process Hitting models.
+Then we show that this class of models is sufficient to represent any
+Process Hitting model with an arbitrary number of classes of priorities,
+and even any Asynchronous Discrete Networks, either Boolean or multivalued.
 Our method thus allows to efficiently under-approximate reachability properties
@@
 
+\section*{References}
 \bibliographystyle{elsarticle-num}

### 2014-04-14 parts/intro.tex
minor rewriting of abstract and intro (additions compared to [12])

@@
 with only two classes of priorities,
-and the other giving a method to cope with successive reachability,
-both extending the application range of the static analysis we developed.
+and the other giving a method to cope with successive reachability.
+Both aim at extending the application range of the static analysis we developed.
 

### 2014-04-14 parts/intro.tex
add internal refs to the new theorems in intro (additions compared to [12])

@@
 The main additions in this paper compared to \cite{FPMR13-CS2Bio} are
-two theorems, the first
-stating that any Process Hitting model with any number of classes of priorities can be represented
-with only two classes of priorities,
-and the other giving a method to cope with successive reachability.
+%two theorems, the first
+\pref{thm:ordered-ua} that gives a method to cope with successive reachability,
+and %the second
+\pref{th:bisimPHP} which states that any Process Hitting model with any number of classes of priorities
+can be represented with only two classes of priorities.
 Both aim at extending the application range of the static analysis we developed.

### 2014-12-08 parts/sa.tex
add TODOs after review
some more explanations in static analysis

@@
 \section{Static Analysis}\label{sec:sa}
+
+\todo{Replacer notre méthode par rapport aux méthodes d'interprétation abstraite en général}
+
+\todo{Gluer : explication des définitions, etc.}
 
@@
 that respects all Conditions (\ref{cr:bounded} \& \ref{cr:compcs}) of \pref{ssec:hypothesis}.
+
+\medskip
+
+\modMF{
+The main idea behind the static analysis presented in this section
+is to abstract the dynamics of a Process Hitting model
+by a more general and easier to analyse dynamics.
+For this, we focus on the notion of objective:
+an objective is a couple of processes (\eg $\PHobj{a_i}{a_j}$) whose reachability
+is required to ensure the global reachability property considered;
+in other words, it is required that a set of actions hitting $a$ exists so that,
+starting from a state containing $a_i$,
+it is possible to play these actions (possibly intertwined with other actions)
+and reach a state containing $a_j$.
+Given the particular form of the actions in Process Hitting,
+the solving of such an objective raises new objectives in the general case,
+because each action can be triggered by (at most) one process from a different sort.
+Indeed, each of these processes also have to be reached before the required actions are played.
+However, the order of the considered actions is abstracted,
+and so is the order of the related objectives,
+thus resulting in an over-approximation of the requirements.
+}
 
@@
 
-A context (\pref{def:context}) extends the notion of state to a set of possible initial states.
+A context (\pref{def:context}) extends the notion of state to a set of possible initial states:
+\modMF{
+to each sort in the model, a context maps a set of processes in this sort.
+}
 We also extend the override operator to contexts (\pref{def:ctxcap}).
@@
 in which the bounce process of each action is the hitter process of the following action.
-Bounce sequences are used to find local solutions to a given objective.
-A bounce sequence on $a$ can be abstracted into sets of all its hitters that are not in sort $a$ (\pref{def:aBS}).
-This abstraction allows to propagate an objective on the sort $a$ into objectives on other sots.
+Bounce sequences are used to find local solutions to a given objective:
+\modMF{
+indeed, the bounce sequences related to an objective $\PHobj{a_i}{a_j}$
+only take depend on the bounces of the actions hitting the sort $a$.
+}%
+A bounce sequence on $a$ can be abstracted into the minimal sets of its hitters that are not in sort $a$ (\pref{def:aBS}).
+This abstraction is later used to propagate an objective on a given sort
+by creating new objectives on other sots.
 In the following, we denote: $\Sol = \powerset(\PHproc)$.
@@
   \]
-  $\BS(\obj{a_i}{a_j}) = \emptyset$ if there is no way to reach $a_j$ from $a_i$ and $\emptyseq \in \BS(\obj{a_i}{a_i})$.
+  $\BS(\obj{a_i}{a_j}) = \emptyset$ if there is no way to reach $a_j$ from $a_i$
+  and $\emptyseq \in \BS(\obj{a_i}{a_i})$
+  \modMF{
+  for a trivial objective $\PHobj{a_i}{a_i}$.
+  }
 \end{definition}
@@
   \]
-  where $\abstr{\zeta} \DEF \{ \PHhitter(\zeta_n) \mid  n \in \indexes{\zeta} \wedge \PHsort(\PHhitter(\zeta_n)) \neq \PHsort(P) \}$.
+  \modMF{
+  where $\forall P \in \Obj, \forall \zeta \in \BS(P)$:
+  \[
+    \abstr{\zeta} \DEF \{ \PHhitter(\zeta_n) \mid
+    n \in \indexes{\zeta} \wedge \PHsort(\PHhitter(\zeta_n)) \neq \PHsort(P) \}
+  \]
+  }%
 \end{definition}
@@
 \begin{enumerate}[(i)]
-\item $\forall\delta\in\concr(\w), \exists s\subseteq\ctx, \delta\in\Sce(s)$
+\item $\forall\delta\in\concr(\w), \modMF{\delta\in\Sce(\ctx)}$
 \item $\forall\delta\in\concr(\w),
@@
   \[
+  \modMF{\forall \w \in \OS,}
   \uconcr(\w) \DEF

### 2014-12-08 parts/example.tex
typos/errors

@@
 
+\todo{Le résultat peut être raffiné avec l'atteignabilité successive}
+
 \begin{figure}[htp]
@@
 Then, we verified the reachability for the independent activation of 4 outputs of the signalling
-cascade (SRE, AP1, NFkB, NFAT) from all possible input combinations (CD45, CD28, TCRlib) using our
+cascade (SRE, AP1, NFkB, NFAT) from all possible input combinations (CD4, CD28, TCRlig) using our
 new reachability under-approximation (answering either \emph{yes} or \emph{inconclusive}) and a 

### 2014-12-08 parts/models-ph-php.tex
typos/errors

@@
   \[\forall h \in \ov{\PHh}, \Fop{h} \equiv \virtualhitters(h) \wedge
-    \left( \bigwedge_{\substack{g \in \ov{\PHh}^{(n)}\\n < \prio(h)}}
+    \left( \bigwedge_{\substack{g \in \ov{\PHh}^{(n)}\\\modMF{1 <} n < \prio(h)}}
     \neg \left( \target{g} \wedge \hitter{g}\right) \right)\]
@@
   \item if the $i$\textsuperscript{th} conjunction of $\Fop{h}$ consists of only one element $p$,
-    then $h$ can be translated as a regular action $\PHhit{p}{\target{h}}{\bounce{h}}$ instead of a cooperative sort
+    then \modMF{this conjunction} can be translated as a regular action $\PHhit{p}{\target{h}}{\bounce{h}}$ instead of a cooperative sort
     (as, apart from the target, only one process is required).

### 2014-12-10 parts/def-ph.tex
add TODOs after review
more explanations in section PH

@@
 \label{sec:ph}
+
+\todo{Gluer : explication des définitions, etc.}
 
@@
 
+\todo{Rajouter un exemple}
+
 Cooperation between processes to make another process bounce can be expressed in PH by building a \emph{cooperative sort}, as described in \cite{PMR10-TCSB}.
@@
 In the scope of this paper, we focus on a specific class of PH models
-in which actions of $\PHh^{(1)}$ are called \emph{prioritised actions} and allow to model non-biological actions.
+in which actions of $\PHh^{(1)}$, called \emph{prioritised actions},
+are only used to model cooperations in the form of strict logic gates.
+\modMF{%
+For this, we formally define in this section the notion of well-formed cooperative sorts,
+and we require that prioritized actions can only be used to update them.
+This particular form in the actions allows to apply the static analysis
+developed in \pref{sec:sa}, which is not directly possible in the general case.
+However, we note here that this class of models is not less expressive than
+the general PH framework as given in \pref{def:ph};
+indeed, the translation given in \pref{ssec:flattening} proves that
+this class of models can reproduce any desired dynamics of the general case.
+}%
+
 We consider in this section a PH model with $k$ classes of priorities: $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$, with $k \in \sNN$
@@
 
-\pref{cr:bounded} states that the dynamics of the studied model $\PH$ contains no infinite sequence of prioritised actions.
+\pref{cr:bounded} states that the dynamics of the studied model $\PH$ contain no infinite sequence of prioritised actions.
 As these actions can be considered as non-biological and therefore instantaneous, we thus prevent the existence of any Zeno-like behaviour
@@
 
+\modMF{%
+\begin{example}
+  The model of \pref{fig:ph-livelock} respects \pref{cr:bounded}:
+  indeed, whatever are the active processes of $a$ and $b$,
+  it is never possible to indefinitely play actions of $\PHh^{(1)}$.
+\end{example}
+}%
+
 Given a sort $a\in\Sigma$ and a state $s\in L$, 
@@
 which is always defined because of \pref{cr:bounded}.
+\modMF{%
+This definition will be useful for cooperative sorts,
+in order to determine their local stable state in every configuration,
+and thus which configuration each of their processes represent.
+}%
 
@@
 
+\modMF{%
+\begin{example}
+  In the model of \pref{fig:ph-livelock}, we have for instance:
+  $\pfp_{s}(ab) = \{ab_{10}\}$ for the state $s = \PHstate{a_1, b_0, ab_{00}, z_0}$.
+  Indeed, starting from $\PHstate{a_1, b_0, ab_{00}, z_0}$,
+  it is only possible to play the action $\PHfrappe{a_1}{ab_{00}}{ab_{10}} \in \PH^{(1)}$,
+  and no other action in $\PH^{(1)}$ is playable in the resulting state
+  $\PHstate{a_1, b_0, ab_{10}, z_0}$.
+  Thus, process $ab_{10}$ can be used to represent the configuration $\PHstate{a_1, b_0}$.
+\end{example}
+}%
+
 Our second condition (\pref{cr:compcs}) imposes that any sort in the Process
@@
 (\pref{def:cs}).
-The former is a sort that is hit only by actions with priority greater than $2$.
+The former is a sort that is hit only by actions with priority greater than $2$,
+\modMF{%
+and thus stands for a regular biological component.
+}%
 The latter is a sort that is hit only by actions with priority $1$ and which
@@
 that have an influence on it (\pref{def:conn}).
+\modMF{%
+Indeed, we require that each process of a cooperative sort corresponds
+to exactly one configuration of the sorts it represents.
+}%
 We note $\components\subset\Sigma$ the set of well-formed components,
@@
 
+\modMF{%
+\begin{example}
+  For the PH model of \pref{fig:ph-livelock}, we have:
+  \begin{align*}
+    \conn(a) &= \{a\} &
+    \conn(ab) &= \{a, b, ab\} \\
+    \conn(b) &= \{b\} &
+    \conn(z) &= \{z\}
+  \end{align*}
+  Therefore, $\compin(ab) = \{a, b\}$.
+\end{example}
+}%
+
 \begin{definition}[Well-formed cooperative sorts ($\cs$)]
@@
 
-We note that a sort $a$ that is hit by no action (\ie $\forall h \in \PHh, \PHsort(\target{h}) \neq a$)
+\modMF{%
+\begin{example}
+  The sorts $a$, $b$ and $z$ of \pref{fig:ph-livelock} are well-formed components
+  regarding \pref{def:component}.
+  Furthermore, $ab$ of is a well-formed cooperative sort,
+  with respect to \pref{def:cs}, which models cooperation between $a$ and $b$
+  because $\compin(ab) = \{a, b\}$ and:
+  \begin{enumerate}[(i)]
+    \item it is only hit by actions in $\PH^{(1)}$;
+    \item in every state, it has exactly one focal process;
+    \item each of its processes corresponds to at least one state of the model;
+    \item its focal processes only depend on $a$ and $b$.
+  \end{enumerate}
+  Therefore, we obviously have:
+  $\components = \{a, b, z\}$ and $\cs = \{ab\}$,
+  which respects \pref{cr:compcs}.
+\end{example}
+}
+
+We note that any sort $a$ that is hit by no action (\ie $\forall h \in \PHh, \PHsort(\target{h}) \neq a$)
 does comply with both definitions of well-formed components and well-formed cooperative sorts.
@@
 or some special cases of cooperative sorts produced by the translations of \pref{sec:encodings}.
+In the following we simply write “component” (\resp “cooperative sort”) instead of “well-formed component” (\resp “well-formed cooperative sort”).
 
@@
 
-In the following we simply write “component” (\resp “cooperative sort”) instead of “well-formed component” (\resp “well-formed cooperative sort”).
-
+\modMF{%
 \begin{example}
-  The PH in \pref{fig:ph-livelock} contains three components ($a$, $b$ and $c$) and a cooperative sort ($ab$, which models cooperation between sorts $a$ and $b$).
+  We have, for the cooperative sort $ab$ of \pref{fig:ph-livelock}
+  $\csState(ab_{10}) = \{\{a_1, b_0\}\}$,
+  which is a direct consequence of the fact that $\pfp_{s}(ab) = \{ab_{10}\}$
+  with $s = \PHstate{a_1, b_0, ab_{00}, z_0}$.
 \end{example}
+}%
 
@@
 
-We first denote by $\update(s)$ the state equivalent to $s$ but in which all cooperative sorts are updated (\pref{def:update}).
+We first denote by $\update(s)$ (\pref{def:update}) the state equivalent to $s$
+\modMF{%
+but in which the active process of all cooperative sorts is changed to the process
+that represent the current state of the components.
+}%
 This state is unique due to the properties of $\pfp$ given in the previous subsection.
-Then, \pref{lem:update} states that from any state, there exists a scenario updating the cooperative sorts of this state.
-%
+Then, \pref{lem:update} states that from any state, there exists a scenario updating the cooperative sorts of this state,
+\modMF{%
+thus allowing to end in $\update(s)$.
+}%
+
 \begin{definition}[$\update : \PHl \rightarrow \PHl$]
@@
 
+\modMF{%
+\begin{example}
+  Regarding the model of \pref{fig:ph-livelock}, we have:
+  $\update(s) = \PHstate{a_1, b_0, ab_{10}, z_0}$,
+  with $s = \PHstate{a_1, b_0, ab_{00}, z_0}$.
+  We note that in $\update(s)$, only the active process of the cooperative sort
+  $ab$ is changed
+  to the process representing the presence of both $a_1$ and $b_0$.
+  Furthermore, \pref{lem:update} states that there exists a scenario $\delta$
+  of actions in $\PH^{(1)}$
+  so that $s \play \delta = \update(s)$.
+  Indeed, $\delta = (\PHfrappe{a_1}{ab_{00}}{ab_{10}})$ is such a scenario,
+  here containing only one action.
+\end{example}
+}%
+
 \pref{lem:hcompcomp} states that for a given state $s$, and for any action $h = \PHhit{a_i}{b_j}{b_k}$ where $a$ and $b$ are components,
@@
 \pref{lem:hcscomp} states the same if $a$ is a cooperative sort, under the condition that $a$ is updated in $s$.
+In other words, prioritized actions cannot prevent a non-prioritized action
+to be eventually played, they only ``delay'' it,
+provided only that the hitter of this action
+matches the active process in the updated state.
+
 \begin{lemma}
@@
 \end{proof}
+
+\modMF{%
+\begin{example}
+  Considering the model of \pref{fig:ph-livelock} and starting from the state
+  $s = \PHstate{a_1, b_0, ab_{00}, z_0}$,
+  \pref{lem:hcompcomp} states that the action $h = \PHfrappe{a_1}{a_1}{a_0}$
+  is playable after a scenario $\delta$ of prioritized actions.
+  In this case, $h$ is indeed playable in the state
+  $s \play \delta = \PHstate{a_1, b_0, ab_{10}, z_0}$,
+  where $\delta = (\PHfrappe{a_1}{ab_{00}}{ab_{10}}) \in \restriction{\Sce}{1}(s)$.
+\end{example}
+}%
+
+\medskip
+
+\modMF{%
+This section aimed at defining the PH framework in a general fashion,
+and focused on a more specific class of PH models
+that will be used later in this paper.
+We gave a definition of the notion of cooperative sort,
+a special sort with no explicit biological existence or meaning,
+which is used to model the joint action of several components
+on another one.
+Using this definition, we defined a specific class of PH models
+that assign a specific role to the set of actions
+of highest priority:
+these actions can only be used to update cooperative sorts to ensure that
+they are equivalent to Boolean gates.
+The static analysis developed in the next section can only be applied
+to PH models belonging to this specific class.
+However, it has to be noted that this class is in fact as expressive as
+the class of all possible PH models with priorities (see \pref{ssec:flattening}).
+}%

### 2014-12-11 parts/sa.tex
begin extraction of the scenario

@@
     (x, y) \in \cwE &\Rightarrow y \in \cwV \label{eq:VE} \\
-    P \in \cwVObj \wedge ps \in \BS(P) &\Rightarrow (P, ps) \in \cwE \label{eq:ESol1} \\
+    P \in \cwVObj \wedge ps \in \modMF{\aBS}(P) &\Rightarrow (P, ps) \in \cwE \label{eq:ESol1} \\
     ps \in \cwVSol \wedge a_i \in ps &\Rightarrow (ps, a_i) \in \cwE \label{eq:ESol2} \\
@@
 \end{proof}
+
+\modMF{
+\subsection{Extraction of the scenario}
+}
+
+\modMF{
+This section gives a recursive method to find a scenario that concretizes
+a given objective sequence $\w \in \OS$.
+All the definitions above are well-defined provided that
+$\uconcr(\w)\neq\emptyset$,
+which can be demonstrated by \pref{thm:ordered-ua} or \pref{th:approxinf}.
+The justification of these definitions can be found by analysing the demonstrations
+of these theorems.
+}
+
+\newcommand{\res}{\mathbf{res}}
+\newcommand{\osres}{\mathbf{OSres}}
+\newcommand{\autoBS}{\mathbf{autoBS}}
+\newcommand{\rec}{\mathbf{rec}}
+\newcommand{\thisobj}[1]{P_{#1}}
+\newcommand{\thisseq}[1]{\Theta_{#1}}
+
+\modMF{
+For all $\w \in \OS$:
+\[
+  \osres_s(\w) = \res_s(\w_1) \concat
+    \osres_{s \play \res_s(\w_1)}(\w_2 \concat \dots \concat \w_{\card{\w}})
+\]
+with $\osres_s(\varepsilon) = \varepsilon$.
+For all $P \in \Obj$:
+\[\res_s(P) =
+  \begin{cases}
+    \varepsilon
+      & \text{if } \target{P} = \bounce{P} \\
+%     pickone(\autoBS(P))
+%       & \text{if } \aBS(P) = \{ \emptyset \} \\
+    \osres_s(P^Q \concat Q)
+      & \text{if } \exists Q \in \Obj, (P, Q) \in \Bee{\Obj}{\Obj} \\
+    \rec_s(\zeta)
+      & \text{otherwise, with } \zeta \in \BS(P)
+  \end{cases}
+\]
+where:
+\[
+  \autoBS(P) = \{ \zeta \in \BS(P) \mid \forall i \in \indexes{\zeta}, \PHsort(\hitter{\zeta_i}) = \PHsort(\target{\zeta_i}) = \PHsort(P) \}
+\]
+\[
+  P^Q = \PHobj{\PHtarget(P)}{\PHtarget(Q)}
+\]
+\[
+  \rec_s(\zeta) = \thisseq{\zeta_1} \play
+    \rec_{s \play \thisseq{\zeta_1}}
+    (\zeta_2 \concat \dots \concat \zeta_{\card{\zeta}})
+\]
+with:
+\[
+  \thisseq{h} = \res_s(\thisobj{h}) \play
+    \delta^{upd}_{s \play \res_s(\thisobj{h})} \play h
+\]
+\[
+  \thisobj{h} = \PHobj{\PHget{s}{\PHsort(\hitter{h})}}{\hitter{h}}
+\]
+and $\delta^{upd}_{s'}$ is a scenario of actions in $\PHh^{(1)}$ that updates
+all cooperative sorts from state $s'$.
+Such a scenario always exists given \pref{lem:update},
+and it can be built, starting from $s'$
+by iteratively putting arbitrary prioritized actions into a sequence
+until no more prioritized action is playable.
+Indeed, the order of the actions do not matter and the final state will
+always be $\update(s')$.
+}
+
+\todo{À terminer et gluer}

### 2014-12-12 parts/example.tex
add sets of actions

@@
 
-The actions of the original model make $3$ classes of priorities, as represented in \pref{fig:metazoan-php}.
+The actions of the original model make $3$ classes of priorities, as represented in \pref{fig:metazoan-php}
+and listed in \pref{tab:metazoan-php-actions}.
 Thus, although the actions of the highest class of priority are only used to update a cooperative sort,
@@
 
-\begin{figure}[htp]
+\begin{figure}[p]
   \centering
@@
 
-\pref{fig:metazoan-ph} gives the flattening of this model.
+\begin{table}[p]
+\modMF{
+\begin{align*}
+  \PHh^{(1)} = \{ \quad
+    & \PHfrappe{f_1}{fc_{00}}{fc_{10}} \quad , \quad
+    \PHfrappe{f_1}{fc_{01}}{fc_{11}} \quad , \\
+    & \PHfrappe{f_0}{fc_{10}}{fc_{00}} \quad , \quad
+    \PHfrappe{f_0}{fc_{11}}{fc_{01}} \quad , \\
+    & \PHfrappe{c_1}{fc_{00}}{fc_{01}} \quad , \quad
+    \PHfrappe{c_1}{fc_{10}}{fc_{11}} \quad , \\
+    & \PHfrappe{c_0}{fc_{01}}{fc_{00}} \quad , \quad
+    \PHfrappe{c_0}{fc_{11}}{fc_{10}}
+  \quad \} \\
+  \PHh^{(2)} = \{ \quad
+    & \PHfrappe{c_1}{a_1}{a_0} \quad , \quad
+    \PHfrappe{fc_{10}}{a_0}{a_1}
+  \quad \} \\
+  \PHh^{(3)} = \{ \quad
+    & \PHfrappe{c_1}{c_1}{c_0} \quad , \quad
+    \PHfrappe{f_1}{c_0}{c_1}
+  \quad \} \\
+\end{align*}%
+}%
+  \caption{\label{tab:metazoan-php-actions}%
+    Sets of actions of the metazoan segmentation model depicted
+    in \pref{fig:metazoan-php}.
+  }
+\end{table}
+
+\pref{fig:metazoan-ph} gives the flattening of this model,
+\modMF{
+whose actions are detailed in \pref{tab:metazoan-ph-actions}.
+}%
 It contains $2$ classes of priority, and prioritised actions are only used to update cooperative sorts.
@@
 
+\begin{table}[p]
+\modMF{
+\begin{align*}
+  \PHh^{(1)} = \{ \quad
+    & \PHfrappe{f_1}{fc_{00}}{fc_{10}} \quad , \quad
+    \PHfrappe{f_1}{fc_{01}}{fc_{11}} \quad , \\
+    & \PHfrappe{f_0}{fc_{10}}{fc_{00}} \quad , \quad
+    \PHfrappe{f_0}{fc_{11}}{fc_{01}} \quad , \\
+    & \PHfrappe{c_1}{fc_{00}}{fc_{01}} \quad , \quad
+    \PHfrappe{c_1}{fc_{10}}{fc_{11}} \quad , \\
+    & \PHfrappe{c_0}{fc_{01}}{fc_{00}} \quad , \quad
+    \PHfrappe{c_0}{fc_{11}}{fc_{10}} \quad , \\
+    & \PHfrappe{f_1}{fa_{00}}{fa_{10}} \quad , \quad
+    \PHfrappe{f_1}{fa_{01}}{fa_{11}} \quad , \\
+    & \PHfrappe{f_0}{fa_{10}}{fa_{00}} \quad , \quad
+    \PHfrappe{f_0}{fa_{11}}{fa_{01}} \quad , \\
+    & \PHfrappe{a_1}{fa_{00}}{fa_{01}} \quad , \quad
+    \PHfrappe{a_1}{fa_{10}}{fa_{11}} \quad , \\
+    & \PHfrappe{a_0}{fa_{01}}{fa_{00}} \quad , \quad
+    \PHfrappe{a_0}{fa_{11}}{fa_{10}}
+  \quad \} \\
+  \PHh^{(2)} = \{ \quad
+    & \PHfrappe{c_1}{a_1}{a_0} \quad , \quad
+    \PHfrappe{fc_{10}}{a_0}{a_1} \quad , \\
+    & \PHfrappe{a_0}{c_1}{c_0} \quad , \quad
+    \PHfrappe{fa_{11}}{c_0}{c_1}
+  \quad \}
+\end{align*}%
+}%
+  \caption{\label{tab:metazoan-ph-actions}%
+    Sets of actions of the flattened metazoan segmentation model depicted
+    in \pref{fig:metazoan-ph}.
+  }
+\end{table}
+
 \subsection{Large-scale Application: T-cell receptor}

### 2014-12-16 parts/def-ph.tex
add sets of actions
add section about the interest of priorities

@@
     \PHl_a &= \{ a_0, a_1 \} \enspace, & \PHl_b &= \{ b_0, b_1 \} \enspace, \\
-    \PHl_c &= \{ c_0, c_1 \} \enspace, & \PHl_{ab} &= \{ ab_{00}, ab_{01}, ab_{10}, ab_{11} \} \enspace.
+    \PHl_c &= \{ c_0, c_1 \} \enspace, & \PHl_{ab} &= \{ ab_{00}, ab_{01}, ab_{10}, ab_{11} \} \\ \enspace,
+    \PHa^{\langle 2 \rangle} &= (\PHa^{(1)}; \PHa^{(2)})
   \end{align*}
-  Note that: $\{ \PHhit{ab_{11}}{c_0}{c_1}, \PHhit{a_1}{a_1}{a_0}, \PHhit{a_0}{b_0}{b_1} \} \subseteq \PHh^{(2)}$.
+  and the sets of actions are:
+  \begin{align*}
+    \PHh^{(1)} = \{ \quad
+      & \PHfrappe{a_1}{ab_{00}}{ab_{10}} \enspace , \quad
+      \PHfrappe{a_1}{ab_{01}}{ab_{11}} \enspace , \\
+      & \PHfrappe{a_0}{ab_{10}}{ab_{00}} \enspace , \quad
+      \PHfrappe{a_0}{ab_{11}}{ab_{01}} \enspace , \\
+      & \PHfrappe{b_1}{ab_{00}}{ab_{01}} \enspace , \quad
+      \PHfrappe{b_1}{ab_{10}}{ab_{11}} \enspace , \\
+      & \PHfrappe{b_0}{ab_{01}}{ab_{00}} \enspace , \quad
+      \PHfrappe{b_0}{ab_{11}}{ab_{10}}
+    \quad \} \\
+    \PHh^{(2)} = \{ \quad
+      & \PHfrappe{a_1}{a_1}{a_0} \enspace , \quad
+      \PHfrappe{b_0}{a_0}{a_1} \enspace , \\
+      & \PHfrappe{b_1}{b_1}{b_0} \enspace , \quad
+      \PHfrappe{a_0}{b_0}{b_1} \enspace , \\
+      & \PHfrappe{ab_{11}}{c_0}{c_1}
+    \quad \} \\
+  \end{align*}
+%   Note that: $\{ \PHhit{ab_{11}}{c_0}{c_1}, \PHhit{a_1}{a_1}{a_0}, \PHhit{a_0}{b_0}{b_1} \} \subseteq \PHh^{(2)}$.
 
@@
 
-Cooperation between processes to make another process bounce can be expressed in PH by building a \emph{cooperative sort}, as described in \cite{PMR10-TCSB}.
+Cooperation between processes to make another process bounce can be expressed in PH by building a \emph{cooperative sort},
+which allows to encode any kind of Boolean function \cite{PMR10-TCSB}.
 \pref{fig:ph-livelock} shows an example of cooperation between processes $a_1$ and $b_1$ to make $c_0$ bounce to $c_1$:
@@
 
-The construction of cooperation in PH allows to encode any Boolean function between cooperating processes \cite{PMR10-TCSB}.
-Due to the introduction of priorities into the PH framework,
-it is possible to build cooperations with no temporal shift by defining actions updating the cooperative sorts with the highest class of priority.
-This allows to gain the same expressivity in PH than in Boolean networks, as stated in \pref{sec:dn}.
-The aim of this paper is to allow the static analysis of the dynamics to be handled on PH models involving such prioritised actions updating cooperative sorts.
+\modMF{
+\subsection{Justification of the priorities}
+}
+
+As explained previously,
+the construction of cooperation in PH allows to encode any Boolean function between cooperating processes \cite{PMR10-TCSB}.
+However, in the original version of the PH framework,
+which contained no classes of priorities
+(or, equivalently, only one class of priority),
+the representation of such Boolean functions was not accurate.
+Indeed, the lack of priorities did not allow cooperative sorts
+to always encode the \emph{current state} of several sorts, as expected,
+but only a \emph{combination of past states}.
+
+Let us for example consider the PH model 
+$\PH = (\PHs; \PHl; \PHh^{\angles{2}})$ from \pref{fig:ph-livelock},
+and the “merged” version of this model:
+$\PH' = (\PHs; \PHl; \PHh'^{\angles{1}})$,
+that is, where $\PHh'^{\angles{1}} = \PHh = \PHh^{(1)} \cup \PHh^{(2)}$.
+In other words, $\PH'$ has the same sorts and processes
+(and therefore the same states) than $\PH$,
+but the actions of the two classes of priories of the latter
+are united into one only class in the former.
+
+Starting from state $\PHstate{a_1, b_0, c_0, ab_{10}}$,
+it is not possible to reach a state where the processes $a_1$ and $b_1$
+are simultaneously active, in either $\PH$ and $\PH'$.
+Indeed, in both cases the actions hitting sorts $a$ and $b$ require that both
+$a_0$ and $b_0$ are active in order to activate $b_1$ (\resp $a_1$).
+Therefore, given the fact that the cooperative sort $ab$ represents
+the combined states of $a$ and $b$,
+and that the action $\PHhit{ab_{11}}{c_0}{c_1}$
+represents a Boolean “conjunction” between $a$ and $b$
+(that is, requires that both have process name “1” active),
+the expected behaviour is that $c_1$ cannot be reached.
+
+However, starting from state $\PHstate{a_1, b_0, c_0, ab_{10}}$,
+it is still possible to activate $c_1$ in $\PH'$
+by visiting the following sequence of states:
+\begin{align*}
+  & \PHstate{a_1, b_0, c_0, ab_{10}} \concat
+    \PHstate{a_0, b_0, c_0, ab_{10}} \concat
+    \PHstate{a_0, b_1, c_0, ab_{10}} \concat \\
+  & \qquad\qquad
+    \PHstate{a_0, b_1, c_0, ab_{11}} \concat
+    \PHstate{a_0, b_1, c_1, ab_{11}}
+\end{align*}
+This is due to the fact that after playing the action
+$\PHhit{a_1}{a_1}{a_0}$,
+the absence of priorities does not constrain the cooperative sort to be updated.
+We clearly see in this example that without priorities,
+the cooperative sort $ab$ only represents a combination of the past
+states of $a$ and $b$, without any notion of simultaneity.
+
+Adding classes of priorities allows to remove this undesired behaviour,
+especially by prioritizing all actions updating the cooperative sorts.
+Indeed, the previous behaviour is not possible in the original model $\PH$,
+where the actions of highest priority ($\PHh^{(1)}$)
+force the update of the cooperative sort before any other action of
+low priority ($\PHh^{(2)}$) can be played.
+The closest possible sequence of states is the following,
+where $ab_{11}$ can never be activated:
+\begin{align*}
+  & \PHstate{a_1, b_0, c_0, ab_{10}} \concat
+    \PHstate{a_0, b_0, c_0, ab_{10}} \concat
+    \PHstate{a_0, b_0, c_0, ab_{00}} \\
+  & \qquad\qquad
+    \PHstate{a_0, b_1, c_0, ab_{00}} \concat
+    \PHstate{a_0, b_1, c_0, ab_{01}}
+\end{align*}
+
+We conclude that the addition of priorities,
+by allowing to represent accurate Boolean gates in the form of cooperative sorts,
+thus allows to reach the same expressivity as Asynchronous Discrete Networks
+(see \pref{sec:dn}).
+Therefore, the next sections \todo{nouvelle section ?}
+formalize this use of the highest class of priority
+to force the update of cooperative sorts.
+The aim of the rest of this paper is to allow the static analysis
+of the dynamics on PH with priorities,
+and for this we rely on models involving
+such prioritised actions to update cooperative sorts.
+However, despite focusing on a sub-class of PH models,
+we show in \pref{ssec:flattening}
+that this sub-class is in fact as expressive as the class
+of all PH with classes of priorities.
 

### 2014-12-18 parts/sa.tex
revise GLC + explanations

@@
 
-The graph of local causality $\cwB = (\V, \E)$ defined in \pref{def:glc} is a graph where $\V \subseteq \Proc \cup \Obj \cup \Sol$ and $\E \subseteq \V \times \V$.
-A node in $\PHproc$ is a required process,
+\modMF{
+A graph of local causality $\aB = (\cwV, \cwE)$
+is a graph where $\cwV \subseteq \Proc \cup \Obj \cup \Sol$ is the set of vertices
+and $\cwE \subseteq \cwV \times \cwV$ is the set of oriented edges.
+Such a graph aims a describing the requirements of a given reachability
+problem, that is, the reachability of $\w$ from the initial context $\ctx$.
+Thus, a node in $\PHproc$ represents a process required to play an action,
 a node in $\Obj$ is an objective to reach a given process
-and a node in $\Sol$ is a set of processes required for the solving.
-An objective $P \in \Obj$ is solvable if the abstractions of bounce sequences $\aBS(P) \in \Sol$ (\pref{def:aBS}) can be reached (\pref{eq:ESol1}), thus leading to several required processes (\pref{eq:ESol2}).
-If $a \in \components$, the reachability of one of its process $a_i$ is approximated by the ability to solve all objectives $\PHobjp{a}{j}{i} \in \Obj$ for all $a_j$ in the initial context (\pref{eq:EReq});
-if $a \in \cs$, the reachability of $a_i$ is simply solved by the set of processes $\csState(a_i)$ (\pref{def:csState}) that it represents (\pref{eq:EPrio}).
-The solving of an objective $P$ may require a process of $\PHsort(P)$, \ie $\gCont(\PHsort(P), P) \neq \emptyset$ (\pref{def:maxCont}); in this case, $P$ is re-targeted (\pref{eq:ECont}).
-\pref{eq:Vw}, \eqref{eq:Vproc} and~\eqref{eq:VE} ensure that all required nodes are in $\cwV$.
-Finally, as the active process of every sort may evolve, $\cwB$ is obtained by iteratively saturating with every process it contains,
-\ie by overriding its initial context $\ctx$ by $\allprocs(\V, \E)$, defined by:
-\[\allprocs(\V, \E) = (V \cap \Proc) \cup \{ \PHtarget(P), \PHbounce(P) \mid P \in \V \cap \Obj \} \enspace.\]
+and a node in $\Sol$ is a set of hitter processes required for the solving
+of an objective.
+}
+
+\modMF{
+The edges of such a graph allow to draw links between these requirements.
+Thus, an objective $P \in \Obj$ is solvable if
+at least one related bounce sequence in $\BS(P)$ can be played;
+therefore, we can consider all minimal sets of hitters of these bounce sequences
+(that is, the sets of $\aBS(P) \in \Sol$, see \pref{def:aBS})
+as requirements to solve this objective (\pref{eq:ESol1}).
+Such a set can then naturally be split into as many process nodes,
+making each of them a new requirement (\pref{eq:ESol2}).
+If $a \in \components$, the reachability of a required process $a_i$
+is approximated by the ability to solve all objectives of the form
+$\PHobjp{a}{j}{i} \in \Obj$ for all $a_j$ in the initial context (\pref{eq:EReq});
+if $a \in \cs$, the reachability of $a_i$ is simply solved by the set of processes $\csState(a_i)$ (see \pref{def:csState}) that it represents (\pref{eq:EPrio}).
+Furthermore, we note that the solving of an objective $P$ may require
+a process of $\PHsort(P)$,
+\ie $\gCont(\PHsort(P), P) \neq \emptyset$ (\pref{def:maxCont});
+in this case, $P$ is re-targeted (\pref{eq:ECont}).
+Finally, \pref{eq:Vw} forces the graph to contain all the initial objectives,
+and \pref{eq:VE} ensures the consistency of $\cwV$.
+}
+
+\modMF{
+However, this graph $\aB$ alone is not sufficient to check the reachability of
+an objective sequence $\w$ from an initial context $\ctx$;
+indeed, the reachability of each intermediate required process
+is only checked starting from the context $\ctx$,
+although this context may be modified by other objectives.
+Therefore, such a reachability requires the building of the
+\emph{saturated graph of local causality} (\pref{def:glc})
+which is obtained by iteratively saturating the initial context with all
+processes referenced in the graph,
+until reaching a fixed point.
+Such a fixed point always exists because the size of the context
+is limited by the size of the initial PH model.
+The set of processes contained in a graph of local causality
+is given by:
+\begin{align*}
+  \allprocs(\cwV, \cwE) = (\cwV \cap \Proc) &\cup \{ \PHtarget(P) \mid P \in \cwV \cap \Obj \}\\
+  & \cup \{ P \neq \w \Rightarrow \PHbounce(P) \mid P \in \cwV \cap \Obj \}
+\end{align*}
+where, if the objective sequence $\w$ consists of only one element,
+then we can omit the hitter of this objective
+if it does not appear elsewhere in the graph.
+}
 
@@
     \w &\subseteq \cwV \label{eq:Vw} \\
-    P \in \cwVObj &\Rightarrow \PHbounce(P) \in \cwV \label{eq:Vproc} \\
+%    P \in \cwVObj &\Rightarrow \PHbounce(P) \in \cwV \label{eq:Vproc} \\
     (x, y) \in \cwE &\Rightarrow y \in \cwV \label{eq:VE} \\
@@
 
-In the graph of local causality, an edge $(p, ps) \in \Proc \times \Sol$
+\todo{“Saturated” partout}
+
+In the saturated graph of local causality, an edge $(p, ps) \in \Proc \times \Sol$
 is said to be coherent (\pref{def:coherent}) if none of the processes in $ps$ conflict with the children processes of $ps$.
@@
   \begin{tikzpicture}[aS]
-    \node[Aproc] (c1) {$c_1$};
-    \node[Aobj,below of=c1] (c01) {$\PHobj{c_0}{c_1}$};
+%    \node[Aproc] (c1) {$c_1$};
+%    \node[Aobj,below of=c1] (c01) {$\PHobj{c_0}{c_1}$};
+    \node[Aobj] (c01) {$\PHobj{c_0}{c_1}$};
     \node[Asol,below of=c01] (c01s) {};
@@
     \path
-    (c1) edge (c01)
+%    (c1) edge (c01)
     (c01) edge (c01s)
@@
   \label{fig:sa-livelock}
-    The graph of local causality of the PH model in \pref{fig:ph-livelock}
+    The saturated graph of local causality of the PH model in \pref{fig:ph-livelock}
     for the objective $\w = \PHobj{c_0}{c_1}$ and the initial context $\ctx = \PHstate{a_1, b_0, c_0, ab_{10}}$.

### 2014-12-18 parts/example.tex
refactor successive reachability in metazoan example

@@
 
+\modMF{
+This section aims at giving application examples of the static analysis method
+that we developed in \pref{sec:sa}.
+In \pref{ssec:ex-metazoan}, we apply our method to a small model of the
+metazoan segmentation process,
+and demonstrate how the flattening of \pref{ssec:flattening}
+be used in such a case.
+In \label{ssec:ex-tcrsig}, we apply our method to a large-scale model
+of the T-cell receptor signalling pathway
+in order to show the scalability of our method.
+}
+
 \subsection{Flattening of a model: Metazoan segmentation}
+\label{ssec:ex-metazoan}
 
-In this section, we illustrate the flattening method presented in \pref{ssec:flattening}
-on a model of metazoan segmentation inspired from a first translation to Process Hitting given in \cite{PMR10-TCSB}.
+\modMF{
+We give in this section a detailed example of the application of the sequential
+under-approximation proposed in \pref{ssec:ordered-ua},
+which consists of several applications of the methods developed in
+\pref{ssec:ua}.
+For this, we first have to use the flattening method presented in \pref{ssec:flattening}
+because the considered model contains 3 classes of priorities (and not only 2, as required).
+}
+
+We consider in the following a model of metazoan segmentation
+inspired from a first translation to Process Hitting given in \cite{PMR10-TCSB}.
 This model was originally established in silico in \cite{MSB:MSB4100192} in a differential equations framework.
@@
   \caption{\label{tab:metazoan-php-actions}%
-    Sets of actions of the metazoan segmentation model depicted
+    The sets of actions of the metazoan segmentation model depicted
     in \pref{fig:metazoan-php}.
@@
 Note that according to the simplifications mentioned at the end of \pref{ssec:flattening},
-the auto-action $h_1 = \PHhit{c_1}{c_1}{c_0}$ in $\oPH$ has been flattened to a regular action $\PHhit{a_0}{c_1}{c_0}$
+the auto-action $h_1 = \PHhit{c_1}{c_1}{c_0}$ in the original model has been flattened to a regular action $\PHhit{a_0}{c_1}{c_0}$
 because its playability property could be simplified to $\Fop{h_1} \equiv c_1 \wedge a_0 \equiv a_0$.
-
-The static analysis results of \pref{ssec:ua} and \pref{ssec:ordered-ua} can be used to check if the model is functional, \ie
-if genes $a$ and $c$ are successively activated and deactivated,
-thus leading to the formation of regular stripes.
-Starting from context $\ctx = \PHstate{f_1, a_0, c_0}$,
-we want to check the reachability of
-$\w = \PHobj{a_0}{a_1} \PHconcat \PHobj{c_0}{c_1} \PHconcat \PHobj{a_1}{a_0} \PHconcat \PHobj{c_1}{c_0}$.
-Rather than checking this whole objective sequence,
-we decompose it into the following ones:
-\begin{align*}
-  \ctx^1 &= \PHstate{f_1, a_0, c_0} \text{ and } P_1 = \PHobj{a_0}{a_1} &
-  \ctx^3 &= \PHstate{f_1, a_1, c_1} \text{ and } P_2 = \PHobj{a_1}{a_0} \\
-  \ctx^2 &= \PHstate{f_1, a_1, c_0} \text{ and } P_3 = \PHobj{c_0}{c_1} &
-  \ctx^4 &= \PHstate{f_1, a_0, c_1} \text{ and } P_4 = \PHobj{c_1}{c_0}
-\end{align*}
-Given \pref{th:approxinf}, we have: $\forall i \in \segm{1}{4}, \muconcr_{\ctx^i}(P_i) \neq \emptyset$.
-Finally, after checking that it can be applied for $i = 3$ down to $i = 1$,
-\pref{thm:ordered-ua} gives: $\uconcr(\w) \neq \emptyset$.
-Thus the model is functional.
-
-\todo{Le résultat peut être raffiné avec l'atteignabilité successive}
 
@@
   \caption{\label{tab:metazoan-ph-actions}%
-    Sets of actions of the flattened metazoan segmentation model depicted
+    The sets of actions of the flattened metazoan segmentation model depicted
     in \pref{fig:metazoan-ph}.
@@
 
+\modMF{
+Finally, the static analysis results presented in
+\pref{ssec:ua} and \pref{ssec:ordered-ua} can be used to check if the model is functional,
+\ie if gene $a$ can oscillate, thus leading to the formation of stripes.
+Starting from context $\ctx = \PHstate{f_1, a_0, c_0, fc_{10}, fa_{00}}$,
+we thus want to check the reachability of
+$\w = \PHobj{a_0}{a_1} \PHconcat \PHobj{a_1}{a_0} \PHconcat \PHobj{a_0}{a_1}$.
+Rather than checking this whole objective sequence with \pref{th:approxinf},
+we break it using \pref{thm:ordered-ua}.
+We first build the first saturated graph of local causality
+based on the first objective, $\w_1 = \PHobj{a_0}{a_1}$, in the initial context $\ctx$.
+This graph is depicted in \pref{fig:metazoan-sa}(left).
+%and given \pref{tmh:approxinf}, we have:
+We have especially:
+\[\allprocs(\thisB{\w_1}{\ctx}) = \{ a_0, c_0, f_1, fc_{10} \}\]
+\[\lastprocs(\PHobj{a_0}{a_1}) = \{\{ a_1, c_0, f_1, fc_{10} \}\}\]
+Therefore, the second step consists of computing the saturated graph of local causality
+of the objective $\w_2 = \PHobj{a_1}{a_0}$
+in the context
+\[\ctx' = \ctx \Cap \allprocs(\thisB{\w_1}{\ctx}) \Cap \lastprocs(\PHobj{a_0}{a_1}) = \PHstate{a_1, c_0, f_1, fc_{10}, fa_{00}}\]
+This second graph is given in \pref{fig:metazoan-sa}(middle).
+Finally, because
+\[\allprocs(\thisB{\w_2}{\ctx'}) = \{ a_1, c_1, f_1, fa_{11} \}\]
+\[\lastprocs(\PHobj{a_1}{a_0}) = \{\{ a_0, c_1 \}\}\]
+The last step is then checking 
+the objective $\w_3 = \PHobj{a_0}{a_1}$
+in the context
+\[\ctx'' = \ctx' \Cap \allprocs(\thisB{\w_2}{\ctx'}) \Cap \lastprocs(\PHobj{a_1}{a_0}) = \PHstate{a_0, c_1, f_1, fc_{10}, fa_{11}}\]
+This last graph is depicted in 
+As all the produced \pref{fig:metazoan-sa}(right).
+In conclusion, by using \pref{thm:ordered-sa} on these saturated graphs of local causality,
+we can conclude that the initial objective $\w$ is reachable,
+and thus that the PH model of \pref{fig:metazoan-ph} is functional.
+This result can be extended to the model of \pref{fig:metazoan-php}
+because they have the same dynamics (given \pref{th:bisimPHP}).
+}
+
+% $\w = \PHobj{a_0}{a_1} \PHconcat \PHobj{c_0}{c_1} \PHconcat \PHobj{a_1}{a_0} \PHconcat \PHobj{c_1}{c_0}$.
+% Rather than checking this whole objective sequence,
+% we decompose it into the following ones:
+% \begin{align*}
+%   \ctx^1 &= \PHstate{f_1, a_0, c_0} \text{ and } P_1 = \PHobj{a_0}{a_1} &
+%   \ctx^3 &= \PHstate{f_1, a_1, c_1} \text{ and } P_2 = \PHobj{a_1}{a_0} \\
+%   \ctx^2 &= \PHstate{f_1, a_1, c_0} \text{ and } P_3 = \PHobj{c_0}{c_1} &
+%   \ctx^4 &= \PHstate{f_1, a_0, c_1} \text{ and } P_4 = \PHobj{c_1}{c_0}
+% \end{align*}
+% Given \pref{th:approxinf}, we have: $\forall i \in \segm{1}{4}, \muconcr_{\ctx^i}(P_i) \neq \emptyset$.
+% Finally, after checking that it can be applied for $i = 3$ down to $i = 1$,
+% \pref{thm:ordered-ua} gives: $\uconcr(\w) \neq \emptyset$.
+% Thus the model is functional.
+
+\begin{figure}[tp]
+  \centering
+  \begin{tikzpicture}[aS]
+    % STEP 1
+    \node[Aobj] (a01) {$\PHobj{a_0}{a_1}$};
+    \node[Asol,below of=a01] (a01s) {};
+
+    \node[AprocPrio,below of=a01s] (fc10) {$fc_{10}$};
+    \node[AsolPrio,below of=fc10] (fc10s) {};
+
+    \node[Aproc,below left of=fc10s] (f1) {$f_1$};
+    \node[Aobj,below of=f1] (f11) {$\PHobj{f_1}{f_1}$};
+    \node[Asol,below of=f11] (f11s) {};
+
+    \node[Aproc,below right of=fc10s] (c0) {$c_0$};
+    \node[Aobj,below of=c0] (c00) {$\PHobj{c_0}{c_0}$};
+    \node[Asol,below of=c00] (c00s) {};
+
+    \path
+    (a01) edge (a01s)
+    (a01s) edge (fc10)
+    (fc10) edge[aSPrio] (fc10s)
+    (fc10s) edge (f1) edge (c0)
+
+    (f1) edge (f11)
+    (f11) edge (f11s)
+
+    (c0) edge (c00)
+    (c00) edge (c00s)
+    ;
+
+    % STEP 2
+    \node[Aobj,right of=a01,node distance=3.5cm] (a10) {$\PHobj{a_1}{a_0}$};
+    \node[Asol,below of=a10] (a10s) {};
+
+    \node[Aproc,below of=a10s] (c1) {$c_1$};
+    \node[Aobj,below right of=c1] (c01) {$\PHobj{c_0}{c_1}$};
+    \node[Asol,below of=c01] (c01s) {};
+    \node[Aobj,below left of=c1] (c11) {$\PHobj{c_1}{c_1}$};
+    \node[Asol,below of=c11] (c11s) {};
+
+    \node[AprocPrio,below of=c01s] (fa11) {$fa_{11}$};
+    \node[AsolPrio,below of=fa11] (fa11s) {};
+
+    \node[Aproc,below left of=fa11s] (a1) {$a_1$};
+    \node[Aobj,below of=a1] (a11) {$\PHobj{a_1}{a_1}$};
+    \node[Asol,below of=a11] (a11s) {};
+
+    \node[Aproc,below right of=fa11s] (f1) {$f_1$};
+    \node[Aobj,below of=f1] (f11) {$\PHobj{f_1}{f_1}$};
+    \node[Asol,below of=f11] (f11s) {};
+
+    \path
+    (a10) edge (a10s)
+    (a10s) edge (c1)
+
+    (c1) edge (c01) edge (c11)
+    (c01) edge (c01s)
+    (c11) edge (c11s)
+    (c01s) edge (fa11)
+
+    (fa11) edge[aSPrio] (fa11s)
+    (fa11s) edge (f1) edge (a1)
+
+    (f1) edge (f11)
+    (f11) edge (f11s)
+
+    (a1) edge (a11)
+    (a11) edge (a11s)
+    ;
+
+    % STEP 3
+    \node[Aobj,right of=a10,node distance=4cm] (ta01) {$\PHobj{a_0}{a_1}$};
+    \node[Asol,below of=ta01] (ta01s) {};
+
+    \node[AprocPrio,below of=ta01s] (tfc10) {$fc_{10}$};
+    \node[AsolPrio,below of=tfc10] (tfc10s) {};
+
+    \node[Aproc,below left of=tfc10s] (tf1) {$f_1$};
+    \node[Aobj,below of=tf1] (tf11) {$\PHobj{f_1}{f_1}$};
+    \node[Asol,below of=tf11] (tf11s) {};
+
+    \node[Aproc,below right of=tfc10s] (tc0) {$c_0$};
+    \node[Aobj,below of=tc0] (tc10) {$\PHobj{c_1}{c_0}$};
+    \node[Asol,below of=tc10] (tc10s) {};
+    \node[Aobj,right of=tc10] (tc00) {$\PHobj{c_0}{c_0}$};
+    \node[Asol,below of=tc00] (tc00s) {};
+
+    \node[Aproc,below of=tc10s] (ta0) {$a_0$};
+    \node[Aobj,below of=ta0] (ta00) {$\PHobj{a_0}{a_0}$};
+    \node[Asol,below of=ta00] (ta00s) {};
+
+    \path
+    (ta01) edge (ta01s)
+    (ta01s) edge (tfc10)
+    (tfc10) edge[aSPrio] (tfc10s)
+    (tfc10s) edge (tf1) edge (tc0)
+
+    (tf1) edge (tf11)
+    (tf11) edge (tf11s)
+
+    (tc0) edge (tc00)
+    (tc00) edge (tc00s)
+    (tc0) edge (tc10)
+    (tc10) edge (tc10s)
+
+    (tc10s) edge (ta0)
+    (ta0) edge (ta00)
+    (ta00) edge (ta00s)
+    ;
+  \end{tikzpicture}
+  \caption{%
+  \label{fig:metazoan-sa}%
+    The three successive saturated graphs of local causality
+    of the PH model in \pref{fig:metazoan-ph}
+    for the objective sequence
+    $\w = \PHobj{a_0}{a_1} \concat \PHobj{a_1}{a_0} \concat \PHobj{a_0}{a_1}$
+    and the initial context
+    $\ctx = \PHstate{a_0, c_0, f_1, fc_{10}, fa_{10}}$.
+    The (left) graph allows to check objective $\PHobj{a_0}{a_1}$
+    from the initial context $\ctx$.
+    The (middle) graph is for the objective $\PHobj{a_1}{a_0}$
+    and the context $\PHstate{a_1, c_0, f_1, fc_{10}, fa_{10}}$.
+    The (right) graph is for the last objective, $\PHobj{a_0}{a_1}$,
+    and the context $\PHstate{a_0, c_1, f_1, fc_{10}, fa_{11}}$.
+%     Rectangular nodes containing a single process are elements in $\Proc$,
+%     borderless nodes containing a couple of processes are elements in $\Obj$
+%     and circle nodes are elements in $\Sol$.
+%     \pref{th:approxinf} is inconclusive on this example as edge $(ab_{11}, \{ a_1, b_1 \}) \in \Proc \times \Sol$ (here represented with a double line) is not coherent (\pref{def:coherent}).
+%     Indeed, $a_0 \in \Proc$ is a child of $\{ a_1, b_1 \}$, but $a_0 \neq a_1$ (and the same also stands for $b_0$).
+  }
+\end{figure}
+
 \subsection{Large-scale Application: T-cell receptor}
+\label{ssec:ex-tcrsig}
 
 In order to support the scalability and applicability of our under-approximation of reachability, we
-apply our new approach for the analysis of large-scale model of the T-cell receptor (TCR)
+apply our new approach to the analysis of a large-scale model of the T-cell receptor (TCR)
 signalling pathway \cite{tcrsig94}.

### 2014-12-18 parts/intro.tex
add TODOs after review
refactor successive reachability in metazoan example

--- 2014-04-11 parts/intro.tex
@@
 
-The main additions in this paper compared to \cite{FPMR13-CS2Bio} are
-two theorems, the first
-stating that any Process Hitting model with any number of classes of priorities can be represented
-with only two classes of priorities,
-and the other giving a method to cope with successive reachability,
-both extending the application range of the static analysis we developed.
+The main addition in this paper compared to \cite{FPMR13-CS2Bio} is
+%two theorems, the first
+\pref{thm:ordered-ua} that gives a method to cope with successive reachability,
+and obtain more conclusive results in the case of several successive objectives.
+Two other additions are 
+\pref{th:bisimPHP} which states that any Process Hitting model with any number of classes of priorities
+can be represented with only two classes of priorities,
+thus extending the scope of our method to any possible Process Hitting model,
+and \todo{def extraction}
+which allows to extract a concrete scenario when our static analysis method
+is conclusive.
+%Both aim at extending the application range of the static analysis we developed.
 

### 2014-12-18 parts/example.tex
'saturated' GLCs + several fixes

@@
 As all the produced \pref{fig:metazoan-sa}(right).
-In conclusion, by using \pref{thm:ordered-sa} on these saturated graphs of local causality,
+In conclusion, by using \pref{thm:ordered-ua} on these saturated graphs of local causality,
 we can conclude that the initial objective $\w$ is reachable,

### 2014-12-18 parts/sa.tex
'saturated' GLCs + several fixes

@@
 \label{def:glc}
-  The graph of local causality $\cwB \DEF (\Bv, \Be)$ is defined as: $\cwB \DEF \lfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs(\myB)}}$,
+  The \modMF{saturated} graph of local causality $\cwB \DEF (\Bv, \Be)$ is defined as:
+  $\cwB \DEF \lfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs(\myB)}}$,
   where $\myB \DEF (\cwV, \cwE)$ is the smallest graph with
@@
 Then, \pref{th:approxinf} gives a sufficient condition for the concretisation of a sequence of objectives in a given context,
-which is derived immediately from the graph of local causality.
+which is derived immediately from the saturated graph of local causality.
 A proof of this theorem is given in \pref{suppl:demoapproxinf}.
@@
 
-Computing the graph of local causality is polynomial in the number of sorts in $\PH$ and exponential in the number of processes in one sort.
+Computing the saturated graph of local causality is polynomial in the number of sorts in $\PH$ and exponential in the number of processes in one sort.
 Checking the properties allowing to apply \pref{th:approxinf} is polynomial in the size of the graph.
@@
 \begin{example}
-  Let $\PH' = (\PHs, \PHl, \PHh'^{\langle 1 \rangle})$ be the “merged” version of the PH in \pref{fig:ph-livelock}, that is: $\PHh'^{\langle 1 \rangle} = \PHh^{(1)} \cup \PHh^{(2)}$,
-  which is how it would have been represented in the semantics without priorities.
-  Due to spurious behaviours inherent to the cooperative sorts in this semantics, 
-  the original under-approximation developed in~\cite{PMR12-MSCS} concludes that $c_1$ is reachable in $\PH'$ from $\ctx = \PHstate{a_1, b_0, c_0, ab_{10}}$.
+  Let $\PH' = (\PHs, \PHl, \PHh'^{\langle 1 \rangle})$ be the “merged” version of the PH
+  depicted in \pref{fig:ph-livelock}, as it was already defined in \pref{ssec:priorties},
+  that is: $\PHh'^{\langle 1 \rangle} = \PHh^{(1)} \cup \PHh^{(2)}$.
+  In other words,
+  $\PH'$ is how $\PH$ would have been represented in the semantics without priorities.
+  We showed in \pref{ssec:priorties} that,
+  due to spurious behaviours inherent to the cooperative sorts in this semantics,
+  process $c_1$ is reachable
+  from the initial context $\ctx = \PHstate{a_1, b_0, c_0, ab_{10}}$.
+%   This is confirmed by the original under-approximation
+%   developed in~\cite{PMR12-MSCS}, which gives the same conclusion.
 
@@
   Indeed, the under-approximation given in \pref{th:approxinf} does not conclude regarding the reachability of $c_1$,
-  as one of the edges of the resulting graph of local causality is not coherent (\pref{def:coherent}),
+  as one of the edges of the resulting saturated graph of local causality is not coherent (\pref{def:coherent}),
   as shown in in \pref{fig:sa-livelock}.
@@
 
-  However, if $\PHhit{a_0}{b_0}{b_1}$ and $\PHhit{b_0}{a_0}{a_1}$ are replaced by the auto-actions
+  We note however that,
+  if $\PHhit{a_0}{b_0}{b_1}$ and $\PHhit{b_0}{a_0}{a_1}$ are replaced by the auto-actions
   $\PHhit{a_0}{a_0}{a_1}$ and $\PHhit{b_0}{b_0}{b_1}$,
-  then \pref{th:approxinf} concludes that $c_1$ is reachable from $\ctx$.
+  then the resulting saturated graph of local causality changes, and
+  \pref{th:approxinf} concludes that $c_1$ is then reachable from $\ctx$.
 

### 2014-12-18 parts/example.tex
revise TCRSIG example + justifictions of our method over [13]

@@
 \footnote{Files are available at
-\url{http://maxime.folschette.name/underapprox-tcrsig94.zip}.}.
+\url{http://maxime.folschette.name/underapprox-tcrsig94.zip}.}
+\modMF{
+by using a translation equivalent to the one given in \pref{sec:dn}.
+\todo{?}
+}
 Then, we verified the reachability for the independent activation of 4 outputs of the signalling
@@
 
-Computations times are in the order of a few hundredths of a second on a 2.4GHz processor with 2GB
-of RAM.
+\modMF{
+By analysing the detail of the results, one can find out that one of the output, NFkB, can never be activated.
+In other words, FkB$_1$ is never reachable, whatever the state of the inputs,
+while some combinations the other outputs (SRE, AP1, NFAT) can be activated for some configurations of inputs.
+We thus want to check if these three outputs can be activated together,
+that is, if the activation of one of the outputs does not prevent the activation of one of the others.
+For this, as proposed in \pref{ssec:simult-ua},
+we add a new cooperative sort $\total$ between SRE, AP1 and NFAT to the model,
+and a sort $\reach$ with two processes ($\PHl_\reach = \{ \reach_0, \reach_1 \}$)
+with the action $\PHhit{\total_{111}}{\reach_0}{\reach_1}$.
+Finally, checking the reachability of $\reach_1$ in all configurations of the inputs
+is always conclusive,
+and the existence of positive answers allows to conclude that
+it is possible to reach a state where SRE, AP1 and NFAT are simultaneously active.
+}
+
+We held all these experiments on a laptop computer with a 2GHz processor
+and 1GB of RAM.
+\modMF{
+Computations times were in the order of a few hundredths to tenths of a second
+in each case (reachability of $\reach_1$ included).
+}
 To give a comparison, we did the same experiments with a standard symbolic model-checker, libDDD
@@
 However, due to the large scale of the model, the program runs out of memory for all the experiments.
+\modMF{
+This limitation shows that studying the dynamics of models is strongly limited to the size of the model for standards model checkers,
+while our method is able to conclude with limited memory and computation time usage.
+Furthermore, given that the complexity of the static analysis presented in this paper
+is polynomial in the size of the models,
+it is expected that our work will be scalable to models that are larger,
+even by orders of magnitude.
+%---~that is, containing thousands of components.
+}
+
+\modMF{
+Finally, we note that similar experiments were conducted in~\cite{PMR12-MSCS}.
+However, if these experiments allowed to obtain some information
+on these model to some extent,
+it did not provide a formal proof of the reachabilities that have been
+checked in the example above.
+Indeed, without any priorities in the update of the cooperative sorts,
+some unwanted behaviours were possible,
+such as those described in \pref{ssec:priorities}.
+Only the method presented in this paper provides a formal proof that
+the observed behaviours are the result of the exact dynamics of the system,
+which was originally described in a format equivalent to synchronous Discrete Networks.
+}
 

### 2014-12-18 parts/sa.tex
revise TCRSIG example + justifictions of our method over [13]

@@
   Let $\PH' = (\PHs, \PHl, \PHh'^{\langle 1 \rangle})$ be the “merged” version of the PH
-  depicted in \pref{fig:ph-livelock}, as it was already defined in \pref{ssec:priorties},
+  depicted in \pref{fig:ph-livelock}, as it was already defined in \pref{ssec:priorities},
   that is: $\PHh'^{\langle 1 \rangle} = \PHh^{(1)} \cup \PHh^{(2)}$.
@@
   $\PH'$ is how $\PH$ would have been represented in the semantics without priorities.
-  We showed in \pref{ssec:priorties} that,
+  We showed in \pref{ssec:priorities} that,
   due to spurious behaviours inherent to the cooperative sorts in this semantics,
@@
 \subsection{Reachability of a state}
+\label{ssec:simult-ua}
 

### 2014-12-18 underapprox-tcrsig94/run.sh
update source of TCRSIG example

@@ -1,12 +1,12 @@
 #!/usr/bin/env bash
 ph="model.ph"
-outputs="sre ap1 nfkb nfat"
+outputs="sre ap1 nfkb nfat sigmab"
 mode=${1}
 
 for i in 0 1; do
 	for j in 0 1; do
 		for k in 0 1; do
-			init="cd45 $i, cd28 $j, tcrlig $k"
+			init="cd4 $i, cd28 $j, tcrlig $k"
 			echo "--- $init"
 			for z in $outputs; do
 				echo "# $z 1"

### 2014-12-18 response.tex
begin response to the reviewers

\documentclass[11pt]{article}

%\usepackage{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage{color}
\usepackage{fullpage}

\def\BibTex{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
         T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\usepackage{amsmath}
\usepackage{amssymb}

% \newcounter{pointno}
% \setcounter{pointno}{0}
% \def\thepoint{\arabic{pointno}}
% \newcommand{\ptno}[1]{\textcolor{blue}{\refstepcounter{pointno} \thepoint. \#1}}
% \newcommand{\question}[1]{\bigskip{\it\ptno{\#1}}}
% \def\answer{}

\newcommand{\todo}[1]{\textcolor{red}{\textbf{[TODO: #1]}}}
\newcommand{\answertodo}[1]{\textcolor{red}{\textbf{À appliquer :}} \textcolor{magenta}{#1}}

\newcommand{\answer}[1]{\textcolor{blue}{#1}}

%\setlength{\parindent}{0pt}

% 
% \def\V{\mathcal V}
% \def\O{\mathcal O}
% 
% \def\zero{\mathbf 0}
% \def\R{\mathbb R}
% \def\Rpos{\R_{\geq 0}}
% \def\Rspos{\R_{>0}}
% \def\Q{\mathbb Q}
% \def\Qpos{\Q_{\geq 0}}
% \def\Qspos{\Q_{>0}}
% \def\Z{\mathbb Z}
% \def\Zpos{\Z_{\geq 0}}
% \def\Zspos{\Z_{> 0}}
% 
% \def\mspan{\mathrm{span}}
% \def\lp{\mathrm{lowerpoint}}
% \def\orderings{\mathrm{orderings}}
% 
% \def\inner\#1\#2{\#1\#2}
% %\def\inner\#1\#2{\langle \#1,\#2 \rangle}
% 
% \def\apply{\bullet}
% 
% \def\B{\mathcal B}

\begin{document}

\noindent
Légende :\\
\answer{Blabla} $\longleftarrow$ Réponse au reviewer\\
\answertodo{Blabla} $\longleftarrow$ Réponse possible sur un point encore non appliqué\\
\todo{Blabla} $\longleftarrow$ À faire / à décider

\begin{center}
  --- --- ---
\end{center}

\section*{Summary of the main changes}

\todo{Résumer et lister les modifs}

\begin{itemize}
  \item Minor changes in the static analysis to make the graph more precise,
    and the Sect.~5.1 was revised in consequence;
  \item New explanations and examples all over the paper,
    especially regarding the use of priorities (Sect.~2.3),
    the lemmas (Sect.~2.4 \&~2.5)
    and the under-approximation (Sect.~3.2);
  \item A section was added (Sect.~3.5) about the extraction of a scenario from the graph of
    local causality, in the case the analysis is conclusive;
\end{itemize}

\section*{Comments and answers to the reviewers}

\subsection*{Reviewer \#2}

[…]

According to the authors, the static analysis approach presented in the paper is inspired from a previous paper ([13] Paulevé, Magnin, Roux. Static analysis of biological regulatory networks dynamics using abstract interpretation). By comparing the paper with [13], I had the impression that most of the developments in the current paper were just an exercise to borrow the techniques developed in [13] into the setting of Process Hitting with *priorities*. This is caused by the fact that in Section 2 (which introduces the PH framework to the reader) there are not enough intuitive explanations and examples to help the reader understand the concepts. (To this aim, in Section 2, a running example would be a welcome addition.)
In particular, a weak point of the paper lies in the restrictions introduced in Sections 2.2 and 2.3, which are not motivated. Those sections should be rewritten to clearly explain why those restriction are needed, and discuss their implications with respect to the reduced modelling expressiveness which ensues (e.g. which models cannot be described anymore?).

\answer{
The intent of this paper is to adapt the static analysis methods previously developed in [13] to the case of the PH with priorities, that is, models with a new kind of dynamics and preemptions that did not exist previously.
The method thus required adaptations that we tried to better motivate in this revision.
We added a section (Sect.~2.3) to motivate the use of priorities in the PH.
Furthermore, we added a running example in Sect~2.4 \& 2.5 in order to explain all the definitions and lemmas.
}

With respect to the workshop version, Section 4.2 has been added to present a translation of PH models with multiple priority classes (with restrictions from Section 2.3 assumed) into an "equivalent" (weakly-bisimilar) PH model with only two priority classes. Since the restrictions from Section 2.3 are already assumed for PH models with multiple priority classes, this strengthens the need for a discussion on those restrictions.

\answer{
This translation allows to apply the static analysis to any PH model with priorities, despite the restrictions defined in Sect. 2.4.
We added some discussion in Sect. 4.2 in order to emphasize this.
}

As regards the biological experiments presented in Section 5.2, this section should be extended by reporting more details about the experiments carried and the results obtained. Moreover, you should compare the results with the analogous experiments from [13], in which the same model (TCR pathway) had been analysed with good results. What improvements are there?
I also point out that the comparisons with a model-checker should be actually carried out. The fact that the test you performed caused out-of-memory errors does not allow any conclusion to be drawn, even more so considering that only 2GB of RAM have been used.

\answer{
The experiment we carried with the LibDDD model-checker led us to the conclusion that the memory needs for such a method is several orders of magnitude above our method, which we would consider a sufficient result in itself.
Furthermore, with such a memory use, one cannot expect to be able to study bigger models (say, thousands of components) while our method has a polynomial complexity in the size of the model, and could tackle such bigger models.
Thus, we have not performed more experiments,
but we have added some precisions about our thoughts in the paper.
}

Beyond the above concerns, the paper would also benefit from a reorganization, since I found it sometimes difficult to follow. This is particularly relevant for Section 4, where the translations proposed are just thrown in, without discussing their relevancy to the purpose of the paper.

\answertodo{
The translations could indeed be better discussed and justified,
we have taken this comment into account.
}

Minor comments […]
% ----------------
% page 1
% - abstract: "... as it is illustrated on the model-checking of a signalling network of 94 components, which is unprecedented.": I am not convinced the such application is "unprecedented", since the same model has been already analysed with good results in [13].
% page 5
% - do not use \ldots for the finite set of sorts
% - for defining prio(h), the same action $h$ must not be present in two different classes (this condition is missing)
% - Def.2: "sub-set" --> "sub-state" (twice)
% - Def.2 (and other places in the paper): symbol $\subset$ is usually means *strict* subset. Check its use in the paper and replace it with $\subseteq$ where appropriate.
% - Def.3: "We also extend this definition to a set of processes given that all processes are from different sorts by the override of each process" ???
% - Def.3: what is $\widetilde{ps}$ ?
% 
% page 6
% - in Figure 1 there are too many arrows that overlap which make it difficult to read
% - the example should be completed by listing all the actions from the two priority classes
% - Sect.2.2: "a1 and b1 to make c0 bounce to c1": you should replace "make" with "allow", since according to the semantics c0 is not forced to go to c1 asap.
% - Sect.2.2: "one for each sub-state of the presence of processes a1 and b1": not clear
% 
% page 7
% - "... instead of independent hits from a1 and b1.": not clear
% - (also in other places) "allows to" --> "allows <someone> to"
% - "build cooperations with no temporal shift": please clarify what you mean with "temporal shift"
% - $Sce|_1$ is not defined

\answertodo{
We took these comments into account
}

\subsection*{Reviewer \#3}

% Minor language issues:
% 
% (1) In introduction first paragraph at the sixth line there is a typo with 3 full stops ...
% (2) Second paragraph in introduction fifth line, it should be USUALLY, rather then USUAL, please change it.
% (3) Same paragraph: Components rarely have more "that" four levels, which should be: Components rarely have more "than" four levels.
% (4) Please add some text around the figures 1,3, and 4 so that a non technical reader (biologist) might have some idea about the interactions in the figures.
% (5) In discussion the following sentence needs to be rewritten: "i.e., without an intermediate encoding; our objective being to increase the conclusiveness of the static analysis   approach".

\answertodo{
We took the comments about the language issues of Reviewer \#3 into account.
}

\subsection*{Reviewer \#4}

[…]

With respect to the workshop version of the paper I don't see a significant improvement that should justify a further publication of the results. In particular, there are several new theorems, but they do not add significant novelties to the already proposed ideas. On the contrary, aspects that could have been given more accurate treatment are left poorly addressed. In particular:

\answer{
The additions regarding the workshop paper are the following:
\begin{itemize}
  \item Theorem 2, which refines successive reachability;
  \item Sect. 4.2, which allows to translate any PH model with priorities
    into a model that can be processed by our method (thus extending its range of application);
  \item Sect. 3.5, which returns a scenario concretizing the desired reachability,
    when possible (this addition is new to this revision).
\end{itemize}
We emphasized these in the introduction.
}

- discussion on the computational gain acquired with the new approach is not formally addressed and very poorly discussed (end of page 12, see also comment below)

\answer{
The aim of our method was not to gain any computation time of memory,
but to improve the expressivity of the PH formalism and its associated static analysis.
We are now able to formally check Asynchronous Discrete Networks
(also called Thomas' models)
which was not the case before.
This has been emphasized in Sect. 5.2.
}

- the static analyses that are proposed are based on abstract interpretation, however there is not a formal introduction of them in this framework. In particular there are abstractions and concretizations whose domains (and their relationships in terms of Galois insertion / connection) are not clearly stated. Moreover, the overall ideas of the abstractions are lost in the heavy technical presentation. This is difficult to read and does not give sufficient intuition to grasp the concepts, which remain hidden behind the notation.

\todo{À faire !}

- the biological examples look interesting and appropriate, but the details that are given in the paper look not sufficient to appreciate the demonstration of the approach that they should give.

\todo{Quels détails supplémentaires devrait-on donner ?}

- the link to Boolean Networks and Multivalued Boolean Networks is given by a translation that is published in another paper. That is ok, but the authors mention Asynchronous Discrete Networks as an "intermediate" model between the models previously mentioned and the Process Hitting framework. This remains an obscure connection and "Asynchronous Discrete Networks" cannot be found as keyword in the literature, at least at a first general search.

\todo{Un autre terme devrait être trouvé, je propose : Discrete Networks.}

- the overall presentation of the ideas and results are heavily technical and frankly difficult to read even for a reader that is used to formality. The most difficult aspect is the proliferation of notation, which forces the reader to continuously go back and forward to recall the meaning of the very large number of symbols.

\todo{Peut-être faudrait-il diminuer le nombre de symboles ? Mais lesquels enlever ?}

\answer{
We have tried to give more explanations and examples
on most of the technical definitions all throughout the paper.
}

Comments and suggestions

[…]

% page 2, paragraph 1: Some general references should be given here, reference papers, overviews, and so on.
% 
% p 2, end of paragraph 2, it is not clear if the name "Asynchronous Discrete Networks" is introduced by the authors or it is taken from [4], where multivalued Boolean Networks are discussed. 
% 
% p 3, line -13 what does it mean "to decide a successive reachability property"?
% 
% p 4, line 12 the least fix point could be greater than $x_0$; moreover, what are the hypotheses on f? It may have not a fix point at all
% 
% p 5, line -16 the set of all sub-sets —> the set of all sub-states 
% 
% p 5, l -14 a symbol like $\preceq$ or $\sqsubseteq$ would be more intuitive than $\subseteq$ for sub-states
% 
% p 5, l -4 can a scenario $\delta$ be empty? This may be important in the subsequent part of the paper, for instance at page 9, Lemma 3, could the empty scenario $\delta$ be selected by the $\exists$ after the main implication?
% 
% p 5, l -3 the fact that there is a set of scenarios implies that there is non-determinism.  Such aspect is never mentioned explicitly in the paper. It could be explicitly addressed.
% 
% p 6, l 4 (caption of figure 1) in drawn -> is drawn
% 
% p 6, last line and page 7 first line: what does it mean "one for each sub-state of the presence of processes $a_1$ and $b_1$"?
% 
% p 7 section 2.3 title: Restrictions may be misleading, why don't call this section "Conditions"?
% 
% p 7, l -2 all actions of priority 1, which —> all actions of priority 1 from s, which
% 
% p 8, l 6 greater than 2 -> greater than or equal to 2
% 
% p 8, l 8 We note $\Gamma$ —> We denote by $\Gamma$
% 
% p 8 Def 7 is a well-formed component if -> is a well-formed component, and so $a \in \Gamma$
% 
% p 8 Def 9 is a well-formed cooperative sort if -> is a well-formed cooperative sort, and so $a \in Delta$, if 
% 
% p 8 Def 9, condition (iv), does it require a sort of "determinism"  of cooperative encodings?
% 
% p 8, l -7 "represented by", in which sense?
% 
% p 10, -19 we note $a_i$ —> we denote by $a_i$
% 
% p 10, l -10 a bounce sequence on a can be abstracted into sets of all its hitters that are not in sort a (Def 16). — Is this an idea for an abstract interpretation? If yes the mechanism of abstraction / concretization, as well as the Galois connection/insertion between the abstract and concrete domains, is not clear and the whole underlying idea I could not catch by the definitions.
% 
% p 10, l -8 on other sots -> on other sorts
% 
% p 11, l 7 we denote $\gamma_\varsigma$ -> we denote by $\gamma_\varsigma$
% 
% p 11, l 7 the set of scenarios concretizing an objective sequence .. (Def 17) .. again the abstract interpretation is mentioned, but not fully introduced and explained.
% 
% p 11, l 16 the notation $\delta_{1 \ldots \Phi(n)}$ is not introduced
% 
% p 11, l 23 given by $maxCont_\varsigma$ -> denoted by $maxCont_\varsigma$
% 
% p 12, Def 20 this looks like a definition of an abstract fixpoint semantics to derive the graph of local causality. Ok, why is it not mentioned?
% 
% p 12, Def 20, rule (1): $\omega$ is an objective sequence , which is neither in Obj nor in Proc or Sol. It seems there is a "type mismatch" with the definition of $V^\omega_\varsigma$.
% 
% p 12 Def 21 it is not clear the definition of "children process"
% 
% p 12 last paragraph the discussion on the complexity issue looks very limited considering that this is supposed to be one of the contributions of the whole work. It is mentioned that "it is possible to compute only a subset of $V \cap Sol$", how?

\answertodo{We have taken these comments into account}

\end{document}

### 2014-12-19 parts/ccl.tex
minor comments of the reviewers

@@
 Furthermore, we are investigating alternative under-approximations that can be
-applied directly on a larger class of Process Hitting models, \ie without an
-intermediate encoding; our objective being to increase the conclusiveness of the static
-analysis approach.
+applied directly to the whole class of Process Hitting models with priorities,
+and not only to a sub-class with particular restrictions;
+such improvement may allow to increase the conclusiveness of the static analysis
+while allowing to analyse any model without the need of a translation.
 Finally, in order to take into account quantitative data in transition delays, the overall approximation method could be extended to handle evolutions that are chronometric instead of only chronologic.

### 2014-12-19 parts/def-ph.tex
refactor successive reachability in metazoan example
'saturated' GLCs + several fixes
revise TCRSIG example + justifictions of our method over [13]
minor comments of the reviewers

@@
 \label{sec:ph}
-
-\todo{Gluer : explication des définitions, etc.}
 
@@
 \label{ssec:PH}
+
 A PH with $k \in \sN^*$ classes of priorities (\pref{def:ph}), also simply called “PH” in the following when it is not ambiguous, gathers a finite number of concurrent \emph{processes} divided into a finite set of \emph{sorts}.
@@
   \begin{itemize}
-    \item $\PHs \DEF \{a, b, \dots\}$ is the finite set of \emph{sorts},
+    \item $\PHs \DEF \{a, b, \dots, z\}$ is the finite set of \emph{sorts},
     \item $\PHl \DEF \underset{a \in \PHs}{\times} \PHl_a$ is the finite set of \emph{states}, where $\PHl_a = \{a_0, \ldots, a_{l_a}\}$ is the finite set of \emph{processes} of sort $a \in \PHs$ and $l_a \in \sN^*$.
@@
   We call $\PHproc \DEF \bigcup_{a \in \PHs} \PHl_a$ the set of all processes, and $\PHh \DEF \bigcup_{n \in \segm{1}{k}} \PHh^{(n)}$ the set of all actions.
-  Furthermore, for all $n \in \sN^*$ and $h \in \PHh^{(n)}$, $\prio(h) \DEF n$.
+  Furthermore, for all $h \in \PHh$,
+  %for all $n \in \sN^*$ and $h \in \PHh^{(n)}$,
+  $\prio(h) \DEF \min\{ n \in \segm{1}{k} \mid h \in \PHh^{(n)} \}$.
 \end{definition}
@@
 \label{def:substate}
-  If $S \subset \PHs$ is a set of sorts, a sub-set on $S$ is an element of:
+  If $S \subseteq \PHs$ is a set of sorts, a sub-state on $S$ is an element of:
   $\PHsubl[\PHl]_S \DEF \bigtimes{a \in S} \PHl_a$.
-  The set of all sub-sets is:
+  The set of all sub-states is:
   $\PHsubl[\PHl] \DEF \bigcup_{S \in\powerset(\PHs)} \PHsubl[\PHl]_S$.
@@
   $\PHget{(s \Cap a_i)}{a} = a_i \wedge \forall b \neq a, \PHget{(s \Cap a_i)}{b} = \PHget{s}{b}$.
-  We also extend this definition to a set of processes given that all processes are from different sorts by the override of each process:
+  Under the condition that all processes are from different sorts,
+  we can also extend this definition to a set of processes
+  by the override of each process independently:
   $\forall ps \in \PHsubl[\PHl], s \Cap \toset{ps} = s \underset{a_i \in \toset{ps}}{\Cap} a_i$.
 \end{definition}
+The notation $\toset{ps}$ represents the set of all elements in $ps$
+(which is not a set but a tuple)
+as defined on page~\pageref{notations}.
 %
@@
   If $s \in \PHl$,
-  a \emph{scenario} $\delta$ from $s$ is a sequence of actions of $\PHh$ that can be played successively in $s$.
+  a \emph{scenario} $\delta$ from $s$ is a (possibly empty) sequence of actions of $\PHh$
+  that can be played successively in $s$.
   The set of all scenarios from $s$ is noted $\Sce(s)$.
@@
 
-In \pref{def:restriction}, we define the $n$-reduction of a given PH as the PH with $n$ classes of priorities in which only actions of priority lower or equal to $n$ are considered.
-\begin{definition}[PH $n$-reduction]
+\modMF{
+In \pref{def:restriction}, we define the $1$-reduction of a given PH as the model
+in which only actions of highest priority lower are considered.
+\begin{definition}[PH $1$-reduction]
 \label{def:restriction}
-  If $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$ is a Process Hitting with $k$ classes of priorities and $n \in \segm{1}{k}$, we denote $\restriction{\PH}{n}$
-  the $n$-reduction of $\PH$.
-  $\restriction{\PH}{n} = (\PHs; \PHl; \PHa'^{\langle n \rangle})$ is a PH with $n$ classes of priorities with:
-  $$\PHa'^{\langle n \rangle} = (\PHa^{(1)}; \dots; \PHa^{(n)})$$
-  Furthermore, we denote: $\restriction{\Sce}{n}(s)$ the set of scenarios from $s$ in $\restriction{\PH}{n}$.
+  If $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$ is a Process Hitting with $k$ classes of priorities, we denote by $\restriction{\PH}{1}$ the $1$-reduction of $\PH$:
+  $\restriction{\PH}{1} = (\PHs; \PHl; \PHa'^{\langle 1 \rangle})$
+  with $\PHa'^{\langle 1 \rangle} = (\PHa^{(1)})$.
+  Furthermore, we denote by $\restriction{\Sce}{1}(s)$ the set of scenarios from $s$ in $\restriction{\PH}{1}$.
 \end{definition}
+}
 
@@
   \begin{align*}
-    \PHs &= \{ a, b, c, ab \} \enspace, \\
-    \PHl_a &= \{ a_0, a_1 \} \enspace, & \PHl_b &= \{ b_0, b_1 \} \enspace, \\
-    \PHl_c &= \{ c_0, c_1 \} \enspace, & \PHl_{ab} &= \{ ab_{00}, ab_{01}, ab_{10}, ab_{11} \} \\ \enspace,
-    \PHa^{\langle 2 \rangle} &= (\PHa^{(1)}; \PHa^{(2)})
+    \PHs &= \{ a, b, c, ab \} \enspace,
+      & \PHa^{\langle 2 \rangle} &= (\PHa^{(1)}; \PHa^{(2)}) \enspace, \\
+    \PHl_a &= \{ a_0, a_1 \} \enspace,
+      & \PHl_b &= \{ b_0, b_1 \} \enspace, \\
+    \PHl_c &= \{ c_0, c_1 \} \enspace,
+      & \PHl_{ab} &= \{ ab_{00}, ab_{01}, ab_{10}, ab_{11} \}
   \end{align*}
@@
   \centering
-  \scalebox{1.2}{
+  \scalebox{1.3}{
   \begin{tikzpicture}
+    \path[use as bounding box] (-.2,-.5) rectangle (7.2,5.7);
+
     \TSort{(0,0)}{a}{2}{l}
@@
 
-    \THit{a_0}{prio}{ab_3}{.south}{ab_1}
-    \THit{a_0}{prio}{ab_2}{.south}{ab_0}
-    \THit{a_1}{prio}{ab_1}{.south}{ab_3}
-    \THit{a_1}{prio}{ab_0}{.south}{ab_2}
+    \THit{a_0.-20}{bend right,in=270,prio}{ab_3}{.south}{ab_1}
+    \THit{a_0.20}{bend right,in=250,prio}{ab_2}{.south}{ab_0}
+    \THit{a_1.-20}{bend right,in=240,prio}{ab_1}{.south}{ab_3}
+    \THit{a_1.20}{bend right,in=220,prio}{ab_0}{.south}{ab_2}
 
-    \THit{b_0}{prio}{ab_3}{.north}{ab_2}
-    \THit{b_0}{prio}{ab_1}{.north}{ab_0}
-    \THit{b_1}{prio}{ab_2}{.north}{ab_3}
-    \THit{b_1}{prio}{ab_0}{.north}{ab_1}
+    \THit{b_0}{bend right,in=70,out=40,prio}{ab_3}{.north}{ab_2}
+    \THit{b_0.south west}{bend right,in=140,out=40,prio}{ab_1}{.north}{ab_0}
+    \THit{b_1}{bend right,in=90,out=40,prio}{ab_2}{.north}{ab_3}
+    \THit{b_1}{bend right,in=170,out=10,prio}{ab_0}{.north}{ab_1}
 
@@
     \THit{b_1}{selfhit}{b_1}{.west}{b_0}
-    \THit{a_0.north}{bend left}{b_0}{.west}{b_1}
-    \THit{b_0.south}{bend right=60}{a_0}{.west}{a_1}
+    \THit{a_0.110}{bend left}{b_0}{.210}{b_1}
+    \THit{b_0.-10}{bend right=60}{a_0}{.west}{a_1}
 
@@
 
-	\path[bounce, bend right=55]
-      \TBounce{ab_0}{}{ab_2}{.west}
-      \TBounce{ab_1}{}{ab_3}{.west}
+	\path[bounce, bend right=90] %55]
+      \TBounce{ab_0}{in=-110}{ab_2}{.south west}
+      \TBounce{ab_1}{in=-110}{ab_3}{.south west}
 	;
-	\path[bounce, bend left=20]
+	\path[bounce, bend left=25]
       \TBounce{ab_3}{}{ab_1}{.south east}
@@
 	;
-    \path[bounce, bend right=20]
-      \TBounce{ab_3}{}{ab_2}{.north east}
-      \TBounce{ab_1}{}{ab_0}{.north east}
+    \path[bounce, bend right=30]
+      \TBounce{ab_3}{}{ab_2}{.30}
+      \TBounce{ab_1}{}{ab_0}{.30}
     ;
-    \path[bounce, bend left=30]
-      \TBounce{ab_2}{}{ab_3}{.west}
-      \TBounce{ab_0}{}{ab_1}{.west}
+    \path[bounce, bend left=40]
+      \TBounce{ab_2}{}{ab_3}{.150}
+      \TBounce{ab_0}{}{ab_1}{.150}
     ;
-    \path[bounce, bend right]
+    \path[bounce, bend right=60]
       \TBounce{a_1}{}{a_0}{.north west}
@@
     ;
-    \path[bounce, bend left]
+    \path[bounce, bend left=60]
       \TBounce{a_0}{}{a_1}{.south west}
@@
   }
-  \caption{
-  \label{fig:ph-livelock}
+  \caption{%
+  \label{fig:ph-livelock}%
     An example of PH with $2$ classes of priorities.
-    Sorts are represented as labelled boxes and processes as circles with their identifier on the side.
+    This model represents the interaction of two exclusive components $a$ and $b$,
+    that cannot be active simultaneously, and that degrade over time.
+    Furthermore, the cooperative sort $ab$ allows to encode a conjunction between
+    the processes $a_1$ and $b_1$ in order to activate the third component $c$.
+    Sorts are represented by labelled boxes and processes by circles with their identifier on the side.
     Actions of $\PHh^{(1)}$ are represented by thick arrows and actions of $\PHh^{(2)}$ are represented by thin arrows;
-    the hit part of each action in drawn in plain line and the bounce part is in dotted line.
-    Greyed processes stand for a possible state $s = \PHstate{a_1, b_0, c_0, ab_{10}}$.
+    the hit part of each action is drawn in plain line and the bounce part is in dotted line.
+    Greyed processes stand for the following possible state: $\PHstate{a_1, b_0, c_0, ab_{10}}$.
   }
@@
 
-\todo{Rajouter un exemple}
-
 Cooperation between processes to make another process bounce can be expressed in PH by building a \emph{cooperative sort},
 which allows to encode any kind of Boolean function \cite{PMR10-TCSB}.
-\pref{fig:ph-livelock} shows an example of cooperation between processes $a_1$ and $b_1$ to make $c_0$ bounce to $c_1$:
-a cooperative sort $ab$ is defined with 4 processes (one for each sub-state of the presence of processes $a_1$ and $b_1$).
+\pref{fig:ph-livelock} shows an example of cooperation between processes $a_1$ and $b_1$
+in order to allow $c_0$ to bounce to $c_1$.
+In this model, a cooperative sort $ab$ is defined with 4 processes
+in order to represent each possible configuration
+of the presence of processes $a_1$ and $b_1$
+(“only $a_1$ is active”, “only $b_1$ is active”, “both are active” and “both are not active”).
 For the sake of clarity, the processes of $ab$ are indexed using the sub-state they represent.
@@
 (\eg $\PHfrappe{a_1}{ab_{00}}{ab_{10}}$ and $\PHfrappe{a_1}{ab_{01}}{ab_{11}}$).
-Then, to represent the cooperation between $a_1$ and $b_1$, the process $ab_{11}$ hits $c_0$ to make it bounce to $c_1$ instead of independent hits from $a_1$ and $b_1$.
+Then, to represent the cooperation between $a_1$ and $b_1$, the process $ab_{11}$ hits $c_0$ to make it bounce to $c_1$.
+Thus, this method based on a cooperative sort
+replaces independent actions, \eg $\PHhit{a_1}{c_0}{c_1}$ and $\PHhit{b_1}{c_0}{c_1}$,
+that would not be sufficient to model the conjunction
+between $a_1$ and $b_1$.
 
@@
 }
+\label{ssec:priorities}
 
@@
 
-\subsection{Restrictions}
+\subsection{Conditions}
 \label{ssec:hypothesis}
@@
 which would allow the play of an infinite sequence of prioritised actions in “zero time”.
-As a consequence, the set $\restriction{\Sce}{1}$ is finite.
+As a consequence, the set $\restriction{\Sce}{1}$,
+\modMF{
+that is, the set of scenarios playable only with actions of $\PHh^{(1)}$,
+(see \pref{def:restriction}),
+}
+is finite.
 
@@
 
-Given a sort $a\in\Sigma$ and a state $s\in L$, 
-we denote $\pfp_s(a)$ (\pref{def:pfp}) the processes of sort $a$ that can be present after
-playing all actions of priority $1$,
+Given a sort $a\in\Sigma$ and a state $s\in \PHl$, 
+we denote by $\pfp_s(a)$ (\pref{def:pfp}) the processes of sort $a$ that can be present after
+playing all actions of priority $1$ in $s$,
 which is always defined because of \pref{cr:bounded}.
@@
 (\pref{def:cs}).
-The former is a sort that is hit only by actions with priority greater than $2$,
+The former is a sort that is hit only by actions with priority greater than or equal to $2$,
 \modMF{%
@@
 }%
-We note $\components\subset\Sigma$ the set of well-formed components,
-and $\cs\subset\Sigma$ the set of well-formed cooperative sorts.
+% We denote by $\components\subseteq\Sigma$ the set of well-formed components,
+% and $\cs\subseteq\Sigma$ the set of well-formed cooperative sorts.
+\modMF{
+We note that some non-determinism may be involved during the update of
+cooperative sorts.
+However, this non-determinism is only confined to the choice of the order of the
+actions played or the update of one cooperative sort before another.
+Thus, there is no non-determinism in the focal process of each cooperative sort,
+that is, from the point of view of lower-priority actions.
+}
 
@@
   A sort $a \in \PHs$ is a \emph{well-formed component} if and only if:
-    $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) \geq 2$ \enspace.
+    $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) \geq 2$.
+  We denote by $\components$ the set of all well-formed components.
 \end{definition}
@@
   Given a sort $a$, $\compin(a)\DEF \conn(a)\cap\components$ where
-$\conn(a) \subset \PHs$ is the smallest set of sorts satisfying the following properties:
+  $\conn(a) \subseteq \PHs$ is the smallest set of sorts satisfying the following properties:
   \begin{align*}
@@
   \end{enumerate}
+  We denote by $\cs$ the set of all well-formed cooperative sorts.
 \end{definition}
@@
 Because of \pref{def:cs}(\ref{csai}), we denote in the following: $\pfp_s(a) = a_i$.
-Furthermore, because of \pref{def:cs}(\ref{css}), we denote $\csState(a_i)$ the set of sub-states represented by the process $a_i$ of any cooperative sort $a$ (\pref{def:csState}).
+Furthermore, because of \pref{def:cs}(\ref{css}), we denote by $\csState(a_i)$ the set of sub-states modelled by the process $a_i$ of any cooperative sort $a$ (\pref{def:csState}),
+that is, the sub-states predecessors for which the focal process of $a$ is $a_i$.
 \begin{definition}[$\csState : \PHproc \rightarrow \powerset(\PHproc)$]
@@
   $$\csState(a_i) \DEF \{ \toset{ps} \mid ps\in\PHsubl[\PHl]_{\compin(a)} \wedge
-  							\exists s\in\PHl, (ps\subset s\wedge \pfp_s(a)=a_i)
+  							\exists s\in\PHl, (ps\subseteq s\wedge \pfp_s(a)=a_i)
 							\}$$
@@
 
-\subsection{Consequences of the restrictions}
+\subsection{Consequences of the Conditions}
 
@@
 
-\pref{lem:hcompcomp} states that for a given state $s$, and for any action $h = \PHhit{a_i}{b_j}{b_k}$ where $a$ and $b$ are components,
+\pref{lem:hcompcomp} states that for a given state $s$, and for any action $h = \PHhit{a_i}{b_j}{b_k} \in \PHh^{(2)}$ where $a$ and $b$ are components,
 if $\PHget{s}{a} = a_i$ and $\PHget{s}{b} = b_j$, then
@@
 \pref{lem:hcscomp} states the same if $a$ is a cooperative sort, under the condition that $a$ is updated in $s$.
-In other words, prioritized actions cannot prevent a non-prioritized action
-to be eventually played, they only ``delay'' it,
+In other words, prioritized actions cannot prevent an action of priority $2$
+to be eventually played; they only ``delay'' it,
 provided only that the hitter of this action
-matches the active process in the updated state.
+matches the active process of its sort in the updated state.
+\modMF{
+We note that in some cases, namely, when all cooperative sorts are already updated,
+this scenario of prioritized actions is empty
+and the action can be immediately played.
+We note also that there may exist several scenarios that fit into these lemmas;
+however, the choice of one scenario over another has no consequence due to
+the unicity of the focal process of the cooperative sorts
+(see (\ref{csai}) in \pref{def:cs}).
+}
 

### 2014-12-19 parts/example.tex
minor comments of the reviewers

@@
 be used in such a case.
-In \label{ssec:ex-tcrsig}, we apply our method to a large-scale model
+In \pref{ssec:ex-tcrsig}, we apply our method to a large-scale model
 of the T-cell receptor signalling pathway
@@
     modelling the process of metazoan segmentation.
-    Actions of $\ov{\PHh}^{(3)}$ (lowest priority) are in thin lines,
+    Component $a$ models the pigment production, and is influenced by
+    component $c$ that has the role of a clock,
+    while $f$ represents the wavefront propagation.
+    If component $a$ oscillates (that is, its active process changes regularly)
+    then regular stripes are created on the metazoan.
+    Actions of $\ov{\PHh}^{(3)}$ (lowest priority) are represented in thin lines,
     actions of $\ov{\PHh}^{(2)}$ (intermediate priority) are in thick lines,
     and actions of $\ov{\PHh}^{(1)}$ (highest priority), whose only purpose is to update the cooperative sort $fc$,
-    are not represented but modelled by the double dashed arrows.
+    are not explicitly represented but modelled by the double dashed arrows.
   }
@@
     which is the flattening of the PH in \pref{fig:metazoan-php}.
-    Actions of $\PHh^{(2)}$ (unprioritised) are in thin lines,
+    In other words, this model has exactly the same dynamics as
+    \pref{fig:metazoan-php}, but its actions make only two classes of priorities.
+    Actions of $\PHh^{(2)}$ (unprioritised) are represented in thin lines,
     and actions of $\PHh^{(1)}$ (prioritised) which are used to update cooperative sorts,
     are abstracted by thick dashed arrows.
+    The additional cooperative sort $fa$ is used to model the previous action
+    $\PHhit{f_1}{c_0}{c_1}$,
+    which belonged to the lowest class of priority and could be preempted 
+    especially by action $\PHhit{fc_{10}}{a_0}{a_1}$.
   }
@@
 \modMF{
-By analysing the detail of the results, one can find out that one of the output, NFkB, can never be activated.
+By analysing the detail of the results, one can find out that one of the outputs, NFkB, can never be activated.
 In other words, FkB$_1$ is never reachable, whatever the state of the inputs,

### 2014-12-19 parts/intro.tex
forgot coloration in intro
minor comments of the reviewers

@@
 It was later enriched in many directions and widely used to elucidate many biological questions.
-Among these questions, a major one is to understand precisely how biological systems evolve and behave; why and how they change their usual behaviours…
+Among these questions, a major one is to understand precisely how biological systems evolve and behave; why and how they change their usual behaviours, etc.
 This leads to questions about the reachability (possible or inevitable) of some states.
 The ultimate goal is to discover how it could be possible to prevent biological systems from reaching some pathological states.
+\todo{Ajouter des références}
 
@@
 As a matter of fact, the abstractions we get are more or less rough or accurate.
-Usual formal frameworks for such modelling activities are state-transition systems or process algebras. % Petri nets
+Prevalent formal frameworks for such modelling activities are state-transition systems or process algebras. % Petri nets
 We developed a quite similar framework named the Process Hitting \cite{PMR10-TCSB},
@@
 They are based on the fact that most biological models have few levels of expression per component:
-in Boolean networks~\cite{kauffman69,Thomas73} there are only two levels per component and in their multivalued equivalent, Asynchronous Discrete Networks~\cite{deJong02}, components rarely have more that four levels.
+in Boolean networks~\cite{kauffman69,Thomas73} there are only two levels per component and in their multivalued equivalent, Asynchronous Discrete Networks~\cite{deJong02}, components rarely have more than four levels.
 
@@
 
-\paragraph{Contributions}
+\subsection*{Contributions}
 Since our formalism (the Process Hitting) can be considered as a subset of Calculus of Communicating Systems, %is inspired from the $\pi$-calculus,
@@
 This local reachability under-approximation can be also easily extended to study the reachability of a global state.
-Furthermore, we provide a new extended under-approximation method to decide a successive reachability property.
+Furthermore, we provide a new extended under-approximation method to check a successive reachability property.
 
@@
 
+\modMF{
 The main addition in this paper compared to \cite{FPMR13-CS2Bio} is
@@
 %Both aim at extending the application range of the static analysis we developed.
+}
 
-\paragraph*{Notations}
+\subsection*{Notations}
+\label{notations}
 %We denote: $\segm{a}{b} = \{ a, a+1, \dots, b-1, b \}$.
 
+\paragraph*{Sets}
 If $A$ is a finite set,
@@
 and $\segm{x}{y} = \{ x, x+1, \dots, y-1, y \}$ is the set of natural numbers from $x$ to $y$ included.
-If $x = (x_i)_{i \in \segm{1}{n}}$ is a sequence of elements indexed by $i \in \segm{1}{n}$,
+The Cartesian product is denoted $\times$;
+if $z$ is a tuple of $n$ components, $\toset{z}$ denotes the corresponding set:
+$\toset{z} = \{z_1, \cdots, z_n\}$.
+
+\paragraph*{Sequences}
+If $n \in \sN$ and
+$x = (x_i)_{i \in \segm{1}{n}}$ is a sequence of elements indexed by $i \in \segm{1}{n}$,
 %we denote %$|x| = (b-a)+1$ the size of this sequence and
-$\indexes{x} = \segm{1}{n}$ is the set of indexes of this sequence.
+then $\indexes{x} = \segm{1}{n}$ is the set of indexes of this sequence.
+Furthermore, if $a, b \in \indexes{x}$ with $a \leq b$,
+then $x_{a..b} = (x_i)_{i \in \segm{a}{b}}$ is a subsequence of $x$.
+%from element $n$ to element $m$ inclusive.
 We also denote by $\emptyseq$ the empty sequence.
+
+\paragraph*{Functions and least fixed point}
 If $A$ and $B$ are sets,
 $f : A \rightarrow B$ denotes an application $f$ that maps the elements of $A$ to elements of $B$.
+Furthermore, if $f$ is a monotonically increasing and bounded function, then
 $\lfp{x_0}{x}{x'}$ is the least fixed point of the function $x \mapsto x'$ which is greater than $x_0$.
-The Cartesian product is denoted $\times$.
-If $z$ is a tuple of $n$ components, $\toset{z}$ denotes the corresponding set
-	$\{z_1, \cdots, z_n\}$.

### 2014-12-19 parts/models-ph-dn.tex
remove a lot of comments
TODO++ in the translation sections
minor comments of the reviewers

@@
 Hitting using two classes of priorities
-that respects all Conditions of \pref{ssec:hypothesis},
 and prove a weak bisimulation relation.
+This translation is important as it allows to efficiently study the dynamics ADNs
+by using the static analysis developed in \pref{sec:sa};
+indeed, the bisimulation relation ensures that the dynamics of the
+resulting PH model are accurately the same than the original.
+Furthermore, the obtained model is ensured to respect
+all Conditions of \pref{ssec:hypothesis}.
 
@@
 a^j_k$ to make it bounce to the process $f^i_{\varsigma \Cap a^j_k}$.
-%$f^i_{\varsigma'}$ where $\get{\varsigma'}{a^j}=a^j_k$.
 $\Hits^{(2)}$ is the set of actions encoding the transitions in the ADN:

### 2014-12-19 parts/models-ph-php.tex
TODO++ in the translation sections
minor comments of the reviewers

@@
 
-Consider a PH with $k \in \sNN$ classes of priories
+In this section, we give a translation that allows to obtain,
+from any PH model with any number of priorities,
+a PH model with 2 classes of priorities
+that respects all Conditions of \pref{ssec:hypothesis}.
+Such a translation is thus particularly useful to be able to study the dynamics of
+any kind of PH model by using the static analysis developed in \pref{sec:sa},
+which is not possible if these conditions are not met.
+
+We consider in the following a PH with $k \in \sNN$ classes of priories
 $\ov{\PH} = (\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}})$

### 2014-12-19 parts/sa.tex
minor comments of the reviewers

@@
 This abstraction is later used to propagate an objective on a given sort
-by creating new objectives on other sots.
+by creating new objectives on other sorts.
 In the following, we denote: $\Sol = \powerset(\PHproc)$.
@@
 
-We denote $\concr(\w)$ (\pref{def:concr}) the set of scenarios concretising an objective sequence $\w$ in the context $\ctx$.
+We denote by $\concr(\w)$ (\pref{def:concr}) the set of scenarios concretising an objective sequence $\w$ in the context $\ctx$.
 In \pref{def:uconcr}, we define $\uconcr(\w)$ as equal to $\concr(\w)$ if and only if $\concr(\w)$ contains scenarios starting from all states $s \subseteq \ctx$.
@@
 \end{definition}
+
+\noindent
+The notation $\delta_{a..b}$ denotes the subsequence of $\delta$
+between indexes $a$ and $b$, as defined on page \pageref{notations}.
+
 \begin{definition}[$\uconcr: \OS \rightarrow \powerset(\Sce)$]
@@
 
-For any objective $P$ and context $\ctx$, \pref{def:maxCont} gives the set of processes of sort $\PHsort(P)$ that are required to solve $P$ in $\ctx$, given by $\gCont_\ctx(\PHsort(P), P)$.
+For any objective $P$ and context $\ctx$, \pref{def:maxCont} gives the set of processes of sort $\PHsort(P)$ that are required to solve $P$ in $\ctx$, denoted by $\gCont_\ctx(\PHsort(P), P)$.
 \begin{definition}[$\gCont_\ctx : \Sigma \times \Obj \rightarrow \powerset(\PHproc)$]
@@
 \modMF{
-A graph of local causality $\aB = (\cwV, \cwE)$
+A graph of local causality $\myB = (\cwV, \cwE)$
 is a graph where $\cwV \subseteq \Proc \cup \Obj \cup \Sol$ is the set of vertices
@@
 \modMF{
-However, this graph $\aB$ alone is not sufficient to check the reachability of
+However, this graph $\myB$ alone is not sufficient to check the reachability of
 an objective sequence $\w$ from an initial context $\ctx$;
@@
   \begin{align}
-    \w &\subseteq \cwV \label{eq:Vw} \\
+    \modMF{\toset{\w}} &\subseteq \cwV \label{eq:Vw} \\
 %    P \in \cwVObj &\Rightarrow \PHbounce(P) \in \cwV \label{eq:Vproc} \\
@@
 
-\todo{“Saturated” partout}
-
 In the saturated graph of local causality, an edge $(p, ps) \in \Proc \times \Sol$
-is said to be coherent (\pref{def:coherent}) if none of the processes in $ps$ conflict with the children processes of $ps$.
+is said to be coherent (\pref{def:coherent}) if none of the processes in $ps$ conflict with the successor processes of $ps$,
+\modMF{
+that is, the successors of $ps$ that are in $\Bv \cap \Proc$.
+}
 Then, \pref{th:approxinf} gives a sufficient condition for the concretisation of a sequence of objectives in a given context,
@@
   An edge $(x, y) \in \cwE$ is said to be coherent if and only if:
-  $(x, y) \in \Be \cap (\Proc \times \Sol) \Rightarrow y$ has no children process $a_j \in \Bv \cap \Proc$ so that $\exists a_i \in y$, $a_i \neq a_j$.
+  $(x, y) \in \Be \cap (\Proc \times \Sol) \Rightarrow y$ has no successor $a_j \in \Bv \cap \Proc$ so that $\exists a_i \in y$, $a_i \neq a_j$.
 \end{definition}
@@
 
-Computing the saturated graph of local causality is polynomial in the number of sorts in $\PH$ and exponential in the number of processes in one sort.
+\modMF{
+Regarding the complexity of the method,
+computing the saturated graph of local causality is polynomial in the number of sorts in $\PH$ and exponential in the number of processes in one sort.
 Checking the properties allowing to apply \pref{th:approxinf} is polynomial in the size of the graph.
-Furthermore, it is possible to compute only a subset of $\V \cap \Sol$;
-in this case, the overall method turns out to be exponential in the number of solutions to each objective.
+Therefore, building and checking process can be considered polynomial in the size
+of the PH model, provided that each sort only is contains a few processes.
+We note that this is particularly true for biological models, where
+each component usually contains a limited number of expression levels.
+In addition, it is possible to “factorize” cooperative sorts
+modelling more than two components,
+as explained in \pref{ssec:cooperation},
+in order to reduce their number of processes.
+}
+
+\modMF{
+We note furthermore that in case the method developed in this section is not conclusive,
+it is possible to compute only a subset of $\Bv \cap \Sol$,
+by removing some solutions from the initial graph of local causality $\myB$,
+or by removing them from the saturated graph of local causality $\cwB$ and by trimming it.
+\pref{th:approxinf} is then still valid on the partial graph obtained,
+which can lead to more conclusiveness by removing parts of the graph
+that were not necessary for the reachability
+(such as cycles for instance).
+If one wants to test each possible subset of solutions,
+the overall method then turns out to be exponential
+in the number of solutions to each objective.
 Our method can thus be considered as efficient compared to regular model-checking which is usually PSPACE-complete~\cite{Harel02}.
+}
 
@@
     \pref{th:approxinf} is inconclusive on this example as edge $(ab_{11}, \{ a_1, b_1 \}) \in \Proc \times \Sol$ (here represented with a double line) is not coherent (\pref{def:coherent}).
-    Indeed, $a_0 \in \Proc$ is a child of $\{ a_1, b_1 \}$, but $a_0 \neq a_1$ (and the same also stands for $b_0$).
+    Indeed, $a_0 \in \Proc$ is a successor of $\{ a_1, b_1 \}$, but $a_0 \neq a_1$ (and the same also stands for $b_0$).
   }
@@
 
-It is also possible to compute the reachability of a set of states $S \subseteq \PHl$ by creating several actions $\PHhit{\total_s}{\reach_0}{\reach_1}$ in $\PHh^{(2)}$ for each state $s \in S$,
-or on a sub-state $s \in \PHsubl[\PHl]_S$ of a set of components $S \subset \PHs$ by adapting the sort $\total$ with: $\PHl_\total = \PHsubl[\PHl]_S$
+It is also possible to compute the reachability of a set of states $\Lambda \subseteq \PHl$ by creating several actions $\PHhit{\total_s}{\reach_0}{\reach_1}$ in $\PHh^{(2)}$ for each state $s \in \Lambda$,
+or on a sub-state $s \in \PHsubl[\PHl]_S$ of a set of components $S \subseteq \PHs$ by adapting the sort $\total$ with: $\PHl_\total = \PHsubl[\PHl]_S$
 
@@
 there exists a set of processes $ps\in\lastprocs(P)$
-such that $ps \subset (s\play\delta)$.
+such that $ps \subseteq (s\play\delta)$.
 Hence, if $\muconcr_{\ctx'\Cap ps}(\w')\neq\emptyset$,
@@
 		  \hitter{\zeta_{\card\zeta}}\in lps$;
-\item $\forall b_j\in lps, b\in\cs, \exists ps\in\csState(b_j), ps\subset lps$;
+\item $\forall b_j\in lps, b\in\cs, \exists ps\in\csState(b_j), ps\subseteq lps$;
 \item $\nexists lps'\in\lastprocs(\obj{a_i}{a_j}), lps'\subset lps \wedge
@@
 If $\uconcr(P)\neq\emptyset$,
-for all $s\in \PHl, s\subset\ctx$,
+for all $s\in \PHl, s\subseteq\ctx$,
 there exists a scenario $\delta\in\uconcr(P)\cap\Sce(s)$;
@@
 $\exists ps\in\lastprocs(P)$ such that
-$(s\play\delta)\subset\ctx'\Cap ps$.
+$(s\play\delta)\subseteq\ctx'\Cap ps$.
 Hence, if $\muconcr_{\ctx'\Cap ps}(\w')\neq\emptyset$,
@@
 Hence, $\delta\concat\delta'$ is a scenario playable in $s$.
-Therefore, for all $s\in \PHl, s\subset\ctx$, there exists a scenario
+Therefore, for all $s\in \PHl, s\subseteq\ctx$, there exists a scenario
 concretising $\w$.

### 2014-12-19 parts/suppl-sa.tex
minor comments of the reviewers

@@
 
-Let $(a_i, ps) \in \Bee{\Proc}{\Sol}$ be an edge linking the required process of a cooperative sort to a solution set and suppose all children of $ps$ are concretisable.
+Let $(a_i, ps) \in \Bee{\Proc}{\Sol}$ be an edge linking the required process of a cooperative sort to a solution set and suppose all successors of $ps$ are concretisable.
 We label all processes of $ps$ by an integer: $ps = \{ p_n \}_{n \in \indexes{ps}}$.
@@
 
-  \item Suppose all children objectives of $P$ are concretisable.
+  \item Suppose all successors objectives of $P$ are concretisable.
     If $\exists (P, Q) \in \Bee{\Obj}{\Obj}$, then by hypothesis,
@@
       $\muconcr_{s}(P) \neq \emptyset$.
-    Else, by \pref{def:maxCont}, the concretisations of the children of $P$ require no process of sort $\PHsort(P)$.
+    Else, by \pref{def:maxCont}, the concretisations of the successors of $P$ require no process of sort $\PHsort(P)$.
       Furthermore, there exists $\zeta \in \BS(P)$ so that $(P, \aZ) \in \Bee{\Obj}{\Sol}$.

### 2014-12-21 main.tex
add TODOs after review
some more explanations in static analysis
begin extraction of the scenario
add sets of actions
fixes and suggestions of Morgan

@@
 
-\usepackage[english]{babel}
+\usepackage[UKenglish]{babel}
 \usepackage[utf8]{inputenc}
@@
 \newrefformat{fig}{Fig.~\ref{#1}}
+\newrefformat{tab}{Table~\ref{#1}}
 \newrefformat{lem}{Lemma~\ref{#1}}
@@
 
+% Ajouts et progression
+\def\modMF#1{\textcolor{teal}{#1}}
+\def\modLP#1{\textcolor{magenta}{#1}}
+\def\modMM#1{\textcolor{blue}{#1}}
+\def\modOR#1{\textcolor{olive}{#1}}
+%\def\modMF#1{#1} \def\modLP#1{#1} \def\modMM#1{#1} \def\modOR#1{#1}
+
 % Special notations
@@
 This allowed to define very efficient static analysis based on local causality to compute reachability properties.
-However, in the case of cooperations between components (for example, when two components are supposed to interact with a third one only when they are in a given configuration), the approach leads to an over-approximated interleaving between actions, because of the pure asynchronous semantics of the model.
+However, in some cases, this modelling lacks some preemption features
+that would allow to model relative time constraints between interactions.
 
-To address this issue, we propose an extended definition of the framework, including priority classes for actions.
-In this paper, we focus on a restriction of the Process Hitting with two classes of priorities and a specific behaviour of the components, that is sufficient to tackle the aforementioned problem of cooperations.
-We develop a new refinement for the under-approximation of the static analysis to give accurate results for this class of Process Hitting models.
-Then we show that this class of models is sufficient to represent any
+In this paper, we propose an extension of the Process Hitting framework
+by using classes of priorities in order to improve its expressivity.
+We also show that these priorities allow to represent accurate Boolean gates in order to model
+cooperations between components
+(that is, for instance, when two components are supposed to interact with a third one
+only when they are in a given configuration)
+which was not possible before.
+
+Furthermore, we develop in this paper a new refinement for the under-approximation of the static analysis
+to give accurate results on Process Hitting models.
+This method applies to a specific sub-class of models,
+but this class turns out to be sufficiently expressive to represent any
 Process Hitting model with an arbitrary number of classes of priorities,
-and even any Asynchronous Discrete Networks, either Boolean or multivalued.
-Our method thus allows to efficiently under-approximate reachability properties
+thus guaranteeing a wide field of application of our method.
+Finally, we show that Process Hitting allows to accurately model
+any Asynchronous Discrete Networks, either Boolean or multivalued.
+Our static analysis method thus allows to efficiently under-approximate reachability properties
 in Asynchronous Discrete Networks,

### 2014-12-21 parts/def-ph.tex
fixes and suggestions of Morgan

@@
 they are equivalent to Boolean gates.
-The static analysis developed in the next section can only be applied
-to PH models belonging to this specific class.
+Technically, the static analysis developed in the next section has to be applied
+to PH models belonging to this specific class with only two sets of priorities.
 However, it has to be noted that this class is in fact as expressive as
-the class of all possible PH models with priorities (see \pref{ssec:flattening}).
+the class of all possible PH models with priorities (see \pref{ssec:flattening}),
+and that the static analysis developed is thus not limited to this sub-class of models.
 }%

### 2014-12-21 parts/example.tex
fixes and suggestions of Morgan

@@
 and demonstrate how the flattening of \pref{ssec:flattening}
-be used in such a case.
+can be used in such a case.
 In \pref{ssec:ex-tcrsig}, we apply our method to a large-scale model

### 2014-12-21 parts/intro.tex
fixes and suggestions of Morgan

@@
 
-Discrete modelling frameworks for biological networks is an active research field where formal methods have proved that they were very powerful.
+Discrete modelling frameworks for biological networks is an active research field where formal methods have proven that they were very powerful.
 Such a work started in the seventies.
@@
 Among these questions, a major one is to understand precisely how biological systems evolve and behave; why and how they change their usual behaviours, etc.
-This leads to questions about the reachability (possible or inevitable) of some states.
+This leads to questions about the (possible or inevitable) reachability of some states.
 The ultimate goal is to discover how it could be possible to prevent biological systems from reaching some pathological states.
@@
 We developed a quite similar framework named the Process Hitting \cite{PMR10-TCSB},
-consisting in a restriction where the evolution of a component is determined by the state of at most one other component that does not evolve.
+consisting in a restriction of these frameworks where the evolution of a component is determined by the state of at most one other component that does not evolve.
 In a sense, these kind of actions are of the form $X + Y \rightarrow X + Y'$ where $X$ behaves like a catalyst molecule that “hits” another molecule $Y$ and changes it into $Y'$, without being changed itself.
@@
 \subsection*{Contributions}
+\todo{Compléter les contributions}
 Since our formalism (the Process Hitting) can be considered as a subset of Calculus of Communicating Systems, %is inspired from the $\pi$-calculus,
@@
 Process Hitting with two classes of priority,
-we provide in \pref{sec:encodings} formal encodings of Asynchronous Discrete Networks and general
-Process Hitting models with priorities.
-Those encodings result in a Process Hitting fulfilling the conditions for our
-static analysis and support the broad applicability of our method.
+we provide in \pref{sec:encodings} a “flattening” of any Process Hitting model into
+this class of models,
+so that its application is not restricted to it.
+We also give in the same section a formal encodings of Asynchronous Discrete Networks,
+allowing to efficiently study this kind of widespread models.
 
@@
 \modMF{
-The main addition in this paper compared to \cite{FPMR13-CS2Bio} is
-%two theorems, the first
-\pref{thm:ordered-ua} that gives a method to cope with successive reachability,
-and obtain more conclusive results in the case of several successive objectives.
-Two other additions are 
-\pref{th:bisimPHP} which states that any Process Hitting model with any number of classes of priorities
+The main addition in this paper compared to \cite{FPMR13-CS2Bio} are the following:
+\pref{th:bisimPHP} states that any Process Hitting model with any number of classes of priorities
 can be represented with only two classes of priorities,
-thus extending the scope of our method to any possible Process Hitting model,
-and \todo{def extraction}
-which allows to extract a concrete scenario when our static analysis method
+thus extending the scope of our method to any possible Process Hitting model;
+\pref{thm:ordered-ua} gives a method to cope with successive reachability,
+and obtain more conclusive results in the case of several successive objectives;
+\todo{def extraction} allows to extract a concrete scenario when our static analysis method
 is conclusive.
-%Both aim at extending the application range of the static analysis we developed.
+%All aim at extending the application range of the static analysis we developed.
 }

### 2014-12-21 main.tex
more corrections from the suggestions of the reviewers

@@
 by using classes of priorities in order to improve its expressivity.
-We also show that these priorities allow to represent accurate Boolean gates in order to model
-cooperations between components
-(that is, for instance, when two components are supposed to interact with a third one
-only when they are in a given configuration)
-which was not possible before.
-
-Furthermore, we develop in this paper a new refinement for the under-approximation of the static analysis
+Furthermore, we develop a new refinement for the under-approximation of the static analysis
 to give accurate results on Process Hitting models.
@@
 thus guaranteeing a wide field of application of our method.
-Finally, we show that Process Hitting allows to accurately model
-any Asynchronous Discrete Networks, either Boolean or multivalued.
-Our static analysis method thus allows to efficiently under-approximate reachability properties
-in Asynchronous Discrete Networks,
-as it is illustrated on the model-checking of a signalling network of 94
+
+Finally, we also show that the priorities
+allow to represent accurate Boolean gates in order to model
+cooperations between components
+(that is, for instance, when two components are supposed to interact with a third one
+only when they are in a given configuration)
+which was not possible before.
+This allows to accurately model
+Asynchronous Discrete Networks, either Boolean or multivalued,
+and efficiently under-approximate reachability properties
+in these models.
+We illustrate this on the model-checking of a signalling network of 94
 components, which is unprecedented.

### 2014-12-21 parts/intro.tex
more corrections from the suggestions of the reviewers

@@
 They are based on the fact that most biological models have few levels of expression per component:
-in Boolean networks~\cite{kauffman69,Thomas73} there are only two levels per component and in their multivalued equivalent, Asynchronous Discrete Networks~\cite{deJong02}, components rarely have more than four levels.
+in Boolean networks~\cite{kauffman69,Thomas73} there are only two levels per component, and in their multivalued equivalent~\cite{deJong02}, components rarely have more than four levels.
 
@@
 so that its application is not restricted to it.
-We also give in the same section a formal encodings of Asynchronous Discrete Networks,
-allowing to efficiently study this kind of widespread models.
+We also give in the same section a formal encoding of Asynchronous Discrete Networks,
+that is, the multivalued version of Asynchronous Boolean Networks.
+These models,
+which encompass variables and evolution functions with a limited number of discrete values,
+also called “Logical Networks” in~\cite{Thomas95,deJong02}.
+This encoding thus allows to efficiently study this kind of widespread models.
 

### 2014-12-21 parts/models-ph-dn.tex
more corrections from the suggestions of the reviewers

@@
 
-We exhibit an encoding of Asynchronous Discrete Networks (ADN) with the Process
-Hitting using two classes of priorities
+We exhibit in this section an encoding of Asynchronous Discrete Networks (ADN),
+also called Logical Networks or equivalently René Thomas Models \cite{Thomas95,deJong02},
+with the Process Hitting using two classes of priorities
 and prove a weak bisimulation relation.

### 2014-12-22 parts/def-ph.tex
begin transformation PH to AAN

--- 2014-12-16 parts/def-ph.tex
@@
-\section{The Process Hitting Framework}
+\section{Asynchronous Automata Networks}
 \label{sec:ph}
 
-\todo{Gluer : explication des définitions, etc.}
+We give in this section the definition and the semantics of the Asynchronous Automata Networks (AAN).
+It is a restriction of the classical Synchronous Automata Networks
+where each set of transitions sharing the same label
+can only change one local state at a time.
+\todo{We also discuss how it is related to the local state Hitting framework (with priorities)
+\cite{PMR10-TCSB,FPMR13-CS2Bio}.}
+As shown in \pref{sec:encodings},
+this class of models is equivalent to Asynchronous Discrete Networks,
+and extending it with classes of priorities does not increase its expressivity.
 
-We give in this section the definition and the semantics of the Process Hitting (PH) with priorities, which is an extension of the basic semantics given in~\cite{PMR10-TCSB}.
-Then we describe the modelling of cooperation between components and discuss how the new aforementioned semantics makes this modelling more accurate.
-Finally, in order to perform a static analysis adapted to this new semantics, we give several criteria to restrict the class of models that we can study,
-and give several lemmas that follow.
-This class of models is equivalent to Asynchronous Discrete Networks.
+\subsection{Definition of Asynchronous Automata Networks}
+\label{ssec:PH}
 
-\subsection{Definition of the Process Hitting with $k$ classes of priorities}
-\label{ssec:PH}
-A PH with $k \in \sN^*$ classes of priorities (\pref{def:ph}), also simply called “PH” in the following when it is not ambiguous, gathers a finite number of concurrent \emph{processes} divided into a finite set of \emph{sorts}.
-A process belongs to a unique sort and is noted $a_i$ where $a$ is the sort and $i$ the identifier of the process within the sort $a$.
-Each process stands for a kind of “activity level” of its sort; a state of the PH thus corresponds to a set of processes containing exactly one process of each sort.
+An AAN (\pref{def:ph}) gathers a finite number of concurrent \emph{local states} divided into a finite set of \emph{automata}, also called \emph{components}.
+A local state belongs to a unique automaton and is noted $a_i$ where $a$ is the name of the automaton and $i$ the identifier of the local state within automaton $a$.
+Each local state stands for a kind of “activity level” of its automaton; a \emph{global state} of the AAN thus corresponds to a set of local states containing exactly one local state of each automaton.
 
-The concurrent interactions between processes are defined by a set of \emph{actions} divided into classes of priorities.
-Actions describe the replacement of a process by another of the same sort conditioned by the presence of at most one other process and by the fact that no other action of higher priority can be played in the considered state of the PH.
-An action is denoted by $\PHhit{a_i}{b_j}{b_k}$ where $a_i,b_j,b_k$ are processes of sorts $a$ and $b$.
-It is required that $b_j \neq b_k$ and that $a=b\Rightarrow a_i=b_j$.
-An action $h=\PHfrappe{a_i}{b_j}{b_k}$ is read as ``$a_i$ \emph{hits} $b_j$ to make it bounce to $b_k$'', and $a_i,b_j,b_k$ are called respectively \emph{hitter}, \emph{target} and \emph{bounce} of the action, and can be referred to as $\PHhitter(h), \PHtarget(h), \PHbounce(h)$, respectively.
+The concurrent interactions between local states are defined by a set of \emph{actions}.
+Actions describe the replacement of the active local state of an automaton by another of the same automaton, conditioned by the presence of as many other local states in the model.
+An action is denoted by $\PHhit{A}{b_j}{b_k}$ where $b_j$ and $b_k$ are local states of an automata $b$, and $A$ is a set of local states.
+It is required that $b_j \neq b_k$ and that
+$A$ does not contain a local state of $b$ or two local states of the same automaton.
+An action $h=\PHfrappe{A}{b_j}{b_k}$ is read as ``$A$ \emph{hit} $b_j$ to make it bounce to $b_k$'', and $A$, $b_j$, $b_k$ are called respectively the set of \emph{hitters}, the \emph{target} and the \emph{bounce} of the action, and can be referred to as $\PHhitter(h), \PHtarget(h), \PHbounce(h)$, respectively.
 
-\begin{definition}[Process Hitting with $k$ classes of priorities]
+\begin{definition}[Asynchronous Automata Networks]
 \label{def:ph}
-  If $k \in \sN^*$, a \emph{Process Hitting with $k$ classes of priorities} is a triplet $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$,
-  where $\PHa^{\langle k \rangle} = (\PHa^{(1)}; \dots; \PHa^{(k)})$ is a $k$-tuple and:
+  An \emph{Asynchronous Automata Networks} is a triplet $\PH = (\PHs; \PHl; \PHa)$,
+  where:
   \begin{itemize}
-    \item $\PHs \DEF \{a, b, \dots\}$ is the finite set of \emph{sorts},
-    \item $\PHl \DEF \underset{a \in \PHs}{\times} \PHl_a$ is the finite set of \emph{states}, where $\PHl_a = \{a_0, \ldots, a_{l_a}\}$ is the finite set of \emph{processes} of sort $a \in \PHs$ and $l_a \in \sN^*$.
-Each process belongs to a unique sort: $\forall (a_i; b_j) \in \PHl_a \times \PHl_b, a \neq b \Rightarrow a_i \neq b_j$,
-    \item $\forall n \in \llbracket 1; k \rrbracket, \PHa^{(n)} \DEF \{\PHfrappe{a_i}{b_j}{b_l} \mid (a; b) \in \PHs^2 \wedge (a_i; b_j; b_l) \in \PHl_a \times \PHl_b \times \PHl_b \wedge b_j \neq b_l \wedge a = b \Rightarrow a_i = b_j \}$ is the finite set of \emph{actions of priority $n$}.
+    \item $\PHs \DEF \{a, b, \dots, z\}$ is the finite set of \emph{automata};
+    \item $\PHl \DEF \underset{a \in \PHs}{\times} \PHl_a$ is the finite set of
+      (global) \emph{states},
+      where $\PHl_a = \{a_0, \ldots, a_{l_a}\}$ is the finite set of \emph{local states}
+      of automaton $a \in \PHs$, with $l_a \in \sN^*$,
+      and so that:
+      $\forall (a_i; b_j) \in \PHl_a \times \PHl_b, a \neq b \Rightarrow a_i \neq b_j$;
+    \item $\PHa \DEF \{\PHfrappe{A}{b_j}{b_k} \mid
+      b \in \PHs \wedge (b_j; b_k) \in \PHl_b \times \PHl_b \wedge
+      b_j \neq b_k \wedge
+      \forall a \in \PHs, \card{A \cap \PHl_a} \leq 1 \wedge
+      A \cap \PHl_b = \emptyset \}$ is the finite set of \emph{actions}.
   \end{itemize}
-  We call $\PHproc \DEF \bigcup_{a \in \PHs} \PHl_a$ the set of all processes, and $\PHh \DEF \bigcup_{n \in \segm{1}{k}} \PHh^{(n)}$ the set of all actions.
-  Furthermore, for all $n \in \sN^*$ and $h \in \PHh^{(n)}$, $\prio(h) \DEF n$.
+  Furthermore,
+  we call $\PHproc \DEF \bigcup_{a \in \PHs} \PHl_a$ the set of all local states in the model.
 \end{definition}
@@
 \noindent
-The sort of a process $a_i$ is referred to as $\PHsort(a_i) = a$.
-Given a state $s\in \PHl$, the process of sort $a \in \PHs$ present in $s$ is denoted by $\PHget{s}{a}$, that is the $a$-coordinate of the state $s$.
+The automaton that a local state $a_i$ belongs to is referred to as $\PHsort(a_i) = a$.
+Given a state $s\in \PHl$, the local state of automaton $a \in \PHs$ present in $s$ is denoted by $\PHget{s}{a}$, that is, the $a$-coordinate of the state $s$.
 If $a_i \in \PHl_a$, we define the notation $a_i \in s \EQDEF \PHget{s}{a} = a_i$.
-\pref{def:substate} defines the notion of sub-state on a set of sorts, that is used to focus on the interesting part of a complete state.
-Note that a state is \textit{a fortiori} a sub-state.
-The override of a state $s$ by a process $a_i$ (or by a set of processes)
-is defined in \pref{def:statecap} as the same state in which the process of sort $a$ has been replaced by $a_i$,
-which then allows to define the dynamics of a PH in \pref{def:play}.
+\pref{def:substate} defines the notion of sub-state on a set of automata, that is used to focus on the interesting part of a complete state.
+We note that a state is \textit{a fortiori} a sub-state.
+The override of a state $s$ by a local state $a_i$ (or by a set of local states)
+is defined in \pref{def:statecap} as the same state in which the local state of automaton $a$ has been replaced by $a_i$;
+this is used to define the dynamics of an AAN in \pref{def:play}.
 %
@@
 \label{def:substate}
-  If $S \subset \PHs$ is a set of sorts, a sub-set on $S$ is an element of:
+  If $S \subseteq \PHs$ is a set of automata, a sub-state on $S$ is an element of:
   $\PHsubl[\PHl]_S \DEF \bigtimes{a \in S} \PHl_a$.
-  The set of all sub-sets is:
+  The set of all sub-states is:
   $\PHsubl[\PHl] \DEF \bigcup_{S \in\powerset(\PHs)} \PHsubl[\PHl]_S$.
@@
   Furthermore, if $\mysigma \in \PHsubl[\PHl]$ and $s \in \PHl$, we note:
-    \[\mysigma \subseteq s \EQDEF \forall a_i \in \Proc, a_i \in \mysigma \Rightarrow a_i \in s \enspace.\]
+    \[\mysigma \subseteq s \EQDEF \forall a_i \in \Proc, a_i \in \toset{\mysigma} \Rightarrow a_i \in s\]
+  where the notation $\toset{\mysigma}$ represents
+  the set of components of the Cartesian product $\mysigma$,
+  as defined on page~\pageref{notations}.
 \end{definition}
-%
+
+In the following, we will also use the notation:
+$\PHsublset[\PHl] = \{ \toset{ps} \subseteq \Proc \mid ps \in \PHsubl[\PHl] \}$
+and, by extension:
+$\forall s \in \PHl, \forall ps \in \PHsublset[\PHl],
+  ps \subseteq s \EQDEF \forall a_i \in ps, a_i \in s$.
+We note also that for all action $h \in \PHh$, by definition of an AAN, we have:
+$\hitter{h} \in \PHsublset[\PHl]$.
+
 \begin{definition}[$\Cap : \PHl \times \PHproc \rightarrow \PHl$]
 \label{def:statecap}
-  Given a state $s \in \PHl$ and a process $a_i \in \PHproc$, $(s \Cap a_i)$ is the state defined by:
+  Given a state $s \in \PHl$ and a local state $a_i \in \PHproc$, $(s \Cap a_i)$ is the state defined by:
   $\PHget{(s \Cap a_i)}{a} = a_i \wedge \forall b \neq a, \PHget{(s \Cap a_i)}{b} = \PHget{s}{b}$.
-  We also extend this definition to a set of processes given that all processes are from different sorts by the override of each process:
-  $\forall ps \in \PHsubl[\PHl], s \Cap \toset{ps} = s \underset{a_i \in \toset{ps}}{\Cap} a_i$.
+  We can also extend this definition to a set $ps$ of local states,
+  under the condition that all local states of $ps$ are from different automata,
+  by the override of each local state independently:
+  $\forall ps \in \PHsublset[\PHl], s \Cap ps = s \underset{a_i \in ps}{\Cap} a_i$.
 \end{definition}
-%
-\begin{definition}[Dynamics of a PH ($\PHPtrans$)]
+% The notation $\toset{ps}$ represents the set of all elements in $ps$
+% (which is not a set but a tuple)
+% as defined on page~\pageref{notations}.
+
+\begin{definition}[Dynamics of an AAN ($\PHPtrans$)]
 \label{def:play}
-  An action $h = \PHhit{a_i}{b_j}{b_k} \in \PHa^{(n)}$ of priority $n$ is \emph{playable} in $s \in \PHl$
-  if and only if $\PHget{s}{a} = a_i$, $\PHget{s}{b} = b_j$ and $\forall m < n, \forall g \in \PHa^{(m)}, \PHhitter(g) \notin s \vee \PHtarget(g) \notin s$.
-  In such a case, $(s \PHplay h)$ stands for the state resulting from the play of the action $h$ in $s$ and is defined by: $(s \PHplay h) = s \Cap b_k$.
+  An action $h = \PHhit{A}{b_j}{b_k} \in \PHa$ is \emph{playable} in $s \in \PHl$
+  if and only if $A \subseteq s$ and $\PHget{s}{b} = b_j$.
+  In such a case, $(s \PHplay h)$ stands for the state resulting from the play of the action $h$ in $s$, which is defined by: $(s \PHplay h) = s \Cap b_k$.
   Moreover, we denote: $s \PHPtrans (s \PHplay h)$.
@@
 
-In \pref{def:restriction}, we define the $n$-reduction of a given PH as the PH with $n$ classes of priorities in which only actions of priority lower or equal to $n$ are considered.
-\begin{definition}[PH $n$-reduction]
-\label{def:restriction}
-  If $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$ is a Process Hitting with $k$ classes of priorities and $n \in \segm{1}{k}$, we denote $\restriction{\PH}{n}$
-  the $n$-reduction of $\PH$.
-  $\restriction{\PH}{n} = (\PHs; \PHl; \PHa'^{\langle n \rangle})$ is a PH with $n$ classes of priorities with:
-  $$\PHa'^{\langle n \rangle} = (\PHa^{(1)}; \dots; \PHa^{(n)})$$
-  Furthermore, we denote: $\restriction{\Sce}{n}(s)$ the set of scenarios from $s$ in $\restriction{\PH}{n}$.
-\end{definition}
-
 \begin{example}
-  \pref{fig:ph-livelock} gives an example of PH with $2$ classes of priorities where:
+  \pref{fig:ph-livelock} gives an example of AAN where:
   \begin{align*}
-    \PHs &= \{ a, b, c, ab \} \enspace, \\
-    \PHl_a &= \{ a_0, a_1 \} \enspace, & \PHl_b &= \{ b_0, b_1 \} \enspace, \\
-    \PHl_c &= \{ c_0, c_1 \} \enspace, & \PHl_{ab} &= \{ ab_{00}, ab_{01}, ab_{10}, ab_{11} \} \\ \enspace,
-    \PHa^{\langle 2 \rangle} &= (\PHa^{(1)}; \PHa^{(2)})
+    \PHs &= \{ a, b, c \} \enspace,
+      & \PHl_a &= \{ a_0, a_1 \} \enspace, \\
+    \PHl_b &= \{ b_0, b_1 \} \enspace,
+      & \PHl_c &= \{ c_0, c_1 \} \enspace, \\
+    \PHh = \{ \quad
+      & \PHfrappem{a_1}{a_0} \enspace , \quad
+        \PHfrappem{a_0}{a_1} \enspace , \\
+      & \PHfrappem{b_1}{b_0} \enspace , \quad
+        \PHfrappem{b_0}{b_1} \enspace , \\
+      & \PHfrappes{a_1, b_1}{c_0}{c_1} \enspace \quad \qquad \qquad
+      \quad \}
   \end{align*}
-  and the sets of actions are:
-  \begin{align*}
-    \PHh^{(1)} = \{ \quad
-      & \PHfrappe{a_1}{ab_{00}}{ab_{10}} \enspace , \quad
-      \PHfrappe{a_1}{ab_{01}}{ab_{11}} \enspace , \\
-      & \PHfrappe{a_0}{ab_{10}}{ab_{00}} \enspace , \quad
-      \PHfrappe{a_0}{ab_{11}}{ab_{01}} \enspace , \\
-      & \PHfrappe{b_1}{ab_{00}}{ab_{01}} \enspace , \quad
-      \PHfrappe{b_1}{ab_{10}}{ab_{11}} \enspace , \\
-      & \PHfrappe{b_0}{ab_{01}}{ab_{00}} \enspace , \quad
-      \PHfrappe{b_0}{ab_{11}}{ab_{10}}
-    \quad \} \\
-    \PHh^{(2)} = \{ \quad
-      & \PHfrappe{a_1}{a_1}{a_0} \enspace , \quad
-      \PHfrappe{b_0}{a_0}{a_1} \enspace , \\
-      & \PHfrappe{b_1}{b_1}{b_0} \enspace , \quad
-      \PHfrappe{a_0}{b_0}{b_1} \enspace , \\
-      & \PHfrappe{ab_{11}}{c_0}{c_1}
-    \quad \} \\
-  \end{align*}
-%   Note that: $\{ \PHhit{ab_{11}}{c_0}{c_1}, \PHhit{a_1}{a_1}{a_0}, \PHhit{a_0}{b_0}{b_1} \} \subseteq \PHh^{(2)}$.
 
@@
   \centering
-  \scalebox{1.2}{
-  \begin{tikzpicture}
-    \TSort{(0,0)}{a}{2}{l}
-    \TSort{(0,4)}{b}{2}{l}
-    \TSort{(7,2.5)}{c}{2}{r}
+  \scalebox{1.3}{
+  \begin{tikzpicture}[aan]
+%    \path[use as bounding box] (-.2,-.5) rectangle (7.2,5.7);
+    \TSort{(0,3)}{a}{2}{b}
+    \TSort{(0,0)}{b}{2}{t}
+    \TSort{(4,1)}{c}{2}{r}
 
-    \TSetTick{ab}{0}{00}
-    \TSetTick{ab}{1}{01}
-    \TSetTick{ab}{2}{10}
-    \TSetTick{ab}{3}{11}
-    \TSort{(2,2.5)}{ab}{4}{t}
+    \TAction{a_0.south west}{b_0.north west}{b_1.north west}{bend right=20}{left}
+    \TAction{b_0.north east}{a_0.south east}{a_1.south west}{bend right=20}{right}
+    \TActionPlur{}{a_1.north}{a_0.north east}{}{1.5,4}{right}
+    \TActionPlur{}{b_1.south}{b_0.south east}{}{1.5,-1}{left}
+    \TActionPlur{a_1, b_1}{c_0.west}{c_1.south west}{}{2.5,1.5}{left}
 
-    \THit{a_0}{prio}{ab_3}{.south}{ab_1}
-    \THit{a_0}{prio}{ab_2}{.south}{ab_0}
-    \THit{a_1}{prio}{ab_1}{.south}{ab_3}
-    \THit{a_1}{prio}{ab_0}{.south}{ab_2}
-
-    \THit{b_0}{prio}{ab_3}{.north}{ab_2}
-    \THit{b_0}{prio}{ab_1}{.north}{ab_0}
-    \THit{b_1}{prio}{ab_2}{.north}{ab_3}
-    \THit{b_1}{prio}{ab_0}{.north}{ab_1}
-
-    \THit{a_1}{selfhit}{a_1}{.west}{a_0}
-    \THit{b_1}{selfhit}{b_1}{.west}{b_0}
-    \THit{a_0.north}{bend left}{b_0}{.west}{b_1}
-    \THit{b_0.south}{bend right=60}{a_0}{.west}{a_1}
-
-    \THit{ab_3}{}{c_0}{.west}{c_1}
-
-	\path[bounce, bend right=55]
-      \TBounce{ab_0}{}{ab_2}{.west}
-      \TBounce{ab_1}{}{ab_3}{.west}
-	;
-	\path[bounce, bend left=20]
-      \TBounce{ab_3}{}{ab_1}{.south east}
-      \TBounce{ab_2}{}{ab_0}{.south east}
-	;
-    \path[bounce, bend right=20]
-      \TBounce{ab_3}{}{ab_2}{.north east}
-      \TBounce{ab_1}{}{ab_0}{.north east}
-    ;
-    \path[bounce, bend left=30]
-      \TBounce{ab_2}{}{ab_3}{.west}
-      \TBounce{ab_0}{}{ab_1}{.west}
-    ;
-    \path[bounce, bend right]
-      \TBounce{a_1}{}{a_0}{.north west}
-      \TBounce{b_1}{}{b_0}{.north west}
-    ;
-    \path[bounce, bend left]
-      \TBounce{a_0}{}{a_1}{.south west}
-      \TBounce{b_0}{}{b_1}{.south west}
-    ;
-    \path[bounce, bend left]
-      \TBounce{c_0}{}{c_1}{.south west}
-    ;
-    \TState{a_1, b_0, ab_2, c_0}
+    \TState{a_1, b_0, c_0}
   \end{tikzpicture}
   }
-  \caption{
-  \label{fig:ph-livelock}
-    An example of PH with $2$ classes of priorities.
-    Sorts are represented as labelled boxes and processes as circles with their identifier on the side.
-    Actions of $\PHh^{(1)}$ are represented by thick arrows and actions of $\PHh^{(2)}$ are represented by thin arrows;
-    the hit part of each action in drawn in plain line and the bounce part is in dotted line.
-    Greyed processes stand for a possible state $s = \PHstate{a_1, b_0, c_0, ab_{10}}$.
+  \caption{%
+  \label{fig:ph-livelock}%
+    An example of AAN.
+    This model represents the interaction of two exclusive components $a$ and $b$,
+    that cannot be active simultaneously, and that degrade over time.
+    Furthermore, these two components can cooperate to activate $c$
+    if their “active” states ($a_1$ and $b_1$)
+    are present in the same state.
+    Automata are represented by labelled boxes
+    and local states by circles with their identifier on the side.
+    Actions are represented by a dot connected by an edge to every hitter
+    and by an arrows to the target, followed by another dotted arrow towards the bounce.
+    Greyed local states stand for the following possible global state:
+    $\PHstate{a_1, b_0, c_0, ab_{10}}$.
   }
@@
 
-\todo{Rajouter un exemple}
+Cooperations between components are a very common in biological systems.
+They represent the fact that a given regulation is not conditioned by only one condition,
+such as the presence of a given concentration of one substance,
+represented in the model by the activity of the one related local state.
+Instead, in the case of a cooperation, two conditions or have to be bet.
+For example, in the example of \pref{fig:ph-livelock},
+the activation of component $c$ requires the cooperation of $a$ and $b$;
+in practice, this is expressed by a set of two hitters for action
+$\PHfrappes{a_1, b_1}{c_0}{c_1}$.
 
-Cooperation between processes to make another process bounce can be expressed in PH by building a \emph{cooperative sort},
-which allows to encode any kind of Boolean function \cite{PMR10-TCSB}.
-\pref{fig:ph-livelock} shows an example of cooperation between processes $a_1$ and $b_1$ to make $c_0$ bounce to $c_1$:
-a cooperative sort $ab$ is defined with 4 processes (one for each sub-state of the presence of processes $a_1$ and $b_1$).
-For the sake of clarity, the processes of $ab$ are indexed using the sub-state they represent.
-Hence, $ab_{10}$ represents the sub-state $\PHstate{a_1,b_0}$, and so on.
-Each process of sort $a$ and $b$ hit $ab$ to make it bounce to the process reflecting the status of the sorts $a$ and $b$
-(\eg $\PHfrappe{a_1}{ab_{00}}{ab_{10}}$ and $\PHfrappe{a_1}{ab_{01}}{ab_{11}}$).
-Then, to represent the cooperation between $a_1$ and $b_1$, the process $ab_{11}$ hits $c_0$ to make it bounce to $c_1$ instead of independent hits from $a_1$ and $b_1$.
+Such a cooperation can be represented in Process Hitting by using a \emph{cooperative sort},
+whose aim is to represent a Boolean formula~\cite{PMR10-TCSB}.
+The different local states of a cooperative sort represent the possible configurations
+of a set of automata,
+and actions allow to update the active local state of the cooperative sort
+in order to have it match the configuration of these automata.
+Then, one or several actions can be added from the desired local states of the cooperative sort
+in order to abstract multiple requirements.
+Cooperative sorts have the advantage to not require any supplementary semantics
+than those of standard Process Hitting,
+but at the cost of slightly over-approximating the expected dynamics of a true Boolean gate.
+Indeed, nothing forces these actions to be played as soon as possible,
+thus resulting in a possible temporal shift between the evolution
+of the active process of the cooperative sorts and those of the automata it represents.
+In other words, a cooperative sorts does not necessarily represent the configuration
+of a given set of automata, but only a combination of past states.
 
-We note that cooperative sorts are standard PH sorts and do not involve any
-special treatment regarding the semantics of related actions.
-Furthermore, it is possible to “factorise” cooperative sorts in order to decrease the number of processes created within each cooperative sort.
-For example, if three processes $x_1$, $y_1$ and $z_1$ cooperate,
-it is preferable to create a cooperative sort $xy$ with 4 processes to state the presence of $x_1$ and $y_1$
-and a second cooperative sort $xyz$ with 4 processes to state the presence of $xy_{11}$ and $z_1$,
-rather than a unique cooperative sort with 8 processes stating the presence of $x_1$, $y_1$ and $z_1$.
-This “factorisation” allows to prevent the combinatorial explosion of the number of processes in cooperative sorts,
-especially for cooperations between more than three processes.
-It may have computational consequences as the static analysis method developed in~\pref{sec:sa} does not suffer from the number of sorts but from the number of processes in each sort.
-
-\modMF{
-\subsection{Justification of the priorities}
-}
-
-As explained previously,
-the construction of cooperation in PH allows to encode any Boolean function between cooperating processes \cite{PMR10-TCSB}.
-However, in the original version of the PH framework,
-which contained no classes of priorities
-(or, equivalently, only one class of priority),
-the representation of such Boolean functions was not accurate.
-Indeed, the lack of priorities did not allow cooperative sorts
-to always encode the \emph{current state} of several sorts, as expected,
-but only a \emph{combination of past states}.
-
-Let us for example consider the PH model 
-$\PH = (\PHs; \PHl; \PHh^{\angles{2}})$ from \pref{fig:ph-livelock},
-and the “merged” version of this model:
-$\PH' = (\PHs; \PHl; \PHh'^{\angles{1}})$,
-that is, where $\PHh'^{\angles{1}} = \PHh = \PHh^{(1)} \cup \PHh^{(2)}$.
-In other words, $\PH'$ has the same sorts and processes
-(and therefore the same states) than $\PH$,
-but the actions of the two classes of priories of the latter
-are united into one only class in the former.
-
-Starting from state $\PHstate{a_1, b_0, c_0, ab_{10}}$,
-it is not possible to reach a state where the processes $a_1$ and $b_1$
-are simultaneously active, in either $\PH$ and $\PH'$.
-Indeed, in both cases the actions hitting sorts $a$ and $b$ require that both
-$a_0$ and $b_0$ are active in order to activate $b_1$ (\resp $a_1$).
-Therefore, given the fact that the cooperative sort $ab$ represents
-the combined states of $a$ and $b$,
-and that the action $\PHhit{ab_{11}}{c_0}{c_1}$
-represents a Boolean “conjunction” between $a$ and $b$
-(that is, requires that both have process name “1” active),
-the expected behaviour is that $c_1$ cannot be reached.
-
-However, starting from state $\PHstate{a_1, b_0, c_0, ab_{10}}$,
-it is still possible to activate $c_1$ in $\PH'$
-by visiting the following sequence of states:
-\begin{align*}
-  & \PHstate{a_1, b_0, c_0, ab_{10}} \concat
-    \PHstate{a_0, b_0, c_0, ab_{10}} \concat
-    \PHstate{a_0, b_1, c_0, ab_{10}} \concat \\
-  & \qquad\qquad
-    \PHstate{a_0, b_1, c_0, ab_{11}} \concat
-    \PHstate{a_0, b_1, c_1, ab_{11}}
-\end{align*}
-This is due to the fact that after playing the action
-$\PHhit{a_1}{a_1}{a_0}$,
-the absence of priorities does not constrain the cooperative sort to be updated.
-We clearly see in this example that without priorities,
-the cooperative sort $ab$ only represents a combination of the past
-states of $a$ and $b$, without any notion of simultaneity.
-
-Adding classes of priorities allows to remove this undesired behaviour,
-especially by prioritizing all actions updating the cooperative sorts.
-Indeed, the previous behaviour is not possible in the original model $\PH$,
-where the actions of highest priority ($\PHh^{(1)}$)
-force the update of the cooperative sort before any other action of
-low priority ($\PHh^{(2)}$) can be played.
-The closest possible sequence of states is the following,
-where $ab_{11}$ can never be activated:
-\begin{align*}
-  & \PHstate{a_1, b_0, c_0, ab_{10}} \concat
-    \PHstate{a_0, b_0, c_0, ab_{10}} \concat
-    \PHstate{a_0, b_0, c_0, ab_{00}} \\
-  & \qquad\qquad
-    \PHstate{a_0, b_1, c_0, ab_{00}} \concat
-    \PHstate{a_0, b_1, c_0, ab_{01}}
-\end{align*}
-
-We conclude that the addition of priorities,
-by allowing to represent accurate Boolean gates in the form of cooperative sorts,
-thus allows to reach the same expressivity as Asynchronous Discrete Networks
-(see \pref{sec:dn}).
-Therefore, the next sections \todo{nouvelle section ?}
-formalize this use of the highest class of priority
-to force the update of cooperative sorts.
-The aim of the rest of this paper is to allow the static analysis
-of the dynamics on PH with priorities,
-and for this we rely on models involving
-such prioritised actions to update cooperative sorts.
-However, despite focusing on a sub-class of PH models,
-we show in \pref{ssec:flattening}
-that this sub-class is in fact as expressive as the class
-of all PH with classes of priorities.
-
-\subsection{Restrictions}
-\label{ssec:hypothesis}
-
-In the scope of this paper, we focus on a specific class of PH models
-in which actions of $\PHh^{(1)}$, called \emph{prioritised actions},
-are only used to model cooperations in the form of strict logic gates.
-\modMF{%
-For this, we formally define in this section the notion of well-formed cooperative sorts,
-and we require that prioritized actions can only be used to update them.
-This particular form in the actions allows to apply the static analysis
-developed in \pref{sec:sa}, which is not directly possible in the general case.
-However, we note here that this class of models is not less expressive than
-the general PH framework as given in \pref{def:ph};
-indeed, the translation given in \pref{ssec:flattening} proves that
-this class of models can reproduce any desired dynamics of the general case.
-}%
-
-We consider in this section a PH model with $k$ classes of priorities: $\PH = (\PHs; \PHl; \PHa^{\langle k \rangle})$, with $k \in \sNN$
-and we define here the restrictions that lead to this class of models.
-
-\pref{cr:bounded} states that the dynamics of the studied model $\PH$ contain no infinite sequence of prioritised actions.
-As these actions can be considered as non-biological and therefore instantaneous, we thus prevent the existence of any Zeno-like behaviour
-which would allow the play of an infinite sequence of prioritised actions in “zero time”.
-As a consequence, the set $\restriction{\Sce}{1}$ is finite.
-
-\begin{condition}[Bounded termination]
-\label{cr:bounded}
-  The dynamics of $\restriction{\PH}{1}$ contains no cycles:
-  $\exists N \in \sN, \forall s \in \PHl, \forall \delta \in \restriction{\Sce}{1}(s), |\delta| \leq N$.
-\end{condition}
-
-\modMF{%
-\begin{example}
-  The model of \pref{fig:ph-livelock} respects \pref{cr:bounded}:
-  indeed, whatever are the active processes of $a$ and $b$,
-  it is never possible to indefinitely play actions of $\PHh^{(1)}$.
-\end{example}
-}%
-
-Given a sort $a\in\Sigma$ and a state $s\in L$, 
-we denote $\pfp_s(a)$ (\pref{def:pfp}) the processes of sort $a$ that can be present after
-playing all actions of priority $1$,
-which is always defined because of \pref{cr:bounded}.
-\modMF{%
-This definition will be useful for cooperative sorts,
-in order to determine their local stable state in every configuration,
-and thus which configuration each of their processes represent.
-}%
-
-\begin{definition}[$\pfp : \PHl \times \PHs \rightarrow \powerset(\PHproc)$]
-\label{def:pfp}
-  For all $s \in \PHl$ and $a \in \PHs$,
-  \begin{align*}
-    \pfp_s(a) = \{ \get{(s\play\delta)}{a} \in \PHl_a &\mid \delta \in \restriction{\Sce}{1}(s)
-					\wedge\nexists h\in\PHh^{(1)}, (\delta; h) \in\restriction{\Sce}{1}(s) \}
-  \end{align*}
-\end{definition}
-
-\modMF{%
-\begin{example}
-  In the model of \pref{fig:ph-livelock}, we have for instance:
-  $\pfp_{s}(ab) = \{ab_{10}\}$ for the state $s = \PHstate{a_1, b_0, ab_{00}, z_0}$.
-  Indeed, starting from $\PHstate{a_1, b_0, ab_{00}, z_0}$,
-  it is only possible to play the action $\PHfrappe{a_1}{ab_{00}}{ab_{10}} \in \PH^{(1)}$,
-  and no other action in $\PH^{(1)}$ is playable in the resulting state
-  $\PHstate{a_1, b_0, ab_{10}, z_0}$.
-  Thus, process $ab_{10}$ can be used to represent the configuration $\PHstate{a_1, b_0}$.
-\end{example}
-}%
-
-Our second condition (\pref{cr:compcs}) imposes that any sort in the Process
-Hitting is either a well-formed component (\pref{def:component}) or a well-formed cooperative sort
-(\pref{def:cs}).
-The former is a sort that is hit only by actions with priority greater than $2$,
-\modMF{%
-and thus stands for a regular biological component.
-}%
-The latter is a sort that is hit only by actions with priority $1$ and which
-always converges to the same process with respect to the state of the components
-that have an influence on it (\pref{def:conn}).
-\modMF{%
-Indeed, we require that each process of a cooperative sort corresponds
-to exactly one configuration of the sorts it represents.
-}%
-We note $\components\subset\Sigma$ the set of well-formed components,
-and $\cs\subset\Sigma$ the set of well-formed cooperative sorts.
-
-\begin{definition}[Well-formed component ($\components$)]
-\label{def:component}
-A sort $a \in \PHs$ is a \emph{well-formed component} if and only if:
-    $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) \geq 2$ \enspace.
-\end{definition}
-
-\begin{definition}[Components influence $(\compin: \PHs\to\powerset(\components))$]
-\label{def:conn}
-Given a sort $a$, $\compin(a)\DEF \conn(a)\cap\components$ where
-$\conn(a) \subset \PHs$ is the smallest set of sorts satisfying the following properties:
-\begin{align*}
-a\in\conn(a) &
-\\
-\forall h\in  \PHh^{(1)},
-	\Sigma(\target{h})\in\conn(a) & \Longrightarrow \Sigma(\hitter{h})\in\conn(a)
-\end{align*}
-\end{definition}
-
-\modMF{%
-\begin{example}
-  For the PH model of \pref{fig:ph-livelock}, we have:
-  \begin{align*}
-    \conn(a) &= \{a\} &
-    \conn(ab) &= \{a, b, ab\} \\
-    \conn(b) &= \{b\} &
-    \conn(z) &= \{z\}
-  \end{align*}
-  Therefore, $\compin(ab) = \{a, b\}$.
-\end{example}
-}%
-
-\begin{definition}[Well-formed cooperative sorts ($\cs$)]
-\label{def:cs}
-A sort $a \in \PHs$ is a \emph{well-formed cooperative} sort if and only if:
-\begin{enumerate}[(i)]
-\item $\forall h\in\PHh, \Sigma(\PHtarget(h))=a \Longrightarrow \prio(h) = 1$;
-\item\label{csai} $\forall s\in\PHl, \card{\pfp_s(a)} = 1$;
-\item\label{css} $\forall a_i \in \PHl_a, \exists s \in \PHl, a_i\in\pfp_s(a)$;
-\item $\forall \sigma\in\PHsubl[\PHl]_{\compin(a)},
-			\forall s,s'\in\PHl,
-				\sigma\subseteq s\wedge \sigma\subseteq s'\Rightarrow 
-							\pfp_s(a) = \pfp_{s'}(a)$\enspace.
-\end{enumerate}
-\end{definition}
-
-\begin{condition}[Components \& cooperative sorts partition]
-\label{cr:compcs}
-  $$\PHs = \components \cup \cs \wedge \components \cap \cs = \emptyset$$
-\end{condition}
-
-\modMF{%
-\begin{example}
-  The sorts $a$, $b$ and $z$ of \pref{fig:ph-livelock} are well-formed components
-  regarding \pref{def:component}.
-  Furthermore, $ab$ of is a well-formed cooperative sort,
-  with respect to \pref{def:cs}, which models cooperation between $a$ and $b$
-  because $\compin(ab) = \{a, b\}$ and:
-  \begin{enumerate}[(i)]
-    \item it is only hit by actions in $\PH^{(1)}$;
-    \item in every state, it has exactly one focal process;
-    \item each of its processes corresponds to at least one state of the model;
-    \item its focal processes only depend on $a$ and $b$.
-  \end{enumerate}
-  Therefore, we obviously have:
-  $\components = \{a, b, z\}$ and $\cs = \{ab\}$,
-  which respects \pref{cr:compcs}.
-\end{example}
-}
-
-We note that any sort $a$ that is hit by no action (\ie $\forall h \in \PHh, \PHsort(\target{h}) \neq a$)
-does comply with both definitions of well-formed components and well-formed cooperative sorts.
-In this case, such a sort can be arbitrarily affected to either set.
-Such a case may occur for “input” sorts (whose state is initially fixed and does not evolve)
-or some special cases of cooperative sorts produced by the translations of \pref{sec:encodings}.
-In the following we simply write “component” (\resp “cooperative sort”) instead of “well-formed component” (\resp “well-formed cooperative sort”).
-
-Because of \pref{def:cs}(\ref{csai}), we denote in the following: $\pfp_s(a) = a_i$.
-Furthermore, because of \pref{def:cs}(\ref{css}), we denote $\csState(a_i)$ the set of sub-states represented by the process $a_i$ of any cooperative sort $a$ (\pref{def:csState}).
-\begin{definition}[$\csState : \PHproc \rightarrow \powerset(\PHproc)$]
-\label{def:csState}
-  If $a \in \cs$ and $a_i \in \PHl_a$, 
-  $$\csState(a_i) \DEF \{ \toset{ps} \mid ps\in\PHsubl[\PHl]_{\compin(a)} \wedge
-  							\exists s\in\PHl, (ps\subset s\wedge \pfp_s(a)=a_i)
-							\}$$
-\end{definition}
-
-\modMF{%
-\begin{example}
-  We have, for the cooperative sort $ab$ of \pref{fig:ph-livelock}
-  $\csState(ab_{10}) = \{\{a_1, b_0\}\}$,
-  which is a direct consequence of the fact that $\pfp_{s}(ab) = \{ab_{10}\}$
-  with $s = \PHstate{a_1, b_0, ab_{00}, z_0}$.
-\end{example}
-}%
-
-\subsection{Consequences of the restrictions}
-
-In this subsection, we give several general lemmas that can be derived from the restrictions of \pref{ssec:hypothesis},
-in the special case of a PH model with $2$ classes of priorities $\PH = (\PHs; \PHl; \PHa^{\langle 2 \rangle})$.
-These results will help building the static analysis of \pref{sec:sa}.
-
-We first denote by $\update(s)$ (\pref{def:update}) the state equivalent to $s$
-\modMF{%
-but in which the active process of all cooperative sorts is changed to the process
-that represent the current state of the components.
-}%
-This state is unique due to the properties of $\pfp$ given in the previous subsection.
-Then, \pref{lem:update} states that from any state, there exists a scenario updating the cooperative sorts of this state,
-\modMF{%
-thus allowing to end in $\update(s)$.
-}%
-
-\begin{definition}[$\update : \PHl \rightarrow \PHl$]
-\label{def:update}
-  For all $s \in \PHl$, we define:
-  \begin{align*}
-    \update(s) = s \Cap \{ \pfp_{s}(a) \mid a \in \cs \} \enspace.
-  \end{align*}
-\end{definition}
-%
-\begin{lemma}
-\label{lem:update}
-  $\forall s \in \PHl, \exists \delta \in \restriction{\Sce}{1}(s), s \PHplay \delta = \update(s)$
-\end{lemma}
-%
-\begin{proof}
-  Let $a$ be a cooperative sort so that $\PHget{s}{a} \neq \pfp_s(a)$.
-  Given the definition of $\pfp_s(a)$, there exists a scenario $\delta$ updating $a$ in $s$ so that
-  $\forall \delta' \in \restriction{\Sce}{1}(s \PHplay \delta)$, $\PHget{(s \PHplay \delta \PHplay \delta')}{a} = \pfp_s(a)$.
-\end{proof}
-
-\modMF{%
-\begin{example}
-  Regarding the model of \pref{fig:ph-livelock}, we have:
-  $\update(s) = \PHstate{a_1, b_0, ab_{10}, z_0}$,
-  with $s = \PHstate{a_1, b_0, ab_{00}, z_0}$.
-  We note that in $\update(s)$, only the active process of the cooperative sort
-  $ab$ is changed
-  to the process representing the presence of both $a_1$ and $b_0$.
-  Furthermore, \pref{lem:update} states that there exists a scenario $\delta$
-  of actions in $\PH^{(1)}$
-  so that $s \play \delta = \update(s)$.
-  Indeed, $\delta = (\PHfrappe{a_1}{ab_{00}}{ab_{10}})$ is such a scenario,
-  here containing only one action.
-\end{example}
-}%
-
-\pref{lem:hcompcomp} states that for a given state $s$, and for any action $h = \PHhit{a_i}{b_j}{b_k}$ where $a$ and $b$ are components,
-if $\PHget{s}{a} = a_i$ and $\PHget{s}{b} = b_j$, then
-$h$ can always be played after a series of prioritised hits (and these hits do not prevent it to be fired).
-\pref{lem:hcscomp} states the same if $a$ is a cooperative sort, under the condition that $a$ is updated in $s$.
-In other words, prioritized actions cannot prevent a non-prioritized action
-to be eventually played, they only ``delay'' it,
-provided only that the hitter of this action
-matches the active process in the updated state.
-
-\begin{lemma}
-\label{lem:hcompcomp}
-  $\forall s \in \PHl, \forall a,b \in \components, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh,$\\
-  $(\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j) \Rightarrow (\exists \delta \in \restriction{\Sce}{1}(s),
-  (s \PHplay \delta) \PHPtrans (s \PHplay \delta \PHplay h))$
-\end{lemma}
-%
-\begin{proof}
-  From \pref{lem:update}, there exists a scenario $\delta$ with: $(s \PHplay \delta) = \update(s)$.
-  As $a,b \in \components$, $a_i \in (s \PHplay \delta)$ and $b_j \in (s \PHplay \delta)$.
-  Finally, by definition of $\update(s)$, no prioritised action can be played in $(s \PHplay \delta)$, thus $h$ can be played in $(s \PHplay \delta)$.
-\end{proof}
-%
-\begin{lemma}
-\label{lem:hcscomp}
-  $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, a \in \cs, b \in \components,$\\
-  $(\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j \wedge \pfp_s(a) = a_i) \Rightarrow (\exists \delta \in \restriction{\Sce}{1}(s),
-  (s \PHplay \delta) \PHPtrans (s \PHplay \delta \PHplay h))$
-\end{lemma}
-\begin{proof}
-  Similar to the proof of \pref{lem:hcompcomp};
-  as $a_i \in \pfp_s(a)$, $a_i \in (s \PHplay \delta)$.
-\end{proof}
-
-\modMF{%
-\begin{example}
-  Considering the model of \pref{fig:ph-livelock} and starting from the state
-  $s = \PHstate{a_1, b_0, ab_{00}, z_0}$,
-  \pref{lem:hcompcomp} states that the action $h = \PHfrappe{a_1}{a_1}{a_0}$
-  is playable after a scenario $\delta$ of prioritized actions.
-  In this case, $h$ is indeed playable in the state
-  $s \play \delta = \PHstate{a_1, b_0, ab_{10}, z_0}$,
-  where $\delta = (\PHfrappe{a_1}{ab_{00}}{ab_{10}}) \in \restriction{\Sce}{1}(s)$.
-\end{example}
-}%
-
-\medskip
-
-\modMF{%
-This section aimed at defining the PH framework in a general fashion,
-and focused on a more specific class of PH models
-that will be used later in this paper.
-We gave a definition of the notion of cooperative sort,
-a special sort with no explicit biological existence or meaning,
-which is used to model the joint action of several components
-on another one.
-Using this definition, we defined a specific class of PH models
-that assign a specific role to the set of actions
-of highest priority:
-these actions can only be used to update cooperative sorts to ensure that
-they are equivalent to Boolean gates.
-The static analysis developed in the next section can only be applied
-to PH models belonging to this specific class.
-However, it has to be noted that this class is in fact as expressive as
-the class of all possible PH models with priorities (see \pref{ssec:flattening}).
-}%
+In~\cite{FPMR13-CS2Bio}, the formalization of classes of priorities into the Process Hitting
+was proposed in order to add some missing features,
+such as the possibility to abstract time properties of regulation or reaction rates.
+Another consequence of the addition of priorities was the possibility to fix
+the aforementioned temporal shift, and thus be able to model accurate Boolean gates,
+by prioritizing the actions used to update the cooperative sorts.
+The AAN formalism proposed in this paper have in fact the same expressivity than
+Process Hitting with classes of priorities.
+Indeed, the actions with multiple hitters play the role of cooperative sorts,
+and the classes of priorities can be encoded into AAN without priorities,
+as detailed in \pref{ssec:flattening}.

### 2014-12-22 parts/intro.tex
begin transformation PH to AAN

@@
 \paragraph*{Sequences}
+We denote by $\emptyseq$ the empty sequence.
 If $n \in \sN$ and
@@
 %from element $n$ to element $m$ inclusive.
-We also denote by $\emptyseq$ the empty sequence.
+Finally, if $x$ is a sequence, $\toset{x}$ also denotes the corresponding set:
+$\toset{x} = \{x_1, \cdots, x_{\card{x}}\}$.
 

### 2014-12-22 parts/sa.tex
fixes and suggestions of Morgan
begin transformation PH to AAN

@@
 
-The aim of this section is to define the problem of reachability in a PH,
+The aim of this section is to define the problem of reachability in an AAN,
 and propose an under-approximation allowing to efficiently solve it.
 The static analysis presented here is inspired from~\cite{PMR12-MSCS}.
-
-We consider in this section a PH model $\PH = (\PHs; \PHl; \PHa^{\langle 2 \rangle})$ with $2$ classes of priorities
-that respects all Conditions (\ref{cr:bounded} \& \ref{cr:compcs}) of \pref{ssec:hypothesis}.
+We consider in this section an AAN $\PH = (\PHs; \PHl; \PHa)$.
 
@@
 The main idea behind the static analysis presented in this section
-is to abstract the dynamics of a Process Hitting model
-by a more general and easier to analyse dynamics.
+is to abstract the dynamics of an AAN model
+by a dynamics that is more general and easier to analyse.
 For this, we focus on the notion of objective:
-an objective is a couple of processes (\eg $\PHobj{a_i}{a_j}$) whose reachability
+an objective is a couple of local states (\eg $\PHobj{a_i}{a_j}$) whose reachability
 is required to ensure the global reachability property considered;
@@
 and reach a state containing $a_j$.
-Given the particular form of the actions in Process Hitting,
-the solving of such an objective raises new objectives in the general case,
-because each action can be triggered by (at most) one process from a different sort.
-Indeed, each of these processes also have to be reached before the required actions are played.
+Given the particular form of the actions in AANs,
+the solving of such an objective raises new objectives in the general case.
+%because each action can be triggered by (at most) one local state from a different automaton.
+Indeed, each of these local states also have to be reached before the required actions are played.
 However, the order of the considered actions is abstracted,
@@
 
-The reachability of a process $a_j$ of a given sort $a$ from another process $a_i$ is called an objective and is denoted $\PHobjp{a}{i}{j}$ (\pref{def:obj}).
-\begin{definition}[Objective ($\Obj$)]
+The reachability of a local state $a_j$ of a given automaton $a$,
+starting from another local state $a_i$,
+is called an objective and is denoted $\PHobjp{a}{i}{j}$ (\pref{def:obj}).
+\begin{definition}[Objective ($\Obj$) \& Objective Sequence ($\OS$)]
 \label{def:obj}
-  If $a \in \components$, the reachability of a process $a_j$ from a process $a_i$ is called an \emph{objective}, noted $\PHobj{a_i}{a_j}$.
+  If $a \in \components$, the reachability of a local state $a_j$ from a local state $a_i$ is called an \emph{objective}, noted $\PHobj{a_i}{a_j}$.
   The set of all objectives is called $\Obj \DEF \{ \PHobj{a_i}{a_j} \mid a \in \components \wedge (a_i, a_j) \in \PHl_a \times \PHl_a \}$.
@@
 
-  We define an \emph{objective sequence} as a sequence of objectives in which each objective target must be equal to the previous objective bounce of the same sort, if it exists.
+  We define an \emph{objective sequence} as a sequence of objectives in which each objective target must be equal to the previous objective bounce of the same automaton, if it exists.
   The set of all objective sequences is denoted by $\OS$.
@@
 \modMF{
-to each sort in the model, a context maps a set of processes in this sort.
+to each automaton in the model, a context maps a set of local states in this automaton.
 }
@@
 \label{def:context}
-  A \emph{context} $\ctx$ associates to each sort in $\PHs$ a non-empty subset of its processes:
+  A \emph{context} $\ctx$ associates to each automaton in $\PHs$ a non-empty subset of its local states:
   $\forall a \in \PHs, \PHget{\ctx}{a} \subseteq \PHl_a \wedge \PHget{\ctx}{a} \neq \emptyset$.
@@
 \label{def:ctxcap}
-  For any $\ctx\in\Ctx$ and set of processes $ps \in \powerset(\PHproc)$,
+  For any $\ctx\in\Ctx$ and set of local states $ps \in \powerset(\PHproc)$,
   the override of $\ctx$ by $ps$ is noted $\ctx \Cap ps$ and is defined by:
@@
 and the play of $\delta$ in $\ctx$ is $\ctx \PHplay \delta = \ctx \Cap \ceil(\delta)$,
-where $\ceil(\delta)$ is the set containing the last process in the sequence $\delta$ (hitter or bounce) of every sort mentioned in $\delta$.
+where $\ceil(\delta)$ is the set containing the last local state in the sequence $\delta$ (hitter or bounce) of every automaton mentioned in $\delta$.
 
-Finally, a bounce sequence on a sort $a$ (\pref{def:bs}) is a sequence of actions hitting $a$
-in which the bounce process of each action is the hitter process of the following action.
-Bounce sequences are used to find local solutions to a given objective:
+Finally, a bounce sequence on a automaton $a$ (\pref{def:bs}) is a sequence of actions hitting $a$
+in which the bounce of each action equals the hitter of the following action.
+Bounce sequences are used to find local solutions to a given objective;
 \modMF{
-indeed, the bounce sequences related to an objective $\PHobj{a_i}{a_j}$
-only take depend on the bounces of the actions hitting the sort $a$.
+indeed, the bounce sequences solving an objective $\PHobj{a_i}{a_j}$
+only depend on the bounce part of the actions hitting the automaton $a$
+and not on the hitters.
 }%
-A bounce sequence on $a$ can be abstracted into the minimal sets of its hitters that are not in sort $a$ (\pref{def:aBS}).
-This abstraction is later used to propagate an objective on a given sort
-by creating new objectives on other sorts.
-In the following, we denote: $\Sol = \powerset(\PHproc)$.
+Then, a bounce sequence on $a$ can be abstracted into
+its combinations of hitters outside automaton $a$ (\pref{def:aBS});
+% the minimal sets of its sets of hitters that are not in automaton $a$ (\pref{def:aBS}).
+This abstraction is later used to propagate an objective on a given automaton
+by creating new objectives on other automata,
+by considering the sets of hitters required by the actions involved.
+
 \begin{definition}[Bounce sequence ($\BS$)]
@@
   \]
-  $\BS(\obj{a_i}{a_j}) = \emptyset$ if there is no way to reach $a_j$ from $a_i$
+  Furthermore, $\BS(\obj{a_i}{a_j}) = \emptyset$ if there is no way to reach $a_j$ from $a_i$
   and $\emptyseq \in \BS(\obj{a_i}{a_i})$
   \modMF{
-  for a trivial objective $\PHobj{a_i}{a_i}$.
+  for any trivial objective.
   }
 \end{definition}
-%
+
+In the following, we denote: $\sSol = \powerset(\PHproc)$
+\moda{%
+and $\Sol = \powerset(\sSol)$.
+}%
+\modMF{%
+The elements of $\sSol$ are sets of local states,
+and will later represent sets of hitters of a given action
+that are required to be active simultaneously in order to play this related action.
+The elements in $\Sol$ are sets of sets of hitters,
+and represent the requirements to play a whole bounce sequence.
+}%
+
 \begin{definition}[$\aBS:\Obj \rightarrow \powerset(\Sol)$]
 \label{def:aBS}
-  The \emph{abstractions of bounce sequences} of an objective $P$, denoted by the set $\aBS(P)$, are the sets of hitters of bounce sequences solving $P$:
+  The \emph{abstractions of bounce sequences} of an objective $P$, denoted by the set $\aBS(P)$, are the minimal sets of hitters of the bounce sequences solving $P$:
   \[
-    \aBS(P) \DEF \{ \abstr{\zeta} \in \Sol \mid \zeta \in \BS(P), \nexists \zeta' \in \BS(P), \abstr{\zeta'} \subsetneq \abstr{\zeta} \} \enspace,
+    \aBS(P) \DEF \{ \abstr{\zeta} \in \Sol \mid
+      \zeta \in \BS(P) \wedge
+      \nexists \zeta' \in \BS(P), \abstr{\zeta'} \subsetneq \abstr{\zeta} \} \enspace,
   \]
@@
   where $\forall P \in \Obj, \forall \zeta \in \BS(P)$:
-  \[
-    \abstr{\zeta} \DEF \{ \PHhitter(\zeta_n) \mid
-    n \in \indexes{\zeta} \wedge \PHsort(\PHhitter(\zeta_n)) \neq \PHsort(P) \}
-  \]
+  $\abstr{\zeta} \DEF \{ \PHhitter(\zeta_n) \mid n \in \indexes{\zeta} \} \setminus \emptyset$.
+  }%
+
+  \noindent
+  \modMF{
+  As a consequence,
+  $\aBS(\obj{a_i}{a_j}) = \emptyset$ if $\BS(\obj{a_i}{a_j}) = \emptyset$,
+  and $\BS(\obj{a_i}{a_i}) = \{ \emptyset \}$.
   }%
@@
 \noindent
-The notation $\delta_{a..b}$ denotes the subsequence of $\delta$
-between indexes $a$ and $b$, as defined on page \pageref{notations}.
+The notation $\delta_{a..b}$ in the previous definition
+denotes the subsequence of $\delta$ between indexes $a$ and $b$,
+as defined on page \pageref{notations}.
 
@@
 
-For any objective $P$ and context $\ctx$, \pref{def:maxCont} gives the set of processes of sort $\PHsort(P)$ that are required to solve $P$ in $\ctx$, denoted by $\gCont_\ctx(\PHsort(P), P)$.
+For any objective $P$ and context $\ctx$, \pref{def:maxCont} gives the set of local states of automaton $\PHsort(P)$ that are required to solve $P$ in $\ctx$, denoted by $\gCont_\ctx(\PHsort(P), P)$.
 \begin{definition}[$\gCont_\ctx : \Sigma \times \Obj \rightarrow \powerset(\PHproc)$]
@@
 A graph of local causality $\myB = (\cwV, \cwE)$
-is a graph where $\cwV \subseteq \Proc \cup \Obj \cup \Sol$ is the set of vertices
+is a graph where $\cwV \subseteq \Proc \cup \Obj \cup \sSol \cup \Sol$ is the set of vertices
 and $\cwE \subseteq \cwV \times \cwV$ is the set of oriented edges.
@@
 problem, that is, the reachability of $\w$ from the initial context $\ctx$.
-Thus, a node in $\PHproc$ represents a process required to play an action,
-a node in $\Obj$ is an objective to reach a given process
-and a node in $\Sol$ is a set of hitter processes required for the solving
-of an objective.
+Thus, a node in $\PHproc$ represents a local state required to play an action,
+a node in $\Obj$ is an objective to reach a given local state,
+a node in $\sSol$ is a set of hitters that have to be active simultaneously
+to solve one step of a given objective,
+and a node in $\Sol$ is a set of sets of hitters,
+thus encompassing all requirement for the solving of a whole objective.
 }
@@
 at least one related bounce sequence in $\BS(P)$ can be played;
-therefore, we can consider all minimal sets of hitters of these bounce sequences
-(that is, the sets of $\aBS(P) \in \Sol$, see \pref{def:aBS})
+therefore, we can consider all minimal sets of sets of hitters of these bounce sequences
+(that is, the sets of $\aBS(P) \subseteq \Sol$, see \pref{def:aBS})
 as requirements to solve this objective (\pref{eq:ESol1}).
-Such a set can then naturally be split into as many process nodes,
-making each of them a new requirement (\pref{eq:ESol2}).
-If $a \in \components$, the reachability of a required process $a_i$
+Such a set can then naturally be split into as many sets of hitters (\pref{eq:ESol3})
+which all have to be simultaneously active.
+These sets of hitters can in turn be split into several local state nodes (\pref{eq:ESol2}).
+This creates new requirements, as the reachability of a required local state $a_i$
 is approximated by the ability to solve all objectives of the form
-$\PHobjp{a}{j}{i} \in \Obj$ for all $a_j$ in the initial context (\pref{eq:EReq});
-if $a \in \cs$, the reachability of $a_i$ is simply solved by the set of processes $\csState(a_i)$ (see \pref{def:csState}) that it represents (\pref{eq:EPrio}).
+$\PHobjp{a}{j}{i} \in \Obj$ for all $a_j$ in the initial context (\pref{eq:EReq}).
 Furthermore, we note that the solving of an objective $P$ may require
-a process of $\PHsort(P)$,
-\ie $\gCont(\PHsort(P), P) \neq \emptyset$ (\pref{def:maxCont});
+a local state of $\PHsort(P)$,
+\ie $\gCont(\PHsort(P), P) \neq \emptyset$ (see \pref{def:maxCont});
 in this case, $P$ is re-targeted (\pref{eq:ECont}).
@@
 an objective sequence $\w$ from an initial context $\ctx$;
-indeed, the reachability of each intermediate required process
+indeed, the reachability of each intermediate required local state
 is only checked starting from the context $\ctx$,
@@
 which is obtained by iteratively saturating the initial context with all
-processes referenced in the graph,
+local states referenced in the graph,
 until reaching a fixed point.
@@
 is limited by the size of the initial PH model.
-The set of processes contained in a graph of local causality
+The set of local states contained in a graph of local causality
 is given by:
@@
 where, if the objective sequence $\w$ consists of only one element,
-then we can omit the hitter of this objective
-if it does not appear elsewhere in the graph.
+we can omit the hitter of this objective
+provided that it does not appear elsewhere in the graph.
 }
@@
 \label{def:glc}
-  The \modMF{saturated} graph of local causality $\cwB \DEF (\Bv, \Be)$ is defined as:
+  The \emph{\modMF{saturated} graph of local causality} $\cwB \DEF (\Bv, \Be)$ is defined as:
   $\cwB \DEF \lfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs(\myB)}}$,
   where $\myB \DEF (\cwV, \cwE)$ is the smallest graph with
-  $\cwV \subseteq \Proc \cup \Obj \cup \Sol$ and $\cwE \subseteq \cwV \times \cwV$
+  $\cwV \subseteq \Proc \cup \Obj \cup \sSol \cup \Sol$ and $\cwE \subseteq \cwV \times \cwV$
   so that:
@@
     (x, y) \in \cwE &\Rightarrow y \in \cwV \label{eq:VE} \\
-    P \in \cwVObj \wedge ps \in \modMF{\aBS}(P) &\Rightarrow (P, ps) \in \cwE \label{eq:ESol1} \\
-    ps \in \cwVSol \wedge a_i \in ps &\Rightarrow (ps, a_i) \in \cwE \label{eq:ESol2} \\
-    a \in \components \wedge a_i \in \cwVProc \wedge a_j \in \ctx &\Rightarrow (a_i, \PHobjp{a}{j}{i}) \in \cwE \label{eq:EReq} \\
-    a \in \cs \wedge a_i \in \cwVProc \wedge ps \in \csState(a_i) &\Rightarrow (a_i, ps) \in \cwE \label{eq:EPrio} \\
+    P \in \cwVObj \wedge pps \in \modMF{\aBS}(P) &\Rightarrow (P, pps) \in \cwE \label{eq:ESol1} \\
+    \moda{pps \in \cwVSol \wedge A \in pps} &\moda{\Rightarrow (pps, A) \in \cwE} \label{eq:ESol3} \\
+    A \in \cwVsSol \wedge a_i \in A &\Rightarrow (A, a_i) \in \cwE \label{eq:ESol2} \\
+    a_i \in \cwVProc \wedge a_j \in \ctx &\Rightarrow (a_i, \PHobjp{a}{j}{i}) \in \cwE \label{eq:EReq} \\
+%    a \in \cs \wedge a_i \in \cwVProc \wedge ps \in \csState(a_i) &\Rightarrow (a_i, ps) \in \cwE \label{eq:EPrio} \\
     P \in \cwVObj \wedge q \in \gCont_\ctx(\PHsort(P), P) &\Rightarrow (P, \PHobj{q}{\PHbounce(P)}) \in \cwE \label{eq:ECont} \!
@@
 
-In the saturated graph of local causality, an edge $(p, ps) \in \Proc \times \Sol$
-is said to be coherent (\pref{def:coherent}) if none of the processes in $ps$ conflict with the successor processes of $ps$,
 \modMF{
-that is, the successors of $ps$ that are in $\Bv \cap \Proc$.
+In the saturated graph of local causality, a set of hitters $A \in \sSol$
+is said to be \emph{coherent} (\pref{def:coherent})
+if none of the local states in $A$ conflict with
+a successor of $A$ in $\Bv \cap \Proc$,
+that is, if there exists no local state node $a_j$ in the successors of $A$
+and no element $a_i \in A$ so that $a_i \neq a_j$.
 }
-Then, \pref{th:approxinf} gives a sufficient condition for the concretisation of a sequence of objectives in a given context,
-which is derived immediately from the saturated graph of local causality.
+Then, \pref{th:approxinf} gives a sufficient condition for the concretisation
+of an objective sequence in a given context,
+which is derived immediately from the saturated graph of local causality,
+and the condition that all sets of hitters are coherent.
 A proof of this theorem is given in \pref{suppl:demoapproxinf}.
-\begin{definition}[Coherent edge]
+\begin{definition}[Coherent node]
 \label{def:coherent}
-  An edge $(x, y) \in \cwE$ is said to be coherent if and only if:
-  $(x, y) \in \Be \cap (\Proc \times \Sol) \Rightarrow y$ has no successor $a_j \in \Bv \cap \Proc$ so that $\exists a_i \in y$, $a_i \neq a_j$.
+  \modMF{
+  In a given saturated graph of local causality $\cwB = (\Bv, \Be)$,
+  a node $x \in \Bv$ is said to be \emph{coherent} if and only if:
+  $x \in \Bv \cap \sSol \Rightarrow x$ has no successor $a_j \in \Bv \cap \Proc$
+  so that $\exists a_i \in x$, $a_i \neq a_j$.
+  }
 \end{definition}
@@
 \label{th:approxinf}
-Given a Process Hitting $(\PHs; \PHl; \PHa^{\langle 2 \rangle})$
-that satisfies \pref{cr:bounded} and \pref{cr:compcs},
-a context $\ctx$ and a sequence of objectives $\w$,
+  Given an AAN $(\PHs; \PHl; \PHa)$,
+  a context $\ctx$ and an objective sequence $\w$,
   if the graph $\cwB$ contains no cycle,
   all objectives have at least one solution
-  and all edges are coherent,
+  and all nodes are coherent,
   then $\uconcr(\w) \neq \emptyset$.
@@
 Regarding the complexity of the method,
-computing the saturated graph of local causality is polynomial in the number of sorts in $\PH$ and exponential in the number of processes in one sort.
+computing the saturated graph of local causality is polynomial in the number of automata in $\PH$ and exponential in the number of local states in one automaton.
 Checking the properties allowing to apply \pref{th:approxinf} is polynomial in the size of the graph.
-Therefore, building and checking process can be considered polynomial in the size
-of the PH model, provided that each sort only is contains a few processes.
+Therefore, the building and checking process can be considered as polynomial in the size
+of the AAN, provided that each automaton only contains a few local states.
 We note that this is particularly true for biological models, where
 each component usually contains a limited number of expression levels.
-In addition, it is possible to “factorize” cooperative sorts
-modelling more than two components,
-as explained in \pref{ssec:cooperation},
-in order to reduce their number of processes.
 }
@@
 \modMF{
-We note furthermore that in case the method developed in this section is not conclusive,
+We note furthermore that in the case where
+the method developed in this section is not conclusive,
 it is possible to compute only a subset of $\Bv \cap \Sol$,
@@
 or by removing them from the saturated graph of local causality $\cwB$ and by trimming it.
-\pref{th:approxinf} is then still valid on the partial graph obtained,
-which can lead to more conclusiveness by removing parts of the graph
+In other words, this consists in ignoring some of the bounce sequences
+for some of the objectives,
+which intuitively cannot create false positives.
+Indeed, \pref{th:approxinf} is then still valid on the partial graph obtained,
+and this removal can lead to more conclusiveness by trimming parts of the graph
 that were not necessary for the reachability
-(such as cycles for instance).
-If one wants to test each possible subset of solutions,
-the overall method then turns out to be exponential
+(especially cycles or unnecessary but inconclusive branches).
+If one wants to try each possible subset of solutions,
+then the overall method turns out to be exponential
 in the number of solutions to each objective.
-Our method can thus be considered as efficient compared to regular model-checking which is usually PSPACE-complete~\cite{Harel02}.
+Our method can thus still be considered as efficient
+compared to regular model-checking which is usually PSPACE-complete~\cite{Harel02}.
 }
@@
 \begin{example}
-  Let $\PH' = (\PHs, \PHl, \PHh'^{\langle 1 \rangle})$ be the “merged” version of the PH
-  depicted in \pref{fig:ph-livelock}, as it was already defined in \pref{ssec:priorities},
-  that is: $\PHh'^{\langle 1 \rangle} = \PHh^{(1)} \cup \PHh^{(2)}$.
-  In other words,
-  $\PH'$ is how $\PH$ would have been represented in the semantics without priorities.
-  We showed in \pref{ssec:priorities} that,
-  due to spurious behaviours inherent to the cooperative sorts in this semantics,
-  process $c_1$ is reachable
-  from the initial context $\ctx = \PHstate{a_1, b_0, c_0, ab_{10}}$.
-%   This is confirmed by the original under-approximation
-%   developed in~\cite{PMR12-MSCS}, which gives the same conclusion.
+  \moda{%
+  If we confider the AAN of \pref{fig:ph-livelock},
+  from the initial state $\PHstate{a_1, b_0, c_0}$ depicted,
+  the under-approximation given in \pref{th:approxinf}
+  does not conclude regarding the reachability of $c_1$.
+  This is due to the fact that the node $\{ a_1, b_1 \} \in \Bv \cap \sSol$
+  is not coherent because of its successor $a_0$ (and $b_0$).
+  (However, from the inconclusiveness of \pref{th:approxinf},
+  one cannot conclude about the unreachability of $c_1$.
+  Such analysis should be driven for instance
+  with over-approximation methods developed in~\cite{PMR12-MSCS}.)
+  }%
 
-  Such unwanted behaviours are palliated by the semantics of PH with priorities proposed in this paper.
-  Indeed, the under-approximation given in \pref{th:approxinf} does not conclude regarding the reachability of $c_1$,
-  as one of the edges of the resulting saturated graph of local causality is not coherent (\pref{def:coherent}),
-  as shown in in \pref{fig:sa-livelock}.
-  (However, from the inconclusiveness of \pref{th:approxinf}, one cannot conclude about the unreachability of $c_1$.
-  Such analysis should be driven for instance with over-approximation methods developed in~\cite{PMR12-MSCS}.)
+  \moda{%
+  This result is new compared to the method proposed in~\cite{PMR12-MSCS}.
+  Indeed, the representation based on the Process Hitting that was proposed
+  in this paper only allowed to represent “over-approximated” Boolean gates
+  with the use of cooperative sorts,
+  as explained in \pref{ssec:cooperation}.
+  This especially did not allow to model the fact that $a_1$ and $b_1$ could not
+  be activated in the same state, but only in successive states.
+  Thus, $c_1$ was indeed reachable,
+  contrary to the behaviour expected from an accurate Boolean gate.
+  }%
 
-  We note however that,
-  if $\PHhit{a_0}{b_0}{b_1}$ and $\PHhit{b_0}{a_0}{a_1}$ are replaced by the auto-actions
-  $\PHhit{a_0}{a_0}{a_1}$ and $\PHhit{b_0}{b_0}{b_1}$,
+  \moda{%
+  Finally, we note however that,
+  if $\PHhits{a_0}{b_0}{b_1}$ and $\PHhits{b_0}{a_0}{a_1}$ are replaced by the actions
+  $\PHhitm{a_0}{a_1}$ and $\PHhitm{b_0}{b_1}$,
   then the resulting saturated graph of local causality changes, and
-  \pref{th:approxinf} concludes that $c_1$ is then reachable from $\ctx$.
+  \pref{th:approxinf} concludes that $c_1$ is reachable from $\ctx$.
+  }%
 
@@
 
-    \node[AprocPrio,below of=c01s] (ab11) {$ab_{11}$};
-    \node[AsolPrio,below of=ab11] (ab11s) {};
-
-    \node[Aproc,below left of=ab11s] (a1) {$a_1$};
+    \node[Assol,below of=c01s] (a1a1ss) {$\{ a_1, b_1 \}$};
+    \node[Aproc,below left of=a1a1ss] (a1) {$a_1$};
     \node[Aobj,below of=a1] (a11) {$\PHobj{a_1}{a_1}$};
     \node[Asol,below of=a11] (a11s) {};
+    \node[Assol,below of=a11s] (na11s) {$\emptyset$};
     \node[Aobj,below left of=a1] (a01) {$\PHobj{a_0}{a_1}$};
@@
     \node[Asol,below of=b00] (b00s) {};
+    \node[Assol,below of=b00s] (nb00s) {$\emptyset$};
     \node[Aobj,below left of=b0] (b10) {$\PHobj{b_1}{b_0}$};
     \node[Asol,below of=b10] (b10s) {};
+    \node[Assol,below of=b10s] (nb10s) {$\emptyset$};
 
-    \node[Aproc,below right of=ab11s] (b1) {$b_1$};
+    \node[Aproc,below right of=a1a1ss] (b1) {$b_1$};
     \node[Aobj,below of=b1] (b11) {$\PHobj{b_1}{b_1}$};
     \node[Asol,below of=b11] (b11s) {};
+    \node[Assol,below of=b11s] (nb11s) {$\emptyset$};
     \node[Aobj,below right of=b1] (b01) {$\PHobj{b_0}{b_1}$};
@@
     \node[Asol,below of=a00] (a00s) {};
+    \node[Assol,below of=a00s] (na00s) {$\emptyset$};
     \node[Aobj,below right of=a0] (a10) {$\PHobj{a_1}{a_0}$};
     \node[Asol,below of=a10] (a10s) {};
+    \node[Assol,below of=a10s] (na10s) {$\emptyset$};
 
@@
     (c01) edge (c01s)
-    (c01s) edge (ab11)
-    (ab11) edge[aSPrio] (ab11s)
-    (ab11s) edge (a1) edge (b1)
+    (c01s) edge (a1a1ss)
+    (a1a1ss) edge (a1) edge (b1)
 
@@
     (a11) edge (a11s)
+    (a11s) edge (na11s)
     (a0) edge (a10) edge (a00)
     (a10) edge (a10s)
+    (a10s) edge (na10s)
     (a00) edge (a00s)
+    (a00s) edge (na00s)
 
@@
     (b10) edge (b10s)
+    (b10s) edge (nb10s)
     (b00) edge (b00s)
+    (b00s) edge (nb00s)
     (b1) edge (b01) edge (b11)
@@
     (b11) edge (b11s)
+    (b11s) edge (nb11s)
     ;
@@
   \label{fig:sa-livelock}
-    The saturated graph of local causality of the PH model in \pref{fig:ph-livelock}
-    for the objective $\w = \PHobj{c_0}{c_1}$ and the initial context $\ctx = \PHstate{a_1, b_0, c_0, ab_{10}}$.
-    Rectangular nodes containing a single process are elements in $\Proc$,
-    borderless nodes containing a couple of processes are elements in $\Obj$
-    and circle nodes are elements in $\Sol$.
-    \pref{th:approxinf} is inconclusive on this example as edge $(ab_{11}, \{ a_1, b_1 \}) \in \Proc \times \Sol$ (here represented with a double line) is not coherent (\pref{def:coherent}).
-    Indeed, $a_0 \in \Proc$ is a successor of $\{ a_1, b_1 \}$, but $a_0 \neq a_1$ (and the same also stands for $b_0$).
+    The saturated graph of local causality of the AAN in \pref{fig:ph-livelock}
+    for the objective $\w = \PHobj{c_0}{c_1}$
+    and the initial context $\ctx = \PHstate{a_1, b_0, c_0}$.
+    Elements in $\Proc$ are represented by rectangular nodes,
+    elements in $\Sol$ are represented by circle nodes,
+    and elements in $\sSol$ and $\Obj$ are the remaining borderless nodes.
+    \pref{th:approxinf} is inconclusive on this example as node $\{ a_1, b_1 \}$
+    is not coherent (see \pref{def:coherent}).
+    Indeed, $a_0 \in \Proc$ is a successor of $\{ a_1, b_1 \}$, but $a_0 \neq a_1$
+    (and the same also stands for $b_0$).
   }
@@
 
-The reachability property studied so far concerns a single process at a time.
-However, we remark that the reachability of a partial or global state can be
-addressed with the very same analysis by introducing a dedicated cooperative
-sort in the scope of the PH semantics with $2$ classes of priorities.
+The reachability property studied so far concerns a single local state at a time.
+However, we remark that the reachability of a global state or a sub-state can be
+addressed with the very same analysis by introducing a dedicated automata.
+Such analysis was not possible with the Process Hitting framework,
+because of the lack of the notion of simultaneity for more than two components.
 
-Indeed, let $\PH = (\PHs, \PHl, (\PHh^{(1)}, \PHh^{(2)}))$ be a PH and suppose that we want to study the reachability of a state $s \in \PHl$.
-Let $\PH' = (\PHs', \PHl', (\PHh'^{(1)}, \PHh'^{(2)}))$
-with: $\PHs' = \PHs \cup \{ \total, \reach \}$ and $\PHl' = \PHl \times \PHl_\total \times \PHl_\reach$,
-where $\total$ is a cooperative sort on all components $\components$ of $\PH$ (thus $\PHl_\total = \underset{a \in \components}{\times} \PHl_a$)
-and $\reach$ is a component with $\PHl_\reach = \{ \reach_0, \reach_1 \}$;
-furthermore, $\PHh'^{(1)}$ is the set $\PHh^{(1)}$ completed with all actions updating the cooperative sort $\total$,
-and $\PHh'^{(2)} = \PHh^{(2)} \cup \{ \PHhit{\pfp_s(\total)}{\reach_0}{\reach_1} \}$.
+In order to check the reachability of a global state $s \in \PHl$,
+let $\PH = (\PHs, \PHl, \PHh)$ be an AAN.
+We define a new AAN $\PH' = (\PHs', \PHl', \PHh')$ with:
+$\PHs' = \PHs \cup \{ \reach \}$, $\PHl' = \PHl \times \PHl_\reach$,
+where $\PHl_\reach = \{ \reach_0, \reach_1 \}$,
+and $\PHh' = \PHh \cup \{ \PHhit{\toset{s}}{\reach_0}{\reach_1} \}$.
+Given an initial context $\ctx$, the reachability of $s$ in $\PH$
+is equivalent to the concretisation of $\PHobjp{\reach}{0}{1}$ in $\PH'$
+from the initial context $\ctx \cup \{ \reach_0 \}$,
+which can be efficiently under-approximated using \pref{th:approxinf}.
 
-Given an initial context $\ctx$, the reachability of $s$ in $\PH$ is equivalent to the concretisation of $\PHobjp{\reach}{0}{1}$ in $\PH'$ from the initial context $\ctx \cup \{ \reach_0 \}$ (the initial state of $\total$ does not matter), which can be efficiently under-approximated using \pref{th:approxinf}.
-Indeed, the additional action $\PHhit{\pfp_s(\total)}{\reach_0}{\reach_1}$ in $\PHh'^{(2)}$ allows to conclude on the reachability of process $\pfp_s(\total)$, that is, on the reachability of the state $s$ (considering only the components).
-
-It is also possible to compute the reachability of a set of states $\Lambda \subseteq \PHl$ by creating several actions $\PHhit{\total_s}{\reach_0}{\reach_1}$ in $\PHh^{(2)}$ for each state $s \in \Lambda$,
-or on a sub-state $s \in \PHsubl[\PHl]_S$ of a set of components $S \subseteq \PHs$ by adapting the sort $\total$ with: $\PHl_\total = \PHsubl[\PHl]_S$
+It is of course also possible to compute the reachability
+of a sub-state $s \in \PHsubl[\PHl]_S$ of a set of components $S \subseteq \PHs$
+with the same method.
+One can also check the reachability of a set of states $\Lambda \subseteq \PHl$
+by creating several actions
+$\PHhit{\toset{s}}{\reach_0}{\reach_1}$ in $\PHh$ for each state $s \in \Lambda$.
 
@@
 progressively takes into account the successive objectives, instead of
-considering all of them at a time, as it is done in the previous sections.
+considering all of them at a time, as it is done in \pref{ssec:ua}.
 Because objectives are taken into account individually, such an approach
@@
 any minimal scenario reaching $a_j$ ends in a state where $a_j$ is present but
-also the hitter of the last bounce of one bounce sequence in $\BS(\obj{a_i}{a_j})$.
-If such hitter $b_k$ is in a cooperative sort $b\in\cs$, it also means that one of the sub-states
-in $\csState(b_k)$ is included in the ending state.
+also the hitters of the last bounce of one bounce sequence in $\BS(\obj{a_i}{a_j})$.
 \pref{def:lastprocs} defines $\lastprocs(\obj{a_i}{a_j})$ as the set of set of
-processes that may be present just after reaching $a_j$.
+local states that may be present just after reaching $a_j$.
+
+\begin{definition}[$\lastprocs : \Obj\to\Sol$]
+\label{def:lastprocs}
+  Given an objective $\obj{a_i}{a_j} \in \Obj$, $\lastprocs(\obj{a_i}{a_j})$ is
+  defined as the largest set such that, $\forall ps\in\lastprocs(\obj{a_i}{a_j})$, 
+  $ps\in\sSol$,
+  \begin{enumerate}
+    \item $a_j \in ps$;
+    \item $\exists \zeta \in \BS(\obj{a_i}{a_j}),
+      \hitter{\zeta_{\card{\zeta}}} \subseteq ps$;
+    \item $\nexists ps' \in \lastprocs(\obj{a_i}{a_j}),
+      ps' \subset ps \wedge ps' \neq ps$.
+  \end{enumerate}
+\end{definition}
 
@@
 for any scenario $\delta$ in $\uconcr(P)$,
-there exists a set of processes $ps\in\lastprocs(P)$
+there exists a set of local states $ps\in\lastprocs(P)$
 such that $ps \subseteq (s\play\delta)$.
@@
 
-\begin{definition}[$\lastprocs$]
-\label{def:lastprocs}
-Given an objective $\obj{a_i}{a_j}$, $\lastprocs:
-\Obj\to\powerset(\powerset(\Proc))$ is
-defined as the largest set such that, $\forall lps\in\lastprocs(\obj{a_i}{a_j})$, 
-$lps\in\powerset(\Proc)$,
-\begin{enumerate}
-\item $a_j\in lps$;
-\item $\exists\zeta\in\BS(\obj{a_i}{a_j}),
-    \PHsort(\hitter{\zeta_{\card\zeta}}) \neq 
-		\PHsort(\bounce{\zeta_{\card\zeta}})
-		 \Rightarrow
-		  \hitter{\zeta_{\card\zeta}}\in lps$;
-\item $\forall b_j\in lps, b\in\cs, \exists ps\in\csState(b_j), ps\subseteq lps$;
-\item $\nexists lps'\in\lastprocs(\obj{a_i}{a_j}), lps'\subset lps \wedge
-									lps'\neq lps$.
-\end{enumerate}
-\end{definition}
-
 \begin{theorem}[Sequential under-approximation]
 \label{thm:ordered-ua}
-Given a Process Hitting $(\PHs; \PHl; \PHa^{\langle 2 \rangle})$
-that satisfies \pref{cr:bounded} and \pref{cr:compcs},
+Given an AAN $(\PHs; \PHl; \PHa)$,
 a context $\ctx$ and an objective sequence $\w =
@@
 $\uconcr(\w)\neq\emptyset$,
-which can be demonstrated by \pref{thm:ordered-ua} or \pref{th:approxinf}.
+which can be demonstrated by \pref{th:approxinf} or \pref{thm:ordered-ua}.
 The justification of these definitions can be found by analysing the demonstrations
@@
 \newcommand{\rec}{\mathbf{rec}}
-\newcommand{\thisobj}[1]{P_{#1}}
-\newcommand{\thisseq}[1]{\Theta_{#1}}
+% \newcommand{\thisobj}[1]{P_{#1}}
+% \newcommand{\thisseq}[1]{\Theta_{#1}}
+\newcommand{\thisobj}{P}
+\newcommand{\thisseq}{\Theta}
+\newcommand{\R}{R}
 
-\modMF{
-For all $\w \in \OS$:
+\modMF{%
+First, $\osres$ is used to split the objective sequence $\w$ to solve,
+by considering successive objectives, in the fashion of \pref{thm:ordered-ua}.
+This function calls $\res$ which allows to solve an objective $P$
+by either re-target it (if $\gCont(\PHsort(P), P) \neq \emptyset$)
+of by searching for a solution to this objective in $\BS(P)$.
+This search may require to try several objective sequences $\zeta \in \BS(P)$.
+For each trial, the chosen objective sequence $\zeta$ is solved with $\rec$,
+which recursively created a scenario to play the whole sequence.
+This scenario is itself recursively created by combining
+smaller scenarios allowing to reach each required hitter of each action
+with the function $\thisseq$.
+Finally, $\thisseq$ calls $\res$ anew to reach the hitters
+that are necessarily contained in other automata.
+}%
+
+\begin{definition}[$\osres : \PHl \times \OS \to \Sce$]
+\modMF{%
+For all $s \in \PHl$ and $\w \in \OS$, we define:
 \[
-  \osres_s(\w) = \res_s(\w_1) \concat
+  \osres_s(\w) \DEF
+    \begin{cases}
+      \emptyseq
+        & \text{ if $\w = \emptyseq$} \\
+      \res_s(\w_1) \concat
       \osres_{s \play \res_s(\w_1)}(\w_2 \concat \dots \concat \w_{\card{\w}})
+        & \text{ otherwise} \\
+    \end{cases}
 \]
-with $\osres_s(\varepsilon) = \varepsilon$.
-For all $P \in \Obj$:
-\[\res_s(P) =
+and, for all $s \in \PHl$ and $P \in \Obj$:
+\[\res_s(P) \DEF
   \begin{cases}
@@
       & \text{if } \target{P} = \bounce{P} \\
-%     pickone(\autoBS(P))
-%       & \text{if } \aBS(P) = \{ \emptyset \} \\
     \osres_s(P^Q \concat Q)
@@
     \rec_s(\zeta)
-      & \text{otherwise, with } \zeta \in \BS(P)
+      & \text{otherwise, with } \zeta \in \BS(P) \text{\todo{Selon possbilités}}
   \end{cases}
 \]
-where:
-\[
-  \autoBS(P) = \{ \zeta \in \BS(P) \mid \forall i \in \indexes{\zeta}, \PHsort(\hitter{\zeta_i}) = \PHsort(\target{\zeta_i}) = \PHsort(P) \}
-\]
-\[
-  P^Q = \PHobj{\PHtarget(P)}{\PHtarget(Q)}
-\]
-\[
-  \rec_s(\zeta) = \thisseq{\zeta_1} \play
-    \rec_{s \play \thisseq{\zeta_1}}
+with $P^Q = \PHobj{\PHtarget(P)}{\PHtarget(Q)}$.
+Furthermore:
+\begin{align*}
+  \forall \zeta \in \BS,
+  \rec_s(\zeta) &\DEF
+    \begin{cases}
+      \emptyseq
+        & \text{ if $\zeta = \emptyseq$} \\
+      \thisseq_s(\zeta_1) \concat \zeta_1 \concat
+      \rec_{s \play \thisseq_s(\zeta_1) \concat \zeta_1}
       (\zeta_2 \concat \dots \concat \zeta_{\card{\zeta}})
-\]
-with:
-\[
-  \thisseq{h} = \res_s(\thisobj{h}) \play
-    \delta^{upd}_{s \play \res_s(\thisobj{h})} \play h
-\]
-\[
-  \thisobj{h} = \PHobj{\PHget{s}{\PHsort(\hitter{h})}}{\hitter{h}}
-\]
-and $\delta^{upd}_{s'}$ is a scenario of actions in $\PHh^{(1)}$ that updates
-all cooperative sorts from state $s'$.
-Such a scenario always exists given \pref{lem:update},
-and it can be built, starting from $s'$
-by iteratively putting arbitrary prioritized actions into a sequence
-until no more prioritized action is playable.
-Indeed, the order of the actions do not matter and the final state will
-always be $\update(s')$.
+        & \text{ otherwise}
+    \end{cases} \\
+  \forall h \in \PHh,
+  \thisseq_s(h) &\DEF
+    \begin{cases}
+      \emptyseq
+        & \text{ if $\hitter{h} = \emptyset$} \\
+      \R_s(h_1) \concat \thisseq_{s \play \R_s(h_1)}(h_2 \concat \dots \concat h_{\card{h}})
+        & \text{ otherwise}
+    \end{cases} \\
+  \forall a_i \in \Proc,
+  \R_s(a_i) &\DEF \res_s(\PHobj{\PHget{s}{\PHsort(a_i)}}{a_i})
+\end{align*}
+and for all action $h \in \PHh$, $(h_i)_{i \in \segm{1}{\card{\hitter{h}}}}$
+is a sequence containing all hitters of $h$ in an arbitrary order.
 }
+\end{definition}
 
-\todo{À terminer et gluer}
+\todo{Gérer les choix multiples possibles de $\zeta \in \BS(P)$}

### 2014-12-22 parts/ccl.tex
continue transformation (encodings + examples + conclusion)

@@
 
-We introduced a new semantics to include priorities into the Process Hitting framework, which prove especially useful to model cooperations.
-Then, we developed a method to efficiently perform a reachability analysis of a sequence of objectives in a restricted class of Process Hitting models,
-but it is also useful to establish the reachability of a partial state.
-This analysis is based on an under-approximation of the true reachability solutions.
-%; however, the most usual cases can be handled.
+In this paper, we focused on the Asynchronous Automata Networks (AANs),
+which is a restriction of classical Automata Networks
+and is equivalent to the Process Hitting with classes of priorities~\cite{FPMR13-CS2Bio}.
+This formalism proves useful to model accurate Boolean gates, which was not possible
+with the standard form of the Process Hitting,
+and avoid an unwanted over-approximation of the dynamics.
+Furthermore, we proposed an extension of this formalism with classes of priorities,
+which prove convenient to abstract time parameters into these kinds of models,
+or more simply to add preemption relations between actions.
 
-We showed that the class of Process Hitting models that can be handled by the aforementioned method are equivalent to Asynchronous Discrete Networks, and therefore to Asynchronous Boolean Networks.
-This allows to efficiently compute reachability results on large biological models provided that they are equivalent to Asynchronous Discrete Networks and that a translation from the original framework into a Process Hitting model is possible.
-Such a translation for interaction graphs of Thomas modelling was proposed in~\cite{PMR10-TCSB}. % \towrite{[À garder ?] and is made possible by the Pint software}.
+Then, we developed a method to perform a reachability analysis
+of a sequence of objectives in an AAN,
+based on an under-approximation of the true reachability solutions.
+The checked objectives can take the form of local states, global states
+or partial states, making the analysis more convenient.
+This method can be considered efficient,
+because it is exponential in the number of possible solutions,
+and each step is only polynomial in the size of the model.
+Furthermore, AANs with classes of priorities can also be studied in this way,
+at the cost of a translation that we gave in this paper.
 
-We also demonstrated that general Process Hitting models with arbitrary priority
-classes can also be encoded in the particular class of two-prioritised Process Hitting.
-Therefore, our static analysis is applicable to a broad range of automata
-networks with priorities.
+Finally, we also showed that AANs are also equivalent to Asynchronous Discrete Networks,
+that is, the multivalued version of the classical Asynchronous Boolean Networks
+with discrete expression levels and evolution functions.
+This framework is also equivalent to Thomas' models with Snoussi parameters
+instead of evolution functions.
+This especially allows to efficiently compute reachability results
+on large biological models,
+provided that they are equivalent to Asynchronous Discrete Networks,
+which ensures that a translation to AANs is possible.
+For example,
+such a translation for generalized Interaction Graphs,
+that is, Discrete Networks without evolution functions or parameters,
+was proposed in~\cite{PMR10-TCSB}.
 

### 2014-12-22 parts/example.tex
begin transformation PH to AAN
continue transformation (encodings + examples + conclusion)

--- 2014-12-19 parts/example.tex
@@
 \section{Biological Examples}\label{sec:example}
+
+\todo{À transformer}
 
@@
 metazoan segmentation process,
-and demonstrate how the flattening of \pref{ssec:flattening}
-be used in such a case.
+and demonstrate how the classes of priorities help in the modelling process,
+and how the flattening of \pref{ssec:flattening}
+can be used in such a case.
 In \pref{ssec:ex-tcrsig}, we apply our method to a large-scale model
@@
 \modMF{
-We give in this section a detailed example of the application of the sequential
+We give in this section a detailed example of the use of classes of priorities
+in order to model a system with temporal constraints.
+This model also allows us to give a detailed example of the application of the sequential
 under-approximation proposed in \pref{ssec:ordered-ua},
@@
 For this, we first have to use the flattening method presented in \pref{ssec:flattening}
-because the considered model contains 3 classes of priorities (and not only 2, as required).
+because the considered model contains 2 classes of priorities.
 }
@@
 We consider in the following a model of metazoan segmentation
-inspired from a first translation to Process Hitting given in \cite{PMR10-TCSB}.
-This model was originally established in silico in \cite{MSB:MSB4100192} in a differential equations framework.
+inspired from a first translation to Process Hitting given in~\cite{PMR10-TCSB}.
+This model was originally established in silico in~\cite{MSB:MSB4100192}
+in a differential equations framework.
 It is composed of a wavefront gene $f$ that activates the gap-gene $a$ whose products are responsible for stripes formation.
@@
 The auto-inhibition of $c$ generalises a chain of repressors on $a$.
-The auto-inhibition of $f$, which terminates the stripes formation in the original model,
+The auto-inhibition of $f$, which normally terminates
+the stripes formation in the original model,
 has been removed in order to focus on the stationary dynamics of the model.
 
-The actions of the original model make $3$ classes of priorities, as represented in \pref{fig:metazoan-php}
-and listed in \pref{tab:metazoan-php-actions}.
-Thus, although the actions of the highest class of priority are only used to update a cooperative sort,
-the actions of the two other classes of priorities do have a biological meaning.
-%by representing different reaction rates.
-Indeed, they have been derived given the different reaction rates,
-given the fact that the switches of genes $a$ and $c$ have to alternate in order not to miss a stripe.
+The actions of the original model make $2$ classes of priorities, as represented in \pref{fig:metazoan-php}:
+\modMF{%
+\begin{align*}
+  \ov{\PHh}^{(1)} = \{ \quad
+    & \PHfrappes{c_1}{a_1}{a_0} \quad , \quad
+    \PHfrappes{f_1, c_0}{a_0}{a_1}
+  \quad \} \\
+  \ov{\PHh}^{(2)} = \{ \quad
+    & \PHfrappem{c_1}{c_0} \quad , \quad
+    \PHfrappes{f_1}{c_0}{c_1}
+  \quad \} \\
+\end{align*}
+Indeed, without this use of priorities,
+some unwanted behaviours emerge, allowing the formation of irregular stripes.
+In order to fix this, a high priority is affected to the actions hitting $a$,
+a low priority to the actions hitting $c$,
+in order to model the fact that the switching of $c$ has to be immediately followed by
+a switching of $a$.
+This forces the the switches of genes $a$ and $c$
+to alternate in order not to miss a stripe;
+$a$ and $c$ thus have intertwined oscillations.
+We can thus consider that these two classes of priorities
+are derived from known reaction relative rates,
+the evolution of the clock $c$ being slower and regular,
+while the evolution of $a$ has to follow the changes of $c$.
+}%
 
@@
   \scalebox{1}{
-  \begin{tikzpicture}
+  \begin{tikzpicture}[aan]
     \TSort{(0,4)}{c}{2}{l}
-    \TSort{(1,1)}{f}{2}{l}
-    \TSort{(6,4)}{a}{2}{r}
+    \TSort{(1,0)}{f}{2}{l}
+    \TSort{(5,4)}{a}{2}{r}
 
-    \TSetTick{fc}{0}{00}
-    \TSetTick{fc}{1}{01}
-    \TSetTick{fc}{2}{10}
-    \TSetTick{fc}{3}{11}
-    \TSort{(4,1)}{fc}{4}{r}
+    \TAction{f_1}{c_0.west}{c_1.south west}{bend left=30, in=90}{left}
+    \TActionPlur{}{c_1.west}{c_0.north west}{}{-1,5.5}{right}
 
-    \THit{fc_2}{prio}{a_0}{.west}{a_1}
-    \path[bounce, bend left]
-      \TBounce{a_0}{prio}{a_1}{.south west};
+    \TAction{c_1}{a_1.west}{a_0.north west}{prio}{right}
+    \TActionPlur{f_1, c_0}{a_0.west}{a_1.south west}{prio}{2.5,2.5}{left}
 
-    \THit{c_1}{prio}{a_1}{.west}{a_0}
-    \path[bounce, bend right]
-      \TBounce{a_1}{prio}{a_0}{.north west};
-
-    \THit{f_1}{bend left=30, in=90}{c_0}{.west}{c_1}
-    \path[bounce, bend left]
-      \TBounce{c_0}{}{c_1}{.south west};
-
-    \THit{c_1}{selfhit}{c_1}{.west}{c_0}
-    \path[bounce, bend right]
-      \TBounce{c_1}{}{c_0}{.north west};
-
-    \path (1.8, 1.5) edge[superprio,coopupdate] (3.2, 2);
-    \path (0.8, 4.5) edge[superprio,coopupdate] (3.2, 3);
+    \TState{f_1, a_0, c_0}
   \end{tikzpicture}
@@
   \label{fig:metazoan-php}
-    An example of PH $\oPH$ with $3$ classes of priorities,
+    An example of AAN$2$
     modelling the process of metazoan segmentation.
@@
     while $f$ represents the wavefront propagation.
-    If component $a$ oscillates (that is, its active process changes regularly)
+    If component $a$ oscillates (that is, its active local state changes regularly)
     then regular stripes are created on the metazoan.
-    Actions of $\ov{\PHh}^{(3)}$ (lowest priority) are represented in thin lines,
-    actions of $\ov{\PHh}^{(2)}$ (intermediate priority) are in thick lines,
-    and actions of $\ov{\PHh}^{(1)}$ (highest priority), whose only purpose is to update the cooperative sort $fc$,
-    are not explicitly represented but modelled by the double dashed arrows.
+    Actions of $\ov{\PHh}^{(2)}$ (low priority) are represented in thin lines
+    and actions of $\ov{\PHh}^{(1)}$ (high priority) are in thick lines.
+    The greyed local states represent a possible initial state:
+    $\PHstate{f_1, a_0, c_0}$.
   }
@@
 
-\begin{table}[p]
-\modMF{
-\begin{align*}
-  \PHh^{(1)} = \{ \quad
-    & \PHfrappe{f_1}{fc_{00}}{fc_{10}} \quad , \quad
-    \PHfrappe{f_1}{fc_{01}}{fc_{11}} \quad , \\
-    & \PHfrappe{f_0}{fc_{10}}{fc_{00}} \quad , \quad
-    \PHfrappe{f_0}{fc_{11}}{fc_{01}} \quad , \\
-    & \PHfrappe{c_1}{fc_{00}}{fc_{01}} \quad , \quad
-    \PHfrappe{c_1}{fc_{10}}{fc_{11}} \quad , \\
-    & \PHfrappe{c_0}{fc_{01}}{fc_{00}} \quad , \quad
-    \PHfrappe{c_0}{fc_{11}}{fc_{10}}
-  \quad \} \\
-  \PHh^{(2)} = \{ \quad
-    & \PHfrappe{c_1}{a_1}{a_0} \quad , \quad
-    \PHfrappe{fc_{10}}{a_0}{a_1}
-  \quad \} \\
-  \PHh^{(3)} = \{ \quad
-    & \PHfrappe{c_1}{c_1}{c_0} \quad , \quad
-    \PHfrappe{f_1}{c_0}{c_1}
-  \quad \} \\
-\end{align*}%
-}%
-  \caption{\label{tab:metazoan-php-actions}%
-    The sets of actions of the metazoan segmentation model depicted
-    in \pref{fig:metazoan-php}.
-  }
-\end{table}
-
 \pref{fig:metazoan-ph} gives the flattening of this model,
 \modMF{
-whose actions are detailed in \pref{tab:metazoan-ph-actions}.
+that is, an AAN with the equivalent dynamics
+(but only one class of priority).
+Its actions are:
+\begin{align*}
+  \PHh = \{ \quad
+    & \PHfrappes{c_1}{a_1}{a_0} \quad , \quad
+    \PHfrappes{f_1, c_0}{a_0}{a_1} \quad , \\
+    & \PHfrappes{a_0}{c_1}{c_0} \quad , \quad
+    \PHfrappes{f_1, a_1}{c_0}{c_1}
+  \quad \}
+\end{align*}
+We note that the two actions in $\ov{\PHh}^{(2)}$ have been replaced by
+the equivalent actions
+$\PHfrappes{a_0}{c_1}{c_0}$ and $\PHfrappes{f_1, a_1}{c_0}{c_1}$,
+in order to model the preemption of the actions in $\ov{\PHh}^{(1)}$.
 }%
-It contains $2$ classes of priority, and prioritised actions are only used to update cooperative sorts.
-Note that according to the simplifications mentioned at the end of \pref{ssec:flattening},
-the auto-action $h_1 = \PHhit{c_1}{c_1}{c_0}$ in the original model has been flattened to a regular action $\PHhit{a_0}{c_1}{c_0}$
-because its playability property could be simplified to $\Fop{h_1} \equiv c_1 \wedge a_0 \equiv a_0$.
 
@@
   \scalebox{1}{
-  \begin{tikzpicture}
-    \TSort{(-5,4)}{c}{2}{l}
+  \begin{tikzpicture}[aan]
+    \TSort{(-3,4)}{c}{2}{l}
     \TSort{(0,1)}{f}{2}{l}
-    \TSort{(5,4)}{a}{2}{r}
+    \TSort{(3,4)}{a}{2}{r}
 
-    \TSetTick{fc}{0}{00}
-    \TSetTick{fc}{1}{01}
-    \TSetTick{fc}{2}{10}
-    \TSetTick{fc}{3}{11}
-    \TSort{(3,0)}{fc}{4}{r}
+%    \TAction{f_1}{c_0.west}{c_1.south west}{bend left=30, in=90}{left}
+    \TActionPlur{f_1, a_1}{c_0.south east}{c_1.south east}{}{-1.5,3.3}{right}
+    \TAction{a_0.west}{c_1.east}{c_0.north east}{}{left}
 
-    \TSetTick{fa}{0}{00}
-    \TSetTick{fa}{1}{01}
-    \TSetTick{fa}{2}{10}
-    \TSetTick{fa}{3}{11}
-    \TSort{(-3,0)}{fa}{4}{l}
+    \TAction{c_1.north east}{a_1.north west}{a_0.north west}{}{right}
+    \TActionPlur{f_1, c_0}{a_0.south west}{a_1.south west}{}{1.5,3.5}{left}
 
-    \THit{fc_2}{}{a_0}{.west}{a_1}
-    \path[bounce, bend left]
-      \TBounce{a_0}{}{a_1}{.south west};
-
-    \THit{fa_3}{}{c_0}{.east}{c_1}
-    \path[bounce, bend right]
-      \TBounce{c_0}{}{c_1}{.south east};
-
-    \THit{c_1.north east}{}{a_1}{.west}{a_0}
-    \path[bounce, bend right]
-      \TBounce{a_1}{}{a_0}{.north west};
-
-    \THit{a_0.south west}{}{c_1}{.east}{c_0}
-    \path[bounce, bend left]
-      \TBounce{c_1}{}{c_0}{.north east};
-
-    \path (0.8, 1.5) edge[prio,coopupdate] (2.2, 1.5);
-    \path (-4.3, 4.5) edge[prio,coopupdate] (2.2, 2.5);
-
-    \path (-0.8, 1.5) edge[prio,coopupdate] (-2.2, 1.5);
-    \path (4.3, 4.5) edge[prio,coopupdate] (-2.2, 2.5);
+    \TState{f_1, a_0, c_0}
   \end{tikzpicture}
@@
   \label{fig:metazoan-ph}
-    An example of PH $\PH$ with $2$ classes of priorities,
-    which is the flattening of the PH in \pref{fig:metazoan-php}.
-    In other words, this model has exactly the same dynamics as
-    \pref{fig:metazoan-php}, but its actions make only two classes of priorities.
-    Actions of $\PHh^{(2)}$ (unprioritised) are represented in thin lines,
-    and actions of $\PHh^{(1)}$ (prioritised) which are used to update cooperative sorts,
-    are abstracted by thick dashed arrows.
-    The additional cooperative sort $fa$ is used to model the previous action
-    $\PHhit{f_1}{c_0}{c_1}$,
-    which belonged to the lowest class of priority and could be preempted 
-    especially by action $\PHhit{fc_{10}}{a_0}{a_1}$.
+    An example of AAN, which is the flattening of the AAN$2$ in \pref{fig:metazoan-php};
+    in other words, this model has exactly the same dynamics as
+    \pref{fig:metazoan-php}, but its actions make only one class of priority.
+    The greyed local states represent the same initial state:
+    $\PHstate{f_1, a_0, c_0}$.
   }
 \end{figure}
-
-\begin{table}[p]
-\modMF{
-\begin{align*}
-  \PHh^{(1)} = \{ \quad
-    & \PHfrappe{f_1}{fc_{00}}{fc_{10}} \quad , \quad
-    \PHfrappe{f_1}{fc_{01}}{fc_{11}} \quad , \\
-    & \PHfrappe{f_0}{fc_{10}}{fc_{00}} \quad , \quad
-    \PHfrappe{f_0}{fc_{11}}{fc_{01}} \quad , \\
-    & \PHfrappe{c_1}{fc_{00}}{fc_{01}} \quad , \quad
-    \PHfrappe{c_1}{fc_{10}}{fc_{11}} \quad , \\
-    & \PHfrappe{c_0}{fc_{01}}{fc_{00}} \quad , \quad
-    \PHfrappe{c_0}{fc_{11}}{fc_{10}} \quad , \\
-    & \PHfrappe{f_1}{fa_{00}}{fa_{10}} \quad , \quad
-    \PHfrappe{f_1}{fa_{01}}{fa_{11}} \quad , \\
-    & \PHfrappe{f_0}{fa_{10}}{fa_{00}} \quad , \quad
-    \PHfrappe{f_0}{fa_{11}}{fa_{01}} \quad , \\
-    & \PHfrappe{a_1}{fa_{00}}{fa_{01}} \quad , \quad
-    \PHfrappe{a_1}{fa_{10}}{fa_{11}} \quad , \\
-    & \PHfrappe{a_0}{fa_{01}}{fa_{00}} \quad , \quad
-    \PHfrappe{a_0}{fa_{11}}{fa_{10}}
-  \quad \} \\
-  \PHh^{(2)} = \{ \quad
-    & \PHfrappe{c_1}{a_1}{a_0} \quad , \quad
-    \PHfrappe{fc_{10}}{a_0}{a_1} \quad , \\
-    & \PHfrappe{a_0}{c_1}{c_0} \quad , \quad
-    \PHfrappe{fa_{11}}{c_0}{c_1}
-  \quad \}
-\end{align*}%
-}%
-  \caption{\label{tab:metazoan-ph-actions}%
-    The sets of actions of the flattened metazoan segmentation model depicted
-    in \pref{fig:metazoan-ph}.
-  }
-\end{table}
 
@@
 \ie if gene $a$ can oscillate, thus leading to the formation of stripes.
-Starting from context $\ctx = \PHstate{f_1, a_0, c_0, fc_{10}, fa_{00}}$,
+Starting from context $\ctx = \PHstate{f_1, a_0, c_0}$,
 we thus want to check the reachability of
@@
 We have especially:
-\[\allprocs(\thisB{\w_1}{\ctx}) = \{ a_0, c_0, f_1, fc_{10} \}\]
-\[\lastprocs(\PHobj{a_0}{a_1}) = \{\{ a_1, c_0, f_1, fc_{10} \}\}\]
+\[\allprocs(\thisB{\w_1}{\ctx}) = \{ a_0, c_0, f_1 \} \enspace \text{and}\]
+\[\lastprocs(\PHobj{a_0}{a_1}) = \{\{ a_1, c_0, f_1 \}\} \enspace.\]
 Therefore, the second step consists of computing the saturated graph of local causality
@@
 in the context
-\[\ctx' = \ctx \Cap \allprocs(\thisB{\w_1}{\ctx}) \Cap \lastprocs(\PHobj{a_0}{a_1}) = \PHstate{a_1, c_0, f_1, fc_{10}, fa_{00}}\]
+\[\ctx' = \ctx \Cap \allprocs(\thisB{\w_1}{\ctx}) \Cap \lastprocs(\PHobj{a_0}{a_1}) = \PHstate{a_1, c_0, f_1} \enspace.\]
 This second graph is given in \pref{fig:metazoan-sa}(middle).
 Finally, because
-\[\allprocs(\thisB{\w_2}{\ctx'}) = \{ a_1, c_1, f_1, fa_{11} \}\]
-\[\lastprocs(\PHobj{a_1}{a_0}) = \{\{ a_0, c_1 \}\}\]
+\[\allprocs(\thisB{\w_2}{\ctx'}) = \{ a_1, c_0, c_1, f_1 \} \enspace \text{and}\]
+\[\lastprocs(\PHobj{a_1}{a_0}) = \{\{ a_0, c_1 \}\} \enspace,\]
 The last step is then checking
@@
 in the context
-\[\ctx'' = \ctx' \Cap \allprocs(\thisB{\w_2}{\ctx'}) \Cap \lastprocs(\PHobj{a_1}{a_0}) = \PHstate{a_0, c_1, f_1, fc_{10}, fa_{11}}\]
-This last graph is depicted in 
-As all the produced \pref{fig:metazoan-sa}(right).
+\[\ctx'' = \ctx' \Cap \allprocs(\thisB{\w_2}{\ctx'}) \Cap \lastprocs(\PHobj{a_1}{a_0}) = \PHstate{a_0, c_1, f_1} \enspace.\]
+This last graph is depicted in \pref{fig:metazoan-sa}(right).
 In conclusion, by using \pref{thm:ordered-ua} on these saturated graphs of local causality,
 we can conclude that the initial objective $\w$ is reachable,
-and thus that the PH model of \pref{fig:metazoan-ph} is functional.
+and thus that the AAN of \pref{fig:metazoan-ph} is functional.
 This result can be extended to the model of \pref{fig:metazoan-php}
@@
     \node[Asol,below of=a01] (a01s) {};
+    \node[Assol,below of=a01s] (a01ss) {$\{ c_0, f_1 \}$};
 
-    \node[AprocPrio,below of=a01s] (fc10) {$fc_{10}$};
-    \node[AsolPrio,below of=fc10] (fc10s) {};
-
-    \node[Aproc,below left of=fc10s] (f1) {$f_1$};
+    \node[Aproc,below right of=a01ss] (f1) {$f_1$};
     \node[Aobj,below of=f1] (f11) {$\PHobj{f_1}{f_1}$};
     \node[Asol,below of=f11] (f11s) {};
+    \node[Assol,below of=f11s] (nf11s) {$\emptyset$};
 
-    \node[Aproc,below right of=fc10s] (c0) {$c_0$};
+    \node[Aproc,below left of=a01ss] (c0) {$c_0$};
     \node[Aobj,below of=c0] (c00) {$\PHobj{c_0}{c_0}$};
     \node[Asol,below of=c00] (c00s) {};
+    \node[Assol,below of=c00s] (nc00s) {$\emptyset$};
 
@@
     (a01) edge (a01s)
-    (a01s) edge (fc10)
-    (fc10) edge[aSPrio] (fc10s)
-    (fc10s) edge (f1) edge (c0)
+    (a01s) edge (a01ss)
+    (a01ss) edge (f1) edge (c0)
 
@@
     (f11) edge (f11s)
+    (f11s) edge (nf11s)
 
@@
     (c00) edge (c00s)
+    (c00s) edge (nc00s)
     ;
@@
     \node[Asol,below of=a10] (a10s) {};
+    \node[Assol,below of=a10s] (a10ss) {$\{ c_1 \}$};
 
-    \node[Aproc,below of=a10s] (c1) {$c_1$};
+    \node[Aproc,below of=a10ss] (c1) {$c_1$};
     \node[Aobj,below right of=c1] (c01) {$\PHobj{c_0}{c_1}$};
     \node[Asol,below of=c01] (c01s) {};
+    \node[Assol,below of=c01s] (c01ss) {$\{ a_1, f_1 \}$};
     \node[Aobj,below left of=c1] (c11) {$\PHobj{c_1}{c_1}$};
     \node[Asol,below of=c11] (c11s) {};
+    \node[Assol,below of=c11s] (nc11s) {$\emptyset$};
 
-    \node[AprocPrio,below of=c01s] (fa11) {$fa_{11}$};
-    \node[AsolPrio,below of=fa11] (fa11s) {};
-
-    \node[Aproc,below left of=fa11s] (a1) {$a_1$};
+    \node[Aproc,below left of=c01ss] (a1) {$a_1$};
     \node[Aobj,below of=a1] (a11) {$\PHobj{a_1}{a_1}$};
     \node[Asol,below of=a11] (a11s) {};
+    \node[Assol,below of=a11s] (na11s) {$\emptyset$};
 
-    \node[Aproc,below right of=fa11s] (f1) {$f_1$};
+    \node[Aproc,below right of=c01ss] (f1) {$f_1$};
     \node[Aobj,below of=f1] (f11) {$\PHobj{f_1}{f_1}$};
     \node[Asol,below of=f11] (f11s) {};
+    \node[Assol,below of=f11s] (nf11s) {$\emptyset$};
 
@@
     (a10) edge (a10s)
-    (a10s) edge (c1)
+    (a10s) edge (a10ss)
+    (a10ss) edge (c1)
 
@@
     (c01) edge (c01s)
+    (c01s) edge (c01ss)
+    (c01ss) edge (f1) edge (a1)
     (c11) edge (c11s)
-    (c01s) edge (fa11)
-
-    (fa11) edge[aSPrio] (fa11s)
-    (fa11s) edge (f1) edge (a1)
 
@@
     (a11) edge (a11s)
+    (a11s) edge (na11s)
     ;
@@
     \node[Asol,below of=ta01] (ta01s) {};
+    \node[Assol,below of=ta01s] (ta01ss) {$\{ c_0, f_1 \}$};
 
-    \node[AprocPrio,below of=ta01s] (tfc10) {$fc_{10}$};
-    \node[AsolPrio,below of=tfc10] (tfc10s) {};
-
-    \node[Aproc,below left of=tfc10s] (tf1) {$f_1$};
+    \node[Aproc,below left of=ta01ss] (tf1) {$f_1$};
     \node[Aobj,below of=tf1] (tf11) {$\PHobj{f_1}{f_1}$};
     \node[Asol,below of=tf11] (tf11s) {};
+    \node[Assol,below of=tf11s] (tnf11s) {$\emptyset$};
 
-    \node[Aproc,below right of=tfc10s] (tc0) {$c_0$};
+    \node[Aproc,below right of=ta01ss] (tc0) {$c_0$};
     \node[Aobj,below of=tc0] (tc10) {$\PHobj{c_1}{c_0}$};
@@
     \node[Asol,below of=tc00] (tc00s) {};
+    \node[Assol,below of=tc00s] (tnc00s) {$\emptyset$};
 
@@
     \node[Asol,below of=ta00] (ta00s) {};
+    \node[Assol,below of=ta00s] (tna00s) {$\emptyset$};
 
@@
     (ta01) edge (ta01s)
-    (ta01s) edge (tfc10)
-    (tfc10) edge[aSPrio] (tfc10s)
-    (tfc10s) edge (tf1) edge (tc0)
+    (ta01s) edge (ta01ss)
+    (ta01ss) edge (tf1) edge (tc0)
 
@@
     (tf11) edge (tf11s)
+    (tf11s) edge (tnf11s)
 
@@
     (tc00) edge (tc00s)
+    (tc00s) edge (tnc00s)
     (tc0) edge (tc10)
@@
     (ta00) edge (ta00s)
+    (ta00s) edge (tna00s)
     ;
@@
     The three successive saturated graphs of local causality
-    of the PH model in \pref{fig:metazoan-ph}
+    of the AAN in \pref{fig:metazoan-ph}
     for the objective sequence
@@
     and the initial context
-    $\ctx = \PHstate{a_0, c_0, f_1, fc_{10}, fa_{10}}$.
+    $\ctx = \PHstate{a_0, c_0, f_1}$.
     The (left) graph allows to check objective $\PHobj{a_0}{a_1}$
@@
     The (middle) graph is for the objective $\PHobj{a_1}{a_0}$
-    and the context $\PHstate{a_1, c_0, f_1, fc_{10}, fa_{10}}$.
+    and the context $\PHstate{a_1, c_0, f_1}$.
     The (right) graph is for the last objective, $\PHobj{a_0}{a_1}$,
-    and the context $\PHstate{a_0, c_1, f_1, fc_{10}, fa_{11}}$.
-%     Rectangular nodes containing a single process are elements in $\Proc$,
-%     borderless nodes containing a couple of processes are elements in $\Obj$
+    and the context $\PHstate{a_0, c_1, f_1}$.
+%     Rectangular nodes containing a single local state are elements in $\Proc$,
+%     borderless nodes containing a couple of local states are elements in $\Obj$
 %     and circle nodes are elements in $\Sol$.
@@
 
-The Boolean model has been automatically encoded into a Process Hitting with 2 classes of priority%
+The Boolean model has been automatically encoded into
+a Process Hitting model with two classes of priorities,
+and a dynamics equivalent to an AAN%
 \footnote{Files are available at
@@
 by using a translation equivalent to the one given in \pref{sec:dn}.
-\todo{?}
 }
 Then, we verified the reachability for the independent activation of 4 outputs of the signalling
-cascade (SRE, AP1, NFkB, NFAT) from all possible input combinations (CD4, CD28, TCRlig) using our
+cascade (SRE, AP1, NFkB, NFAT) for all possible input combinations (CD4, CD28, TCRlig) using our
 new reachability under-approximation (answering either \emph{yes} or \emph{inconclusive}) and a 
@@
 By analysing the detail of the results, one can find out that one of the outputs, NFkB, can never be activated.
-In other words, FkB$_1$ is never reachable, whatever the state of the inputs,
-while some combinations the other outputs (SRE, AP1, NFAT) can be activated for some configurations of inputs.
+In other words, FkB$_1$ is never reachable, whatever the initial state of the inputs,
+the other outputs (SRE, AP1, NFAT) can be independently activated
+for some configurations of inputs.
 We thus want to check if these three outputs can be activated together,
@@
 For this, as proposed in \pref{ssec:simult-ua},
-we add a new cooperative sort $\total$ between SRE, AP1 and NFAT to the model,
-and a sort $\reach$ with two processes ($\PHl_\reach = \{ \reach_0, \reach_1 \}$)
-with the action $\PHhit{\total_{111}}{\reach_0}{\reach_1}$.
+we add a new automaton $\reach$ into the model
+with two local states ($\PHl_\reach = \{ \reach_0, \reach_1 \}$)
+and the action:
+\[ \PHhits{\text{SRE}_1, \text{AP1}_1, \text{NFAT}_1}{\reach_0}{\reach_1} \enspace. \]
 Finally, checking the reachability of $\reach_1$ in all configurations of the inputs
 is always conclusive,
-and the existence of positive answers allows to conclude that
+and the existence of 4 positive answers
+(amongst all 8 possible initial configurations of the inputs) allows to conclude that
 it is possible to reach a state where SRE, AP1 and NFAT are simultaneously active.
@@
 However, if these experiments allowed to obtain some information
-on these model to some extent,
+on this model to some extent,
 it did not provide a formal proof of the reachabilities that have been
 checked in the example above.
-Indeed, without any priorities in the update of the cooperative sorts,
-some unwanted behaviours were possible,
-such as those described in \pref{ssec:priorities}.
-Only the method presented in this paper provides a formal proof that
-the observed behaviours are the result of the exact dynamics of the system,
+The semantics of Process Hitting does not allow to model accurate Boolean gates,
+as explained in \pref{ssec:cooperation},
+thus leading to some unwanted behaviours that take the form of temporal shifts.
+Only the adding of classes of priorities allows to remove these temporal shifts,
+as explained in~\cite{FPMR13-CS2Bio},
+with a construction that is equivalent to the AANs presented in \pref{se:ph}.
+Therefore, only the method presented in this paper provides a formal proof that
+the observed behaviours are the result of the true dynamics of the system,
 which was originally described in a format equivalent to synchronous Discrete Networks.
@@
 
-While ensuring a low complexity for the analysis of reachability in Boolean and discrete networks, our
-under-approximation method reveals to be conclusive in numerous cases when applied to real
+In conclusion,
+while ensuring a low complexity for the analysis of reachability in Boolean and discrete networks,
+our under-approximation method turns out to be conclusive in numerous cases when applied to real
 large-scale biological models, which were not tractable with exact model-checking.

### 2014-12-22 parts/models-ph-dn.tex
continue transformation (encodings + examples + conclusion)

--- 2014-04-03 parts/models-ph-dn.tex
@@
 
-We exhibit an encoding of Asynchronous Discrete Networks (ADN) with the Process
-Hitting using two classes of priorities
-that respects all Conditions of \pref{ssec:hypothesis},
-and prove a weak bisimulation relation.
+We exhibit in this section an encoding of Asynchronous Discrete Networks (ADN),
+also called Logical Networks or equivalently René Thomas Models \cite{Thomas95,deJong02},
+into AANs and prove a weak bisimulation relation.
+This translation is important as it allows to efficiently study the dynamics of ADNs
+by using the static analysis developed in \pref{sec:sa};
+indeed, the bisimulation relation ensures that the dynamics of the
+resulting AAN model are accurately the same than the original.
 
-A Discrete Network gathers a finite number of components $i\in\segm{1}{n}$ having a discrete finite domain
+A \emph{Discrete Network} gathers a finite number of components $i\in\segm{1}{n}$ having a discrete finite domain
 $\mathbb F^i$ that we note $\mathbb{F}^i = \segm{1}{l_i}$.
@@
 Typically $f^i$ depends on a subset of components that we denote $\DNdep(f^i)$.
-In the case of Asynchronous Discrete Networks (ADN), a transition relation $\DNtrans\subseteq \mathbb
+In the case of \emph{Asynchronous Discrete Networks} (ADN), a transition relation $\DNtrans\subseteq \mathbb
 F\times \mathbb F$ is defined such that $x\DNtrans x'$ if and only if there exists a unique
@@
 
-\begin{definition}[Asynchronous Discrete Network (ADN)]
+\begin{definition}[Asynchronous Discrete Network]
 \label{def:DN}
-  An ADN is defined by a couple $(\mathbb F, \langle f^1, \dots, f^n \rangle)$
+  An \emph{Asynchronous Discrete Networks} (ADN) is defined by a couple $(\mathbb F, \langle f^1, \dots, f^n \rangle)$
   where $\mathbb{F} = \mathbb{F}^1\times\dots\times\mathbb{F}^n$,
@@
   $f^i: \mathbb{F} \rightarrow \mathbb{F}^i$ with
-  $\mathbb{F}^i = \segm{1}{l_i}$.
+  $\mathbb{F}^i = \segm{1}{l_i}$ and $l_i \in \sNN$.
   Given two states $x,x'\in\mathbb F$, the transition relation $\DNtrans$ is given by
@@
   \]
-  where $\get{x}{i}$ is the $i$-th component of $x$.
+  where $\get{x}{i}$ is the $i$\textsuperscript{th} component of $x$.
   %
@@
 
-Let us denote the encoding of the ADN $\DNdef$ in Process Hitting with $2$ classes
-of priorities by $\toPH\DNdef$ (\pref{def:DN2PH}).
-For each component $i\in\segm{1}{n}$ of the ADN, two sorts are built: $a^i$ acting for the component
-value, and $f^i$ acting for a cooperative sort between the components $\DNdep(f^i)$.
-Sorts $a^i$ have one process $a^i_k$ per element in $k\in\mathbb F^i$.
-Sorts $f^i$ have one process $f^i_\varsigma$ per state $\varsigma \in \underset{j\in\DNdep(f^i)}{\times}
-\PHl_{a^j}$.
-Two classes of actions are then defined:
-$\Hits^{(1)}$ is the set of actions updating the cooperative sorts according to the current state of the
-components:
-if $j\in\DNdep(f^i)$, $a^j_k$ hits each process $f^i_\varsigma$ where $\get{\varsigma}{a^j}\neq
-a^j_k$ to make it bounce to the process $f^i_{\varsigma \Cap a^j_k}$.
-%$f^i_{\varsigma'}$ where $\get{\varsigma'}{a^j}=a^j_k$.
-$\Hits^{(2)}$ is the set of actions encoding the transitions in the ADN:
-$f^i_\varsigma$ hits the processes of sort $a^i$ to make them bounce to the process
+Let us denote the encoding of a given ADN $\DNdef$ into an AAN by $\toPH\DNdef$ (\pref{def:DN2PH}).
+For each component $i\in\segm{1}{n}$ of the ADN,
+one automaton $a^i$ is built, acting for the component value.
+Obviously, $a^i$ has one local state $a^i_k$ per element $k \in \mathbb F^i$.
+It is then sufficient to build actions towards $a^i$
+depending on any possible state of the components in $\DNdep(f^i)$
+and the related value of the evolution function $f^i$.
+
+$f^i_\varsigma$ hits the local states of automaton $a^i$ to make them bounce to the local state
 $a^i_{k'}$ if and only if $k'=f^i(\decode \varsigma)$;
@@
 
+% 
+% between the components $\DNdep(f^i)$.
+% 
+% Two classes of actions are then defined:
+% $\Hits^{(1)}$ is the set of actions updating the cooperative automata according to the current state of the
+% components:
+% if $j\in\DNdep(f^i)$, $a^j_k$ hits each local state $f^i_\varsigma$ where $\get{\varsigma}{a^j}\neq
+% a^j_k$ to make it bounce to the local state $f^i_{\varsigma \Cap a^j_k}$.
+% $\Hits^{(2)}$ is the set of actions encoding the transitions in the ADN:
+% $f^i_\varsigma$ hits the local states of automaton $a^i$ to make them bounce to the local state
+% $a^i_{k'}$ if and only if $k'=f^i(\decode \varsigma)$;
+% $\decode \varsigma$ being the ADN state corresponding to the PH (partial) state $\varsigma$ (note that
+% $f^i(\decode \varsigma)$ is fully defined because $\decode \varsigma$ specifies the state for all
+% the components in $\DNdep(f^i)$).
+
 \begin{definition}
 \label{def:DN2PH}
-  $\toPH\DNdef=(\Sigma,\PHl,(\Hits^{(1)},\Hits^{(2)}))$ is the Process Hitting with 2 classes of priority encoding the
-  ADN $\DNdef$, with:
+  $\toPH\DNdef=(\Sigma,\PHl,\Hits)$ is the AAN encoding the ADN $\DNdef$, with:
   \begin{itemize}
-    \item $\Sigma = \{ a^1, \dots, a^n \} \cup \{ f^1, \dots, f^n \}$,
-      the sorts for components ($a^i$) and cooperative sorts ($f^i$);
+    \item $\Sigma = \{ a^1, \dots, a^n \}$;
+%      the automata representing components;
 
-    \item $\PHl=\underset{i\in\segm{1}{n}}{\times} \PHl_{a^i} \times \underset{i\in\segm{1}{n}}{\times} \PHl_{f^i}$, where
-      $\PHl_{a^i}=\{a^i_0, \dots, a^i_{l_i}\}$, and
-      $\PHl_{f^i}=\{f^i_\varsigma \mid \varsigma\in\underset{j\in\DNdep(f^i)}{\times} \PHl_{a^i} \}$
-      if $\DNdep(f^i)\neq\emptyset$, otherwise
-      $\PHl_{f^i}=\{f^i_\emptyset\}$;
+    \item $\PHl=\underset{i\in\segm{1}{n}}{\times} \PHl_{a^i}$, where
+      $\PHl_{a^i}=\{a^i_0, \dots, a^i_{l_i}\}$;
 
-    \item $\Hits^{(1)}= \{ \hit{a^j_k}{f^i_\varsigma}{f^i_{\varsigma'}}
-      \mid i\in\segm{1}{n} \wedge
-      j\in\DNdep(f^i) \wedge a^j_k\in \PHl_{a^j} \wedge f^i_\varsigma\in \PHl_{f^i}
-      \wedge
-      \get{\varsigma}{a^j}\neq a^j_k 
-      \wedge \get{\varsigma'}{a^j}=a^j_k
-      \wedge (\get{\varsigma'}{a^{l}}=\get{\varsigma}{a^l},
-      \forall l\in\segm{1}{n},l\neq j)
-      \}$, 
-      the set of actions with priority $1$ that update cooperative sorts;
+    \item $\PHh = \{ \PHfrappe{A}{a^i_j}{a^i_k} \mid
+      \exists \varsigma \PHsubl[\PHl]_{\DNdep(f^i)}, \exists x \in \mathbb{F},
+      \varsigma \subseteq \encode{x} \wedge
+      f^i(x) = k \wedge \PHget{x}{i} = j \wedge j \neq k \wedge
+      A = \toset{\varsigma} \}$ where $\encode{x}$ is defined below.
 
-    \item $\Hits^{(2)}=\{ \hit{f^i_\varsigma}{a^i_k}{a^i_{k'}} \mid i\in\segm{1}{n} \wedge
-          f^i_\varsigma\in \PHl_{f^i} \wedge
-          a^i_k\in \PHl_{a^i}\wedge k\neq k' \wedge f^i(\decode \varsigma) = k'
-        \}$,
-      the set of actions with priority $2$ for updating the components using their respective discrete
-      maps.
-      $\decode \varsigma$ is defined below.
+%     \item $\Hits^{(1)}= \{ \hit{a^j_k}{f^i_\varsigma}{f^i_{\varsigma'}}
+%       \mid i\in\segm{1}{n} \wedge
+%       j\in\DNdep(f^i) \wedge a^j_k\in \PHl_{a^j} \wedge f^i_\varsigma\in \PHl_{f^i}
+%       \wedge
+%       \get{\varsigma}{a^j}\neq a^j_k 
+%       \wedge \get{\varsigma'}{a^j}=a^j_k
+%       \wedge (\get{\varsigma'}{a^{l}}=\get{\varsigma}{a^l},
+%       \forall l\in\segm{1}{n},l\neq j)
+%       \}$, 
+%       the set of actions with priority $1$ that update cooperative automata;
+% 
+%     \item $\Hits^{(2)}=\{ \hit{f^i_\varsigma}{a^i_k}{a^i_{k'}} \mid i\in\segm{1}{n} \wedge
+%           f^i_\varsigma\in \PHl_{f^i} \wedge
+%           a^i_k\in \PHl_{a^i}\wedge k\neq k' \wedge f^i(\decode \varsigma) = k'
+%         \}$,
+%       the set of actions with priority $2$ for updating the components using their respective discrete
+%       maps.
+%       $\decode \varsigma$ is defined below.
   \end{itemize}
-  Given a state $s\in \PHl$ of the Process Hitting, 
+  Given a state $s \in \PHl$ of the AAN,
   $\decode s=x$ is the corresponding state in the ADN:
   $\forall i\in\segm{1}{n}, \get{s}{a^i}=a^i_k \Rightarrow \get{x}{i}=k$.
-
-  \noindent
-  Given a state $x\in \mathbb F$ of the ADN, 
-  $\encode x=s$ is the corresponding state in the Process Hitting:
-  $\forall i\in\segm{1}{n}, \get{x}{i}=k \Rightarrow \get{s}{a^i}=a^i_k$
-  and
-  $\forall i\in\segm{1}{n}, \get{s}{f^i}=f^i_\varsigma$ with $f^i_\varsigma\in \PHl_{f^i}$
-  and $\forall j\in\DNdep(f^i), \get{\varsigma}{j}=\get{s}{a^j}$.
+  Conversely, given a state $x\in \mathbb F$ of the ADN, 
+  $\encode x=s$ is the corresponding state in the AAN:
+  $\forall i\in\segm{1}{n}, \get{x}{i}=k \Rightarrow \get{s}{a^i}=a^i_k$.
 \end{definition}
 
-By construction, the cooperative sorts are well-formed, hence $\toPH\DNdef$
-satisfies the Conditions of \pref{ssec:hypothesis}.
-\pref{th:bisimDN} states the weak bisimulation relation between an ADN and its encoding in
-PH with $2$ classes of priorities.
-Intuitively, actions updating cooperative sorts being prioritised, actions updating component
-sorts follow strictly the possible transitions of the ADN.
+Finally,
+\pref{th:bisimDN} states the weak bisimulation relation between an ADN and its encoding in AAN.
+Intuitively, the actions follow strictly the possible transitions of the ADN.
 A detailed proof is given in \pref{suppl:proofbisimADN}.

### 2014-12-22 parts/models-ph-php.tex
continue transformation (encodings + examples + conclusion)

--- 2014-12-08 parts/models-ph-php.tex
@@
-\subsection{Process Hitting with multiple classes of priorities}
+\subsection{local state Hitting with multiple classes of priorities}
 \label{ssec:flattening}
 
-Consider a PH with $k \in \sNN$ classes of priories
-$\ov{\PH} = (\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}})$
-that respects all Conditions given in \pref{ssec:hypothesis}.
-If $\oPH$ does not respect these Conditions,
-it is then sufficient to instead consider the PH model with $k+1$ classes of priorities
-$\ov{\PH}' = (\ov{\PHs}; \ov{\PHl}; \ov{\PHa}'^{\angles{k+1}})$
-where $\ov{\PHh}'^{(1)} = \emptyset$.
-The aim of this section is to propose a translation of $\oPH$
-into a PH model with $2$ classes of priorities $\PH = (\PHs; \PHl; \PHa^{\angles{2}})$
-called \emph{flattening},
-which is weakly bisimilar
-and that also respects all Conditions of \pref{ssec:hypothesis}.
+In this section, we define the notion of AANs with classes of priorities,
+and give a translation from any of these AANs into
+an AAN without priorities, as defined in \pref{sec:ph}.
+
+The idea behind AANs with classes of priorities (\pref{def:php})
+is to split the set of actions into several subsets assigned to priorities,
+and adapting the behaviour of the model to make any action unplayable
+until no other action of higher priority is playable (\pref{def:playp}).
+Such model allows to model preemptions between sets of actions,
+which can be helpful to abstract time or duration properties under certain conditions.
+
+\begin{definition}[AANs with $k$ classes of priorities]
+\label{def:php}
+  If $k \in \sN^*$,
+  an \emph{Asynchronous Automata Network with $k$ classes of priorities} (AAN$k$)
+  is a triplet $\PH = (\PHs; \PHl; \PHa^{\angles{k}})$,
+  where $\PH^{\angles{k}} = (\PHh^{(1)} \dots; \PHh^{(k)})$,
+  and:
+  \begin{itemize}
+    \item $\PHs \DEF \{a, b, \dots, z\}$ is the finite set of \emph{automata};
+    \item $\PHl \DEF \underset{a \in \PHs}{\times} \PHl_a$ is the finite set of
+      (global) \emph{states},
+      where $\PHl_a = \{a_0, \ldots, a_{l_a}\}$ is the finite set of \emph{local states}
+      of automaton $a \in \PHs$, with $l_a \in \sN^*$,
+      and so that:
+      $\forall (a_i; b_j) \in \PHl_a \times \PHl_b, a \neq b \Rightarrow a_i \neq b_j$;
+    \item $\forall n \in \llbracket 1; k \rrbracket,
+      \PHa^{(n)} \DEF \{\PHfrappe{A}{b_j}{b_k} \mid
+      b \in \PHs \wedge (b_j; b_k) \in \PHl_b \times \PHl_b \wedge
+      b_j \neq b_k \wedge
+      \forall a \in \PHs, \card{A \cap \PHl_a} \leq 1 \wedge
+      A \cap \PHl_b = \emptyset \}$ is the finite set of \emph{actions of priority $n$}.
+  \end{itemize}
+  We also use the same notations as those defined in \pref{sec:ph}, when applicable.
+  Furthermore,
+  we denote by $\PHh \DEF \bigcup_{n \in \segm{1}{k}} \PHh^{(n)}$ the set of all actions
+  and, for all $h \in \PHh$,
+  by $\prio(h) \DEF \min\{ n \in \segm{1}{k} \mid h \in \PHh^{(n)} \}$
+  the priority of action $h$.
+\end{definition}
+
+\begin{definition}[Dynamics of an AAN$k$ ($\PHPtrans$)]
+\label{def:playp}
+  An action $h = \PHhit{A}{b_j}{b_k} \in \PHa^{(n)}$ of priority $n$
+  is \emph{playable} in $s \in \PHl$
+  if and only if $A \subseteq s$, $\PHget{s}{b} = b_j$ and
+  $\forall m < n, \forall g \in \PHa^{(m)},
+    \neg (\PHhitter(g) \subseteq s \wedge \PHtarget(g) \in s)$.
+  In such a case, $(s \PHplay h)$ stands for the state resulting from the play
+  of the action $h$ in $s$, which is defined by: $(s \PHplay h) = s \Cap b_k$.
+  Moreover, we denote: $s \PHPtrans (s \PHplay h)$.
+\end{definition}
+
+We consider in the following an AAN$k$ with $k \in \sNN$:
+$\ov{\PH} = (\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}})$.
+The aim of the rest this section is to propose a translation of $\oPH$
+into an AAN with $1$ class of priority $\PH = (\PHs; \PHl; \PHa^{\angles{1}})$
+called \emph{flattening}, which we also prove to be weakly bisimilar.
+This AAN with 1 class of priority is equivalent to a regular AAN without priorities;
+Therefore, such a translation is particularly useful to be able to study the dynamics of
+any kind of AAN with priorities by using the static analysis developed in \pref{sec:sa}.
 
 This translation is based on the notion of \emph{playability property} defined in \pref{def:pp}
-which is a Boolean formula where the atoms are processes of $\ov{\PH}$.
+which is a Boolean formula where the atoms are local states of $\ov{\PH}$.
 
@@
   \Fsem{\neg a_i}{\mysigma} \Leftrightarrow \Fsem{\bigvee_{\substack{a_j \in \ov{\PHl}_a\\a_j \neq a_i}} a_j}{\mysigma}\]
-Indeed, if a process is not active in a state, this means that another process of the same sort is active.
+Indeed, if a local state is not active in a state, this means that another local state of the same automaton is active.
+Furthermore, we note that:
+\[\forall a \in \ov{\PHs}, \forall a_i, a_j \in \ov{\PHl}_a,
+  a_i \neq a_j \Longrightarrow a_i \wedge a_j \equiv \bot \]
+because two different processes can never be active simultaneously.
 
 In \pref{def:fop}, we define the the operator $\Fopsymbol$ which characterises the playability of an action
-given the semantics of PH (\pref{def:play}).
-This operator considers the \emph{virtual hitters} of an action,
-which are the sub-states given by $\csState$ to activate the hitter of the given action if it is a process of cooperative sort.
-Furthermore, the target of the action is not taken into account as it is not needed for the rest of the flattening.
-%
-\begin{definition}[Playability property of an action ($\Fopsymbol : \PHh \rightarrow \F$)]\label{def:fop}
-  \[\forall h \in \ov{\PHh}, \Fop{h} \equiv \virtualhitters(h) \wedge
+given the semantics of AAN$k$s (see \pref{def:playp}).
+This operator simply states that the hitters of an action have to be active,
+and no other action of higher priority have to be playable.
+% The target of the considered action is not taken into account
+% as it is not needed for the rest of the flattening.
+
+\begin{definition}[Playability property operator ($\Fopsymbol : \PHh \rightarrow \F$)]\label{def:fop}
+  For all $h = \PHfrappe{A}{b_x}{b_y} \in \ov{\PHh}$, we define:
+  \[
+    \Fop{h} \equiv
+    b_x \wedge
+    \left(\bigwedge_{a_i \in A} a_i\right)
+    %\hitter{h}
+    \wedge
       \left( \bigwedge_{\substack{g \in \ov{\PHh}^{(n)}\\\modMF{1 <} n < \prio(h)}}
-    \neg \left( \target{g} \wedge \hitter{g}\right) \right)\]
-  where if we note $\hitter{h} = a_i$, then:
-  \[\virtualhitters(h) =
-    \begin{cases}
-      a_i & \text{if } a \in \components \text{ or } h \in \ov{\PHh}^{(1)} \\
-      \bigvee_{ps \in \csState(a_i)} \left( \bigwedge_{p \in ps} p \right) & \text{if } a \in \cs
-    \end{cases}\]
+      \neg \left( \target{g} \wedge \left(\bigwedge_{c_l \in \hitter{g}} c_l\right)\right) \right)
+%   \moda{\bigwedge_{\substack{b_z \in \PH_b\\b_z \neq b_x}} \neg b_z}
+  \]
 \end{definition}
 %
-By construction of this operator and given the dynamics of a PH model,
+By construction of this operator and given the dynamics of a AAN$k$,
 an action $h$ is playable in a state $s \in \ov{\PHl}$ if and only if: $\Fsem{\Fop{h}}{s} \wedge \target{h} \in s$.
@@
 can be seen as a disjunction of $\n$ smaller playability properties consisting only of conjunctions of atoms.
-These $\n$ conjunctions can be translated to as many prioritised cooperative sorts,
-thus creating a new PH model which is entailed in the restrictions depicted in \pref{ssec:hypothesis}.
-In this second case, we denote, for any $i \in \segm{1}{\n}$:
+These $\n$ conjunctions can be translated to as many actions,
+thus creating a new AAN$1$.
+In this case, we denote, for any $i \in \segm{1}{\n}$:
 $\PHdep{i}{h} = \{ \PHsort(p_{i,j}) \mid j \in \segm{1}{\m} \}$.
@@
 Finally, \pref{def:flattening} gives the construction of the flattening of $\oPH$:
-for each action $h \in \ov{\PHh}$, several cooperative sorts $f^{h,i}$ are built to reflect each of the conjunction in $\Fop{h}$,
+for each action $h \in \ov{\PHh}$, several actions $f^{h,i}$ are built to reflect each of the conjunctions in $\Fop{h}$,
 \ie for $i \in \segm{1}{\n}$.
@@
   ($\Leftarrow$)
-    $\Fsem{\Fop{h}}{\mysigma}$ therefore $\Fsem{\Fop{h}}{s}$; as $\target{h} \in s$, $h$ is playable in $s$.
+    $\Fsem{\Fop{h}}{\mysigma}$ therefore $\Fsem{\Fop{h}}{s}$; as $\target{h} \in s$,
+    $h$ is playable in $s$.
 \end{proof}
@@
   \label{def:flattening}
-  If $k \in \sNN$ and $\oPH = (\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}})$
-  is a PH with $k$ classes of priorities that respects all Conditions of \pref{ssec:hypothesis},
-  we note $\PHflat(\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}}) = (\PHs; \PHl; \PHa^{\angles{2}})$
+  If $k \in \sNN$ and $\oPH = (\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}})$ is an AAN$k$,
+  we denote by
+  $\PHflat(\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}}) = (\PHs; \PHl; \PHa)$
   the \emph{flattening} of $\oPH$, where:
   \begin{itemize}
-    \item $\PHs = \ov{\PHs} \cup \PHs_f$
-      where $\PHs_f = \{ f^{h,i} \mid h \in \ov{\PHh} \wedge \n \geq 1 \wedge i \in \segm{1}{\n} \}$;
-    \item $\PHl = \left( \bigtimes{a \in \ov{\PHs}} \PHl_{a} \right) \times
-      \left(\bigtimes{f^{h,i} \in \PHs_f} \PHl_{f^{h,i}} \right)$,
-      where $\forall a \in \ov{\PHs}, \PHl_{a} = \ov{\PHl}_{a}$, and
-      $\forall f^{h,i} \in \PHs_f,
-      \PHl_{f^{h,i}} = \{ f^{h,i}_\mysigma \mid \mysigma \in \PHsubl_{\PHdep{i}{h}} \}$;
-    \item $\PHh^{(1)} = \{ \PHhit{a_k}{f^{h,i}_\mysigma}{f^{h,i}_{\mysigma'}} \mid
-      h \in \ov{\PHh} \wedge
-      f^{h,i} \in \PHs_f \wedge
-      a \in \PHdep{i}{h} \wedge a_k \in \PHl_a \wedge
-      f^{h,i}_\mysigma , f^{h,i}_{\mysigma'} \in \PHl_{f^{h,i}} \wedge
-      \PHget{\mysigma}{a} \neq a_k \wedge \mysigma' = \mysigma \Cap \{ a_k \} \}$;
-    \item $\PHh^{(2)}=\{ \PHhit{f^{h,i}_\mysigma}{\target{h}}{\bounce{h}} \mid
-      h \in \ov{\PHh} \setminus \ov{\PHh}^{(1)} \wedge
-      f^{h,i} \in \PHs_f \wedge
-      f^{h,i}_\mysigma \in \PHl_{f^{h,i}} \wedge \Fsem{\Fop{h}}{\mysigma} \}$.
+    \item $\PHs = \ov{\PHs}$;
+
+    \item $\PHl = \ov{\PHl}$;
+
+    \item $\PHh = \{
+      \PHfrappe{(\toset{\mysigma} \setminus \{ \target{h} \})}{\target{h}}{\bounce{h}} \mid
+      h \in \ov{\PHh} \wedge \n \geq 1 \wedge i \in \segm{1}{\n} \wedge
+      \mysigma \in \PHsubl_{\PHdep{i}{h}} \wedge
+      \Fsem{\Fop{h}}{\mysigma} \}$.
   \end{itemize}
-  Given a state $s \in \PHl$, $\unflats{s} = \os$ is the corresponding state in $\ov{\PHl}$:
-  $\forall a \in \ov{\PHs}, \PHget{\os}{a} = \PHget{s}{a}$.
+%   Given a state $s \in \PHl$, $\unflats{s} = \os$ is the corresponding state in $\ov{\PHl}$:
+%   $\forall a \in \ov{\PHs}, \PHget{\os}{a} = \PHget{s}{a}$.
+%   Conversely,
+%   given a state $\os \in \ov{\PHl}$, $\flats{\os} = s$ is the corresponding state in $\PHl$:
+%   $\forall a \in \ov{\PHs}, \PHget{s}{a} = \PHget{\os}{a}$.
+\end{definition}
 
-  \noindent
-  Given a state $\os \in \ov{\PHl}$, $\flats{\os} = s$ is the corresponding state in $\PHl$:
-  $\forall a \in \ov{\PHs}, \PHget{s}{a} = \PHget{\os}{a}$
-  and $\forall f^{h,i} \in \PHs_f, \PHget{s}{f^{h,i}} = f^{h,i}_\mysigma$ with $f^{h,i}_\mysigma \in \PHl_{f^{h,i}}$
-  and $\forall b \in \PHdep{i}{h}, \PHget{\mysigma}{b} = \PHget{\os}{b}$.
-\end{definition}
+We note that the set of global states of an AAN$k$
+and the set of global states of its flattening are the same.
 
@@
 \label{th:bisimPHP}
-  Let $\ov{\PH} = (\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}})$ a PH with $k$ classes of priorities,
-  and $\PH = \PHflat(\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}}) = (\PHs; \PHl; \PHa^{\angles{2}})$ its flattening.
-  \begin{enumerate}
-    \item \label{php2ph} $\forall \os, \os' \in \ov{\PHl}$,
-      $\os \PHPtrans[\oPH] \os' \Longrightarrow \flats{\os} \PHPtrans[\oPH]^* \flats{\os'}$,
-      where $\PHPtrans[\oPH]^*$ is a finite sequence of $\PHPtrans[\oPH]$ transitions.
-    \item \label{ph2php} $\forall s, s' \in \PHl$,
-      $s \PHPtrans s' \Longrightarrow \unflats{s} = \unflats{s'} \vee
-      \unflats{s} \PHPtrans \unflats{s'} \enspace.$
-  \end{enumerate}
+  If $\ov{\PH} = (\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}})$ is an AAN$k$
+  and $\PH = \PHflat(\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}}) =
+    (\PHs; \PHl; \PHa)$ is its flattening, then:
+  \[ \forall s, s' \in \PHl, s \PHPtrans[\oPH] s' \Longleftrightarrow s \PHPtrans[\PH] s' \]
 \end{theorem}
 
-We showed in this subsection that it is possible to model a PH with $k$ classes of priorities as a PH
-with $2$ classes of priorities and the same dynamics.
-Furthermore, by construction, the cooperative sorts are well-formed, and $\PHflat(\oPH)$
-thus satisfies the Conditions of \pref{ssec:hypothesis}.
-We note however that the translation given in this section may not be minimal in terms of number of actions
-or cooperative sorts.
-We give here several ways to simplify the resulting model, but we do not give the proofs.
-
-\paragraph{Playability properties simplifications}
-The playability property $\Fop{h}$ of an action $h = \PHhit{a_i}{b_j}{b_k}$ can be simplified with the following properties,
-which may remove the necessity to create some useless actions (that are never playable) or cooperations (that are always true):
-\begin{itemize}
-  \item it is always possible to simplify the target because its presence is checked besides: $b_j \equiv \top$;
-  \item any process $b_l \neq b_j$ of the same sort than the target always prevents the playability, thus: $b_l \equiv \bot$;
-  \item if $c_p, c_q$ are different processes ($c_p \neq c_q$) of the same sort $c$, then $c_p \wedge c_q \equiv \bot$.
-\end{itemize}
-
-\paragraph{Removal of the unnecessary cooperative sorts}
-There are two cases where it is possible to remove a cooperative sort $f^{h,i}$ in the flattening:
-\begin{itemize}
-  \item if $\Fop{h} \equiv \top$, then the action $h$ can be translated as an auto-action
-    (as it is always playable if the target is present);
-  \item if the $i$\textsuperscript{th} conjunction of $\Fop{h}$ consists of only one element $p$,
-    then \modMF{this conjunction} can be translated as a regular action $\PHhit{p}{\target{h}}{\bounce{h}}$ instead of a cooperative sort
-    (as, apart from the target, only one process is required).
-\end{itemize}
+We showed in this subsection that it is possible to model any AAN$k$
+as an AAN (or, equivalently, as an AAN$1$).
+this translation thus extends the applicability of the static analysis developed in
+\pref{sec:sa} to any AAN$k$, with $k \in \sN^*$.
+The translation given in this section
+is exponential in the number of actions of higher priority for each action.

### 2014-12-22 main.tex
begin transformation PH to AAN
continue transformation (encodings + examples + conclusion)
almost finish transformation (except appendix)

@@
 \newrefformat{th}{Theorem~\ref{#1}}
+\newrefformat{thm}{Theorem~\ref{#1}}
 \newrefformat{co}{Corollary~\ref{#1}}
@@
 \newcommand{\update}{\mathsf{update}}
-\newcommand{\components}{\Gamma}
+\newcommand{\components}{\PHs}
 %\newcommand{\cs}{CS}
-\newcommand{\cs}{\Delta}
+\newcommand{\cs}{\textcolor{red}{\Delta}}
 
@@
 \def\modMF#1{\textcolor{teal}{#1}}
-\def\modLP#1{\textcolor{magenta}{#1}}
-\def\modMM#1{\textcolor{blue}{#1}}
-\def\modOR#1{\textcolor{olive}{#1}}
-%\def\modMF#1{#1} \def\modLP#1{#1} \def\modMM#1{#1} \def\modOR#1{#1}
+\def\moda#1{\textcolor{blue}{#1}}
+% \def\modLP#1{\textcolor{magenta}{#1}}
+% \def\modMM#1{\textcolor{blue}{#1}}
+% \def\modOR#1{\textcolor{olive}{#1}}
+%\def\modMF#1{#1} \def\moda#1{#1} \def\modLP#1{#1} \def\modMM#1{#1} \def\modOR#1{#1}
 
@@
 \begin{abstract}
-The Process Hitting is a recently introduced framework designed for the modelling of concurrent systems.
-Its originality lies in a compact representation of both components of the model and its corresponding actions:
-each action can modify the status of a component, and is conditioned by the status of at most one other component.
-This allowed to define very efficient static analysis based on local causality to compute reachability properties.
-However, in some cases, this modelling lacks some preemption features
-that would allow to model relative time constraints between interactions.
+The Process Hitting is a recently introduced framework
+designed for the modelling and analysis of concurrent systems.
+The particular form of its actions (encoding the dynamics into the models)
+allowed to define very efficient static analysis
+based on local causality to compute reachability properties.
+However, this modelling shows its limits when preemption features are needed,
+and especially for cooperations
+(that is, the regulation of two components that jointly interact with a third one).
 
-In this paper, we propose an extension of the Process Hitting framework
-by using classes of priorities in order to improve its expressivity.
-Furthermore, we develop a new refinement for the under-approximation of the static analysis
-to give accurate results on Process Hitting models.
-This method applies to a specific sub-class of models,
-but this class turns out to be sufficiently expressive to represent any
-Process Hitting model with an arbitrary number of classes of priorities,
-thus guaranteeing a wide field of application of our method.
+In this paper, we focus on
+the Asynchronous Automata Network (AAN) formalism,
+which is an extension of the Process Hitting with an increased expressivity.
+Like the Process Hitting,
+the originality of AANs is the restrictions of the actions
+that have an effect limited to exactly one component;
+but unlike Process Hitting, their causality is not restricted to at most one other component.
 
-Finally, we also show that the priorities
-allow to represent accurate Boolean gates in order to model
-cooperations between components
-(that is, for instance, when two components are supposed to interact with a third one
-only when they are in a given configuration)
-which was not possible before.
-This allows to accurately model
+We then develop a new refinement for the under-approximation of the static analysis
+to efficiently compute results on the dynamics of AANs.
+Because of the expressivity improvements,
+this analysis gives more accurate results
+than the previous works carried on the Process Hitting.
+Furthermore, its complexity is still polynomial in the size of the model
+and exponential in the number of possible “branchings” during the solving.
+
+We also extend the applicability of this static analysis to
+AANs with classes of priorities and to
 Asynchronous Discrete Networks, either Boolean or multivalued,
-and efficiently under-approximate reachability properties
-in these models.
+which allows to efficiently study the dynamics of these widespread models
+% efficiently under-approximate reachability properties
+% in these widespread models.
 We illustrate this on the model-checking of a signalling network of 94

### 2014-12-22 parts/def-ph.tex
almost finish transformation (except appendix)

@@
 can only change one local state at a time.
-\todo{We also discuss how it is related to the local state Hitting framework (with priorities)
-\cite{PMR10-TCSB,FPMR13-CS2Bio}.}
-As shown in \pref{sec:encodings},
-this class of models is equivalent to Asynchronous Discrete Networks,
-and extending it with classes of priorities does not increase its expressivity.
+We also discuss how it is related to the Process Hitting framework
+(with or without classes of priorities).
+In \pref{sec:encodings}, we will also introduce classes of priorities into these models,
+and show that they are equivalent to Asynchronous Discrete Networks.
 
@@
 as detailed in \pref{ssec:flattening}.
+
+We note that obviously, Process Hitting~\cite{PMR10-TCSB} being a restriction of AANs,
+one can easily encode any Process Hitting model as an AAN by using only actions
+$\PHfrappe{A}{b_j}{b_k}$ so that $0 \leq \card{A} \leq 1$.
+Process Hitting with classes of priorities~\cite{FPMR13-CS2Bio} can also be encoded as AANs
+with priorities, as defined in \pref{sec:encodings},
+by using the same priorities for each action,
+and possibly translate them into simple AANs.

### 2014-12-22 parts/intro.tex
almost finish transformation (except appendix)

@@
 Among these questions, a major one is to understand precisely how biological systems evolve and behave; why and how they change their usual behaviours, etc.
-This leads to questions about the (possible or inevitable) reachability of some states.
-The ultimate goal is to discover how it could be possible to prevent biological systems from reaching some pathological states.
+These questions are strongly linked to the (possible or inevitable) reachability of some states.
+The ultimate goal is to discover how it could be possible to prevent biological systems from reaching some pathological conditions.
 \todo{Ajouter des références}
@@
 Prevalent formal frameworks for such modelling activities are state-transition systems or process algebras. % Petri nets
-We developed a quite similar framework named the Process Hitting \cite{PMR10-TCSB},
+We developed a quite similar framework named the Process Hitting~\cite{PMR10-TCSB},
 consisting in a restriction of these frameworks where the evolution of a component is determined by the state of at most one other component that does not evolve.
@@
 that are based on the simple founding idea that actions with higher priority have to be processed before the ones with lower priority.
-Furthermore, due to the Process Hitting framework restrictions, multimolecular reactions are not immediately available, but one can simulate them with an encoding called “cooperation”.
-That encoding however introduces extra reactions, and this is where the priorities become useful, if not necessary.
-The extra reactions can be given “infinite speed” (highest priority) so that they do not affect the behaviour of “normal” (lower priority) reactions, including the multimolecular ones.
+Furthermore, due to the Process Hitting framework restrictions, multimolecular reactions were previously not immediately available, but one could simulate them with an encoding called “cooperative sort”.
+That encoding however introduces extra reactions,
+that produce a temporal shift between the presence of the reactants
+and the playability of the reaction.
+This is where the priorities become useful, if not necessary:
+the extra reactions can for example be given “infinite speed” (highest priority) so that they do not affect the behaviour of “normal” (lower priority) reactions, including the multimolecular ones.
+Another approach consists in considering another class of models,
+that we call Asynchronous Automata Network,
+and that allows to naturally model these cooperations
+by defining several requisites for a reaction.
+Furthermore, such automata networks are still compatible with the notion of priority,
+that can also be used to model different reaction rates in the model.
 
 Until now, such a priority scheduling of the actions was not studied extensively in the different formal modelling frameworks dedicated to systems biology.
-Nevertheless, such an attempt has been carried out for Petri nets by F.~Bause \cite{Bause97},
-and the concept of priority relations among the transitions of a network has also more recently been introduced by A.~K.~Wagler \textit{et~al.} \cite{waw,WaglerW12} in order to allow modelling deterministic systems for biological applications.
-The concept of priority is much straightforward in the approach of process algebras as it was shown by R.~Cleaveland and M.~Hennessy in \cite{Cleaveland199058,Cleaveland99prioritiesin} and their abstractions and equivalences were studied in \cite{Cleaveland:2007:PAP:1282576.1282847}.
-It was later extended for applications in the field of systems biology by M.~John \textit{et~al.} \cite{jlnu2010}.
+Nevertheless, such an attempt has been carried out for Petri nets by F.~Bause~\cite{Bause97},
+and the concept of priority relations among the transitions of a network has also more recently been introduced by A.~K.~Wagler \textit{et~al.}~\cite{waw,WaglerW12} in order to allow modelling deterministic systems for biological applications.
+The concept of priority is much straightforward in the approach of process algebras as it was shown by R.~Cleaveland and M.~Hennessy in~\cite{Cleaveland199058,Cleaveland99prioritiesin} and their abstractions and equivalences were studied in~\cite{Cleaveland:2007:PAP:1282576.1282847}.
+It was later extended for applications in the field of systems biology by M.~John \textit{et~al.}~\cite{jlnu2010}.
 
 \subsection*{Contributions}
-\todo{Compléter les contributions}
-Since our formalism (the Process Hitting) can be considered as a subset of Calculus of Communicating Systems, %is inspired from the $\pi$-calculus,
+Since our formalisms (the Asynchronous Automata Network and the Process Hitting)
+can be considered as a subset of Calculus of Communicating Systems,
+or Synchronous Automata Networks,
+%is inspired from the $\pi$-calculus,
 our work is related to such semantic ramifications of extending traditional process algebras with the concept of priority that allows for some transitions to be given precedence over others.
@@
 The actions modelling biological processes are divided in several classes of priorities which stand for the different reaction rates or relative preemptions.
-Furthermore, the highest class of priority is used to model particular nonbiological actions, designated as “prioritised”,
-that are used to encode Boolean functions inside the model.
+Furthermore, the multiple causality of the actions in Asynchronous Automata Networks
+allow to abstract a highest class of priority that would be used
+to model particular nonbiological actions
+that encode Boolean functions inside the model.
 
-This paper is an extension of \cite{FPMR13-CS2Bio} where we
-introduced a new extension to the semantics of Process Hitting by partitioning actions into classes of priorities
-(\pref{sec:ph}).
-One of the objectives is to reach an accurate representation of cooperating components in the model, that was not fulfilled with the initial semantics, using only two classes of priorities.
+This paper is an extension of~\cite{FPMR13-CS2Bio} where we
+introduced a new extension to the semantics of Process Hitting
+by partitioning actions into classes of priorities.
+One of our objectives was to reach an accurate representation of cooperating components in the model, that was not fulfilled with the initial semantics.
+Although in~\cite{FPMR13-CS2Bio} this was achieved with a particular class of high priority,
+the work presented in this paper, however, focuses on Asynchronous Automata Networks.
+The simple version of this formalism (without classes of priorities)
+is defined in \pref{sec:ph}
+and consists of an extension of Process Hitting with classes of priorities
+that allows to simplify the formalisation with the same benefits.
 In \pref{sec:sa},
-we develop an efficient under-approximation of the reachability of the state of components on a subclass of this new framework, thus allowing to compute efficient static analysis.
-This local reachability under-approximation can be also easily extended to study the reachability of a global state.
-Furthermore, we provide a new extended under-approximation method to check a successive reachability property.
+we develop an efficient under-approximation of the reachability
+of several local states of components,
+thus allowing to compute efficient static analysis of the dynamics.
+This local reachability under-approximation can be also easily extended to study the reachability of a global or partial state.
+Furthermore, we provide a new extended under-approximation method to refine this method
+in the case of a successive reachability property.
 
-Whereas the analysis presented in \pref{sec:sa} considers a particular class of
-Process Hitting with two classes of priority,
-we provide in \pref{sec:encodings} a “flattening” of any Process Hitting model into
-this class of models,
-so that its application is not restricted to it.
+Furthermore,
+we define in \pref{sec:encodings} the notion of Asynchronous Automata Networks
+with classes of priorities,
+that consists of a convenient way to introduce time parameters
+into the models, under the form of preemptions.
+We also provide in \pref{sec:encodings} a “flattening”
+of any Asynchronous Automata Networks with classes of priorities
+into a model without classes of priorities,
+thus extending the range of applicability of the static analysis.
 We also give in the same section a formal encoding of Asynchronous Discrete Networks,
@@
 which encompass variables and evolution functions with a limited number of discrete values,
-also called “Logical Networks” in~\cite{Thomas95,deJong02}.
+are also called “Logical Networks” in~\cite{Thomas95,deJong02}.
 This encoding thus allows to efficiently study this kind of widespread models.
 
-In \pref{sec:example}, after giving an example of the encoding of a biological
-network with multiple priority classes,
-we apply our method on a large-scale biological model containing 94 components.
-The under-approximation turned out to be conclusive in all cases and results were computed in hundredths of seconds,
+In \pref{sec:example}, we give two examples of the use of our method.
+The first consists of a detailed application of the analysis of a biological network expressed as
+an ANN with 2 classes of priorities,
+which requires to be encoded into a simple ANN (without priorities).
+The second consists of applying our method
+on a large-scale biological model containing 94 components;
+the under-approximation turned out to be conclusive in all cases and results were computed in hundredths of seconds,
 thus overtaking the efficiency of usual model-checkers.
@@
 \modMF{
-The main addition in this paper compared to \cite{FPMR13-CS2Bio} are the following:
-\pref{th:bisimPHP} states that any Process Hitting model with any number of classes of priorities
-can be represented with only two classes of priorities,
+The main addition in this paper compared to~\cite{FPMR13-CS2Bio} is
+the representation under the form of ANNs, that allow to simplify the formalisation.
+Furthermore, we give new tools to improve the applicability of our method:
+\pref{th:bisimPHP} states that any ANN with any number of classes of priorities
+can be represented into a simple ANN (or, equivalently, with only one class of priority),
 thus extending the scope of our method to any possible Process Hitting model;
-\pref{thm:ordered-ua} gives a method to cope with successive reachability,
+\pref{thm:ordered-ua} gives a method to refine successive reachability,
 and obtain more conclusive results in the case of several successive objectives;
-\todo{def extraction} allows to extract a concrete scenario when our static analysis method
+\pref{def:concret} allows to extract a concrete scenario when our static analysis method
 is conclusive.
-%All aim at extending the application range of the static analysis we developed.
 }

### 2014-12-22 parts/models-ph-dn.tex
almost finish transformation (except appendix)

@@
 
-$f^i_\varsigma$ hits the local states of automaton $a^i$ to make them bounce to the local state
-$a^i_{k'}$ if and only if $k'=f^i(\decode \varsigma)$;
-$\decode \varsigma$ being the ADN state corresponding to the PH (partial) state $\varsigma$ (note that
-$f^i(\decode \varsigma)$ is fully defined because $\decode \varsigma$ specifies the state for all
-the components in $\DNdep(f^i)$).
-
-% 
-% between the components $\DNdep(f^i)$.
-% 
-% Two classes of actions are then defined:
-% $\Hits^{(1)}$ is the set of actions updating the cooperative automata according to the current state of the
-% components:
-% if $j\in\DNdep(f^i)$, $a^j_k$ hits each local state $f^i_\varsigma$ where $\get{\varsigma}{a^j}\neq
-% a^j_k$ to make it bounce to the local state $f^i_{\varsigma \Cap a^j_k}$.
-% $\Hits^{(2)}$ is the set of actions encoding the transitions in the ADN:
-% $f^i_\varsigma$ hits the local states of automaton $a^i$ to make them bounce to the local state
-% $a^i_{k'}$ if and only if $k'=f^i(\decode \varsigma)$;
-% $\decode \varsigma$ being the ADN state corresponding to the PH (partial) state $\varsigma$ (note that
-% $f^i(\decode \varsigma)$ is fully defined because $\decode \varsigma$ specifies the state for all
-% the components in $\DNdep(f^i)$).
-
-\begin{definition}
+\begin{definition}[Encoding ($\toPH$)]
 \label{def:DN2PH}
@@
     \item $\Sigma = \{ a^1, \dots, a^n \}$;
-%      the automata representing components;
 
@@
       A = \toset{\varsigma} \}$ where $\encode{x}$ is defined below.
-
-%     \item $\Hits^{(1)}= \{ \hit{a^j_k}{f^i_\varsigma}{f^i_{\varsigma'}}
-%       \mid i\in\segm{1}{n} \wedge
-%       j\in\DNdep(f^i) \wedge a^j_k\in \PHl_{a^j} \wedge f^i_\varsigma\in \PHl_{f^i}
-%       \wedge
-%       \get{\varsigma}{a^j}\neq a^j_k 
-%       \wedge \get{\varsigma'}{a^j}=a^j_k
-%       \wedge (\get{\varsigma'}{a^{l}}=\get{\varsigma}{a^l},
-%       \forall l\in\segm{1}{n},l\neq j)
-%       \}$, 
-%       the set of actions with priority $1$ that update cooperative automata;
-% 
-%     \item $\Hits^{(2)}=\{ \hit{f^i_\varsigma}{a^i_k}{a^i_{k'}} \mid i\in\segm{1}{n} \wedge
-%           f^i_\varsigma\in \PHl_{f^i} \wedge
-%           a^i_k\in \PHl_{a^i}\wedge k\neq k' \wedge f^i(\decode \varsigma) = k'
-%         \}$,
-%       the set of actions with priority $2$ for updating the components using their respective discrete
-%       maps.
-%       $\decode \varsigma$ is defined below.
   \end{itemize}
@@
 Intuitively, the actions follow strictly the possible transitions of the ADN.
-A detailed proof is given in \pref{suppl:proofbisimADN}.
+A detailed proof is given in \pref{suppl:proofbisimADN}. \todo{Utile ?}
 
-\begin{theorem}[$\DNdef \approx \toPH\DNdef$]~
+\begin{theorem}[$\DNdef \approx \toPH\DNdef$]
 \label{th:bisimDN}
+  If $\DNdef$ is an ADN
+  and $\PH = \toPH\DNdef = (\PHs; \PHl; \PHa)$ is its AAN encoding, then:
   \begin{enumerate}
     \item \label{adn2ph} $\forall x,x'\in\mathbb F$,
-      $x\DNtrans x' \Longrightarrow \encode x \PHPtrans^* \encode{x'}$,
-      where $\PHPtrans^*$ is a finite sequence of $\PHPtrans$ transitions.
-
+      $x\DNtrans x' \Longrightarrow \encode x \PHPtrans \encode{x'}$,
     \item \label{ph2adn} $\forall s,s'\in \PHl$,
-      $s\PHPtrans s' \Longrightarrow \decode s = \decode {s'} \vee \decode s \DNtrans
+      $s\PHPtrans s' \Longrightarrow \decode s \DNtrans
       \decode{s'}\enspace.$

### 2014-12-22 parts/sa.tex
almost finish transformation (except appendix)

@@
 \todo{Replacer notre méthode par rapport aux méthodes d'interprétation abstraite en général}
-
-\todo{Gluer : explication des définitions, etc.}
 
@@
 that are necessarily contained in other automata.
+In the end, a scenario can be obtained by analysing all values of
+$\osres_s(\w)$ (\pref{def:concret})
+for all possible initial state $s \subseteq \ctx$ in the considered context,
+and all possible bounce sequences $\zeta \in \BS(P)$ that are chosen during the resolution.
 }%
@@
 \begin{definition}[$\osres : \PHl \times \OS \to \Sce$]
+\label{def:concret}
 \modMF{%
@@
     \rec_s(\zeta)
-      & \text{otherwise, with } \zeta \in \BS(P) \text{\todo{Selon possbilités}}
+      & \text{otherwise, with } \zeta \in \BS(P)
   \end{cases}
@@
 \end{definition}
-
-\todo{Gérer les choix multiples possibles de $\zeta \in \BS(P)$}

### 2014-12-23 parts/models-ph-php.tex
almost finish transformation (except appendix)
finish transformation on the appendix

@@
-\subsection{local state Hitting with multiple classes of priorities}
+\subsection{Asynchronous Automata Networks with classes of priorities}
 \label{ssec:flattening}
@@
 \begin{definition}[Playability property operator ($\Fopsymbol : \PHh \rightarrow \F$)]\label{def:fop}
-  For all $h = \PHfrappe{A}{b_x}{b_y} \in \ov{\PHh}$, we define:
+  For all $h = \PHfrappe{A}{b_j}{b_m} \in \ov{\PHh}$, we define:
   \[
     \Fop{h} \equiv
-    b_x \wedge
+    b_j \wedge
     \left(\bigwedge_{a_i \in A} a_i\right)
@@
 By construction of this operator and given the dynamics of a AAN$k$,
-an action $h$ is playable in a state $s \in \ov{\PHl}$ if and only if: $\Fsem{\Fop{h}}{s} \wedge \target{h} \in s$.
+an action $h$ is playable in a state $s \in \ov{\PHl}$ if and only if: $\Fsem{\Fop{h}}{s}$.
 
@@
 This construction allows to obtain the same dynamics as $\oPH$, as stated by \pref{th:bisimPHP}.
-A detailed proof of this theorem is available in \pref{suppl:demoflattening}.
-%
+
 \begin{lemma}
@@
 
-\begin{definition}
+\begin{definition}[Flattening ($\PHflat$)]
   \label{def:flattening}
@@
 
+\begin{proof}
+  By definition of $\PHflat$.
+\end{proof}
+
 We showed in this subsection that it is possible to model any AAN$k$

### 2014-12-23 parts/suppl-sa.tex
finish transformation on the appendix

@@
 In the following, we denote:
-$\Bee{X}{Y} = \Be \cap (X \times Y)$, with $X, Y$ amongst $\PHproc$, $\Obj$ and $\Sol$.
+$\Bee{X}{Y} = \Be \cap (X \times Y)$, with $X, Y$
+amongst $\PHproc$, $\Obj$, $\sSol$ and $\Sol$.
 
@@
 
-Let $(a_i, ps) \in \Bee{\Proc}{\Sol}$ be an edge linking the required process of a cooperative sort to a solution set and suppose all successors of $ps$ are concretisable.
-We label all processes of $ps$ by an integer: $ps = \{ p_n \}_{n \in \indexes{ps}}$.
+Let $ps \in \Bv \cap \sSol$ be a set of hitters
+and suppose all of its successors are concretisable.
+We first want to demonstrate that
+there exists a scenario that activate all the local states it contains.
+We label all local states of $ps$ by an integer: $ps = \{ p_n \}_{n \in \indexes{ps}}$.
 Let us prove by induction that for all $n \in \indexes{ps}$, there exists a scenario $\delta_n$ so that:
@@
   \item Suppose such $\delta_n$ exists and let $q = \PHget{(s \PHplay \delta_n)}{\PHsort(p_{n+1})}$.
-    By hypothesis, $(a_i, ps)$ is coherent (\pref{def:coherent}) and all processes of $ps$ are processes of components;
-    this means that none of the processes needed to solve $p_{n+1}$ is another process of the same sort than another process of $ps$.
+    By construction, $p_{n+1} \in \Bv \cap \Proc$ is a direct successor of $ps$.
+    Furthermore, by hypothesis, $ps$ is coherent (see \pref{def:coherent}).
+    This means that amongst all the successors in $\Proc$ of $p_{n+1}$,
+    there does not exist a local state $b_j$ to that
+    $\exists b_k \in ps, \PHsort(b_j) = \PHsort(b_k) \wedge b_j \neq b_k$;
+    in other words, the resolution of $p_{n+1}$ does not require a local state
+    that may change the other local states of the set $ps$.
     Therefore, there exists $\delta' \in \muconcr_{s \PHplay \delta_n}(\PHobj{q}{p_{n+1}})$,
     so that $\forall i \in \segm{1}{n+1}$, $\PHget{(s \PHplay \delta_n \PHplay \delta')}{\PHsort(p_{i})} = p_{i}$.
-    Finally, by \pref{lem:update}, there exists a scenario $\delta'' \in \restriction{\Sce}{1}(s \PHplay \delta_n \PHplay \delta')$
-    so that, if we denote $\delta_{n+1} = \delta_n \PHplay \delta' \PHplay \delta''$,
-    we have: $\update(s \PHplay \delta_n \PHplay \delta') = s \PHplay
-	\delta_{n+1}$ and the same property about processes (by \pref{lem:hcscomp}).
+    We denote then: $\delta_{n+1} = \delta_n \play \delta'$.
 \end{itemize}
-Therefore, $\delta = \delta_{|ps|}$ exists, and given its properties, we have: $\PHget{(s \PHplay \delta)}{a} = a_i$
-and $\update(s \PHplay \delta) = s \PHplay \delta$.
+Therefore, $\delta = \delta_{\card{ps}}$ exists, and given its properties, we have:
+$\forall i \in \segm{1}{\card{ps}}, \PHget{(s \PHplay \delta)}{\PHsort(p_{i})} = p_{i}$.
 
-As there is no cycle in $\cwB$, we show by induction that $\forall s\in L, s\subseteq max\ctx$, 
-for all objective $P$ in $\Bv \cap \Obj$ so that $\PHtarget(P) \in s$,
-$\exists \delta \in \muconcr_s(P)$.
+As there is no cycle in $\cwB$, we show by induction in the following that
+$\forall s\in L, s\subseteq max\ctx, \forall P \in \Bv \cap \Obj,
+\PHtarget(P) \in s \Longrightarrow \exists \delta \in \muconcr_s(P)$.
 \begin{itemize}
-  \item If $(P, \emptyset) \in \Bee{\Obj}{\Sol}$, either $\PHtarget(P) = \PHbounce(P)$ and $\delta = \emptyseq$;
-    or $\forall \zeta \in \BS(P), \zeta \in \Sce(s) \wedge \PHsort(\zeta) = \{ \PHsort(P) \}$
-    and $\delta = \delta_1 \PHplay \zeta_1 \PHplay \dots \PHplay
-	\delta_{|\zeta|} \PHplay \zeta_{|\zeta|}$ is a valid sequence given by
-	\pref{lem:hcompcomp}.
+  \item If $(P, \{ \emptyset \}) \in \Bee{\Obj}{\Sol}$,
+    either $\PHtarget(P) = \PHbounce(P)$ and $\delta = \emptyseq$;
+    or $\exists \zeta \in \BS(P), \zeta \in \Sce(s) \wedge
+      \forall i \in \indexes{\zeta}, \hitter{\zeta_i} = \emptyset$
+    and in this case, $\delta = \zeta$ is a valid scenario in $s$.
 
@@
       $\muconcr_{s}(P) \neq \emptyset$.
-    Else, by \pref{def:maxCont}, the concretisations of the successors of $P$ require no process of sort $\PHsort(P)$.
+    Else, by \pref{def:maxCont}, the concretisations of the successors of $P$ require no local state of automaton $\PHsort(P)$.
       Furthermore, there exists $\zeta \in \BS(P)$ so that $(P, \aZ) \in \Bee{\Obj}{\Sol}$.
@@
       \begin{itemize}
-        \item[$\circ$] Suppose that $\delta_n$ exists and let $\zeta_n = \PHhit{b_i}{a_j}{a_k}$.
-        By hypothesis there exists $\delta' \in \muconcr_{s \PHplay \delta_n}(\PHobj{\any}{b_i})$ with $\PHsort(P) \notin \PHsort(\delta')$ (by \pref{def:maxCont}).
-        By \pref{lem:update} there exists $\delta'' \in \restriction{\Sce}{1}(s \PHplay \delta')$ so that $\update(s \PHplay \delta') = s \PHplay \delta' \PHplay \delta''$.
-        Furthermore, $\PHget{(s \PHplay \delta' \PHplay \delta'')}{b} = b_j$ (by
-		\pref{lem:hcompcomp} if $b \in \components$ or \pref{lem:hcscomp} if $b \in \cs$).
-        Therefore, $\delta_{n+1} = \delta_n \PHplay \delta' \PHplay \delta'' \PHplay \zeta_n$.
+%        \item[$\circ$] If $\zeta = \emptyseq$, then trivially, $\delta = \emptyseq$.
+        \item[$\circ$] Suppose that $\delta_n$ exists and let $\zeta_n = \PHhit{A}{a_j}{a_k}$.
+        By construction, there exists $A \in \Bv \cap \sSol$
+        amongst the direct successors of $\aZ$.
+        By the first result of this demonstration,
+        there exists a scenario $\delta'$ in $s \play \delta_n$ so that
+        $\forall a_i \in A, \PHget{(s \play \delta_n \PHplay \delta')}{a} = a_i$.
+        Therefore, $\zeta_n$ is playable in $s \play \delta_n \PHplay \delta'$,
+        and $\delta_{n+1} = \delta_n \concat \delta' \concat \zeta_n$.
       \end{itemize}

### 2014-12-23 parts/def-ph.tex
fix titles and refs

@@
 
-\subsection{Modelling cooperation}
+\subsection{Modelling Cooperation}
 \label{ssec:cooperation}
@@
 Process Hitting with classes of priorities~\cite{FPMR13-CS2Bio} can also be encoded as AANs
-with priorities, as defined in \pref{sec:encodings},
+with priorities, as defined in \pref{ssec:flattening},
 by using the same priorities for each action,

### 2014-12-23 parts/example.tex
almost finish transformation (except appendix)
fix titles and refs

@@
 \section{Biological Examples}\label{sec:example}
-
-\todo{À transformer}
 
@@
 
-\subsection{Flattening of a model: Metazoan segmentation}
+\subsection{Under-approximation of a Model with Priorities: Metazoan Segmentation}
 \label{ssec:ex-metazoan}
@@
 
-\subsection{Large-scale Application: T-cell receptor}
+\subsection{Large-scale Application: T-cell Receptor}
 \label{ssec:ex-tcrsig}
@@
 as explained in~\cite{FPMR13-CS2Bio},
-with a construction that is equivalent to the AANs presented in \pref{se:ph}.
+with a construction that is equivalent to the AANs presented in \pref{sec:ph}.
 Therefore, only the method presented in this paper provides a formal proof that

### 2014-12-23 parts/models-ph-dn.tex
finish transformation on the appendix
fix titles and refs

@@
-\subsection{Weak Bisimulation of Asynchronous Discrete Networks}
+\subsection{Asynchronous Discrete Networks}
 \label{sec:dn}
@@
 also called Logical Networks or equivalently René Thomas Models \cite{Thomas95,deJong02},
-into AANs and prove a weak bisimulation relation.
+into AANs with a bisimulation relation.
 This translation is important as it allows to efficiently study the dynamics of ADNs
@@
 Finally,
-\pref{th:bisimDN} states the weak bisimulation relation between an ADN and its encoding in AAN.
-Intuitively, the actions follow strictly the possible transitions of the ADN.
-A detailed proof is given in \pref{suppl:proofbisimADN}. \todo{Utile ?}
+\pref{th:bisimDN} states the bisimulation relation between an ADN and its encoding in AAN.
+Indeed, the actions follow strictly the possible transitions of the ADN,
+making the dynamics strictly equivalent.
 
@@
 \end{theorem}
+
+\begin{proof}
+  By definition of $\toPH$.
+\end{proof}

### 2014-12-23 parts/models-ph-php.tex
fix titles and refs

@@
 
-\begin{definition}[AANs with $k$ classes of priorities]
+\begin{definition}[AAN with $k$ classes of priorities]
 \label{def:php}
@@
 into an AAN with $1$ class of priority $\PH = (\PHs; \PHl; \PHa^{\angles{1}})$
-called \emph{flattening}, which we also prove to be weakly bisimilar.
+called \emph{flattening}, which is bisimilar.
 This AAN with 1 class of priority is equivalent to a regular AAN without priorities;

### 2014-12-23 response.tex
update response to reviewers

@@
 
-\newcommand{\answer}[1]{\textcolor{blue}{#1}}
+\newcommand{\answer}[1]{\textcolor{blue}{#1}\vspace*{1em}}
 
-%\setlength{\parindent}{0pt}
-
-% 
-% \def\V{\mathcal V}
-% \def\O{\mathcal O}
-% 
-% \def\zero{\mathbf 0}
-% \def\R{\mathbb R}
-% \def\Rpos{\R_{\geq 0}}
-% \def\Rspos{\R_{>0}}
-% \def\Q{\mathbb Q}
-% \def\Qpos{\Q_{\geq 0}}
-% \def\Qspos{\Q_{>0}}
-% \def\Z{\mathbb Z}
-% \def\Zpos{\Z_{\geq 0}}
-% \def\Zspos{\Z_{> 0}}
-% 
-% \def\mspan{\mathrm{span}}
-% \def\lp{\mathrm{lowerpoint}}
-% \def\orderings{\mathrm{orderings}}
-% 
-% \def\inner\#1\#2{\#1\#2}
-% %\def\inner\#1\#2{\langle \#1,\#2 \rangle}
-% 
-% \def\apply{\bullet}
-% 
-% \def\B{\mathcal B}
+\title{Response to the reviewers --- First review of “Sufficient Conditions for Reachability in Automata Networks with Priorities”}
+\author{Maxime Folschette, Loïc Paulevé, Morgan Magnin, Olivier Roux}
+\date{}
 
@@
 
-\noindent
-Légende :\\
-\answer{Blabla} $\longleftarrow$ Réponse au reviewer\\
-\answertodo{Blabla} $\longleftarrow$ Réponse possible sur un point encore non appliqué\\
-\todo{Blabla} $\longleftarrow$ À faire / à décider
+\maketitle
 
-\begin{center}
-  --- --- ---
-\end{center}
+% \noindent
+% Légende :\\
+% \answer{Blabla} $\longleftarrow$ Réponse au reviewer\\
+% \answertodo{Blabla} $\longleftarrow$ Réponse possible sur un point encore non appliqué\\
+% \todo{Blabla} $\longleftarrow$ À faire / à décider
 
@@
 
-\todo{Résumer et lister les modifs}
+We wish thank the reviewers for their comments.
+Please find a summary of the main changes brought to the paper here, and a detailed response to all comments below.
 
 \begin{itemize}
-  \item Minor changes in the static analysis to make the graph more precise,
-    and the Sect.~5.1 was revised in consequence;
-  \item New explanations and examples all over the paper,
-    especially regarding the use of priorities (Sect.~2.3),
-    the lemmas (Sect.~2.4 \&~2.5)
-    and the under-approximation (Sect.~3.2);
-  \item A section was added (Sect.~3.5) about the extraction of a scenario from the graph of
-    local causality, in the case the analysis is conclusive;
+  \item We have changed the main model representation from Process Hitting
+    with classes of priorities (PH) to Asynchronous Automata Networks (AANs).
+    This formalism is equivalent but saves a lot of over-complicated formalism,
+    thus gaining in clarity.
+    All sections have been revised in consequence
+    (some became irrelevant and were completely removed)
+    and we added a discussion about the links between PH and AAN.
+  \item We have made minor changes in the static analysis to make the graph more precise,
+    and the Sect.~5.1 was revised in consequence.
+  \item New explanations and examples have been added all over the paper,
+    especially for the under-approximation (Sect.~3.2)
+    and the detailed example (Sect.~5.1).
+  \item A section has been added (Sect.~3.5) about the extraction of a scenario
+    from the graph of local causality, in the case the analysis is conclusive.
 \end{itemize}
@@
 The intent of this paper is to adapt the static analysis methods previously developed in [13] to the case of the PH with priorities, that is, models with a new kind of dynamics and preemptions that did not exist previously.
-The method thus required adaptations that we tried to better motivate in this revision.
-We added a section (Sect.~2.3) to motivate the use of priorities in the PH.
-Furthermore, we added a running example in Sect~2.4 \& 2.5 in order to explain all the definitions and lemmas.
+In this revision, we finally focus on AANs, that are equivalent models,
+but better highlights the difference with the “standard” PH of [13],
+that is, PH without priorities.
+The static analysis method thus required adaptations
+that we tried to better motivate in this revision.
 }
@@
 \answer{
-This translation allows to apply the static analysis to any PH model with priorities, despite the restrictions defined in Sect. 2.4.
-We added some discussion in Sect. 4.2 in order to emphasize this.
+The new AAN representation makes this difference clearer:
+the previously emphasized sub-class of PH models used for the static analysis
+is equivalent to AANs,
+while the whole class of PH models with any number of classes of priorities
+is equivalent to AANs with classes of priorities.
+Thus, the encoding of Sect. 4.2 actually extends the applicability
+of our static analysis; we have added some discussion to emphasize this.
 }
@@
 What improvements are there?
+
+\answer{
+The improvements concern the expressivity of the models tackled.
+The experiments of [13] only conclude on the reachability for dynamics
+that are not exactly those of ADNs (a.k.a.~Logical Networks).
+We have added some discussion to emphasize this.
+}
+
 I also point out that the comparisons with a model-checker should be actually carried out.
@@
 The experiment we carried with the LibDDD model-checker led us to the conclusion that the memory needs for such a method is several orders of magnitude above our method, which we would consider a sufficient result in itself.
-Furthermore, with such a memory use, one cannot expect to be able to study bigger models (say, thousands of components) while our method has a polynomial complexity in the size of the model, and could tackle such bigger models.
+Furthermore, with such a memory use, one cannot expect to be able to study bigger models (say, thousands of components) while our method has a polynomial complexity in the size of the model or the construction of the saturated graph of local causality, and could thus tackle such bigger models.
 Thus, we have not performed more experiments,
@@
 
-\answertodo{
+\answer{
 The translations could indeed be better discussed and justified,
 we have taken this comment into account.
+We also hope that the use of AANs simplifies the formalism
+and emphasizes the use of these translations.
 }
@@
 
-\answertodo{
-We took these comments into account
+\answer{
+We these comments into account.
 }
@@
 
-% Minor language issues:
-% 
+Minor language issues: […]
+
 % (1) In introduction first paragraph at the sixth line there is a typo with 3 full stops ...
@@
 
-\answertodo{
+\answer{
 We took the comments about the language issues of Reviewer \#3 into account.
@@
 \begin{itemize}
+  \item The use of AANs (new to this revision) that simplifies the formalism
+    and gives a new viewpoint to the overall work;
   \item Theorem 2, which refines successive reachability;
-  \item Sect. 4.2, which allows to translate any PH model with priorities
-    into a model that can be processed by our method (thus extending its range of application);
-  \item Sect. 3.5, which returns a scenario concretizing the desired reachability,
-    when possible (this addition is new to this revision).
+  \item Sect. 4.2, which allows to translate any AAN with classes of priorities
+    into a simple AAN (with one class of priority),
+    thus extending the range of application of the static analysis;
+  \item Sect. 3.5 (new to this revision),
+    which returns a scenario concretizing the desired reachability, when possible.
 \end{itemize}
@@
 which was not the case before.
-This has been emphasized in Sect. 5.2.
+This has been emphasized especially in Sect. 5.2.
 }
@@
 
-\todo{Un autre terme devrait être trouvé, je propose : Discrete Networks.}
+\answer{
+We called Asynchronous Discrete Networks (ADN) the class of Logical Models
+with discrete values of the variables,
+either Boolean or multivalued,
+and evolution functions (or, equivalently, focal parameters).
+Although the denomination “ADN” does not exist in the literature,
+there is in fact no widespread or unified term to qualify this class of models.
+We have detailed this choice in the paper and justified the use of this term,
+and emphasized references that also defined these kinds of models.
+}
 
@@
 
-\todo{Peut-être faudrait-il diminuer le nombre de symboles ? Mais lesquels enlever ?}
-
 \answer{
-We have tried to give more explanations and examples
-on most of the technical definitions all throughout the paper.
+The use of AANs instead of PH with classes of priorities
+allows to greatly simplify the whole paper
+and, we hope, increase comprehension.
 }
 
-Comments and suggestions
-
-[…]
+Comments and suggestions […]
 
@@
 
-\answertodo{We have taken these comments into account}
+\answer{We have taken most of these comments into account.}
 

### 2015-01-05 parts/sa.tex
fix titles and refs
ref to detailed example
fix figure of SA example

@@
 
-\subsection{Preliminary definitions}
+\subsection{Preliminary Definitions}
 \label{ssec:sa-def}
@@
   \pref{th:approxinf} concludes that $c_1$ is reachable from $\ctx$.
+  The reader can also refer to \pref{ssec:ex-metazoan}
+  for a detailed conclusive example.
   }%
@@
     \node[Asol,below of=a01] (a01s) {};
-    \node[Aproc,below of=a01s] (b0) {$b_0$};
+    \node[Assol,below of=a01s] (a01ss) {$\{b_0\}$};
+    \node[Aproc,below of=a01ss] (b0) {$b_0$};
     \node[Aobj,below of=b0] (b00) {$\PHobj{b_0}{b_0}$};
@@
     \node[Asol,below of=b01] (b01s) {};
-    \node[Aproc,below of=b01s] (a0) {$a_0$};
+    \node[Assol,below of=b01s] (b01ss) {$\{a_0\}$};
+    \node[Aproc,below of=b01ss] (a0) {$a_0$};
     \node[Aobj,below of=a0] (a00) {$\PHobj{a_0}{a_0}$};
@@
     (a01) edge (a01s)
-    (a01s) edge (b0)
+    (a01s) edge (a01ss)
+    (a01ss) edge (b0)
     (a11) edge (a11s)
@@
     (b01) edge (b01s)
-    (b01s) edge (a0)
+    (b01s) edge (b01ss)
+    (b01ss) edge (a0)
     (b11) edge (b11s)
@@
 
-\subsection{Reachability of a state}
+\subsection{Reachability of a State}
 \label{ssec:simult-ua}
@@
 
-\subsection{Sequential under-approximation}
+\subsection{Sequential Under-approximation}
 \label{ssec:ordered-ua}
@@
 \modMF{
-\subsection{Extraction of the scenario}
+\subsection{Extraction of a Scenario}
 }

### 2015-01-05 parts/intro.tex
add references in first paragraph

@@
 
-Discrete modelling frameworks for biological networks is an active research field where formal methods have proven that they were very powerful.
-Such a work started in the seventies.
+Discrete modelling frameworks for biological networks is an active research field where formal methods have proven that they were very
+powerful~\cite{thomas1990biological,deJong02,snoussi_logical_1993}.
+Such a work started in the seventies, with~\cite{kauffman69,Thomas73}.
 It was later enriched in many directions and widely used to elucidate many biological questions.
@@
 The ultimate goal is to discover how it could be possible to prevent biological systems from reaching some pathological conditions.
-\todo{Ajouter des références}
 

### 2015-01-05 parts/def-ph.tex
fixes after comments from Morgan

--- 2014-12-22 parts/def-ph.tex
@@
     that cannot be active simultaneously, and that degrade over time.
-    Furthermore, these two components can cooperate to activate $c$
+    Moreover, these two components can cooperate to activate $c$
     if their “active” states ($a_1$ and $b_1$)
@@
 
-\subsection{Modelling cooperation}
+\subsection{Comparison with the Process Hitting and Modelling of Cooperations}
 \label{ssec:cooperation}
 
-Cooperations between components are a very common in biological systems.
-They represent the fact that a given regulation is not conditioned by only one condition,
+The AAN formalism can be seen as an extension of the Process Hitting framework
+previously introduced in~\cite{PMR10-TCSB}.
+Indeed, the representation of Process Hitting models is also based on automata
+(called “sorts”), local states (called “processes”) and actions.
+The particularity of Process Hitting lies in the following restriction:
+each action can have at most one hitter;
+in other words, a Process Hitting model is an AAN so that
+$\forall h \in \PHh, 0 \leq \card{\hitter{h}} \leq 1$.
+Conversely, any Process Hitting model can obviously be encoded into an AAN.
+% In \pref{ssec:flattening}, we also show that Process Hitting models with
+% classes of priorities~\cite{FPMR13-CS2Bio}
+% can also be encoded into AANs.
+
+The difference between AAN and Process Hitting especially appears when one
+needs to represent cooperations between components.
+%are a very common in biological systems.
+A cooperations represents the fact that
+a given regulation is not conditioned by only one condition,
 such as the presence of a given concentration of one substance,
 represented in the model by the activity of the one related local state.
-Instead, in the case of a cooperation, two conditions or have to be bet.
+Instead, in the case of a cooperation, two conditions or more have to be bet.
 For example, in the example of \pref{fig:ph-livelock},
 the activation of component $c$ requires the cooperation of $a$ and $b$;
-in practice, this is expressed by a set of two hitters for action
+in practice, this is naturally expressed by a set of two hitters for action
 $\PHfrappes{a_1, b_1}{c_0}{c_1}$.
 
-Such a cooperation can be represented in Process Hitting by using a \emph{cooperative sort},
-whose aim is to represent a Boolean formula~\cite{PMR10-TCSB}.
+Such a cooperation can also be represented in Process Hitting
+by using a “cooperative sort”~\cite{PMR10-TCSB},
+which is an additional automata
+whose aim is to represent a Boolean formula.
 The different local states of a cooperative sort represent the possible configurations
 of a set of automata,
-and actions allow to update the active local state of the cooperative sort
+and actions allow to “update” the active local state of the cooperative sort
 in order to have it match the configuration of these automata.
@@
 Cooperative sorts have the advantage to not require any supplementary semantics
-than those of standard Process Hitting,
+than those of standard Process Hitting
+(that is, not more that one hitter per action),
 but at the cost of slightly over-approximating the expected dynamics of a true Boolean gate.
-Indeed, nothing forces these actions to be played as soon as possible,
+Indeed, nothing forces the updating actions to be played as soon as possible,
 thus resulting in a possible temporal shift between the evolution
 of the active process of the cooperative sorts and those of the automata it represents.
-In other words, a cooperative sorts does not necessarily represent the configuration
-of a given set of automata, but only a combination of past states.
+In other words, a cooperative sorts does not necessarily represent the current configuration
+of a given set of automata, but only a combination of their past states.
+AAN thus fixes this temporal shift by removing the need for cooperative sorts,
+but at the cost of changing the semantics of the formalism.
 
@@
 by prioritizing the actions used to update the cooperative sorts.
-The AAN formalism proposed in this paper have in fact the same expressivity than
+The AAN formalism proposed in this paper has in fact the same expressivity than
 Process Hitting with classes of priorities.
@@
 as detailed in \pref{ssec:flattening}.
-
-We note that obviously, Process Hitting~\cite{PMR10-TCSB} being a restriction of AANs,
-one can easily encode any Process Hitting model as an AAN by using only actions
-$\PHfrappe{A}{b_j}{b_k}$ so that $0 \leq \card{A} \leq 1$.
-Process Hitting with classes of priorities~\cite{FPMR13-CS2Bio} can also be encoded as AANs
-with priorities, as defined in \pref{sec:encodings},
-by using the same priorities for each action,
-and possibly translate them into simple AANs.
+% 
+% We note that obviously, Process Hitting~\cite{PMR10-TCSB} being a restriction of AANs,
+% one can easily encode any Process Hitting model as an AAN by using only actions
+% $\PHfrappe{A}{b_j}{b_k}$ so that $0 \leq \card{A} \leq 1$.
+% Process Hitting with classes of priorities~\cite{FPMR13-CS2Bio} can also be encoded as AANs
+% with priorities, as defined in \pref{ssec:flattening},
+% by using the same priorities for each action,
+% and possibly translate them into simple AANs.

### 2015-01-05 parts/intro.tex
fixes after comments from Morgan

@@
 by defining several requisites for a reaction.
-Furthermore, such automata networks are still compatible with the notion of priority,
+Moreover, such automata networks are still compatible with the notion of priority,
 that can also be used to model different reaction rates in the model.
@@
 Although in~\cite{FPMR13-CS2Bio} this was achieved with a particular class of high priority,
-the work presented in this paper, however, focuses on Asynchronous Automata Networks.
+the work presented in this paper focuses instead on Asynchronous Automata Networks.
 The simple version of this formalism (without classes of priorities)
 is defined in \pref{sec:ph}
-and consists of an extension of Process Hitting with classes of priorities
-that allows to simplify the formalisation with the same benefits.
+and is equivalent to an extension of Process Hitting with classes of priorities,
+but allows to simplify the formalisation with the same benefits.
 In \pref{sec:sa},
@@
 
-Furthermore,
+Moreover,
 we define in \pref{sec:encodings} the notion of Asynchronous Automata Networks
@@
 If $A$ and $B$ are sets,
-$f : A \rightarrow B$ denotes an application $f$ that maps the elements of $A$ to elements of $B$.
-Furthermore, if $f$ is a monotonically increasing and bounded function, then
+$f : A \rightarrow B$ denotes a function $f$ that maps the elements of $A$ to elements of $B$.
+If $f$ is a monotonically increasing and bounded function, then
 $\lfp{x_0}{x}{x'}$ is the least fixed point of the function $x \mapsto x'$ which is greater than $x_0$.

### 2015-01-05 parts/models-ph-php.tex
fixes after comments from Morgan

@@
 Indeed, if a local state is not active in a state, this means that another local state of the same automaton is active.
-Furthermore, we note that:
+Moreover, we note that:
 \[\forall a \in \ov{\PHs}, \forall a_i, a_j \in \ov{\PHl}_a,
@@
 as an AAN (or, equivalently, as an AAN$1$).
-this translation thus extends the applicability of the static analysis developed in
+This translation thus extends the applicability of the static analysis developed in
 \pref{sec:sa} to any AAN$k$, with $k \in \sN^*$.
+Moreover, it allows to represent
+any Process Hitting model with classes of priorities~\cite{FPMR13-CS2Bio}
+under the form of an AAN
+(or, equivalently, of a Process Hitting model with $2$ classes of priorities).
 The translation given in this section

### 2015-01-09 underapprox-tcrsig94/run-egfr104-full.sh
add egfr104 test file + tests generator

@@ -1,0 +1,53 @@
+#!/usr/bin/env bash
+
+# sh run-generator.sh egfr104 'erbb1 erbb2 erbb3 erbb4 ar bir btc egf epr hbegf nrg1a nrg1b nrg2a nrg2b nrg3 nrg4 tgfa' 'elk1 creb ap1 hsp27 actin_reorg cmyc pro_apoptotic p70s6_2 pkc stat1 stat3 stat5'
+
+ph="egfr104.ph"
+outputs="elk1 creb ap1 hsp27 actin_reorg cmyc pro_apoptotic p70s6_2 pkc stat1 stat3 stat5"
+mode=${1}
+
+ulimit -t 4
+
+for erbb1 in 0 1; do
+for erbb2 in 0 1; do
+for erbb3 in 0 1; do
+for erbb4 in 0 1; do
+for ar in 0 1; do
+for bir in 0 1; do
+for btc in 0 1; do
+for egf in 0 1; do
+for epr in 0 1; do
+for hbegf in 0 1; do
+for nrg1a in 0 1; do
+for nrg1b in 0 1; do
+for nrg2a in 0 1; do
+for nrg2b in 0 1; do
+for nrg3 in 0 1; do
+for nrg4 in 0 1; do
+for tgfa in 0 1; do
+
+init="erbb1 $erbb1, erbb2 $erbb2, erbb3 $erbb3, erbb4 $erbb4, ar $ar, bir $bir, btc $btc, egf $egf, epr $epr, hbegf $hbegf, nrg1a $nrg1a, nrg1b $nrg1b, nrg2a $nrg2a, nrg2b $nrg2b, nrg3 $nrg3, nrg4 $nrg4, tgfa $tgfa"
+echo "--- $init"
+for z in $outputs; do
+  echo "# $z 1"
+  ./unitrun.sh $mode "x" --no-debug --initial-state "$init" -i $ph $z 1
+  [ $? -eq 137 ] && echo '*** Killed ***';
+done
+
+done
+done
+done
+done
+done
+done
+done
+done
+done
+done
+done
+done
+done
+done
+done
+done
+done

### 2015-01-09 underapprox-tcrsig94/run-generator.sh

@@ -1,0 +1,70 @@
+#!/usr/bin/env bash
+
+# Generator of .sh scripts for multiple reachability tests.
+# 
+# Usage:
+#   sh run-generator.sh <filename> <inputs> <outputs>
+# where <filename> is the name of the .ph file (without extension)
+# and determines the name of the file created: run-<filename>.sh,
+# and <input> and <output> are strings containing the input and output
+# sort names separated by spaces.
+# 
+# Example:
+#   sh run-generator.sh egfr104 'erbb1 erbb2 erbb3' 'elk1 creb ap1'
+# creates a file named run-egfr104.sh that checks the reachability
+# of process 1 of each output for all initial configuration fo the inputs.
+# This file can be executed with:
+#   sh run-egfr104.sh ph
+# Separating program outputs and debug outputs can be achieved with:
+#   (sh run-egfr104.sh ph) 1> run-egfr104.out 2> run-egfr104.debug.out
+
+
+
+model="$1.ph"
+runfile="run-$1.sh"
+inputs=$2
+outputs=$3
+
+
+
+# Header
+echo '#!/usr/bin/env bash' > $runfile
+echo '' >> $runfile
+echo "# File: $model" >> $runfile
+echo "# Inputs: $inputs" >> $runfile
+echo "# Outputs: $outputs" >> $runfile
+echo '' >> $runfile
+echo "ph=\"${model}\"" >> $runfile
+echo "outputs=\"${outputs}\"" >> $runfile
+echo 'mode=${1}' >> $runfile
+echo '' >> $runfile
+
+# For loops
+for curinput in $inputs; do
+  echo "for $curinput in 0 1; do" >> $runfile
+done
+lastinput=$curinput
+echo '' >> $runfile
+
+# Initial state
+echo -n "init=\"" >> $runfile
+for curinput in $inputs; do
+  echo -n "$curinput \$$curinput" >> $runfile
+  [ $curinput != $lastinput ] && (echo -n ", " >> $runfile);
+done
+echo "\"" >> $runfile
+
+# Loop body
+
+echo "echo \"--- \$init\"" >> $runfile
+echo "for z in \$outputs; do" >> $runfile
+echo "  echo \"# \$z 1\"" >> $runfile
+echo "  ./unitrun.sh \$mode \"x\" --no-debug --initial-state \"\$init\" -i \$ph \$z 1" >> $runfile
+echo "done" >> $runfile
+echo '' >> $runfile
+
[…]

### 2015-01-12 main.tex
remove colors
new abstract

@@
 % \def\modOR#1{\textcolor{olive}{#1}}
-%\def\modMF#1{#1} \def\moda#1{#1} \def\modLP#1{#1} \def\modMM#1{#1} \def\modOR#1{#1}
+\def\modMF#1{#1} \def\moda#1{#1} \def\modLP#1{#1} \def\modMM#1{#1} \def\modOR#1{#1}
 
@@
 \begin{abstract}
-The Process Hitting is a recently introduced framework
-designed for the modelling and analysis of concurrent systems.
-The particular form of its actions (encoding the dynamics into the models)
-allowed to define very efficient static analysis
-based on local causality to compute reachability properties.
-However, this modelling shows its limits when preemption features are needed,
-and especially for cooperations
-(that is, the regulation of two components that jointly interact with a third one).
-
-In this paper, we focus on
-the Asynchronous Automata Network (AAN) formalism,
-which is an extension of the Process Hitting with an increased expressivity.
-Like the Process Hitting,
-the originality of AANs is the restrictions of the actions
-that have an effect limited to exactly one component;
-but unlike Process Hitting, their causality is not restricted to at most one other component.
-
-We then develop a new refinement for the under-approximation of the static analysis
-to efficiently compute results on the dynamics of AANs.
-Because of the expressivity improvements,
-this analysis gives more accurate results
-than the previous works carried on the Process Hitting.
-Furthermore, its complexity is still polynomial in the size of the model
+In this paper,
+we develop a new refinement for an efficient under-approximation of the dynamics of
+Asynchronous Automata Networks (AANs).
+An AAN is an Automata Network with synchronous transitions between automata,
+where each transition change the local state of exactly one automaton
+(but any number of synchronizing local states are allowed).
+The work we propose here
+is based on static analysis by abstract interpretation,
+which allows to prove that reaching a state with a given property
+is possible,
+without the same computational cost of usual model checkers.
+Furthermore, its complexity is polynomial in the size of the model
 and exponential in the number of possible “branchings” during the solving.
 
-We also extend the applicability of this static analysis to
-AANs with classes of priorities and to
-Asynchronous Discrete Networks, either Boolean or multivalued,
-which allows to efficiently study the dynamics of these widespread models
-% efficiently under-approximate reachability properties
-% in these widespread models.
-We illustrate this on the model-checking of a signalling network of 94
-components, which is unprecedented.
+The under-approximation method presented in this paper is inspired
+from the one developed specifically for the Process Hitting,
+which is a sub-class of AANs.
+Furthermore, we also introduce the notion of AANs with classes of priorities,
+and show that they have the same expressivity as AANs without priorities,
+thus extending the range of our under-approximation.
+Finally, we illustrate our method on the model-checking of a signalling network
+of 94 components, which is unprecedented.
 \end{abstract}

### 2015-01-12 parts/intro.tex
revised introduction

@@
 the extra reactions can for example be given “infinite speed” (highest priority) so that they do not affect the behaviour of “normal” (lower priority) reactions, including the multimolecular ones.
-Another approach consists in considering another class of models,
+
+\modn{
+The approach used in this paper, however,
+consists in considering another class of models,
 that we call Asynchronous Automata Network,
@@
 that can also be used to model different reaction rates in the model.
+Asynchronous Automata Networks
+(and, a fortiori, their restriction, the Process Hitting framework)
+can be considered as a subset of Communicating Finite State Machines
+or safe Petri Nets.
+%or Synchronous Automata Networks,
+%is inspired from the $\pi$-calculus,
+Our work is thus related to such semantic ramifications
+of extending traditional process algebras with the concept of priority
+that allows for some transitions to be given precedence over others.
+We focus here on static priorities that allow to model
+time constraints such as reaction rates or delays between regulations,
+but can also model preemptions between evolutions branches.
+}
 
@@
 \subsection*{Contributions}
-Since our formalisms (the Asynchronous Automata Network and the Process Hitting)
-can be considered as a subset of Calculus of Communicating Systems,
-or Synchronous Automata Networks,
+\modn{
+This paper is an extension of~\cite{FPMR13-CS2Bio}.
+Its main contribution consists in the development of a method
+that allows to efficiently compute under-approximations of the dynamics
+of Asynchronous Automata Networks (AANs),
+based on a similar work carried out on Process Hitting~\cite{PMR12-MSCS}.
+Rather than using brute force or symbolic model checking techniques,
+our method focuses on static analysis by abstract interpretation.
+Our work aims at checking reachability properties that,
+for a given initial state $\ctx$ and a given local state $x$,
+have the form:
+“Starting from state $\ctx$, is it possible to reach
+a state in which $x$ is active?”,
+thus answering either “True”
+(in which case the reachability is formally proven)
+or “Inconclusive”
+(which however does not stand for “False”, that can be proven by other analysis tools,
+such as the over-approximation proposed in~\cite{PMR12-MSCS}).
+Moreover, the successive or simultaneous reachability of several local states
+can also be checked,
+and in the case of a “True” response,
+an execution path satisfying the property can be produced.
+Our work thus allows to efficiently analyse the dynamics
+of regulation networks,
+especially the widespread Logical Networks \cite{Thomas95,deJong02},
+which encompass variables with a limited number of discrete values
+alongside with evolution functions or focal parameters.
+To show the scalability of our method, we apply it to a
+large-scale biological model containing 94 components;
+the under-approximation turns out to be conclusive in
+all cases and results have been computed in hundredths of seconds,
+thus overtaking the efficiency of usual model-checkers.
+}
+
+\modn{
+AANs (and, a fortiori, their restriction, the Process Hitting)
+can be considered as a subset of Communicating Finite State Machines
+or safe Petri Nets.
+%or Synchronous Automata Networks,
 %is inspired from the $\pi$-calculus,
-our work is related to such semantic ramifications of extending traditional process algebras with the concept of priority that allows for some transitions to be given precedence over others.
-The concept is derived in two directions: dynamic versus static, the difference being naturally that the former one refers to a semantics where priority values may change during execution according to some evolution rules.
-In our work, actions exhibit a static priority structure.
-The actions modelling biological processes are divided in several classes of priorities which stand for the different reaction rates or relative preemptions.
-Furthermore, the multiple causality of the actions in Asynchronous Automata Networks
-allow to abstract a highest class of priority that would be used
-to model particular nonbiological actions
-that encode Boolean functions inside the model.
+Our work is thus related to such semantic ramifications
+of extending traditional process algebras with the concept of priority
+that allows for some transitions to be given precedence over others.
+We focus here on static priorities that allow to model
+time constraints such as reaction rates or delays between regulations,
+but can also model preemptions between evolutions branches.
+Thus, although the under-approximation method presented in this paper
+is initially developed on AANs without classes of priorities,
+we show that adding classes of priorities into AANs
+does not increase their expressivity.
+Thus, we exhibit an encoding that allows to extend the range
+of application of our method to AANs with classes of priorities.
+}
 
-This paper is an extension of~\cite{FPMR13-CS2Bio} where we
-introduced a new extension to the semantics of Process Hitting
-by partitioning actions into classes of priorities.
-One of our objectives was to reach an accurate representation of cooperating components in the model, that was not fulfilled with the initial semantics.
-Although in~\cite{FPMR13-CS2Bio} this was achieved with a particular class of high priority,
-the work presented in this paper focuses instead on Asynchronous Automata Networks.
-The simple version of this formalism (without classes of priorities)
-is defined in \pref{sec:ph}
-and is equivalent to an extension of Process Hitting with classes of priorities,
-but allows to simplify the formalisation with the same benefits.
+\modn{
+\pref{sec:ph} presents the Asynchronous Automata Networks (AANs)
+without any notion of classes of priorities.
 In \pref{sec:sa},
-we develop an efficient under-approximation of the reachability
-of several local states of components,
-thus allowing to compute efficient static analysis of the dynamics.
-This local reachability under-approximation can be also easily extended to study the reachability of a global or partial state.
-Furthermore, we provide a new extended under-approximation method to refine this method
-in the case of a successive reachability property.
+we develop our under-approximation method allowing to efficiently
+compute reachability analysis;
+we also show how to extract a valid execution path if the response is positive,
+and propose two refinements in case one needs to check
+successive or simultaneous reachability properties.
+The framework of AANs with classes of priorities is given in \pref{sec:encodings},
+alongside with an encoding into AANs without classes of priorities
+(or, equivalently, with one class of priority).
+Finally, \pref{sec:example} provides a detailed example and a large-scale example
+of the application of our method,
+and \pref{sec:ccl} gives a conclusion and a discussion about our work.
+}
 
-Moreover,
-we define in \pref{sec:encodings} the notion of Asynchronous Automata Networks
-with classes of priorities,
-that consists of a convenient way to introduce time parameters
-into the models, under the form of preemptions.
-We also provide in \pref{sec:encodings} a “flattening”
-of any Asynchronous Automata Networks with classes of priorities
-into a model without classes of priorities,
-thus extending the range of applicability of the static analysis.
-We also give in the same section a formal encoding of Asynchronous Discrete Networks,
-that is, the multivalued version of Asynchronous Boolean Networks.
-These models,
-which encompass variables and evolution functions with a limited number of discrete values,
-are also called “Logical Networks” in~\cite{Thomas95,deJong02}.
-This encoding thus allows to efficiently study this kind of widespread models.
-
-In \pref{sec:example}, we give two examples of the use of our method.
-The first consists of a detailed application of the analysis of a biological network expressed as
-an ANN with 2 classes of priorities,
-which requires to be encoded into a simple ANN (without priorities).
-The second consists of applying our method
-on a large-scale biological model containing 94 components;
-the under-approximation turned out to be conclusive in all cases and results were computed in hundredths of seconds,
-thus overtaking the efficiency of usual model-checkers.
-
-\modMF{
-The main addition in this paper compared to~\cite{FPMR13-CS2Bio} is
-the representation under the form of ANNs, that allow to simplify the formalisation.
-Furthermore, we give new tools to improve the applicability of our method:
-\pref{th:bisimPHP} states that any ANN with any number of classes of priorities
-can be represented into a simple ANN (or, equivalently, with only one class of priority),
-thus extending the scope of our method to any possible Process Hitting model;
-\pref{thm:ordered-ua} gives a method to refine successive reachability,
-and obtain more conclusive results in the case of several successive objectives;
-\pref{def:concret} allows to extract a concrete scenario when our static analysis method
-is conclusive.
+\modn{
+The main additions in this paper compared to~\cite{FPMR13-CS2Bio} are
+\pref{ssec:concret} that allows the extraction of a concrete trace of execution
+when our static analysis method is conclusive,
+\pref{ssec:ordered-ua} that refines our approach in the case
+of a successive reachability in order to increase the conclusiveness,
+and \pref{ssec:flattening} which states that any ANN
+with any number of classes of priorities
+can be represented into a simple ANN
+(or, equivalently, with only one class of priority),
+thus extending the scope of our method.
+We note however that the use of AANs without priorities alone
+instead of Process Hitting models
+allows to simplify the notations, but does not increase
+the range of applicability of the results.
 }

### 2015-01-12 parts/def-ph.tex
revised section 2

--- 2014-12-22 parts/def-ph.tex
@@
 We give in this section the definition and the semantics of the Asynchronous Automata Networks (AAN).
-It is a restriction of the classical Synchronous Automata Networks
+It is a restriction of the classical (synchronous) Automata Networks
 where each set of transitions sharing the same label
@@
 
-An AAN (\pref{def:ph}) gathers a finite number of concurrent \emph{local states} divided into a finite set of \emph{automata}, also called \emph{components}.
-A local state belongs to a unique automaton and is noted $a_i$ where $a$ is the name of the automaton and $i$ the identifier of the local state within automaton $a$.
-Each local state stands for a kind of “activity level” of its automaton; a \emph{global state} of the AAN thus corresponds to a set of local states containing exactly one local state of each automaton.
+\modn{
+We consider an AAN (\pref{def:ph})
+which gathers a finite number of \emph{automata},
+each one containing a finite number of \emph{local states}.
+A local state is noted $a_i$ where $a$ is the name of the automaton it belongs to,
+and $i$ is the identifier of this local state within automaton $a$.
+A \emph{global state} of the system is the gathering
+of exactly one local state from each automata.
+}
 
+\modn{
 The concurrent interactions between local states are defined by a set of \emph{actions}.
-Actions describe the replacement of the active local state of an automaton by another of the same automaton, conditioned by the presence of as many other local states in the model.
-An action is denoted by $\PHhit{A}{b_j}{b_k}$ where $b_j$ and $b_k$ are local states of an automata $b$, and $A$ is a set of local states.
-It is required that $b_j \neq b_k$ and that
+An action stands for a set of transitions sharing the same label,
+so that playing them changes exactly one local state.
+Therefore, an action is denoted by $\PHhit{A}{b_j}{b_k}$
+where $A$ is a set of local states
+and $b_j$ and $b_k$ are local states of a same automaton $b$,
+and it is required that $b_j \neq b_k$ and that
 $A$ does not contain a local state of $b$ or two local states of the same automaton.
-An action $h=\PHfrappe{A}{b_j}{b_k}$ is read as ``$A$ \emph{hit} $b_j$ to make it bounce to $b_k$'', and $A$, $b_j$, $b_k$ are called respectively the set of \emph{hitters}, the \emph{target} and the \emph{bounce} of the action, and can be referred to as $\PHhitter(h), \PHtarget(h), \PHbounce(h)$, respectively.
+An action $h=\PHfrappe{A}{b_j}{b_k}$ is read as
+``$A$ \emph{hit} $b_j$ to make it bounce to $b_k$'',
+and $A$, $b_j$, $b_k$ are called respectively the set of
+\emph{hitters}, the \emph{target} and the \emph{bounce} of the action,
+and can be referred to as $\PHhitter(h), \PHtarget(h), \PHbounce(h)$, respectively.
+}
 
@@
 \label{def:ph}
-  An \emph{Asynchronous Automata Networks} is a triplet $\PH = (\PHs; \PHl; \PHa)$,
+  An \emph{Asynchronous Automata Network} (AAN) is a triplet $\PH = (\PHs; \PHl; \PHa)$,
   where:
@@
 is defined in \pref{def:statecap} as the same state in which the local state of automaton $a$ has been replaced by $a_i$;
-this is used to define the dynamics of an AAN in \pref{def:play}.
+this is used to define the semantics of an AAN in \pref{def:play}.
 %
@@
 
-\begin{definition}[Dynamics of an AAN ($\PHPtrans$)]
+\begin{definition}[Semantics of an AAN ($\PHPtrans$)]
 \label{def:play}
@@
 
-\subsection{Modelling cooperation}
-\label{ssec:cooperation}
-
-Cooperations between components are a very common in biological systems.
-They represent the fact that a given regulation is not conditioned by only one condition,
-such as the presence of a given concentration of one substance,
-represented in the model by the activity of the one related local state.
-Instead, in the case of a cooperation, two conditions or have to be bet.
-For example, in the example of \pref{fig:ph-livelock},
-the activation of component $c$ requires the cooperation of $a$ and $b$;
-in practice, this is expressed by a set of two hitters for action
-$\PHfrappes{a_1, b_1}{c_0}{c_1}$.
-
-Such a cooperation can be represented in Process Hitting by using a \emph{cooperative sort},
-whose aim is to represent a Boolean formula~\cite{PMR10-TCSB}.
-The different local states of a cooperative sort represent the possible configurations
-of a set of automata,
-and actions allow to update the active local state of the cooperative sort
-in order to have it match the configuration of these automata.
-Then, one or several actions can be added from the desired local states of the cooperative sort
-in order to abstract multiple requirements.
-Cooperative sorts have the advantage to not require any supplementary semantics
-than those of standard Process Hitting,
-but at the cost of slightly over-approximating the expected dynamics of a true Boolean gate.
-Indeed, nothing forces these actions to be played as soon as possible,
-thus resulting in a possible temporal shift between the evolution
-of the active process of the cooperative sorts and those of the automata it represents.
-In other words, a cooperative sorts does not necessarily represent the configuration
-of a given set of automata, but only a combination of past states.
-
-In~\cite{FPMR13-CS2Bio}, the formalization of classes of priorities into the Process Hitting
-was proposed in order to add some missing features,
-such as the possibility to abstract time properties of regulation or reaction rates.
-Another consequence of the addition of priorities was the possibility to fix
-the aforementioned temporal shift, and thus be able to model accurate Boolean gates,
-by prioritizing the actions used to update the cooperative sorts.
-The AAN formalism proposed in this paper have in fact the same expressivity than
-Process Hitting with classes of priorities.
-Indeed, the actions with multiple hitters play the role of cooperative sorts,
-and the classes of priorities can be encoded into AAN without priorities,
-as detailed in \pref{ssec:flattening}.
-
-We note that obviously, Process Hitting~\cite{PMR10-TCSB} being a restriction of AANs,
-one can easily encode any Process Hitting model as an AAN by using only actions
-$\PHfrappe{A}{b_j}{b_k}$ so that $0 \leq \card{A} \leq 1$.
-Process Hitting with classes of priorities~\cite{FPMR13-CS2Bio} can also be encoded as AANs
-with priorities, as defined in \pref{sec:encodings},
-by using the same priorities for each action,
-and possibly translate them into simple AANs.
+\modn{
+\begin{remark}[Comparison with the Process Hitting]
+  The Process Hitting framework
+  previously introduced in~\cite{PMR10-TCSB}
+  is a restriction of the AAN formalism;
+  indeed, a Process Hitting model is an AAN so that
+  $\forall h \in \PHh, 0 \leq \card{\hitter{h}} \leq 1$.
+  However, the AANs defined in this paper have the same expressivity than
+  the Process Hitting with classes of priorities, as previously
+  introduced in~\cite{FPMR13-CS2Bio}.
+  Indeed, in the Process Hitting with at least classes of priorities
+  it is possible to use additional sorts, called “cooperative sorts”,
+  in order to model the actions of any AAN that have more than one hitter.
+\end{remark}
+}

### 2015-01-12 parts/example.tex
fix figure
revised section 2

@@
     (c11) edge (c11s)
+    (c11s) edge (nc11s)
 
@@
 
-\modMF{
+\modn{
 Finally, we note that similar experiments were conducted in~\cite{PMR12-MSCS}.
@@
 checked in the example above.
-The semantics of Process Hitting does not allow to model accurate Boolean gates,
-as explained in \pref{ssec:cooperation},
+Indeed, the semantics of Process Hitting (without classes of priorities)
+do not allow to model accurate Boolean gates,
 thus leading to some unwanted behaviours that take the form of temporal shifts.
@@
 the observed behaviours are the result of the true dynamics of the system,
-which was originally described in a format equivalent to synchronous Discrete Networks.
+which was originally described in a format equivalent to Logical Networks.
 }

### 2015-01-12 parts/sa.tex
revised introduction
revised section 2

@@
 
-  \moda{%
+  \modn{%
   This result is new compared to the method proposed in~\cite{PMR12-MSCS}.
@@
   in this paper only allowed to represent “over-approximated” Boolean gates
-  with the use of cooperative sorts,
-  as explained in \pref{ssec:cooperation}.
+  with the use of cooperative sorts.
   This especially did not allow to model the fact that $a_1$ and $b_1$ could not
   be activated in the same state, but only in successive states.
-  Thus, $c_1$ was indeed reachable,
+  Thus, when using Process Hitting, $c_1$ was indeed reachable,
   contrary to the behaviour expected from an accurate Boolean gate.
@@
 \subsection{Extraction of a Scenario}
+\label{ssec:concret}
 }

### 2015-01-12 parts/def-ph.tex
revised end of section 5

@@
 
-We give in this section the definition and the semantics of the Asynchronous Automata Networks (AAN).
+We give in this section the definition and the semantics of the Asynchronous Automata Networks (AANs).
 It is a restriction of the classical (synchronous) Automata Networks
@@
 (with or without classes of priorities).
-In \pref{sec:encodings}, we will also introduce classes of priorities into these models,
-and show that they are equivalent to Asynchronous Discrete Networks.
+Another definition of AANs introducing classes of priorities
+is proposed in \pref{sec:encodings},
+and we show that they have the same expressivity as AANs.
 
-\subsection{Definition of Asynchronous Automata Networks}
-\label{ssec:PH}
+\medskip
 

### 2015-01-12 parts/example.tex
revised end of section 5

@@
 and 1GB of RAM.
-\modMF{
 Computations times were in the order of a few hundredths to tenths of a second
 in each case (reachability of $\reach_1$ included).
-}
 To give a comparison, we did the same experiments with a standard symbolic model-checker, libDDD
@@
 as a Petri net.
-However, due to the large scale of the model, the program runs out of memory for all the experiments.
+However, due to the large scale of the model, the program runs out of memory for all the experiments,
+\modn{%
+showing that this method is not scalable.
+Because standard model checkers are often PSPACE-complete~\cite{Harel02},
+using them to study the dynamics of a model is strongly limited to its size.
+On the other hand,
+our method is able to conclude with limited memory and computation time usage.
+Indeed, the under-approximation developed in this paper comes in two versions:
+\begin{itemize}
+  \item One version is polynomial in the size of the model,
+    and consists in building the saturated graph of local causality once
+    and checking \pref{th:approxinf} on this graph only.
+    This version is scalable by nature by its low complexity;
+  \item The other one is exponential in the size of the model,
+    and consists in checking \pref{th:approxinf}
+    on every sub-graph obtained by considering sub-sets of the nodes in $\Sol$
+    of the saturated graph of local causality.
+    Although not as scalable, it is still efficient on this example,
+    due to an adapted enumeration of these sub-sets.%
+\end{itemize}
+It is therefore expected that our work will be scalable to models that are larger,
+even by orders of magnitude.
+}%
+%---~that is, containing thousands of components.
+
 \modMF{
-This limitation shows that studying the dynamics of models is strongly limited to the size of the model for standards model checkers,
-while our method is able to conclude with limited memory and computation time usage.
-Furthermore, given that the complexity of the static analysis presented in this paper
-is polynomial in the size of the models,
-it is expected that our work will be scalable to models that are larger,
-even by orders of magnitude.
-%---~that is, containing thousands of components.
-}
-
-\modn{
 Finally, we note that similar experiments were conducted in~\cite{PMR12-MSCS}.

### 2015-01-13 parts/def-ph.tex
remove section 4.1 (ADN to AAN)

@@
 Another definition of AANs introducing classes of priorities
-is proposed in \pref{sec:encodings},
-and we show that they have the same expressivity as AANs.
+is proposed in \pref{sec:flattening},
+where we also show that they have the same expressivity as AANs.
 

### 2015-01-13 parts/example.tex
remove section 4.1 (ADN to AAN)

@@
 and demonstrate how the classes of priorities help in the modelling process,
-and how the flattening of \pref{ssec:flattening}
+and how the flattening of \pref{sec:flattening}
 can be used in such a case.
@@
 \pref{ssec:ua}.
-For this, we first have to use the flattening method presented in \pref{ssec:flattening}
+For this, we first have to use the flattening method presented in \pref{sec:flattening}
 because the considered model contains 2 classes of priorities.
@@
 a Process Hitting model with two classes of priorities,
-and a dynamics equivalent to an AAN%
+whose dynamics is equivalent to an AAN%
 \footnote{Files are available at
-\url{http://maxime.folschette.name/underapprox-tcrsig94.zip}.}
-\modMF{
-by using a translation equivalent to the one given in \pref{sec:dn}.
-}
+\url{http://maxime.folschette.name/underapprox-tcrsig94.zip}.}.
+\modn{%
+Logical Networks being a subclass of AANs, this translation is straightforward.
+}%
 Then, we verified the reachability for the independent activation of 4 outputs of the signalling

### 2015-01-13 parts/intro.tex
remove section 4.1 (ADN to AAN)

@@
 successive or simultaneous reachability properties.
-The framework of AANs with classes of priorities is given in \pref{sec:encodings},
+The framework of AANs with classes of priorities is given in \pref{sec:flattening},
 alongside with an encoding into AANs without classes of priorities
@@
 of a successive reachability in order to increase the conclusiveness,
-and \pref{ssec:flattening} which states that any ANN
+and \pref{sec:flattening} which states that any ANN
 with any number of classes of priorities

### 2015-01-14 parts/example.tex
fix GLC (re-add objective processes)

@@
     % STEP 1
-    \node[Aobj] (a01) {$\PHobj{a_0}{a_1}$};
+    \node[Aproc] (a1) {$a_1$};
+    \node[Aobj,below of=a1] (a01) {$\PHobj{a_0}{a_1}$};
     \node[Asol,below of=a01] (a01s) {};
@@
     \path
+    (a1) edge (a01)
     (a01) edge (a01s)
@@
     % STEP 2
-    \node[Aobj,right of=a01,node distance=3.5cm] (a10) {$\PHobj{a_1}{a_0}$};
+    \node[Aproc,right of=a1,node distance=3.5cm] (a0) {$a_0$};
+    \node[Aobj,below of=a0] (a10) {$\PHobj{a_1}{a_0}$};
     \node[Asol,below of=a10] (a10s) {};
@@
     \path
+    (a0) edge (a10)
     (a10) edge (a10s)
@@
     % STEP 3
-    \node[Aobj,right of=a10,node distance=4cm] (ta01) {$\PHobj{a_0}{a_1}$};
+    \node[Aproc,right of=a0,node distance=4cm] (ta1) {$a_1$};
+    \node[Aobj,below of=ta1] (ta01) {$\PHobj{a_0}{a_1}$};
     \node[Asol,below of=ta01] (ta01s) {};
@@
     \path
+    (ta1) edge (ta01)
     (ta01) edge (ta01s)

### 2015-01-14 parts/sa.tex
revised end of section 5
fix GLC (re-add objective processes)

@@
 in this case, $P$ is re-targeted (\pref{eq:ECont}).
-Finally, \pref{eq:Vw} forces the graph to contain all the initial objectives,
+Finally, \pref{eq:Vw} and \eqref{eq:Vproc}
+force the graph to contain all the initial objectives
+and the related local states,
 and \pref{eq:VE} ensures the consistency of $\cwV$.
@@
   \allprocs(\cwV, \cwE) = (\cwV \cap \Proc) &\cup \{ \PHtarget(P) \mid P \in \cwV \cap \Obj \}\\
-  & \cup \{ P \neq \w \Rightarrow \PHbounce(P) \mid P \in \cwV \cap \Obj \}
+  & \cup \{ \PHbounce(P) \mid P \in \cwV \cap \Obj \wedge P \neq \w \}
 \end{align*}
@@
     \modMF{\toset{\w}} &\subseteq \cwV \label{eq:Vw} \\
-%    P \in \cwVObj &\Rightarrow \PHbounce(P) \in \cwV \label{eq:Vproc} \\
+    P \in \cwVObj &\Rightarrow \PHbounce(P) \in \cwV \label{eq:Vproc} \\
     (x, y) \in \cwE &\Rightarrow y \in \cwV \label{eq:VE} \\
@@
 
-  \modn{%
+  \modMF{%
   This result is new compared to the method proposed in~\cite{PMR12-MSCS}.
@@
   \begin{tikzpicture}[aS]
-%    \node[Aproc] (c1) {$c_1$};
-%    \node[Aobj,below of=c1] (c01) {$\PHobj{c_0}{c_1}$};
-    \node[Aobj] (c01) {$\PHobj{c_0}{c_1}$};
+    \node[Aproc] (c1) {$c_1$};
+    \node[Aobj,below of=c1] (c01) {$\PHobj{c_0}{c_1}$};
+%    \node[Aobj] (c01) {$\PHobj{c_0}{c_1}$};
     \node[Asol,below of=c01] (c01s) {};
@@
     \path
-%    (c1) edge (c01)
+    (c1) edge (c01)
     (c01) edge (c01s)

### 2015-01-24 parts/sa.tex
sa++

@@
 % vi:spell spelllang=en:
-\section{Static Analysis}\label{sec:sa}
+\section{Under-approximation of Reachability}\label{sec:sa}
 
-\todo{Replacer notre méthode par rapport aux méthodes d'interprétation abstraite en général}
+\modLP{%
+We present a static analysis that takes as input an AAN
+$\PH = (\PHs; \PHl; \PHa)$,
+an initial state, and a local state of an automata in $\PHs$, for identifying sufficient conditions
+that ensure the existence of a scenario starting from the initial state and leading to a state
+where the given local state is present.}
 
-The aim of this section is to define the problem of reachability in an AAN,
-and propose an under-approximation allowing to efficiently solve it.
-The static analysis presented here is inspired from~\cite{PMR12-MSCS}.
-We consider in this section an AAN $\PH = (\PHs; \PHl; \PHa)$.
+A classical approach for determining if a local state of an automaton can be reach from a
+given initial state is to build sequences of transitions from the initial state until a state
+containing the given local state is reached.
+This is essentially what model-checkers do, and the complexity of such analysis (PSPACE-complete
+\cite{Harel02}) makes it intractable on large systems, even with advanced symbolic approaches
+\cite{PMR12-MSCS}.
 
-\medskip
+Our approach relies on abstractions of scenarios that have been introduced in
+\cite{PMR12-MSCS} for the static analysis of reachability in the Process Hitting framework,
+a particular sub-class of AAN (see the Remark at the end of the previous section).
+In this paper, we generalize the static analysis for the case of the under-approximation of
+reachability in any AAN.
 
-\modMF{
-The main idea behind the static analysis presented in this section
-is to abstract the dynamics of an AAN model
-by a dynamics that is more general and easier to analyse.
-For this, we focus on the notion of objective:
-an objective is a couple of local states (\eg $\PHobj{a_i}{a_j}$) whose reachability
-is required to ensure the global reachability property considered;
-in other words, it is required that a set of actions hitting $a$ exists so that,
-starting from a state containing $a_i$,
-it is possible to play these actions (possibly intertwined with other actions)
-and reach a state containing $a_j$.
-Given the particular form of the actions in AANs,
-the solving of such an objective raises new objectives in the general case.
-%because each action can be triggered by (at most) one local state from a different automaton.
-Indeed, each of these local states also have to be reached before the required actions are played.
-However, the order of the considered actions is abstracted,
-and so is the order of the related objectives,
-thus resulting in an over-approximation of the requirements.
-}
+\todo{outline}
 
-\subsection{Preliminary Definitions}
-\label{ssec:sa-def}
+\subsection{Abstractions for Scenarios}
+\label{ssec:abstr-sce}
 
-The reachability of a local state $a_j$ of a given automaton $a$,
-starting from another local state $a_i$,
-is called an objective and is denoted $\PHobjp{a}{i}{j}$ (\pref{def:obj}).
+The approach presented in this section is based on two complementary notions,
+the \emph{objectives} and their \emph{local causality},
+that are intertwined in so-called \emph{Local Causality Graphs}.
+
+\subsubsection{Objectives}
+
+An \emph{objective} (\pref{def:obj}) denotes the reachability of a local state (e.g., $a_j$) of a given automaton $a$
+from the initial local state of that automaton (e.g., $a_i$).
+Such an objective is written $\PHobjp{a}{i}{j}$.
+Successive objectives are described with objective sequences (\pref{def:obj}).
+
 \begin{definition}[Objective ($\Obj$) \& Objective Sequence ($\OS$)]
@@
 
-A context (\pref{def:context}) extends the notion of state to a set of possible initial states:
-\modMF{
-to each automaton in the model, a context maps a set of local states in this automaton.
-}
-We also extend the override operator to contexts (\pref{def:ctxcap}).
-\begin{definition}[Context ($\Ctx$)]
-\label{def:context}
-  A \emph{context} $\ctx$ associates to each automaton in $\PHs$ a non-empty subset of its local states:
-  $\forall a \in \PHs, \PHget{\ctx}{a} \subseteq \PHl_a \wedge \PHget{\ctx}{a} \neq \emptyset$.
-  $\Ctx$ is the set of all contexts.
-\end{definition}
-%
-\begin{definition}[$\Cap: \Ctx \times \powerset(\PHproc) \rightarrow \Ctx$]
-\label{def:ctxcap}
-  For any $\ctx\in\Ctx$ and set of local states $ps \in \powerset(\PHproc)$,
-  the override of $\ctx$ by $ps$ is noted $\ctx \Cap ps$ and is defined by:
-  \[ \forall a \in \PHs, \PHget{(\ctx \Cap ps)}{a} \DEF
-  \begin{cases}
-    \{ p \in ps \mid \PHsort(p)=a \} & \text{if } \exists p \in ps, \PHsort(p)=a,\\
-    \PHget{\ctx}{a} & \text{else.}
-  \end{cases}
-  \]
-\end{definition}
-\noindent
-For a given context $\ctx$, we note $a_i \in \ctx$ if and only if $a_i \in \PHget{\ctx}{a}$,
-and for all $ps \in \powerset(\PHproc)$ or $ps \in \PHl$, $ps \subseteq \ctx \EQDEF \forall a_i \in ps, a_i \in \ctx$.
-A sequence of actions $\delta$ is \emph{playable} in a context $\ctx$ if and only if 
-$\exists s \subseteq \ctx, \delta \in \Sce(s)$.
-We denote then: $\delta \in \Sce(\ctx)$,
-and the play of $\delta$ in $\ctx$ is $\ctx \PHplay \delta = \ctx \Cap \ceil(\delta)$,
-where $\ceil(\delta)$ is the set containing the last local state in the sequence $\delta$ (hitter or bounce) of every automaton mentioned in $\delta$.
+We define the partial ordering relation $\ltw$ between two objective sequences (\pref{def:ltw}) as
+follows:
+$w\ltw w'$ if and only if there exists a mapping between all the objective bounces of $w'$ in $w$
+that preserve the sequentiality.
 
-Finally, a bounce sequence on a automaton $a$ (\pref{def:bs}) is a sequence of actions hitting $a$
-in which the bounce of each action equals the hitter of the following action.
-Bounce sequences are used to find local solutions to a given objective;
-\modMF{
-indeed, the bounce sequences solving an objective $\PHobj{a_i}{a_j}$
-only depend on the bounce part of the actions hitting the automaton $a$
-and not on the hitters.
-}%
-Then, a bounce sequence on $a$ can be abstracted into
-its combinations of hitters outside automaton $a$ (\pref{def:aBS});
-% the minimal sets of its sets of hitters that are not in automaton $a$ (\pref{def:aBS}).
-This abstraction is later used to propagate an objective on a given automaton
-by creating new objectives on other automata,
-by considering the sets of hitters required by the actions involved.
+\todo{support compatibility}
 
-\begin{definition}[Bounce sequence ($\BS$)]
-\label{def:bs}
-  A \emph{bounce sequence} $\zeta$ is a sequence of actions so that $\forall n \in \indexes{\zeta}, n < |\zeta|, \PHbounce(\zeta_{n}) = \PHtarget(\zeta_{n+1})$.
-  $\BS$ denotes the set of all bounce sequences, and
-  $\BS(P)$ denotes the set of bounce sequences \emph{solving} an objective $P$:
-  \[
-    \BS(\PHobj{a_i}{a_j}) \DEF \{ \zeta \in \BS \mid \PHtarget(\zeta_1)= a_i \wedge \PHbounce(\zeta_{|\zeta|}) = a_j \} \enspace.
-  \]
-  Furthermore, $\BS(\obj{a_i}{a_j}) = \emptyset$ if there is no way to reach $a_j$ from $a_i$
-  and $\emptyseq \in \BS(\obj{a_i}{a_i})$
-  \modMF{
-  for any trivial objective.
-  }
+\begin{definition}[$\ltw \subset \OS\times\OS$]\label{def:ltw}
+$\w\ltw\w'$ if and only if
+$|\w|\geq|\w'|$ and
+there exists a mapping $\phi: \indexes{\w'}\mapsto \indexes{\w}$ such that
+$\forall n,m \in\indexes{\w'}, n<m \Leftrightarrow \phi(n)<\phi(m)$,
+and
+$\forall n\in\indexes{\w'}, \bounce{\w'_n}=\bounce{\w_{\phi(n)}}$
 \end{definition}
 
+\begin{example}
+\[\obj{b_0}{b_1}\concat\obj{a_0}{a_1}\concat\obj{b_1}{b_2}
+\ltw
+\obj{a_0}{a_1}\concat\obj{b_0}{b_2}
+\ltw
+\obj{b_0}{b_2}\]
+\[\obj{b_0}{b_1}\not\ltw\obj{b_0}{b_2}\]
+\end{example}
+
+An objective sequence can be seen as an abstract representation of a set of scenarios that describe
+(part of) the successive state changes of the automata.
+We denote by $\concr(\w)$ (\pref{def:concr}) the set of scenarios concretising an objective sequence
+$\w$ in the state $s\in\PHs$.
+It is essentially all the scenarios for which there exists a mapping from the bounces of each
+objective to the bounce of an action in the scenario which preserve the sequential ordering.
+
+\todo{compatibility of $\w$ with $s$}
+
+\begin{definition}[$\concr: \OS \to \powerset(\Sce)$]\label{def:concr}
+Given $\w\in\OS$, $\concr(\w)$ is the set of scenarios concretising $\w$ in the
+state $s$:
+\begin{align*}
+\concr(\w) \DEF \{ \delta\in\Sce(s)\mid & (\w^\vartriangle=\emptyseq \wedge
+\delta=\emptyseq)  \vee (
+\w^\vartriangle\neq \emptyseq\wedge
+\\ &
+ \wedge \exists \phi:\indexes{\w}\mapsto\indexes{\delta},
+    (\forall n,m\in\indexes{\w}, n<m \Leftrightarrow \phi(n)\leq\phi(m))
+\\ & \qquad
+	\wedge \forall n\in\indexes{\w},
+	  \bounce{\w_n} \in s\play\delta_{1..\phi(n)})
+\}
+\enspace,
+\end{align*}
+where $\omega^\vartriangle$ refers to the objective sequence $\omega$ where
+trivial objectives have been removed.
+The notation $\delta_{a..b}$ in the previous definition
+denotes the subsequence of $\delta$ between indexes $a$ and $b$,
+as defined on page \pageref{notations}.
+\end{definition}
+
+From \pref{def:ltw} and \pref{def:concr}, we derive that if 
+$w\ltw w'$, then $\concr(w)\subseteq\concr(\w')$ (\pref{lem:ltw}).
+\begin{lemma}\label{lem:ltw}
+$\w\ltw\w' \Longrightarrow \concr(\w)\subseteq\concr(\w')$\enspace.
+\end{lemma}
+
+\subsubsection{Local Causality for Objectives}
+
+The aim of searching for the existence of a scenario from a state $s$ leading to a state
+where a given local state of an automaton $a_j$ is present
+can be reformulated as the checking for the non-emptiness of $\concr(\obj{a_i}{a_j})$, where
+$a_i=\get{s}{a}$.
+A first hint for checking this emptiness is to look for actions that have to be played in order to
+reach the state $i$ from $0$ within the automaton $a$.
+
+Given an objective $P = \obj{a_i}{a_j} \in\Obj$, we define $\BS(P)$ the \emph{bounce sequences} of
+$P$ as the set of minimal sequences of actions hitting $a$ in which the bounce of each action is
+the target of the following action (\pref{def:bs}).
+
+\begin{definition}[Bounce Sequence ($\BS$)]\label{def:bs}
+A \emph{bounce sequence} $\zeta$  is a sequence of actions such that
+$\forall n\in\indexes{\zeta}, n<|\zeta|,
+\bounce{\zeta_{n}} = \target{\zeta_{n+1}}$.
+$\BS$ denotes the set of bounce sequences.
+We refer to the set of bounce sequences \emph{resolving} the objective $P$ as
+$\BS(P)$:
+\begin{align*}
+\BS(\obj{a_i}{a_j}) \DEF \{ \zeta\in\BS\mid & \target{\zeta_1}=a_i\wedge
+			    \bounce{\zeta_{|\zeta|}}=a_j \\
+& \wedge \forall m,n\in\indexes{\zeta}, n>m, \bounce{\zeta_n}\neq\target{\zeta_m}
+				\}\enspace.
+\end{align*}
+\end{definition}
+
+Therefore,
+$\BS(\obj{a_i}{a_i}) = \{\emptyseq\}$; and
+$\BS(\obj{a_i}{a_j}) = \emptyset$ if there is no possibility to reach $a_j$ from
+$a_i$.
+
+\todo{example}
+
+From \pref{def:bs}, we can derive that any scenario concretising an objective includes all the
+actions of one of the bounce sequences of the objective (\pref{lem:bs-concr}).
+\begin{lemma}
+Given a state $s\in L$ and an objective $\obj{a_i}{a_j}$ with $\get{s}{a}=a_i$,
+$\forall\delta\in\concr(\obj{a_i}{a_j})$,
+$\exists\zeta\in\BS(\obj{a_i}{a_j})$ such that
+$\exists \phi: \indexes{\zeta}\to\indexes{\delta}$
+with
+$\forall n,m\in\indexes{\zeta}, n<m \Leftrightarrow \phi(n)<\phi(m)$
+and
+$\forall n\in\indexes{\zeta}$, $\zeta_n = \delta_{\phi(n)}$.
+\label{lem:bs-concr}
+\end{lemma}
+
+\todo{revise}
 In the following, we denote: $\sSol = \powerset(\PHproc)$
@@
 
-\subsection{Under-approximation}
-\label{ssec:ua}
+\subsubsection{Local Causality Graph}
 
-We denote by $\concr(\w)$ (\pref{def:concr}) the set of scenarios concretising an objective sequence $\w$ in the context $\ctx$.
-In \pref{def:uconcr}, we define $\uconcr(\w)$ as equal to $\concr(\w)$ if and only if $\concr(\w)$ contains scenarios starting from all states $s \subseteq \ctx$.
-\pref{lem:uconcr-ctx} is used to over-approximate the initial context $\ctx$.
+Given one initial objective, one could then recursively refine the objective into objective
+sequences following its bounce sequences \cite{PMR12-MSCS}:
+the refinement of objective $P$ with $\zeta\in\BS(P)$ would consists in prepending to $P$ the
+objectives leading to the hitters of the actions in $\zeta$, in the same sequential order;
+the generalisation of the refinement to an objective sequence would require to consider all possible
+interleaving between the refinements.
 
-\begin{definition}[$\concr: \OS \to \powerset(\Sce)$]\label{def:concr}
-Given $\w\in\OS$, $\concr(\w)$ is the set of minimal scenarios concretising $\w$ in the
-context $\ctx$. It is defined as the largest set satisfying the following conditions:
-\begin{enumerate}[(i)]
-\item $\forall\delta\in\concr(\w), \modMF{\delta\in\Sce(\ctx)}$
-\item $\forall\delta\in\concr(\w),
-  \exists \phi:\indexes{\w}\to\indexes{\delta},
-    (\forall n,m\in\indexes{\w}, n<m \Leftrightarrow \phi(n)\leq\phi(m)),$
-\\\hspace*{2cm}$\forall n\in\indexes{\w}, \PHbounce(\w_n) \in \ctx\play\delta_{1..\phi(n)}$
-\item $\forall\delta,\delta'\in\concr(\w)
-				\card{\delta}\leq\card{\delta'} \Rightarrow
-					\delta\neq\delta'_{1..\card{\delta}}$.
-\end{enumerate}
-\end{definition}
-
-\noindent
-The notation $\delta_{a..b}$ in the previous definition
-denotes the subsequence of $\delta$ between indexes $a$ and $b$,
-as defined on page \pageref{notations}.
-
-\begin{definition}[$\uconcr: \OS \rightarrow \powerset(\Sce)$]
-\label{def:uconcr}
-  \[
-  \modMF{\forall \w \in \OS,}
-  \uconcr(\w) \DEF
-  \begin{cases}
-    \concr(\w) & \text{if } \forall s \in \PHl, s \subseteq \ctx, \exists \delta \in \concr(\w), \delta \in \Sce(s) \\
-    \emptyset & \text{else.}
-  \end{cases}
-  \]
-\end{definition}
-% 
-\begin{lemma}
-\label{lem:uconcr-ctx}
-  $\ctx \subseteq \ctx' \wedge \muconcr_{\ctx'}(\w) \neq \emptyset \Longrightarrow \muconcr_{\ctx}(\w) \neq \emptyset$.
-\end{lemma}
-
-For any objective $P$ and context $\ctx$, \pref{def:maxCont} gives the set of local states of automaton $\PHsort(P)$ that are required to solve $P$ in $\ctx$, denoted by $\gCont_\ctx(\PHsort(P), P)$.
-\begin{definition}[$\gCont_\ctx : \Sigma \times \Obj \rightarrow \powerset(\PHproc)$]
-  \label{def:maxCont}
-  \begin{align*}
-    \gCont_\ctx(a,P) \DEF
-    \{ p \in \PHproc &\mid \exists ps \in \aBS(P), \exists b_i \in ps, b = a \wedge p = b_i \\
-      & \vee b \neq a \wedge p \in \gCont_\ctx(a, \PHobj{b_j}{b_i}) \wedge b_j \in \PHget{\ctx}{b} \}
-    \enspace.
-  \end{align*}
-\end{definition}
-
-\modMF{
-A graph of local causality $\myB = (\cwV, \cwE)$
-is a graph where $\cwV \subseteq \Proc \cup \Obj \cup \sSol \cup \Sol$ is the set of vertices
+These refinements can be summarized compactly with a so-called Local Causality Graph (LCG).
+A LCG $\myB = (\cwV, \cwE)$
+is a digraph where $\cwV \subseteq \Proc \cup \Obj \cup \sSol \cup \Sol$ is the set of vertices
 and $\cwE \subseteq \cwV \times \cwV$ is the set of oriented edges.
+\todo{explain nodes}
 Such a graph aims a describing the requirements of a given reachability
@@
 thus encompassing all requirement for the solving of a whole objective.
-}
 
-\modMF{
+\todo{explain edges}
 The edges of such a graph allow to draw links between these requirements.
@@
 and \pref{eq:VE} ensures the consistency of $\cwV$.
+
+\todo{motivate context}
+A context (\pref{def:context}) extends the notion of state to a set of possible initial states:
+\modMF{
+to each automaton in the model, a context maps a set of local states in this automaton.
 }
+\begin{definition}[Context ($\Ctx$)]
+\label{def:context}
+  A \emph{context} $\ctx$ associates to each automaton in $\PHs$ a non-empty subset of its local states:
+  $\forall a \in \PHs, \PHget{\ctx}{a} \subseteq \PHl_a \wedge \PHget{\ctx}{a} \neq \emptyset$.
+  $\Ctx$ is the set of all contexts.
+\end{definition}
 
-\modMF{
-However, this graph $\myB$ alone is not sufficient to check the reachability of
-an objective sequence $\w$ from an initial context $\ctx$;
-indeed, the reachability of each intermediate required local state
-is only checked starting from the context $\ctx$,
-although this context may be modified by other objectives.
-Therefore, such a reachability requires the building of the
-\emph{saturated graph of local causality} (\pref{def:glc})
-which is obtained by iteratively saturating the initial context with all
-local states referenced in the graph,
-until reaching a fixed point.
-Such a fixed point always exists because the size of the context
-is limited by the size of the initial PH model.
-The set of local states contained in a graph of local causality
-is given by:
-\begin{align*}
-  \allprocs(\cwV, \cwE) = (\cwV \cap \Proc) &\cup \{ \PHtarget(P) \mid P \in \cwV \cap \Obj \}\\
-  & \cup \{ \PHbounce(P) \mid P \in \cwV \cap \Obj \wedge P \neq \w \}
-\end{align*}
-where, if the objective sequence $\w$ consists of only one element,
-we can omit the hitter of this objective
-provided that it does not appear elsewhere in the graph.
-}
+Given a context $\ctx$ and an objective sequence $\w$, the corresponding LCG can be built
+recursively starting from the objectives in $\w$ and recursively adding their possible refinements
+following $\BS$ (\pref{def:glc}).
 
@@
 \label{def:glc}
-  The \emph{\modMF{saturated} graph of local causality} $\cwB \DEF (\Bv, \Be)$ is defined as:
-  $\cwB \DEF \lfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs(\myB)}}$,
-  where $\myB \DEF (\cwV, \cwE)$ is the smallest graph with
-  $\cwV \subseteq \Proc \cup \Obj \cup \sSol \cup \Sol$ and $\cwE \subseteq \cwV \times \cwV$
-  so that:
-  \begin{align}
-    \modMF{\toset{\w}} &\subseteq \cwV \label{eq:Vw} \\
-    P \in \cwVObj &\Rightarrow \PHbounce(P) \in \cwV \label{eq:Vproc} \\
-    (x, y) \in \cwE &\Rightarrow y \in \cwV \label{eq:VE} \\
-    P \in \cwVObj \wedge pps \in \modMF{\aBS}(P) &\Rightarrow (P, pps) \in \cwE \label{eq:ESol1} \\
-    \moda{pps \in \cwVSol \wedge A \in pps} &\moda{\Rightarrow (pps, A) \in \cwE} \label{eq:ESol3} \\
-    A \in \cwVsSol \wedge a_i \in A &\Rightarrow (A, a_i) \in \cwE \label{eq:ESol2} \\
-    a_i \in \cwVProc \wedge a_j \in \ctx &\Rightarrow (a_i, \PHobjp{a}{j}{i}) \in \cwE \label{eq:EReq} \\
-%    a \in \cs \wedge a_i \in \cwVProc \wedge ps \in \csState(a_i) &\Rightarrow (a_i, ps) \in \cwE \label{eq:EPrio} \\
-    P \in \cwVObj \wedge q \in \gCont_\ctx(\PHsort(P), P) &\Rightarrow (P, \PHobj{q}{\PHbounce(P)}) \in \cwE \label{eq:ECont} \!
-  \end{align}
+Given a context $\ctx$ and a local state $p\in \Proc$,
+the Local Causality Graph (LCG) for reachability under-approximation
+$\cwB \DEF (\Bv, \Be)$
+with
+$\cwBNodes \subseteq \Proc \cup \Obj \cup \NSol \cup \powerset(\Proc)$
+and
+$\cwBEdges \subseteq \cwBNodes \times \cwBNodes$,
+is the smallest graph such that:
+\begin{enumerate}
+\item
+$p \in \cwBNodes$
+\item
+$a_i\in\cwBNodes\cap\Proc \Leftrightarrow \{ (a_i,\obj{a_j}{a_i}) \mid
+a_j\in\ctx$ \\
+\hspace*{3cm}
+$\vee (a_j\neq a_i\wedge a_j\neq\w\wedge a_j\in\cwBNodes\cap\Proc)
+\}\subseteq\cwBEdges$
+\item
+$P\in\cwBNodes\cap\Obj \Leftrightarrow 
+	\{ (P,\langle P,nls\rangle) \mid nls\in\nsol(P) \}\subseteq\cwBEdges$
+\item
+$\langle P, nls \rangle\in\cwBNodes\cap\NSol \Leftrightarrow
+	\{ (\langle P,nls\rangle, ls) \mid ls\in nls \}\subseteq\cwBEdges$
+\item
+$ls \in\cwBNodes\cap\powerset(\Proc) \Leftrightarrow
+	\{ (ls, a_i) \mid a_i\in ls \}\subseteq\cwBEdges$
+\item
+$\obj{a_i}{a_j}\in \cwBNodes\cap\Obj \Rightarrow 
+	\{(\obj{a_i}{a_j},\obj{a_k}{a_j}) \mid a_k\neq a_j,$
+\\
+\hspace*{4cm}
+$a_k\in \conn_{(\cwBNodes,\cwBEdges)}(\langle\obj{a_i}{a_j},nls\rangle),$
+\\
+\hspace*{4cm}
+$nls\in\nsol(\obj{a_i}{a_j}) \}\subset\cwBEdges$
+\end{enumerate}
+
+\todo{def conn, nsol}
 \end{definition}
 
+%
+\begin{comment}
+\noindent
+For a given context $\ctx$, we note $a_i \in \ctx$ if and only if $a_i \in \PHget{\ctx}{a}$,
+and for all $ps \in \powerset(\PHproc)$ or $ps \in \PHl$, $ps \subseteq \ctx \EQDEF \forall a_i \in ps, a_i \in \ctx$.
+A sequence of actions $\delta$ is \emph{playable} in a context $\ctx$ if and only if 
+$\exists s \subseteq \ctx, \delta \in \Sce(s)$.
+We denote then: $\delta \in \Sce(\ctx)$,
+and the play of $\delta$ in $\ctx$ is $\ctx \PHplay \delta = \ctx \Cap \ceil(\delta)$,
+where $\ceil(\delta)$ is the set containing the last local state in the sequence $\delta$ (hitter or bounce) of every automaton mentioned in $\delta$.
+
+\end{comment}
+
+\subsection{Sufficient condition for reachability of a local state}
+\label{ssec:ua}
+
+\todo{explain rational}
+\begin{itemize}
+\item we want to identify an objective sequence that for sure has a concrete scenario
+\item LCG is abstract representation of a set of objective sequences
+\item we prove that if LCG has no cycle, and all its local states synchronizations are independent,
+then such a sequence exists.
+\item Note: as we are under-approximating, we de not require that this set is complete.
+\end{itemize}
+
+\todo{motivate $\uconcr$}
+\begin{definition}[$\uconcr: \OS \rightarrow \powerset(\Sce)$]
+\label{def:uconcr}
+  \[
+  \modMF{\forall \w \in \OS,}
+  \uconcr(\w) \DEF
+  \begin{cases}
+    \concr(\w) & \text{if } \forall s \in \PHl, \concr(\w)\neq\emptyset\\
+    \emptyset & \text{else.}
+  \end{cases}
+  \]
+\end{definition}
+
+\todo{revise}
 \modMF{
@@
 }
-Then, \pref{th:approxinf} gives a sufficient condition for the concretisation
-of an objective sequence in a given context,
+\begin{definition}[Independant synchronisations]
+\label{def:coherent}
+  In a LCG $\cwB = (\Bv, \Be)$,
+  a node $x \in \Bv\cap\sSol$ is an \emph{independent synchronisation} if and only if
+  $x$ has no successor $a_j \in \Bv \cap \Proc$ such that $\exists a_i \in x$, $a_i \neq a_j$.
+\end{definition}
+
+\todo{intuition on sufficient condition}
+Then, \pref{th:approxinf} gives a sufficient condition for the reachability of 
+a local state in a given context
+of an objective sequence in a given context
 which is derived immediately from the saturated graph of local causality,
@@
 A proof of this theorem is given in \pref{suppl:demoapproxinf}.
-\begin{definition}[Coherent node]
-\label{def:coherent}
-  \modMF{
-  In a given saturated graph of local causality $\cwB = (\Bv, \Be)$,
-  a node $x \in \Bv$ is said to be \emph{coherent} if and only if:
-  $x \in \Bv \cap \sSol \Rightarrow x$ has no successor $a_j \in \Bv \cap \Proc$
-  so that $\exists a_i \in x$, $a_i \neq a_j$.
-  }
-\end{definition}
 
-\begin{theorem}[Under-Approximation]
+\begin{theorem}[Under-approximation]
 \label{th:approxinf}
@@
   a context $\ctx$ and an objective sequence $\w$,
-  if the graph $\cwB$ contains no cycle,
-  all objectives have at least one solution
-  and all nodes are coherent,
+  if the LCG $\cwB$ contains no cycle,
+  all objective nodes have at least one child,
+  and all the synchronisations are independent,
   then $\uconcr(\w) \neq \emptyset$.
@@
 Regarding the complexity of the method,
-computing the saturated graph of local causality is polynomial in the number of automata in $\PH$ and exponential in the number of local states in one automaton.
+computing the LCG is polynomial in the number of automata in $\PH$ and exponential in the number of local states in one automaton.
 Checking the properties allowing to apply \pref{th:approxinf} is polynomial in the size of the graph.
@@
 in the number of solutions to each objective.
-Our method can thus still be considered as efficient
-compared to regular model-checking which is usually PSPACE-complete~\cite{Harel02}.
 }
@@
 
+\todo{integrate}
+We also extend the override operator to contexts (\pref{def:ctxcap}).
+\begin{definition}[$\Cap: \Ctx \times \powerset(\PHproc) \rightarrow \Ctx$]
+\label{def:ctxcap}
+  For any $\ctx\in\Ctx$ and set of local states $ps \in \powerset(\PHproc)$,
+  the override of $\ctx$ by $ps$ is noted $\ctx \Cap ps$ and is defined by:
+  \[ \forall a \in \PHs, \PHget{(\ctx \Cap ps)}{a} \DEF
+  \begin{cases}
+    \{ p \in ps \mid \PHsort(p)=a \} & \text{if } \exists p \in ps, \PHsort(p)=a,\\
+    \PHget{\ctx}{a} & \text{else.}
+  \end{cases}
+  \]
+\end{definition}
+
 From \pref{th:approxinf}, we can deduce that

### 2015-01-25 parts/def-ph.tex
sa++

@@
 
+Finally, a context (\pref{def:context}) extends the notion of state to a set of possible initial states:
+\modMF{
+to each automaton in the model, a context maps a set of local states in this automaton.
+}
+\begin{definition}[Context ($\Ctx$)]
+\label{def:context}
+  A \emph{context} $\ctx$ associates to each automaton in $\PHs$ a non-empty subset of its local states:
+  $\forall a \in \PHs, \PHget{\ctx}{a} \subseteq \PHl_a \wedge \PHget{\ctx}{a} \neq \emptyset$.
+  $\Ctx$ is the set of all contexts.
+\end{definition}
+\noindent
+For a given context $\ctx$, we note $a_i \in \ctx$ if and only if $a_i \in \PHget{\ctx}{a}$,
+and for all $ps \in \powerset(\PHproc)$ or $ps \in \PHl$, $ps \subseteq \ctx \EQDEF \forall a_i \in ps, a_i \in \ctx$.
+\begin{comment}
+A sequence of actions $\delta$ is \emph{playable} in a context $\ctx$ if and only if 
+$\exists s \subseteq \ctx, \delta \in \Sce(s)$.
+We denote then: $\delta \in \Sce(\ctx)$,
+and the play of $\delta$ in $\ctx$ is $\ctx \PHplay \delta = \ctx \Cap \ceil(\delta)$,
+where $\ceil(\delta)$ is the set containing the last local state in the sequence $\delta$ (hitter or bounce) of every automaton mentioned in $\delta$.
+
+\end{comment}
+
+We also extend the override operator to contexts (\pref{def:ctxcap}).
+\begin{definition}[$\Cap: \Ctx \times \powerset(\PHproc) \rightarrow \Ctx$]
+\label{def:ctxcap}
+  For any $\ctx\in\Ctx$ and set of local states $ps \in \powerset(\PHproc)$,
+  the override of $\ctx$ by $ps$ is noted $\ctx \Cap ps$ and is defined by:
+  \[ \forall a \in \PHs, \PHget{(\ctx \Cap ps)}{a} \DEF
+  \begin{cases}
+    \{ p \in ps \mid \PHsort(p)=a \} & \text{if } \exists p \in ps, \PHsort(p)=a,\\
+    \PHget{\ctx}{a} & \text{else.}
+  \end{cases}
+  \]
+\end{definition}
+
 \modn{

### 2015-01-25 parts/intro.tex
sa++

@@
 
-\paragraph*{Functions and least fixed point}
-If $A$ and $B$ are sets,
-$f : A \rightarrow B$ denotes a function $f$ that maps the elements of $A$ to elements of $B$.
-If $f$ is a monotonically increasing and bounded function, then
-$\lfp{x_0}{x}{x'}$ is the least fixed point of the function $x \mapsto x'$ which is greater than $x_0$.
+\paragraph*{Digraph}
+If $(V,E)$ is a directed graph, $V$ are the nodes, $E \subset V\times V$ the edges,
+the children of a node $n$ are given by
+$\childs: V \to \powerset(V)$, with
+$\childs(n) \DEF \{ m\in V\mid (n,m)\in E\}$;
+its parents are given by
+$\parents: V \to \powerset(V)$ with
+$\parents(n) \DEF \{ m\in N\mid (m,n)\in E\}$;
+and its descendants are give by
+$\conn_{(V,E)}(n)$ which is the least fixed point containing $n$
+of the function
+$\f{f}\conn:\powerset(N)\to \powerset(N)$
+with $\f{f}\conn(W) \DEF \bigcup_{m\in W} \childs(m)$.
+
+%\paragraph*{Functions and least fixed point}
+%If $A$ and $B$ are sets,
+%$f : A \rightarrow B$ denotes a function $f$ that maps the elements of $A$ to elements of $B$.
+%If $f$ is a monotonically increasing and bounded function, then
+%$\lfp{x_0}{x}{x'}$ is the least fixed point of the function $x \mapsto x'$ which is greater than $x_0$.

### 2015-01-25 parts/sa.tex
sa++

@@
 
-The aim of searching for the existence of a scenario from a state $s$ leading to a state
+The existence of a scenario from a state $s$ leading to a state
 where a given local state of an automaton $a_j$ is present
@@
 A first hint for checking this emptiness is to look for actions that have to be played in order to
-reach the state $i$ from $0$ within the automaton $a$.
+reach the state $j$ from $i$ within the automaton $a$.
 
@@
 
+\begin{comment}
 \todo{revise}
@@
 These refinements can be summarized compactly with a so-called Local Causality Graph (LCG).
-A LCG $\myB = (\cwV, \cwE)$
-is a digraph where $\cwV \subseteq \Proc \cup \Obj \cup \sSol \cup \Sol$ is the set of vertices
-and $\cwE \subseteq \cwV \times \cwV$ is the set of oriented edges.
-\todo{explain nodes}
-Such a graph aims a describing the requirements of a given reachability
-problem, that is, the reachability of $\w$ from the initial context $\ctx$.
-Thus, a node in $\PHproc$ represents a local state required to play an action,
-a node in $\Obj$ is an objective to reach a given local state,
-a node in $\sSol$ is a set of hitters that have to be active simultaneously
-to solve one step of a given objective,
-and a node in $\Sol$ is a set of sets of hitters,
-thus encompassing all requirement for the solving of a whole objective.
-
-\todo{explain edges}
-The edges of such a graph allow to draw links between these requirements.
-Thus, an objective $P \in \Obj$ is solvable if
-at least one related bounce sequence in $\BS(P)$ can be played;
-therefore, we can consider all minimal sets of sets of hitters of these bounce sequences
-(that is, the sets of $\aBS(P) \subseteq \Sol$, see \pref{def:aBS})
-as requirements to solve this objective (\pref{eq:ESol1}).
-Such a set can then naturally be split into as many sets of hitters (\pref{eq:ESol3})
-which all have to be simultaneously active.
-These sets of hitters can in turn be split into several local state nodes (\pref{eq:ESol2}).
-This creates new requirements, as the reachability of a required local state $a_i$
-is approximated by the ability to solve all objectives of the form
-$\PHobjp{a}{j}{i} \in \Obj$ for all $a_j$ in the initial context (\pref{eq:EReq}).
-Furthermore, we note that the solving of an objective $P$ may require
-a local state of $\PHsort(P)$,
-\ie $\gCont(\PHsort(P), P) \neq \emptyset$ (see \pref{def:maxCont});
-in this case, $P$ is re-targeted (\pref{eq:ECont}).
-Finally, \pref{eq:Vw} and \eqref{eq:Vproc}
-force the graph to contain all the initial objectives
-and the related local states,
-and \pref{eq:VE} ensures the consistency of $\cwV$.
-
-\todo{motivate context}
-A context (\pref{def:context}) extends the notion of state to a set of possible initial states:
-\modMF{
-to each automaton in the model, a context maps a set of local states in this automaton.
-}
-\begin{definition}[Context ($\Ctx$)]
-\label{def:context}
-  A \emph{context} $\ctx$ associates to each automaton in $\PHs$ a non-empty subset of its local states:
-  $\forall a \in \PHs, \PHget{\ctx}{a} \subseteq \PHl_a \wedge \PHget{\ctx}{a} \neq \emptyset$.
-  $\Ctx$ is the set of all contexts.
-\end{definition}
-
-Given a context $\ctx$ and an objective sequence $\w$, the corresponding LCG can be built
-recursively starting from the objectives in $\w$ and recursively adding their possible refinements
-following $\BS$ (\pref{def:glc}).
+Given an initial context $\ctx$ and a local state $p\in\Proc$,
+A LCG $\cwB = (\cwV, \cwE)$
+is a digraph where $\cwV \subseteq \Proc\cup \Obj \cup \Sol \cup \sSol$ is the set of vertices
+where $\sSol=\powerset(\Proc)$ and $\Sol=\Obj\times\powerset(\sSol)$
+and $\cwE \subseteq \cwV \times \cwV$ is the set of oriented edges
+(\pref{def:lcg}).
+A node in $\Obj$ represents an objective that have to be refined.
+Such a node can then be related to nodes in $\Sol$ which represents a set of hitter set of a
+bounce sequence of the objective:
+given an objective $P$, if $\zeta\in\BS(P)$, $\abstr\zeta \DEF \{\PHhitter(\zeta_n) \mid
+n\in\indexes\zeta \}$, then $P$ is related to $\langle P, \abstr\zeta\rangle\in\Sol$
+(\pref{def:lcg}-3).
+Given a node $\langle P,\abstr\zeta\rangle\in\cwV\cap\Sol$, for each $ps\in\abstr\zeta$,
+it is related to a node $ps\in\sSol$
+(\pref{def:lcg}-4).
+A node $ps\in\sSol$ is then related to each $a\in\Proc$
+(\pref{def:lcg}-5).
+Given a node $a_i\in\cwV\cap\Proc$, for each $a_j\in\ctx$ or $a_j\in\cwV\cap\Proc$,
+it is related to an objective $\obj{a_j}{a_i}$
+(\pref{def:lcg}-2).
+Finally, given a node $\obj{a_j}{a_i}\in\cwV\cap\Obj$,
+if a local state $a_k\neq a_i$ is in its descendants (given by
+$\conn_{(\cwBNodes,\cwBEdges)}(\obj{a_j}{a_i})$), then
+$\obj{a_j}{a_i}$ is related to $\obj{a_k}{a_i}$ in the LCG
+(\pref{def:lcg}-6).
 
 \begin{definition}
-\label{def:glc}
+\label{def:lcg}
 Given a context $\ctx$ and a local state $p\in \Proc$,
@@
 with
-$\cwBNodes \subseteq \Proc \cup \Obj \cup \NSol \cup \powerset(\Proc)$
+$\cwBNodes \subseteq \Proc \cup \Obj \cup \NSol \cup \sSol$
 and
@@
 $a_i\in\cwBNodes\cap\Proc \Leftrightarrow \{ (a_i,\obj{a_j}{a_i}) \mid
-a_j\in\ctx$ \\
-\hspace*{3cm}
-$\vee (a_j\neq a_i\wedge a_j\neq\w\wedge a_j\in\cwBNodes\cap\Proc)
+a_j\in\ctx \vee a_j\in\cwBNodes\cap\Proc)
 \}\subseteq\cwBEdges$
@@
 $P\in\cwBNodes\cap\Obj \Leftrightarrow 
-	\{ (P,\langle P,nls\rangle) \mid nls\in\nsol(P) \}\subseteq\cwBEdges$
+	\{ (P,\langle P,\abstr \zeta\rangle) \mid \zeta\in\BS(P) \}\subseteq\cwBEdges$
 \item
@@
 \item
-$ls \in\cwBNodes\cap\powerset(\Proc) \Leftrightarrow
+$ls \in\cwBNodes\cap\sSol \Leftrightarrow
 	\{ (ls, a_i) \mid a_i\in ls \}\subseteq\cwBEdges$
@@
 \hspace*{4cm}
-$a_k\in \conn_{(\cwBNodes,\cwBEdges)}(\langle\obj{a_i}{a_j},nls\rangle),$
+$a_k\in \conn_{(\cwBNodes,\cwBEdges)}(\langle\obj{a_i}{a_j},\abstr\zeta\rangle),$
 \\
 \hspace*{4cm}
-$nls\in\nsol(\obj{a_i}{a_j}) \}\subset\cwBEdges$
+$\zeta\in\BS(\obj{a_i}{a_j}) \}\subset\cwBEdges$
 \end{enumerate}
-
-\todo{def conn, nsol}
+with $\abstr\zeta \DEF \{\PHhitter(\zeta_n) \mid n\in\indexes\zeta \}$.
 \end{definition}
-
-%
-\begin{comment}
-\noindent
-For a given context $\ctx$, we note $a_i \in \ctx$ if and only if $a_i \in \PHget{\ctx}{a}$,
-and for all $ps \in \powerset(\PHproc)$ or $ps \in \PHl$, $ps \subseteq \ctx \EQDEF \forall a_i \in ps, a_i \in \ctx$.
-A sequence of actions $\delta$ is \emph{playable} in a context $\ctx$ if and only if 
-$\exists s \subseteq \ctx, \delta \in \Sce(s)$.
-We denote then: $\delta \in \Sce(\ctx)$,
-and the play of $\delta$ in $\ctx$ is $\ctx \PHplay \delta = \ctx \Cap \ceil(\delta)$,
-where $\ceil(\delta)$ is the set containing the last local state in the sequence $\delta$ (hitter or bounce) of every automaton mentioned in $\delta$.
-
-\end{comment}
 
@@
 
-\todo{explain rational}
-\begin{itemize}
-\item we want to identify an objective sequence that for sure has a concrete scenario
-\item LCG is abstract representation of a set of objective sequences
-\item we prove that if LCG has no cycle, and all its local states synchronizations are independent,
-then such a sequence exists.
-\item Note: as we are under-approximating, we de not require that this set is complete.
-\end{itemize}
+Given a context $\ctx$ and a local state $p\in\Proc$, the LCG $\cwB$ contains a set of objectives
+that can be used to build a concrete scenario reaching $p$.
+Because we are focused on sufficient conditions for reachability, we do not require that all
+possible scenarios can be derived from the LCG.
 
-\todo{motivate $\uconcr$}
-\begin{definition}[$\uconcr: \OS \rightarrow \powerset(\Sce)$]
-\label{def:uconcr}
-  \[
-  \modMF{\forall \w \in \OS,}
-  \uconcr(\w) \DEF
-  \begin{cases}
-    \concr(\w) & \text{if } \forall s \in \PHl, \concr(\w)\neq\emptyset\\
-    \emptyset & \text{else.}
-  \end{cases}
-  \]
+In this section, we prove that if the LCG has no cycle, if all its nodes in $\Obj$ have at least one
+child, and if all its nodes in $\sSol$ satisfy a
+particular criteria, so-called independence, then from any state
+delimited by the context $\ctx$, there exists a scenario that reaches $p$
+(\pref{th:approxinf}).
+
+A node $x$ of the LCG in $\sSol$ is \emph{independent} (\pref{def:coherent}) if for each local state
+$a_i\in x$, none of the other local state $b_j\in x$ have a local state of automaton $a$ different
+than $a_i$ in their descendants.
+This criteria ensures that once a local state in $x$ has been reached, reaching another local state
+in $x$ should not require to change the first local state.
+
+\begin{definition}[Independent synchronisations]
+\label{def:coherent}
+  In a LCG $\cwB = (\Bv, \Be)$,
+  a node $x \in \Bv\cap\sSol$ is \emph{independent} if and only if
+  for each $a_i\in x$,
+  for each $b_j\in x, b_j\neq a_i$,
+  $a_k \in\conn_{\cwB}(x) \cap \Proc \Rightarrow a_k = a_i$.
 \end{definition}
 
-\todo{revise}
-\modMF{
-In the saturated graph of local causality, a set of hitters $A \in \sSol$
-is said to be \emph{coherent} (\pref{def:coherent})
-if none of the local states in $A$ conflict with
-a successor of $A$ in $\Bv \cap \Proc$,
-that is, if there exists no local state node $a_j$ in the successors of $A$
-and no element $a_i \in A$ so that $a_i \neq a_j$.
-}
-\begin{definition}[Independant synchronisations]
-\label{def:coherent}
-  In a LCG $\cwB = (\Bv, \Be)$,
-  a node $x \in \Bv\cap\sSol$ is an \emph{independent synchronisation} if and only if
-  $x$ has no successor $a_j \in \Bv \cap \Proc$ such that $\exists a_i \in x$, $a_i \neq a_j$.
-\end{definition}
-
-\todo{intuition on sufficient condition}
-Then, \pref{th:approxinf} gives a sufficient condition for the reachability of 
-a local state in a given context
-of an objective sequence in a given context
-which is derived immediately from the saturated graph of local causality,
-and the condition that all sets of hitters are coherent.
-A proof of this theorem is given in \pref{suppl:demoapproxinf}.
+The intuition is the following.
+Given a state $s\subset\ctx$, we recursively refine the initial objective (reaching $p$ from the initial
+state) according to its children.
+As the LCG is acyclic, such a recursion always terminates, and as all the objective nodes have at
+least one child, it never get stuck.
+The refinement of an objective node $\obj{a_i}{a_j}$ acts as follows:
+if the node has another objective node $\obj{a_k}{a_j}$ as child, we first refine the objective
+$\obj{a_i}{a_k}$ (which, by construction, is necessarily in the LCG)
+and then will refine the objective $\obj{a_k}{a_j}$.
+If the objective nodes has only nodes in $\Sol$ (bounce sequences), one is picked arbitrarily.
+If $\langle P, nls\rangle$ is the chosen node,
+by construction there exists $\zeta\in\BS(P)$ such that $\abstr\zeta = nls \in \powerset(\sSol)$.
+If $\zeta = \emptyseq$ (for instance in the case when $a_i = a_j$), the recursion stops and we
+continue to the next stage.
+Otherwise, for each $n\in\indexes\zeta$,
+for each $b_i \in\PHhitter(\zeta_n)$,
+we refine the objective $\obj{b_j}{b_i}$ where $b_j$ is the state of $b$ in the current state.
+By induction, $\obj{b_j}{b_i}$ is a child of $b_i$ in the LCG of \pref{def:lcg}.
+Then, we know (by induction) that the current state of $b$ is $b_i$.
+After having repeated this procedure for each $b_i\in\PHhitter(\zeta_n)$,
+because all the nodes in $\sSol$, and in particular $\PHhitter(\zeta_n)$, are independent,
+we know that all the local states in $\PHhitter(\zeta_n)$ are in the current state.
+In addition, we know that the state of automaton $a$ has remained unchanged, otherwise
+$\obj{a_i}{a_j}$ would have an objective child.
+Hence, the action $\zeta_n$ is playable in the current state.
+We apply this action, modifying the state of $a$ to $a_j$ and continue to the next stage.
+At the end, this recursive procedures builds a scenario from $s\subset\ctx$ to a state containing $p$.
 
@@
   if the LCG $\cwB$ contains no cycle,
-  all objective nodes have at least one child,
-  and all the synchronisations are independent,
-  then $\uconcr(\w) \neq \emptyset$.
+  all nodes in $\Obj$ have at least one child,
+  and all nodes in $\sSol$ are independent,
+  then for any state $s\in\PHl$ such that $s\subset\ctx$,
+  there exists a scenario $\delta\in\Sce$ with $p\in s\play\delta$.
 \end{theorem}
@@
 
-\modMF{
-We note furthermore that in the case where
-the method developed in this section is not conclusive,
-it is possible to compute only a subset of $\Bv \cap \Sol$,
-by removing some solutions from the initial graph of local causality $\myB$,
-or by removing them from the saturated graph of local causality $\cwB$ and by trimming it.
-In other words, this consists in ignoring some of the bounce sequences
-for some of the objectives,
-which intuitively cannot create false positives.
-Indeed, \pref{th:approxinf} is then still valid on the partial graph obtained,
-and this removal can lead to more conclusiveness by trimming parts of the graph
-that were not necessary for the reachability
-(especially cycles or unnecessary but inconclusive branches).
-If one wants to try each possible subset of solutions,
-then the overall method turns out to be exponential
-in the number of solutions to each objective.
-}
+We note furthermore that the method does not require any completeness of the bounce sequences
+$\BS$.
+Therefore, in order to reduce the number of bounce sequences to consider, and potentially removing
+cycles and non-satisfying nodes,
+one can consider only a sub-set of, or single, bounce sequences for each objectives.
+However, such an approach would imply to enumerate all possible combinations of bounce sequences
+subsets, hence being exponential in the number of objectives having at least two bounce sequences.
 
@@
 In this section, we briefly explain an alternative sufficient condition that
-progressively takes into account the successive objectives, instead of
-considering all of them at a time, as it is done in \pref{ssec:ua}.
-Because objectives are taken into account individually, such an approach
-considers only a subset of scenarios.
-However, because each iteration focuses on a smaller part of the network, this
-sequential under-approximation may be more conclusive.
+can be applied when looking for scenarios that successively reach a sequence of local states (e.g.,
+first reach $a_j$, then later $b_k$, \ldots).
 
-Let us define a sequence of objectives $\w=\obj{a_i}{a_j}\concat\w'$ with
-$a_i\neq a_j$ and a state $s\in \PHl$ with $\get{s}{a}=a_i$.
-One can remark that any scenario reaching $a_j$ necessarily includes one of the
-bounce sequences in $\BS(\obj{a_i}{a_j})$, and, in particular,
-any minimal scenario reaching $a_j$ ends in a state where $a_j$ is present but
-also the hitters of the last bounce of one bounce sequence in $\BS(\obj{a_i}{a_j})$.
-\pref{def:lastprocs} defines $\lastprocs(\obj{a_i}{a_j})$ as the set of set of
-local states that may be present just after reaching $a_j$.
+The approach proposed in this sub-section essentially applies the previous under-approximation for
+the first local states, and then computes a set of contexts that may be considered as the starting
+point for the next local states.
+In that way, the local states to reach are taken into account separately, which implies that only a
+subset of scenarios can be captured.
+%However, because each iteration focuses on a smaller part of the network, this
+%sequential under-approximation may be more conclusive.
 
-\begin{definition}[$\lastprocs : \Obj\to\Sol$]
-\label{def:lastprocs}
-  Given an objective $\obj{a_i}{a_j} \in \Obj$, $\lastprocs(\obj{a_i}{a_j})$ is
-  defined as the largest set such that, $\forall ps\in\lastprocs(\obj{a_i}{a_j})$, 
-  $ps\in\sSol$,
-  \begin{enumerate}
-    \item $a_j \in ps$;
-    \item $\exists \zeta \in \BS(\obj{a_i}{a_j}),
-      \hitter{\zeta_{\card{\zeta}}} \subseteq ps$;
-    \item $\nexists ps' \in \lastprocs(\obj{a_i}{a_j}),
-      ps' \subset ps \wedge ps' \neq ps$.
-  \end{enumerate}
-\end{definition}
-
-\todo{integrate}
-We also extend the override operator to contexts (\pref{def:ctxcap}).
-\begin{definition}[$\Cap: \Ctx \times \powerset(\PHproc) \rightarrow \Ctx$]
-\label{def:ctxcap}
-  For any $\ctx\in\Ctx$ and set of local states $ps \in \powerset(\PHproc)$,
-  the override of $\ctx$ by $ps$ is noted $\ctx \Cap ps$ and is defined by:
-  \[ \forall a \in \PHs, \PHget{(\ctx \Cap ps)}{a} \DEF
-  \begin{cases}
-    \{ p \in ps \mid \PHsort(p)=a \} & \text{if } \exists p \in ps, \PHsort(p)=a,\\
-    \PHget{\ctx}{a} & \text{else.}
-  \end{cases}
-  \]
-\end{definition}
-
-From \pref{th:approxinf}, we can deduce that
-for any scenario $\delta$ in $\uconcr(P)$,
-there exists a set of local states $ps\in\lastprocs(P)$
-such that $ps \subseteq (s\play\delta)$.
-Hence, if $\muconcr_{\ctx'\Cap ps}(\w')\neq\emptyset$,
-with $\ctx'=\ctx\Cap\procs(\mycwB{\ctx}{P})$,
-there exists a scenario $\delta'$ concretising $\w'$ from the
-state $(s\play\delta)$.
-Therefore, the scenario $\delta\concat\delta'$ concretises
-$\w$.
-
-\begin{theorem}[Sequential under-approximation]
-\label{thm:ordered-ua}
-Given an AAN $(\PHs; \PHl; \PHa)$,
-a context $\ctx$ and an objective sequence $\w =
-P\concat\w'\in\OS$,
-$\uconcr(P)\neq\emptyset \wedge
-	\forall ps \in\lastprocs(P),
-	\muconcr_{\ctx'\Cap ps}(\w')\neq\emptyset
-	\Longrightarrow \uconcr(\w)\neq\emptyset$,
-where $\ctx' = \ctx\Cap\procs(\mycwB{\ctx}{P})$.
-\end{theorem}
-\begin{proof}
-If $\uconcr(P)\neq\emptyset$,
-for all $s\in \PHl, s\subseteq\ctx$,
-there exists a scenario $\delta\in\uconcr(P)\cap\Sce(s)$;
-from \pref{def:lastprocs} and proof of \pref{th:approxinf},
-$\exists ps\in\lastprocs(P)$ such that
-$(s\play\delta)\subseteq\ctx'\Cap ps$.
-Hence, if $\muconcr_{\ctx'\Cap ps}(\w')\neq\emptyset$,
-there exists a scenario $\delta'\in\muconcr_{\ctx'\Cap ps}(\w')$ such that
-$\delta'\in\Sce(s\play\delta)$.
-Hence, $\delta\concat\delta'$ is a scenario playable in $s$.
-Therefore, for all $s\in \PHl, s\subseteq\ctx$, there exists a scenario
-concretising $\w$.
-Hence, $\uconcr(\w)\neq\emptyset$.
-\end{proof}
+\todo{computes possible outcomes from the LCG, gives it as context for the next stage}.
 

### 2015-02-02 parts/intro.tex
typos & update new notations

@@
 and $\segm{x}{y} = \{ x, x+1, \dots, y-1, y \}$ is the set of natural numbers from $x$ to $y$ included.
-The Cartesian product is denoted $\times$;
+The Cartesian product of sets is denoted by $\times$;
 if $z$ is a tuple of $n$ components, $\toset{z}$ denotes the corresponding set:
@@
 \paragraph*{Digraph}
-If $(V,E)$ is a directed graph, $V$ are the nodes, $E \subset V\times V$ the edges,
+If $(V,E)$ is a directed graph whose $V$ are the nodes and $E \subseteq V\times V$ the edges,
 the children of a node $n$ are given by
@@
 $\parents(n) \DEF \{ m\in N\mid (m,n)\in E\}$;
-and its descendants are give by
+and its successors are given by
 $\conn_{(V,E)}(n)$ which is the least fixed point containing $n$
 of the function
-$\f{f}\conn:\powerset(N)\to \powerset(N)$
+$\f{f}\conn:\powerset(V)\to \powerset(V)$
 with $\f{f}\conn(W) \DEF \bigcup_{m\in W} \childs(m)$.

### 2015-02-02 parts/sa.tex
typos & update new notations

@@
 $\PH = (\PHs; \PHl; \PHa)$,
-an initial state, and a local state of an automata in $\PHs$, for identifying sufficient conditions
+an initial state, and a local state of an automaton in $\PHs$, for identifying sufficient conditions
 that ensure the existence of a scenario starting from the initial state and leading to a state
@@
 objectives leading to the hitters of the actions in $\zeta$, in the same sequential order;
-the generalisation of the refinement to an objective sequence would require to consider all possible
+the generalization of the refinement to an objective sequence would require to consider all possible
 interleaving between the refinements.
@@
 n\in\indexes\zeta \}$, then $P$ is related to $\langle P, \abstr\zeta\rangle\in\Sol$
-(\pref{def:lcg}-3).
+(\pref{def:lcg}-\ref{lcg-obj-sol}).
 Given a node $\langle P,\abstr\zeta\rangle\in\cwV\cap\Sol$, for each $ps\in\abstr\zeta$,
 it is related to a node $ps\in\sSol$
-(\pref{def:lcg}-4).
+(\pref{def:lcg}-\ref{lcg-sol-sync}).
 A node $ps\in\sSol$ is then related to each $a\in\Proc$
-(\pref{def:lcg}-5).
+(\pref{def:lcg}-\ref{lcg-sync-ls}).
 Given a node $a_i\in\cwV\cap\Proc$, for each $a_j\in\ctx$ or $a_j\in\cwV\cap\Proc$,
 it is related to an objective $\obj{a_j}{a_i}$
-(\pref{def:lcg}-2).
+(\pref{def:lcg}-\ref{lcg-ls-obj}).
 Finally, given a node $\obj{a_j}{a_i}\in\cwV\cap\Obj$,
-if a local state $a_k\neq a_i$ is in its descendants (given by
+if a local state $a_k\neq a_i$ is in its successors (given by
 $\conn_{(\cwBNodes,\cwBEdges)}(\obj{a_j}{a_i})$), then
 $\obj{a_j}{a_i}$ is related to $\obj{a_k}{a_i}$ in the LCG
-(\pref{def:lcg}-6).
+(\pref{def:lcg}-\ref{lcg-conn}).
 
@@
 \}\subseteq\cwBEdges$
+\label{lcg-ls-obj}
 \item
@@
 	\{ (P,\langle P,\abstr \zeta\rangle) \mid \zeta\in\BS(P) \}\subseteq\cwBEdges$
+\label{lcg-obj-sol}
 \item
@@
 	\{ (\langle P,nls\rangle, ls) \mid ls\in nls \}\subseteq\cwBEdges$
+\label{lcg-sol-sync}
 \item
@@
 	\{ (ls, a_i) \mid a_i\in ls \}\subseteq\cwBEdges$
+\label{lcg-sync-ls}
 \item
@@
 	\{(\obj{a_i}{a_j},\obj{a_k}{a_j}) \mid a_k\neq a_j,$
+\label{lcg-conn}
 \\
@@
 $a_i\in x$, none of the other local state $b_j\in x$ have a local state of automaton $a$ different
-than $a_i$ in their descendants.
+than $a_i$ in their successors.
 This criteria ensures that once a local state in $x$ has been reached, reaching another local state
@@
 
-\begin{definition}[Independent synchronisations]
+\begin{definition}[Independent synchronizations]
 \label{def:coherent}
@@
   for each $b_j\in x, b_j\neq a_i$,
-  $a_k \in\conn_{\cwB}(x) \cap \Proc \Rightarrow a_k = a_i$.
+  $a_k \in\conn_{\cwB}(b_j) \cap \Proc \Rightarrow a_k = a_i$.
 \end{definition}
@@
 The intuition is the following.
-Given a state $s\subset\ctx$, we recursively refine the initial objective (reaching $p$ from the initial
-state) according to its children.
+Given a state $s\subset\ctx$, we recursively refine the initial objective
+(which is: reaching $p$ from the initial state) according to its children.
 As the LCG is acyclic, such a recursion always terminates, and as all the objective nodes have at
-least one child, it never get stuck.
+least one child, it never gets stuck.
 The refinement of an objective node $\obj{a_i}{a_j}$ acts as follows:
@@
 $\obj{a_i}{a_k}$ (which, by construction, is necessarily in the LCG)
-and then will refine the objective $\obj{a_k}{a_j}$.
-If the objective nodes has only nodes in $\Sol$ (bounce sequences), one is picked arbitrarily.
+and then we refine the objective $\obj{a_k}{a_j}$.
+If the objective node has only successors in $\Sol$ (bounce sequences), one is picked arbitrarily.
 If $\langle P, nls\rangle$ is the chosen node,
@@
 Hence, the action $\zeta_n$ is playable in the current state.
-We apply this action, modifying the state of $a$ to $a_j$ and continue to the next stage.
-At the end, this recursive procedures builds a scenario from $s\subset\ctx$ to a state containing $p$.
+We can thus apply this action, modifying the state of $a$ to $a_j$ and continue to the next stage.
+In the end, this recursive procedures builds a scenario from $s\subset\ctx$ to a state containing $p$.
 
@@
 cycles and non-satisfying nodes,
-one can consider only a sub-set of, or single, bounce sequences for each objectives.
+one can consider only a sub-set of bounce sequences
+(and in particular: a single bounce sequence) for each objective.
 However, such an approach would imply to enumerate all possible combinations of bounce sequences
@@
   This is due to the fact that the node $\{ a_1, b_1 \} \in \Bv \cap \sSol$
-  is not coherent because of its successor $a_0$ (and $b_0$).
+  is not independent because of its successor $a_0$ (and $b_0$).
   (However, from the inconclusiveness of \pref{th:approxinf},
@@
     \pref{th:approxinf} is inconclusive on this example as node $\{ a_1, b_1 \}$
-    is not coherent (see \pref{def:coherent}).
+    is not independent (see \pref{def:coherent}).
     Indeed, $a_0 \in \Proc$ is a successor of $\{ a_1, b_1 \}$, but $a_0 \neq a_1$
@@
 Given an initial context $\ctx$, the reachability of $s$ in $\PH$
-is equivalent to the concretisation of $\PHobjp{\reach}{0}{1}$ in $\PH'$
+is equivalent to the concretization of $\PHobjp{\reach}{0}{1}$ in $\PH'$
 from the initial context $\ctx \cup \{ \reach_0 \}$,

### 2015-02-02 parts/suppl-sa.tex
typos & update new notations

@@
 \label{suppl:demoapproxinf}
+
+\todo{Check with the new notations ($\muconcr$, $\procs$)}
 
@@
 Let $ps \in \Bv \cap \sSol$ be a set of hitters
-and suppose all of its successors are concretisable.
+and suppose all of its successors are concretizable.
 We first want to demonstrate that
@@
   \item Suppose such $\delta_n$ exists and let $q = \PHget{(s \PHplay \delta_n)}{\PHsort(p_{n+1})}$.
-    By construction, $p_{n+1} \in \Bv \cap \Proc$ is a direct successor of $ps$.
-    Furthermore, by hypothesis, $ps$ is coherent (see \pref{def:coherent}).
+    By construction, $p_{n+1} \in \Bv \cap \Proc$ is a child of $ps$.
+    Furthermore, by hypothesis, $ps$ is independent (see \pref{def:coherent}).
     This means that amongst all the successors in $\Proc$ of $p_{n+1}$,
@@
 
-  \item Suppose all successors objectives of $P$ are concretisable.
+  \item Suppose all successors objectives of $P$ are concretizable.
     If $\exists (P, Q) \in \Bee{\Obj}{\Obj}$, then by hypothesis,
@@
       $\muconcr_{s}(P) \neq \emptyset$.
-    Else, by \pref{def:maxCont}, the concretisations of the successors of $P$ require no local state of automaton $\PHsort(P)$.
+    Else, by \pref{def:lcg}-\ref{lcg-conn}, the concretizations of the successors of $P$ require no local state of automaton $\PHsort(P)$.
       Furthermore, there exists $\zeta \in \BS(P)$ so that $(P, \aZ) \in \Bee{\Obj}{\Sol}$.
@@
         By construction, there exists $A \in \Bv \cap \sSol$
-        amongst the direct successors of $\aZ$.
+        amongst the children of $\aZ$.
         By the first result of this demonstration,

### 2015-02-02 parts/sa.tex
change process name from p to u

@@
 These refinements can be summarized compactly with a so-called Local Causality Graph (LCG).
-Given an initial context $\ctx$ and a local state $p\in\Proc$,
-A LCG $\cwB = (\cwV, \cwE)$
+Given an initial context $\ctx$ and a local state $\myp\in\Proc$,
+an LCG $\cwB = (\cwV, \cwE)$
 is a digraph where $\cwV \subseteq \Proc\cup \Obj \cup \Sol \cup \sSol$ is the set of vertices
@@
 \label{def:lcg}
-Given a context $\ctx$ and a local state $p\in \Proc$,
+Given a context $\ctx$ and a local state $\myp\in \Proc$,
 the Local Causality Graph (LCG) for reachability under-approximation
@@
 \item
-$p \in \cwBNodes$
+$\myp \in \cwBNodes$
 \item
@@
 
-Given a context $\ctx$ and a local state $p\in\Proc$, the LCG $\cwB$ contains a set of objectives
-that can be used to build a concrete scenario reaching $p$.
+Given a context $\ctx$ and a local state $\myp\in\Proc$, the LCG $\cwB$ contains a set of objectives
+that can be used to build a concrete scenario reaching $\myp$.
 Because we are focused on sufficient conditions for reachability, we do not require that all
@@
 particular criteria, so-called independence, then from any state
-delimited by the context $\ctx$, there exists a scenario that reaches $p$
+delimited by the context $\ctx$, there exists a scenario that reaches $\myp$
 (\pref{th:approxinf}).
@@
 Given a state $s\subset\ctx$, we recursively refine the initial objective
-(which is: reaching $p$ from the initial state) according to its children.
+(which is: reaching $\myp$ from the initial state) according to its children.
 As the LCG is acyclic, such a recursion always terminates, and as all the objective nodes have at
@@
 We can thus apply this action, modifying the state of $a$ to $a_j$ and continue to the next stage.
-In the end, this recursive procedures builds a scenario from $s\subset\ctx$ to a state containing $p$.
+In the end, this recursive procedures builds a scenario from $s\subset\ctx$ to a state containing $\myp$.
 
@@
   then for any state $s\in\PHl$ such that $s\subset\ctx$,
-  there exists a scenario $\delta\in\Sce$ with $p\in s\play\delta$.
+  there exists a scenario $\delta\in\Sce$ with $\myp\in s\play\delta$.
 \end{theorem}

### 2015-02-03 parts/def-ph.tex
add def of support

@@
 
-Finally, a context (\pref{def:context}) extends the notion of state to a set of possible initial states:
+A context (\pref{def:context}) extends the notion of state to a set of possible initial states:
 \modMF{
@@
 
+Finally, we define the support (\pref{def:supp}) of a sequence of actions $\zeta$
+as the set containing the first local state of each automata appearing in $\zeta$,
+that is, as a hitter or as a target.
+For this, we first define the \emph{first appearance} of an automata
+in this sequence.
+
+\begin{definition}[$\supp$ \& $\first$]
+\label{def:supp}
+  For all sequences of actions $\zeta$, we define:
+  \[
+    \suppf{\zeta} = \bigcup_{a \in \PHs} \firstf{a}{\zeta}
+  \]
+  where:
+  \begin{align*}
+  \forall a \in \PHs, \firstf{a}{\zeta} &=
+    \begin{cases}
+      \emptyset &
+        \text{if } \forall n \in \indexes{\zeta},
+        B^\zeta_n \cap \PHl_a \neq \emptyset \\
+      B^\zeta_m \cap \PHl_a &
+        \text{else, if } m =
+        \min\{ n \in \indexes{\zeta} \mid B^\zeta_n \cap \PHl_a \neq \emptyset \}
+    \end{cases} \\
+  \forall n \in \indexes{\zeta}, B^\zeta_n &= \hitter{\zeta_n} \cup \{ \target{\zeta_n} \}.
+  \end{align*}
+\end{definition}
+
+We note that for all sequence of actions $\zeta$,
+$\forall a \in \PHs, 0 \leq \card{\firstf{a}{\zeta}} \leq 1$,
+because given the particular for of the actions of an AAN (see \pref{def:ph}),
+$\forall n \in \indexes{\zeta}, B_n \in \PHsublset[\PHl]$.
+This also means that: $\suppf{\zeta} \in \PHsublset[\PHl]$.
+
 \modn{

### 2015-02-03 parts/def-ph.tex
typos

@@
   introduced in~\cite{FPMR13-CS2Bio}.
-  Indeed, in the Process Hitting with at least classes of priorities
-  it is possible to use additional sorts, called “cooperative sorts”,
+  Indeed, in the Process Hitting with at least 2 classes of priorities
+  it is possible to use additional automata, called “cooperative sorts”,
   in order to model the actions of any AAN that have more than one hitter.

### 2015-02-03 parts/sa.tex
typos

@@
 \begin{lemma}
-Given a state $s\in L$ and an objective $\obj{a_i}{a_j}$ with $\get{s}{a}=a_i$,
+Given a state $s\in \PHl$ and an objective $\obj{a_i}{a_j}$ with $\get{s}{a}=a_i$,
 $\forall\delta\in\concr(\obj{a_i}{a_j})$,
@@
   in this paper only allowed to represent “over-approximated” Boolean gates
-  with the use of cooperative sorts.
+  with the use of so-called cooperative sorts.
   This especially did not allow to model the fact that $a_1$ and $b_1$ could not

### 2015-02-03 parts/def-ph.tex
remove \mod commands

@@
 
-\modn{
 We consider an AAN (\pref{def:ph})
@@
 of exactly one local state from each automata.
-}
 
-\modn{
 The concurrent interactions between local states are defined by a set of \emph{actions}.
@@
 and can be referred to as $\PHhitter(h), \PHtarget(h), \PHbounce(h)$, respectively.
-}
 
@@
 A context (\pref{def:context}) extends the notion of state to a set of possible initial states:
-\modMF{
 to each automaton in the model, a context maps a set of local states in this automaton.
-}
 \begin{definition}[Context ($\Ctx$)]
@@
 
-\modn{
 \begin{remark}[Comparison with the Process Hitting]
@@
 \end{remark}
-}

### 2015-02-03 parts/example.tex
typos & update new notations
remove \mod commands

@@
 
-\modMF{
 This section aims at giving application examples of the static analysis method
@@
 in order to show the scalability of our method.
-}
 
@@
 
-\modMF{
+\todo{Check section and remove $\procs$ and $\lastprocs$.}
+
 We give in this section a detailed example of the use of classes of priorities
@@
 because the considered model contains 2 classes of priorities.
-}
 
@@
 The actions of the original model make $2$ classes of priorities, as represented in \pref{fig:metazoan-php}:
-\modMF{%
 \begin{align*}
@@
 while the evolution of $a$ has to follow the changes of $c$.
-}%
 
@@
 \pref{fig:metazoan-ph} gives the flattening of this model,
-\modMF{
 that is, an AAN with the equivalent dynamics
@@
 in order to model the preemption of the actions in $\ov{\PHh}^{(1)}$.
-}%
 
@@
 
-\modMF{
 Finally, the static analysis results presented in
@@
 because they have the same dynamics (given \pref{th:bisimPHP}).
-}
-
-% $\w = \PHobj{a_0}{a_1} \PHconcat \PHobj{c_0}{c_1} \PHconcat \PHobj{a_1}{a_0} \PHconcat \PHobj{c_1}{c_0}$.
-% Rather than checking this whole objective sequence,
-% we decompose it into the following ones:
-% \begin{align*}
-%   \ctx^1 &= \PHstate{f_1, a_0, c_0} \text{ and } P_1 = \PHobj{a_0}{a_1} &
-%   \ctx^3 &= \PHstate{f_1, a_1, c_1} \text{ and } P_2 = \PHobj{a_1}{a_0} \\
-%   \ctx^2 &= \PHstate{f_1, a_1, c_0} \text{ and } P_3 = \PHobj{c_0}{c_1} &
-%   \ctx^4 &= \PHstate{f_1, a_0, c_1} \text{ and } P_4 = \PHobj{c_1}{c_0}
-% \end{align*}
-% Given \pref{th:approxinf}, we have: $\forall i \in \segm{1}{4}, \muconcr_{\ctx^i}(P_i) \neq \emptyset$.
-% Finally, after checking that it can be applied for $i = 3$ down to $i = 1$,
-% \pref{thm:ordered-ua} gives: $\uconcr(\w) \neq \emptyset$.
-% Thus the model is functional.
 
@@
     and the context $\PHstate{a_0, c_1, f_1}$.
-%     Rectangular nodes containing a single local state are elements in $\Proc$,
-%     borderless nodes containing a couple of local states are elements in $\Obj$
-%     and circle nodes are elements in $\Sol$.
-%     \pref{th:approxinf} is inconclusive on this example as edge $(ab_{11}, \{ a_1, b_1 \}) \in \Proc \times \Sol$ (here represented with a double line) is not coherent (\pref{def:coherent}).
-%     Indeed, $a_0 \in \Proc$ is a child of $\{ a_1, b_1 \}$, but $a_0 \neq a_1$ (and the same also stands for $b_0$).
   }
@@
 \url{http://maxime.folschette.name/underapprox-tcrsig94.zip}.}.
-\modn{%
 Logical Networks being a subclass of AANs, this translation is straightforward.
-}%
 Then, we verified the reachability for the independent activation of 4 outputs of the signalling
@@
 
-\modMF{
 By analysing the detail of the results, one can find out that one of the outputs, NFkB, can never be activated.
@@
 it is possible to reach a state where SRE, AP1 and NFAT are simultaneously active.
-}
 
@@
 However, due to the large scale of the model, the program runs out of memory for all the experiments,
-\modn{%
 showing that this method is not scalable.
@@
 even by orders of magnitude.
-}%
-%---~that is, containing thousands of components.
 
-\modMF{
 Finally, we note that similar experiments were conducted in~\cite{PMR12-MSCS}.
@@
 which was originally described in a format equivalent to Logical Networks.
-}
 

### 2015-02-03 parts/intro.tex
remove \mod commands

@@
 
-\modn{
 The approach used in this paper, however,
@@
 but can also model preemptions between evolutions branches.
-}
 
@@
 \subsection*{Contributions}
-\modn{
 This paper is an extension of~\cite{FPMR13-CS2Bio}.
@@
 thus overtaking the efficiency of usual model-checkers.
-}
 
-\modn{
 AANs (and, a fortiori, their restriction, the Process Hitting)
@@
 of application of our method to AANs with classes of priorities.
-}
 
-\modn{
 \pref{sec:ph} presents the Asynchronous Automata Networks (AANs)
@@
 and \pref{sec:ccl} gives a conclusion and a discussion about our work.
-}
 
-\modn{
 The main additions in this paper compared to~\cite{FPMR13-CS2Bio} are
@@
 the range of applicability of the results.
-}
 

### 2015-02-03 parts/sa.tex
remove \mod commands

@@
 
-\modLP{%
 We present a static analysis that takes as input an AAN
@@
 that ensure the existence of a scenario starting from the initial state and leading to a state
-where the given local state is present.}
+where the given local state is present.
 
@@
 
-\begin{comment}
-\todo{revise}
-In the following, we denote: $\sSol = \powerset(\PHproc)$
-\moda{%
-and $\Sol = \powerset(\sSol)$.
-}%
-\modMF{%
-The elements of $\sSol$ are sets of local states,
-and will later represent sets of hitters of a given action
-that are required to be active simultaneously in order to play this related action.
-The elements in $\Sol$ are sets of sets of hitters,
-and represent the requirements to play a whole bounce sequence.
-}%
-
-\begin{definition}[$\aBS:\Obj \rightarrow \powerset(\Sol)$]
-\label{def:aBS}
-  The \emph{abstractions of bounce sequences} of an objective $P$, denoted by the set $\aBS(P)$, are the minimal sets of hitters of the bounce sequences solving $P$:
-  \[
-    \aBS(P) \DEF \{ \abstr{\zeta} \in \Sol \mid
-      \zeta \in \BS(P) \wedge
-      \nexists \zeta' \in \BS(P), \abstr{\zeta'} \subsetneq \abstr{\zeta} \} \enspace,
-  \]
-  \modMF{
-  where $\forall P \in \Obj, \forall \zeta \in \BS(P)$:
-  $\abstr{\zeta} \DEF \{ \PHhitter(\zeta_n) \mid n \in \indexes{\zeta} \} \setminus \emptyset$.
-  }%
-
-  \noindent
-  \modMF{
-  As a consequence,
-  $\aBS(\obj{a_i}{a_j}) = \emptyset$ if $\BS(\obj{a_i}{a_j}) = \emptyset$,
-  and $\BS(\obj{a_i}{a_i}) = \{ \emptyset \}$.
-  }%
-\end{definition}
-\end{comment}
-
 \subsubsection{Local Causality Graph}
@@
 
-\modMF{
 Regarding the complexity of the method,
@@
 each component usually contains a limited number of expression levels.
-}
 
@@
 \begin{example}
-  \moda{%
   If we confider the AAN of \pref{fig:ph-livelock},
@@
   with over-approximation methods developed in~\cite{PMR12-MSCS}.)
-  }%
 
-  \modMF{%
   This result is new compared to the method proposed in~\cite{PMR12-MSCS}.
@@
   contrary to the behaviour expected from an accurate Boolean gate.
-  }%
 
-  \moda{%
   Finally, we note however that,
@@
   for a detailed conclusive example.
-  }%
 
@@
 
-\modMF{
 \subsection{Extraction of a Scenario}
 \label{ssec:concret}
-}
 
-\modMF{
 This section gives a recursive method to find a scenario that concretizes
@@
 of these theorems.
-}
 
@@
 
-\modMF{%
 First, $\osres$ is used to split the objective sequence $\w$ to solve,
@@
 and all possible bounce sequences $\zeta \in \BS(P)$ that are chosen during the resolution.
-}%
 
@@
 \label{def:concret}
-\modMF{%
 For all $s \in \PHl$ and $\w \in \OS$, we define:
@@
 is a sequence containing all hitters of $h$ in an arbitrary order.
-}
 \end{definition}

### 2015-02-03 parts/sa.tex
add new extraction algorithm

@@
 This section gives a recursive method to find a scenario that concretizes
-a given objective sequence $\w \in \OS$.
-All the definitions above are well-defined provided that
-$\uconcr(\w)\neq\emptyset$,
-which can be demonstrated by \pref{th:approxinf} or \pref{thm:ordered-ua}.
-The justification of these definitions can be found by analysing the demonstrations
-of these theorems.
+the reachability of a given local state $\myp \in \Proc$,
+from a given initial state $s_0 \in \PHl$,
+provided that \pref{th:approxinf} answered positively
+for a context $\ctx \in \Ctx$ so that $s_0 \subset \ctx$.
+The algorithm proposed in the following relies on a traversal of the Local Causality Graph
+$\cwB$ that has been used for this conclusion.
+The correctness of this extraction can be demonstrated
+in the same fashion as \pref{th:approxinf}.
 
-\newcommand{\res}{\mathbf{res}}
-\newcommand{\osres}{\mathbf{OSres}}
-\newcommand{\autoBS}{\mathbf{autoBS}}
-\newcommand{\rec}{\mathbf{rec}}
-% \newcommand{\thisobj}[1]{P_{#1}}
-% \newcommand{\thisseq}[1]{\Theta_{#1}}
-\newcommand{\thisobj}{P}
-\newcommand{\thisseq}{\Theta}
-\newcommand{\R}{R}
+This algorithm consists in visiting all required nodes in a given order,
+to build a sequence of actions that concretizes the objective.
+The actions to perform on a given node,
+listed below,
+depend on the current state, the type of node, the markers on this node
+and the state of the traversal which can be either “descending” (D) or “ascending” (A).
+Nodes in $\Sol$ can be marked with a sequence of actions
+and nodes in $\sSol$ can be marked with a set of local states.
+The traversal starts in node $\myp$ in descending mode,
+the starting state is $s = s_0$
+and the initial output is the empty sequence $\emptyseq$.
 
-First, $\osres$ is used to split the objective sequence $\w$ to solve,
-by considering successive objectives, in the fashion of \pref{thm:ordered-ua}.
-This function calls $\res$ which allows to solve an objective $P$
-by either re-target it (if $\gCont(\PHsort(P), P) \neq \emptyset$)
-of by searching for a solution to this objective in $\BS(P)$.
-This search may require to try several objective sequences $\zeta \in \BS(P)$.
-For each trial, the chosen objective sequence $\zeta$ is solved with $\rec$,
-which recursively created a scenario to play the whole sequence.
-This scenario is itself recursively created by combining
-smaller scenarios allowing to reach each required hitter of each action
-with the function $\thisseq$.
-Finally, $\thisseq$ calls $\res$ anew to reach the hitters
-that are necessarily contained in other automata.
-In the end, a scenario can be obtained by analysing all values of
-$\osres_s(\w)$ (\pref{def:concret})
-for all possible initial state $s \subseteq \ctx$ in the considered context,
-and all possible bounce sequences $\zeta \in \BS(P)$ that are chosen during the resolution.
+\begin{itemize}
+  \item In a node $a_k \in \Proc$:
+    \begin{itemize}
+      \item[D)] Descend in the node $\PHobj{\PHget{s}{a}}{a_k} \in \Obj$.
+      \item[A)] Ascend in the parent $\sSol$ node, if any,
+        and remove the element $a_k$ from its marking set.
+        If the node has no $\sSol$ parent, the traversal is complete
+        and the output of the algorithm is the current output.
+    \end{itemize}
 
-\begin{definition}[$\osres : \PHl \times \OS \to \Sce$]
-\label{def:concret}
-For all $s \in \PHl$ and $\w \in \OS$, we define:
-\[
-  \osres_s(\w) \DEF
-    \begin{cases}
-      \emptyseq
-        & \text{ if $\w = \emptyseq$} \\
-      \res_s(\w_1) \concat
-      \osres_{s \play \res_s(\w_1)}(\w_2 \concat \dots \concat \w_{\card{\w}})
-        & \text{ otherwise} \\
-    \end{cases}
-\]
-and, for all $s \in \PHl$ and $P \in \Obj$:
-\[\res_s(P) \DEF
-  \begin{cases}
-    \varepsilon
-      & \text{if } \target{P} = \bounce{P} \\
-    \osres_s(P^Q \concat Q)
-      & \text{if } \exists Q \in \Obj, (P, Q) \in \Bee{\Obj}{\Obj} \\
-    \rec_s(\zeta)
-      & \text{otherwise, with } \zeta \in \BS(P)
-  \end{cases}
-\]
-with $P^Q = \PHobj{\PHtarget(P)}{\PHtarget(Q)}$.
-Furthermore:
-\begin{align*}
-  \forall \zeta \in \BS,
-  \rec_s(\zeta) &\DEF
-    \begin{cases}
-      \emptyseq
-        & \text{ if $\zeta = \emptyseq$} \\
-      \thisseq_s(\zeta_1) \concat \zeta_1 \concat
-      \rec_{s \play \thisseq_s(\zeta_1) \concat \zeta_1}
-      (\zeta_2 \concat \dots \concat \zeta_{\card{\zeta}})
-        & \text{ otherwise}
-    \end{cases} \\
-  \forall h \in \PHh,
-  \thisseq_s(h) &\DEF
-    \begin{cases}
-      \emptyseq
-        & \text{ if $\hitter{h} = \emptyset$} \\
-      \R_s(h_1) \concat \thisseq_{s \play \R_s(h_1)}(h_2 \concat \dots \concat h_{\card{h}})
-        & \text{ otherwise}
-    \end{cases} \\
-  \forall a_i \in \Proc,
-  \R_s(a_i) &\DEF \res_s(\PHobj{\PHget{s}{\PHsort(a_i)}}{a_i})
-\end{align*}
-and for all action $h \in \PHh$, $(h_i)_{i \in \segm{1}{\card{\hitter{h}}}}$
-is a sequence containing all hitters of $h$ in an arbitrary order.
-\end{definition}
+  \item In a node $\PHobj{a_j}{a_k} \in \Obj$:
+    \begin{itemize}
+      \item[D)] Descend in an arbitrarily chosen $\sSol$ node,
+        and mark it with a sequence $\zeta \in \BS$ so that $\abstr{\zeta} = pps$.
+      \item[A)] Ascend in the parent $\Proc$ or $\Obj$ node.
+    \end{itemize}
+
+  \item In a node $pps \in \Sol$ with the current marking $\zeta$:
+    \begin{itemize}
+      \item If $\zeta \neq \emptyseq$,
+        descend in the node $ps \in \sSol$
+        so that $ps = \hitter{\zeta_1}$
+        and mark it with the set $ps$.
+      \item If $\zeta = \emptyseq$,
+        ascend in the parent $\Obj$ node and carry on ascending.
+    \end{itemize}
+
+  \item In a $\sSol$ node with the current marking $m$:
+    \begin{itemize}
+      \item If $m \neq \emptyset$,
+        descend in a child node $a_k \in \Proc$ arbitrarily chosen,
+        so that $a_k \in m$ and carry on descending.
+      \item If $m = \emptyset$,
+        ascend in the parent $\sSol$ node.
+        Let $\zeta$ be the current marking of this node.
+        If $\zeta_1$ is playable in $s$:
+          append $\zeta_1$ to the output,
+          change the current state to $s \play \zeta_1$
+          and mark this node with $\zeta_{2..|\zeta|}$.
+        If $\zeta_1$ is not playable
+        (which means that $\target{\zeta_1}$ has changed):
+          go to the node $\PHobj{\PHget{s}{\PHsort(\bounce{\zeta_1})}}{\bounce{\zeta_1}} \in \Obj$
+          and start descending.
+    \end{itemize}
+\end{itemize}
+
+% * On applique les règles suivants de parcours où, à tout moment, s représente l'état courant, et l'état du parcours peut être « en descente » ou « en montée » :
+% 
+% - Dans un nœud a_k \in LS :
+%   - Si en cours de descente, descendre dans le nœud s[a] />* a_k \in Obj.
+%   - Si en cours de remontée, monter dans le nœud Sol parent et enlever l'élément a_k de son marquage.
+% 
+% - Dans un nœud a_j />* a_k \in Obj :
+%   - Si en cours de descente, descendre dans un nœud pps \in NSol au choix. Marquer ce nœud avec une séquence \zeta \in BS tq \zeta^ = pps.
+%   - Si en cours de remontée, monter dans le nœud LS ou Obj parent.
+% 
+% - Dans un nœud pps \in NSol (marqué par \zeta) :
+%   - Si \zeta ≠ \emptyseq, descendre dans le nœud ps \in Sol tq ps = hitters(\zeta_1). Marquer le nœud ps par l'ensemble ps.
+%   - Si \zeta = \emptyseq, alors remonter dans le nœud Obj parent et continuer la remontée.
+% 
+% - Dans un nœud Sol marqué par m :
+%   - Si m ≠ \emptyset, alors descendre dans un des nœuds fils a_k \in LS tq a_k \in m.
+%   - Si m = \emptyset, alors remonter dans le nœud NSol parent, marqué par \zeta.
+Si \zeta_1 est jouable, jouer cette action et marquer le nœud par \zeta_{2..|\zeta|}.
+Si \zeta_1 n'est pas jouable (c.-à-d.
+si target(\zeta_1) a changé), aller au nœud s[sort(bounce(\zeta_1))] />* bounce(\zeta_1) \in Obj et commencer une descente.
+
+%%%%%%%%% Tnetative 1 %%%%%%%%%%%%%%%%%%%%%
+% 
+% \newcommand{\res}{\mathbf{res}}
+% \newcommand{\osres}{\mathbf{OSres}}
+% \newcommand{\autoBS}{\mathbf{autoBS}}
+% \newcommand{\rec}{\mathbf{rec}}
+% % \newcommand{\thisobj}[1]{P_{#1}}
+% % \newcommand{\thisseq}[1]{\Theta_{#1}}
+% \newcommand{\thisobj}{P}
+% \newcommand{\thisseq}{\Theta}
+% \newcommand{\R}{R}
+% 
+% First, $\osres$ is used to split the objective sequence $\w$ to solve,
+% by considering successive objectives, in the fashion of \pref{thm:ordered-ua}.
+% This function calls $\res$ which allows to solve an objective $P$
+% by either re-target it (if $\gCont(\PHsort(P), P) \neq \emptyset$)
+% of by searching for a solution to this objective in $\BS(P)$.
+% This search may require to try several objective sequences $\zeta \in \BS(P)$.
+% For each trial, the chosen objective sequence $\zeta$ is solved with $\rec$,
+% which recursively created a scenario to play the whole sequence.
+% This scenario is itself recursively created by combining
+% smaller scenarios allowing to reach each required hitter of each action
+% with the function $\thisseq$.
+% Finally, $\thisseq$ calls $\res$ anew to reach the hitters
+% that are necessarily contained in other automata.
+% In the end, a scenario can be obtained by analysing all values of
+% $\osres_s(\w)$ (\pref{def:concret})
+% for all possible initial state $s \subseteq \ctx$ in the considered context,
+% and all possible bounce sequences $\zeta \in \BS(P)$ that are chosen during the resolution.
+% 
+% \begin{definition}[$\osres : \PHl \times \OS \to \Sce$]
+% \label{def:concret}
+% For all $s \in \PHl$ and $\w \in \OS$, we define:
+% \[
+%   \osres_s(\w) \DEF
+%     \begin{cases}
+%       \emptyseq
+%         & \text{ if $\w = \emptyseq$} \\
+%       \res_s(\w_1) \concat
+%       \osres_{s \play \res_s(\w_1)}(\w_2 \concat \dots \concat \w_{\card{\w}})
+%         & \text{ otherwise} \\
+%     \end{cases}
+% \]
+% and, for all $s \in \PHl$ and $P \in \Obj$:
+% \[\res_s(P) \DEF
+%   \begin{cases}
+%     \varepsilon
+%       & \text{if } \target{P} = \bounce{P} \\
+%     \osres_s(P^Q \concat Q)
+%       & \text{if } \exists Q \in \Obj, (P, Q) \in \Bee{\Obj}{\Obj} \\
+%     \rec_s(\zeta)
+%       & \text{otherwise, with } \zeta \in \BS(P)
+%   \end{cases}
+% \]
+% with $P^Q = \PHobj{\PHtarget(P)}{\PHtarget(Q)}$.
+% Furthermore:
+% \begin{align*}
+%   \forall \zeta \in \BS,
+%   \rec_s(\zeta) &\DEF
+%     \begin{cases}
+%       \emptyseq
+%         & \text{ if $\zeta = \emptyseq$} \\
+%       \thisseq_s(\zeta_1) \concat \zeta_1 \concat
+%       \rec_{s \play \thisseq_s(\zeta_1) \concat \zeta_1}
+%       (\zeta_2 \concat \dots \concat \zeta_{\card{\zeta}})
+%         & \text{ otherwise}
+%     \end{cases} \\
+%   \forall h \in \PHh,
+%   \thisseq_s(h) &\DEF
+%     \begin{cases}
+%       \emptyseq
+%         & \text{ if $\hitter{h} = \emptyset$} \\
+%       \R_s(h_1) \concat \thisseq_{s \play \R_s(h_1)}(h_2 \concat \dots \concat h_{\card{h}})
+%         & \text{ otherwise}
+%     \end{cases} \\
+%   \forall a_i \in \Proc,
+%   \R_s(a_i) &\DEF \res_s(\PHobj{\PHget{s}{\PHsort(a_i)}}{a_i})
+% \end{align*}
+% and for all action $h \in \PHh$, $(h_i)_{i \in \segm{1}{\card{\hitter{h}}}}$
+% is a sequence containing all hitters of $h$ in an arbitrary order.
+% \end{definition}
+
+%%%%%%%% Tentative 2 %%%%%%%%%%%%%%%%%%%%%%%
+% % \newcommand{\resP}{\mathbf{\Obj res}}
+% % \newcommand{\resOS}{\mathbf{\OS res}}
+% \newcommand{\resP}{\mathsf{res}^\Obj}
+% \newcommand{\resOS}{\mathsf{res}^\OS}
+% 
+% \newcommand{\res}{\mathbf{res}}
+% \newcommand{\autoBS}{\mathbf{autoBS}}
+% \newcommand{\rec}{\mathbf{rec}}
+% 
+% Pour tout objectif $P$ dans $\cwB$,
+% on note $X_P$ une séquence d'objectifs obtenue en effectuant
+% un parcours en profondeur d'abord de $\cwB$.
+% Un tel parcours existe car $\cwB$ ne comporte pas de cycle.
+% 
+% $$\res_s(\w) = \resOS_s((X_{\w_i})_{i \in \indexes{\w}})$$
+% 
+% \[
+%   \resOS_s(\w) \DEF
+%     \begin{cases}
+%       \emptyseq
+%         & \text{ if $\w = \emptyseq$} \\
+%       \resP_s(\w_1) \concat
+%       \resOS_{s \play \resP_s(\w_1)}(\w_{2..\card{\w}})
+%         & \text{ otherwise} \\
+%     \end{cases}
+% \]
+% 
+% $
+% \resP_s(\PHobj{a_j}{a_k}) \DEF
+%   \todo{resP}$
+% 
+% % $\resP_s(P) \DEF
+% %     \begin{cases}
+% %       \emptyseq
+% %         & \text{ if $P$ is trivial} \\
+% %       \res_s(\w_1) \concat
+% %       \osres_{s \play \res_s(\w_1)}(\w_2 \concat \dots \concat \w_{\card{\w}})
+% %         & \text{ otherwise} \\
+% %     \end{cases}$
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-02-04 parts/sa.tex
remove comments
change order of subsections in section 3 (extraction; successive reachability; simultaneous reachability)
minor fixes
ls/nls -> ps/pps

@@
 $a_i\in\cwBNodes\cap\Proc \Leftrightarrow \{ (a_i,\obj{a_j}{a_i}) \mid
-a_j\in\ctx \vee a_j\in\cwBNodes\cap\Proc)
+a_j \neq \myp \wedge (a_j\in\ctx \vee a_j\in\cwBNodes\cap\Proc)
 \}\subseteq\cwBEdges$
@@
 \item
-$\langle P, nls \rangle\in\cwBNodes\cap\NSol \Leftrightarrow
-	\{ (\langle P,nls\rangle, ls) \mid ls\in nls \}\subseteq\cwBEdges$
+$\langle P, pps \rangle\in\cwBNodes\cap\NSol \Leftrightarrow
+	\{ (\langle P,pps\rangle, ps) \mid ps\in pps \}\subseteq\cwBEdges$
 \label{lcg-sol-sync}
 \item
-$ls \in\cwBNodes\cap\sSol \Leftrightarrow
-	\{ (ls, a_i) \mid a_i\in ls \}\subseteq\cwBEdges$
+$ps \in\cwBNodes\cap\sSol \Leftrightarrow
+	\{ (ps, a_i) \mid a_i\in ps \}\subseteq\cwBEdges$
 \label{lcg-sync-ls}
@@
 \hspace*{4cm}
-$\zeta\in\BS(\obj{a_i}{a_j}) \}\subset\cwBEdges$
+$\zeta\in\BS(\obj{a_i}{a_j}) \}\subseteq\cwBEdges$
 \end{enumerate}
@@
 If the objective node has only successors in $\Sol$ (bounce sequences), one is picked arbitrarily.
-If $\langle P, nls\rangle$ is the chosen node,
-by construction there exists $\zeta\in\BS(P)$ such that $\abstr\zeta = nls \in \powerset(\sSol)$.
+If $\langle P, pps\rangle$ is the chosen node,
+by construction there exists $\zeta\in\BS(P)$ such that $\abstr\zeta = pps \in \powerset(\sSol)$.
 If $\zeta = \emptyseq$ (for instance in the case when $a_i = a_j$), the recursion stops and we
@@
 
-\subsection{Reachability of a State}
-\label{ssec:simult-ua}
-
-\newcommand{\total}{\tau}
-\newcommand{\reach}{\sigma}
-
-The reachability property studied so far concerns a single local state at a time.
-However, we remark that the reachability of a global state or a sub-state can be
-addressed with the very same analysis by introducing a dedicated automata.
-Such analysis was not possible with the Process Hitting framework,
-because of the lack of the notion of simultaneity for more than two components.
-
-In order to check the reachability of a global state $s \in \PHl$,
-let $\PH = (\PHs, \PHl, \PHh)$ be an AAN.
-We define a new AAN $\PH' = (\PHs', \PHl', \PHh')$ with:
-$\PHs' = \PHs \cup \{ \reach \}$, $\PHl' = \PHl \times \PHl_\reach$,
-where $\PHl_\reach = \{ \reach_0, \reach_1 \}$,
-and $\PHh' = \PHh \cup \{ \PHhit{\toset{s}}{\reach_0}{\reach_1} \}$.
-Given an initial context $\ctx$, the reachability of $s$ in $\PH$
-is equivalent to the concretization of $\PHobjp{\reach}{0}{1}$ in $\PH'$
-from the initial context $\ctx \cup \{ \reach_0 \}$,
-which can be efficiently under-approximated using \pref{th:approxinf}.
-
-It is of course also possible to compute the reachability
-of a sub-state $s \in \PHsubl[\PHl]_S$ of a set of components $S \subseteq \PHs$
-with the same method.
-One can also check the reachability of a set of states $\Lambda \subseteq \PHl$
-by creating several actions
-$\PHhit{\toset{s}}{\reach_0}{\reach_1}$ in $\PHh$ for each state $s \in \Lambda$.
-
-\subsection{Sequential Under-approximation}
-\label{ssec:ordered-ua}
-
-In this section, we briefly explain an alternative sufficient condition that
-can be applied when looking for scenarios that successively reach a sequence of local states (e.g.,
-first reach $a_j$, then later $b_k$, \ldots).
-
-The approach proposed in this sub-section essentially applies the previous under-approximation for
-the first local states, and then computes a set of contexts that may be considered as the starting
-point for the next local states.
-In that way, the local states to reach are taken into account separately, which implies that only a
-subset of scenarios can be captured.
-%However, because each iteration focuses on a smaller part of the network, this
-%sequential under-approximation may be more conclusive.
-
-\todo{computes possible outcomes from the LCG, gives it as context for the next stage}.
-
 \subsection{Extraction of a Scenario}
@@
       \item If $m = \emptyset$,
-        ascend in the parent $\sSol$ node.
+        ascend in the parent $\Sol$ node.
         Let $\zeta$ be the current marking of this node.
@@
 
-% * On applique les règles suivants de parcours où, à tout moment, s représente l'état courant, et l'état du parcours peut être « en descente » ou « en montée » :
-% 
-% - Dans un nœud a_k \in LS :
-%   - Si en cours de descente, descendre dans le nœud s[a] />* a_k \in Obj.
-%   - Si en cours de remontée, monter dans le nœud Sol parent et enlever l'élément a_k de son marquage.
-% 
-% - Dans un nœud a_j />* a_k \in Obj :
-%   - Si en cours de descente, descendre dans un nœud pps \in NSol au choix. Marquer ce nœud avec une séquence \zeta \in BS tq \zeta^ = pps.
-%   - Si en cours de remontée, monter dans le nœud LS ou Obj parent.
-% 
-% - Dans un nœud pps \in NSol (marqué par \zeta) :
-%   - Si \zeta ≠ \emptyseq, descendre dans le nœud ps \in Sol tq ps = hitters(\zeta_1). Marquer le nœud ps par l'ensemble ps.
-%   - Si \zeta = \emptyseq, alors remonter dans le nœud Obj parent et continuer la remontée.
-% 
-% - Dans un nœud Sol marqué par m :
-%   - Si m ≠ \emptyset, alors descendre dans un des nœuds fils a_k \in LS tq a_k \in m.
-%   - Si m = \emptyset, alors remonter dans le nœud NSol parent, marqué par \zeta.
-Si \zeta_1 est jouable, jouer cette action et marquer le nœud par \zeta_{2..|\zeta|}.
-Si \zeta_1 n'est pas jouable (c.-à-d.
-si target(\zeta_1) a changé), aller au nœud s[sort(bounce(\zeta_1))] />* bounce(\zeta_1) \in Obj et commencer une descente.
+\subsection{Sequential Under-approximation}
+\label{ssec:ordered-ua}
 
-%%%%%%%%% Tnetative 1 %%%%%%%%%%%%%%%%%%%%%
-% 
-% \newcommand{\res}{\mathbf{res}}
-% \newcommand{\osres}{\mathbf{OSres}}
-% \newcommand{\autoBS}{\mathbf{autoBS}}
-% \newcommand{\rec}{\mathbf{rec}}
-% % \newcommand{\thisobj}[1]{P_{#1}}
-% % \newcommand{\thisseq}[1]{\Theta_{#1}}
-% \newcommand{\thisobj}{P}
-% \newcommand{\thisseq}{\Theta}
-% \newcommand{\R}{R}
-% 
-% First, $\osres$ is used to split the objective sequence $\w$ to solve,
-% by considering successive objectives, in the fashion of \pref{thm:ordered-ua}.
-% This function calls $\res$ which allows to solve an objective $P$
-% by either re-target it (if $\gCont(\PHsort(P), P) \neq \emptyset$)
-% of by searching for a solution to this objective in $\BS(P)$.
-% This search may require to try several objective sequences $\zeta \in \BS(P)$.
-% For each trial, the chosen objective sequence $\zeta$ is solved with $\rec$,
-% which recursively created a scenario to play the whole sequence.
-% This scenario is itself recursively created by combining
-% smaller scenarios allowing to reach each required hitter of each action
-% with the function $\thisseq$.
-% Finally, $\thisseq$ calls $\res$ anew to reach the hitters
-% that are necessarily contained in other automata.
-% In the end, a scenario can be obtained by analysing all values of
-% $\osres_s(\w)$ (\pref{def:concret})
-% for all possible initial state $s \subseteq \ctx$ in the considered context,
-% and all possible bounce sequences $\zeta \in \BS(P)$ that are chosen during the resolution.
-% 
-% \begin{definition}[$\osres : \PHl \times \OS \to \Sce$]
-% \label{def:concret}
-% For all $s \in \PHl$ and $\w \in \OS$, we define:
-% \[
-%   \osres_s(\w) \DEF
-%     \begin{cases}
-%       \emptyseq
-%         & \text{ if $\w = \emptyseq$} \\
-%       \res_s(\w_1) \concat
-%       \osres_{s \play \res_s(\w_1)}(\w_2 \concat \dots \concat \w_{\card{\w}})
-%         & \text{ otherwise} \\
-%     \end{cases}
-% \]
-% and, for all $s \in \PHl$ and $P \in \Obj$:
-% \[\res_s(P) \DEF
-%   \begin{cases}
-%     \varepsilon
-%       & \text{if } \target{P} = \bounce{P} \\
-%     \osres_s(P^Q \concat Q)
-%       & \text{if } \exists Q \in \Obj, (P, Q) \in \Bee{\Obj}{\Obj} \\
-%     \rec_s(\zeta)
-%       & \text{otherwise, with } \zeta \in \BS(P)
-%   \end{cases}
-% \]
-% with $P^Q = \PHobj{\PHtarget(P)}{\PHtarget(Q)}$.
-% Furthermore:
-% \begin{align*}
-%   \forall \zeta \in \BS,
-%   \rec_s(\zeta) &\DEF
-%     \begin{cases}
-%       \emptyseq
-%         & \text{ if $\zeta = \emptyseq$} \\
-%       \thisseq_s(\zeta_1) \concat \zeta_1 \concat
-%       \rec_{s \play \thisseq_s(\zeta_1) \concat \zeta_1}
-%       (\zeta_2 \concat \dots \concat \zeta_{\card{\zeta}})
-%         & \text{ otherwise}
-%     \end{cases} \\
-%   \forall h \in \PHh,
-%   \thisseq_s(h) &\DEF
-%     \begin{cases}
-%       \emptyseq
-%         & \text{ if $\hitter{h} = \emptyset$} \\
-%       \R_s(h_1) \concat \thisseq_{s \play \R_s(h_1)}(h_2 \concat \dots \concat h_{\card{h}})
-%         & \text{ otherwise}
-%     \end{cases} \\
-%   \forall a_i \in \Proc,
-%   \R_s(a_i) &\DEF \res_s(\PHobj{\PHget{s}{\PHsort(a_i)}}{a_i})
-% \end{align*}
-% and for all action $h \in \PHh$, $(h_i)_{i \in \segm{1}{\card{\hitter{h}}}}$
-% is a sequence containing all hitters of $h$ in an arbitrary order.
-% \end{definition}
+In this section, we briefly explain an alternative sufficient condition that
+can be applied when looking for scenarios that successively reach a sequence of local states (e.g.,
+first reach $a_j$, then later $b_k$, \ldots).
 
-%%%%%%%% Tentative 2 %%%%%%%%%%%%%%%%%%%%%%%
-% % \newcommand{\resP}{\mathbf{\Obj res}}
-% % \newcommand{\resOS}{\mathbf{\OS res}}
-% \newcommand{\resP}{\mathsf{res}^\Obj}
-% \newcommand{\resOS}{\mathsf{res}^\OS}
-% 
-% \newcommand{\res}{\mathbf{res}}
-% \newcommand{\autoBS}{\mathbf{autoBS}}
-% \newcommand{\rec}{\mathbf{rec}}
-% 
-% Pour tout objectif $P$ dans $\cwB$,
-% on note $X_P$ une séquence d'objectifs obtenue en effectuant
-% un parcours en profondeur d'abord de $\cwB$.
-% Un tel parcours existe car $\cwB$ ne comporte pas de cycle.
-% 
-% $$\res_s(\w) = \resOS_s((X_{\w_i})_{i \in \indexes{\w}})$$
-% 
-% \[
-%   \resOS_s(\w) \DEF
-%     \begin{cases}
-%       \emptyseq
-%         & \text{ if $\w = \emptyseq$} \\
-%       \resP_s(\w_1) \concat
-%       \resOS_{s \play \resP_s(\w_1)}(\w_{2..\card{\w}})
-%         & \text{ otherwise} \\
-%     \end{cases}
-% \]
-% 
-% $
-% \resP_s(\PHobj{a_j}{a_k}) \DEF
-%   \todo{resP}$
-% 
-% % $\resP_s(P) \DEF
-% %     \begin{cases}
-% %       \emptyseq
-% %         & \text{ if $P$ is trivial} \\
-% %       \res_s(\w_1) \concat
-% %       \osres_{s \play \res_s(\w_1)}(\w_2 \concat \dots \concat \w_{\card{\w}})
-% %         & \text{ otherwise} \\
-% %     \end{cases}$
+The approach proposed in this sub-section essentially applies the previous under-approximation for
+the first local states, and then computes a set of contexts that may be considered as the starting
+point for the next local states.
+In that way, the local states to reach are taken into account separately, which implies that only a
+subset of scenarios can be captured.
+%However, because each iteration focuses on a smaller part of the network, this
+%sequential under-approximation may be more conclusive.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\todo{computes possible outcomes from the LCG, gives it as context for the next stage}.
+
+\subsection{Reachability of a State}
+\label{ssec:simult-ua}
+
+\newcommand{\total}{\tau}
+\newcommand{\reach}{\sigma}
+
+The reachability property studied so far concerns a single local state at a time.
+However, we remark that the reachability of a global state or a sub-state can be
+addressed with the very same analysis by introducing a dedicated automata.
+Such analysis was not possible with the Process Hitting framework,
+because of the lack of the notion of simultaneity for more than two components.
+
+In order to check the reachability of a global state $s \in \PHl$,
+let $\PH = (\PHs, \PHl, \PHh)$ be an AAN.
+We define a new AAN $\PH' = (\PHs', \PHl', \PHh')$ with:
+$\PHs' = \PHs \cup \{ \reach \}$, $\PHl' = \PHl \times \PHl_\reach$,
+where $\PHl_\reach = \{ \reach_0, \reach_1 \}$,
+and $\PHh' = \PHh \cup \{ \PHhit{\toset{s}}{\reach_0}{\reach_1} \}$.
+Given an initial context $\ctx$, the reachability of $s$ in $\PH$
+is equivalent to the concretization of $\PHobjp{\reach}{0}{1}$ in $\PH'$
+from the initial context $\ctx \cup \{ \reach_0 \}$,
+which can be efficiently under-approximated using \pref{th:approxinf}.
+
+It is of course also possible to compute the reachability
+of a sub-state $s \in \PHsubl[\PHl]_S$ of a set of components $S \subseteq \PHs$
+with the same method.
+One can also check the reachability of a set of states $\Lambda \subseteq \PHl$
+by creating several actions
+$\PHhit{\toset{s}}{\reach_0}{\reach_1}$ in $\PHh$ for each state $s \in \Lambda$.

### 2015-02-04 parts/sa.tex
fix scenario extraction

@@
 and nodes in $\sSol$ can be marked with a set of local states.
+When ascending, the traversal always ascend into the node it previously descended from
+(in order to cover the same path backwards).
 The traversal starts in node $\myp$ in descending mode,
@@
     \begin{itemize}
-      \item[D)] Descend in an arbitrarily chosen $\sSol$ node,
-        and mark it with a sequence $\zeta \in \BS$ so that $\abstr{\zeta} = pps$.
+      \item[D)] Descend in an arbitrarily chosen node $\langle P, pps \rangle \in \Sol$,
+        and mark it with an arbitrarily chosen sequence
+        $\zeta \in \BS(P)$ so that $\abstr{\zeta} = pps$.
       \item[A)] Ascend in the parent $\Proc$ or $\Obj$ node.
@@
 
-  \item In a node $pps \in \Sol$ with the current marking $\zeta$:
+  \item In a node $\langle P, pps \rangle \in \Sol$ with the current marking $\zeta$:
     \begin{itemize}
@@
       \item If $\zeta = \emptyseq$,
-        ascend in the parent $\Obj$ node and carry on ascending.
+        ascend in the parent node $P \in \Obj$ and carry on ascending.
     \end{itemize}

### 2015-02-09 underapprox-tcrsig94/egfr104-possible-Inconc-tests.sh
tests++

@@ -1,0 +1,26 @@
+#!/bin/bash
+
+#ulimit -t 10
+
+#ph-reach -i egfr104.ph --initial-state "erbb1 1, erbb2 0, erbb3 0, erbb4 1, ar 0, bir 0, btc 0, egf 0, epr 1, hbegf 0" elk1 1 --coop-priority ; echo $?
+
+# Valeurs originales :
+#outputs="elk1 creb ap1 hsp27 actin_reorg cmyc pro_apoptotic p70s6_2 pkc stat1 stat3 stat5"
+#init="erbb1 1, erbb2 0, erbb3 0, erbb4 1, ar 0, bir 0, btc 0, egf 0, epr 1, hbegf 0"
+
+outputs="elk1 creb ap1 hsp27 actin_reorg cmyc pro_apoptotic p70s6_2 pkc stat1 stat3 stat5"
+init="erbb1 1, erbb2 0, erbb3 0, erbb4 1, ar 0, bir 0, btc 0, egf 1, epr 0, hbegf 0"
+
+echo "--- $init"
+for z in $outputs; do
+  echo "# $z 1"
+  ./unitrun.sh $1 "x" --no-debug --initial-state "$init" -i "egfr104.ph" $z 1
+  [ $? -eq 137 ] && echo '*** Killed ***';
+done
+
+
+# Inconc potentiels pour les états initiaux :
+#   erbb1 = 1 & erbb2 = 0 & erbb4 = 1 &
+# bir = 1 \/ btc = 1 \/ egf = 1 \/ epr = 1
+# \/ nrg1a = 1 \/ nrg1b = 1 \/ nrg2b = 1 \/ nrg4 = 1 \/ tgfa 1
+

### 2015-02-09 underapprox-tcrsig94/egfr104-possible-Inconc.sh

@@ -1,0 +1,15 @@
+#!/bin/bash
+
+ulimit -t 10
+
+#ph-reach -i egfr104.ph --initial-state "erbb1 1, erbb2 0, erbb3 0, erbb4 1, ar 0, bir 0, btc 0, egf 0, epr 1, hbegf 0" elk1 1 --coop-priority ; echo $?
+
+outputs="elk1 creb ap1 hsp27 actin_reorg cmyc pro_apoptotic p70s6_2 pkc stat1 stat3 stat5"
+init="erbb1 1, erbb2 0, erbb3 0, erbb4 1, ar 0, bir 0, btc 0, egf 0, epr 1, hbegf 0"
+echo "--- $init"
+for z in $outputs; do
+  echo "# $z 1"
+  ./unitrun.sh $1 "x" --no-debug --initial-state "$init" -i "egfr104.ph" $z 1
+  [ $? -eq 137 ] && echo '*** Killed ***';
+done
+

### 2015-02-09 underapprox-tcrsig94/run-egfr104-full.sh

@@ -1,53 +1,0 @@
-#!/usr/bin/env bash
-
-# sh run-generator.sh egfr104 'erbb1 erbb2 erbb3 erbb4 ar bir btc egf epr hbegf nrg1a nrg1b nrg2a nrg2b nrg3 nrg4 tgfa' 'elk1 creb ap1 hsp27 actin_reorg cmyc pro_apoptotic p70s6_2 pkc stat1 stat3 stat5'
-
-ph="egfr104.ph"
-outputs="elk1 creb ap1 hsp27 actin_reorg cmyc pro_apoptotic p70s6_2 pkc stat1 stat3 stat5"
-mode=${1}
-
-ulimit -t 4
-
-for erbb1 in 0 1; do
-for erbb2 in 0 1; do
-for erbb3 in 0 1; do
-for erbb4 in 0 1; do
-for ar in 0 1; do
-for bir in 0 1; do
-for btc in 0 1; do
-for egf in 0 1; do
-for epr in 0 1; do
-for hbegf in 0 1; do
-for nrg1a in 0 1; do
-for nrg1b in 0 1; do
-for nrg2a in 0 1; do
-for nrg2b in 0 1; do
-for nrg3 in 0 1; do
-for nrg4 in 0 1; do
-for tgfa in 0 1; do
-
-init="erbb1 $erbb1, erbb2 $erbb2, erbb3 $erbb3, erbb4 $erbb4, ar $ar, bir $bir, btc $btc, egf $egf, epr $epr, hbegf $hbegf, nrg1a $nrg1a, nrg1b $nrg1b, nrg2a $nrg2a, nrg2b $nrg2b, nrg3 $nrg3, nrg4 $nrg4, tgfa $tgfa"
-echo "--- $init"
-for z in $outputs; do
-  echo "# $z 1"
-  ./unitrun.sh $mode "x" --no-debug --initial-state "$init" -i $ph $z 1
-  [ $? -eq 137 ] && echo '*** Killed ***';
-done
-
-done
-done
-done
-done
-done
-done
-done
-done
-done
-done
-done
-done
-done
-done
-done
-done
-done

### 2015-02-09 underapprox-tcrsig94/run-generator.sh

@@ -30,6 +30,11 @@ outputs=$3
 # Header
 echo '#!/usr/bin/env bash' > $runfile
 echo '' >> $runfile
+echo -n "# Date: " >> $runfile
+date >> $runfile
+echo "# Generated by:" >> $runfile
+echo "# sh $0 $1 '$2' '$3'" >> $runfile
+echo '' >> $runfile
 echo "# File: $model" >> $runfile
 echo "# Inputs: $inputs" >> $runfile
 echo "# Outputs: $outputs" >> $runfile
@@ -37,6 +42,17 @@ echo '' >> $runfile
 echo "ph=\"${model}\"" >> $runfile
 echo "outputs=\"${outputs}\"" >> $runfile
 echo 'mode=${1}' >> $runfile
+echo '' >> $runfile
+
+echo "echo -n \"Start time: \" && date" >> $runfile
+echo "echo 'Model: $model'" >> $runfile
+echo "echo 'Inputs: $inputs'" >> $runfile
+echo "echo 'Outputs: $outputs'" >> $runfile
+echo '' >> $runfile
+echo "(echo -n \"Start time: \" && date) >&2" >> $runfile
+echo "(echo 'Model: $model') >&2" >> $runfile
+echo "(echo 'Inputs: $inputs') >&2" >> $runfile
+echo "(echo 'Outputs: $outputs') >&2" >> $runfile
 echo '' >> $runfile
 
 # For loops
@@ -55,11 +71,11 @@ done
 echo "\"" >> $runfile
 
 # Loop body
-
 echo "echo \"--- \$init\"" >> $runfile
 echo "for z in \$outputs; do" >> $runfile
 echo "  echo \"# \$z 1\"" >> $runfile
 echo "  ./unitrun.sh \$mode \"x\" --no-debug --initial-state \"\$init\" -i \$ph \$z 1" >> $runfile
+echo "  [ \$? -eq 137 ] && echo '*** Killed ***'" >> $runfile
 echo "done" >> $runfile
 echo '' >> $runfile
 
@@ -67,4 +83,10 @@ echo '' >> $runfile
 for curinput in $inputs; do
   echo "done" >> $runfile
 done
+echo '' >> $runfile
+
+# Footer
+echo "echo -n \"End time: \" && date" >> $runfile
+echo "(echo -n \"End time: \" && date) >&2" >> $runfile
+echo '' >> $runfile
 

### 2015-02-09 underapprox-tcrsig94/run.sh

@@ -1,6 +1,8 @@
 #!/usr/bin/env bash
 ph="model.ph"
 outputs="sre ap1 nfkb nfat sigmab"
+#outputs="sigmab"
+#outputs="sre ap1 nfkb nfat"
 mode=${1}
 
 for i in 0 1; do

### 2015-02-09 underapprox-tcrsig94/tests-init-egfr104.sh

@@ -1,0 +1,48 @@
+#!/usr/bin/env bash
+
+
+
+# Comments:
+# This script tests all outputs when a given input is active,
+# in the predefined configuration:
+#   erbb1 = 1 & erbb2 = 0 & erbb4 = 1
+# The following inputs seem to have an influence:
+#   erbb3 = 1 \/
+#   bir = 1 \/ btc = 1 \/ egf = 1 \/ epr = 1 \/
+#   nrg1a = 1 \/ nrg1b = 1 \/ nrg2b = 1 \/ nrg4 = 1 \/ tgfa 1
+# The activation of the following outputs is then compromised:
+#   elk1, creb, ap1, actin_reorg, cmyc
+
+
+
+# Date: lundi 9 février 2015, 20:06:05 (UTC+0100)
+# Generated by:
+# sh run-generator.sh egfr104 'erbb1 erbb2 erbb3 erbb4 ar bir btc egf epr hbegf nrg1a nrg1b nrg2a nrg2b nrg3 nrg4 tgfa' 'elk1 creb ap1 hsp27 actin_reorg cmyc pro_apoptotic p70s6_2 pkc stat1 stat3 stat5'
+
+# File: egfr104.ph
+# Inputs: erbb1 erbb2 erbb3 erbb4 ar bir btc egf epr hbegf nrg1a nrg1b nrg2a nrg2b nrg3 nrg4 tgfa
+# Outputs: elk1 creb ap1 hsp27 actin_reorg cmyc pro_apoptotic p70s6_2 pkc stat1 stat3 stat5
+
+ph="egfr104.ph"
+outputs="elk1 creb ap1 hsp27 actin_reorg cmyc pro_apoptotic p70s6_2 pkc stat1 stat3 stat5"
+mode=${1}
+
+echo -n "Start time: " && date
+echo 'Model: egfr104.ph'
+echo 'Outputs: elk1 creb ap1 hsp27 actin_reorg cmyc pro_apoptotic p70s6_2 pkc stat1 stat3 stat5'
+
+for curinput in erbb3 ar bir btc egf epr hbegf nrg1a nrg1b nrg2a nrg2b nrg3 nrg4 tgfa sos1r eps8r csrc pi3kr pten ship2 pdk1 pp2a mtorr mkp pp2b; do
+
+init="erbb1 1, erbb2 0, erbb4 1, $curinput 1"
+echo "--- $init"
+for z in $outputs; do
+  echo "# $z 1"
[…]

### 2015-02-09 underapprox-tcrsig94/unitrun.sh

@@ -1,4 +1,8 @@
 #!/usr/bin/env bash
+
+# Max CPU time in seconds
+ulimit -t 4
+
 mode=$1; shift
 name=$1; shift
 

### 2015-02-10 underapprox-tcrsig94/run-egfr104-full.sh
tests++

@@ -1,0 +1,93 @@
+#!/usr/bin/env bash
+
+# Date: lundi 9 février 2015, 23:42:58 (UTC+0100)
+# Generated by:
+# sh run-generator.sh egfr104 'erbb1 erbb2 erbb3 erbb4 ar bir btc egf epr hbegf nrg1a nrg1b nrg2a nrg2b nrg3 nrg4 tgfa sos1r eps8r csrc pi3kr pten ship2 pdk1 pp2a mtorr mkp pp2b' 'elk1 creb ap1 hsp27 actin_reorg cmyc pro_apoptotic p70s6_2 pkc stat1 stat3 stat5'
+
+# File: egfr104.ph
+# Inputs: erbb1 erbb2 erbb3 erbb4 ar bir btc egf epr hbegf nrg1a nrg1b nrg2a nrg2b nrg3 nrg4 tgfa sos1r eps8r csrc pi3kr pten ship2 pdk1 pp2a mtorr mkp pp2b
+# Outputs: elk1 creb ap1 hsp27 actin_reorg cmyc pro_apoptotic p70s6_2 pkc stat1 stat3 stat5
+
+ph="egfr104.ph"
+outputs="elk1 creb ap1 hsp27 actin_reorg cmyc pro_apoptotic p70s6_2 pkc stat1 stat3 stat5"
+mode=${1}
+
+echo -n "Start time: " && date
+echo 'Model: egfr104.ph'
+echo 'Inputs: erbb1 erbb2 erbb3 erbb4 ar bir btc egf epr hbegf nrg1a nrg1b nrg2a nrg2b nrg3 nrg4 tgfa sos1r eps8r csrc pi3kr pten ship2 pdk1 pp2a mtorr mkp pp2b'
+echo 'Outputs: elk1 creb ap1 hsp27 actin_reorg cmyc pro_apoptotic p70s6_2 pkc stat1 stat3 stat5'
+
+(echo -n "Start time: " && date) >&2
+(echo 'Model: egfr104.ph') >&2
+(echo 'Inputs: erbb1 erbb2 erbb3 erbb4 ar bir btc egf epr hbegf nrg1a nrg1b nrg2a nrg2b nrg3 nrg4 tgfa sos1r eps8r csrc pi3kr pten ship2 pdk1 pp2a mtorr mkp pp2b') >&2
+(echo 'Outputs: elk1 creb ap1 hsp27 actin_reorg cmyc pro_apoptotic p70s6_2 pkc stat1 stat3 stat5') >&2
+
[…]

### 2015-02-10 underapprox-tcrsig94/run-egfr104.sh

@@ -1,0 +1,63 @@
+#!/usr/bin/env bash
+
+# Date: mardi 10 février 2015, 11:25:48 (UTC+0100)
+# Generated by:
+# sh run-generator.sh egfr104 'erbb1 erbb2 erbb3 erbb4 bir btc egf epr nrg1a nrg1b nrg2b nrg4 tgfa' 'elk1 creb ap1 hsp27 actin_reorg cmyc pro_apoptotic p70s6_2 pkc stat1 stat3 stat5'
+
+# File: egfr104.ph
+# Inputs: erbb1 erbb2 erbb3 erbb4 bir btc egf epr nrg1a nrg1b nrg2b nrg4 tgfa
+# Outputs: elk1 creb ap1 hsp27 actin_reorg cmyc pro_apoptotic p70s6_2 pkc stat1 stat3 stat5
+
+ph="egfr104.ph"
+outputs="elk1 creb ap1 hsp27 actin_reorg cmyc pro_apoptotic p70s6_2 pkc stat1 stat3 stat5"
+mode=${1}
+
+echo -n "Start time: " && date
+echo 'Model: egfr104.ph'
+echo 'Inputs: erbb1 erbb2 erbb3 erbb4 bir btc egf epr nrg1a nrg1b nrg2b nrg4 tgfa'
+echo 'Outputs: elk1 creb ap1 hsp27 actin_reorg cmyc pro_apoptotic p70s6_2 pkc stat1 stat3 stat5'
+
+(echo -n "Start time: " && date) >&2
+(echo 'Model: egfr104.ph') >&2
+(echo 'Inputs: erbb1 erbb2 erbb3 erbb4 bir btc egf epr nrg1a nrg1b nrg2b nrg4 tgfa') >&2
+(echo 'Outputs: elk1 creb ap1 hsp27 actin_reorg cmyc pro_apoptotic p70s6_2 pkc stat1 stat3 stat5') >&2
+
+for erbb1 in 0 1; do
+for erbb2 in 0 1; do
+for erbb3 in 0 1; do
+for erbb4 in 0 1; do
+for bir in 0 1; do
+for btc in 0 1; do
+for egf in 0 1; do
+for epr in 0 1; do
+for nrg1a in 0 1; do
+for nrg1b in 0 1; do
+for nrg2b in 0 1; do
+for nrg4 in 0 1; do
+for tgfa in 0 1; do
+
[…]

### 2015-02-10 underapprox-tcrsig94/tests-init-egfr104.sh

@@ -9,7 +9,7 @@
 # The following inputs seem to have an influence:
 #   erbb3 = 1 \/
 #   bir = 1 \/ btc = 1 \/ egf = 1 \/ epr = 1 \/
-#   nrg1a = 1 \/ nrg1b = 1 \/ nrg2b = 1 \/ nrg4 = 1 \/ tgfa 1
+#   nrg1a = 1 \/ nrg1b = 1 \/ nrg2b = 1 \/ nrg4 = 1 \/ tgfa = 1
 # The activation of the following outputs is then compromised:
 #   elk1, creb, ap1, actin_reorg, cmyc
 

### 2015-02-10 underapprox-tcrsig94/unitrun.sh

@@ -1,7 +1,7 @@
 #!/usr/bin/env bash
 
 # Max CPU time in seconds
-ulimit -t 4
+ulimit -t 3
 
 mode=$1; shift
 name=$1; shift

### 2015-02-12 parts/def-ph.tex
sect 3

@@
 If $a_i \in \PHl_a$, we define the notation $a_i \in s \EQDEF \PHget{s}{a} = a_i$.
+
+\begin{comment}
 \pref{def:substate} defines the notion of sub-state on a set of automata, that is used to focus on the interesting part of a complete state.
@@
 $\hitter{h} \in \PHsublset[\PHl]$.
+
+\end{comment}
 
@@
       & \PHfrappem{a_1}{a_0} \enspace , \quad
-        \PHfrappem{a_0}{a_1} \enspace , \\
+        \PHfrappes{b_0}{a_0}{a_1} \enspace , \\
       & \PHfrappem{b_1}{b_0} \enspace , \quad
-        \PHfrappem{b_0}{b_1} \enspace , \\
+        \PHfrappes{a_0}{b_0}{b_1} \enspace , \\
       & \PHfrappes{a_1, b_1}{c_0}{c_1} \enspace \quad \qquad \qquad
@@
 
+\begin{comment}
 Finally, we define the support (\pref{def:supp}) of a sequence of actions $\zeta$
@@
 
+\end{comment}
+
 \begin{remark}[Comparison with the Process Hitting]

### 2015-02-12 parts/example.tex
minor fixes
sect 3

@@
 Rather than checking this whole objective sequence with \pref{th:approxinf},
-we break it using \pref{thm:ordered-ua}.
+we break it using \pref{ssec:ordered-ua}.
 We first build the first saturated graph of local causality
@@
 This last graph is depicted in \pref{fig:metazoan-sa}(right).
-In conclusion, by using \pref{thm:ordered-ua} on these saturated graphs of local causality,
+In conclusion, by following \pref{ssec:ordered-ua} on these saturated graphs of local causality,
 we can conclude that the initial objective $\w$ is reachable,
@@
     \node[Asol,below of=tc10] (tc10s) {};
+    \node[Assol,below of=tc10s] (tnc10s) {$\{ a_0 \}$};
     \node[Aobj,right of=tc10] (tc00) {$\PHobj{c_0}{c_0}$};
@@
 
-    \node[Aproc,below of=tc10s] (ta0) {$a_0$};
+    \node[Aproc,below of=tnc10s] (ta0) {$a_0$};
     \node[Aobj,below of=ta0] (ta00) {$\PHobj{a_0}{a_0}$};
@@
 
-    (tc10s) edge (ta0)
+    (tc10s) edge (tnc10s)
+    (tnc10s) edge (ta0)
     (ta0) edge (ta00)

### 2015-02-12 parts/sa.tex
sect 3

@@
 
-Our approach relies on abstractions of scenarios that have been introduced in
+Our approach relies on abstractions of scenarios (\pref{ssec:abstr-sce}) that have been introduced in
 \cite{PMR12-MSCS} for the static analysis of reachability in the Process Hitting framework,
@@
 In this paper, we generalize the static analysis for the case of the under-approximation of
-reachability in any AAN.
+reachability in any AAN (\pref{ssec:ua}).
 
-\todo{outline}
+In \pref{ssec:concret}, we detail a procedure to extract a witness scenario
+concretizing a given local state reachability property.
+Finally, we discuss in \pref{ssec:ordered-ua} how the static analysis can be
+extended to sequential (sub)states reachability properties.
 
@@
   The set of all objective sequences is denoted by $\OS$.
+  Given $\w\in\OS$, $\PHsort(\w) \DEF \{\PHsort(\w_i)\mid i\in\indexes{\w}\}$.
+For each automaton $a\in\PHsort(\w)$,  the first local state of $a$ referenced in
+$\w$ is denoted by $\first_a(\w) \DEF \target{\w_m}$, where $m=\min\{n\in\indexes{\w}\mid \PHsort(\w)=a\}$.
 \end{definition}
@@
 $w\ltw w'$ if and only if there exists a mapping between all the objective bounces of $w'$ in $w$
-that preserve the sequentiality.
-
-\todo{support compatibility}
+that preserve the sequentiality, provided that each automaton starts in the same
+local state.
 
@@
 $\w\ltw\w'$ if and only if
-$|\w|\geq|\w'|$ and
-there exists a mapping $\phi: \indexes{\w'}\mapsto \indexes{\w}$ such that
+$|\w|\geq|\w'|$,
+$\forall a\in\PHsort(\w'), a\in\PHsort(\w) \wedge \first_a(\w')=\first_a(\w)$;
+and there exists a mapping $\phi: \indexes{\w'}\mapsto \indexes{\w}$ such that
 $\forall n,m \in\indexes{\w'}, n<m \Leftrightarrow \phi(n)<\phi(m)$,
@@
 (part of) the successive state changes of the automata.
-We denote by $\concr(\w)$ (\pref{def:concr}) the set of scenarios concretising an objective sequence
+We denote by $\concr(\w)$ (\pref{def:concr}) the set of scenarios matching with an objective sequence
 $\w$ in the state $s\in\PHs$.
@@
 
-\todo{compatibility of $\w$ with $s$}
-
 \begin{definition}[$\concr: \OS \to \powerset(\Sce)$]\label{def:concr}
-Given $\w\in\OS$, $\concr(\w)$ is the set of scenarios concretising $\w$ in the
-state $s$:
+Given a state $s\in\PHl$ and an objective sequence
+$\w\in\OS$ such that $\forall a\in\PHsort(\w), \first_a(\w)\in s$,
+$\concr(\w)$ is the set of scenarios matching with $\w$:
 \begin{align*}
@@
 
-\todo{example}
+\begin{example}
+Given the AAN of \pref{fig:ph-livelock},
+$\BS(\obj{c_0}{c_1}) = \{\PHfrappes{a_1,b_1}{c_0}{c_1}\}$;
+and 
+$\BS(\obj{a_0}{a_1}) = \{\PHfrappes{b_0}{a_0}{a_1}\}$.
+\end{example}
 
-From \pref{def:bs}, we can derive that any scenario concretising an objective includes all the
+From \pref{def:bs}, we can derive that any scenario matching with an objective includes all the
 actions of one of the bounce sequences of the objective (\pref{lem:bs-concr}).
@@
 
+\todo{the procedure is non-deterministic, make it deterministic? (list all the
+scenarios}
+
 \begin{itemize}
@@
 
-\subsection{Sequential Under-approximation}
+\todo{name + prototype of the procedure}
+
+\todo{example}
+
+\subsection{Addressing Sequential and Sub-state Reachability}
 \label{ssec:ordered-ua}
-
-In this section, we briefly explain an alternative sufficient condition that
-can be applied when looking for scenarios that successively reach a sequence of local states (e.g.,
-first reach $a_j$, then later $b_k$, \ldots).
-
-The approach proposed in this sub-section essentially applies the previous under-approximation for
-the first local states, and then computes a set of contexts that may be considered as the starting
-point for the next local states.
-In that way, the local states to reach are taken into account separately, which implies that only a
-subset of scenarios can be captured.
-%However, because each iteration focuses on a smaller part of the network, this
-%sequential under-approximation may be more conclusive.
-
-\todo{computes possible outcomes from the LCG, gives it as context for the next stage}.
-
-\subsection{Reachability of a State}
 \label{ssec:simult-ua}
@@
 
-The reachability property studied so far concerns a single local state at a time.
-However, we remark that the reachability of a global state or a sub-state can be
-addressed with the very same analysis by introducing a dedicated automata.
+In this section, we briefly discuss how the presented static analysis for local
+state reachability properties can be extended to sequential (sub)states
+reachability properties.
+
+\paragraph{Sub-state reachability.}
+Given an AAN $\PH = (\PHs, \PHl, \PHh)$,
+a sub-set of automata local states
+$ps = \{ a_i \in\Proc\mid a\in\PHs, a_i\in\PHl(a)\}$,
+the reachability from $s\in\PHl$ of a state $s'\in\PHl$ such that
+$ps\subset s'$ is equivalent to the reachability of the local state
+$\reach_1$ from a state $s\uplus\langle\reach_0\rangle$
+in the AAN
+$\PH' = (\PHs', \PHl', \PHh')$ with:
+$\PHs' = \PHs \cup \{ \reach \}$, $\PHl' = \PHl \times \PHl_\reach$,
+where $\PHl_\reach = \{ \reach_0, \reach_1 \}$,
+and $\PHh' = \PHh \cup \{ \PHhit{ps}{\reach_0}{\reach_1} \}$.
+
 Such analysis was not possible with the Process Hitting framework,
@@
 
-In order to check the reachability of a global state $s \in \PHl$,
-let $\PH = (\PHs, \PHl, \PHh)$ be an AAN.
-We define a new AAN $\PH' = (\PHs', \PHl', \PHh')$ with:
-$\PHs' = \PHs \cup \{ \reach \}$, $\PHl' = \PHl \times \PHl_\reach$,
-where $\PHl_\reach = \{ \reach_0, \reach_1 \}$,
-and $\PHh' = \PHh \cup \{ \PHhit{\toset{s}}{\reach_0}{\reach_1} \}$.
-Given an initial context $\ctx$, the reachability of $s$ in $\PH$
-is equivalent to the concretization of $\PHobjp{\reach}{0}{1}$ in $\PH'$
-from the initial context $\ctx \cup \{ \reach_0 \}$,
-which can be efficiently under-approximated using \pref{th:approxinf}.
+\paragraph{Sequential reachability.}
+Given a sequence of local state to reach (e.g., reach $a_i$, then $b_j$),
+one can use the same approach as for sub-state reachability by introducing
+a new automaton $\reach$ having $n+1$ local states where $n$ is the size of the
+sequence of reachability and $n$ actions making it bounce from $\reach_0$ to
+$\reach_n$ with hitters corresponding the successive local states
+(e.g., $\PHfrappes{a_i}{\reach_0}{\reach_1}$ and
+$\PHfrappes{b_j}{\reach_0}{\reach_1}$).
 
-It is of course also possible to compute the reachability
-of a sub-state $s \in \PHsubl[\PHl]_S$ of a set of components $S \subseteq \PHs$
-with the same method.
-One can also check the reachability of a set of states $\Lambda \subseteq \PHl$
-by creating several actions
-$\PHhit{\toset{s}}{\reach_0}{\reach_1}$ in $\PHh$ for each state $s \in \Lambda$.
+An alternative approach is to use the extraction of a scenario of the previous
+sub-section:
+given the initial state, and a first local state reachability property, one
+compute a possible scenario witnessing this reachability.
+Then the next local state reachability properties is computed from the
+state that outcomes from the latter scenario.

### 2015-02-12 parts/example.tex
todos + simplification

@@
 Rather than checking this whole objective sequence with \pref{th:approxinf},
-we break it using \pref{ssec:ordered-ua}.
+we split it following \pref{ssec:ordered-ua}.
+\todo{update method: extract a witness scenario, and use the resulting state for
+the rest - remove $\Cap$, $\allprocs$, $\lastprocs$, etc.}
 We first build the first saturated graph of local causality

### 2015-02-12 parts/sa.tex
todos + simplification

@@
 a sub-set of automata local states
-$ps = \{ a_i \in\Proc\mid a\in\PHs, a_i\in\PHl(a)\}$,
+$ps = \{ a_i \in\Proc\mid a\in\PHs, a_i\in\PHl_a\}$,
 the reachability from $s\in\PHl$ of a state $s'\in\PHl$ such that

### 2015-02-12 parts/suppl-sa.tex
typos
todos + simplification

@@
 
-\todo{Check with the new notations ($\muconcr$, $\procs$)}
+\todo{Check with the new notations ($\procs$)}
 
@@
 \begin{proofapproxinf}
-We note $max\ctx = \ctx \Cap \allprocs(\cwB)$ the context supported by $\cwB$.
+Given the LCG $\cwB=(\cwV,\cwE)$,
+we note $max\ctx = \{a\mapsto \cwV\cap\PHl_a \mid a\in\PHs\}$ the context supported by $\cwB$.
 
@@
     that may change the other local states of the set $ps$.
-    Therefore, there exists $\delta' \in \muconcr_{s \PHplay \delta_n}(\PHobj{q}{p_{n+1}})$,
+    Therefore, there exists $\delta' \in \mconcr_{s \PHplay \delta_n}(\PHobj{q}{p_{n+1}})$,
     so that $\forall i \in \segm{1}{n+1}$, $\PHget{(s \PHplay \delta_n \PHplay \delta')}{\PHsort(p_{i})} = p_{i}$.
@@
 As there is no cycle in $\cwB$, we show by induction in the following that
-$\forall s\in L, s\subseteq max\ctx, \forall P \in \Bv \cap \Obj,
-\PHtarget(P) \in s \Longrightarrow \exists \delta \in \muconcr_s(P)$.
+$\forall s\in \PHl, s\subseteq max\ctx, \forall P \in \Bv \cap \Obj,
+\PHtarget(P) \in s \Longrightarrow \exists \delta \in \mconcr_s(P)$.
 \begin{itemize}
@@
     If $\exists (P, Q) \in \Bee{\Obj}{\Obj}$, then by hypothesis,
-      $\muconcr_{s}(\obj{\PHtarget(P)}{\PHtarget(Q)} \concat Q) \neq \emptyset$, thus
-      $\muconcr_{s}(P) \neq \emptyset$.
+      $\mconcr_{s}(\obj{\PHtarget(P)}{\PHtarget(Q)} \concat Q) \neq \emptyset$, thus
+      $\mconcr_{s}(P) \neq \emptyset$.
     Else, by \pref{def:lcg}-\ref{lcg-conn}, the concretizations of the successors of $P$ require no local state of automaton $\PHsort(P)$.
@@
       \end{itemize}
-      Thus, $\delta_{|\zeta|} \in \muconcr_s(P)$. % and $\ceil(\delta) \subseteq max\ctx$.
+      Thus, $\delta_{|\zeta|} \in \mconcr_s(P)$. % and $\ceil(\delta) \subseteq max\ctx$.
 \end{itemize}
-Finally, as $\muconcr_{max\ctx}(\w) \neq \emptyset$, $\uconcr(\w) \neq
-\emptyset$ (\pref{lem:uconcr-ctx}).
 \end{proofapproxinf}

### 2015-02-12 parts/sa.tex
typo

@@
 
-A classical approach for determining if a local state of an automaton can be reach from a
-given initial state is to build sequences of transitions from the initial state until a state
+A classical approach for determining if a local state of an automaton can be
+reached from a given initial state is to build sequences of transitions from the initial state until a state
 containing the given local state is reached.
@@
 Such an objective is written $\PHobjp{a}{i}{j}$.
-Successive objectives are described with objective sequences (\pref{def:obj}).
+Successive objectives are described with objective sequences.
 

### 2015-02-13 response.tex
galois connection + response

@@
 \begin{itemize}
-  \item The use of AANs (new to this revision) that simplifies the formalism
-    and gives a new viewpoint to the overall work;
-  \item Theorem 2, which refines successive reachability;
-  \item Sect. 4.2, which allows to translate any AAN with classes of priorities
-    into a simple AAN (with one class of priority),
-    thus extending the range of application of the static analysis;
-  \item Sect. 3.5 (new to this revision),
-    which returns a scenario concretizing the desired reachability, when possible.
+  \item In this revision, we generalised the results to Asynchronous Automata
+  Networks (AANs) which also simplies the formalism;
+  \item In this revision, we also included a new section (3.3) which give a
+  procedures to extract a witness scenario satisfying a given reachability
+  property.
+  \item The encoding of AANs with classes of priorities into simple AANs
+  (section 4).
 \end{itemize}
@@
 
-\todo{À faire !}
+\answer{With this revision, we removed and simplies a lot a notations, and added
+more explanations for the under-approximation of reachability properties in AANs
+(section 3).
+More details on the abstract domain (objective sequences) and their
+interconnections with concrete scenarios are given in section 3.1.
+The relationship of Local Causality Graphs with objective sequences is also
+better motivated (collecting semantics for the possible refinements of the
+objective sequences).
+However, the goal of this section being at building particular cases of
+scenarios, no completness of the collection is required.
+We believe that the revision of this section brings sufficient intuition to
+capture the main concepts of the analysis, while avoiding un-necessary technical
+definitions.
+}
 

### 2015-02-13 parts/sa.tex
galois connection + response

@@
 $\w$ is denoted by $\first_a(\w) \DEF \target{\w_m}$, where $m=\min\{n\in\indexes{\w}\mid \PHsort(\w)=a\}$.
+  The set of objective sequences starting in a state $s\in\PHl$ are denoted by
+  $\OS(s)\DEF \{\w\in\OS\mid\forall a\in\PHsort(\w), \first_a(\w)\in s\}$.
 \end{definition}
@@
 and
-$\forall n\in\indexes{\w'}, \bounce{\w'_n}=\bounce{\w_{\phi(n)}}$
+$\forall n\in\indexes{\w'}, \bounce{\w'_n}=\bounce{\w_{\phi(n)}}$.
 \end{definition}
@@
 Given a state $s\in\PHl$ and an objective sequence
-$\w\in\OS$ such that $\forall a\in\PHsort(\w), \first_a(\w)\in s$,
-$\concr(\w)$ is the set of scenarios matching with $\w$:
+$\w\in\OS(s)$, $\concr(\w)$ is the set of scenarios matching with $\w$:
 \begin{align*}
-\concr(\w) \DEF \{ \delta\in\Sce(s)\mid & (\w^\vartriangle=\emptyseq \wedge
-\delta=\emptyseq)  \vee (
-\w^\vartriangle\neq \emptyseq\wedge
+\concr(\w) \DEF \{ \delta\in\Sce(s)\mid &
+\w^\vartriangle\neq \emptyseq\Rightarrow
+\bounce{\delta_{\card\delta}} = \bounce{\w_{\card\w}}
 \\ &
@@
 \end{lemma}
+
+Given a non-empty set $\Delta\subseteq\Sce(s)$ of non-empty scenarios that have a common last bounce
+($\exists a_i\in\Proc, \forall\delta\in\Delta,
+\bounce{\delta_{\card\delta}}=a_i$), one can define an abstraction $\alpha_s$ of
+such a set as the smallest objective sequence $\w\in\OS(s)$ such that
+$\bounce{\w_{\card\w}} = \bounce{\delta_{\card\delta}}, \delta\in\Delta$
+and
+$\forall\delta\in\Delta, \exists \phi:\indexes{\w}\mapsto\indexes{\delta}
+    (\forall n,m\in\indexes{\w}, n<m \Leftrightarrow \phi(n)\leq\phi(m))
+	\wedge \forall n\in\indexes{\w},
+	  \bounce{\w_n} \in s\play\delta_{1..\phi(n)})$.
+In such a setting, $\alpha_s$ and $\concr$ form a Galois connection between sets
+of scenarios and objective sequences.
 
@@
 
-Given one initial objective, one could then recursively refine the objective into objective
-sequences following its bounce sequences \cite{PMR12-MSCS}:
+Given one initial objective, one could then iteratively refine the objective into objective
+sequences following its bounce sequences:
 the refinement of objective $P$ with $\zeta\in\BS(P)$ would consists in prepending to $P$ the
@@
 the generalization of the refinement to an objective sequence would require to consider all possible
-interleaving between the refinements.
+interleaving between the refinements \cite{PMR12-MSCS}.
+
+For example, given the AAN of \pref{fig:ph-livelock},
+in the state $\langle a_0,b_0,c_0\rangle$,
+the objective $\obj{a_0}{a_1}$ can be refined in the objective sequence
+$\obj{b_0}{b_0}\concat\obj{a_0}{a_1}$
+and
+the objective $\obj{c_0}{c_1}$ can be refined in the objective sequence
+$\obj{a_0}{a_1}\concat\obj{b_0}{b_1}\concat\obj{c_0}{c_1}$
+or
+$\obj{b_0}{b_1}\concat\obj{a_0}{a_1}\concat\obj{c_0}{c_1}$
+(which can be further refined).
 

### 2015-02-13 parts/sa.tex
sa++

@@
 $\obj{b_0}{b_1}\concat\obj{a_0}{a_1}\concat\obj{c_0}{c_1}$
-(which can be further refined).
+(which can then be further refined).
 
-These refinements can be summarized compactly with a so-called Local Causality Graph (LCG).
+These refinements can be summarized with a so-called Local Causality Graph (LCG).
 Given an initial context $\ctx$ and a local state $\myp\in\Proc$,
@@
 (\pref{def:lcg}).
-A node in $\Obj$ represents an objective that have to be refined.
-Such a node can then be related to nodes in $\Sol$ which represents a set of hitter set of a
-bounce sequence of the objective:
+A node in $\cwV\cap\Obj$ represents an objective to refine.
+Such a node is related to nodes in $\cwV\cap\Sol$ which represent sets of hitter set of a
+bounce sequence of the objective (one for each bounce sequence in $\BS(P)$):
 given an objective $P$, if $\zeta\in\BS(P)$, $\abstr\zeta \DEF \{\PHhitter(\zeta_n) \mid
@@
 (\pref{def:lcg}-\ref{lcg-obj-sol}).
-Given a node $\langle P,\abstr\zeta\rangle\in\cwV\cap\Sol$, for each $ps\in\abstr\zeta$,
-it is related to a node $ps\in\sSol$
+For each hitter set $ps\in\abstr\zeta$,
+the node $\langle P,\abstr\zeta\rangle\in\cwV\cap\Sol$ is
+related to the node $ps\in\sSol$
 (\pref{def:lcg}-\ref{lcg-sol-sync}).
-A node $ps\in\sSol$ is then related to each $a\in\Proc$
+Then, each node $ps\in\sSol$ is related to each local state $a\in\Proc$
 (\pref{def:lcg}-\ref{lcg-sync-ls}).
-Given a node $a_i\in\cwV\cap\Proc$, for each $a_j\in\ctx$ or $a_j\in\cwV\cap\Proc$,
-it is related to an objective $\obj{a_j}{a_i}$
+Each local state node $a_i\in\cwV\cap\Proc$,
+is related to each objective $\obj{a_j}{a_i}$ where
+$a_j$ is either in the initial context $\ctx$, or
+is a local state node in the LCG
 (\pref{def:lcg}-\ref{lcg-ls-obj}).

### 2015-02-13 parts/sa.tex
update

@@
 A node $x$ of the LCG in $\sSol$ is \emph{independent} (\pref{def:coherent}) if for each local state
-$a_i\in x$, none of the other local state $b_j\in x$ have a local state of automaton $a$ different
-than $a_i$ in their successors.
+$a_i\in x$, none of the other local states $b_j\in x$ have in their accessors a local state of automaton $a$ different
+than $a_i$.
 This criteria ensures that once a local state in $x$ has been reached, reaching another local state

### 2015-02-13 parts/sa.tex
typo

@@
 (e.g., $\PHfrappes{a_i}{\reach_0}{\reach_1}$ and
-$\PHfrappes{b_j}{\reach_0}{\reach_1}$).
+$\PHfrappes{b_j}{\reach_1}{\reach_2}$).
 

### 2015-02-13 underapprox-tcrsig94/run-tcrsig94.sh
tcrsig94 test files

@@ -1,0 +1,43 @@
+#!/usr/bin/env bash
+
+# Date: jeudi 12 février 2015, 12:59:18 (UTC+0100)
+# Generated by:
+# sh run-generator.sh tcrsig94 'cd4 cd28 tcrlig' 'sre ap1 nfkb nfat sigmab'
+
+# File: tcrsig94.ph
+# Inputs: cd4 cd28 tcrlig
+# Outputs: sre ap1 nfkb nfat sigmab
+
+ph="tcrsig94.ph"
+outputs="sre ap1 nfkb nfat sigmab"
+mode=${1}
+
+echo -n "Start time: " && date
+echo 'Model: tcrsig94.ph'
+echo 'Inputs: cd4 cd28 tcrlig'
+echo 'Outputs: sre ap1 nfkb nfat sigmab'
+
+(echo -n "Start time: " && date) >&2
+(echo 'Model: tcrsig94.ph') >&2
+(echo 'Inputs: cd4 cd28 tcrlig') >&2
+(echo 'Outputs: sre ap1 nfkb nfat sigmab') >&2
+
+for cd4 in 0 1; do
+for cd28 in 0 1; do
+for tcrlig in 0 1; do
+
+init="cd4 $cd4, cd28 $cd28, tcrlig $tcrlig"
+echo "--- $init"
+for z in $outputs; do
+  echo "# $z 1"
+  ./unitrun.sh $mode "x" --no-debug --initial-state "$init" -i $ph $z 1
+  [ $? -eq 137 ] && echo '*** Killed ***'
+done
+
+done
+done
+done
+
+echo -n "End time: " && date
+(echo -n "End time: " && date) >&2
+

### 2015-02-13 underapprox-tcrsig94/run.sh

@@ -1,20 +1,0 @@
-#!/usr/bin/env bash
-ph="model.ph"
-outputs="sre ap1 nfkb nfat sigmab"
-#outputs="sigmab"
-#outputs="sre ap1 nfkb nfat"
-mode=${1}
-
-for i in 0 1; do
-	for j in 0 1; do
-		for k in 0 1; do
-			init="cd4 $i, cd28 $j, tcrlig $k"
-			echo "--- $init"
-			for z in $outputs; do
-				echo "# $z 1"
-				./unitrun.sh $mode "$i$j$k" --no-debug --initial-state "$init" -i $ph $z 1
-			done
-		done
-	done
-done
-

### 2015-02-13 parts/example.tex
large scale application examples (esp. EGFR)

--- 2015-02-03 parts/example.tex
@@
 can be used in such a case.
-In \pref{ssec:ex-tcrsig}, we apply our method to a large-scale model
-of the T-cell receptor signalling pathway
+In \pref{ssec:ex-tcrsig}, we apply our method to two large-scale models
 in order to show the scalability of our method.
@@
 
-\subsection{Large-scale Application: T-cell Receptor}
+\subsection{Large-scale Applications}
 \label{ssec:ex-tcrsig}
@@
 In order to support the scalability and applicability of our under-approximation of reachability, we
-apply our new approach to the analysis of a large-scale model of the T-cell receptor (TCR)
-signalling pathway \cite{tcrsig94}.
-This model gathers 94 interacting components and is specified as a Boolean network.
-The under-approximation presented in this paper has been implemented in the existing Pint
-software\footnote{Pint is freely available at \url{http://loicpauleve.name/pint}.}.
-
-The Boolean model has been automatically encoded into
+apply our new approach to the analysis of two large-scale models:
+a T-cell receptor (TCR) signalling pathway~\cite{tcrsig94}
+and an epidermal growth factor receptor (EGFR) signalling pathway~\cite{Samaga2009}.
+These models both gather around a hundred components and are detailed below.
+They are originally specified as Boolean networks,
+and have been automatically encoded into
 a Process Hitting model with two classes of priorities,
@@
 \footnote{Files are available at
-\url{http://maxime.folschette.name/underapprox-tcrsig94.zip}.}.
-Logical Networks being a subclass of AANs, this translation is straightforward.
-Then, we verified the reachability for the independent activation of 4 outputs of the signalling
-cascade (SRE, AP1, NFkB, NFAT) for all possible input combinations (CD4, CD28, TCRlig) using our
-new reachability under-approximation (answering either \emph{yes} or \emph{inconclusive}) and a 
-previously defined reachability over-approximation \cite{PMR12-MSCS} (answering either \emph{no} or
-\emph{inconclusive}).
-All result in conclusive decisions, and the under-approximation has been satisfied in 12 cases (over
+\url{http://maxime.folschette.name/underapprox-aan.zip}. \todo{Mettre en ligne}}.
+Boolean networks being a subclass of AANs, this translation is straightforward.
+In the following, we first present the Pint implementation,
+then the two models that were used for our tests,
+and the finally summarise the quantitative results of these tests.
+
+\subsubsection*{The Pint Implementation}
+
+The under-approximation presented in \pref{sec:sa} has been implemented
+in the existing Pint software%
+\footnote{Pint gathers tools related to the Process Hitting
+and is freely available at \url{http://loicpauleve.name/pint}.
+The release “2015-02-11” was used for these experiments.}.
+It comes in two versions:
+\begin{itemize}
+  \item One version consists in building the local causality graph once
+    and checking \pref{th:approxinf} on this graph only.
+    This version is polynomial in the size of the model,
+    and therefore scalable by nature by its low complexity.
+    However, it may be non-conclusive due to the presence of cycles
+    or dependent synchronizations that could be avoided.
+  \item The other version consists in checking \pref{th:approxinf}
+    on every sub-graph obtained by considering sub-sets of the nodes in $\Sol$
+    of the local causality graph.
+    This enumeration of “sub-solutions” may allow to find conclusive
+    responses by removing cycles or unnecessary local states in the graph.
+    However, due to its exhaustive nature,
+    it is exponential in the number of solutions of each objective,
+    and thus not as scalable.
+\end{itemize}
+In other words, when this implementation is unable to conclude with the
+local causality graph alone, it tries to enumerate sub-solutions
+in order to reach a conclusion.
+Although this search is guided in order to remove in priority
+the solutions that could create cycles or depended synchronizations,
+\todo{à confirmer}
+in the worst case all combinations have to be checked.
+Therefore, for the following tests, we capped the execution time
+of each call to Pint to 3 seconds,
+considering that the implementation is inconclusive above this threshold.
+
+The under-approximation presented in this paper can therefore answer
+either \emph{True} or \emph{Inconclusive} regarding the reachability
+of a given local state.
+We used it together with a previously defined
+reachability over-approximation~\cite{PMR12-MSCS}
+that allows to answer either \emph{False} or \emph{Inconclusive},
+but which was not tailored specifically, but still valid, for AANs.
+
+\subsubsection*{The T-cell Receptor Model}
+
+The TCR signalling pathway consists of 94 components.
+We checked the reachability for the independent activation of
+4 outputs of the signalling cascade (SRE, AP1, NFkB, NFAT)
+for all possible combinations of the 3 inputs (CD4, CD28, TCRlig).
+All result in conclusive decisions,
+and our under-approximation has been satisfied in 12 cases (over
 32) proving the satisfiability of the concerned reachability property in the encoded Boolean network
-(and non-satisfiability in the other cases).
+(and non-satisfiability in the other cases, using the previously existing over-approximation).
 
@@
 In other words, FkB$_1$ is never reachable, whatever the initial state of the inputs,
-the other outputs (SRE, AP1, NFAT) can be independently activated
+while the other outputs (SRE, AP1, NFAT) can be independently activated
 for some configurations of inputs.
 We thus want to check if these three outputs can be activated together,
-that is, if the activation of one of the outputs does not prevent the activation of one of the others.
+that is, if the activation of one of the outputs does not prevent the activation another one.
 For this, as proposed in \pref{ssec:simult-ua},
@@
 
-We held all these experiments on a laptop computer with a 2GHz processor
-and 1GB of RAM.
-Computations times were in the order of a few hundredths to tenths of a second
-in each case (reachability of $\reach_1$ included).
+\subsubsection*{The Epidermal Growth Factor Receptor Model}
+
+The EGFR signalling pathway gathers 104 components, amongst which one can distinguish
+21 inputs and 12 outputs.
+Analysing the consequences of the variations of all inputs
+would require too many tests;
+therefore, we selected 13 of them
+(erbb1, erbb2, erbb3, erbb4, bir, btc, egf, epr, nrg1a, nrg1b, nrg2b, nrg4, tgfa)
+and observed the impact of their variations on all outputs
+(elk1, creb, ap1, hsp27, actin\_reorg, cmyc, pro\_apoptotic, p70s6\_2, pkc, stat1, stat3, stat5).
+We note that some of the experiments trigger the exponential search
+of sub-solutions described above, and are cut after 3 seconds of computation
+(thus leading to \emph{Inconclusive} cases).
+These experiments represent about 10\% of all tests,
+amongst the remaining 90\%, while all the others are conclusive.
+We note that none of the tests terminated normally (without being cut after 3 seconds)
+with an inconclusive answer, which is however theoretically possible.
+
+\subsubsection*{Synthesis of the Results}
+
+The results of all tests performed with the implementation of our under-approximation
+are summarised in \pref{tab:results} (columns “AAN”).
+We held all these experiments on a personal computer,
+and computations times were in the order of a few tenths of a second to about one second.
 To give a comparison, we did the same experiments with a standard symbolic model-checker, libDDD
@@
 as a Petri net.
-However, due to the large scale of the model, the program runs out of memory for all the experiments,
-showing that this method is not scalable.
+However, due to the large scale of the model,
+this program takes at least several minutes to terminate,
+and runs out of memory for the majority of all experiments.
+%showing that this method is not scalable.
 Because standard model checkers are often PSPACE-complete~\cite{Harel02},
-using them to study the dynamics of a model is strongly limited to its size.
+using them to study the dynamics of a model is strongly limited by its size.
 On the other hand,
-our method is able to conclude with limited memory and computation time usage.
-Indeed, the under-approximation developed in this paper comes in two versions:
-\begin{itemize}
-  \item One version is polynomial in the size of the model,
-    and consists in building the saturated graph of local causality once
-    and checking \pref{th:approxinf} on this graph only.
-    This version is scalable by nature by its low complexity;
-  \item The other one is exponential in the size of the model,
-    and consists in checking \pref{th:approxinf}
-    on every sub-graph obtained by considering sub-sets of the nodes in $\Sol$
-    of the saturated graph of local causality.
-    Although not as scalable, it is still efficient on this example,
-    due to an adapted enumeration of these sub-sets.%
-\end{itemize}
-It is therefore expected that our work will be scalable to models that are larger,
+our method is able to conclude with limited memory and computation time usage
+in the majority of the cases,
+and is expected to be scalable to models that are even larger,
 even by orders of magnitude.
@@
 However, if these experiments allowed to obtain some information
-on this model to some extent,
-it did not provide a formal proof of the reachabilities that have been
-checked in the example above.
+on the TCR and EGFR models to some extent,
+they did not provide a formal proof of the reachabilities that have been
+checked in the examples above.
 Indeed, the semantics of Process Hitting (without classes of priorities)
-do not allow to model accurate Boolean gates,
-thus leading to some unwanted behaviours that take the form of temporal shifts.
-Only the adding of classes of priorities allows to remove these temporal shifts,
+does not allow to model accurate Boolean gates,
+thus leading to some unwanted spurious behaviours
+that especially take the form of temporal shifts.
+The adding of classes of priorities allows to remove these temporal shifts,
 as explained in~\cite{FPMR13-CS2Bio},
@@
 Therefore, only the method presented in this paper provides a formal proof that
-the observed behaviours are the result of the true dynamics of the system,
-which was originally described in a format equivalent to Logical Networks.
+the observed behaviours are the result of the true dynamics of the systems.
+The same experiments have been conducted with the previous version
+of the under-approximation and reported alongside in \pref{tab:results}
+(in columns “PH”).
+We note that indeed, about 10\% of the positive results regarding the EGFR model
+could not be proven with our new under-approximation,
+and are thus still formally uncertain.
+
+\definecolor{lightgraycell}{gray}{0.8}
+\newcommand{\grcl}{\cellcolor{lightgraycell}}
+
+\begin{table}[htp]
+  \centering
+  \begin{tabular}{|c||c|c||c|c|}
+  \hline
+    & \multicolumn{2}{c||}{TCR} & \multicolumn{2}{c|}{EGFR} \\
+  \hline
+  \hline
+    Inputs & \multicolumn{2}{c||}{3} & \multicolumn{2}{c|}{13} \\
+  \hline
+    Outputs & \multicolumn{2}{c||}{4 + $\reach$} & \multicolumn{2}{c|}{12} \\
+  \hline
+    Total tests & \multicolumn{2}{c||}{40} & \multicolumn{2}{c|}{98'304} \\
+  \hline
+  \hline
+               & PH        & AAN       & PH               & AAN              \\
+  \hline
+  \hline
+    True       & 16 (40\%) & \grcl 16 (40\%) & 74'268 (75,55\%) & \grcl 64'282 (65,39\%) \\
+  \hline
+    Inconclusive & 0 (0\%) & \grcl 0 (0\%)   & 0 (0\%)          & \grcl 9'986 (10,16\%)  \\
+  \hline
+    False      & \multicolumn{2}{c||}{24 (60\%)} & \multicolumn{2}{c|}{24'036 (24,45\%)} \\
+  \hline
+  \hline
+    Max time   & 0.043s    & \grcl 0.20s     & 0.37s            & \grcl 0.87s            \\
+  \hline
+    Total time & <1s       & \grcl <1s       & 45min            & \grcl 9h50min          \\
+  \hline
+  \end{tabular}
+  \caption{\label{tab:results}%
+    Results of the tests on large-scale examples.
+    The “AAN” column gives the related results on AAN models,
+    using the under-approximation presented in this paper,
+    while the “PH” column gives the results for PH models
+    using cooperative sorts to model actions with multiple hitters,
+    and using the under-approximation of~\cite{PMR12-MSCS}.
+    The lines labelled “True”, “Inconclusive” and “False” lines give respectively
+    the number of positive, cut and negative answers,
+    while “Max time” and “Total time” depict respectively
+    the maximum time of the individual computations (except those cut after 3 seconds)
+    and the overall execution time of all tests (including those cut after 3 seconds).
+    The greyed cells highlight the results that are proper to the
+    under-approximation presented in this paper.
+  }
+\end{table}
 

### 2015-02-13 parts/example.tex
detailed small example with scenario extraction

@@
 
-Finally, the static analysis results presented in
-\pref{ssec:ua} and \pref{ssec:ordered-ua} can be used to check if the model is functional,
+\medskip
+
+At this point, the static analysis results presented in
+\pref{ssec:ua} can be used to check if the model is functional,
 \ie if gene $a$ can oscillate, thus leading to the formation of stripes.
-Starting from context $\ctx = \PHstate{f_1, a_0, c_0}$,
-we thus want to check the reachability of
-$\w = \PHobj{a_0}{a_1} \PHconcat \PHobj{a_1}{a_0} \PHconcat \PHobj{a_0}{a_1}$.
-Rather than checking this whole objective sequence with \pref{th:approxinf},
-we break it using \pref{thm:ordered-ua}.
-We first build the first saturated graph of local causality
-based on the first objective, $\w_1 = \PHobj{a_0}{a_1}$, in the initial context $\ctx$.
+Starting from context $\ctx^1 = \PHstate{f_1, a_0, c_0}$,
+we thus want to check the reachability of $\myp^1 = a_1$;
+then, starting from any new state obtained,
+we want to check the reachability of $\myp^2 = a_0$,
+and finally $\myp^3 = a_1$ once again to ensure that we entered a cycle.
+This consists in using \pref{th:approxinf} several times
+to check these reachabilities successively.
+
+We first build the local causality graph $\thisB{\myp^1}{\ctx^1}$
+related to the reachability of $\myp^1 = a_1$ from the initial state $\ctx^1$.
 This graph is depicted in \pref{fig:metazoan-sa}(left).
-%and given \pref{tmh:approxinf}, we have:
-We have especially:
-\[\allprocs(\thisB{\w_1}{\ctx}) = \{ a_0, c_0, f_1 \} \enspace \text{and}\]
-\[\lastprocs(\PHobj{a_0}{a_1}) = \{\{ a_1, c_0, f_1 \}\} \enspace.\]
-Therefore, the second step consists of computing the saturated graph of local causality
-of the objective $\w_2 = \PHobj{a_1}{a_0}$
-in the context
-\[\ctx' = \ctx \Cap \allprocs(\thisB{\w_1}{\ctx}) \Cap \lastprocs(\PHobj{a_0}{a_1}) = \PHstate{a_1, c_0, f_1} \enspace.\]
-This second graph is given in \pref{fig:metazoan-sa}(middle).
-Finally, because
-\[\allprocs(\thisB{\w_2}{\ctx'}) = \{ a_1, c_0, c_1, f_1 \} \enspace \text{and}\]
-\[\lastprocs(\PHobj{a_1}{a_0}) = \{\{ a_0, c_1 \}\} \enspace,\]
-The last step is then checking
-the objective $\w_3 = \PHobj{a_0}{a_1}$
-in the context
-\[\ctx'' = \ctx' \Cap \allprocs(\thisB{\w_2}{\ctx'}) \Cap \lastprocs(\PHobj{a_1}{a_0}) = \PHstate{a_0, c_1, f_1} \enspace.\]
-This last graph is depicted in \pref{fig:metazoan-sa}(right).
-In conclusion, by using \pref{thm:ordered-ua} on these saturated graphs of local causality,
-we can conclude that the initial objective $\w$ is reachable,
+\pref{th:approxinf} allows to conclude that this reachability is true.
+One can thus extract a concretizing scenario from this local causality graph
+with a traversal of the graph, as explained in \pref{ssec:concret}.
+Such a traversal is detailed in \pref{tab:concret-metazoan};
+the scenario extracted from this example is:
+$\emptyseq \concat \emptyseq \concat \PHfrappes{c_0, f_1}{a_0}{a_1} =
+\PHfrappes{c_0, f_1}{a_0}{a_1}$.
+Another traversal would consist in visiting node $f_1$ before node $c_0$
+when first descending from node $\{ c_0, f_1 \}$;
+however, the same scenario would be extracted.
+As there exists no other traversal, we thus have in this case:
+$\Delta(\thisB{\myp^1}{\ctx^1}) = \{ \PHfrappes{c_0, f_1}{a_0}{a_1} \}$.
+
+\newcommand{\xproc}[1]{#1}
+%\newcommand{\xsol}[1]{\circ^{{#1}}}
+\newcommand{\xsol}{\circ}
+
+\begin{table}[htp]
+  \centering
+  \begin{tabular}{|c|c|c|l|l|l|}
+    \hline
+    \# & Dir. & Node & Marking & Output & State \\\hline\hline
+    1  & $\searrow$ & $\xproc{a_1}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
+    2  & $\searrow$ & $\PHobj{a_0}{a_1}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
+    3  & $\searrow$ & $\xsol$ & $\PHfrappes{c_0, f_1}{a_0}{a_1}$ &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
+    4  & $\searrow$ & $\{ c_0, f_1 \}$ & $\{ c_0, f_1 \}$ &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
+    \phantom{*}%
+    5* & $\searrow$ & $\xproc{c_0}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
+    6  & $\searrow$ & $\PHobj{c_0}{c_0}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
+    7  & $\searrow$ & $\xsol$ & $\emptyseq$ & $\emptyseq$ & $\PHstate{f_1, a_0, c_0}$ \\\hline
+    8  & $\nearrow$ & $\PHobj{c_0}{c_0}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
+    9  & $\nearrow$ & $\xproc{c_0}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
+    10 & $\nearrow$ & $\{ c_0, f_1 \}$ & $\{ f_1 \}$ &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
+%    \phantom{*}%
+    11 & $\searrow$ & $\xproc{f_1}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
+    12 & $\searrow$ & $\PHobj{f_1}{f_1}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
+    13 & $\searrow$ & $\xsol$ & $\emptyseq$ & $\emptyseq$ & $\PHstate{f_1, a_0, c_0}$ \\\hline
+    14 & $\nearrow$ & $\PHobj{f_1}{f_1}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
+    15 & $\nearrow$ & $\xproc{f_1}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
+    16 & $\nearrow$ & $\{ c_0, f_1 \}$ & $\emptyset$ &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
+    17 & $\nearrow$ & $\xsol$ & $\emptyseq$ & $\PHfrappes{c_0, f_1}{a_0}{a_1}$ & $\PHstate{f_1, a_1, c_0}$ \\\hline
+    18 & $\nearrow$ & $\PHobj{a_0}{a_1}$ &  &  & $\PHstate{f_1, a_1, c_0}$ \\\hline
+    19 & $\nearrow$ & $\xproc{a_1}$ &  &  & $\PHstate{f_1, a_1, c_0}$ \\\hline
+  \end{tabular}
+  \caption{\label{tab:concret-metazoan}%
+    Example of the extraction of a concretizing scenario
+    from the local causality graph of \pref{fig:metazoan-sa}(left),
+    by using the algorithm of \pref{ssec:concret}.
+    The first column denotes the step number in the traversal,
+    the second depicts the direction of traversal,
+    either “$\searrow$” for descending or “$\nearrow$” for ascending,
+    the third one is the name of the node,
+    the fourth one gives the marking when the node is left,
+    the fifth one gives the actions output by the algorithm
+    and the last column gives the current state of the model when leaving each node.
+    In step \#5, marked with an asterisk,
+    the traversal visits node $c_0$, but this was arbitrarily chosen
+    amongst the set $\{ c_0, f_1 \}$.
+    Another traversal thus consists in visiting node $f_1$ first,
+    although in this example it does not change the result.
+  }
+\end{table}
+
+We denote in the following:
+$\ctx^2 = \PHstate{f_1, c_0, a_0} \play \PHfrappes{c_0, f_1}{a_0}{a_1} =
+\PHstate{f_1, c_0, a_1}$
+the state resulting from the play of a scenario concretizing
+$\myp^1$ in $\ctx^1$.
+As explained in \todo{ref succ-reach},
+One can use this resulting state in order to carry on with another
+successive reachability,
+such as the reachability of $\myp^2 = a_0$ in this case.
+The local causality graph used to check the reachability of $\myp^2$
+from $ctx^2$ is given in \pref{fig:metazoan-sa}(middle).
+The same reasoning allows to conclude that this reachability is true, and
+to extract the following set of concretizing scenarios:
+$\Delta(\thisB{\myp^2}{\ctx^2}) =
+\{ \PHfrappem{a_1, f_1}{c_0}{c_1} \concat \PHfrappem{c_1}{a_1}{a_0} \}$.
+We note that once again, two traversals are possible
+(by visiting node $a_1$ before or after note $f_1$)
+but both output the same scenario, and therefore end up in the same sate
+$\ctx^3 = \PHstate{f_1, a_0, c_1}$.
+Finally, the last local causality graph $\thisB{\myp^3}{\ctx^3}$,
+depicted in \pref{fig:metazoan-sa}(right),
+allows to conclude that this final reachability is true.
+
+In conclusion, by using \pref{th:approxinf} on these local causality graphs,
+and the traversal of \pref{ssec:concret} to determine
+the starting states of the following reachability step,
+we showed that it is possible to reach successively
+$a_1$, $a_0$ and $a_1$
 and thus that the AAN of \pref{fig:metazoan-ph} is functional.

### 2015-02-13 parts/sa.tex
detailed small example with scenario extraction

--- 2015-02-13 parts/sa.tex
@@
 
-A classical approach for determining if a local state of an automaton can be
-reached from a given initial state is to build sequences of transitions from the initial state until a state
+A classical approach for determining if a local state of an automaton can be reach from a
+given initial state is to build sequences of transitions from the initial state until a state
 containing the given local state is reached.
@@
 
-Our approach relies on abstractions of scenarios (\pref{ssec:abstr-sce}) that have been introduced in
+Our approach relies on abstractions of scenarios that have been introduced in
 \cite{PMR12-MSCS} for the static analysis of reachability in the Process Hitting framework,
@@
 In this paper, we generalize the static analysis for the case of the under-approximation of
-reachability in any AAN (\pref{ssec:ua}).
+reachability in any AAN.
 
-In \pref{ssec:concret}, we detail a procedure to extract a witness scenario
-concretizing a given local state reachability property.
-Finally, we discuss in \pref{ssec:ordered-ua} how the static analysis can be
-extended to sequential (sub)states reachability properties.
+\todo{outline}
 
@@
 Such an objective is written $\PHobjp{a}{i}{j}$.
-Successive objectives are described with objective sequences.
+Successive objectives are described with objective sequences (\pref{def:obj}).
 
@@
   The set of all objective sequences is denoted by $\OS$.
-  Given $\w\in\OS$, $\PHsort(\w) \DEF \{\PHsort(\w_i)\mid i\in\indexes{\w}\}$.
-For each automaton $a\in\PHsort(\w)$,  the first local state of $a$ referenced in
-$\w$ is denoted by $\first_a(\w) \DEF \target{\w_m}$, where $m=\min\{n\in\indexes{\w}\mid \PHsort(\w)=a\}$.
-  The set of objective sequences starting in a state $s\in\PHl$ are denoted by
-  $\OS(s)\DEF \{\w\in\OS\mid\forall a\in\PHsort(\w), \first_a(\w)\in s\}$.
 \end{definition}
@@
 $w\ltw w'$ if and only if there exists a mapping between all the objective bounces of $w'$ in $w$
-that preserve the sequentiality, provided that each automaton starts in the same
-local state.
+that preserve the sequentiality.
+
+\todo{support compatibility}
 
@@
 $\w\ltw\w'$ if and only if
-$|\w|\geq|\w'|$,
-$\forall a\in\PHsort(\w'), a\in\PHsort(\w) \wedge \first_a(\w')=\first_a(\w)$;
-and there exists a mapping $\phi: \indexes{\w'}\mapsto \indexes{\w}$ such that
+$|\w|\geq|\w'|$ and
+there exists a mapping $\phi: \indexes{\w'}\mapsto \indexes{\w}$ such that
 $\forall n,m \in\indexes{\w'}, n<m \Leftrightarrow \phi(n)<\phi(m)$,
 and
-$\forall n\in\indexes{\w'}, \bounce{\w'_n}=\bounce{\w_{\phi(n)}}$.
+$\forall n\in\indexes{\w'}, \bounce{\w'_n}=\bounce{\w_{\phi(n)}}$
 \end{definition}
@@
 (part of) the successive state changes of the automata.
-We denote by $\concr(\w)$ (\pref{def:concr}) the set of scenarios matching with an objective sequence
+We denote by $\concr(\w)$ (\pref{def:concr}) the set of scenarios concretising an objective sequence
 $\w$ in the state $s\in\PHs$.
@@
 
+\todo{compatibility of $\w$ with $s$}
+
 \begin{definition}[$\concr: \OS \to \powerset(\Sce)$]\label{def:concr}
-Given a state $s\in\PHl$ and an objective sequence
-$\w\in\OS(s)$, $\concr(\w)$ is the set of scenarios matching with $\w$:
+Given $\w\in\OS$, $\concr(\w)$ is the set of scenarios concretising $\w$ in the
+state $s$:
 \begin{align*}
-\concr(\w) \DEF \{ \delta\in\Sce(s)\mid &
-\w^\vartriangle\neq \emptyseq\Rightarrow
-\bounce{\delta_{\card\delta}} = \bounce{\w_{\card\w}}
+\concr(\w) \DEF \{ \delta\in\Sce(s)\mid & (\w^\vartriangle=\emptyseq \wedge
+\delta=\emptyseq)  \vee (
+\w^\vartriangle\neq \emptyseq\wedge
 \\ &
@@
 \end{lemma}
-
-Given a non-empty set $\Delta\subseteq\Sce(s)$ of non-empty scenarios that have a common last bounce
-($\exists a_i\in\Proc, \forall\delta\in\Delta,
-\bounce{\delta_{\card\delta}}=a_i$), one can define an abstraction $\alpha_s$ of
-such a set as the smallest objective sequence $\w\in\OS(s)$ such that
-$\bounce{\w_{\card\w}} = \bounce{\delta_{\card\delta}}, \delta\in\Delta$
-and
-$\forall\delta\in\Delta, \exists \phi:\indexes{\w}\mapsto\indexes{\delta}
-    (\forall n,m\in\indexes{\w}, n<m \Leftrightarrow \phi(n)\leq\phi(m))
-	\wedge \forall n\in\indexes{\w},
-	  \bounce{\w_n} \in s\play\delta_{1..\phi(n)})$.
-In such a setting, $\alpha_s$ and $\concr$ form a Galois connection between sets
-of scenarios and objective sequences.
 
@@
 
-\begin{example}
-Given the AAN of \pref{fig:ph-livelock},
-$\BS(\obj{c_0}{c_1}) = \{\PHfrappes{a_1,b_1}{c_0}{c_1}\}$;
-and 
-$\BS(\obj{a_0}{a_1}) = \{\PHfrappes{b_0}{a_0}{a_1}\}$.
-\end{example}
+\todo{example}
 
-From \pref{def:bs}, we can derive that any scenario matching with an objective includes all the
+From \pref{def:bs}, we can derive that any scenario concretising an objective includes all the
 actions of one of the bounce sequences of the objective (\pref{lem:bs-concr}).
@@
 
-Given one initial objective, one could then iteratively refine the objective into objective
-sequences following its bounce sequences:
+Given one initial objective, one could then recursively refine the objective into objective
+sequences following its bounce sequences \cite{PMR12-MSCS}:
 the refinement of objective $P$ with $\zeta\in\BS(P)$ would consists in prepending to $P$ the
@@
 the generalization of the refinement to an objective sequence would require to consider all possible
-interleaving between the refinements \cite{PMR12-MSCS}.
+interleaving between the refinements.
 
-For example, given the AAN of \pref{fig:ph-livelock},
-in the state $\langle a_0,b_0,c_0\rangle$,
-the objective $\obj{a_0}{a_1}$ can be refined in the objective sequence
-$\obj{b_0}{b_0}\concat\obj{a_0}{a_1}$
-and
-the objective $\obj{c_0}{c_1}$ can be refined in the objective sequence
-$\obj{a_0}{a_1}\concat\obj{b_0}{b_1}\concat\obj{c_0}{c_1}$
-or
-$\obj{b_0}{b_1}\concat\obj{a_0}{a_1}\concat\obj{c_0}{c_1}$
-(which can then be further refined).
-
-These refinements can be summarized with a so-called Local Causality Graph (LCG).
+These refinements can be summarized compactly with a so-called Local Causality Graph (LCG).
 Given an initial context $\ctx$ and a local state $\myp\in\Proc$,
@@
 (\pref{def:lcg}).
-A node in $\cwV\cap\Obj$ represents an objective to refine.
-Such a node is related to nodes in $\cwV\cap\Sol$ which represent sets of hitter set of a
-bounce sequence of the objective (one for each bounce sequence in $\BS(P)$):
+A node in $\Obj$ represents an objective that have to be refined.
+Such a node can then be related to nodes in $\Sol$ which represents a set of hitter set of a
+bounce sequence of the objective:
 given an objective $P$, if $\zeta\in\BS(P)$, $\abstr\zeta \DEF \{\PHhitter(\zeta_n) \mid
@@
 (\pref{def:lcg}-\ref{lcg-obj-sol}).
-For each hitter set $ps\in\abstr\zeta$,
-the node $\langle P,\abstr\zeta\rangle\in\cwV\cap\Sol$ is
-related to the node $ps\in\sSol$
+Given a node $\langle P,\abstr\zeta\rangle\in\cwV\cap\Sol$, for each $ps\in\abstr\zeta$,
+it is related to a node $ps\in\sSol$
 (\pref{def:lcg}-\ref{lcg-sol-sync}).
-Then, each node $ps\in\sSol$ is related to each local state $a\in\Proc$
+A node $ps\in\sSol$ is then related to each $a\in\Proc$
 (\pref{def:lcg}-\ref{lcg-sync-ls}).
-Each local state node $a_i\in\cwV\cap\Proc$,
-is related to each objective $\obj{a_j}{a_i}$ where
-$a_j$ is either in the initial context $\ctx$, or
-is a local state node in the LCG
+Given a node $a_i\in\cwV\cap\Proc$, for each $a_j\in\ctx$ or $a_j\in\cwV\cap\Proc$,
+it is related to an objective $\obj{a_j}{a_i}$
 (\pref{def:lcg}-\ref{lcg-ls-obj}).
@@
 
-\todo{the procedure is non-deterministic, make it deterministic? (list all the
-scenarios}
-
 \begin{itemize}
@@
 
-\todo{name + prototype of the procedure}
+The execution of such a traversal outputs a scenario.
+We denote $\Delta(\cwB)$ the set of all scenarios extracted from the
+local causality graph $\cwB$.
+Indeed, several scenarios may exist for a same graph,
+generated by the successors that can be arbitrarily chosen
+in this algorithm.
 
-\todo{example}
+\subsection{Sequential Under-approximation}
+\label{ssec:ordered-ua}
 
-\subsection{Addressing Sequential and Sub-state Reachability}
-\label{ssec:ordered-ua}
+In this section, we briefly explain an alternative sufficient condition that
+can be applied when looking for scenarios that successively reach a sequence of local states (e.g.,
+first reach $a_j$, then later $b_k$, \ldots).
+
+The approach proposed in this sub-section essentially applies the previous under-approximation for
+the first local states, and then computes a set of contexts that may be considered as the starting
+point for the next local states.
+In that way, the local states to reach are taken into account separately, which implies that only a
+subset of scenarios can be captured.
+%However, because each iteration focuses on a smaller part of the network, this
+%sequential under-approximation may be more conclusive.
+
+\todo{computes possible outcomes from the LCG, gives it as context for the next stage}.
+
+\subsection{Reachability of a State}
 \label{ssec:simult-ua}
@@
 
-In this section, we briefly discuss how the presented static analysis for local
-state reachability properties can be extended to sequential (sub)states
-reachability properties.
-
-\paragraph{Sub-state reachability.}
-Given an AAN $\PH = (\PHs, \PHl, \PHh)$,
-a sub-set of automata local states
-$ps = \{ a_i \in\Proc\mid a\in\PHs, a_i\in\PHl_a\}$,
-the reachability from $s\in\PHl$ of a state $s'\in\PHl$ such that
-$ps\subset s'$ is equivalent to the reachability of the local state
-$\reach_1$ from a state $s\uplus\langle\reach_0\rangle$
-in the AAN
-$\PH' = (\PHs', \PHl', \PHh')$ with:
-$\PHs' = \PHs \cup \{ \reach \}$, $\PHl' = \PHl \times \PHl_\reach$,
-where $\PHl_\reach = \{ \reach_0, \reach_1 \}$,
-and $\PHh' = \PHh \cup \{ \PHhit{ps}{\reach_0}{\reach_1} \}$.
-
+The reachability property studied so far concerns a single local state at a time.
+However, we remark that the reachability of a global state or a sub-state can be
+addressed with the very same analysis by introducing a dedicated automata.
 Such analysis was not possible with the Process Hitting framework,
@@
 
-\paragraph{Sequential reachability.}
-Given a sequence of local state to reach (e.g., reach $a_i$, then $b_j$),
-one can use the same approach as for sub-state reachability by introducing
-a new automaton $\reach$ having $n+1$ local states where $n$ is the size of the
-sequence of reachability and $n$ actions making it bounce from $\reach_0$ to
-$\reach_n$ with hitters corresponding the successive local states
-(e.g., $\PHfrappes{a_i}{\reach_0}{\reach_1}$ and
-$\PHfrappes{b_j}{\reach_0}{\reach_1}$).
+In order to check the reachability of a global state $s \in \PHl$,
+let $\PH = (\PHs, \PHl, \PHh)$ be an AAN.
+We define a new AAN $\PH' = (\PHs', \PHl', \PHh')$ with:
+$\PHs' = \PHs \cup \{ \reach \}$, $\PHl' = \PHl \times \PHl_\reach$,
+where $\PHl_\reach = \{ \reach_0, \reach_1 \}$,
+and $\PHh' = \PHh \cup \{ \PHhit{\toset{s}}{\reach_0}{\reach_1} \}$.
+Given an initial context $\ctx$, the reachability of $s$ in $\PH$
+is equivalent to the concretization of $\PHobjp{\reach}{0}{1}$ in $\PH'$
+from the initial context $\ctx \cup \{ \reach_0 \}$,
+which can be efficiently under-approximated using \pref{th:approxinf}.
 
-An alternative approach is to use the extraction of a scenario of the previous
-sub-section:
-given the initial state, and a first local state reachability property, one
-compute a possible scenario witnessing this reachability.
-Then the next local state reachability properties is computed from the
-state that outcomes from the latter scenario.
+It is of course also possible to compute the reachability
+of a sub-state $s \in \PHsubl[\PHl]_S$ of a set of components $S \subseteq \PHs$
+with the same method.
+One can also check the reachability of a set of states $\Lambda \subseteq \PHl$
+by creating several actions
+$\PHhit{\toset{s}}{\reach_0}{\reach_1}$ in $\PHh$ for each state $s \in \Lambda$.

### 2015-02-13 parts/def-ph.tex

@@
 
+\begin{comment}
 \begin{definition}[$\Cap : \PHl \times \PHproc \rightarrow \PHl$]
@@
 \end{definition}
+\end{comment}
 % The notation $\toset{ps}$ represents the set of all elements in $ps$
@@
   if and only if $A \subseteq s$ and $\PHget{s}{b} = b_j$.
-  In such a case, $(s \PHplay h)$ stands for the state resulting from the play of the action $h$ in $s$, which is defined by: $(s \PHplay h) = s \Cap b_k$.
+  In such a case, $(s \PHplay h)$ stands for the state resulting from the play of the action $h$ in $s$, which is defined by:
+    $(s \PHplay h)_b = b_k$
+	and
+	$\forall a\in\PHs, a\neq b, (s\PHplay h)_a = s_a$.
   Moreover, we denote: $s \PHPtrans (s \PHplay h)$.
@@
 
+\begin{comment}
 We also extend the override operator to contexts (\pref{def:ctxcap}).

### 2015-02-13 parts/example.tex

@@
 This consists in using \pref{th:approxinf} several times
-to check these reachabilities successively.
+to check these reachabilities successively,
+by splitting it following \pref{ssec:ordered-ua}.
 
@@
 
-In conclusion, by using \pref{th:approxinf} on these local causality graphs,
-and the traversal of \pref{ssec:concret} to determine
-the starting states of the following reachability step,
+In conclusion, by following \pref{ssec:ordered-ua},
 we showed that it is possible to reach successively

### 2015-02-13 parts/models-ph-php.tex
revised section 2
remove section 4.1 (ADN to AAN)
fix section mistake
remove \mod commands

@@
-\subsection{Asynchronous Automata Networks with classes of priorities}
-\label{ssec:flattening}
+\section{Asynchronous Automata Networks with classes of priorities}
+\label{sec:flattening}
 
@@
 
-\begin{definition}[Dynamics of an AAN$k$ ($\PHPtrans$)]
+\begin{definition}[Semantics of an AAN$k$ ($\PHPtrans$)]
 \label{def:playp}
@@
   In such a case, $(s \PHplay h)$ stands for the state resulting from the play
-  of the action $h$ in $s$, which is defined by: $(s \PHplay h) = s \Cap b_k$.
+  of the action $h$ in $s$, which is defined by: 
+    $(s \PHplay h)_b = b_k$
+	and
+	$\forall a\in\PHs, a\neq b, (s\PHplay h)_a = s_a$.
   Moreover, we denote: $s \PHPtrans (s \PHplay h)$.
@@
     \wedge
-      \left( \bigwedge_{\substack{g \in \ov{\PHh}^{(n)}\\\modMF{1 <} n < \prio(h)}}
+      \left( \bigwedge_{\substack{g \in \ov{\PHh}^{(n)}\\1 < n < \prio(h)}}
       \neg \left( \target{g} \wedge \left(\bigwedge_{c_l \in \hitter{g}} c_l\right)\right) \right)
-%   \moda{\bigwedge_{\substack{b_z \in \PH_b\\b_z \neq b_x}} \neg b_z}
   \]

### 2015-02-13 parts/sa.tex

--- 2015-02-13 parts/sa.tex
@@
 
-\todo{name + prototype of the procedure}
-
-\todo{example}
+The execution of such a traversal outputs a scenario.
+We denote $\Delta(\cwB)$ the set of all scenarios extracted from the
+local causality graph $\cwB$.
+Indeed, several scenarios may exist for a same graph,
+generated by the successors that can be arbitrarily chosen
+in this algorithm.
+An example of such a traversal is given on a small example
+in \pref{ssec:ex-metazoan}.
 

### 2015-02-13 parts/example.tex
todo--

@@
 \label{ssec:ex-metazoan}
-
-\todo{Check section and remove $\procs$ and $\lastprocs$.}
 
@@
 $\myp^1$ in $\ctx^1$.
-As explained in \todo{ref succ-reach},
+As explained in \pref{ssec:ordered-ua},
 One can use this resulting state in order to carry on with another

### 2015-02-13 parts/models-ph-php.tex
reintroduce PHsubl for the flattening

@@
 
-This translation is based on the notion of \emph{playability property} defined in \pref{def:pp}
+The translation given in the following relies on the notion of \emph{sub-state},
+which is a set of local states containing at most one local state of each automata.
+Thus, a sub-state can be considered as a partial state.
+This notion if formally expressed in \pref{def:substate}.
+
+\begin{definition}[Sub-state ($\PHsublize{\PHl}$)]
+\label{def:substate}
+  If $S \subseteq \PHs$ is a set of automata, a sub-state on $S$ is an element of:
+  $\PHsubl[\PHl]_S \DEF \{ \toset{\rho} \subseteq \Proc \mid
+    \rho \in \bigtimes{a \in S} \PHl_a \}$
+  where the notation $\toset{\rho}$ represents
+  the set of components of the Cartesian product $\rho$,
+  as defined on page~\pageref{notations}.
+  The set of all sub-states is denoted by:
+  $\PHsubl[\PHl] \DEF \bigcup_{S \in \powerset(\PHs)} \PHsubl[\PHl]_S$.
+  Furthermore, if $\mysigma \in \PHsubl[\PHl]$ and $s \in \PHl$, we note:
+    \[\mysigma \subseteq s \EQDEF \forall a_i \in \Proc, a_i \in \mysigma \Rightarrow a_i \in s\]
+\end{definition}
+
+The translation of an AAN$k$ into an AAN
+is based on the notion of \emph{playability property} defined in \pref{def:pp}
 which is a Boolean formula where the atoms are local states of $\ov{\PH}$.
@@
   $h$ is playable in $s$ if and only if:
-  \[\target{h} \in s \wedge \exists \mysigma \subseteq s, \Fsem{\Fop{h}}{\mysigma} \enspace.\]
+  \[\target{h} \in s \wedge \exists  \mysigma \in \PHsubl,
+    \mysigma \subseteq s \wedge \Fsem{\Fop{h}}{\mysigma} \enspace.\]
 \end{lemma}
@@
     \item $\PHh = \{
-      \PHfrappe{(\toset{\mysigma} \setminus \{ \target{h} \})}{\target{h}}{\bounce{h}} \mid
+      \PHfrappe{(\mysigma \setminus \{ \target{h} \})}{\target{h}}{\bounce{h}} \mid
       h \in \ov{\PHh} \wedge \n \geq 1 \wedge i \in \segm{1}{\n} \wedge

### 2015-02-13 parts/def-ph.tex
remove comments

@@
 If $a_i \in \PHl_a$, we define the notation $a_i \in s \EQDEF \PHget{s}{a} = a_i$.
-
-\begin{comment}
-\pref{def:substate} defines the notion of sub-state on a set of automata, that is used to focus on the interesting part of a complete state.
-We note that a state is \textit{a fortiori} a sub-state.
-The override of a state $s$ by a local state $a_i$ (or by a set of local states)
-is defined in \pref{def:statecap} as the same state in which the local state of automaton $a$ has been replaced by $a_i$;
-this is used to define the semantics of an AAN in \pref{def:play}.
-%
-\begin{definition}[Sub-states ($\PHsublize{\PHl}$)]
-\label{def:substate}
-  If $S \subseteq \PHs$ is a set of automata, a sub-state on $S$ is an element of:
-  $\PHsubl[\PHl]_S \DEF \bigtimes{a \in S} \PHl_a$.
-  The set of all sub-states is:
-  $\PHsubl[\PHl] \DEF \bigcup_{S \in\powerset(\PHs)} \PHsubl[\PHl]_S$.
-
-  \noindent
-  Furthermore, if $\mysigma \in \PHsubl[\PHl]$ and $s \in \PHl$, we note:
-    \[\mysigma \subseteq s \EQDEF \forall a_i \in \Proc, a_i \in \toset{\mysigma} \Rightarrow a_i \in s\]
-  where the notation $\toset{\mysigma}$ represents
-  the set of components of the Cartesian product $\mysigma$,
-  as defined on page~\pageref{notations}.
-\end{definition}
-
-In the following, we will also use the notation:
-$\PHsublset[\PHl] = \{ \toset{ps} \subseteq \Proc \mid ps \in \PHsubl[\PHl] \}$
-and, by extension:
-$\forall s \in \PHl, \forall ps \in \PHsublset[\PHl],
-  ps \subseteq s \EQDEF \forall a_i \in ps, a_i \in s$.
-We note also that for all action $h \in \PHh$, by definition of an AAN, we have:
-$\hitter{h} \in \PHsublset[\PHl]$.
-
-\end{comment}
-
-\begin{comment}
-\begin{definition}[$\Cap : \PHl \times \PHproc \rightarrow \PHl$]
-\label{def:statecap}
-  Given a state $s \in \PHl$ and a local state $a_i \in \PHproc$, $(s \Cap a_i)$ is the state defined by:
-  $\PHget{(s \Cap a_i)}{a} = a_i \wedge \forall b \neq a, \PHget{(s \Cap a_i)}{b} = \PHget{s}{b}$.
-  We can also extend this definition to a set $ps$ of local states,
-  under the condition that all local states of $ps$ are from different automata,
-  by the override of each local state independently:
-  $\forall ps \in \PHsublset[\PHl], s \Cap ps = s \underset{a_i \in ps}{\Cap} a_i$.
-\end{definition}
-\end{comment}
-% The notation $\toset{ps}$ represents the set of all elements in $ps$
-% (which is not a set but a tuple)
-% as defined on page~\pageref{notations}.
 
@@
 and for all $ps \in \powerset(\PHproc)$ or $ps \in \PHl$, $ps \subseteq \ctx \EQDEF \forall a_i \in ps, a_i \in \ctx$.
-\begin{comment}
-A sequence of actions $\delta$ is \emph{playable} in a context $\ctx$ if and only if 
-$\exists s \subseteq \ctx, \delta \in \Sce(s)$.
-We denote then: $\delta \in \Sce(\ctx)$,
-and the play of $\delta$ in $\ctx$ is $\ctx \PHplay \delta = \ctx \Cap \ceil(\delta)$,
-where $\ceil(\delta)$ is the set containing the last local state in the sequence $\delta$ (hitter or bounce) of every automaton mentioned in $\delta$.
-
-\end{comment}
-
-\begin{comment}
-We also extend the override operator to contexts (\pref{def:ctxcap}).
-\begin{definition}[$\Cap: \Ctx \times \powerset(\PHproc) \rightarrow \Ctx$]
-\label{def:ctxcap}
-  For any $\ctx\in\Ctx$ and set of local states $ps \in \powerset(\PHproc)$,
-  the override of $\ctx$ by $ps$ is noted $\ctx \Cap ps$ and is defined by:
-  \[ \forall a \in \PHs, \PHget{(\ctx \Cap ps)}{a} \DEF
-  \begin{cases}
-    \{ p \in ps \mid \PHsort(p)=a \} & \text{if } \exists p \in ps, \PHsort(p)=a,\\
-    \PHget{\ctx}{a} & \text{else.}
-  \end{cases}
-  \]
-\end{definition}
-\end{comment}
-
-\begin{comment}
-Finally, we define the support (\pref{def:supp}) of a sequence of actions $\zeta$
-as the set containing the first local state of each automata appearing in $\zeta$,
-that is, as a hitter or as a target.
-For this, we first define the \emph{first appearance} of an automata
-in this sequence.
-
-\begin{definition}[$\supp$ \& $\first$]
-\label{def:supp}
-  For all sequences of actions $\zeta$, we define:
-  \[
-    \suppf{\zeta} = \bigcup_{a \in \PHs} \firstf{a}{\zeta}
-  \]
-  where:
-  \begin{align*}
-  \forall a \in \PHs, \firstf{a}{\zeta} &=
-    \begin{cases}
-      \emptyset &
-        \text{if } \forall n \in \indexes{\zeta},
-        B^\zeta_n \cap \PHl_a \neq \emptyset \\
-      B^\zeta_m \cap \PHl_a &
-        \text{else, if } m =
-        \min\{ n \in \indexes{\zeta} \mid B^\zeta_n \cap \PHl_a \neq \emptyset \}
-    \end{cases} \\
-  \forall n \in \indexes{\zeta}, B^\zeta_n &= \hitter{\zeta_n} \cup \{ \target{\zeta_n} \}.
-  \end{align*}
-\end{definition}
-
-We note that for all sequence of actions $\zeta$,
-$\forall a \in \PHs, 0 \leq \card{\firstf{a}{\zeta}} \leq 1$,
-because given the particular for of the actions of an AAN (see \pref{def:ph}),
-$\forall n \in \indexes{\zeta}, B_n \in \PHsublset[\PHl]$.
-This also means that: $\suppf{\zeta} \in \PHsublset[\PHl]$.
-
-\end{comment}
 

### 2015-02-17 main.tex
revised introduction
revised section 2
remove section 4.1 (ADN to AAN)
sa++
remove \mod commands
affiliation
large scale application examples (esp. EGFR)
corrections

@@
 
-\usepackage[UKenglish]{babel}
+\usepackage[british]{babel}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{array}   % Tableaux évolués
+\usepackage{color, colortbl}  % Cellules de couleur dans les tableaux
 
@@
 \newproof{example}{Example}
+\newproof{remark}{Remark}
 \newproof{rawproof}{Proof}
@@
 
-% Ajouts et progression
-\def\modMF#1{\textcolor{teal}{#1}}
-\def\moda#1{\textcolor{blue}{#1}}
-% \def\modLP#1{\textcolor{magenta}{#1}}
-% \def\modMM#1{\textcolor{blue}{#1}}
-% \def\modOR#1{\textcolor{olive}{#1}}
-\def\modMF#1{#1} \def\moda#1{#1} \def\modLP#1{#1} \def\modMM#1{#1} \def\modOR#1{#1}
-
 % Special notations
@@
 \ead{Maxime.Folschette@irccyn.ec-nantes.fr}
-\author[lri,amib]{Loïc Paulevé}
+\author[lri]{Loïc Paulevé}
 \author[irccyn]{Morgan Magnin}
@@
 		Université Paris-Sud - CNRS UMR 8623, France}
-\address[amib]{AMIB group, Inria Saclay, France}{}
 
@@
 In this paper,
-we develop a new refinement for an efficient under-approximation of the dynamics of
+we develop a framework for an efficient under-approximation of the dynamics of
 Asynchronous Automata Networks (AANs).
-An AAN is an Automata Network with synchronous transitions between automata,
+An AAN is an Automata Network with synchronised transitions between automata,
 where each transition change the local state of exactly one automaton
@@
 is possible,
-without the same computational cost of usual model checkers.
-Furthermore, its complexity is polynomial in the size of the model
-and exponential in the number of possible “branchings” during the solving.
-
-The under-approximation method presented in this paper is inspired
-from the one developed specifically for the Process Hitting,
-which is a sub-class of AANs.
-Furthermore, we also introduce the notion of AANs with classes of priorities,
-and show that they have the same expressivity as AANs without priorities,
-thus extending the range of our under-approximation.
-Finally, we illustrate our method on the model-checking of a signalling network
-of 94 components, which is unprecedented.
+without the same computational cost of usual model checkers:
+the complexity is polynomial with the total number of local states and exponential with the number of
+local states within a single automaton.
+Furthermore, we address AANs with classes of priorities,
+and show that an encoding in AANs without priorities,
+thus extending the application range of our under-approximation.
+Finally, we illustrate our method for the model-checking of
+large-scale biological networks.
 \end{abstract}
@@
 
-\input{parts/models}
+\input{parts/models-ph-php.tex}
 

### 2015-02-17 parts/ccl.tex
fixes after comments from Morgan
corrections

@@
 and each step is only polynomial in the size of the model.
-Furthermore, AANs with classes of priorities can also be studied in this way,
+Moreover, AANs with classes of priorities can also be studied in this way,
 at the cost of a translation that we gave in this paper.
@@
 but may be refined given the restrictions proposed in this paper,
-and a specific search of key processes or cut sets may be derived.
+and a specific search of key processes or cut sets \cite{PAK13-CAV} may be derived.
 %but turns out to be too wide even in some obvious cases that are consequently not conclusive.

### 2015-02-17 parts/example.tex
corrections

@@
 the solutions that could create cycles or depended synchronizations,
-\todo{à confirmer}
 in the worst case all combinations have to be checked.
@@
 and runs out of memory for the majority of all experiments.
-%showing that this method is not scalable.
-Because standard model checkers are often PSPACE-complete~\cite{Harel02},
-using them to study the dynamics of a model is strongly limited by its size.
 On the other hand,

### 2015-02-17 parts/intro.tex
corrections

@@
 
-Discrete modelling frameworks for biological networks is an active research field where formal methods have proven that they were very
+Discrete modelling frameworks for biological networks is an active research field where formal
+methods have be proven very
 powerful~\cite{thomas1990biological,deJong02,snoussi_logical_1993}.
@@
 
-The approach used in this paper, however,
-consists in considering another class of models,
+The approach used in this paper, 
+consists in considering a broader class of models,
 that we call Asynchronous Automata Network,
 and that allows to naturally model these cooperations
-by defining several requisites for a reaction.
+by defining several requisites for a transition.
 Moreover, such automata networks are still compatible with the notion of priority,
@@
 \subsection*{Contributions}
-This paper is an extension of~\cite{FPMR13-CS2Bio}.
-Its main contribution consists in the development of a method
+In this paper, we develop a method
 that allows to efficiently compute under-approximations of the dynamics
 of Asynchronous Automata Networks (AANs),
-based on a similar work carried out on Process Hitting~\cite{PMR12-MSCS}.
+generalising a prior work carried out on Process Hitting~\cite{PMR12-MSCS}.
 Rather than using brute force or symbolic model checking techniques,
@@
 Our work aims at checking reachability properties that,
-for a given initial state $\ctx$ and a given local state $x$,
+for a given initial state $s$ and a given local state $x$,
 have the form:
-“Starting from state $\ctx$, is it possible to reach
+“Starting from state $x$, is it possible to reach
 a state in which $x$ is active?”,
@@
 an execution path satisfying the property can be produced.
+Extensions of AANs where transitions are split in priority classes are addressed with an encoding in
+AANs without classes of priorities.
 Our work thus allows to efficiently analyse the dynamics
@@
 To show the scalability of our method, we apply it to a
-large-scale biological model containing 94 components;
-the under-approximation turns out to be conclusive in
-all cases and results have been computed in hundredths of seconds,
-thus overtaking the efficiency of usual model-checkers.
-
-AANs (and, a fortiori, their restriction, the Process Hitting)
-can be considered as a subset of Communicating Finite State Machines
-or safe Petri Nets.
-%or Synchronous Automata Networks,
-%is inspired from the $\pi$-calculus,
-Our work is thus related to such semantic ramifications
-of extending traditional process algebras with the concept of priority
-that allows for some transitions to be given precedence over others.
-We focus here on static priorities that allow to model
-time constraints such as reaction rates or delays between regulations,
-but can also model preemptions between evolutions branches.
-Thus, although the under-approximation method presented in this paper
-is initially developed on AANs without classes of priorities,
-we show that adding classes of priorities into AANs
-does not increase their expressivity.
-Thus, we exhibit an encoding that allows to extend the range
-of application of our method to AANs with classes of priorities.
+large-scale biological models with around 100 components.
 

### 2015-02-17 parts/sa.tex
todo--
corrections

@@
 \bounce{\delta_{\card\delta}}=a_i$), one can define an abstraction $\alpha_s$ of
-such a set as the smallest objective sequence $\w\in\OS(s)$ such that
+such a set as the smallest (according to $\ltw$) objective sequence $\w\in\OS(s)$ such that
 $\bounce{\w_{\card\w}} = \bounce{\delta_{\card\delta}}, \delta\in\Delta$
@@
 The existence of a scenario from a state $s$ leading to a state
-where a given local state of an automaton $a_j$ is present
+where a given local state $a_j$ is present
 can be reformulated as the checking for the non-emptiness of $\concr(\obj{a_i}{a_j})$, where
@@
 A node $x$ of the LCG in $\sSol$ is \emph{independent} (\pref{def:coherent}) if for each local state
-$a_i\in x$, none of the other local states $b_j\in x$ have in their accessors a local state of automaton $a$ different
+$a_i\in x$, none of the other local states $b_j\in x$ have in their successors a local state of automaton $a$ different
 than $a_i$.
@@
   the under-approximation given in \pref{th:approxinf}
+  concludes that $a_1$ is reachable, as well as $b_1$, but
   does not conclude regarding the reachability of $c_1$.
@@
 
-\paragraph{Sub-state reachability.}
+\paragraph{Sub-state reachability}
 Given an AAN $\PH = (\PHs, \PHl, \PHh)$,
@@
 
-\paragraph{Sequential reachability.}
+\paragraph{Sequential reachability}
 Given a sequence of local state to reach (e.g., reach $a_i$, then $b_j$),

### 2015-02-17 main.tex
fixes & typos

@@
 An AAN is an Automata Network with synchronised transitions between automata,
-where each transition change the local state of exactly one automaton
+where each transition changes the local state of exactly one automaton
 (but any number of synchronizing local states are allowed).
@@
 Furthermore, we address AANs with classes of priorities,
-and show that an encoding in AANs without priorities,
+and give an encoding into AANs without priorities,
 thus extending the application range of our under-approximation.

### 2015-02-17 parts/def-ph.tex
corrections
fixes & typos

@@
 where $A$ is a set of local states
-and $b_j$ and $b_k$ are local states of a same automaton $b$,
-and it is required that $b_j \neq b_k$ and that
+and $b_j$ and $b_k$ are local states of a same automaton $b$;
+it is moreover required that $b_j \neq b_k$ and that
 $A$ does not contain a local state of $b$ or two local states of the same automaton.
 An action $h=\PHfrappe{A}{b_j}{b_k}$ is read as
-``$A$ \emph{hit} $b_j$ to make it bounce to $b_k$'',
-and $A$, $b_j$, $b_k$ are called respectively the set of
+``$A$ \emph{hits} $b_j$ to make it bounce to $b_k$'',
+and $A$, $b_j$, $b_k$ are called respectively the (set of)
 \emph{hitters}, the \emph{target} and the \emph{bounce} of the action,
-and can be referred to as $\PHhitter(h), \PHtarget(h), \PHbounce(h)$, respectively.
+and can be referred to as $\PHhitter(h)$, $\PHtarget(h)$ and $\PHbounce(h)$, respectively.
 
@@
 \end{definition}
-%
-\noindent
-The automaton that a local state $a_i$ belongs to is referred to as $\PHsort(a_i) = a$.
+
+\paragraph{Notations}
+The automaton that a local state $a_i$ belongs to is referred to as $\PHsort(a_i) = a$,
+and if $A \subseteq \PHproc$, we denote:
+$\PHsortf{A} = \{ \PHsortf{a_i} \in \PHs \mid a_i \in A \}$.
 Given a state $s\in \PHl$, the local state of automaton $a \in \PHs$ present in $s$ is denoted by $\PHget{s}{a}$, that is, the $a$-coordinate of the state $s$.
-If $a_i \in \PHl_a$, we define the notation $a_i \in s \EQDEF \PHget{s}{a} = a_i$.
+If $a_i \in \PHproc$, we denote $a_i \in s \Leftrightarrow \PHget{s}{a} = a_i$;
+and if $A\subseteq\PHproc$, $A\subseteq s \Leftrightarrow \forall a_i\in A, \PHget{s}{a} = a_i$.
 
@@
 \label{def:play}
-  An action $h = \PHhit{A}{b_j}{b_k} \in \PHa$ is \emph{playable} in $s \in \PHl$
+  If $\PH = (\PHs; \PHl; \PHa)$ is an AAN,
+  an action $h = \PHhit{A}{b_j}{b_k} \in \PHa$ is \emph{playable} in $s \in \PHl$
   if and only if $A \subseteq s$ and $\PHget{s}{b} = b_j$.
   In such a case, $(s \PHplay h)$ stands for the state resulting from the play of the action $h$ in $s$, which is defined by:
-    $(s \PHplay h)_b = b_k$
+    $\PHget{(s \PHplay h)}{b} = b_k$
   and
-	$\forall a\in\PHs, a\neq b, (s\PHplay h)_a = s_a$.
+    $\forall a \in \PHs, a \neq b, \PHget{(s\PHplay h)}{a} = \PHget{s}{a}$.
   Moreover, we denote: $s \PHPtrans (s \PHplay h)$.
@@
     An example of AAN.
-    This model represents the interaction of two exclusive components $a$ and $b$,
-    that cannot be active simultaneously, and that degrade over time.
+    This model represents the interaction of two components $a$ and $b$,
+    whose production is mutually exclusive and that degrade over time.
     Moreover, these two components can cooperate to activate $c$
@@
     Actions are represented by a dot connected by an edge to every hitter
-    and by an arrows to the target, followed by another dotted arrow towards the bounce.
+    and by an arrow to the target, followed by another dotted arrow towards the bounce.
     Greyed local states stand for the following possible global state:
-    $\PHstate{a_1, b_0, c_0, ab_{10}}$.
+    $\PHstate{a_1, b_0, c_0}$.
   }
@@
 \end{definition}
-\noindent
+
+\paragraph{Notations}
 For a given context $\ctx$, we note $a_i \in \ctx$ if and only if $a_i \in \PHget{\ctx}{a}$,
-and for all $ps \in \powerset(\PHproc)$ or $ps \in \PHl$, $ps \subseteq \ctx \EQDEF \forall a_i \in ps, a_i \in \ctx$.
+and for all $ps \in \powerset(\PHproc)$ or $ps \in \PHl$, $ps \subseteq \ctx \Leftrightarrow \forall a_i \in ps, a_i \in \ctx$.
 

### 2015-02-17 parts/example.tex
fixes & typos

@@
 under-approximation proposed in \pref{ssec:ordered-ua},
-which consists of several applications of the methods developed in
+which consists of several applications of the method developed in
 \pref{ssec:ua}.
@@
 We consider in the following a model of metazoan segmentation
-inspired from a first translation to Process Hitting given in~\cite{PMR10-TCSB}.
+inspired from a first translation to Process Hitting model given in~\cite{PMR10-TCSB}.
 This model was originally established in silico in~\cite{MSB:MSB4100192}
@@
 some unwanted behaviours emerge, allowing the formation of irregular stripes.
-In order to fix this, a high priority is affected to the actions hitting $a$,
-a low priority to the actions hitting $c$,
+In order to fix this, a high priority is affected to the actions hitting $a$
+and a low priority to the actions hitting $c$,
 in order to model the fact that the switching of $c$ has to be immediately followed by
 a switching of $a$.
-This forces the the switches of genes $a$ and $c$
+This forces the the evolution of genes $a$ and $c$
 to alternate in order not to miss a stripe;
@@
 We can thus consider that these two classes of priorities
-are derived from known reaction relative rates,
+are derived from known relative reaction rates,
 the evolution of the clock $c$ being slower and regular,
@@
 to check these reachabilities successively,
-by splitting it following \pref{ssec:ordered-ua}.
+by splitting it following the method given in \pref{ssec:ordered-ua}.
 
@@
 Such a traversal is detailed in \pref{tab:concret-metazoan};
-the scenario extracted from this example is:
-$\emptyseq \concat \emptyseq \concat \PHfrappes{c_0, f_1}{a_0}{a_1} =
-\PHfrappes{c_0, f_1}{a_0}{a_1}$.
-Another traversal would consist in visiting node $f_1$ before node $c_0$
+the scenario extracted from this example consists of only one action:
+$\PHfrappes{c_0, f_1}{a_0}{a_1}$.
+Another traversal of the same graph
+would consist in visiting node $f_1$ before node $c_0$
 when first descending from node $\{ c_0, f_1 \}$;
@@
 
-\newcommand{\xproc}[1]{#1}
-%\newcommand{\xsol}[1]{\circ^{{#1}}}
-\newcommand{\xsol}{\circ}
-
-\begin{table}[htp]
-  \centering
-  \begin{tabular}{|c|c|c|l|l|l|}
-    \hline
-    \# & Dir. & Node & Marking & Output & State \\\hline\hline
-    1  & $\searrow$ & $\xproc{a_1}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
-    2  & $\searrow$ & $\PHobj{a_0}{a_1}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
-    3  & $\searrow$ & $\xsol$ & $\PHfrappes{c_0, f_1}{a_0}{a_1}$ &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
-    4  & $\searrow$ & $\{ c_0, f_1 \}$ & $\{ c_0, f_1 \}$ &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
-    \phantom{*}%
-    5* & $\searrow$ & $\xproc{c_0}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
-    6  & $\searrow$ & $\PHobj{c_0}{c_0}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
-    7  & $\searrow$ & $\xsol$ & $\emptyseq$ & $\emptyseq$ & $\PHstate{f_1, a_0, c_0}$ \\\hline
-    8  & $\nearrow$ & $\PHobj{c_0}{c_0}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
-    9  & $\nearrow$ & $\xproc{c_0}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
-    10 & $\nearrow$ & $\{ c_0, f_1 \}$ & $\{ f_1 \}$ &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
-%    \phantom{*}%
-    11 & $\searrow$ & $\xproc{f_1}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
-    12 & $\searrow$ & $\PHobj{f_1}{f_1}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
-    13 & $\searrow$ & $\xsol$ & $\emptyseq$ & $\emptyseq$ & $\PHstate{f_1, a_0, c_0}$ \\\hline
-    14 & $\nearrow$ & $\PHobj{f_1}{f_1}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
-    15 & $\nearrow$ & $\xproc{f_1}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
-    16 & $\nearrow$ & $\{ c_0, f_1 \}$ & $\emptyset$ &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
-    17 & $\nearrow$ & $\xsol$ & $\emptyseq$ & $\PHfrappes{c_0, f_1}{a_0}{a_1}$ & $\PHstate{f_1, a_1, c_0}$ \\\hline
-    18 & $\nearrow$ & $\PHobj{a_0}{a_1}$ &  &  & $\PHstate{f_1, a_1, c_0}$ \\\hline
-    19 & $\nearrow$ & $\xproc{a_1}$ &  &  & $\PHstate{f_1, a_1, c_0}$ \\\hline
-  \end{tabular}
-  \caption{\label{tab:concret-metazoan}%
-    Example of the extraction of a concretizing scenario
-    from the local causality graph of \pref{fig:metazoan-sa}(left),
-    by using the algorithm of \pref{ssec:concret}.
-    The first column denotes the step number in the traversal,
-    the second depicts the direction of traversal,
-    either “$\searrow$” for descending or “$\nearrow$” for ascending,
-    the third one is the name of the node,
-    the fourth one gives the marking when the node is left,
-    the fifth one gives the actions output by the algorithm
-    and the last column gives the current state of the model when leaving each node.
-    In step \#5, marked with an asterisk,
-    the traversal visits node $c_0$, but this was arbitrarily chosen
-    amongst the set $\{ c_0, f_1 \}$.
-    Another traversal thus consists in visiting node $f_1$ first,
-    although in this example it does not change the result.
-  }
-\end{table}
-
 We denote in the following:
-$\ctx^2 = \PHstate{f_1, c_0, a_0} \play \PHfrappes{c_0, f_1}{a_0}{a_1} =
-\PHstate{f_1, c_0, a_1}$
-the state resulting from the play of a scenario concretizing
+$\ctx^2 = \PHstate{f_1, a_0, c_0} \play \PHfrappes{c_0, f_1}{a_0}{a_1} =
+\PHstate{f_1, a_1, c_0}$
+the state resulting from the play of the scenario concretizing
 $\myp^1$ in $\ctx^1$.
 As explained in \pref{ssec:ordered-ua},
-One can use this resulting state in order to carry on with another
+one can use this resulting state in order to carry on with another
 successive reachability,
-such as the reachability of $\myp^2 = a_0$ in this case.
+such as the reachability of $\myp^2 = a_0$ in our case.
 The local causality graph used to check the reachability of $\myp^2$
-from $ctx^2$ is given in \pref{fig:metazoan-sa}(middle).
+from $\ctx^2$ is given in \pref{fig:metazoan-sa}(middle).
 The same reasoning allows to conclude that this reachability is true, and
-to extract the following set of concretizing scenarios:
+to extract the following set containing only one concretizing scenario:
 $\Delta(\thisB{\myp^2}{\ctx^2}) =
-\{ \PHfrappem{a_1, f_1}{c_0}{c_1} \concat \PHfrappem{c_1}{a_1}{a_0} \}$.
+\{ \PHfrappes{a_1, f_1}{c_0}{c_1} \concat \PHfrappes{c_1}{a_1}{a_0} \}$.
 We note that once again, two traversals are possible
@@
     of the AAN in \pref{fig:metazoan-ph}
-    for the objective sequence
-    $\w = \PHobj{a_0}{a_1} \concat \PHobj{a_1}{a_0} \concat \PHobj{a_0}{a_1}$
-    and the initial context
-    $\ctx = \PHstate{a_0, c_0, f_1}$.
-    The (left) graph allows to check objective $\PHobj{a_0}{a_1}$
+    for the successive reachability of $a_0$, $a_1$ and $a_0$
+    from the initial context
+    $\ctx = \PHstate{f_1, a_0, c_0}$.
+    The (left) graph allows to check the reachability of $a_1$
     from the initial context $\ctx$.
-    The (middle) graph is for the objective $\PHobj{a_1}{a_0}$
-    and the context $\PHstate{a_1, c_0, f_1}$.
-    The (right) graph is for the last objective, $\PHobj{a_0}{a_1}$,
-    and the context $\PHstate{a_0, c_1, f_1}$.
+    The (middle) graph is for the reachability of $a_0$
+    and the context $\PHstate{f_1, a_1, c_0}$.
+    The (right) graph is for the last reachability, $a_1$,
+    and the context $\PHstate{f_1, a_0, c_1}$.
   }
 \end{figure}
+
+\newcommand{\xproc}[1]{#1}
+%\newcommand{\xsol}[1]{\circ^{{#1}}}
+\newcommand{\xsol}{\circ}
+
+\begin{table}[p]
+  \centering
+  \begin{tabular}{|c|c|c|l|l|l|}
+    \hline
+    \# & Dir. & Node & Marking & Output & State \\\hline\hline
+    1  & $\searrow$ & $\xproc{a_1}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
+    2  & $\searrow$ & $\PHobj{a_0}{a_1}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
+    3  & $\searrow$ & $\xsol$ & $\PHfrappes{c_0, f_1}{a_0}{a_1}$ &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
+    4  & $\searrow$ & $\{ c_0, f_1 \}$ & $\{ c_0, f_1 \}$ &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
+    \phantom{*}%
+    5* & $\searrow$ & $\xproc{c_0}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
+    6  & $\searrow$ & $\PHobj{c_0}{c_0}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
+    7  & $\searrow$ & $\xsol$ & $\emptyseq$ &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
+    8  & $\nearrow$ & $\PHobj{c_0}{c_0}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
+    9  & $\nearrow$ & $\xproc{c_0}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
+    10 & $\nearrow$ & $\{ c_0, f_1 \}$ & $\{ f_1 \}$ &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
+%    \phantom{*}%
+    11 & $\searrow$ & $\xproc{f_1}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
+    12 & $\searrow$ & $\PHobj{f_1}{f_1}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
+    13 & $\searrow$ & $\xsol$ & $\emptyseq$ &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
+    14 & $\nearrow$ & $\PHobj{f_1}{f_1}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
+    15 & $\nearrow$ & $\xproc{f_1}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
+    16 & $\nearrow$ & $\{ c_0, f_1 \}$ & $\emptyset$ &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
+    17 & $\nearrow$ & $\xsol$ & $\emptyseq$ & $\PHfrappes{c_0, f_1}{a_0}{a_1}$ & $\PHstate{f_1, a_1, c_0}$ \\\hline
+    18 & $\nearrow$ & $\PHobj{a_0}{a_1}$ &  &  & $\PHstate{f_1, a_1, c_0}$ \\\hline
+    19 & $\nearrow$ & $\xproc{a_1}$ &  &  & $\PHstate{f_1, a_1, c_0}$ \\\hline
+  \end{tabular}
+  \caption{\label{tab:concret-metazoan}%
+    Example of the extraction of a concretizing scenario
+    from the local causality graph of \pref{fig:metazoan-sa}(left),
+    by using the algorithm of \pref{ssec:concret}.
+    The first column denotes the step number in the traversal,
+    the second depicts the direction of traversal,
+    either “$\searrow$” for descending or “$\nearrow$” for ascending,
+    the third one is the name of the current node,
+    the fourth one gives the marking of this node when it is left,
+    the fifth one gives the actions output by the algorithm
+    and the last column gives the current state of the model when leaving each node.
+    In step \#5, marked with an asterisk,
+    the traversal visits node $c_0$, but this was arbitrarily chosen
+    amongst the set $\{ c_0, f_1 \}$.
+    Another traversal thus consists in visiting node $f_1$ first,
+    although in this example it does not change the result.
+  }
+\end{table}
 
@@
 and an epidermal growth factor receptor (EGFR) signalling pathway~\cite{Samaga2009}.
-These models both gather around a hundred components and are detailed below.
+These models both gather about a hundred components and are detailed below.
 They are originally specified as Boolean networks,
@@
     However, it may be non-conclusive due to the presence of cycles
-    or dependent synchronizations that could be avoided.
+    or non-independent synchronizations that could be avoided.
   \item The other version consists in checking \pref{th:approxinf}
@@
 We checked the reachability for the independent activation of
-4 outputs of the signalling cascade (SRE, AP1, NFkB, NFAT)
+the 4 outputs of the signalling cascade (SRE, AP1, NFkB, NFAT)
 for all possible combinations of the 3 inputs (CD4, CD28, TCRlig).

### 2015-02-17 parts/intro.tex
fixes & typos

@@
 consisting in a restriction of these frameworks where the evolution of a component is determined by the state of at most one other component that does not evolve.
-In a sense, these kind of actions are of the form $X + Y \rightarrow X + Y'$ where $X$ behaves like a catalyst molecule that “hits” another molecule $Y$ and changes it into $Y'$, without being changed itself.
+This is modelled by actions are of the form $X + Y \rightarrow X + Y'$ where $X$ behaves like a catalyst molecule that “hits” another molecule $Y$ and changes it into $Y'$, without being changed itself.
 Assuming catalysts are always available, this can represent any biochemical system made of monomolecular reactions, and can also represent catalytic networks such as metabolic networks.
@@
 
-The approach used in this paper, 
+The approach used in this paper
 consists in considering a broader class of models,
@@
 time constraints such as reaction rates or delays between regulations,
-but can also model preemptions between evolutions branches.
+but can also model preemptions between evolution branches.
 
@@
 alongside with evolution functions or focal parameters.
-To show the scalability of our method, we apply it to a
+To show the scalability of our method, we apply it to two
 large-scale biological models with around 100 components.
@@
 we develop our under-approximation method allowing to efficiently
-compute reachability analysis;
+compute reachability analyses;
 we also show how to extract a valid execution path if the response is positive,
@@
 (or, equivalently, with one class of priority).
-Finally, \pref{sec:example} provides a detailed example and a large-scale example
+Finally, \pref{sec:example} provides a detailed example and two large-scale examples
 of the application of our method,
@@
 If $A$ is a finite set,
-$|A|$ is the cardinality of $A$
+$\card{A}$ is the cardinality of $A$
 and $\powerset(A)$ is the power set of $A$.
 $\sN$ is the set of natural numbers,
-$\sN^* = \sN \setminus \{ 0 \}$ is the set of positive natural numbers,
-$\sNN = \sN \setminus \{ 0, 1 \}$ is the set of natural numbers strictly greater than 1,
+$\sN^* = \sN \setminus \{ 0 \}$ is the set of positive natural numbers
 and $\segm{x}{y} = \{ x, x+1, \dots, y-1, y \}$ is the set of natural numbers from $x$ to $y$ included.
-The Cartesian product of sets is denoted by $\times$;
+The Cartesian product of sets is denoted by $\times$ and
 if $z$ is a tuple of $n$ components, $\toset{z}$ denotes the corresponding set:
@@
 $x = (x_i)_{i \in \segm{1}{n}}$ is a sequence of elements indexed by $i \in \segm{1}{n}$,
+then $\card{x} = n$ is the size of $x$
 %we denote %$|x| = (b-a)+1$ the size of this sequence and
-then $\indexes{x} = \segm{1}{n}$ is the set of indexes of this sequence.
+and $\indexes{x} = \segm{1}{n}$ is the set of indexes of this sequence.
 Furthermore, if $a, b \in \indexes{x}$ with $a \leq b$,
-then $x_{a..b} = (x_i)_{i \in \segm{a}{b}}$ is a subsequence of $x$.
+then $x_{a..b} = (x_i)_{i \in \segm{a}{b}}$ is the subsequence of $x$
+between indexes $a$ and $b$ included.
 %from element $n$ to element $m$ inclusive.
@@
 
-\paragraph*{Digraph}
-If $(V,E)$ is a directed graph whose $V$ are the nodes and $E \subseteq V\times V$ the edges,
+\paragraph*{Digraphs}
+If $(V,E)$ is a directed graph whose set of nodes is $V$ and whose set of edges is $E \subseteq V\times V$,
 the children of a node $n$ are given by
 $\childs: V \to \powerset(V)$, with
-$\childs(n) \DEF \{ m\in V\mid (n,m)\in E\}$;
+$\childs(n) = \{ m\in V\mid (n,m)\in E\}$;
 its parents are given by
 $\parents: V \to \powerset(V)$ with
-$\parents(n) \DEF \{ m\in N\mid (m,n)\in E\}$;
+$\parents(n) = \{ m\in N\mid (m,n)\in E\}$;
 and its successors are given by
@@
 $\f{f}\conn:\powerset(V)\to \powerset(V)$
-with $\f{f}\conn(W) \DEF \bigcup_{m\in W} \childs(m)$.
+with $\f{f}\conn(W) = \bigcup_{m\in W} \childs(m)$.
 

### 2015-02-17 parts/models-ph-php.tex
fixes & typos

@@
 In this section, we define the notion of AANs with classes of priorities,
-and give a translation from any of these AANs into
-an AAN without priorities, as defined in \pref{sec:ph}.
+and give a translation from these into
+AANs without priorities, as defined in \pref{sec:ph}.
 
@@
 is to split the set of actions into several subsets assigned to priorities,
-and adapting the behaviour of the model to make any action unplayable
+and to adapt the behaviour of the model to make any action unplayable
 until no other action of higher priority is playable (\pref{def:playp}).
@@
   \end{itemize}
-  We also use the same notations as those defined in \pref{sec:ph}, when applicable.
+\end{definition}
+
+\paragraph{Notations}
+We use the same notations as those defined in \pref{sec:ph}, when applicable.
 Furthermore,
-  we denote by $\PHh \DEF \bigcup_{n \in \segm{1}{k}} \PHh^{(n)}$ the set of all actions
+we denote by $\PHh = \bigcup_{n \in \segm{1}{k}} \PHh^{(n)}$ the set of all actions
 and, for all $h \in \PHh$,
-  by $\prio(h) \DEF \min\{ n \in \segm{1}{k} \mid h \in \PHh^{(n)} \}$
+by $\prio(h) = \min\{ n \in \segm{1}{k} \mid h \in \PHh^{(n)} \}$
 the priority of action $h$.
-\end{definition}
 
@@
   of the action $h$ in $s$, which is defined by: 
-    $(s \PHplay h)_b = b_k$
+    $\PHget{(s \PHplay h)}{b} = b_k$
   and
-	$\forall a\in\PHs, a\neq b, (s\PHplay h)_a = s_a$.
+    $\forall a \in \PHs, a \neq b, \PHget{(s\PHplay h)}{a} = \PHget{s}{a}$.
   Moreover, we denote: $s \PHPtrans (s \PHplay h)$.
@@
 
-We consider in the following an AAN$k$ with $k \in \sNN$:
-$\ov{\PH} = (\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}})$.
+We consider in the following an AAN$k$:
+$\ov{\PH} = (\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}})$
+with $k \in \sN$, $k > 1$.
 The aim of the rest this section is to propose a translation of $\oPH$
@@
 called \emph{flattening}, which is bisimilar.
-This AAN with 1 class of priority is equivalent to a regular AAN without priorities;
-Therefore, such a translation is particularly useful to be able to study the dynamics of
+As an AAN with 1 class of priority is equivalent to a regular AAN without priorities,
+such a translation is particularly useful to be able to study the dynamics of
 any kind of AAN with priorities by using the static analysis developed in \pref{sec:sa}.
 
-The translation given in the following relies on the notion of \emph{sub-state},
+The translation given in the following relies on the notion of \emph{sub-state}
+(\pref{def:substate}),
 which is a set of local states containing at most one local state of each automata.
 Thus, a sub-state can be considered as a partial state.
-This notion if formally expressed in \pref{def:substate}.
 
@@
     \rho \in \bigtimes{a \in S} \PHl_a \}$
-  where the notation $\toset{\rho}$ represents
+  (where the notation $\toset{\rho}$ represents
   the set of components of the Cartesian product $\rho$,
-  as defined on page~\pageref{notations}.
+  as defined on page~\pageref{notations}).
   The set of all sub-states is denoted by:
   $\PHsubl[\PHl] \DEF \bigcup_{S \in \powerset(\PHs)} \PHsubl[\PHl]_S$.
-  Furthermore, if $\mysigma \in \PHsubl[\PHl]$ and $s \in \PHl$, we note:
-    \[\mysigma \subseteq s \EQDEF \forall a_i \in \Proc, a_i \in \mysigma \Rightarrow a_i \in s\]
+  Furthermore, we recall the notation from \pref{sec:ph},
+  if $\mysigma \in \PHsubl[\PHl]$ and $s \in \PHl$:
+    \[\mysigma \subseteq s \Leftrightarrow \forall a_i \in \mysigma, \PHget{s}{a} = a_i\]
+%    \[\mysigma \subseteq s \EQDEF \forall a_i \in \Proc, a_i \in \mysigma \Rightarrow a_i \in s\]
 \end{definition}
@@
 The translation of an AAN$k$ into an AAN
-is based on the notion of \emph{playability property} defined in \pref{def:pp}
+is based on the notion of \emph{playability property} (\pref{def:pp})
 which is a Boolean formula where the atoms are local states of $\ov{\PH}$.
@@
   \end{itemize}
-  If $P \in \F$ is a playability property and $\mysigma \in \PHsubl$ is a sub-state of $\oPH$,
+  If $P \in \F$ is a playability property, we denote by: $\PHsortf{P}$
+  the set of sorts whom at least one local state is mentioned in $P$.
+  Then, if $\mysigma \in \PHsubl$
+  with $\PHsortf{P} \subseteq \PHsortf{\mysigma}$,
   we note $\Fsem{P}{\mysigma}$ the \emph{evaluation} of $P$ in $\mysigma$:
@@
     \item if $P = a_i \in \ov{\PHl}_a$ is an atom, with $a \in \ov{\PHs}$, then $\Fsem{a_i}{\mysigma}$ is true iff $a_i \in \mysigma$;
-    \item if $P$ is not an atom, then $\Fsem{P}{\mysigma}$ is true iff all its subformulas are inductively true in $\mysigma$
+    \item if $P$ is not an atom, then $\Fsem{P}{\mysigma}$ is evaluated in $\mysigma$
       with the classical semantics for the logic operators $\top$, $\bot$, $\neg$, $\wedge$ and $\vee$.
@@
 We also have the following property for the negation of an atom:
-\[\forall a \in \ov{\PHs}, \forall a_i \in \ov{\PHl}_a, \forall \mysigma \in \PHsubl,
-  \Fsem{\neg a_i}{\mysigma} \Leftrightarrow \Fsem{\bigvee_{\substack{a_j \in \ov{\PHl}_a\\a_j \neq a_i}} a_j}{\mysigma}\]
+% \[\forall a \in \ov{\PHs}, \forall a_i \in \ov{\PHl}_a, \forall \mysigma \in \PHsubl,
+%   a \in \PHsortf{\mysigma},
+%   \Fsem{\neg a_i}{\mysigma} \Leftrightarrow \Fsem{\bigvee_{\substack{a_j \in \ov{\PHl}_a\\a_j \neq a_i}} a_j}{\mysigma}\]
+\[\forall a \in \ov{\PHs}, \forall a_i \in \ov{\PHl}_a,
+  \neg a_i \Longleftrightarrow \bigvee_{\substack{a_j \in \ov{\PHl}_a\\a_j \neq a_i}} a_j\]
 Indeed, if a local state is not active in a state, this means that another local state of the same automaton is active.
@@
 This operator simply states that the hitters of an action have to be active,
-and no other action of higher priority have to be playable.
+and every other action of higher priority has to be not playable.
 % The target of the considered action is not taken into account
@@
     \wedge
-      \left( \bigwedge_{\substack{g \in \ov{\PHh}^{(n)}\\1 < n < \prio(h)}}
+      \left( \bigwedge_{\substack{g \in \ov{\PHh}^{(n)}\\1 \leq n < \prio(h)}}
       \neg \left( \target{g} \wedge \left(\bigwedge_{c_l \in \hitter{g}} c_l\right)\right) \right)
@@
   $h$ is playable in $s$ if and only if:
-  \[\target{h} \in s \wedge \exists  \mysigma \in \PHsubl,
+  \[\target{h} \in s \wedge \exists \n \in \sN, \exists \mysigma \in \PHsubl_{\PHdep{i}{h}},
     \mysigma \subseteq s \wedge \Fsem{\Fop{h}}{\mysigma} \enspace.\]
@@
   \label{def:flattening}
-  If $k \in \sNN$ and $\oPH = (\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}})$ is an AAN$k$,
+  If $k \in \sNN$, $k > 1$ and $\oPH = (\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}})$ is an AAN$k$,
   we denote by

### 2015-02-17 parts/sa.tex
fixes & typos

@@
   a$, $\PHtarget(P)\DEF a_i$, $\PHbounce(P)\DEF a_j$,
-  and $P$ is said \emph{trivial} if $a_i = a_j$.
+  and $P$ is said \emph{trivial} iff $a_i = a_j$.
 
@@
 \obj{b_0}{b_2}\]
-\[\obj{b_0}{b_1}\not\ltw\obj{b_0}{b_2}\]
+\[\obj{b_0}{b_1}\not\ltw\obj{b_0}{b_2}
+\quad\text{and}\quad
+\obj{b_0}{b_2}\not\ltw\obj{b_0}{b_1}\]
 \end{example}
@@
 \begin{align*}
-\concr(\w) \DEF \{ \delta\in\Sce(s)\mid &
+\concr(\w) \DEF \{ \delta\in\Sce(s)\mid &\ 
 \w^\vartriangle\neq \emptyseq\Rightarrow
@@
  \wedge \exists \phi:\indexes{\w}\mapsto\indexes{\delta},
-    (\forall n,m\in\indexes{\w}, n<m \Leftrightarrow \phi(n)\leq\phi(m))
+    (\forall n,m\in\indexes{\w}, n<m \Leftrightarrow \phi(n)\leq\phi(m)
 \\ & \qquad
@@
 From \pref{def:ltw} and \pref{def:concr}, we derive that if 
-$w\ltw w'$, then $\concr(w)\subseteq\concr(\w')$ (\pref{lem:ltw}).
+$\w \ltw \w'$, then $\concr(\w)\subseteq\concr(\w')$ (\pref{lem:ltw}).
 \begin{lemma}\label{lem:ltw}
@@
 \bounce{\zeta_{n}} = \target{\zeta_{n+1}}$.
-$\BS$ denotes the set of bounce sequences.
+$\BS$ denotes the set of minimal bounce sequences.
 We refer to the set of bounce sequences \emph{resolving} the objective $P$ as
@@
 A node in $\cwV\cap\Obj$ represents an objective to refine.
-Such a node is related to nodes in $\cwV\cap\Sol$ which represent sets of hitter set of a
-bounce sequence of the objective (one for each bounce sequence in $\BS(P)$):
-given an objective $P$, if $\zeta\in\BS(P)$, $\abstr\zeta \DEF \{\PHhitter(\zeta_n) \mid
+Such a node is related to nodes in $\cwV\cap\Sol$ which represent
+sets of hitter sets extracted from a
+bounce sequence of the objective
+(that is, one for each bounce sequence in $\BS(P)$): indeed,
+given an objective $P$, if $\zeta\in\BS(P)$
+and $\abstr\zeta \DEF \{\PHhitter(\zeta_n) \mid
 n\in\indexes\zeta \}$, then $P$ is related to $\langle P, \abstr\zeta\rangle\in\Sol$
@@
 (\pref{def:lcg}-\ref{lcg-sol-sync}).
-Then, each node $ps\in\sSol$ is related to each local state $a\in\Proc$
+Then, a node $ps\in\cwV\cap\sSol$ is related to each local state $a_i \in ps$ is contains
 (\pref{def:lcg}-\ref{lcg-sync-ls}).
-Each local state node $a_i\in\cwV\cap\Proc$,
-is related to each objective $\obj{a_j}{a_i}$ where
-$a_j$ is either in the initial context $\ctx$, or
+A local state node $a_i\in\cwV\cap\Proc$
+is related to each objective $\obj{a_j}{a_i} \in \Obj$, where
+$a_j$ is either in the initial context $\ctx$ or
 is a local state node in the LCG
@@
 
-The intuition is the following.
-Given a state $s\subset\ctx$, we recursively refine the initial objective
+The intuition of the under-approximation is the following.
+Given a state $s\subseteq\ctx$, we recursively refine the initial objective
 (which is: reaching $\myp$ from the initial state) according to its children.
@@
 We can thus apply this action, modifying the state of $a$ to $a_j$ and continue to the next stage.
-In the end, this recursive procedures builds a scenario from $s\subset\ctx$ to a state containing $\myp$.
+In the end, this recursive procedures builds a scenario from $s\subseteq\ctx$ to a state containing $\myp$.
 
@@
   and all nodes in $\sSol$ are independent,
-  then for any state $s\in\PHl$ such that $s\subset\ctx$,
+  then for any state $s\in\PHl$ such that $s\subseteq\ctx$,
   there exists a scenario $\delta\in\Sce$ with $\myp\in s\play\delta$.
@@
 Checking the properties allowing to apply \pref{th:approxinf} is polynomial in the size of the graph.
-Therefore, the building and checking process can be considered as polynomial in the size
+Therefore, the building and checking processes can be considered as polynomial in the size
 of the AAN, provided that each automaton only contains a few local states.
@@
   This is due to the fact that the node $\{ a_1, b_1 \} \in \Bv \cap \sSol$
-  is not independent because of its successor $a_0$ (and $b_0$).
+  is not independent because of its successor $a_0$ (and $b_0$)
+  as we can see in the LCG of \pref{fig:sa-livelock}.
   (However, from the inconclusiveness of \pref{th:approxinf},
@@
 
-  Finally, we note however that,
-  if $\PHhits{a_0}{b_0}{b_1}$ and $\PHhits{b_0}{a_0}{a_1}$ are replaced by the actions
+  Finally, we note however that
+  if actions $\PHhits{a_0}{b_0}{b_1}$ and $\PHhits{b_0}{a_0}{a_1}$
+  are replaced respectively by
   $\PHhitm{a_0}{a_1}$ and $\PHhitm{b_0}{b_1}$,
   then the resulting saturated graph of local causality changes, and
-  \pref{th:approxinf} concludes that $c_1$ is reachable from $\ctx$.
+  \pref{th:approxinf} concludes that $c_1$ is reachable from $\PHstate{a_1, b_0, c_0}$.
   The reader can also refer to \pref{ssec:ex-metazoan}
@@
   \label{fig:sa-livelock}
-    The saturated graph of local causality of the AAN in \pref{fig:ph-livelock}
-    for the objective $\w = \PHobj{c_0}{c_1}$
-    and the initial context $\ctx = \PHstate{a_1, b_0, c_0}$.
+    The local causality graph $\cwB$ on the AAN in \pref{fig:ph-livelock}
+    for the reachability of $\myp = c_1$
+    from the initial context $\ctx = \PHstate{a_1, b_0, c_0}$.
     Elements in $\Proc$ are represented by rectangular nodes,
-    elements in $\Sol$ are represented by circle nodes,
+    elements in $\Sol$ are represented by small circles,
     and elements in $\sSol$ and $\Obj$ are the remaining borderless nodes.
-    \pref{th:approxinf} is inconclusive on this example as node $\{ a_1, b_1 \}$
+    \pref{th:approxinf} is inconclusive on this example as
+    node $\{ a_1, b_1 \} \in \sSol$
     is not independent (see \pref{def:coherent}).
-    Indeed, $a_0 \in \Proc$ is a successor of $\{ a_1, b_1 \}$, but $a_0 \neq a_1$
-    (and the same also stands for $b_0$).
+    Indeed, $a_0$ is a successor of $b_1$, but $a_0 \neq a_1$
+    (and the same also stands for $b_0$, which is a successor of $a_1$).
   }
@@
         If $\zeta_1$ is not playable
-        (which means that $\target{\zeta_1}$ has changed):
-          go to the node $\PHobj{\PHget{s}{\PHsort(\bounce{\zeta_1})}}{\bounce{\zeta_1}} \in \Obj$
+        (which means that $\target{\zeta_1}$ has changed),
+          then go to the node $\PHobj{\PHget{s}{\PHsort(\bounce{\zeta_1})}}{\bounce{\zeta_1}} \in \Obj$
           and start descending.
@@
 
-The execution of such a traversal outputs a scenario.
-We denote $\Delta(\cwB)$ the set of all scenarios extracted from the
+The execution of such a traversal outputs a scenario from $s_0$.
+In the following, we denote by $\Delta(\cwB)$ the set of all scenarios extracted from the
 local causality graph $\cwB$.
 Indeed, several scenarios may exist for a same graph,
-generated by the successors that can be arbitrarily chosen
-in this algorithm.
+generated by the arbitrary choices that exist in this algorithm.
 An example of such a traversal is given on a small example
@@
 
-\paragraph{Sub-state reachability}
-Given an AAN $\PH = (\PHs, \PHl, \PHh)$,
+\subsubsection*{Sub-state reachability}
+Given an AAN $\PH = (\PHs, \PHl, \PHh)$ and
 a sub-set of automata local states
@@
 $ps\subset s'$ is equivalent to the reachability of the local state
-$\reach_1$ from a state $s\uplus\langle\reach_0\rangle$
+$\reach_1$ from a state $s \times \{ \reach_0 \}$
 in the AAN
@@
 
-\paragraph{Sequential reachability}
-Given a sequence of local state to reach (e.g., reach $a_i$, then $b_j$),
+\subsubsection*{Sequential reachability}
+Given a sequence of local state to reach (e.g., reach $a_i$, then $b_j$, etc.),
 one can use the same approach as for sub-state reachability by introducing
 a new automaton $\reach$ having $n+1$ local states where $n$ is the size of the
-sequence of reachability and $n$ actions making it bounce from $\reach_0$ to
+sequence of reachability, and $n$ actions making it bounce gradually from $\reach_0$ to
 $\reach_n$ with hitters corresponding the successive local states
-(e.g., $\PHfrappes{a_i}{\reach_0}{\reach_1}$ and
-$\PHfrappes{b_j}{\reach_1}{\reach_2}$).
+(e.g., $\PHfrappes{a_i}{\reach_0}{\reach_1}$,
+$\PHfrappes{b_j}{\reach_1}{\reach_2}$, etc.).
 
-An alternative approach is to use the extraction of a scenario of the previous
-sub-section:
-given the initial state, and a first local state reachability property, one
-compute a possible scenario witnessing this reachability.
-Then the next local state reachability properties is computed from the
-state that outcomes from the latter scenario.
+An alternative approach is to use the extraction of a scenario of
+\pref{ssec:concret}:
+given an initial state $s_0$, and a first local state reachability property $\myp_1$,
+one can compute a possible scenario $\delta \in \Delta(\mycwB{s_0}{\myp})$
+witnessing this reachability;
+then the next local state reachability properties ($\myp_2$, $\myp_3$, etc.)
+are computed from the
+state $s_0 \play \delta$ that outcomes from the latter scenario.

### 2015-02-17 parts/ccl.tex
finish corrections

--- 2014-12-22 parts/ccl.tex
@@
 
-In this paper, we focused on the Asynchronous Automata Networks (AANs),
-which is a restriction of classical Automata Networks
-and is equivalent to the Process Hitting with classes of priorities~\cite{FPMR13-CS2Bio}.
+In this paper, we focused on Asynchronous Automata Networks (AANs),
+which are a restriction of classical Automata Networks
+and are equivalent to Process Hitting models with classes of priorities~\cite{FPMR13-CS2Bio}.
 This formalism proves useful to model accurate Boolean gates, which was not possible
@@
 Furthermore, we proposed an extension of this formalism with classes of priorities,
-which prove convenient to abstract time parameters into these kinds of models,
-or more simply to add preemption relations between actions.
+which prove convenient to abstract time parameters into these kinds of models
+or more simply to add preemption relations between actions,
+and showed that any AAN with priorities can be translated into
+an equivalent AAN without priorities.
 
 Then, we developed a method to perform a reachability analysis
-of a sequence of objectives in an AAN,
+of a local state in an AAN,
 based on an under-approximation of the true reachability solutions.
-The checked objectives can take the form of local states, global states
-or partial states, making the analysis more convenient.
-This method can be considered efficient,
-because it is exponential in the number of possible solutions,
-and each step is only polynomial in the size of the model.
-Furthermore, AANs with classes of priorities can also be studied in this way,
-at the cost of a translation that we gave in this paper.
+We also extended this analysis to global and
+partial states, and to the successive reachability of several local states.
+The method can be considered efficient,
+because it is polynomial in the size of the model.
+A more conclusive analysis also exists,
+but at the price of being exponential in the number of local solutions.
+Finally, AANs with classes of priorities can also be studied in this way,
+at the cost of an exponential translation that we gave in this paper.
+We applied it to a large number of experiments on two large-scale
+biological models, and obtained in the worst case a ratio of
+%65\% of positively responding cases, growing to
+90\% of conclusive cases
+with the joint use of a previously proposed over-approximation,
+although limiting the computation time to 3 seconds for each test.
 
-Finally, we also showed that AANs are also equivalent to Asynchronous Discrete Networks,
-that is, the multivalued version of the classical Asynchronous Boolean Networks
-with discrete expression levels and evolution functions.
-This framework is also equivalent to Thomas' models with Snoussi parameters
-instead of evolution functions.
+AANs are also equivalent to Logical Networks, that is,
+either multivalued or Boolean networks
+with evolution functions or focal parameters,
+such as Thomas' models with Snoussi parameters.
 This especially allows to efficiently compute reachability results
 on large biological models,
-provided that they are equivalent to Asynchronous Discrete Networks,
+provided that they are equivalent to Logical Networks,
 which ensures that a translation to AANs is possible.
@@
 The over-approximation on Process Hitting models without priorities proposed in~\cite{PMR12-MSCS}
-is still accurate in the framework with priorities (by “merging” all actions),
-but may be refined given the restrictions proposed in this paper,
-and a specific search of key processes or cut sets may be derived.
+and that was used in this work
+is still accurate on AANs (by over-approximating dynamics)
+but may be refined given the particular for of AANs proposed in this paper.
+A specific search of key processes or cut sets \cite{PAK13-CAV} may especially be derived.
 %but turns out to be too wide even in some obvious cases that are consequently not conclusive.
@@
 Furthermore, we are investigating alternative under-approximations that can be
-applied directly to the whole class of Process Hitting models with priorities,
-and not only to a sub-class with particular restrictions;
+applied directly to the whole class of AANs or Process Hitting models with priorities,
+and not only to a sub-class with only one class of priority or particular restrictions;
 such improvement may allow to increase the conclusiveness of the static analysis

### 2015-02-17 parts/example.tex
finish corrections

@@
 and our under-approximation has been satisfied in 12 cases (over
-32) proving the satisfiability of the concerned reachability property in the encoded Boolean network
+32) proving the satisfiability of the concerned reachability properties in the encoded Boolean network
 (and non-satisfiability in the other cases, using the previously existing over-approximation).
@@
 for some configurations of inputs.
-We thus want to check if these three outputs can be activated together,
-that is, if the activation of one of the outputs does not prevent the activation another one.
+We thus wanted to check if these three outputs could be activated together,
+that is, if the activation of one of the outputs did not prevent the activation another one.
 For this, as proposed in \pref{ssec:simult-ua},
-we add a new automaton $\reach$ into the model
+we have added a new automaton $\reach$ into the model
 with two local states ($\PHl_\reach = \{ \reach_0, \reach_1 \}$)
@@
 Finally, checking the reachability of $\reach_1$ in all configurations of the inputs
-is always conclusive,
+has always been conclusive,
 and the existence of 4 positive answers
@@
 21 inputs and 12 outputs.
-Analysing the consequences of the variations of all inputs
-would require too many tests;
-therefore, we selected 13 of them
+We selected 13 of all inputs
 (erbb1, erbb2, erbb3, erbb4, bir, btc, egf, epr, nrg1a, nrg1b, nrg2b, nrg4, tgfa)
@@
 (thus leading to \emph{Inconclusive} cases).
-These experiments represent about 10\% of all tests,
-amongst the remaining 90\%, while all the others are conclusive.
-We note that none of the tests terminated normally (without being cut after 3 seconds)
-with an inconclusive answer, which is however theoretically possible.
+These “interrupted” experiments represent about 10\% of all tests.
+%amongst the remaining 90\%, while all the others are conclusive.
+We note that amongst all tests that terminated “normally” (without being cut after 3 seconds)
+%none of the tests terminated normally (without being cut after 3 seconds)
+none of them responded with an inconclusive answer, which is however theoretically possible.
 
@@
 We held all these experiments on a personal computer,
-and computations times were in the order of a few tenths of a second to about one second.
-To give a comparison, we did the same experiments with a standard symbolic model-checker, libDDD
+and regarding the experiments that were not cut at the 3 seconds limit,
+computations times were in the order of a few tenths of a second to about one second.
+To give a comparison, we did the same experiments with a standard symbolic model-checker, LibDDD
 \cite{libddd}, known for its good performances, the input model being the Boolean network expressed
@@
 on the TCR and EGFR models to some extent,
-they did not provide a formal proof of the reachabilities that have been
+they did not provide a formal “True” response regarding the reachabilities that have been
 checked in the examples above.
@@
 the observed behaviours are the result of the true dynamics of the systems.
-The same experiments have been conducted with the previous version
-of the under-approximation and reported alongside in \pref{tab:results}
+Thus, additionally to the experiments previously mentioned,
+we conducted similar experiments with the previous version
+of the under-approximation, that are reported alongside in \pref{tab:results}
 (in columns “PH”).
-We note that indeed, about 10\% of the positive results regarding the EGFR model
+We note that indeed, about 15\% of the positive results regarding the EGFR model
 could not be proven with our new under-approximation,
@@
 
-\definecolor{lightgraycell}{gray}{0.8}
+\definecolor{lightgraycell}{gray}{0.85}
 \newcommand{\grcl}{\cellcolor{lightgraycell}}
@@
     and using the under-approximation of~\cite{PMR12-MSCS}.
-    The lines labelled “True”, “Inconclusive” and “False” lines give respectively
-    the number of positive, cut and negative answers,
+    The lines labelled “True”, “Inconclusive” and “False” give respectively
+    the number of positive answers,
+    experiments cut after 3 seconds and negative answers;
     while “Max time” and “Total time” depict respectively
-    the maximum time of the individual computations (except those cut after 3 seconds)
-    and the overall execution time of all tests (including those cut after 3 seconds).
+    the maximum time of the individual computations (except those cut at 3 seconds)
+    and the overall execution time of all tests (including those cut at 3 seconds).
     The greyed cells highlight the results that are proper to the
@@
 our under-approximation method turns out to be conclusive in numerous cases when applied to real
-large-scale biological models, which were not tractable with exact model-checking.
+large-scale biological models, which were not tractable in most cases with exact model-checking.

### 2015-02-17 main.tex
Uni Kassel affiliation + ERC

@@
 
-\author[irccyn]{Maxime Folschette}
+\author[irccyn,unikassel]{Maxime Folschette}
 \ead{Maxime.Folschette@irccyn.ec-nantes.fr}
@@
 1 rue de la No\"e - B.P. 92101 - 44321 Nantes Cedex 3, France.}
+
+\address[unikassel]{School of Electrical Engineering and Computer Science,\\
+  University of Kassel, Germany}
 
@@
 
+{\small
+\paragraph{Acknowledgement}
+The European Research Council has provided financial support
+under the European Community's Seventh Framework Programme (FP7/2007--2013)~/
+ERC grant agreement no.~259267.
+}
+
 \section*{References}

### 2015-02-18 parts/def-ph.tex
corrections after Morgan's review

@@
 and $i$ is the identifier of this local state within automaton $a$.
-A \emph{global state} of the system is the gathering
-of exactly one local state from each automata.
+A \emph{global state} of the system is a Cartesian product
+with exactly one local state from each automata.
 
@@
     and local states by circles with their identifier on the side.
-    Actions are represented by a dot connected by an edge to every hitter
+    Actions are represented by a dot connected by an edge to the set of hitters
     and by an arrow to the target, followed by another dotted arrow towards the bounce.
@@
   introduced in~\cite{FPMR13-CS2Bio}.
-  Indeed, in the Process Hitting with at least 2 classes of priorities
-  it is possible to use additional automata, called “cooperative sorts”,
-  in order to model the actions of any AAN that have more than one hitter.
+  Indeed, in the Process Hitting with at least 2 classes of priorities,
+  it is possible to use additional automata called “cooperative sorts”
+  in order to model the actions in an AAN that have more than one hitter.
 \end{remark}

### 2015-02-18 parts/example.tex
corrections after Morgan's review

@@
 metazoan segmentation process,
-and demonstrate how the classes of priorities help in the modelling process,
+and demonstrate how classes of priorities help in the modelling process,
 and how the flattening of \pref{sec:flattening}
@@
 
-The actions of the original model make $2$ classes of priorities, as represented in \pref{fig:metazoan-php}:
+The actions of the original model are split into $2$ classes of priorities, as represented in \pref{fig:metazoan-php}:
 \begin{align*}
@@
 and a low priority to the actions hitting $c$,
-in order to model the fact that the switching of $c$ has to be immediately followed by
-a switching of $a$.
+in order to model the fact that the switch of $c$ has to be immediately followed by
+a switch of $a$.
 This forces the the evolution of genes $a$ and $c$

### 2015-02-18 parts/intro.tex
corrections after Morgan's review

@@
 and the concept of priority relations among the transitions of a network has also more recently been introduced by A.~K.~Wagler \textit{et~al.}~\cite{waw,WaglerW12} in order to allow modelling deterministic systems for biological applications.
-The concept of priority is much straightforward in the approach of process algebras as it was shown by R.~Cleaveland and M.~Hennessy in~\cite{Cleaveland199058,Cleaveland99prioritiesin} and their abstractions and equivalences were studied in~\cite{Cleaveland:2007:PAP:1282576.1282847}.
+The concept of priority is much straightforward in the approach of process algebras as it was shown by R.~Cleaveland and M.~Hennessy in~\cite{Cleaveland199058} and their abstractions and equivalences were studied in~\cite{Cleaveland:2007:PAP:1282576.1282847}.
 It was later extended for applications in the field of systems biology by M.~John \textit{et~al.}~\cite{jlnu2010}.
@@
 Our work aims at checking reachability properties that,
-for a given initial state $s$ and a given local state $x$,
+for a given initial state $s$ and the discrete expression level $n$
+of a given component $x$,
 have the form:
-“Starting from state $x$, is it possible to reach
-a state in which $x$ is active?”,
+“Starting from state $s$, is it possible to reach
+a state in which $x$ is at level $n$?”,
 thus answering either “True”

### 2015-02-18 parts/models-ph-php.tex
corrections after Morgan's review

@@
 is to split the set of actions into several subsets assigned to priorities,
-and to adapt the behaviour of the model to make any action unplayable
+and to constrain the behaviour of the model to make any action unplayable
 until no other action of higher priority is playable (\pref{def:playp}).
-Such model allows to model preemptions between sets of actions,
+Such a framework allows to model preemptions between sets of actions,
 which can be helpful to abstract time or duration properties under certain conditions.

### 2015-02-18 parts/sa.tex
corrections after Morgan's review

@@
 A classical approach for determining if a local state of an automaton can be
-reached from a given initial state is to build sequences of transitions from the initial state until a state
-containing the given local state is reached.
+reached from a given initial state is to build sequences of transitions from the initial state
+until reaching a state in which the given local state is active.
+%containing the given local state is reached.
 This is essentially what model-checkers do, and the complexity of such analysis (PSPACE-complete
@@
 $w\ltw w'$ if and only if there exists a mapping between all the objective bounces of $w'$ in $w$
-that preserve the sequentiality, provided that each automaton starts in the same
+that preserves the sequentiality, provided that each automaton starts in the same
 local state.

### 2015-02-19 underapprox-tcrsig94/run-egfr104.sh
add name un scripts

@@ -40,7 +40,7 @@ init="erbb1 $erbb1, erbb2 $erbb2, erbb3 $erbb3, erbb4 $erbb4, bir $bir, btc $btc
 echo "--- $init"
 for z in $outputs; do
   echo "# $z 1"
-  ./unitrun.sh $mode "x" --no-debug --initial-state "$init" -i $ph $z 1
+  ./unitrun.sh $mode "$erbb1$erbb2$erbb3$erbb4$bir$btc$egf$epr$nrg1a$nrg1b$nrg2b$nrg4$tgfa" --no-debug --initial-state "$init" -i $ph $z 1
   [ $? -eq 137 ] && echo '*** Killed ***'
 done
 

### 2015-02-19 underapprox-tcrsig94/run-generator.sh

@@ -74,7 +74,14 @@ echo "\"" >> $runfile
 echo "echo \"--- \$init\"" >> $runfile
 echo "for z in \$outputs; do" >> $runfile
 echo "  echo \"# \$z 1\"" >> $runfile
-echo "  ./unitrun.sh \$mode \"x\" --no-debug --initial-state \"\$init\" -i \$ph \$z 1" >> $runfile
+echo -n "  ./unitrun.sh \$mode \"" >> $runfile
+
+# Initial state name
+for curinput in $inputs; do
+  echo -n "\$$curinput" >> $runfile
+done
+
+echo "\" --no-debug --initial-state \"\$init\" -i \$ph \$z 1" >> $runfile
 echo "  [ \$? -eq 137 ] && echo '*** Killed ***'" >> $runfile
 echo "done" >> $runfile
 echo '' >> $runfile

### 2015-02-19 underapprox-tcrsig94/run-tcrsig94.sh

@@ -30,7 +30,7 @@ init="cd4 $cd4, cd28 $cd28, tcrlig $tcrlig"
 echo "--- $init"
 for z in $outputs; do
   echo "# $z 1"
-  ./unitrun.sh $mode "x" --no-debug --initial-state "$init" -i $ph $z 1
+  ./unitrun.sh $mode "$cd4$cd28$tcrlig" --no-debug --initial-state "$init" -i $ph $z 1
   [ $? -eq 137 ] && echo '*** Killed ***'
 done
 

### 2015-02-19 parts/intro.tex
last ref & remove last TODO

@@
 can be considered as a subset of Communicating Finite State Machines
-or safe Petri Nets.
+or safe Petri Nets~\cite{PMR-PetriNets}.
 %or Synchronous Automata Networks,

### 2015-02-23 parts/models-ph-php.tex
fix flattening with 3-valued logic

@@
 
-We consider in the following an AAN$k$:
-$\ov{\PH} = (\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}})$
-with $k \in \sN$, $k > 1$.
-The aim of the rest this section is to propose a translation of $\oPH$
-into an AAN with $1$ class of priority $\PH = (\PHs; \PHl; \PHa^{\angles{1}})$
-called \emph{flattening}, which is bisimilar.
-As an AAN with 1 class of priority is equivalent to a regular AAN without priorities,
-such a translation is particularly useful to be able to study the dynamics of
-any kind of AAN with priorities by using the static analysis developed in \pref{sec:sa}.
-
 The translation given in the following relies on the notion of \emph{sub-state}
@@
 
+We consider in the following an AAN$k$:
+$\ov{\PH} = (\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}})$
+with $k \in \sN$, $k > 1$.
+The aim of the rest this section is to propose a translation of $\oPH$
+into an AAN with $1$ class of priority $\PH = (\PHs; \PHl; \PHa^{\angles{1}})$
+called \emph{flattening}, which is bisimilar.
+As an AAN with 1 class of priority is equivalent to a regular AAN without priorities,
+such a translation is particularly useful to be able to study the dynamics of
+any kind of AAN with priorities by using the static analysis developed in \pref{sec:sa}.
+
 The translation of an AAN$k$ into an AAN
@@
   \end{itemize}
-  If $P \in \F$ is a playability property, we denote by: $\PHsortf{P}$
-  the set of sorts whom at least one local state is mentioned in $P$.
-  Then, if $\mysigma \in \PHsubl$
-  with $\PHsortf{P} \subseteq \PHsortf{\mysigma}$,
-  we note $\Fsem{P}{\mysigma}$ the \emph{evaluation} of $P$ in $\mysigma$:
+  If $P \in \F$ is a playability property and $\mysigma \in \PHsubl$ is a sub-state of $\oPH$,
+  we note $\Fsem{P}{\mysigma}$ the \emph{evaluation} of $P$ in $\mysigma$
+  in a three-valued Kleene logic (\emph{true}, \emph{undecided} or \emph{false})
+  which is given by:
   \begin{itemize}
-    \item if $P = a_i \in \ov{\PHl}_a$ is an atom, with $a \in \ov{\PHs}$, then $\Fsem{a_i}{\mysigma}$ is true iff $a_i \in \mysigma$;
+    \item if $P = a_i \in \ov{\PHl}_a$ is an atom,
+%      with $a \in \ov{\PHs}$, 
+      then $\Fsem{a_i}{\mysigma}$ is
+    $\begin{cases}
+       \text{true}      & \text{if } a_i \in \mysigma \\
+       \text{undecided} & \text{if } \mysigma \cap \ov{\PHl}_a = \emptyset \\
+       \text{false}     & \text{otherwise }
+     \end{cases}$ \enspace;
+%    true iff $a_i \in \mysigma$;
     \item if $P$ is not an atom, then $\Fsem{P}{\mysigma}$ is evaluated in $\mysigma$
-      with the classical semantics for the logic operators $\top$, $\bot$, $\neg$, $\wedge$ and $\vee$.
+      with the classical semantics for the logic operators $\top$, $\bot$, $\neg$, $\wedge$ and $\vee$, which is recalled in \pref{fig:kleene}.
   \end{itemize}
+  Furthermore, in the following, we will use $\Fsem{\Fop{h}}{s}$ as a shorthand for
+  $\Fsem{\Fop{h}}{\toset{s}}$.
 \end{definition}
+
+\begin{figure}[ht]
+  For all playability properties $P, Q \in \F$ that are not atoms,
+  and for all sub-state $\mysigma \in \PHsubl$:
+  \begin{itemize}
+    \item $\Fsem{\top}{\mysigma}$ is always true;
+    \item $\Fsem{\bot}{\mysigma}$ is always false;
+    \item $\Fsem{\neg P}{\mysigma}$ is
+      $\begin{cases}
+        \text{true} & \text{if $\Fsem{P}{\mysigma}$ is false} \\
+        \text{false} & \text{if $\Fsem{P}{\mysigma}$ is true} \\
+        \text{undecided} & \text{if $\Fsem{P}{\mysigma}$ is undecided}
+      \end{cases}$ \enspace;
+    \item $\Fsem{P \wedge Q}{\mysigma}$ is
+      $\begin{cases}
+        \text{true} & \text{if both $\Fsem{P}{\mysigma}$ and $\Fsem{Q}{\mysigma}$ are true} \\
+        \text{false} & \text{if $\Fsem{P}{\mysigma}$ is false or $\Fsem{Q}{\mysigma}$ is false} \\
+        \text{undecided} & \text{otherwise}
+      \end{cases}$ \enspace;
+    \item $\Fsem{P \vee Q}{\mysigma}$ is
+      $\begin{cases}
+        \text{true} & \text{if $\Fsem{P}{\mysigma}$ is true or $\Fsem{Q}{\mysigma}$ is true} \\
+        \text{false} & \text{if both $\Fsem{P}{\mysigma}$ and $\Fsem{Q}{\mysigma}$ are false} \\
+        \text{undecided} & \text{otherwise}
+      \end{cases}$ \enspace.
+  \end{itemize}
+  \caption{\label{fig:kleene}%
+    Explicit semantics of the evaluation of playability properties in the
+    three-valued Kleene logic.
+  }
+\end{figure}
 
@@
 We also have the following property for the negation of an atom:
-% \[\forall a \in \ov{\PHs}, \forall a_i \in \ov{\PHl}_a, \forall \mysigma \in \PHsubl,
-%   a \in \PHsortf{\mysigma},
-%   \Fsem{\neg a_i}{\mysigma} \Leftrightarrow \Fsem{\bigvee_{\substack{a_j \in \ov{\PHl}_a\\a_j \neq a_i}} a_j}{\mysigma}\]
 \[\forall a \in \ov{\PHs}, \forall a_i \in \ov{\PHl}_a,
@@
 Indeed, if a local state is not active in a state, this means that another local state of the same automaton is active.
-Moreover, we note that:
+Moreover,
+provided that in the following we are only interested in properties that are true
+and thus we make no distinction between false and undecided results,
+playability properties can be simplified with the following result:
 \[\forall a \in \ov{\PHs}, \forall a_i, a_j \in \ov{\PHl}_a,
@@
 This operator simply states that the hitters of an action have to be active,
-and every other action of higher priority has to be not playable.
-% The target of the considered action is not taken into account
-% as it is not needed for the rest of the flattening.
+and every other action of higher priority must not be playable.
 
@@
 By construction of this operator and given the dynamics of a AAN$k$,
-an action $h$ is playable in a state $s \in \ov{\PHl}$ if and only if: $\Fsem{\Fop{h}}{s}$.
+an action $h$ is playable in a state $s \in \ov{\PHl}$ if and only if
+$\Fsem{\Fop{h}}{s}$ is true.
 
@@
   \[\target{h} \in s \wedge \exists \n \in \sN, \exists \mysigma \in \PHsubl_{\PHdep{i}{h}},
-    \mysigma \subseteq s \wedge \Fsem{\Fop{h}}{\mysigma} \enspace.\]
+    \mysigma \subseteq s \wedge \Fsem{\Fop{h}}{\mysigma} \text{ is true} \enspace.\]
 \end{lemma}
@@
   ($\Rightarrow$)
-    If $h$ is playable in $s$, then $\target{h} \in s$ and $\Fsem{\Fop{h}}{s}$.
+    If $h$ is playable in $s$, then $\target{h} \in s$ and $\Fsem{\Fop{h}}{s}$ is true.
     Thus, $\Fop{h} \not\equiv \bot$ and, by property of a DNF,
@@
     We immediately have: $\mysigma \subseteq s$,
-    and, by construction of $\PHdep{i}{h}$, $\Fsem{\Fop{h}}{\mysigma}$.
+    and, by construction of $\PHdep{i}{h}$, $\Fsem{\Fop{h}}{\mysigma}$ is true.
 
   ($\Leftarrow$)
-    $\Fsem{\Fop{h}}{\mysigma}$ therefore $\Fsem{\Fop{h}}{s}$; as $\target{h} \in s$,
-    $h$ is playable in $s$.
+    $\Fsem{\Fop{h}}{\mysigma}$ is true, and therefore $\Fsem{\Fop{h}}{s}$ is true;
+    as $\target{h} \in s$, $h$ is playable in $s$.
 \end{proof}
@@
   \label{def:flattening}
-  If $k \in \sNN$, $k > 1$ and $\oPH = (\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}})$ is an AAN$k$,
+  If $k \in \sN$, $k > 1$ and $\oPH = (\ov{\PHs}; \ov{\PHl}; \ov{\PHa}^{\angles{k}})$ is an AAN$k$,
   we denote by
@@
       \mysigma \in \PHsubl_{\PHdep{i}{h}} \wedge
-      \Fsem{\Fop{h}}{\mysigma} \}$.
+      \Fsem{\Fop{h}}{\mysigma} \text{ is true} \}$.
   \end{itemize}
-%   Given a state $s \in \PHl$, $\unflats{s} = \os$ is the corresponding state in $\ov{\PHl}$:
-%   $\forall a \in \ov{\PHs}, \PHget{\os}{a} = \PHget{s}{a}$.
-%   Conversely,
-%   given a state $\os \in \ov{\PHl}$, $\flats{\os} = s$ is the corresponding state in $\PHl$:
-%   $\forall a \in \ov{\PHs}, \PHget{s}{a} = \PHget{\os}{a}$.
 \end{definition}

### 2015-02-24 response.tex
todo-- in response
proofread response

@@
 
-\newcommand{\todo}[1]{\textcolor{red}{\textbf{[TODO: #1]}}}
-\newcommand{\answertodo}[1]{\textcolor{red}{\textbf{À appliquer :}} \textcolor{magenta}{#1}}
+%\newcommand{\todo}[1]{\textcolor{red}{\textbf{[TODO: #1]}}}
+%\newcommand{\answertodo}[1]{\textcolor{red}{\textbf{À appliquer :}} \textcolor{magenta}{#1}}
 
@@
     and the detailed example (Sect.~5.1).
+  \item A new large-scale example has been introduced (Sect.~5.2)
+    in order to better justify this work compared to the existing approach.
   \item A section has been added (Sect.~3.5) about the extraction of a scenario
@@
 The static analysis method thus required adaptations
-that we tried to better motivate in this revision.
+that we tried to better motivate in this revision,
+especially with the new EGFR example of Sect.~5.2.
 }
@@
 The new AAN representation makes this difference clearer:
-the previously emphasized sub-class of PH models used for the static analysis
+the previously considered sub-class of PH models used for the static analysis
 is equivalent to AANs,
@@
 is equivalent to AANs with classes of priorities.
-Thus, the encoding of Sect. 4.2 actually extends the applicability
+Thus, the encoding of Sect.~4 (previously Sect.~4.2)
+actually extends the applicability
 of our static analysis; we have added some discussion to emphasize this.
@@
 that are not exactly those of ADNs (a.k.a.~Logical Networks).
-We have added some discussion to emphasize this.
+We have added some discussion to emphasize this,
+and a new illustration in Sect.~5.2 with the EGFR example.
 }
@@
 The experiment we carried with the LibDDD model-checker led us to the conclusion that the memory needs for such a method is several orders of magnitude above our method, which we would consider a sufficient result in itself.
+Indeed, LibDDD is not able to conclude on most cases with large models,
+and when it does, the computation takes several minutes,
+to be compared to less than a second for most cases with our method
+(see the new quantitative results added to Sect.~5.2).
 Furthermore, with such a memory use, one cannot expect to be able to study bigger models (say, thousands of components) while our method has a polynomial complexity in the size of the model or the construction of the saturated graph of local causality, and could thus tackle such bigger models.
@@
 \answer{
-We these comments into account.
+We took all these comments into account.
 }
@@
 \answer{
-We took the comments about the language issues of Reviewer \#3 into account.
+We took all the comments about the language issues of Reviewer \#3 into account.
 }
@@
 \answer{
-The additions regarding the workshop paper are the following:
+The additions regarding the workshop paper are the following
+(some have been added for this revision):
 \begin{itemize}
-  \item In this revision, we generalised the results to Asynchronous Automata
-  Networks (AANs) which also simplies the formalism;
-  \item In this revision, we also included a new section (3.3) which give a
-  procedures to extract a witness scenario satisfying a given reachability
-  property.
+  \item We generalised the results to Asynchronous Automata
+    Networks (AANs) which also simplifies the formalism;
   \item The encoding of AANs with classes of priorities into simple AANs
-  (section 4).
+    (Sect.~4) were added.
+  \item We included a new section (Sect.~3.3)
+    which gives a procedure to extract a witness scenario
+    satisfying a given reachability property.
+  \item Sect.~5 now features a detailed application example
+    and a new large-scale application example.
 \end{itemize}
@@
 
-\answer{With this revision, we removed and simplies a lot a notations, and added
+\answer{With this revision, we removed and simplified a lot a notations, and added
 more explanations for the under-approximation of reachability properties in AANs
-(section 3).
+(Sect.~3).
 More details on the abstract domain (objective sequences) and their
-interconnections with concrete scenarios are given in section 3.1.
+interconnections with concrete scenarios are given in Sect.~3.1.
 The relationship of Local Causality Graphs with objective sequences is also
@@
 
-\todo{Quels détails supplémentaires devrait-on donner ?}
+\answer{We added a new and more appropriate example to emphasize the new results brought by our method.}
 
@@
 Although the denomination “ADN” does not exist in the literature,
-there is in fact no widespread or unified term to qualify this class of models.
+there is in fact no widespread or unified term to qualify this class of logical models.
 We have detailed this choice in the paper and justified the use of this term,
@@
 
-\answer{We have taken most of these comments into account.}
+\answer{We have taken these comments into account.}
 

### 2015-02-24 response.tex
fix response after Loïc and Morgan's reviews

@@
 
-We wish thank the reviewers for their comments.
-Please find a summary of the main changes brought to the paper here, and a detailed response to all comments below.
+We wish to thank the reviewers for their comments.
+Please find below a summary of the main changes brought to the paper, and a detailed response to all comments.
 
@@
     with classes of priorities (PH) to Asynchronous Automata Networks (AANs).
-    This formalism is equivalent but saves a lot of over-complicated formalism,
+    This formalism is equivalent
+    and has the advantage to avoid using too much complicated formalism,
     thus gaining in clarity.
@@
   \item We have made minor changes in the static analysis to make the graph more precise,
-    and the Sect.~5.1 was revised in consequence.
+    and Sect.~5.1 was revised in consequence.
+  \item A section has been added (Sect.~3.3) about the extraction of a scenario
+    from the graph of local causality, in the case the analysis is conclusive,
+    and the successive reachability analysis (Sect.~3.4) now benefits from this.
   \item New explanations and examples have been added all over the paper,
-    especially for the under-approximation (Sect.~3.2)
-    and the detailed example (Sect.~5.1).
-  \item A new large-scale example has been introduced (Sect.~5.2)
+    especially for the under-approximation (Sect.~3)
+    for which we emphasized the Galois connection.
+  \item More explanations have also been added to the detailed example (Sect.~5.1)
+    and a new large-scale example has been introduced (Sect.~5.2)
     in order to better justify this work compared to the existing approach.
-  \item A section has been added (Sect.~3.5) about the extraction of a scenario
-    from the graph of local causality, in the case the analysis is conclusive.
 \end{itemize}
@@
 is equivalent to AANs with classes of priorities.
-Thus, the encoding of Sect.~4 (previously Sect.~4.2)
+Thus, the encoding given in Sect.~4 (previously Sect.~4.2)
 actually extends the applicability
@@
 \begin{itemize}
-  \item We generalised the results to Asynchronous Automata
+  \item We have generalised the results to Asynchronous Automata
     Networks (AANs) which also simplifies the formalism;
   \item The encoding of AANs with classes of priorities into simple AANs
-    (Sect.~4) were added.
-  \item We included a new section (Sect.~3.3)
+    (Sect.~4) have been added.
+  \item We have included a new section (Sect.~3.3)
     which gives a procedure to extract a witness scenario
@@
 \end{itemize}
-We emphasized these in the introduction.
+We have emphasized these in the introduction.
 }
@@
 \answer{
-The aim of our method was not to gain any computation time of memory,
+The aim of our method is not to gain any computation time nor memory,
 but to improve the expressivity of the PH formalism and its associated static analysis.
@@
 which was not the case before.
-This has been emphasized especially in Sect. 5.2.
+This has been emphasized especially in Sect.~5.2.
 }

### 2015-02-24 parts-suppl-sa.tex
flatten folders for the TCS submission system

--- 2015-02-12 parts/suppl-sa.tex
@@
 \label{suppl:demoapproxinf}
-
-\todo{Check with the new notations ($\procs$)}
 
@@
 We first want to demonstrate that
-there exists a scenario that activate all the local states it contains.
-We label all local states of $ps$ by an integer: $ps = \{ p_n \}_{n \in \indexes{ps}}$.
-Let us prove by induction that for all $n \in \indexes{ps}$, there exists a scenario $\delta_n$ so that:
+there exists a scenario that activates all the local states it contains.
+We label all local states of $ps$ by an integer: $ps = \{ p_m \}_{m \in \indexes{ps}}$.
+Let us prove by induction that for all $n \in \{ 0 \} \cup \indexes{ps}$,
+there exists a scenario $\delta_n$ so that:
 $\forall i \in \segm{1}{n}, \PHget{(s \PHplay \delta_n)}{\PHsort(p_i)} = p_i$.
@@
 \begin{itemize}
-  \item If $(P, \{ \emptyset \}) \in \Bee{\Obj}{\Sol}$,
+  \item If $(P, \langle P, \{ \emptyset \} \rangle) \in \Bee{\Obj}{\Sol}$,
     either $\PHtarget(P) = \PHbounce(P)$ and $\delta = \emptyseq$;

### 2015-05-28 response.tex
new response

--- 2015-02-13 response.tex
@@
 \newcommand{\todo}[1]{\textcolor{red}{\textbf{[TODO: #1]}}}
-\newcommand{\answertodo}[1]{\textcolor{red}{\textbf{À appliquer :}} \textcolor{magenta}{#1}}
+%+\newcommand{\answertodo}[1]{\textcolor{red}{\textbf{À appliquer :}} \textcolor{magenta}{#1}}
 
@@
 
-% \noindent
-% Légende :\\
-% \answer{Blabla} $\longleftarrow$ Réponse au reviewer\\
-% \answertodo{Blabla} $\longleftarrow$ Réponse possible sur un point encore non appliqué\\
-% \todo{Blabla} $\longleftarrow$ À faire / à décider
-
 \section*{Summary of the main changes}
 
-We wish thank the reviewers for their comments.
-Please find a summary of the main changes brought to the paper here, and a detailed response to all comments below.
+We wish to thank the reviewers for their comments.
+Please find below a summary of the main changes brought to the paper, and a detailed response to all comments.
 
 \begin{itemize}
-  \item We have changed the main model representation from Process Hitting
-    with classes of priorities (PH) to Asynchronous Automata Networks (AANs).
-    This formalism is equivalent but saves a lot of over-complicated formalism,
-    thus gaining in clarity.
-    All sections have been revised in consequence
-    (some became irrelevant and were completely removed)
-    and we added a discussion about the links between PH and AAN.
-  \item We have made minor changes in the static analysis to make the graph more precise,
-    and the Sect.~5.1 was revised in consequence.
-  \item New explanations and examples have been added all over the paper,
-    especially for the under-approximation (Sect.~3.2)
-    and the detailed example (Sect.~5.1).
-  \item A section has been added (Sect.~3.5) about the extraction of a scenario
-    from the graph of local causality, in the case the analysis is conclusive.
+  \item \todo{Main changes}
 \end{itemize}
@@
 
+\subsection*{Reviewer \#1}
+
+Reviewer \#1: In this article the  Asynchronous Automata Networks (AANs) are studied.
+An AAN is an Automata Network with synchronised transitions between automata, where each transition changes the local state of exactly one automaton, but the number of synchronazing state sis not restricted.
+The AAN with priorities are also studied.
+
+Authors build a method of efficient under-approximation for the problem of state reachability.
+The computational cost is lower than the cost of usual model checker methods.
+Also, a reduction from AANs with priorities to the AANs without priorities is given.
+
+Clearly, the paper is based on real applications of the system studied.
+It seems that the method and the theory are build for and from some specific applications with a interesting idea.
+Therefore, from the purely automata theoretical point of view,  the methods and results are not very strong nor interesting as themself.
+On the other hand, the method is used in two example applications in the end of the paper to support the fact that the model and the method work well in practise.
+This is probably the strongest part of the paper.
+
+General: 1) somehow the system of AANs seems such that it has conection or roots or generalization by cellural automata.
+Obviously, CA are a more general model and AANs are a restriction, but it could be interesting to see whether can you generalize or simulate in simple manners your system with CA?
+
+2) Just a note: As I see it, the AANs is an interactive model of computation, and that is interesting.
+based on this, can you consider the reachability of state as a game in (multiplayer) game of AAN?
+Does  your work give a fast method for checking for winning strategy?
+
+Minor coments to the authors:
+
+page 1, authors: names are not in alphabetical order probably for a good reason, but it strikes my mathematician eye badly.
+
+page 3, line 13: is much straightforward. More?
+
+page 4, line 20: size, I would say length.
+
+page 8, line -5 -- -4. Index a and b for delta are a bad choise a and b are for the automata and states, and delta's subscripts are numbers.
+
 \subsection*{Reviewer \#2}
 
-[…]
+Reviewer \#2: SUMMARY OF THE RESULTS
 
-According to the authors, the static analysis approach presented in the paper is inspired from a previous paper ([13] Paulevé, Magnin, Roux.
-Static analysis of biological regulatory networks dynamics using abstract interpretation).
-By comparing the paper with [13], I had the impression that most of the developments in the current paper were just an exercise to borrow the techniques developed in [13] into the setting of Process Hitting with *priorities*.
-This is caused by the fact that in Section 2 (which introduces the PH framework to the reader) there are not enough intuitive explanations and examples to help the reader understand the concepts.
-(To this aim, in Section 2, a running example would be a welcome addition.)
-In particular, a weak point of the paper lies in the restrictions introduced in Sections 2.2 and 2.3, which are not motivated.
-Those sections should be rewritten to clearly explain why those restriction are needed, and discuss their implications with respect to the reduced modelling expressiveness which ensues (e.g.
-which models cannot be described anymore?).
+In this paper the authors introduce so-called asynchronous automata networks, which are automata networks with transitions synchronized between the automata in such a way that each transition changes the local state of exactly one automaton.
+There is also a generalization of asynchronous automata networks, called asynchronous automata networks with classes of priorities.
+This model is shown to be equivalent to the named networks without priorities.
 
-\answer{
-The intent of this paper is to adapt the static analysis methods previously developed in [13] to the case of the PH with priorities, that is, models with a new kind of dynamics and preemptions that did not exist previously.
-In this revision, we finally focus on AANs, that are equivalent models,
-but better highlights the difference with the “standard” PH of [13],
-that is, PH without priorities.
-The static analysis method thus required adaptations
-that we tried to better motivate in this revision.
-}
+The authors have developed a method of performing reachability analysis and a way of getting a valid execution path if the reachability question has a positive answer.
+The method of performing reachability analysis is based upon abstract interpretation, and the complexity of such an analysis is polynomial in the total number of local states and exponential in the number of local states within a single automaton.
 
-With respect to the workshop version, Section 4.2 has been added to present a translation of PH models with multiple priority classes (with restrictions from Section 2.3 assumed) into an "equivalent" (weakly-bisimilar) PH model with only two priority classes.
-Since the restrictions from Section 2.3 are already assumed for PH models with multiple priority classes, this strengthens the need for a discussion on those restrictions.
+The applicability of the method has been demonstrated by the authors by considering two large-scale biological models.
 
-\answer{
-The new AAN representation makes this difference clearer:
-the previously emphasized sub-class of PH models used for the static analysis
-is equivalent to AANs,
-while the whole class of PH models with any number of classes of priorities
-is equivalent to AANs with classes of priorities.
-Thus, the encoding of Sect. 4.2 actually extends the applicability
-of our static analysis; we have added some discussion to emphasize this.
-}
+My main concern about the paper is that it is written in a rather unclear manner.
+Some of the definitions are given in a very formal way; this does not help understanding the intuition behind them.
+On the other hand, the authors have managed to give a very good intuition in description of the running examples of the paper.
 
-As regards the biological experiments presented in Section 5.2, this section should be extended by reporting more details about the experiments carried and the results obtained.
-Moreover, you should compare the results with the analogous experiments from [13], in which the same model (TCR pathway) had been analysed with good results.
-What improvements are there?
+In my opinion, the presentation of the material of the paper should be improved.
 
-\answer{
-The improvements concern the expressivity of the models tackled.
-The experiments of [13] only conclude on the reachability for dynamics
-that are not exactly those of ADNs (a.k.a.~Logical Networks).
-We have added some discussion to emphasize this.
-}
+COMMENTS TO AUTHORS
 
-I also point out that the comparisons with a model-checker should be actually carried out.
-The fact that the test you performed caused out-of-memory errors does not allow any conclusion to be drawn, even more so considering that only 2GB of RAM have been used.
+page 1, line 49 ---
+I would reformulate the phrase "with [4,5]" somehow in different way.
 
-\answer{
-The experiment we carried with the LibDDD model-checker led us to the conclusion that the memory needs for such a method is several orders of magnitude above our method, which we would consider a sufficient result in itself.
-Furthermore, with such a memory use, one cannot expect to be able to study bigger models (say, thousands of components) while our method has a polynomial complexity in the size of the model or the construction of the saturated graph of local causality, and could thus tackle such bigger models.
-Thus, we have not performed more experiments,
-but we have added some precisions about our thoughts in the paper.
-}
+page 1, line 52 ---
+Replace "behaviours" in the phrase "their usual behaviours" with "behaviour".
 
-Beyond the above concerns, the paper would also benefit from a reorganization, since I found it sometimes difficult to follow.
-This is particularly relevant for Section 4, where the translations proposed are just thrown in, without discussing their relevancy to the purpose of the paper.
+page 2, line 21 ---
+Remove the second verb "are" in the phrase "This is modelled by actions are of the form".
 
-\answer{
-The translations could indeed be better discussed and justified,
-we have taken this comment into account.
-We also hope that the use of AANs simplifies the formalism
-and emphasizes the use of these translations.
-}
+page 2, line 27, "avoid to build" ---
+Reformulate as "avoid building".
+The same comment applies to many other places within the paper (for instance, page 5, line 51, page 3, line 43).
 
-Minor comments […]
-% ----------------
-% page 1
-% - abstract: "...
-as it is illustrated on the model-checking of a signalling network of 94 components, which is unprecedented.": I am not convinced the such application is "unprecedented", since the same model has been already analysed with good results in [13].
-% page 5
-% - do not use \ldots for the finite set of sorts
-% - for defining prio(h), the same action $h$ must not be present in two different classes (this condition is missing)
-% - Def.2: "sub-set" --> "sub-state" (twice)
-% - Def.2 (and other places in the paper): symbol $\subset$ is usually means *strict* subset. Check its use in the paper and replace it with $\subseteq$ where appropriate.
-% - Def.3: "We also extend this definition to a set of processes given that all processes are from different sorts by the override of each process" ???
-% - Def.3: what is $\widetilde{ps}$ ?
-% 
-% page 6
-% - in Figure 1 there are too many arrows that overlap which make it difficult to read
-% - the example should be completed by listing all the actions from the two priority classes
-% - Sect.2.2: "a1 and b1 to make c0 bounce to c1": you should replace "make" with "allow", since according to the semantics c0 is not forced to go to c1 asap.
-% - Sect.2.2: "one for each sub-state of the presence of processes a1 and b1": not clear
-% 
-% page 7
-% - "... instead of independent hits from a1 and b1.": not clear
-% - (also in other places) "allows to" --> "allows <someone> to"
-% - "build cooperations with no temporal shift": please clarify what you mean with "temporal shift"
-% - $Sce|_1$ is not defined
+page 7, line 29 ---
+I would replace "Subsect." with "Subsection" throughout the paper.
 
-\answer{
-We these comments into account.
-}
+page 7, Definition 4, line 55, in the sentence "The set of all objectives is called ..." ---
+Using the logical AND operator "$\land$" is too formal and this unnecessarily complicates reading of the definition.
+I would replace "$\land$" with a word "and".
 
-\subsection*{Reviewer \#3}
+page 8, Definition 6 ---
+The comment "($\gamma_s: OSeq \to$ ...)" in the parentheses after "Definition 6" complicates the perception of the material. This also applies to other definitions.
 
-Minor language issues: […]
+page 8, line 52 ---
+To which definition does the phrase "in the previous definition" refer to?
 
-% (1) In introduction first paragraph at the sixth line there is a typo with 3 full stops ...
-% (2) Second paragraph in introduction fifth line, it should be USUALLY, rather then USUAL, please change it.
-% (3) Same paragraph: Components rarely have more "that" four levels, which should be: Components rarely have more "than" four levels.
-% (4) Please add some text around the figures 1,3, and 4 so that a non technical reader (biologist) might have some idea about the interactions in the figures.
-% (5) In discussion the following sentence needs to be rewritten: "i.e., without an intermediate encoding; our objective being to increase the conclusiveness of the static analysis   approach".
+page 8, Lemma 1 ---
+I recommend changing the formulation of the lemma so that it contains at least some words.
+The comment right before the formulation of the lemma states essentially the same thing as the lemma, without any intuition.
 
-\answer{
-We took the comments about the language issues of Reviewer \#3 into account.
-}
+page 9, line 53 ---
+Replace "would consists" either with "would consist" or with "consists".
 
-\subsection*{Reviewer \#4}
+page 10, comment before Definition 8 ---
+First of all, I would give a shorter intuition before Definition 8 and only then this delaited explanation of the definition.
+The definition itself is very difficult to follow and the explanation is written in a really succinct way, that does not make it easier to get.
+Perhaps the authors could state how this definition is different from a similar definition in the cited work [16].
 
-[…]
+page 10, line 53 ---
+In the phrase "we prove that if ..., if ..., and if ..., then" I would only leave the first "if" and remove the two others.
 
-With respect to the workshop version of the paper I don't see a significant improvement that should justify a further publication of the results.
-In particular, there are several new theorems, but they do not add significant novelties to the already proposed ideas.
-On the contrary, aspects that could have been given more accurate treatment are left poorly addressed.
-In particular:
+page 11, line 33 ---
+Remove "we know" in the sentence "Then, we know (by induction)".
 
-\answer{
-The additions regarding the workshop paper are the following:
-\begin{itemize}
-  \item In this revision, we generalised the results to Asynchronous Automata
-  Networks (AANs) which also simplies the formalism;
-  \item In this revision, we also included a new section (3.3) which give a
-  procedures to extract a witness scenario satisfying a given reachability
-  property.
-  \item The encoding of AANs with classes of priorities into simple AANs
-  (section 4).
-\end{itemize}
-We emphasized these in the introduction.
-}
+page 12, lines 10-12 ---
+In the sentence "in order to reduce the number ..., and potentially removing cycles" replace "removing" with "remove".
 
-- discussion on the computational gain acquired with the new approach is not formally addressed and very poorly discussed (end of page 12, see also comment below)
+page 12, line 14 ---
+Something seems to be wrong with the phrase "would imply to enumerate".
 
-\answer{
-The aim of our method was not to gain any computation time of memory,
-but to improve the expressivity of the PH formalism and its associated static analysis.
-We are now able to formally check Asynchronous Discrete Networks
-(also called Thomas' models)
-which was not the case before.
-This has been emphasized especially in Sect. 5.2.
-}
+page 12, lind 18 ---
+In the sentence "from the initial state ... depicted" I would replace "depicted" to "illustrated" and actually put this word to another place within the sentence.
 
-- the static analyses that are proposed are based on abstract interpretation, however there is not a formal introduction of them in this framework.
-In particular there are abstractions and concretizations whose domains (and their relationships in terms of Galois insertion / connection) are not clearly stated.
-Moreover, the overall ideas of the abstractions are lost in the heavy technical presentation.
-This is difficult to read and does not give sufficient intuition to grasp the concepts, which remain hidden behind the notation.
+page 12, line 20 ---
+I think the phrase "but does not conclude regarding the reachability of $c_1$" could be rewritten in a simpler way.
 
-\answer{With this revision, we removed and simplies a lot a notations, and added
-more explanations for the under-approximation of reachability properties in AANs
-(section 3).
-More details on the abstract domain (objective sequences) and their
-interconnections with concrete scenarios are given in section 3.1.
-The relationship of Local Causality Graphs with objective sequences is also
-better motivated (collecting semantics for the possible refinements of the
-objective sequences).
-However, the goal of this section being at building particular cases of
-scenarios, no completness of the collection is required.
-We believe that the revision of this section brings sufficient intuition to
-capture the main concepts of the analysis, while avoiding un-necessary technical
-definitions.
-}
+page 15, line 12 ---
+Put a comma before "where" in the phrase "having n+1 local states where n".
+This also concerns some other places of the paper.
 
-- the biological examples look interesting and appropriate, but the details that are given in the paper look not sufficient to appreciate the demonstration of the approach that they should give.
+page 15, line 16 ---
+Remove the second period in "etc.).".
 
-\todo{Quels détails supplémentaires devrait-on donner ?}
+page 15, line 26 ---
+I would consider using the term "transformation" instead of "translation".
 
-- the link to Boolean Networks and Multivalued Boolean Networks is given by a translation that is published in another paper.
-That is ok, but the authors mention Asynchronous Discrete Networks as an "intermediate" model between the models previously mentioned and the Process Hitting framework.
-This remains an obscure connection and "Asynchronous Discrete Networks" cannot be found as keyword in the literature, at least at a first general search.
+page 15, paragraph before Definition 10 ---
+This is a comment both to Definition 10 and Definition 11. I would try to "separate" them.
 
-\answer{
-We called Asynchronous Discrete Networks (ADN) the class of Logical Models
-with discrete values of the variables,
-either Boolean or multivalued,
-and evolution functions (or, equivalently, focal parameters).
-Although the denomination “ADN” does not exist in the literature,
-there is in fact no widespread or unified term to qualify this class of models.
-We have detailed this choice in the paper and justified the use of this term,
-and emphasized references that also defined these kinds of models.
-}
+page 16, line 56 ---
+Consider replacing "in the following" with "in what follows".
+This comment applies to several other places in the paper.
 
-- the overall presentation of the ideas and results are heavily technical and frankly difficult to read even for a reader that is used to formality.
-The most difficult aspect is the proliferation of notation, which forces the reader to continuously go back and forward to recall the meaning of the very large number of symbols.
+page 19, Section 5 ---
+The phrases "this section aims at giving application examples", "we give in this section a detailed example", "we consider in the following a model of" repeat the same idea within a half of the page.
+I would try to restructure the introductory text to Section 5 and its Subsection 5.1.
 
-\answer{
-The use of AANs instead of PH with classes of priorities
-allows to greatly simplify the whole paper
-and, we hope, increase comprehension.
-}
+page 20, line 25 ---
+Remove the second article in "the the".
 
-Comments and suggestions […]
+page 20, line 46 ---
+The sentence starting with "This consists in using Theorem 1 ..." is written in a very sophisticated way.
 
-% page 2, paragraph 1: Some general references should be given here, reference papers, overviews, and so on.
-% 
-% p 2, end of paragraph 2, it is not clear if the name "Asynchronous Discrete Networks" is introduced by the authors or it is taken from [4], where multivalued Boolean Networks are discussed. 
-% 
-% p 3, line -13 what does it mean "to decide a successive reachability property"?
-% 
-% p 4, line 12 the least fix point could be greater than $x_0$; moreover, what are the hypotheses on f? It may have not a fix point at all
-% 
-% p 5, line -16 the set of all sub-sets —> the set of all sub-states 
-% 
-% p 5, l -14 a symbol like $\preceq$ or $\sqsubseteq$ would be more intuitive than $\subseteq$ for sub-states
-% 
-% p 5, l -4 can a scenario $\delta$ be empty?
-This may be important in the subsequent part of the paper, for instance at page 9, Lemma 3, could the empty scenario $\delta$ be selected by the $\exists$ after the main implication?
-% 
-% p 5, l -3 the fact that there is a set of scenarios implies that there is non-determinism.  Such aspect is never mentioned explicitly in the paper. It could be explicitly addressed.
-% 
-% p 6, l 4 (caption of figure 1) in drawn -> is drawn
-% 
-% p 6, last line and page 7 first line: what does it mean "one for each sub-state of the presence of processes $a_1$ and $b_1$"?
-% 
-% p 7 section 2.3 title: Restrictions may be misleading, why don't call this section "Conditions"?
-% 
-% p 7, l -2 all actions of priority 1, which —> all actions of priority 1 from s, which
-% 
-% p 8, l 6 greater than 2 -> greater than or equal to 2
-% 
-% p 8, l 8 We note $\Gamma$ —> We denote by $\Gamma$
-% 
-% p 8 Def 7 is a well-formed component if -> is a well-formed component, and so $a \in \Gamma$
-% 
-% p 8 Def 9 is a well-formed cooperative sort if -> is a well-formed cooperative sort, and so $a \in Delta$, if 
-% 
-% p 8 Def 9, condition (iv), does it require a sort of "determinism"  of cooperative encodings?
-% 
-% p 8, l -7 "represented by", in which sense?
-% 
-% p 10, -19 we note $a_i$ —> we denote by $a_i$
-% 
-% p 10, l -10 a bounce sequence on a can be abstracted into sets of all its hitters that are not in sort a (Def 16).
-— Is this an idea for an abstract interpretation?
-If yes the mechanism of abstraction / concretization, as well as the Galois connection/insertion between the abstract and concrete domains, is not clear and the whole underlying idea I could not catch by the definitions.
-% 
-% p 10, l -8 on other sots -> on other sorts
-% 
-% p 11, l 7 we denote $\gamma_\varsigma$ -> we denote by $\gamma_\varsigma$
-% 
-% p 11, l 7 the set of scenarios concretizing an objective sequence .. (Def 17) .. again the abstract interpretation is mentioned, but not fully introduced and explained.
-% 
-% p 11, l 16 the notation $\delta_{1 \ldots \Phi(n)}$ is not introduced
-% 
-% p 11, l 23 given by $maxCont_\varsigma$ -> denoted by $maxCont_\varsigma$
-% 
-% p 12, Def 20 this looks like a definition of an abstract fixpoint semantics to derive the graph of local causality. Ok, why is it not mentioned?
-% 
-% p 12, Def 20, rule (1): $\omega$ is an objective sequence , which is neither in Obj nor in Proc or Sol. It seems there is a "type mismatch" with the definition of $V^\omega_\varsigma$.
-% 
-% p 12 Def 21 it is not clear the definition of "children process"
-% 
-% p 12 last paragraph the discussion on the complexity issue looks very limited considering that this is supposed to be one of the contributions of the whole work.
-It is mentioned that "it is possible to compute only a subset of $V \cap Sol$", how?
-
-\answer{We have taken most of these comments into account.}
+page 29, reference [18] ---
+The year and the pages of the publication are missing.
 

### 2015-05-28 response.tex
response++

@@
 
+% Citations et bibliographie style Harvard
+\usepackage[agsm,dcucite]{harvard}
+\renewcommand{\harvardand}[1]{\& }
+\renewcommand{\harvardurl}[1]{\url{#1}}
+\newcommand{\citefullname}[2]{#2 \citeasnoun{#1}}
+
 % \newcounter{pointno}
@@
 
-\newcommand{\answer}[1]{\textcolor{blue}{#1}\vspace*{1em}}
+\newcommand{\ilanswer}[1]{\textcolor{blue}{#1}}
+\newcommand{\answer}[1]{\ilanswer{#1}\vspace*{1em}}
 
@@
 
+\ilanswer{Indeed, The links between AANs and cellular automata could be studied more thoroughly.
+However, we are not sure that AANs consist in a restriction of cellular automata.}
+
+\ilanswer{We show in the following that an AAN can represent an Asynchronous Finite Cellular Automata (AFCA).
+An AFCA is a finite set of cells that share a same update rule (we consider no border effects).
+We consider that the transitions between each global states are asynchronous in the meaning of the “Random Independent” scheme given in \cite{cornforth_artificial_2003} and \cite{harvey_time_1997},
+that is, exactly one randomly chosen cell is updated between two states.
+Any AFCA can be represented as an AAN by considering one automaton for each cell containing two local states (corresponding to “active” and “inactive”).
+The rules are modeled by actions that represent the creation/vanishing of a cell given all possible states of its neighborhood.
+This is possible because we can create one action for each configuration of the neighborhood (for the cases where the state of the cell must change).}
+
+\ilanswer{The result is a (very repetitive) AAN that encompasses the same dynamics than the AFCA,
+with the exception of unchanged states in AFCA that are:
+\begin{itemize}
+  \item either a stable state, in which case the AAN has no next state,
+  \item or not a stable state, in which case the next state of the AAN will necessarily
+    encompass exactly one change (because we do not allow a transition with no change).
+\end{itemize}}
+
+\ilanswer{Thus, the representation of AFCA in AANs is possible with the considered updating scheme.
+However, the representation has a high complexity, and AANs are not very suited to represent this kind of repetitive patterns.
+Furthermore, it is more likely that this kind of patterns will lead to some inconclusiveness
+when studying its dynamics with the method proposed in our paper,
+especially due to the creation of cycles in the Local Causality Graphs
+(which may represent the fact that a cell has to change its state several times to allow the reaching of a given objective).}
+
+\answer{In conclusion,
+more experiments may be required in order to acknowledge how our method fits into the modeling and analysis of cellular automata,
+and some enrichments of the static analysis may be needed to obtain satisfying results.
+}
+
+\todo{Déplacer une partie dans le papier}
+
 2) Just a note: As I see it, the AANs is an interactive model of computation, and that is interesting.
@@
 
+\answer{This question is also very interesting.
+The main problem here seems to be able to represent the given multiplayer game as an AAN ---
+in which case the analysis tools can be used straightforwardly.
+However, the notion of two players playing alternately (and not randomly) seems quite difficult
+to represent in an AAN, even with the notion of priorities.
+One way would be to introduce dynamic priorities (as opposed to static priorities as presented in the current paper) which would however require some way to translate them back into an AAN with static priorities (or without priorities at all).
+}
+
+\todo{Voir formalismes courants en théorie des jeux}
+
+\todo{Déplacer une partie dans le papier ?}
+
 Minor coments to the authors:
+
+\todo{À appliquer}
 
@@
 In my opinion, the presentation of the material of the paper should be improved.
+
+\todo{Rajouter des explications infromelles}
+
+\todo{Simplifier les définitions formelles ?}
 
@@
 
+\bibliography{biblio}
+
 \end{document}

### 2015-05-29 response.tex
apply minor changes

@@
 
-\todo{À appliquer}
-
 page 1, authors: names are not in alphabetical order probably for a good reason, but it strikes my mathematician eye badly.
 
-page 3, line 13: is much straightforward. More?
+\answer{We willingly chose the order of the authors' names related to the individual participation of each one.}
 
-page 4, line 20: size, I would say length.
+\answer{We have taken the other minor comments into account.}
 
-page 8, line -5 -- -4. Index a and b for delta are a bad choise a and b are for the automata and states, and delta's subscripts are numbers.
+%page 3, line 13: is much straightforward. More?
+
+%page 4, line 20: size, I would say length.
+
+%page 8, line -5 -- -4. Index a and b for delta are a bad choise a and b are for the automata and states, and delta's subscripts are numbers.
 
@@
 I would replace "$\land$" with a word "and".
+
+\answer{In a general fashion, we tied to use formal symbols as much as possible in all definitions.
+However, we tried to change the paging/formulation in order to make the definitions clearer.}
 

### 2015-05-29 parts-def-ph.tex
apply minor changes

--- 2015-02-18 parts/def-ph.tex
@@
 each one containing a finite number of \emph{local states}.
-A local state is noted $a_i$ where $a$ is the name of the automaton it belongs to,
+A local state is noted $a_i$, where $a$ is the name of the automaton it belongs to,
 and $i$ is the identifier of this local state within automaton $a$.
@@
 so that playing them changes exactly one local state.
-Therefore, an action is denoted by $\PHhit{A}{b_j}{b_k}$
+Therefore, an action is denoted by $\PHhit{A}{b_j}{b_k}$,
 where $A$ is a set of local states

### 2015-05-29 parts-example.tex
apply minor changes

--- 2015-02-18 parts/example.tex
@@
 
-We give in this section a detailed example of the use of classes of priorities
+We give here a detailed example of the use of classes of priorities
 in order to model a system with temporal constraints.
@@
 
-We consider in the following a model of metazoan segmentation
+Let us consider a model of metazoan segmentation
 inspired from a first translation to Process Hitting model given in~\cite{PMR10-TCSB}.
@@
 a switch of $a$.
-This forces the the evolution of genes $a$ and $c$
+This forces the evolution of genes $a$ and $c$
 to alternate in order not to miss a stripe;
@@
 and finally $\myp^3 = a_1$ once again to ensure that we entered a cycle.
-This consists in using \pref{th:approxinf} several times
-to check these reachabilities successively,
-by splitting it following the method given in \pref{ssec:ordered-ua}.
+%This consists in using 
+For this, we apply the method proposed in \pref{ssec:ordered-ua}:
+we consider each reachability step independently
+and we use \pref{th:approxinf} three times;
+the initial states of steps 2 and 3 are computed with the
+extraction method of \pref{ssec:concret}.
 
@@
 \footnote{Files are available at
-\url{http://maxime.folschette.name/underapprox-aan.zip}. \todo{Mettre en ligne}}.
+\url{http://maxime.folschette.name/underapprox-aan.zip}.}.
 Boolean networks being a subclass of AANs, this translation is straightforward.
-In the following, we first present the Pint implementation,
+In the rest of this section, we first present the Pint implementation,
 then the two models that were used for our tests,

### 2015-05-29 parts-intro.tex
flatten folders for the TCS submission system
apply minor changes

--- 2015-02-19 parts/intro.tex
@@
 powerful~\cite{thomas1990biological,deJong02,snoussi_logical_1993}.
-Such a work started in the seventies, with~\cite{kauffman69,Thomas73}.
+Such a work started in the seventies,
+with the emergence of the notion of Boolean Network~\cite{kauffman69}
+and its use to represent biological phenomena~\cite{Thomas73}.
 It was later enriched in many directions and widely used to elucidate many biological questions.
-Among these questions, a major one is to understand precisely how biological systems evolve and behave; why and how they change their usual behaviours, etc.
+Among these questions, a major one is to understand precisely how biological systems evolve and behave; why and how they change their usual behaviour, etc.
 These questions are strongly linked to the (possible or inevitable) reachability of some states.
@@
 consisting in a restriction of these frameworks where the evolution of a component is determined by the state of at most one other component that does not evolve.
-This is modelled by actions are of the form $X + Y \rightarrow X + Y'$ where $X$ behaves like a catalyst molecule that “hits” another molecule $Y$ and changes it into $Y'$, without being changed itself.
+This is modelled by actions of the form $X + Y \rightarrow X + Y'$, where $X$ behaves like a catalyst molecule that “hits” another molecule $Y$ and changes it into $Y'$, without being changed itself.
 Assuming catalysts are always available, this can represent any biochemical system made of monomolecular reactions, and can also represent catalytic networks such as metabolic networks.
@@
 Our motivation behind this framework was to design a model and analysis techniques adapted to biological modelling.
-These analyses avoid to build the whole state space, which allows to tackle very large systems (that would have led to a huge number of states, hopelessly too huge to be analysed).
+These analyses avoid building the whole state space, which allows to tackle very large systems (that would have led to a huge number of states, hopelessly too huge to be analysed).
 They are based on the fact that most biological models have few levels of expression per component:
@@
 and the concept of priority relations among the transitions of a network has also more recently been introduced by A.~K.~Wagler \textit{et~al.}~\cite{waw,WaglerW12} in order to allow modelling deterministic systems for biological applications.
-The concept of priority is much straightforward in the approach of process algebras as it was shown by R.~Cleaveland and M.~Hennessy in~\cite{Cleaveland199058} and their abstractions and equivalences were studied in~\cite{Cleaveland:2007:PAP:1282576.1282847}.
+The concept of priority is rather straightforward in the approach of process algebras as it was shown by R.~Cleaveland and M.~Hennessy in~\cite{Cleaveland199058} and their abstractions and equivalences were studied in~\cite{Cleaveland:2007:PAP:1282576.1282847}.
 It was later extended for applications in the field of systems biology by M.~John \textit{et~al.}~\cite{jlnu2010}.
@@
 the range of applicability of the results.
+Finally, \pref{sec:example} has been improved with a detailed example
+and a new large-scale example with a quantitative examination of the results.
 
@@
 $x = (x_i)_{i \in \segm{1}{n}}$ is a sequence of elements indexed by $i \in \segm{1}{n}$,
-then $\card{x} = n$ is the size of $x$
+then $\card{x} = n$ is the length of $x$
 %we denote %$|x| = (b-a)+1$ the size of this sequence and

### 2015-05-29 parts-models-ph-php.tex
apply minor changes

--- 2015-02-23 parts/models-ph-php.tex
@@
 In this section, we define the notion of AANs with classes of priorities,
-and give a translation from these into
+and give a transformation from these into
 AANs without priorities, as defined in \pref{sec:ph}.
@@
   \end{itemize}
-  Furthermore, in the following, we will use $\Fsem{\Fop{h}}{s}$ as a shorthand for
+  Furthermore, in what follows, we will use $\Fsem{\Fop{h}}{s}$ as a shorthand for
   $\Fsem{\Fop{h}}{\toset{s}}$.
@@
 Moreover,
-provided that in the following we are only interested in properties that are true
+provided that in what follows we are only interested in properties that are true
 and thus we make no distinction between false and undecided results,

### 2015-05-29 parts-sa.tex
apply minor changes

--- 2015-02-18 parts/sa.tex
@@
   If $a \in \components$, the reachability of a local state $a_j$ from a local state $a_i$ is called an \emph{objective}, noted $\PHobj{a_i}{a_j}$.
-  The set of all objectives is called $\Obj \DEF \{ \PHobj{a_i}{a_j} \mid a \in \components \wedge (a_i, a_j) \in \PHl_a \times \PHl_a \}$.
+  The set of all objectives is noted:
+  \[\Obj \DEF \{ \PHobj{a_i}{a_j} \mid a \in \components \wedge (a_i, a_j) \in \PHl_a \times \PHl_a \} \enspace.\]
   For an objective $P = \PHobj{a_i}{a_j} \in \Obj$, we define: $\PHsort(P) \DEF
-  a$, $\PHtarget(P)\DEF a_i$, $\PHbounce(P)\DEF a_j$,
-  and $P$ is said \emph{trivial} iff $a_i = a_j$.
+  a$, $\PHtarget(P)\DEF a_i$, $\PHbounce(P)\DEF a_j$.
+  Finally, $P$ is said \emph{trivial} iff $a_i = a_j$.
 
@@
 \end{align*}
-where $\omega^\vartriangle$ refers to the objective sequence $\omega$ where
+in which $\omega^\vartriangle$ refers to the objective sequence $\omega$ where
 trivial objectives have been removed.
-The notation $\delta_{a..b}$ in the previous definition
-denotes the subsequence of $\delta$ between indexes $a$ and $b$,
+The notation $\delta_{j..k}$
+denotes the subsequence of $\delta$ between indexes $j$ and $k$,
 as defined on page \pageref{notations}.
@@
 From \pref{def:ltw} and \pref{def:concr}, we derive that if
-$\w \ltw \w'$, then $\concr(\w)\subseteq\concr(\w')$ (\pref{lem:ltw}).
+$\w \ltw \w'$, then the scenarios matching $\w$ also match $\w'$ (\pref{lem:ltw}).
+%$\concr(\w)\subseteq\concr(\w')$ (\pref{lem:ltw}).
 \begin{lemma}\label{lem:ltw}
-$\w\ltw\w' \Longrightarrow \concr(\w)\subseteq\concr(\w')$\enspace.
+$\forall \w, \w' \in \OS, \forall s \in \PHl,
+\w\ltw\w' \Longrightarrow \concr(\w)\subseteq\concr(\w')$\enspace.
 \end{lemma}
@@
 sequences following its bounce sequences:
-the refinement of objective $P$ with $\zeta\in\BS(P)$ would consists in prepending to $P$ the
+the refinement of objective $P$ with $\zeta\in\BS(P)$ consists in prepending to $P$ the
 objectives leading to the hitters of the actions in $\zeta$, in the same sequential order;
@@
 
-In this section, we prove that if the LCG has no cycle, if all its nodes in $\Obj$ have at least one
-child, and if all its nodes in $\sSol$ satisfy a
+In this section, we prove that if the LCG has no cycle, all its nodes in $\Obj$ have at least one
+child, and all its nodes in $\sSol$ satisfy a
 particular criteria, so-called independence, then from any state
@@
 for each $b_i \in\PHhitter(\zeta_n)$,
-we refine the objective $\obj{b_j}{b_i}$ where $b_j$ is the state of $b$ in the current state.
+we refine the objective $\obj{b_j}{b_i}$, where $b_j$ is the state of $b$ in the current state.
 By induction, $\obj{b_j}{b_i}$ is a child of $b_i$ in the LCG of \pref{def:lcg}.
-Then, we know (by induction) that the current state of $b$ is $b_i$.
+Thus, we know that the current state of $b$ is $b_i$.
 After having repeated this procedure for each $b_i\in\PHhitter(\zeta_n)$,
@@
 $\BS$.
-Therefore, in order to reduce the number of bounce sequences to consider, and potentially removing
+Therefore, in order to reduce the number of bounce sequences to consider, and potentially remove
 cycles and non-satisfying nodes,
@@
 (and in particular: a single bounce sequence) for each objective.
-However, such an approach would imply to enumerate all possible combinations of bounce sequences
-subsets, hence being exponential in the number of objectives having at least two bounce sequences.
+However, such an approach requires to enumerate all possible combinations of bounce sequences
+subsets, hence being exponential in the number of considered bounce sequences.
+%objectives solved by at least two bounce sequences.
 
 \begin{example}
-  If we confider the AAN of \pref{fig:ph-livelock},
-  from the initial state $\PHstate{a_1, b_0, c_0}$ depicted,
-  the under-approximation given in \pref{th:approxinf}
-  concludes that $a_1$ is reachable, as well as $b_1$, but
-  does not conclude regarding the reachability of $c_1$.
+  We consider in this example the AAN of \pref{fig:ph-livelock},
+  and the initial state $\PHstate{a_1, b_0, c_0}$
+  that is also represented in this Figure.
+  The under-approximation given in \pref{th:approxinf}
+  concludes that $a_1$ is reachable from this initial state, as well as $b_1$.
+  Nevertheless, it does not conclude regarding the reachability of $c_1$.
   This is due to the fact that the node $\{ a_1, b_1 \} \in \Bv \cap \sSol$
@@
 for a context $\ctx \in \Ctx$ so that $s_0 \subset \ctx$.
-The algorithm proposed in the following relies on a traversal of the Local Causality Graph
+The algorithm proposed in what follows relies on a traversal of the Local Causality Graph
 $\cwB$ that has been used for this conclusion.
@@
 one can use the same approach as for sub-state reachability by introducing
-a new automaton $\reach$ having $n+1$ local states where $n$ is the size of the
+a new automaton $\reach$ having $n+1$ local states, where $n$ is the size of the
 sequence of reachability, and $n$ actions making it bounce gradually from $\reach_0$ to
 $\reach_n$ with hitters corresponding the successive local states
-(e.g., $\PHfrappes{a_i}{\reach_0}{\reach_1}$,
+(\eg $\PHfrappes{a_i}{\reach_0}{\reach_1}$,
 $\PHfrappes{b_j}{\reach_1}{\reach_2}$, etc.).

### 2015-06-01 parts-sa.tex
add informal explanations about the LCG

@@
 actions of one of the bounce sequences of the objective (\pref{lem:bs-concr}).
+
 \begin{lemma}
@@
 
-Given one initial objective, one could then iteratively refine the objective into objective
-sequences following its bounce sequences:
-the refinement of objective $P$ with $\zeta\in\BS(P)$ consists in prepending to $P$ the
-objectives leading to the hitters of the actions in $\zeta$, in the same sequential order;
-the generalization of the refinement to an objective sequence would require to consider all possible
-interleaving between the refinements \cite{PMR12-MSCS}.
+\modmf{%
+The previous subsections permitted to define all the tools needed to build the Local Causality Graph (LCG), such as the on depicted in \pref{fig:sa-livelock}.
+This graph is denoted $\cwB$ where $u$ is the local state to be reached
+from the initial context $\ctx$.
+It will be the basis of our static analysis,
+as it represents the causality links between the different objectives involved
+in the solving of the reachability of $u$.
+This LCG is built recursively by considering some required local states (\eg $u$),
+linking them to objectives (\eg, $\PHobj{w}{u}$, if $w \in \ctx$),
+and locally solving these objectives in order to create new required local states
+from other automata.
+}
+
+Technically,
+one can iteratively refine a given objective into (possibly several) objective
+sequences following its bounce sequences.
+Indeed, the refinement of an objective $P$ with $\zeta\in\BS(P)$
+consists in prepending to $P$ the
+objectives leading to the activation of all hitters of the actions in $\zeta$,
+in the same sequential order.
+The generalization of this refinement to an objective sequence would
+naturally require to consider all possible
+interleaving between the refinements~\cite{PMR12-MSCS}.
 
@@
 
-These refinements can be summarized with a so-called Local Causality Graph (LCG).
-Given an initial context $\ctx$ and a local state $\myp\in\Proc$,
-an LCG $\cwB = (\cwV, \cwE)$
-is a digraph where $\cwV \subseteq \Proc\cup \Obj \cup \Sol \cup \sSol$ is the set of vertices
-where $\sSol=\powerset(\Proc)$ and $\Sol=\Obj\times\powerset(\sSol)$
+\medskip
+
+Formally, a Local Causality Graph (LCG)
+is a digraph where $\cwV \subseteq \Proc\cup \Obj \cup \Sol \cup \sSol$ is the set of vertices,
+with $\sSol=\powerset(\Proc)$ and $\Sol=\Obj\times\powerset(\sSol)$,
 and $\cwE \subseteq \cwV \times \cwV$ is the set of oriented edges
 (\pref{def:lcg}).
+% 
+% These refinements can be summarized with a so-called Local Causality Graph (LCG).
+% Given an initial context $\ctx$ and a local state $\myp\in\Proc$,
+% an LCG $\cwB = (\cwV, \cwE)$
+% is a digraph where $\cwV \subseteq \Proc\cup \Obj \cup \Sol \cup \sSol$ is the set of vertices
+% where $\sSol=\powerset(\Proc)$ and $\Sol=\Obj\times\powerset(\sSol)$
+% and $\cwE \subseteq \cwV \times \cwV$ is the set of oriented edges
+% (\pref{def:lcg}).
 A node in $\cwV\cap\Obj$ represents an objective to refine.
-Such a node is related to nodes in $\cwV\cap\Sol$ which represent
+Such a node is linked to nodes in $\Sol$ which represent
 sets of hitter sets extracted from a
 bounce sequence of the objective
-(that is, one for each bounce sequence in $\BS(P)$): indeed,
+(that is, one node for each bounce sequence in $\BS(P)$); thus,
 given an objective $P$, if $\zeta\in\BS(P)$
-and $\abstr\zeta \DEF \{\PHhitter(\zeta_n) \mid
-n\in\indexes\zeta \}$, then $P$ is related to $\langle P, \abstr\zeta\rangle\in\Sol$
-(\pref{def:lcg}-\ref{lcg-obj-sol}).
+and $\abstr\zeta$ is the set of all hitters of $\zeta$,
+% and $\abstr\zeta \DEF \{\PHhitter(\zeta_n) \mid
+% n\in\indexes\zeta \}$,
+then $P$ is linked to a node $\langle P, \abstr\zeta\rangle\in\Sol$
+(\pref{def:lcg}\nobreakdash-\ref{lcg-obj-sol}).
 For each hitter set $ps\in\abstr\zeta$,
 the node $\langle P,\abstr\zeta\rangle\in\cwV\cap\Sol$ is
-related to the node $ps\in\sSol$
-(\pref{def:lcg}-\ref{lcg-sol-sync}).
-Then, a node $ps\in\cwV\cap\sSol$ is related to each local state $a_i \in ps$ is contains
-(\pref{def:lcg}-\ref{lcg-sync-ls}).
+linked to the node $ps\in\sSol$
+(\pref{def:lcg}\nobreakdash-\ref{lcg-sol-sync}).
+Then, a node $ps\in\cwV\cap\sSol$ is linked to each local state $a_i \in ps$ is contains
+(\pref{def:lcg}\nobreakdash-\ref{lcg-sync-ls}).
 A local state node $a_i\in\cwV\cap\Proc$
-is related to each objective $\obj{a_j}{a_i} \in \Obj$, where
+is linked to each objective $\obj{a_j}{a_i} \in \Obj$, where
 $a_j$ is either in the initial context $\ctx$ or
 is a local state node in the LCG
-(\pref{def:lcg}-\ref{lcg-ls-obj}).
-Finally, given a node $\obj{a_j}{a_i}\in\cwV\cap\Obj$,
-if a local state $a_k\neq a_i$ is in its successors (given by
+(\pref{def:lcg}\nobreakdash-\ref{lcg-ls-obj}).
+Finally, given an objective node $\obj{a_j}{a_i}\in\cwV\cap\Obj$,
+if a local state $a_k\neq a_i$ is in its successors (which is given by
 $\conn_{(\cwBNodes,\cwBEdges)}(\obj{a_j}{a_i})$), then
-$\obj{a_j}{a_i}$ is related to $\obj{a_k}{a_i}$ in the LCG
-(\pref{def:lcg}-\ref{lcg-conn}).
+$\obj{a_j}{a_i}$ is linked to $\obj{a_k}{a_i}$ in the LCG
+(\pref{def:lcg}\nobreakdash-\ref{lcg-conn}).
 
@@
 \end{definition}
+
+\modmf{%
+The definition of an LCG tackles two cases
+where the bounce local state of an objective may be changed.
+First,
+the addition of objectives based on the local states already mentioned anywhere in the LCG,
+as performed in \pref{def:lcg}\nobreakdash-\ref{lcg-ls-obj},
+ensures to take into account the possible changes in the active local states
+made by other objectives.
+We thus try to ensure that a required local state is reachable even when
+starting from another local state of the same automaton that may be active at some point.
+Second, \pref{def:lcg}\nobreakdash-\ref{lcg-conn},
+allows to re-target objectives whose solving changes their target local state.
+This happens if the actions allowing to activate the local processes required to solve
+an objective $P$ change the active process of $\PHsort(P)$.
+In this case, the objective changes to another objective $\PHobj{w}{\bounce{P}}$.
+Linking to all objectives of this kind ensures that all possible disturbances
+are taken into account.
+}
+
+\modmf{%
+The LCG of \pref{def:lcg} contains synchronizing nodes ($\sSol$)
+that allow to express the need for several local states simultaneously
+in order to play a given action.
+This is the main difference regarding~\cite{PMR12-MSCS}
+which tackled with Process Hitting, whose actions are limited to at most one hitter
+and did not require this kind of synchronization.
+Nevertheless, \pref{def:lcg} is equivalent to the definition of LCG
+given in~\cite{FPMR13-CS2Bio},
+although adapted for AANs which notably allowed to simplify its formalism.
+}
 

### 2015-06-02 parts-ccl.tex
mods++

--- 2015-02-17 parts/ccl.tex
@@
 
-Further work can be derived from what have been presented in this paper.
+\modmf{%
+The static analysis method proposed in this paper can theoretically be applied to other
+kinds of formalisms that are not mentioned in the rest of this paper.
+For example, AANs are expressive enough to represent Asynchronous Finite Cellular Automata,
+that is, randomly updated and thus completely asynchronous Finite Cellular Automata.
+Another possibility is to represent multiplayer games, which is possible
+in AANs with 3 classes of priorities, with the addition of several automata
+to tackle the rules of the game, and especially the sequentiality of the turns of each player.
+In both cases, the considered formalism can be represented as an AAN,
+making the application of our analysis method possible in theory.
+However, in practice, the conclusiveness on such “unusual” models
+can be potentially lowered, as the static analysis is not specifically tailored for them.
+Indeed, some particular structures may create loops or non-independent nodes
+in the Local Causality Graph,
+making the whole method inconclusive.
+However, more study and experiments are required to evaluate
+the effectiveness of our method on these kinds of models.
+}
+
+Further work can be directly derived to improve the method presented in this paper.
 The over-approximation on Process Hitting models without priorities proposed in~\cite{PMR12-MSCS}
@@
 applied directly to the whole class of AANs or Process Hitting models with priorities,
-and not only to a sub-class with only one class of priority or particular restrictions;
-such improvement may allow to increase the conclusiveness of the static analysis
+and not only to a sub-class with particular restrictions;
+such improvement may permit to increase the conclusiveness of the static analysis
 while allowing to analyse any model without the need of a translation.
 Finally, in order to take into account quantitative data in transition delays, the overall approximation method could be extended to handle evolutions that are chronometric instead of only chronologic.
+This may require the addition of information such as time delays in the model,
+that would be exploited during the solving.

### 2015-06-02 parts-sa.tex
mods++

@@
 \modmf{%
-The previous subsections permitted to define all the tools needed to build the Local Causality Graph (LCG), such as the on depicted in \pref{fig:sa-livelock}.
+The previous subsections permitted to define all the tools needed to build the Local Causality Graph (LCG).
 This graph is denoted $\cwB$ where $u$ is the local state to be reached
 from the initial context $\ctx$.
+and an example is depicted in \pref{fig:sa-livelock}.
 It will be the basis of our static analysis,
@@
 This LCG is built recursively by considering some required local states (\eg $u$),
-linking them to objectives (\eg, $\PHobj{w}{u}$, if $w \in \ctx$),
-and locally solving these objectives in order to create new required local states
-from other automata.
-}
+linking them to objectives (\eg $\PHobj{w}{u}$, if $w \in \ctx$),
+and locally refining these objectives in order to include new required local states
+from other automata.}
 
@@
 We thus try to ensure that a required local state is reachable even when
-starting from another local state of the same automaton that may be active at some point.
+starting from a local state of the same automaton that is not in the initial context,
+but that may be active at some point of the solving.
 Second, \pref{def:lcg}\nobreakdash-\ref{lcg-conn},
-allows to re-target objectives whose solving changes their target local state.
-This happens if the actions allowing to activate the local processes required to solve
-an objective $P$ change the active process of $\PHsort(P)$.
-In this case, the objective changes to another objective $\PHobj{w}{\bounce{P}}$.
+allows to re-target objectives whose own solving changes their target local state.
+This happens when playing the actions that activate the local states required to solve
+an objective $P$ also changes the active local state of $\PHsort(P)$.
+In this case, the initial objective $P$ is re-targeted to another
+objective $\PHobj{p}{\bounce{P}}$, where $p$ is the new active local state in $\PHsort(P)$.
 Linking to all objectives of this kind ensures that all possible disturbances
@@
 which tackled with Process Hitting, whose actions are limited to at most one hitter
-and did not require this kind of synchronization.
-Nevertheless, \pref{def:lcg} is equivalent to the definition of LCG
+and thus did not require this kind of synchronization.
+However, \pref{def:lcg} is equivalent to the definition of the structure
 given in~\cite{FPMR13-CS2Bio},
-although adapted for AANs which notably allowed to simplify its formalism.
+although it was adapted for AANs which notably allowed to simplify its formalism.
 }
@@
 
-A node $x$ of the LCG in $\sSol$ is \emph{independent} (\pref{def:coherent}) if for each local state
-$a_i\in x$, none of the other local states $b_j\in x$ have in their successors a local state of automaton $a$ different
-than $a_i$.
-This criteria ensures that once a local state in $x$ has been reached, reaching another local state
-in $x$ should not require to change the first local state.
+A node $ps \in \sSol$ of the LCG is \emph{independent} (\pref{def:coherent}) if for each local state
+$a_i\in ps$, none of the other local states $b_j\in ps$ have in their successors
+a local state of automaton $a$ but that is different than $a_i$.
+This criteria ensures that once a local state in $ps$ has been reached, reaching another local state
+in $ps$ should not impact the first.
 
@@
   In a LCG $\cwB = (\Bv, \Be)$,
-  a node $x \in \Bv\cap\sSol$ is \emph{independent} if and only if
-  for each $a_i\in x$,
-  for each $b_j\in x, b_j\neq a_i$,
+  a node $ps \in \Bv\cap\sSol$ is \emph{independent} if and only if
+  for each $a_i\in ps$,
+  for each $b_j\in ps, b_j\neq a_i$,
   $a_k \in\conn_{\cwB}(b_j) \cap \Proc \Rightarrow a_k = a_i$.
@@
 
-The intuition of the under-approximation is the following.
+The intuition of the under-approximation of \pref{th:approxinf} is the following.
 Given a state $s\subseteq\ctx$, we recursively refine the initial objective
 (which is: reaching $\myp$ from the initial state) according to its children.
-As the LCG is acyclic, such a recursion always terminates, and as all the objective nodes have at
+As the LCG is acyclic, by hypothesis, such a recursion always terminates, and as all the objective nodes have at
 least one child, it never gets stuck.
@@
 by construction there exists $\zeta\in\BS(P)$ such that $\abstr\zeta = pps \in \powerset(\sSol)$.
-If $\zeta = \emptyseq$ (for instance in the case when $a_i = a_j$), the recursion stops and we
+If $\zeta = \emptyseq$ (for instance in the case where $a_i = a_j$), the recursion stops and we
 continue to the next stage.
@@
   and the initial state $\PHstate{a_1, b_0, c_0}$
-  that is also represented in this Figure.
+  that is also represented.
   The under-approximation given in \pref{th:approxinf}
@@
 \subsubsection*{Sub-state reachability}
-Given an AAN $\PH = (\PHs, \PHl, \PHh)$ and
-a sub-set of automata local states
-$ps = \{ a_i \in\Proc\mid a\in\PHs, a_i\in\PHl_a\}$,
-the reachability from $s\in\PHl$ of a state $s'\in\PHl$ such that
-$ps\subset s'$ is equivalent to the reachability of the local state
-$\reach_1$ from a state $s \times \{ \reach_0 \}$
-in the AAN
+Given an AAN $\PH = (\PHs, \PHl, \PHh)$,
+an initial state $s \in \PHl$ and
+a sub-set of local states
+$\total \subseteq \Proc$ % = \{ a_i \in\Proc\mid a\in\PHs, a_i\in\PHl_a\}$
+so that $\forall a \in \PHs, \card{\total \cap \PHl_a} \leq 1$,
+the reachability of a state containing all local states of $\total$
+from the initial state $s\in\PHl$
+can be tackled by our method.
+Indeed,
+consider the AAN
 $\PH' = (\PHs', \PHl', \PHh')$ with:
@@
 where $\PHl_\reach = \{ \reach_0, \reach_1 \}$,
-and $\PHh' = \PHh \cup \{ \PHhit{ps}{\reach_0}{\reach_1} \}$.
+and $\PHh' = \PHh \cup \{ \PHhit{\total}{\reach_0}{\reach_1} \}$.
+Obviously,
+the reachability in $\PH$
+of any state $s'\in\PHl$ such that
+$\total \subset s'$ from the initial state $s$
+is equivalent to the reachability in $\PH'$ of the local state
+$\reach_1$ from state $s \times \{ \reach_0 \}$.
 
@@
 \subsubsection*{Sequential reachability}
-Given a sequence of local state to reach (e.g., reach $a_i$, then $b_j$, etc.),
+Given a sequence of local states to reach (\eg reach $a_i$, then $b_j$, etc.),
 one can use the same approach as for sub-state reachability by introducing

### 2015-06-02 response.tex
response++

@@
 
-\title{Response to the reviewers --- First review of “Sufficient Conditions for Reachability in Automata Networks with Priorities”}
+\title{Response to the reviewers on “Sufficient Conditions for Reachability in Automata Networks with Priorities”}
 \author{Maxime Folschette, Loïc Paulevé, Morgan Magnin, Olivier Roux}
@@
 \ilanswer{Indeed, The links between AANs and cellular automata could be studied more thoroughly.
-However, we are not sure that AANs consist in a restriction of cellular automata.}
+The main difference between both however, is that each component in an AAN has particular incoming interactions, while all cells of a cellular automata share the same unique rule.
+On the other hand, we do not tackle “infinite” AANs while cellular automata can be infinite.}
 
@@
 that is, exactly one randomly chosen cell is updated between two states.
-Any AFCA can be represented as an AAN by considering one automaton for each cell containing two local states (corresponding to “active” and “inactive”).
-The rules are modeled by actions that represent the creation/vanishing of a cell given all possible states of its neighborhood.
-This is possible because we can create one action for each configuration of the neighborhood (for the cases where the state of the cell must change).}
+Any AFCA can be represented as an AAN by considering one automaton containing two local states (corresponding to “active” and “inactive”) for each cell.
+The rules are modelled by actions that represent the creation/vanishing of a cell given all possible states of its neighbourhood.
+This is possible because we can create one action for each configuration of the neighbourhood (and no action is required if the state of a cell does not change).}
 
 \ilanswer{The result is a (very repetitive) AAN that encompasses the same dynamics than the AFCA,
-with the exception of unchanged states in AFCA that are:
-\begin{itemize}
-  \item either a stable state, in which case the AAN has no next state,
-  \item or not a stable state, in which case the next state of the AAN will necessarily
-    encompass exactly one change (because we do not allow a transition with no change).
-\end{itemize}}
+with the exception of unchanged states in AFCA (a state that is identical because the updated cell remains unchanged) that are not visible in the dynamics of the AAN.}
+% \begin{itemize}
+%   \item either a stable state, in which case the AAN has no next state,
+%   \item or not a stable state, in which case the next state of the AAN will necessarily
+%     encompass exactly one change (because we do not allow a transition with no change).
+% \end{itemize}}
 
 \ilanswer{Thus, the representation of AFCA in AANs is possible with the considered updating scheme.
-However, the representation has a high complexity, and AANs are not very suited to represent this kind of repetitive patterns.
-Furthermore, it is more likely that this kind of patterns will lead to some inconclusiveness
-when studying its dynamics with the method proposed in our paper,
-especially due to the creation of cycles in the Local Causality Graphs
-(which may represent the fact that a cell has to change its state several times to allow the reaching of a given objective).}
+% However, this representation has a high complexity, and AANs are not very suited to represent this kind of repetitive patterns.
+However, as the AANs are not really suited to this kind of representations,
+it is possible that this kind of patterns will lead to some inconclusiveness
+when studying its dynamics with the method proposed in our paper.
+This would be especially due to the creation of cycles in the Local Causality Graphs,
+because the approximation of the dynamics is not well tailored to analyse “pumping” cases
+(where an automaton has to swap its state several times to allow the reaching of a given objective).}
 
@@
 
-\answer{This question is also very interesting.
-The main problem here seems to be able to represent the given multiplayer game as an AAN ---
+\ilanswer{There are two ways we understand this questions and we are not sure which one the reviewer really meant. Therefore we will try to briefly answer both here.
+\begin{itemize}
+  \item “Is it possible to use game theory to solve a reachability problem?”
+    An AAN may be considered as a game where each automaton is a player with its own set of possible moves (modelled by actions).
+    The semantics would simply require that each player can pass (or play when desired).
+    The reachability problem is then equivalent to finding a winning strategy with the cooperation of all players to reach a given state.
+    Although changing the reachability problem into a winning strategy problem is theoretically possible,
+    \textbf{it misses the point to provide efficient tools} to find this strategy,
+    as this method would rely on the available tools of game theory, with their inherent complexity.
+  \item “Is it possible to represent multiplayer games as AANs?”
+    This question is the most interesting to us, as it would allow to use the static analysis methods on the provided game.
+    The main issue here is the ability to represent the given multiplayer game as an AAN ---
     in which case the analysis tools can be used straightforwardly.
-However, the notion of two players playing alternately (and not randomly) seems quite difficult
-to represent in an AAN, even with the notion of priorities.
-One way would be to introduce dynamic priorities (as opposed to static priorities as presented in the current paper) which would however require some way to translate them back into an AAN with static priorities (or without priorities at all).
+    Such a representation is theoretically possible but unfortunately not really straightforward in AANs.
+    To grasp the idea, it requires additional automata: one “turn” automaton to tell the player's current turn, and as many “update” automata as there are players' moves, in order to synchronize the play of each move with a change of the active local state of the “turn” automaton.
+    The easiest way to model this is with an AAN with 3 classes of priorities,
+    which can be translated into an AAN without priorities with a transformation given in this paper.
+    However, this transformation into an AAN without priorities (besides having a high complexity)
+    potentially creates actions with a lot of hitters.
+    Although complexity of the static analysis method we presented in this paper does not suffer from the many additional “update” automata required (as it is polynomial in the number of automata, and these “update” automata only have 2 local states),
+    the particular form of these “update” automata may create cycles in the Local Causality Graph,
+    and the presence of actions with many hitter is likely to make a lot of $\mathbf{Sync}$ nodes non-independent.
+    Both facts may decrease the conclusiveness of our method, although it is hard to say to which extent with no additional study or experiments.
+%     To grasp the idea, let us consider an Turn AAN that divides the set of actions into $n$ “player” sets (one for each player) and that includes a “turn” variable (telling which player's turn it currently is).
+%     In this Turn AAN, an action can be played only if the “player” set it belongs to matches the value of the “turn” variable.
+%     Furthermore, playing an action automatically changes the “turn” variable to the next player.
+%     This modelling represents a game where players play alternatively (we could also add the possibility to pass, etc.).
+%     In fact, such Turn AAN can be translated into an AAN with 3 classes of priorities,
+%     but at the price of introducing a “turn” automaton modelling the “turn” variable,
+%     and as many “change” automata as there are actions in the Turn AAN,
+%     in order to synchronize the play of each action (changing the active local state of one automaton) and the changes in the “turn” automaton.
+%     Note that each “change” automaton contains two local states, requires two actions of priority 1 and one of priority 2.
+% %     (Note that these “change” automata may not have any meaning biologically speaking.)
+%     One first drawback is that this AAN3 has to be translated into an AAN (without priorities)
+%     despite the numerous high priority actions it will contain that will make this transformation very complex.
+%     On the other hand, the efficiency of the static analysis we proposed in this paper should not suffer from these new numerous automata, as it is polynomial in the number of automata,
+%     and the “change” automata are very small.
+%     Nevertheless, its conclusiveness may be compromised by the high number of hitters in each
+%     action of the final model, which are more likely to create loops or non-independent synchronizations in the Local Causality Graph.
+    \textbf{In a nutshell, although it is theoretically feasible, more analyses are required in order to judge if the conclusiveness is satisfying enough.}
+\end{itemize}
 }
@@
 \answer{In a general fashion, we tied to use formal symbols as much as possible in all definitions.
-However, we tried to change the paging/formulation in order to make the definitions clearer.}
+However, we changed the paging \& formulation in order to make this definition clearer.}
 

### 2015-06-03 response.tex
game theory++

@@
 \begin{itemize}
+  \item We added a paragraph in the conclusion to briefly tackle the questions raised by reviewer \#1;
+  \item We added several paragraphs of informal explanations around Def. 8 after the comments of reviewer \#2.
   \item \todo{Main changes}
@@
     \textbf{it misses the point to provide efficient tools} to find this strategy,
-    as this method would rely on the available tools of game theory, with their inherent complexity.
+    as this method would rely on the available tools of game theory,
+    that is usually based on the state-transition graph, which we want to avoid to compute because of its inherent complexity.
   \item “Is it possible to represent multiplayer games as AANs?”
@@
     Such a representation is theoretically possible but unfortunately not really straightforward in AANs.
-    To grasp the idea, it requires additional automata: one “turn” automaton to tell the player's current turn, and as many “update” automata as there are players' moves, in order to synchronize the play of each move with a change of the active local state of the “turn” automaton.
-    The easiest way to model this is with an AAN with 3 classes of priorities,
-    which can be translated into an AAN without priorities with a transformation given in this paper.
-    However, this transformation into an AAN without priorities (besides having a high complexity)
-    potentially creates actions with a lot of hitters.
-    Although complexity of the static analysis method we presented in this paper does not suffer from the many additional “update” automata required (as it is polynomial in the number of automata, and these “update” automata only have 2 local states),
-    the particular form of these “update” automata may create cycles in the Local Causality Graph,
-    and the presence of actions with many hitter is likely to make a lot of $\mathbf{Sync}$ nodes non-independent.
-    Both facts may decrease the conclusiveness of our method, although it is hard to say to which extent with no additional study or experiments.
+    The multiple hitters of the actions in an AAN are fine enough to permit to represent
+    kinds of “play sets” that delimit which player can move in each (global) state,
+    as defined in \cite{gradel_infinite_2002} for example.
+    It is also possible to model the fact that the players can move alternately
+    with additional automata: one “turn” automaton to tell the player's current turn,
+    and as many “update” automata as there are players' moves,
+    in order to synchronize the play of each move with a change of the active local state of the “turn” automaton.
+    This has to be modelled with an AAN with 3 classes of priorities,
+    which can be translated into an AAN without priorities with the transformation given in this paper.
+    In the end, both solutions contain actions with a lot of hitters.
+    Although complexity of the static analysis method we presented in this paper does not suffer from the many additional automata required (as it is polynomial in the number of automata),
+    the presence of actions with many hitters is likely to make a lot of $\mathbf{Sync}$ nodes non-independent,
+    which may decrease the conclusiveness of our method
+    It is however hard to say to which extent.
+%     To grasp the idea, it requires additional automata: one “turn” automaton to tell the player's current turn, and as many “update” automata as there are players' moves, in order to synchronize the play of each move with a change of the active local state of the “turn” automaton.
+%     The easiest way to model this is with an AAN with 3 classes of priorities,
+%     which can be translated into an AAN without priorities with the transformation given in this paper.
+%     However, this transformation into an AAN without priorities (besides having a high complexity)
+%     potentially creates actions with a lot of hitters.
+%     Although complexity of the static analysis method we presented in this paper does not suffer from the many additional “update” automata required (as it is polynomial in the number of automata, and these “update” automata only have 2 local states),
+%     the particular form of these “update” automata may create cycles in the Local Causality Graph,
+%     and the presence of actions with many hitters is likely to make a lot of $\mathbf{Sync}$ nodes non-independent.
+%     Both facts may decrease the conclusiveness of our method, although it is hard to say to which extent with no additional study or experiments.
+%     
 %     To grasp the idea, let us consider an Turn AAN that divides the set of actions into $n$ “player” sets (one for each player) and that includes a “turn” variable (telling which player's turn it currently is).

### 2015-06-03 parts-ccl.tex
game theory++

@@
 For example, AANs are expressive enough to represent Asynchronous Finite Cellular Automata,
-that is, randomly updated and thus completely asynchronous Finite Cellular Automata.
-Another possibility is to represent multiplayer games, which is possible
-in AANs with 3 classes of priorities, with the addition of several automata
-to tackle the rules of the game, and especially the sequentiality of the turns of each player.
-In both cases, the considered formalism can be represented as an AAN,
+that is, randomly updated and thus completely asynchronous Finite Cellular Automata
+\cite{cornforth_artificial_2003,harvey_time_1997}.
+Another possibility is to represent turn-based multiplayer games,
+such as arena \cite{gradel_infinite_2002}
+where a specific player can move in each state,
+or games in which players move alternately,
+with the use of classes of priorities and special automata to model these rules.
+% in AANs with 3 classes of priorities, with the addition of several automata
+% to tackle the rules of the game, that is, the sequentiality of the turns of each player.
+In each case, the considered formalism can be represented as an AAN,
 making the application of our analysis method possible in theory.
-However, in practice, the conclusiveness on such “unusual” models
-can be potentially lowered, as the static analysis is not specifically tailored for them.
-Indeed, some particular structures may create loops or non-independent nodes
-in the Local Causality Graph,
-making the whole method inconclusive.
+Furthermore, the addition of new automata does not significantly impact its overall complexity.
 However, more study and experiments are required to evaluate
-the effectiveness of our method on these kinds of models.
+the effectiveness of our method on these kinds of models,
+especially regarding its conclusiveness, given their particular form.
+% However, in practice, the conclusiveness on such “unusual” models
+% can be potentially lowered, as the static analysis is not specifically tailored for them.
+% Indeed, some particular structures may create loops or non-independent nodes
+% in the Local Causality Graph,
+% making the whole method inconclusive.
+% Therefore, more study and experiments are required to evaluate
+% the effectiveness of our method on these kinds of models.
 }
 
-Further work can be directly derived to improve the method presented in this paper.
+Further work can also be directly derived to improve the method presented in this paper.
 The over-approximation on Process Hitting models without priorities proposed in~\cite{PMR12-MSCS}

### 2015-06-05 parts-models-ph-php.tex
process -> local state

@@
   a_i \neq a_j \Longrightarrow a_i \wedge a_j \equiv \bot \]
-because two different processes can never be active simultaneously.
+because two different local states can never be active simultaneously.
 

### 2015-06-05 parts-def-ph.tex
proofread + move contexts to appendix

@@
 
-A context (\pref{def:context}) extends the notion of state to a set of possible initial states:
-to each automaton in the model, a context maps a set of local states in this automaton.
-\begin{definition}[Context ($\Ctx$)]
-\label{def:context}
-  A \emph{context} $\ctx$ associates to each automaton in $\PHs$ a non-empty subset of its local states:
-  $\forall a \in \PHs, \PHget{\ctx}{a} \subseteq \PHl_a \wedge \PHget{\ctx}{a} \neq \emptyset$.
-  $\Ctx$ is the set of all contexts.
-\end{definition}
-
-\paragraph{Notations}
-For a given context $\ctx$, we note $a_i \in \ctx$ if and only if $a_i \in \PHget{\ctx}{a}$,
-and for all $ps \in \powerset(\PHproc)$ or $ps \in \PHl$, $ps \subseteq \ctx \Leftrightarrow \forall a_i \in ps, a_i \in \ctx$.
-
 \begin{remark}[Comparison with the Process Hitting]

### 2015-06-05 parts-example.tex
proofread + move contexts to appendix

@@
 \ie if gene $a$ can oscillate, thus leading to the formation of stripes.
-Starting from context $\ctx^1 = \PHstate{f_1, a_0, c_0}$,
+Starting from state $s^1 = \PHstate{f_1, a_0, c_0}$,
 we thus want to check the reachability of $\myp^1 = a_1$;
@@
 
-We first build the local causality graph $\thisB{\myp^1}{\ctx^1}$
-related to the reachability of $\myp^1 = a_1$ from the initial state $\ctx^1$.
+We first build the local causality graph $\thisB{\myp^1}{s^1}$
+related to the reachability of $\myp^1 = a_1$ from the initial state $s^1$.
 This graph is depicted in \pref{fig:metazoan-sa}(left).
@@
 As there exists no other traversal, we thus have in this case:
-$\Delta(\thisB{\myp^1}{\ctx^1}) = \{ \PHfrappes{c_0, f_1}{a_0}{a_1} \}$.
+$\Delta(\thisB{\myp^1}{s^1}) = \{ \PHfrappes{c_0, f_1}{a_0}{a_1} \}$.
 
 We denote in the following:
-$\ctx^2 = \PHstate{f_1, a_0, c_0} \play \PHfrappes{c_0, f_1}{a_0}{a_1} =
+$s^2 = \PHstate{f_1, a_0, c_0} \play \PHfrappes{c_0, f_1}{a_0}{a_1} =
 \PHstate{f_1, a_1, c_0}$
 the state resulting from the play of the scenario concretizing
-$\myp^1$ in $\ctx^1$.
+$\myp^1$ in $s^1$.
 As explained in \pref{ssec:ordered-ua},
@@
 The local causality graph used to check the reachability of $\myp^2$
-from $\ctx^2$ is given in \pref{fig:metazoan-sa}(middle).
+from $s^2$ is given in \pref{fig:metazoan-sa}(middle).
 The same reasoning allows to conclude that this reachability is true, and
 to extract the following set containing only one concretizing scenario:
-$\Delta(\thisB{\myp^2}{\ctx^2}) =
+$\Delta(\thisB{\myp^2}{s^2}) =
 \{ \PHfrappes{a_1, f_1}{c_0}{c_1} \concat \PHfrappes{c_1}{a_1}{a_0} \}$.
@@
 but both output the same scenario, and therefore end up in the same sate
-$\ctx^3 = \PHstate{f_1, a_0, c_1}$.
-Finally, the last local causality graph $\thisB{\myp^3}{\ctx^3}$,
+$s^3 = \PHstate{f_1, a_0, c_1}$.
+Finally, the last local causality graph $\thisB{\myp^3}{s^3}$,
 depicted in \pref{fig:metazoan-sa}(right),
@@
     for the successive reachability of $a_0$, $a_1$ and $a_0$
-    from the initial context
-    $\ctx = \PHstate{f_1, a_0, c_0}$.
+    from the initial state
+    $s = \PHstate{f_1, a_0, c_0}$.
     The (left) graph allows to check the reachability of $a_1$
-    from the initial context $\ctx$.
+    from the initial state $s$.
     The (middle) graph is for the reachability of $a_0$
-    and the context $\PHstate{f_1, a_1, c_0}$.
+    and the state $\PHstate{f_1, a_1, c_0}$.
     The (right) graph is for the last reachability, $a_1$,
-    and the context $\PHstate{f_1, a_0, c_1}$.
+    and the state $\PHstate{f_1, a_0, c_1}$.
   }

### 2015-06-05 parts-sa.tex
proofread + move contexts to appendix

@@
 $\PH = (\PHs; \PHl; \PHa)$,
-an initial state, and a local state of an automaton in $\PHs$, for identifying sufficient conditions
-that ensure the existence of a scenario starting from the initial state and leading to a state
-where the given local state is present.
+an initial state in $\PHl$, and a local state in $\Proc$.
+Its objective it to identify sufficient conditions
+that ensure the existence of a scenario starting from the initial state,
+and leading to a state where the given local state is present.
 
@@
 We denote by $\concr(\w)$ (\pref{def:concr}) the set of scenarios matching with an objective sequence
-$\w$ in the state $s\in\PHs$.
+$\w$ in the state $s\in\PHl$.
 It is essentially all the scenarios for which there exists a mapping from the bounces of each
@@
 This graph is denoted $\cwB$ where $u$ is the local state to be reached
-from the initial context $\ctx$.
-and an example is depicted in \pref{fig:sa-livelock}.
+from the initial state $s$.
 It will be the basis of our static analysis,
@@
 This LCG is built recursively by considering some required local states (\eg $u$),
-linking them to objectives (\eg $\PHobj{w}{u}$, if $w \in \ctx$),
+linking them to objectives (\eg $\PHobj{t}{u}$, if $t \in s$),
 and locally refining these objectives in order to include new required local states
-from other automata.}
+from other automata.
+An example of LCG is depicted in \pref{fig:sa-livelock}.
+}
 
@@
 one can iteratively refine a given objective into (possibly several) objective
-sequences following its bounce sequences.
+sequences extracted from its bounce sequences.
 Indeed, the refinement of an objective $P$ with $\zeta\in\BS(P)$
@@
 % These refinements can be summarized with a so-called Local Causality Graph (LCG).
-% Given an initial context $\ctx$ and a local state $\myp\in\Proc$,
+% Given an initial context $s$ and a local state $\myp\in\Proc$,
 % an LCG $\cwB = (\cwV, \cwE)$
@@
 is linked to each objective $\obj{a_j}{a_i} \in \Obj$, where
-$a_j$ is either in the initial context $\ctx$ or
+$a_j$ is either in the initial state $s$ or
 is a local state node in the LCG
@@
 \label{def:lcg}
-Given a context $\ctx$ and a local state $\myp\in \Proc$,
+Given a state $s \in \PHl$ and a local state $\myp\in \Proc$,
 the Local Causality Graph (LCG) for reachability under-approximation
-$\cwB \DEF (\Bv, \Be)$
+$\cwB \DEF (\Bv, \Be)$,
 with
@@
 $a_i\in\cwBNodes\cap\Proc \Leftrightarrow \{ (a_i,\obj{a_j}{a_i}) \mid
-a_j \neq \myp \wedge (a_j\in\ctx \vee a_j\in\cwBNodes\cap\Proc)
+a_j \neq \myp \wedge (a_j\in s \vee a_j\in\cwBNodes\cap\Proc)
 \}\subseteq\cwBEdges$
@@
 The definition of an LCG tackles two cases
-where the bounce local state of an objective may be changed.
+where the target of an objective may be changed.
 First,
@@
 We thus try to ensure that a required local state is reachable even when
-starting from a local state of the same automaton that is not in the initial context,
+starting from a local state of the same automaton that is not in the initial state,
 but that may be active at some point of the solving.
 Second, \pref{def:lcg}\nobreakdash-\ref{lcg-conn},
-allows to re-target objectives whose own solving changes their target local state.
+allows to “re-target” objectives whose own solving changes their target.
 This happens when playing the actions that activate the local states required to solve
-an objective $P$ also changes the active local state of $\PHsort(P)$.
+an objective $P$ also changes the active local state of automaton $\PHsort(P)$.
 In this case, the initial objective $P$ is re-targeted to another
@@
 \modmf{%
-The LCG of \pref{def:lcg} contains synchronizing nodes ($\sSol$)
+Finally, we note that
+the LCG of \pref{def:lcg} contains synchronizing nodes ($\sSol$)
 that allow to express the need for several local states simultaneously
@@
 
-Given a context $\ctx$ and a local state $\myp\in\Proc$, the LCG $\cwB$ contains a set of objectives
+Given a state $s \in \PHl$ and a local state $\myp\in\Proc$, the LCG $\cwB$ contains a set of objectives
 that can be used to build a concrete scenario reaching $\myp$.
@@
 child, and all its nodes in $\sSol$ satisfy a
-particular criteria, so-called independence, then from any state
-delimited by the context $\ctx$, there exists a scenario that reaches $\myp$
-(\pref{th:approxinf}).
+particular criteria, so-called independence,
+then there exists a scenario that reaches $\myp$ from state $s$ (\pref{th:approxinf}).
 
@@
 The intuition of the under-approximation of \pref{th:approxinf} is the following.
-Given a state $s\subseteq\ctx$, we recursively refine the initial objective
+Given the initial state $s$, we recursively refine the initial objective
 (which is: reaching $\myp$ from the initial state) according to its children.
@@
 We can thus apply this action, modifying the state of $a$ to $a_j$ and continue to the next stage.
-In the end, this recursive procedures builds a scenario from $s\subseteq\ctx$ to a state containing $\myp$.
+In the end, this recursive procedures builds a scenario from $s$ to a state containing $\myp$.
 
@@
   Given an AAN $(\PHs; \PHl; \PHa)$,
-  a context $\ctx$ and an objective sequence $\w$,
+  a state $s$ and local state $\myp$,
   if the LCG $\cwB$ contains no cycle,
@@
   and all nodes in $\sSol$ are independent,
-  then for any state $s\in\PHl$ such that $s\subseteq\ctx$,
-  there exists a scenario $\delta\in\Sce$ with $\myp\in s\play\delta$.
+  then there exists a scenario $\delta\in\Sce$ such as $\myp\in s\play\delta$.
 \end{theorem}
@@
 one can consider only a sub-set of bounce sequences
-(and in particular: a single bounce sequence) for each objective.
+(and in particular: a unique bounce sequence) for each objective.
 However, such an approach requires to enumerate all possible combinations of bounce sequences
@@
     for the reachability of $\myp = c_1$
-    from the initial context $\ctx = \PHstate{a_1, b_0, c_0}$.
+    from the initial state $s = \PHstate{a_1, b_0, c_0}$.
     Elements in $\Proc$ are represented by rectangular nodes,
@@
 from a given initial state $s_0 \in \PHl$,
-provided that \pref{th:approxinf} answered positively
-for a context $\ctx \in \Ctx$ so that $s_0 \subset \ctx$.
+provided that \pref{th:approxinf} answered positively on this couple of inputs.
 The algorithm proposed in what follows relies on a traversal of the Local Causality Graph
-$\cwB$ that has been used for this conclusion.
+$\cwBz$ that has been used for this conclusion.
 The correctness of this extraction can be demonstrated
@@
 The execution of such a traversal outputs a scenario from $s_0$.
-In the following, we denote by $\Delta(\cwB)$ the set of all scenarios extracted from the
-local causality graph $\cwB$.
+In the following, we denote by $\Delta(\cwBz)$ the set of all scenarios extracted from the
+local causality graph $\cwBz$.
 Indeed, several scenarios may exist for a same graph,

### 2015-06-05 parts-suppl-sa.tex
proofread + move contexts to appendix

@@
 
-In the following, we denote:
+We introduce for this proof the notion of context (\pref{def:context}),
+which extends the notion of state to a set of possible initial states:
+to each automaton in the model, a context maps a set of local states in this automaton.
+\begin{definition}[Context]
+\label{def:context}
+  A \emph{context} $\varsigma$ associates to each automaton in $\PHs$ a non-empty subset of its local states:
+  $\forall a \in \PHs, \varsigma(a) \subseteq \PHl_a \wedge \varsigma(a) \neq \emptyset$.
+%  $\Ctx$ is the set of all contexts.
+\end{definition}
+
+For a given context $\varsigma$,
+%we note $a_i \in \varsigma$ if and only if $a_i \in \varsigma(a)$,
+and for all state $s \in \PHl$,
+we note $s \subseteq \varsigma$ if and only if $\forall a_i \in s, a_i \in \varsigma(a)$.
+
+In the following, we also denote:
 $\Bee{X}{Y} = \Be \cap (X \times Y)$, with $X, Y$
@@
 Given the LCG $\cwB=(\cwV,\cwE)$,
-we note $max\ctx = \{a\mapsto \cwV\cap\PHl_a \mid a\in\PHs\}$ the context supported by $\cwB$.
+we note $\varsigma = \{a\mapsto \cwV\cap\PHl_a \mid a\in\PHs\}$ the context supported by $\cwB$.
 
 Let $ps \in \Bv \cap \sSol$ be a set of hitters
+that is a node in the LCG,
 and suppose all of its successors are concretizable.
@@
 \begin{itemize}
-  \item It is straightforward for $\delta_0 = \varepsilon$.
+  \item It is straightforward that $\varepsilon$ is a valid value for $\delta_0$.
   \item Suppose such $\delta_n$ exists and let $q = \PHget{(s \PHplay \delta_n)}{\PHsort(p_{n+1})}$.
@@
 As there is no cycle in $\cwB$, we show by induction in the following that
-$\forall s\in \PHl, s\subseteq max\ctx, \forall P \in \Bv \cap \Obj,
+$\forall s\in \PHl$ so that $s\subseteq \varsigma$ and $\forall P \in \Bv \cap \Obj,
 \PHtarget(P) \in s \Longrightarrow \exists \delta \in \mconcr_s(P)$.
@@
       \end{itemize}
-      Thus, $\delta_{|\zeta|} \in \mconcr_s(P)$. % and $\ceil(\delta) \subseteq max\ctx$.
+      Thus, $\delta_{|\zeta|} \in \mconcr_s(P)$. % and $\ceil(\delta) \subseteq maxs$.
 \end{itemize}

### 2015-06-10 response.tex
simplify additions + response

--- 2015-05-29 response.tex
@@
 We wish to thank the reviewers for their comments.
-Please find below a summary of the main changes brought to the paper, and a detailed response to all comments.
+Please find below a brief summary of the main changes brought to the paper.
+A detailed response to all comments follows.
 
 \begin{itemize}
-  \item \todo{Main changes}
+%   \item We have added a paragraph in the conclusion to briefly tackle the questions raised by reviewer~\#1;
+  \item We have added several paragraphs of informal explanations around Def.~7 (previously Def.~8) after the comments of reviewer~\#2.
+  \item The notion of context has been removed from the body of the paper,
+    without weakening our results.
 \end{itemize}
@@
 
-\ilanswer{Indeed, The links between AANs and cellular automata could be studied more thoroughly.
-However, we are not sure that AANs consist in a restriction of cellular automata.}
-
-\ilanswer{We show in the following that an AAN can represent an Asynchronous Finite Cellular Automata (AFCA).
-An AFCA is a finite set of cells that share a same update rule (we consider no border effects).
-We consider that the transitions between each global states are asynchronous in the meaning of the “Random Independent” scheme given in \cite{cornforth_artificial_2003} and \cite{harvey_time_1997},
-that is, exactly one randomly chosen cell is updated between two states.
-Any AFCA can be represented as an AAN by considering one automaton for each cell containing two local states (corresponding to “active” and “inactive”).
-The rules are modeled by actions that represent the creation/vanishing of a cell given all possible states of its neighborhood.
-This is possible because we can create one action for each configuration of the neighborhood (for the cases where the state of the cell must change).}
-
-\ilanswer{The result is a (very repetitive) AAN that encompasses the same dynamics than the AFCA,
-with the exception of unchanged states in AFCA that are:
-\begin{itemize}
-  \item either a stable state, in which case the AAN has no next state,
-  \item or not a stable state, in which case the next state of the AAN will necessarily
-    encompass exactly one change (because we do not allow a transition with no change).
-\end{itemize}}
-
-\ilanswer{Thus, the representation of AFCA in AANs is possible with the considered updating scheme.
-However, the representation has a high complexity, and AANs are not very suited to represent this kind of repetitive patterns.
-Furthermore, it is more likely that this kind of patterns will lead to some inconclusiveness
-when studying its dynamics with the method proposed in our paper,
-especially due to the creation of cycles in the Local Causality Graphs
-(which may represent the fact that a cell has to change its state several times to allow the reaching of a given objective).}
-
-\answer{In conclusion,
-more experiments may be required in order to acknowledge how our method fits into the modeling and analysis of cellular automata,
-and some enrichments of the static analysis may be needed to obtain satisfying results.
-}
-
-\todo{Déplacer une partie dans le papier}
+% \ilanswer{Indeed, The links between AANs and cellular automata could be studied more thoroughly.
+% The main difference between both however, is that each component in an AAN has particular incoming interactions, while all cells of a cellular automata share the same unique rule.
+% On the other hand, we do not tackle “infinite” AANs while cellular automata can be infinite.}
+% 
+% \ilanswer{We show in the following that an AAN can represent what we will call Asynchronous Finite Cellular Automata (AFCA) in the following.
+% An AFCA is a finite set of cells that share a same update rule (except on the border).
+% We consider that the transitions between each global states are asynchronous in the meaning of the “Random Independent” scheme given in \cite{cornforth_artificial_2003} and \cite{harvey_time_1997},
+% that is, exactly one randomly chosen cell is updated between two states.
+% Any AFCA can be represented as an AAN by considering one automaton containing two local states (corresponding to “active” and “inactive”) for each cell.
+% The rules are modelled by actions that represent the creation/vanishing of a cell given all possible states of its neighbourhood.
+% This is possible because we can create one action for each configuration of the neighbourhood (and no action is required if the state of a cell does not change).}
+% 
+% \ilanswer{The result is a (very repetitive) AAN that encompasses the same dynamics than the AFCA,
+% at the exception of unchanged states in AFCA.
+% %that are not visible in the dynamics of the AAN
+% Indeed, an unchanged state is a that that is identical to the previous one because the cell selected for update remains unchanged.
+% This cannot be represented in an AAN because it is mandatory that an action is played between two states.}
+% % \begin{itemize}
+% %   \item either a stable state, in which case the AAN has no next state,
+% %   \item or not a stable state, in which case the next state of the AAN will necessarily
+% %     encompass exactly one change (because we do not allow a transition with no change).
+% % \end{itemize}}
+% 
+% \ilanswer{Thus, the representation of AFCA in AANs is possible with the considered updating scheme and by ignoring unchanged states.
+% % However, this representation has a high complexity, and AANs are not very suited to represent this kind of repetitive patterns.
+% However, as the AANs are not really suited to this kind of representations,
+% it is possible that this kind of patterns will lead to some inconclusiveness
+% when studying its dynamics with the method proposed in our paper.
+% This would be especially due to the creation of cycles in the Local Causality Graphs,
+% because the approximation of the dynamics is not well tailored to analyse “pumping” cases
+% (where an automaton has to swap its state several times to allow the reaching of a given objective).}
+% 
+% \answer{In conclusion,
+% more experiments may be required in order to acknowledge how our method fits into the modeling and analysis of cellular automata,
+% and some enrichments of the static analysis may be needed to obtain satisfying results.
+% }
 
@@
 
-\answer{This question is also very interesting.
-The main problem here seems to be able to represent the given multiplayer game as an AAN ---
-in which case the analysis tools can be used straightforwardly.
-However, the notion of two players playing alternately (and not randomly) seems quite difficult
-to represent in an AAN, even with the notion of priorities.
-One way would be to introduce dynamic priorities (as opposed to static priorities as presented in the current paper) which would however require some way to translate them back into an AAN with static priorities (or without priorities at all).
+% \ilanswer{There are two ways we understand this questions and we are not sure which one the reviewer really meant. Therefore we will try to briefly answer both here.
+% \begin{itemize}
+%   \item “Is it possible to use game theory to solve a reachability problem?”
+%     An AAN may be considered as a game where each automaton is a player with its own set of possible moves (modelled by actions).
+%     The semantics would simply require that each player can pass (or play when desired).
+%     The reachability problem is then equivalent to finding a winning strategy with the cooperation of all players to reach a given state.
+%     Although changing the reachability problem into a winning strategy problem is theoretically possible,
+%     it misses the point to provide efficient tools to find this strategy.
+%     Indeed, this method would rely on the available tools of game theory,
+%     that are usually based on the state-transition graph, which we want to avoid to compute because of its inherent complexity.
+%   \item “Is it possible to represent multiplayer games as AANs?”
+%     This question is the most interesting to us, as it would allow to use the static analysis methods on the provided game.
+%     The main issue here is the ability to represent the given multiplayer game as an AAN ---
+%     in which case the analysis tools can be used straightforwardly.
+%     Such a representation is theoretically possible but unfortunately not really straightforward in AANs.
+%     The multiple hitters of the actions in an AAN are fine enough to permit to represent
+%     kinds of “play sets” that delimit which player can move in each (global) state,
+%     as defined in \cite{gradel_infinite_2002} for example.
+%     It is also possible to model the fact that the players can move alternately
+%     with additional automata: one “turn” automaton to tell the player's current turn,
+%     and as many “update” automata as there are players' moves,
+%     in order to synchronize the play of each move with a change of the active local state of the “turn” automaton.
+%     This has to be modelled with an AAN with 3 classes of priorities,
+%     which can be translated into an AAN without priorities with the transformation given in this paper.
+%     In the end, both solutions contain actions with a lot of hitters.
+%     Although complexity of the static analysis method we presented in this paper does not suffer from the many additional automata required by the second solution (as it is polynomial in the number of automata),
+%     the presence of actions with many hitters is likely to make a lot of $\mathbf{Sync}$ nodes non-independent,
+%     which may decrease the conclusiveness of our method.
+%     It is however hard to say to which extent.
+% %     To grasp the idea, it requires additional automata: one “turn” automaton to tell the player's current turn, and as many “update” automata as there are players' moves, in order to synchronize the play of each move with a change of the active local state of the “turn” automaton.
+% %     The easiest way to model this is with an AAN with 3 classes of priorities,
+% %     which can be translated into an AAN without priorities with the transformation given in this paper.
+% %     However, this transformation into an AAN without priorities (besides having a high complexity)
+% %     potentially creates actions with a lot of hitters.
+% %     Although complexity of the static analysis method we presented in this paper does not suffer from the many additional “update” automata required (as it is polynomial in the number of automata, and these “update” automata only have 2 local states),
+% %     the particular form of these “update” automata may create cycles in the Local Causality Graph,
+% %     and the presence of actions with many hitters is likely to make a lot of $\mathbf{Sync}$ nodes non-independent.
+% %     Both facts may decrease the conclusiveness of our method, although it is hard to say to which extent with no additional study or experiments.
+% %     
+% %     To grasp the idea, let us consider an Turn AAN that divides the set of actions into $n$ “player” sets (one for each player) and that includes a “turn” variable (telling which player's turn it currently is).
+% %     In this Turn AAN, an action can be played only if the “player” set it belongs to matches the value of the “turn” variable.
+% %     Furthermore, playing an action automatically changes the “turn” variable to the next player.
+% %     This modelling represents a game where players play alternatively (we could also add the possibility to pass, etc.).
+% %     In fact, such Turn AAN can be translated into an AAN with 3 classes of priorities,
+% %     but at the price of introducing a “turn” automaton modelling the “turn” variable,
+% %     and as many “change” automata as there are actions in the Turn AAN,
+% %     in order to synchronize the play of each action (changing the active local state of one automaton) and the changes in the “turn” automaton.
+% %     Note that each “change” automaton contains two local states, requires two actions of priority 1 and one of priority 2.
+% % %     (Note that these “change” automata may not have any meaning biologically speaking.)
+% %     One first drawback is that this AAN3 has to be translated into an AAN (without priorities)
+% %     despite the numerous high priority actions it will contain that will make this transformation very complex.
+% %     On the other hand, the efficiency of the static analysis we proposed in this paper should not suffer from these new numerous automata, as it is polynomial in the number of automata,
+% %     and the “change” automata are very small.
+% %     Nevertheless, its conclusiveness may be compromised by the high number of hitters in each
+% %     action of the final model, which are more likely to create loops or non-independent synchronizations in the Local Causality Graph.
+%     In a nutshell, although it is theoretically feasible, more analyses are required in order to judge if the conclusiveness is satisfying enough.
+% \end{itemize}
+% }
+
+\ilanswer{
+1) Contrary to cellular automata, the neighbourhoods in AANs are not regular
+(each component has its own regulation rules).
+One can thus straightforwardly encode finite cellular automata
+with an asynchronous semantics into AANs.
 }
 
-\todo{Voir formalismes courants en théorie des jeux}
+\ilanswer{
+2) Our analysis focuses on finding sufficient conditions for achieving a
+reachability goal, but does not account for an “opposing player” which would
+try to prevent the concerned reachability to occur.
+Therefore our analysis is not directly applicable in such a game theory setting.
+However, it can be used to solve cooperation games
+(where all players cooperate in reaching the goal).
+}
 
-\todo{Déplacer une partie dans le papier ?}
+\answer{
+We have added a word about these subjects in the conclusion of the article.
+}
 
 Minor coments to the authors:
+
+\answer{Except the comment below, we have taken all minor comments into account.}
 
@@
 \answer{We willingly chose the order of the authors' names related to the individual participation of each one.}
-
-\answer{We have taken the other minor comments into account.}
 
@@
 
-\todo{Rajouter des explications infromelles}
-
-\todo{Simplifier les définitions formelles ?}
+\answer{Our aim was to achieve a double understanding from the reader,
+by presenting our definitions and results both in an informal and intuitive manner,
+so that readers can easily understand the background idea,
+and in a formal way in order to avoid any ambiguities.
+Therefore, we prefer not to make the definitions and theorems less formal.
+However, we added several paragraphs of explanations around the definition of the Local Causality Graph (Def. 7; previously Def. 8) to ease its understanding.
+Furthermore, we have removed the notion of context from the body of the paper,
+which allows a bit of simplification
+(this does not weaken the results as several tests can replace the use of a context).
+}
 
@@
 
-page 1, line 49 ---
-I would reformulate the phrase "with [4,5]" somehow in different way.
-
-page 1, line 52 ---
-Replace "behaviours" in the phrase "their usual behaviours" with "behaviour".
-
-page 2, line 21 ---
-Remove the second verb "are" in the phrase "This is modelled by actions are of the form".
-
-page 2, line 27, "avoid to build" ---
-Reformulate as "avoid building".
-The same comment applies to many other places within the paper (for instance, page 5, line 51, page 3, line 43).
-
-page 7, line 29 ---
-I would replace "Subsect." with "Subsection" throughout the paper.
+\answer{Except the comment below, we have taken all comments to authors into account.}
 
@@
 
-\answer{In a general fashion, we tied to use formal symbols as much as possible in all definitions.
-However, we tried to change the paging/formulation in order to make the definitions clearer.}
+\answer{In a general fashion, we tried to use formal symbols as much as possible in all definitions.
+However, we changed the paging and formulation in order to make this definition more readable.}
 
-page 8, Definition 6 ---
-The comment "($\gamma_s: OSeq \to$ ...)" in the parentheses after "Definition 6" complicates the perception of the material. This also applies to other definitions.
-
-page 8, line 52 ---
-To which definition does the phrase "in the previous definition" refer to?
-
-page 8, Lemma 1 ---
-I recommend changing the formulation of the lemma so that it contains at least some words.
-The comment right before the formulation of the lemma states essentially the same thing as the lemma, without any intuition.
-
-page 9, line 53 ---
-Replace "would consists" either with "would consist" or with "consists".
-
-page 10, comment before Definition 8 ---
-First of all, I would give a shorter intuition before Definition 8 and only then this delaited explanation of the definition.
-The definition itself is very difficult to follow and the explanation is written in a really succinct way, that does not make it easier to get.
-Perhaps the authors could state how this definition is different from a similar definition in the cited work [16].
-
-page 10, line 53 ---
-In the phrase "we prove that if ..., if ..., and if ..., then" I would only leave the first "if" and remove the two others.
-
-page 11, line 33 ---
-Remove "we know" in the sentence "Then, we know (by induction)".
-
-page 12, lines 10-12 ---
-In the sentence "in order to reduce the number ..., and potentially removing cycles" replace "removing" with "remove".
-
-page 12, line 14 ---
-Something seems to be wrong with the phrase "would imply to enumerate".
-
-page 12, lind 18 ---
-In the sentence "from the initial state ... depicted" I would replace "depicted" to "illustrated" and actually put this word to another place within the sentence.
-
-page 12, line 20 ---
-I think the phrase "but does not conclude regarding the reachability of $c_1$" could be rewritten in a simpler way.
-
-page 15, line 12 ---
-Put a comma before "where" in the phrase "having n+1 local states where n".
-This also concerns some other places of the paper.
-
-page 15, line 16 ---
-Remove the second period in "etc.).".
-
-page 15, line 26 ---
-I would consider using the term "transformation" instead of "translation".
-
-page 15, paragraph before Definition 10 ---
-This is a comment both to Definition 10 and Definition 11. I would try to "separate" them.
-
-page 16, line 56 ---
-Consider replacing "in the following" with "in what follows".
-This comment applies to several other places in the paper.
-
-page 19, Section 5 ---
-The phrases "this section aims at giving application examples", "we give in this section a detailed example", "we consider in the following a model of" repeat the same idea within a half of the page.
-I would try to restructure the introductory text to Section 5 and its Subsection 5.1.
-
-page 20, line 25 ---
-Remove the second article in "the the".
-
-page 20, line 46 ---
-The sentence starting with "This consists in using Theorem 1 ..." is written in a very sophisticated way.
-
-page 29, reference [18] ---
-The year and the pages of the publication are missing.
-
-\bibliography{biblio}
+%\bibliography{biblio}
 

### 2015-06-10 parts-ccl.tex
process -> local state
simplify additions + response

--- 2015-02-17 parts/ccl.tex
@@
 was proposed in~\cite{PMR10-TCSB}.
+\modmf{%
+AANs can also be used to represent sub-sets of
+cellular automata \cite{cornforth_artificial_2003}
+or multiplayer games \cite{gradel_infinite_2002},
+although more experiments would be required to evaluate
+the conclusiveness of our static analysis method on models of such particular forms.
+}
 
-Further work can be derived from what have been presented in this paper.
+% \modmf{%
+% The static analysis method proposed in this paper can theoretically be applied to other
+% kinds of formalisms that are not mentioned in the rest of this paper.
+% For example, AANs are expressive enough to represent Asynchronous Finite Cellular Automata,
+% that is, randomly updated and thus completely asynchronous Finite Cellular Automata
+% \cite{cornforth_artificial_2003,harvey_time_1997}.
+% Another possibility is to represent turn-based multiplayer games,
+% such as arena \cite{gradel_infinite_2002}
+% where a specific player can move in each state,
+% or games in which players move alternately,
+% with the use of classes of priorities and special automata to model these rules.
+% % in AANs with 3 classes of priorities, with the addition of several automata
+% % to tackle the rules of the game, that is, the sequentiality of the turns of each player.
+% In each case, the considered formalism can be represented as an AAN,
+% making the application of our analysis method possible in theory.
+% Furthermore, the addition of new automata does not significantly impact its overall complexity.
+% However, more study and experiments are required to evaluate
+% the effectiveness of our method on these kinds of models,
+% especially regarding its conclusiveness, given their particular form.
+% % However, in practice, the conclusiveness on such “unusual” models
+% % can be potentially lowered, as the static analysis is not specifically tailored for them.
+% % Indeed, some particular structures may create loops or non-independent nodes
+% % in the Local Causality Graph,
+% % making the whole method inconclusive.
+% % Therefore, more study and experiments are required to evaluate
+% % the effectiveness of our method on these kinds of models.
+% }
+
+Further work can also be directly derived to improve the method presented in this paper.
 The over-approximation on Process Hitting models without priorities proposed in~\cite{PMR12-MSCS}
@@
 but may be refined given the particular for of AANs proposed in this paper.
-A specific search of key processes or cut sets \cite{PAK13-CAV} may especially be derived.
+A specific search of key local states or cut sets \cite{PAK13-CAV} may especially be derived.
 %but turns out to be too wide even in some obvious cases that are consequently not conclusive.

### 2015-06-11 response.tex
minor modifications bis

@@
 
-% \newcounter{pointno}
-% \setcounter{pointno}{0}
-% \def\thepoint{\arabic{pointno}}
-% \newcommand{\ptno}[1]{\textcolor{blue}{\refstepcounter{pointno} \thepoint. \#1}}
-% \newcommand{\question}[1]{\bigskip{\it\ptno{\#1}}}
+\newcounter{pointno}
+\setcounter{pointno}{0}
+\def\thepoint{\arabic{pointno}}
+\newcommand{\ptno}[1]{\textcolor{blue}{\refstepcounter{pointno} \thepoint. \#1}}
+\newcommand{\question}[1]{\bigskip{\it\ptno{\#1}}}
 % \def\answer{}
@@
 
-\section*{Summary of the main changes}
-
 We wish to thank the reviewers for their comments.
-Please find below a brief summary of the main changes brought to the paper.
-A detailed response to all comments follows.
-
-\begin{itemize}
-%   \item We have added a paragraph in the conclusion to briefly tackle the questions raised by reviewer~\#1;
-  \item We have added several paragraphs of informal explanations around Def.~7 (previously Def.~8) after the comments of reviewer~\#2.
-  \item The notion of context has been removed from the body of the paper,
-    without weakening our results.
-\end{itemize}
+Following reviewers comments,
+with this revision
+we added
+  several paragraphs of informal explanations to give more intuition 
+  for technical definitions (in particular in section 3);
+  and simplified a few notations.
 
@@
 
-Reviewer \#1: In this article the  Asynchronous Automata Networks (AANs) are studied.
-An AAN is an Automata Network with synchronised transitions between automata, where each transition changes the local state of exactly one automaton, but the number of synchronazing state sis not restricted.
-The AAN with priorities are also studied.
+1) somehow the system of AANs seems such that it has conection or roots or generalization by cellural automata.
+Obviously, CA are a more general model and AANs are a restriction, but it could be interesting to see whether can you generalize or simulate in simple manners your system with CA?
 
-Authors build a method of efficient under-approximation for the problem of state reachability.
-The computational cost is lower than the cost of usual model checker methods.
-Also, a reduction from AANs with priorities to the AANs without priorities is given.
-
-Clearly, the paper is based on real applications of the system studied.
-It seems that the method and the theory are build for and from some specific applications with a interesting idea.
-Therefore, from the purely automata theoretical point of view,  the methods and results are not very strong nor interesting as themself.
-On the other hand, the method is used in two example applications in the end of the paper to support the fact that the model and the method work well in practise.
-This is probably the strongest part of the paper.
-
-General: 1) somehow the system of AANs seems such that it has conection or roots or generalization by cellural automata.
-Obviously, CA are a more general model and AANs are a restriction, but it could be interesting to see whether can you generalize or simulate in simple manners your system with CA?
+\ilanswer{
+Contrary to cellular automata, the neighbourhoods in AANs are not regular
+(each component has its own regulation rules).
+One can thus straightforwardly encode finite cellular automata
+with an asynchronous semantics into AANs.
+}
 
@@
 
+\medskip
+
+\noindent
 2) Just a note: As I see it, the AANs is an interactive model of computation, and that is interesting.
@@
 \ilanswer{
-1) Contrary to cellular automata, the neighbourhoods in AANs are not regular
-(each component has its own regulation rules).
-One can thus straightforwardly encode finite cellular automata
-with an asynchronous semantics into AANs.
-}
-
-\ilanswer{
-2) Our analysis focuses on finding sufficient conditions for achieving a
+Our analysis focuses on finding sufficient conditions for achieving a
 reachability goal, but does not account for an “opposing player” which would
@@
 
+\noindent
 Minor coments to the authors:
@@
 
+\noindent
 page 1, authors: names are not in alphabetical order probably for a good reason, but it strikes my mathematician eye badly.
 
-\answer{We willingly chose the order of the authors' names related to the individual participation of each one.}
+\answer{We willingly chose the order of the authors' names related to the individual participation
+of each one (following the common practice in computational systems biology community).}
 
@@
 \subsection*{Reviewer \#2}
-
-Reviewer \#2: SUMMARY OF THE RESULTS
-
-In this paper the authors introduce so-called asynchronous automata networks, which are automata networks with transitions synchronized between the automata in such a way that each transition changes the local state of exactly one automaton.
-There is also a generalization of asynchronous automata networks, called asynchronous automata networks with classes of priorities.
-This model is shown to be equivalent to the named networks without priorities.
-
-The authors have developed a method of performing reachability analysis and a way of getting a valid execution path if the reachability question has a positive answer.
-The method of performing reachability analysis is based upon abstract interpretation, and the complexity of such an analysis is polynomial in the total number of local states and exponential in the number of local states within a single automaton.
-
-The applicability of the method has been demonstrated by the authors by considering two large-scale biological models.
 
@@
 Furthermore, we have removed the notion of context from the body of the paper,
-which allows a bit of simplification
-(this does not weaken the results as several tests can replace the use of a context).
+which allows some notation simplification without weakening the presented results.
 }
 
+\noindent
 COMMENTS TO AUTHORS
@@
 
+\noindent
 page 7, Definition 4, line 55, in the sentence "The set of all objectives is called ..." ---

### 2015-06-11 parts-sa.tex
minor change
minor modifications bis

@@
 \modmf{%
-The previous subsections permitted to define all the tools needed to build the Local Causality Graph (LCG).
+The previous subsections \modLP{introduced the necessary definitions to build the
+so-called} Local Causality Graph (LCG).
 This graph is denoted $\cwB$ where $u$ is the local state to be reached
@@
 in order to play a given action.
-This is the main difference regarding~\cite{PMR12-MSCS}
+This is the main difference regarding~\cite{PMR12-MSCS,FPMR13-CS2Bio}
 which tackled with Process Hitting, whose actions are limited to at most one hitter
 and thus did not require this kind of synchronization.
-However, \pref{def:lcg} is equivalent to the definition of the structure
-given in~\cite{FPMR13-CS2Bio},
-although it was adapted for AANs which notably allowed to simplify its formalism.
 }
+%However, \pref{def:lcg} is equivalent to the definition of the structure
+%given in~\cite{FPMR13-CS2Bio},
+%although it was adapted for AANs which notably allowed to simplify its formalism.
 

### 2015-06-18 parts-ccl.tex
remove mod commands

--- 2015-06-02 parts-ccl.tex
@@
 was proposed in~\cite{PMR10-TCSB}.
+AANs can also be used to represent sub-sets of
+cellular automata \cite{cornforth_artificial_2003}
+or multiplayer games \cite{gradel_infinite_2002},
+although more experiments would be required to evaluate
+the conclusiveness of our static analysis method on models of such particular forms.
 
-\modmf{%
-The static analysis method proposed in this paper can theoretically be applied to other
-kinds of formalisms that are not mentioned in the rest of this paper.
-For example, AANs are expressive enough to represent Asynchronous Finite Cellular Automata,
-that is, randomly updated and thus completely asynchronous Finite Cellular Automata.
-Another possibility is to represent multiplayer games, which is possible
-in AANs with 3 classes of priorities, with the addition of several automata
-to tackle the rules of the game, and especially the sequentiality of the turns of each player.
-In both cases, the considered formalism can be represented as an AAN,
-making the application of our analysis method possible in theory.
-However, in practice, the conclusiveness on such “unusual” models
-can be potentially lowered, as the static analysis is not specifically tailored for them.
-Indeed, some particular structures may create loops or non-independent nodes
-in the Local Causality Graph,
-making the whole method inconclusive.
-However, more study and experiments are required to evaluate
-the effectiveness of our method on these kinds of models.
-}
-
-Further work can be directly derived to improve the method presented in this paper.
+Further work can also be directly derived to improve the method presented in this paper.
 The over-approximation on Process Hitting models without priorities proposed in~\cite{PMR12-MSCS}

### 2015-06-18 parts-sa.tex
remove mod commands

@@
 
-\modmf{%
-The previous subsections \modLP{introduced the necessary definitions to build the
-so-called} Local Causality Graph (LCG).
+The previous subsections introduced the necessary definitions to build the
+so-called Local Causality Graph (LCG).
 This graph is denoted $\cwB$ where $u$ is the local state to be reached
@@
 An example of LCG is depicted in \pref{fig:sa-livelock}.
-}
 
@@
 
-\modmf{%
 The definition of an LCG tackles two cases
@@
 are taken into account.
-}
 
-\modmf{%
 Finally, we note that
@@
 and thus did not require this kind of synchronization.
-}
-%However, \pref{def:lcg} is equivalent to the definition of the structure
-%given in~\cite{FPMR13-CS2Bio},
-%although it was adapted for AANs which notably allowed to simplify its formalism.
 

### 2015-09-21 parts-models-ph-php.tex
typo

@@
 
-In \pref{def:fop}, we define the the operator $\Fopsymbol$ which characterises the playability of an action
+In \pref{def:fop}, we define the operator $\Fopsymbol$ which characterises the playability of an action
 given the semantics of AAN$k$s (see \pref{def:playp}).
